### 2017-11-07 paper.tex
first draft

\documentclass{article}
\usepackage[utf8]{inputenc}

\usepackage[english]{babel}

\usepackage{blindtext}
\usepackage{amssymb}

\usepackage[]{algorithm}
\usepackage[]{algorithmic}
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{xr} 
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsthm}
\usepackage{comment}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{dblfloatfix}
\usepackage{bbm}

\newcommand{\IE}{IE}

\newcommand\floor[1]{\lfloor#1\rfloor}
\newcommand\ceil[1]{\lceil#1\rceil}

\newcommand{\bccomment}[1]{{\color{blue}BC: #1}}
\newcommand{\pfcomment}[1]{{\color{blue}PF: #1}}

\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}

\title{Incentivizing Exploration with Heterogeneous Utilities}

\begin{document}

\maketitle

\section{Problem Setting}
\label{sec:prob}
Suppose we have $N$ arms. For the $i^{th}$ arm, it has a latent utility vector $u_i\in \mathbb{R}^{m}$. As the principal, we hope to learn each arm's latent utility vector $u_i$ through the interaction with the agents. We denote $u_{i,t}$ as our estimation for $u_i$ at time t.

A stream of agents come to our system and we use $\theta\in \mathbb{R}^{m}$ to denote the agent's preference. We assume $\theta\sim F(\cdot)$.

Throughout this paper, we abbreviate ``agent with preference vector $\theta$'' as just ``$\theta$''. We denote the agent comes to the system at time $t$ as $\theta_{t}$. For simplicity, we assume each type of agents has a unique favourite arm, denoted agent $\theta$'s best arm index as $B(\theta)$.

At each time $t$, an agent comes to the system and can observe our current estimation $u_{i,t}$ for all arms. As the principal, we know $F(\cdot)$ from the prior knowledge. However, we do not know $\theta_t$.

Without incentive, each agent pulls the arm myopically, i.e. agent with $\theta_t$ will choose arm $A_t=\arg\max_{i}\{\theta_t\cdot u_{i,t}\}$. \bccomment{We focus on the linear utility function in the current writeup} To balance the exploration and exploitation, at time $t$, we (the principal) offer each arm an non-negative payment $c_{i,t}\geq 0$. In this case, we assume the agent with $\theta_t$ will pull the arm $A_t=\arg\max_{i}\{\theta_t\cdot u_{i,t}+c_{i,t}\}$, breaking tie in favor of the principal's incentive. We use $c_t=c_{A_{t},t}$ to denote the actual incentive payment at time $t$.

After the agent pulls an arm $A_t$, the principal can observe a noisy observation of $u_{A_{t}}$ in the form of $O_t=u_{A_{t}}+\epsilon_{t}$, where $\epsilon_t\sim N(0, \sigma^2 I_{m})$ is a $m$ dimensional white noise. Here, we use $I_m$ to denote a $m$ dimensional identity matrix. For simplicity, we assume the noise has the same variance across different dimensions, but same proof holds true even we assume different variance for each component.

We use $\tau(i,t)$ to denote the set of times which arm i was pulled up to time $t$. At each time $t$, $\tau(i,t)$ is updated as
\[ \tau(i,t) =
\begin{cases}
\tau(i,t-1) \cup \{t\}       & \text{if } i = A_t, \\
\tau(i,t-1)  & \text{if } i \neq A_t. \\
\end{cases}
\]

We use $N(i,t)$ to denote the total number of pulls for the $i_{th}$ arm up to time $t$, which is updated at each time $t$ as follows:
\[ N(i,t) =
\begin{cases}
N(i,t-1) + 1       & \text{if } i = A_t, \\
N(i,t-1)  & \text{if } i \neq A_t. \\
\end{cases}
\]

As the principal, we use the average of all previous observation for an arm as its estimation, i.e. $u_{i,t}=\frac{1}{N(i,t)}\sum_{k\in \tau(i,t)}O_{k}$. So after observing $O_t$, we update estimation for $u_{i,t}$ as follows:
\[ u_{i,t} =
\begin{cases}
u_{i,t-1}+\frac{O_t-u_{i,t-1}}{N(i,t)} & \text{if } i \neq A_t, \\
u_{i,t-1}  & \text{if } i \neq A_t. \\
\end{cases}
\]

Define the regret at time $t$ as $r(t)=\max_{i}\{\theta_{t}\cdot u_{i}\}-\theta_t\cdot u_{A_t}$. Denote the cumulative regret up to time T as $R(T)=\sum_{t=1}^{T}r(t)$. Denote the cumulative payment upto time T as $C(t)=\sum_{t=1}^{T}c(t)$.

As the principal, we want to find a strategy $\mathcal{A}$ which (1) minimizes the cumulative expected regret $\mathbb{E}_{\mathcal{A}}[R(T)]$ and (2) minimizes the cumulative expected payment $\mathbb{E}_{\mathcal{A}}[C(T)]$.

Throughout this paper, we assume $m\geq 2$. For $m=1$,  \cite{han2015incentivizing} provides a complete characterization for its solution.

\section{Upper Bound}

In this section, we propose a simple policy that mostly exploits, and occasionally incentivizes exploration when an arm would be unpulled by all agent types given the current posterior. We prove that with the help of heterogeneous preferences, we can get a certain amount of exploration for free via heterogeneity.

Throughout this section, we assume $F(\cdot)$ is a continuous distribution. Denote

\begin{align}
\Omega_{i,j}=\{\theta:B(\theta)=i, \hat{B}(\theta)=j\}, \nonumber 
\end{align}
which is the users whose best arm is arm $i$ and the second best arm is arm $j$. We need the following assumption in our analysis:

\begin{assumption} Let $f_{i,j}(y)$ be the density of $(u_i-u_j)\cdot\theta$ conditioned on $\theta \in \Omega_{i,j}$. We assume $M^{'}=\sup_{i,j}\limsup_{y\rightarrow 0^{+}}f_{i,j}(y) <\infty$.
\label{A1}
\end{assumption}

Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm. For simplicity in our analysis, we use a slightly stronger condition below: $M=\sup_{i,j}sup_{y\in R^{+}}f_{i,j}(y) <\infty$.

\begin{assumption} We assume $F$ has a compact support set. Without loss of generality, we assume $\theta\in [0,W]^m$.
\label{A2}
\end{assumption}

Throughout this write up, we use $R$ to denote the maximum regret it can occur at each time.

\subsection{Unknown $p$ Value}

Before we introduce our algorithm, we need to use the following definition:

\begin{definition}
We call time $t_{n}$ as the starting point of the $n_{th}$ round if $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$. We call the time period from $t_{n}$ to $t_{n+1}$ as the $n_{th}$ round.
\end{definition}

In this setting, we consider an algorithm that offers incentive to an arm if and only if 
\begin{itemize}
\item there is no agents will play it anymore;
\item this arm has not been played or incentivized before in this round.
\end{itemize}
We break ties randomly. If we decides to incentivize an arm, we use ``pay what it takes strategy''. This algorithm does not need to know $T$ in advance. The detailed algorithm is as follows:

\begin{algorithm}
\caption{Algorithm: Upper Bound}
\label{Alg1}
\begin{algorithmic}
\STATE Set n = 1 to denote the round number; g(n) to be a increasing function which we choose later;
\FOR{ $t = 1, 2, 3, \cdots$}{
	\IF{the myopic probability of pulling an arm is less than $g(n)^{-1}$ and we haven’t pulled that arm in this round}
	\STATE{ we pay whatever it takes to incentivize that arm}\ELSE 
		\STATE {let the agents play myopically}\ENDIF
		\STATE $n = min_{i} N(i,t)$
}\ENDFOR

\end{algorithmic}
\end{algorithm}

Now we analyze the regret occurred by Algorithm~\ref{Alg1} and its payment budget. Before we start our analysis, we need the following notations. Denote $\hat{B}(\theta)=\arg\max_{i\neq B(\theta)}\{\theta\cdot u_{i}\}$ to the $\theta$'s second best arm. We use $S(\delta)$ to denote the proportion of user whose utility difference between their best arm and the second best arm is less than $\delta$. Formally, $S(\delta)=P(\theta: \theta \cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}\leq \delta)$. Denote $\lambda(\delta)=\frac{\delta}{2m}$. Denote $p=\min_{i}P(\{\theta: B(\theta)=i\})$ and we assume $p>0$ in our analysis, where means for each arm $i$, there exist a positive proportion of users whose best arm is $i$. Denote $p(\delta)=\min_{i}P(\{\theta:\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$ and we know $p(0)=p$.

With the help of our assumptions and the above notations, we can prove the following main results:

\begin{theorem}
The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$.
\label{rst:budget}
\end{theorem}

\begin{theorem}
The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2) + O(N \sum_{n=1}^{T}n^{\alpha})$ for $-1<\alpha<0$.
\label{rst:regret}
\end{theorem}

Before we prove our main results, we need to prove several lemmas. First, based on assumption~\ref{A1}, we can get the following bound for $S(\delta)$.

\begin{lemma}
$S(\delta)\leq M\delta$.
\label{lemma:sdelta}
\end{lemma}

\begin{proof}
\begin{align}
S(\delta)&=\sum_{B(\theta)=i}\sum_{\hat{B}(\theta)=j}P(\{\theta(u_{i}-u_{j})<\delta\}) \nonumber \\
&=\sum_{B(\theta)=i}\sum_{\hat{B}(\theta)=j}P(\{\theta(u_{i}-u_{j})<\delta|\theta\in \Omega_{i,j}\})P(\theta\in \Omega_{i,j}) \nonumber \\
&\leq \sum_{B(\theta)=i}\sum_{\hat{B}(\theta)=j}M\delta \times P(\theta\in \Omega_{i,j}) \nonumber \\
&=M\delta \nonumber 
\end{align}
\end{proof}

The following lemma bounds the probability of making a mistake if we let the agents play myopically in the $n_{th}$ round, given that the utility difference between his/her best and second best arm is bounded below by a constant.

\begin{lemma}
For those user whose utility difference between their best arm and the second best arm is at least $2m\lambda$, the probability that myopic action can incur regret at any time $t\in [t_{n-1},t_{n}-1]$ in the $n_{th}$ round is bounded above by $24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
\label{round:prob}
\end{lemma}

We need the following lemma in order to prove Lemma~\ref{round:prob}.

\begin{lemma}
For $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$, we have
\begin{align}
\frac{n\lambda}{2\sqrt{2}\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
\end{align}
\label{n0-inequality}
\end{lemma}

\begin{proof}
First, we observe that
\begin{align}
&\frac{n\lambda}{2\sqrt{2}\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)} \nonumber \\
\iff &\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{4.8\sigma^2}{\lambda^2}. \nonumber 
\end{align}
Since $\log(x)\leq x-1$ for $x>0$, we know 
\begin{align}
\log(\log_{1.1}(n)+1)=\log\left(\frac{\log(n)}{\log(1.1)}+1\right)\leq \log(11\log(n)+1)\leq \log(11n)\leq 3+\log(n). \nonumber
\end{align}

Thus, we know
\begin{align}
\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{n}{3+\log(n)}. \nonumber 
\end{align}

In order to prove the original lemma, we just need to show for $n\geq n_{0}$, we have
\begin{align}
\frac{n}{3+\log(n)}\geq \frac{4.8\sigma^2}{\lambda^2}. \label{n0-equ}
\end{align}
Inequality~(\ref{n0-equ}) is true because the following two observations:
\begin{itemize}
\item for $n\geq 50$, we have $\frac{n}{3+\log(n)}\geq n^{0.5}$;
\item $n\geq \frac{23.04\sigma^4}{\lambda^4}$ we have $n^{0.5}\geq {4.8\sigma^{2}}{\lambda^{2}}$.
\end{itemize}

Thus, we know our lemma is true.

\end{proof}

We also need to use an adaptive concentration inequality, which is introduce in \cite{zhao2016adaptive}. For reference, we state it as a Lemma.

\begin{lemma}[Corollary 1 in \cite{zhao2016adaptive}]
Let $X_{i}$ be zero mean $1/2$-subgaussian random variables. $\{S_{n}=\sum_{i=1}^{n}X_{i},n\geq 1\}$ be a random walk. Let $J$ be any random variable taking value in $\mathbb{N}$. If
\begin{align}
f(n)=\sqrt{0.6n\log(\log_{1.1}(n)+1)+bn}, \nonumber
\end{align}
then
\begin{align}
Pr[S_{J}\geq f(J)]\leq 12e^{-1.8b}. \nonumber
\end{align}
\label{ACI-inequality}
\end{lemma}

Now we can get back to prove Lemma~\ref{round:prob}.

\begin{proof}
In the $n_{th}$ round, we know all arms have been pulled at least $n$ times. Thus, the probability that myopic action can occur regret is bounded by
\begin{align}
&P(\text{myopic action incurs regret})\nonumber \\
\leq &P(\exists i, \exists j, |u_{i,t}^{j}-u_{i}^{j}|>\lambda) \nonumber \\
\leq & \sum_{i}\sum_{j} P(|u_{i,t}^{j}-u_{i}^{j}|>\lambda) \nonumber \\
= &  \sum_{i}\sum_{j} P\left(\bigg|\sum_{k\in \tau_{i,t}}\epsilon_{k}\bigg|>N(i,t)\lambda\right). \label{ACI}
\end{align}

To bound equation~(\ref{ACI}), we need to use Lemma~\ref{ACI-inequality}. Similar to Lemma~\ref{ACI-inequality}, we define
\begin{align}
S_{N(i,t)}=\sum_{k\in\tau_{i,t}}\frac{\epsilon_{k}}{\sqrt{2}\sigma}=\frac{1}{\sqrt{2}\sigma}\sum_{k\in\tau_{i,t}}\epsilon_{k}. \nonumber
\end{align}

Based on Lemma~\ref{n0-inequality}, we know there exists a $n_{0}=\max\{50, \frac{23.04\sigma^2}{\lambda^2}\}$ such that for $n\geq n_{0}$, we have
\begin{align}
\frac{n\lambda}{2\sqrt{2}\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
\end{align}

Thus, if we set $b=\frac{n\lambda^2}{8\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,t)\geq n\geq n_{0}$, we have
\begin{align}
\frac{N(i,t)\lambda}{\sqrt{2}\sigma}\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)}+\frac{\lambda}{2\sqrt{2}\sigma}\sqrt{n N(i,t)} \nonumber \\
\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+bN(i,t)}, \nonumber 
\end{align}
where the last inequality is because $\sqrt{x}+\sqrt{y}\geq \sqrt{x+y}$. Thus, we have
\begin{align}
&P\left(\bigg|\sum_{k\in \tau_{i,t}}\epsilon_{k}\bigg|>N(i,t)\lambda\right) \nonumber \\
=&2P\left(S_{N(i,t)}>\frac{N(i,t)\lambda}{\sqrt{2}\sigma}\right) \nonumber \\
\leq & 2P\left(S_{N(i,t)}> \sqrt{0.6 N_{i,t}\log(\log_{1.1}(N(i,t))+1)+b N(i,t)}\right) \nonumber \\
\leq & 24\exp( -1.8b) \nonumber \\
= & 24\exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber
\end{align}

Thus, we know
\begin{align}
&\sum_{i}\sum_{j} P\left(\bigg|\sum_{k\in \tau_{i,t}}\epsilon_{k}\bigg|>N(i,t)\lambda\right)  \nonumber \\
=& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber
\end{align}

\end{proof}

Before we start analyzing the cumulative regret, we first prove the following lemma which bounds the expected length of each round.

\begin{lemma}
Using our algorithm, we have $\mathbb{E}[t_{n}-t_{n-1}]\leq Ng(n)$, $\forall n\geq 1$.
\label{round:length}
\end{lemma}

\begin{proof}
In each round, each arm needs to be pulled at least once. Denote $X_{i}$ to be the number of agents come to the system between $i-1$ different arms were pulled and the $i_{th}$ different arm was pulled. Then we know 
\begin{align}
\mathbb{E}[t_{n}-t_{n-1}]=\sum_{i=1}^{N}E[X_{i}]. \nonumber
\end{align}

Denote $t^{0}=t_{n-1}+\sum_{j=1}^{i-1}X_{j}$, then $X_{i}$ follows a ``geometric distribution'', which counts the total number of trials before the $i_{th}$ different arm were pulled at time $t=t^{0},t^{0}+1,\cdots$. At each time $t=t^{0}, t^{0}+1,\cdots$, there are two possibilities for a success trial:
\begin{itemize}
\item If there exists an arm has not been pulled and the proportion of agents who would pull this arm is less than $\frac{1}{g(n)}$, then based on our algorithm, the principal will offer an payment for that arm and it will be pulled. In this case, the probability that the $i_{th}$ different arm will be pulled is 1.  
\item There exists at least $\frac{1}{g(n)}$ proportion of agents who will choose an un-pulled arm as his/her myopic action. In this case, we know each type of agent shows up with probability at least $p$. Thus, the probability that the $i_{th}$ different arm will be pulled is at least $\frac{1}{g(n)}$.
\end{itemize}

Since $X_{i}$ follows a ``geometric distribution'' with success probability at least $\frac{1}{g(n)}$ at each time, we know 
\begin{align}
E[t_{n}-t_{n-1}]\leq Ng(n). \nonumber
\end{align}
\end{proof}

\begin{lemma}
The expected incentive payment at round $n$ is bounded above by \bccomment{How to bound this conditional expectation?}
\end{lemma}

\begin{proof}
Denote $\Delta=\sup_{\theta}\max_{i}\{\theta\cdot u_{B(\theta)}-\theta\cdot u_{i}\}$ to be the theoretical maximum payment with no noisy. We first consider the expected payment for arm $1$ in the $n_{th}$ round. Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$.

\begin{align}
&E[\max_{i}\theta_t\cdot u_{i,t}-\theta_t\cdot u_{1,t}|\text{agents pull arm $1$ with prob less than $g(n)^{-1}$}] \nonumber \\
\leq & \Delta + E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\theta_t\cdot \epsilon_{B(\theta_t),t}|\text{agents pull arm $1$ with prob less than $g(n)^{-1}$}] \nonumber 
\end{align}

Denote $p_1=P_{\theta\sim F}(B(\theta)=1)$.

If in the $n_{th}$ round we have $g(n)^{-1}>p_1$:

If in the $n_{th}$ round we have $g(n)^{-1}<\frac{p}{2}$:
\begin{align}
E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\theta_t\cdot \epsilon_{B(\theta_t),t}|\text{agents pull arm $1$ with prob less than $g(n)^{-1}$}]  \nonumber 
\end{align}

\end{proof}

Now we are ready to prove our first main result, Theorem~\ref{rst:budget}.

\begin{proof}
If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2m\lambda\}$, they will correctly identify their best arm. Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, and $1/g(n)<p/2$, we do not need to incentivize any arms.

Denote 
\begin{align}
n_{1}=\max\bigg\{50, \frac{23.04\sigma^4}{\lambda\left(p^{-1}(\frac{p}{2})\right)^4},\min_{n}\{n:1/g(n)<\frac{p}{2}\}\bigg\}. \nonumber
\end{align}

The cumulative payment is bounded above by:

\begin{align}
&E[C(T)] \nonumber \\
= & \sum_{t=1}^{\infty}E[\mathbbm{1}\{\text{need to offer payment to an arm}\}] \nonumber \\
\leq &\sum_{n=1}^{\infty}\sum_{t=1}^{\infty}E[\mathbbm{1}\{t_{n-1}\leq t\leq t_{n}: \text{myopic action occurs regret for agents with } \nonumber \\
&\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq p^{-1}(1/g(n))\}\}] \nonumber \\
\leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}P(\text{myopic action occurs regret for agents with }\nonumber \\
&\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq p^{-1}\left(\frac{p}{2}\right)\}|t_{n-1}\leq t\leq t_{n})P(t_{n-1}\leq t\leq t_{n})+Nn_{1} \nonumber \\
\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\left(p^{-1}(\frac{p}{2})\right)^2}{32m^2\sigma^2}\right)\times Ng(n)+Nn_{1} \nonumber 
\end{align}

If we choose $g(n)=n$ and $\delta_{0}=p^{-1}(\frac{p}{2})$, then we have
\begin{align}
\frac{1}{n}<\frac{p}{2} \implies n\geq (\frac{2}{p})+1. \nonumber
\end{align}
We know the expected payment is bounded above by:
\begin{align}
E[C(T)] \leq 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2}+N(\max\{n_{0},(\frac{2}{p})+1\}). \nonumber
\end{align}

Since we have $N$ arms in total, we know the $\mathbb{E}[C(T)]=O(N^2)$.\end{proof}

Now we are ready to prove our second main result, Theorem~\ref{rst:regret}.

\begin{proof}
For regret occurred in the first $n_0$ round, it is bounded above by $\sum_{n=1}^{n_{0}}NRg(n)$.

For regret occurred after the first $n_0$ round, it has two different components: the regret occurred when we let the agents play myopically and the regret occured when we incentivize the agents. For the regret occurred when we let the agents play myopically at time t, it consists of the following two components:
\begin{itemize}
\item For those user whose utility difference between their best and the second best arm is greater than $f(t)$: suppose it is at the $n(t)_{th}$ round, the probability of these user making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n(t) f(t)^2}{32 m^2\sigma^2}\right)$ at time $t$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n(t) f(t)^2}{32 m^2\sigma^2}\right)\times R$. We denote the regret occured by these agents as $r_1(t)$.
\item For those user whose utility difference between their best and the second best arm is smaller than $f(t)$: this happens with probability $S(f(t))$ at each time and regret is bounded above by $S(f(t)) \times f(t)=Mf(t)^2$. We denote the regret occured by these agents as $r_2(t)$.
\end{itemize}

Thus, the cumulative expected regret occured up to time $T$ when we let the agent play myopically is bounded above by:
\begin{align}
&E\left[\sum_{t=1}^{T}r(t)\right] \nonumber \\
=&E\left[\sum_{t=1}^{t_{n_{0}}} r(t) + \sum_{t=t_{n_{0}}}^{T}(r_1(t)+r_2(t))\right]  \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRg(n) + E\left[\sum_{t=t_{n_{0}}}^{T}r_1(t)\right]+ E\left[\sum_{t=t_{n_{0}}}^{T}r_2(t)\right] \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRg(n) + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRg(n) + \sum_{n=n_{0}}^{T}E\left[\sum_{t=t_{n}}^{t_{n+1}}24Nm\exp\left(-\frac{1.8n f(t)^2}{32 m^2\sigma^2}\right) R\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRg(n) + \sum_{n=n_{0}}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(t_n)^2}{32 m^2\sigma^2}\right)R \times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRg(n) + \sum_{n=1}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)R\times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
\leq & \sum_{n=1}^{n_{0}}NRg(n) + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Ng(n)+ \sum_{t=1}^{T}Mf(t)^2 \nonumber
\end{align}

The expected regret occurred when we incentivize the agents is calculated in Theorem~\ref{rst:budget}. Thus if we set $g(n)=n$, the cumulative regret at time $T$ is bounded above by
\begin{align}
&\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
+ & 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2}+N(\max\{n_{0},(\frac{2}{p})+1\}). \nonumber
\end{align}

For a fixed $T$, we only need to minimizing the following two terms since all others are constant:

\begin{align}
\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2.
\end{align}

For a fixed $T$, if we choose $f(n)=n^{-1/2+\frac{1}{2\log(T)}}$, we have
\begin{align}
&\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
\leq & \sum_{n=1}^{T} 24N^{2} Rmn\exp\left(-\frac{1.8n^{1/\log(T)}}{32 m^2\sigma^2}\right) + \left(\sum_{t=1}^{T} Mn^{-1}\right) \times T^{\frac{1}{\log(T)}} \nonumber \\
= & + e(\log(T) + 1)
\end{align}

\end{proof}

\section{Lower Bound $O(\log(T))$}
\label{sec:continuous}

In this section, we assume $\theta$ follows a continuous distribution $F(\cdot)$. We provide a example to show the best possible lower bound is $O(N\log(T))$.

Suppose you have two arms. Arm $1$ has utility vector $(0,0)$ and arm $2$ has utility vector $(0,1)$. We assume the users' preference are uniformly distributed on the unit circle. If the user knows the true reward for both arms, then the users with preference on the bottom half circle will choose arm $1$ and the users with preference on the top half circle will choose arm $2$.

Consider the following algorithm: at each step, let the agents play myopically; however, they are going to see the noisy rewards for both arms.

For simplicity, we assume that the agents already know the true utility vector for arm $1$. Without loss of generality, denote $u_{t} = (0,1)+(z_{t1},z_{t,2}) = (0,1)+ (N(0,1/n),N(0,1/n))$ to be the estimate reward for arm $2$ (I assume the variance for the noise is $1$).

At time $n$, suppose we know arm $1$ has utility vector $(0,0)$ and arm $2$ has utility vector $u_n\sim (N(0,\frac{1}{n}), N(1,\frac{1}{n}))$. Since we know $(z_{t,1}, z_{t,2})$ is symmetric around $(0,0)$, we know

\begin{align}
&E[r_n] \nonumber \\
= &E[r_n | z_{n,1}>0,z_{n,2}>0] \times P(z_{n,1}>0,z_{n,2}>0) + E[r_n |z_{n,1}>0,z_{n,2}<0] \times P(z_{n,1}>0,z_{n,2}<0) \nonumber \\
= &E[r_n | z_{n,1}<0,z_{n,2}>0] \times P(z_{n,1}<0,z_{n,2}>0) + E[r_n |z_{n,1}<0,z_{n,2}<0] \times P(z_{n,1}<0,z_{n,2}<0) \nonumber \\
\geq & 0.25 \times E[r_n | z_{n,1}>0, z_{n,2}>0]. \nonumber
\end{align}

Given $z_{n,1}>0$ and $z_{n,2}>0$, we know the user between $(-1,0)$ and $(\frac{-1-z_{n,2}}{\sqrt{z_{n,1}^2+(1+z_{n,2})^2}}, \frac{z_{n,1}}{\sqrt{z_{n,1}^2+(1+z_{n,2})^2}})$ and the user between $(1,0)$ to $(\frac{1+z_{n,2}}{\sqrt{z_{n,1}^2+(1+z_{n,2})^2}}, \frac{-z_{n,1}}{\sqrt{z_{n,1}^2+(1+z_{n,2})^2}})$ will make a mistake. And the regret is the absolute value of the second coordinate of the user's preference vector. Thus, we know

\begin{align}
&E[r_n| z_{n,1}>0, z_{n,2}>0] \nonumber \\
=& 4\times 2 \int_{0}^{\infty} \int_{0}^{\infty} \int_{0}^{\arctan(\frac{z_{n,1}}{1+z_{n,2}})}\frac{\sin(\theta)}{2\pi}d(\theta)\frac{e^{-\frac{n \times z_{n,1}^2}{2}}\sqrt{n}}{\sqrt{2\pi}}d(z_{n,1})\frac{e^{-\frac{n \times z_{n,2}^2}{2}}\sqrt{n}}{\sqrt{2\pi}}d(z_{n,2}) \nonumber \\
=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}n\times [1-\frac{1+z_{n,2}}{\sqrt{z_{n,1}^2+(1+z_{n,2})^2}}]e^{-\frac{n \times z_{n,1}^2}{2}}e^{-\frac{n \times z_{n,2}^2}{2}}d(z_{n,1})d(z_{n,2}) \nonumber \\
=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty} \left[1-\frac{\sqrt{n}+z_{n,2}}{\sqrt{z_{n,1}^2+(\sqrt{n}+z_{n,2})^2}}\right]e^{-\frac{z_{n,1}^2}{2}}e^{-\frac{z_{n,2}^2}{2}}d(z_{n,1})d(z_{n,2}) \nonumber 
\end{align}

Below, we want to show 
\begin{align}
\lim_{n\rightarrow}\frac{E[r_n| z_{n,1}>0, z_{n,2}>0]}{n} = O(1). \nonumber
\end{align}

Denote $d(n)=n\left[1-\frac{\sqrt{n}+z_{n,2}}{\sqrt{z_{n,1}^2+(\sqrt{n}+z_{n,2})^2}}\right]$.
Since
\begin{align}
d^{'}(n)=\frac{-z_{n,1}^2(2z_{n,2}+3\sqrt{n})-2(z_{n,2}+\sqrt{n})^3}{2(z_{n,1}^2+(z_{n,2}+\sqrt{n})^2)^{3/2}}+1. \nonumber
\end{align}

and $\lim_{n\rightarrow \infty}d^{'}(n)=2$, we know for $n$ large enough, $d(n)$ is a increasing function in terms of n. Thus, based on the Monotone Convergence Theorem, we have

\begin{align}
&\lim_{n\rightarrow \infty}\frac{E[r_n| z_{n,1}>0, z_{n,2}>0]}{n} \nonumber \\
=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{n\rightarrow \infty}\left[ \left[1-\frac{\sqrt{n}+z_{n,2}}{\sqrt{z_{n,1}^2+(\sqrt{n}+z_{n,2})^2}}\right]e^{-\frac{z_{n,1}^2}{2}}e^{-\frac{z_{n,2}^2}{2}}\right]d(z_{n,1})d(z_{n,2}) \nonumber  
\end{align}

Based on Wolframalpha, we know

\begin{align}
\lim_{n\rightarrow \infty} d(n)=\frac{z_{n,1}^2}{2}. \nonumber
\end{align}
Thus,
\begin{align}
&\lim_{n\rightarrow \infty}\frac{E[r_n| z_{n,1}>0, z_{n,2}>0]}{n} \nonumber \\
=&\frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{n\rightarrow \infty}\left[ \frac{z_{n,1}^2}{2}e^{-\frac{z_{n,1}^2}{2}}e^{-\frac{z_{n,2}^2}{2}}\right]d(z_{n,1})d(z_{n,2}) = \frac{1}{2\pi}. \nonumber
\end{align}

Thus, the cumulative expected regret is at least $O(\log(T))$.

\section{Conclusion}

\bibliography{reference}{}
\bibliographystyle{plain}

\end{document}

### 2017-11-07 paper.tex
added a introduction and edited a little

@@
 
+\section{Introduction}
+In this paper, we study a variant of incentivizing exploration with heterogeneous agents' preferences, that generalizes \cite{frazier2014incentivizing} and \cite{han2015incentivizing}.
+
+In our setting we have arms that have unknown multivariate attributes, and agents have heterogeneous utility functions that map these attribute vectors onto utilities.
+All agents see the attribute outcomes from previous agents.
+We study a simple policy that mostly exploits, and occasionally incentivizes exploration when an arm would be unpulled by all agent types given the current posterior.
+
+The intuition behind is that heterogeneity of a certain kind reduces but doesn't eliminate the need for incentivizing exploration --- basically that you get a certain amount of exploration for free via heterogeneity.
+
+We structure our paper as follows: In Section~\ref{sec:prob}, we state our problem formulation; In Section~\ref{sec:ub}, we state our algorithm and prove a upper bound for both the payment budget as well as the regret; In Section~\ref{sec:lb}, we construct an example to show that the regret bound is at least $O(\log(T))$ in the worst case example, regardless the payment budget.
+
+\subsection{Related Work}
+
+With money transfer: \cite{frazier2014incentivizing} considers a problem setting where the principal pays the agents extra money in order to incentivize them to explore.
+In their paper, they assume all agents have equal value of money and provide a complete characterization of achievable reward with a fixed budget.
+\cite{han2015incentivizing} generalizes this framework to allow agents have heterogeneous value of money.
+Further, it assumes there is a external signal scheme which provides partial information about each agent.
+Under this setting, they proved a similar bound as in \cite{frazier2014incentivizing} which depends on the signal scheme.
+
+Without money transfer but using information asymmetry:
+\cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time.
+\cite{mansour2015bayesian} generalizes \cite{kremer2014implementing} by allowing finite number of actions at each time.
+\cite{mansour2016bayesian} considers a problem setting where there are multiple agents at each time and allow agents to interact with each other.
+At each time, the principal provides each agent an recommendation, which is Bayesian incentive-compatible.
+They prove principal can achieve constant regret when utilities are deterministic and logarithmic regret when utilities are stochastic.
+
+\subsection{Applications}
+
+The motivation of this project is to build a recommender system.
+Agent arrives to the system one at a time.
+Upon arrival, he/she receives a recommendation from the system and chooses a product based on the recommendation.
+At the end, the agent provides some feedback about the product when he/she leaves the system.
+Here are a few applications where we can apply our framework:
+
+\begin{itemize}
+\item \textit{Recommender systems/Online Retailers}: For recommender systems such as Yelp, they want to find the best restaurants based on the user's review.
+As the system, it wants all restaurants to have as many reviews as possible so that it knows which restaurants are good.
+However, as a user, he/she may only want to try the restaurants with a large number of positive reviews.
+In this case, the system may incentivize the user to review the new restaurants by offering them extra money as a reward.
+As for users, they may have different utilities vectors about the restaurant's location, environment, service, queueing time etc, which could be the restaurant's attribute vector.
+This is also the case for online retailers such as Amazon.
+In this case, the attribute vector could be each item's quality, design and price etc.
+\item \textit{Citizen Science}:  \cite{frazier2014incentivizing} mentioned for scientific organizations like Galaxy Zoo, they will guide the enthusiasts to explore the less-explored parts of domain.
+For each enthusiast, he/she may have different preference towards the location's sight-seeing, weather, distance and safety etc.
+Thus, as the organization, it needs to incentivize each person differently.
+\end{itemize}
+
 \section{Problem Setting}
 \label{sec:prob}
-Suppose we have $N$ arms.
-For the $i^{th}$ arm, it has a latent utility vector $u_i\in \mathbb{R}^{m}$.
-As the principal, we hope to learn each arm's latent utility vector $u_i$ through the interaction with the agents.
-We denote $u_{i,t}$ as our estimation for $u_i$ at time t.
 
+Suppose we have $N$ arms. For the $i^{th}$ arm, it has a latent utility vector $u_i\in \mathbb{R}^{m}$. 
 A stream of agents come to our system and we use $\theta\in \mathbb{R}^{m}$ to denote the agent's preference. We assume $\theta\sim F(\cdot)$.
+Each agent would pull one arm based on his/her preference and provides the feedback before he/she leaves.
+As the principal, we hope to learn each arm's latent utility vector $u_i$ through the interaction with the agents. We denote $u_{i,t}$ as our estimation for $u_i$ at time t.
 
@@
 We denote the agent comes to the system at time $t$ as $\theta_{t}$.
-For simplicity, we assume each type of agents has a unique favourite arm, denoted agent $\theta$'s best arm index as $B(\theta)$.
+We denote agent $\theta$'s best arm index as $B(\theta)$ (break ties randomly).
 
@@
 As the principal, we know $F(\cdot)$ from the prior knowledge.
-However, we do not know $\theta_t$.
+However, we do not know each agent's preference vector $\theta_t$.
 
@@
 
-Throughout this paper, we assume $m\geq 2$. For $m=1$,  \cite{han2015incentivizing} provides a complete characterization for its solution.
-
 \section{Upper Bound}
+\label{sec:ub}
 
@@
 
-Throughout this section, we assume $F(\cdot)$ is a continuous distribution. Denote
+\subsection{Assumptions}
+Throughout this section, we use $F(\cdot)$ to denote the agent's preference distribution, which could either be a continuous distribution or a discrete distribution. Denote
 
@@
 \end{align}
-which is the users whose best arm is arm $i$ and the second best arm is arm $j$. We need the following assumption in our analysis:
+which is the users whose best arm is arm $i$ and the second best arm is arm $j$. We need the following assumptions in our analysis:
 
-\begin{assumption} Let $f_{i,j}(y)$ be the density of $(u_i-u_j)\cdot\theta$ conditioned on $\theta \in \Omega_{i,j}$. We assume $M^{'}=\sup_{i,j}\limsup_{y\rightarrow 0^{+}}f_{i,j}(y) <\infty$.
+\begin{assumption} Let $f_{i,j}(y)$ be the marginal probability density function (or marginal probability mass function if $F(\cdot)$ is a discrete distribution) of $(u_i-u_j)\cdot\theta$ conditioned on $\theta \in \Omega_{i,j}$.
+We assume $M^{'}=\max_{i,j}\limsup_{y\rightarrow 0^{+}}f_{i,j}(y) <\infty$.
 \label{A1}
@@
 Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm.
-For simplicity in our analysis, we use a slightly stronger condition below: $M=\sup_{i,j}sup_{y\in R^{+}}f_{i,j}(y) <\infty$.
+For simplicity in our analysis, we use a slightly stronger condition below: $M=\max_{i,j}sup_{y\in R^{+}}f_{i,j}(y) <\infty$.
 
@@
 
-Throughout this write up, we use $R$ to denote the maximum regret it can occur at each time.
+Throughout this write up, we use $R$ to denote the maximum regret it can occur at each time. We know $R<\infty$ due to Assumption~\ref{A2}.
 
-\subsection{Unknown $p$ Value}
+\begin{assumption}
+Denote $p=\min_{i}P(\{\theta: B(\theta)=i\})$. Throughout this paper, we assume $p>0$.
+\label{A3}
+\end{assumption}
 
+Assumption~\ref{A3} means for each arm $i$, there exist a positive proportion of users whose best arm is $i$.
+
+\subsection{Our Algorithm}
 Before we introduce our algorithm, we need to use the following definition:
@@
 
+\subsection{General Results}
+
 Now we analyze the regret occurred by Algorithm~\ref{Alg1} and its payment budget.
@@
 Denote $\lambda(\delta)=\frac{\delta}{2m}$.
-Denote $p=\min_{i}P(\{\theta: B(\theta)=i\})$ and we assume $p>0$ in our analysis, where means for each arm $i$, there exist a positive proportion of users whose best arm is $i$.
 Denote $p(\delta)=\min_{i}P(\{\theta:\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$ and we know $p(0)=p$.
@@
 
-Before we prove our main results, we need to prove several lemmas. First, based on assumption~\ref{A1}, we can get the following bound for $S(\delta)$.
+Before we prove our main results, we need to prove several lemmas. First, based on Assumption~\ref{A1}, we can get the following bound for $S(\delta)$.
 
@@
 
+\subsection{Special Case}
+
+In this section, we consider a special case of our problem, in which the agent's preference distribution $F(\cdot)$ satisfies $S(\delta)=0$ for $\delta<\delta^{'}$.
+Under this assumption, we still have $O(N^2)$ budget bound, however we get a better regret bound.
+The proof is similar to the proof of Theorem~\ref{rst:regret}, but for $t$ large enough, $S(f(t))=0$.
+Thus,
+
+\subsection{Practical Issues}
+
+In our algorithm, we take ``pay what it takes'' strategy when we decided to incentivize the agent. However, as long as
+
 \section{Lower Bound $O(\log(T))$}
-\label{sec:continuous}
+\label{sec:lb}
 

### 2017-11-08 paper.tex
Edits to section 2

@@
 \newcommand{\IE}{IE} 
+\newcommand{\argmax}{\mathop{\mathrm{argmax}}}
 
@@
 
-Suppose we have $N$ arms. For the $i^{th}$ arm, it has a latent utility vector $u_i\in \mathbb{R}^{m}$. 
-A stream of agents come to our system and we use $\theta\in \mathbb{R}^{m}$ to denote the agent's preference. We assume $\theta\sim F(\cdot)$.
-Each agent would pull one arm based on his/her preference and provides the feedback before he/she leaves.
-As the principal, we hope to learn each arm's latent utility vector $u_i$ through the interaction with the agents. We denote $u_{i,t}$ as our estimation for $u_i$ at time t.
+We have $N$ arms. Arm $i$ has a fixed but unknown attribute vector $u_i\in \mathbb{R}^{m}$.
 
-Throughout this paper, we abbreviate ``agent with preference vector $\theta$'' as just ``$\theta$''.
-We denote the agent comes to the system at time $t$ as $\theta_{t}$.
-We denote agent $\theta$'s best arm index as $B(\theta)$ (break ties randomly).
+A stream of myopic selfish agents come to our system.
+Agent $t$ has linear preferences over attributes described by a vector $\theta_t \in \mathbb{R}^m$ that is unknown to the principal and drawn iid from a known distribution $F$.
+We refer synonomously to an agent and that agent's preference vector: when we say ``an agent $\theta$'', we mean ``an agent with preference vector $\theta$.''
 
-At each time $t$, an agent comes to the system and can observe our current estimation $u_{i,t}$ for all arms.
-As the principal, we know $F(\cdot)$ from the prior knowledge.
-However, we do not know each agent's preference vector $\theta_t$.
+Each agent $t$ chooses an arm to pull $A_t$, according to a process described below, and obtains utility $\theta_t \cdot u_{A_{t}}$.
+The principal and all agents then see a noisy observation of the attribute vector of the pulled arm of the form $O_t=u_{A_{t}}+\epsilon_{t}$, where $\epsilon_t\sim N(0, \sigma^2 I_{m})$ is independent normally distributed noise, and $I_m$ denotes an $m$-dimensional identity matrix.
+Although we assume a common variance across attributes for simplicity of presentation, our theoretical results hold if the variance differs.
 
-Without incentive, each agent pulls the arm myopically, i.e.
-agent with $\theta_t$ will choose arm $A_t=\arg\max_{i}\{\theta_t\cdot u_{i,t}\}$.
-\bccomment{We focus on the linear utility function in the current writeup} To balance the exploration and exploitation, at time $t$, we (the principal) offer each arm an non-negative payment $c_{i,t}\geq 0$.
-In this case, we assume the agent with $\theta_t$ will pull the arm $A_t=\arg\max_{i}\{\theta_t\cdot u_{i,t}+c_{i,t}\}$, breaking tie in favor of the principal's incentive.
+At each time $t$, for each arm $i$, we (the principal) offer a non-negative payment $c_{i,t}\geq 0$ based on previous observations.
+We assume that agent $t$ chooses to pull the arm that myopically maximizes the sum of this payment and an estimate of the utility obtained $\theta_t \cdot u_{i,t}$ where $u_{i,t}$ denotes the simple average of $O_s$ over all previous pulls of arm $i$ if it has been pulled at least once, or a default value of $0$ if not.
+That is, $u_{i,t} = \sum_{s<t} O_s 1\{A_s = i\} / \sum_{s<t} 1\{A_s = i\}$ if the denominator is strictly positive and $0$ otherwise; and $A_t=\argmax_{i}\{\theta_t\cdot u_{i,t}\}$, breaking ties in favor of the arm with the highest incentive.
 We use $c_t=c_{A_{t},t}$ to denote the actual incentive payment at time $t$.
+\pfcomment{Bangrui, I assumed that $u(i,t)$ starts from $0$.
+Do you want to do this, or do you want to assume that every arm is pulled at least once?
+Or do you want to assume that they start from some general starting value?
+We could perhaps do the analysis assuming they start from $0$, but then comment that the proofs all carry through if they start from some other value.}
 
-After the agent pulls an arm $A_t$, the principal can observe a noisy observation of $u_{A_{t}}$ in the form of $O_t=u_{A_{t}}+\epsilon_{t}$, where $\epsilon_t\sim N(0, \sigma^2 I_{m})$ is a $m$ dimensional white noise.
-Here, we use $I_m$ to denote a $m$ dimensional identity matrix.
-For simplicity, we assume the noise has the same variance across different dimensions, but same proof holds true even we assume different variance for each component.
+This behavior may be recovered if agents are Bayesian and share a common non-informative prior distribution that is constant over $\mathbb{R}^m$ and know $\sigma^2$.
+In this case, the posterior distribution on $u_{i}$ at time $t$ is multivariate normal with mean $u_{i,t}$, and the expected value of $\theta_t \cdot u_i$ under this posterior conditioned on $\theta_t$ is $\theta_t \cdot u_{i,t}$ \cite[equation 2.13 in section 2.5]{Ge04}.
+Alternatively, one may simply take our assumption that agents use the average as their estimate of an attribute value directly without such a Bayesian justification.
 
-We use $\tau(i,t)$ to denote the set of times which arm i was pulled up to time $t$. At each time $t$, $\tau(i,t)$ is updated as
-\[ \tau(i,t) =
-\begin{cases}
-\tau(i,t-1) \cup \{t\}       & \text{if } i = A_t, \\
-\tau(i,t-1)  & \text{if } i \neq A_t. \\
-\end{cases}
-\]
+We define the regret at time $t$ as $r(t)=\max_{i}\{\theta_{t}\cdot u_{i}\}-\theta_t\cdot u_{A_t}$, and the cumulative regret up to time T as $R(T)=\sum_{t=1}^{T}r(t)$.
+Define the cumulative payment up to time T similarly as $C(t)=\sum_{t=1}^{T}c(t)$.
+As the principal, we want to find a strategy $\mathcal{A}$ under which both the cumulative expected regret $\mathbb{E}_{\mathcal{A}}[R(T)]$ and the cumulative expected payment $\mathbb{E}_{\mathcal{A}}[C(T)]$ are small.
 
-We use $N(i,t)$ to denote the total number of pulls for the $i_{th}$ arm up to time $t$, which is updated at each time $t$ as follows:
-\[ N(i,t) =
-\begin{cases}
-N(i,t-1) + 1       & \text{if } i = A_t, \\
-N(i,t-1)  & \text{if } i \neq A_t. \\
-\end{cases}
-\]
-
-As the principal, we use the average of all previous observation for an arm as its estimation, i.e.
-$u_{i,t}=\frac{1}{N(i,t)}\sum_{k\in \tau(i,t)}O_{k}$.
-So after observing $O_t$, we update estimation for $u_{i,t}$ as follows:
-\[ u_{i,t} =
-\begin{cases}
-u_{i,t-1}+\frac{O_t-u_{i,t-1}}{N(i,t)} & \text{if } i \neq A_t, \\
-u_{i,t-1}  & \text{if } i \neq A_t. \\
-\end{cases}
-\]
-
-Define the regret at time $t$ as $r(t)=\max_{i}\{\theta_{t}\cdot u_{i}\}-\theta_t\cdot u_{A_t}$.
-Denote the cumulative regret up to time T as $R(T)=\sum_{t=1}^{T}r(t)$.
-Denote the cumulative payment upto time T as $C(t)=\sum_{t=1}^{T}c(t)$.
-
-As the principal, we want to find a strategy $\mathcal{A}$ which (1) minimizes the cumulative expected regret $\mathbb{E}_{\mathcal{A}}[R(T)]$ and (2) minimizes the cumulative expected payment $\mathbb{E}_{\mathcal{A}}[C(T)]$.
+To support later development, we define three additional pieces of notation.
+We let $B(\theta)$ refer to the index of the arm that is best for an agent with preference vector $\theta$, $B(\theta) \in \argmax_i \theta \cdot u_i$, breaking ties uniformly at random. 
+We use $\tau(i,t)$ to denote the set of times at which arm i was pulled up to time $t$,
+$\tau(i,t) = \{ s : 1 \le s \le t, A_s = i \}$.
+We let $N(i,t)$ denote the cardinality of $A_t$, i.e., the number of pulls of arm $i$ at times up to and including $t$.
+\pfcomment{Bangrui, if we don't use $\tau(i,t)$ or $N(i,t)$ later, we can drop them here.}
 

### 2017-11-09 paper.tex
edited the calculation a little
added the proof of Theorem 2 and Lemma 6

@@
 \begin{algorithmic}
-\STATE Set n = 1 to denote the round number; g(n) to be a increasing function which we choose later;
+\STATE Set n = 1 to denote the round number;
 \FOR{ $t = 1, 2, 3, \cdots$}{
-	\IF{the myopic probability of pulling an arm is less than $g(n)^{-1}$ and we haven’t pulled that arm in this round}
+	\IF{the myopic probability of pulling an arm is less than $n^{-1}$ and we haven’t pulled that arm in this round}
 	\STATE{ we pay whatever it takes to incentivize that arm}\ELSE 
@@
 \begin{theorem}
-The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$.
+The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^3)$.
 \label{rst:budget}
@@
 \begin{theorem}
-The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2) + O(N \sum_{n=1}^{T}n^{\alpha})$ for $-1<\alpha<0$.
+The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2 m + M m^2\log(T))$.
 \label{rst:regret}
@@
 \begin{lemma}
-Using our algorithm, we have $\mathbb{E}[t_{n}-t_{n-1}]\leq Ng(n)$, $\forall n\geq 1$.
+Using our algorithm, we have $\mathbb{E}[t_{n}-t_{n-1}]\leq Nn$, $\forall n\geq 1$.
 \label{round:length}
@@
 \begin{itemize}
-\item If there exists an arm has not been pulled and the proportion of agents who would pull this arm is less than $\frac{1}{g(n)}$, then based on our algorithm, the principal will offer an payment for that arm and it will be pulled.
+\item If there exists an arm has not been pulled and the proportion of agents who would pull this arm is less than $n^{-1}$, then based on our algorithm, the principal will offer an payment for that arm and it will be pulled.
 In this case, the probability that the $i_{th}$ different arm will be pulled is 1.
-\item There exists at least $\frac{1}{g(n)}$ proportion of agents who will choose an un-pulled arm as his/her myopic action.
+\item There exists at least $n^{-1}$ proportion of agents who will choose an un-pulled arm as his/her myopic action.
 In this case, we know each type of agent shows up with probability at least $p$.
-Thus, the probability that the $i_{th}$ different arm will be pulled is at least $\frac{1}{g(n)}$.
+Thus, the probability that the $i_{th}$ different arm will be pulled is at least $n^{-1}$.
 \end{itemize}
 
-Since $X_{i}$ follows a ``geometric distribution'' with success probability at least $\frac{1}{g(n)}$ at each time, we know 
+Since $X_{i}$ follows a ``geometric distribution'' with success probability at least $n^{-1}$ at each time, we know 
 \begin{align}
-E[t_{n}-t_{n-1}]\leq Ng(n). \nonumber
+E[t_{n}-t_{n-1}]\leq Nn. \nonumber
 \end{align}
@@
 \begin{lemma}
-The expected incentive payment at round $n$ is bounded above by \bccomment{How to bound this conditional expectation?}
+For $t\in[t_n,t_{n+1}]$, the expected incentive payment $E[c(t)]$ is bounded above by $\Delta + Nm \sqrt{\frac{2}{n\pi}}$. 
 \end{lemma}
@@
 Denote $\Delta=\sup_{\theta}\max_{i}\{\theta\cdot u_{B(\theta)}-\theta\cdot u_{i}\}$ to be the theoretical maximum payment with no noisy.
-We first consider the expected payment for arm $1$ in the $n_{th}$ round.
+We consider the expected payment in the $n_{th}$ round.
 Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$.
@@
 \begin{align}
-&E[\max_{i}\theta_t\cdot u_{i,t}-\theta_t\cdot u_{1,t}|\text{agents pull arm $1$ with prob less than $g(n)^{-1}$}] \nonumber \\
-\leq & \Delta + E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\theta_t\cdot \epsilon_{B(\theta_t),t}|\text{agents pull arm $1$ with prob less than $g(n)^{-1}$}] \nonumber 
-\end{align}
-
-Denote $p_1=P_{\theta\sim F}(B(\theta)=1)$.
-
-If in the $n_{th}$ round we have $g(n)^{-1}>p_1$:
-
-If in the $n_{th}$ round we have $g(n)^{-1}<\frac{p}{2}$:
-\begin{align}
-E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\theta_t\cdot \epsilon_{B(\theta_t),t}|\text{agents pull arm $1$ with prob less than $g(n)^{-1}$}]  \nonumber 
+&E[c(t)] \nonumber \\
+\leq & \Delta \times P(c(t)>0) + E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\theta_t\cdot \epsilon_{B(\theta_t),t}1\{c(t)>0\}] \nonumber \\
+\leq & \Delta + E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\theta_t\cdot \epsilon_{B(\theta_t),t}] \nonumber \\
+\leq & \Delta + \sum_{j=1}^{m}E[\max_{i}|\epsilon_{i,t}^{j}|] \nonumber \\
+\leq & \Delta + \sum_{j=1}^{m}E\left[\sum_{i=1}^{N}|\epsilon_{i,t}^{j}|\right] \nonumber \\
+\leq & \Delta + Nm E[|\epsilon_{1,t}^{1}|] \nonumber \\
+\leq & \Delta + Nm \sqrt{\frac{2}{n\pi}} \nonumber
 \end{align}
@@
 If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2m\lambda\}$, they will correctly identify their best arm.
-Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, and $1/g(n)<p/2$, we do not need to incentivize any arms.
+Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, and $n^{-1}<p/2$, we do not need to incentivize any arms.
 
@@
 \begin{align}
-n_{1}=\max\bigg\{50, \frac{23.04\sigma^4}{\lambda\left(p^{-1}(\frac{p}{2})\right)^4},\min_{n}\{n:1/g(n)<\frac{p}{2}\}\bigg\}. \nonumber
+n_{1}=\max\bigg\{50, \frac{23.04\sigma^4}{\lambda\left(p^{-1}(\frac{p}{2})\right)^4},\min_{n}\{n:n^{-1}<\frac{p}{2}\}\bigg\}. \nonumber
 \end{align}
@@
 &E[C(T)] \nonumber \\
-= & \sum_{t=1}^{\infty}E[\mathbbm{1}\{\text{need to offer payment to an arm}\}] \nonumber \\
-\leq &\sum_{n=1}^{\infty}\sum_{t=1}^{\infty}E[\mathbbm{1}\{t_{n-1}\leq t\leq t_{n}: \text{myopic action occurs regret for agents with } \nonumber \\
-&\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq p^{-1}(1/g(n))\}\}] \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}P(\text{myopic action occurs regret for agents with }\nonumber \\
-&\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq p^{-1}\left(\frac{p}{2}\right)\}|t_{n-1}\leq t\leq t_{n})P(t_{n-1}\leq t\leq t_{n})+Nn_{1} \nonumber \\
-\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\left(p^{-1}(\frac{p}{2})\right)^2}{32m^2\sigma^2}\right)\times Ng(n)+Nn_{1} \nonumber 
+= & \sum_{t=1}^{\infty}E[c(t)\mathbbm{1}\{\text{need to offer payment to an arm}\}] \nonumber \\
+\leq &\sum_{n=1}^{\infty}\sum_{t=1}^{\infty}E[c(t)\mathbbm{1}\{t_{n-1}\leq t\leq t_{n}: \text{myopic action occurs regret for agents with } \nonumber \\
+&\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq p^{-1}(n^{-1})\}\}] \nonumber \\
+\leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}\left(\Delta+Nm\sqrt{\frac{2}{n\pi}}\right)P(\text{myopic action occurs regret for agents with }\nonumber \\
+&\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq p^{-1}\left(\frac{p}{2}\right)\}|t_{n-1}\leq t\leq t_{n})P(t_{n-1}\leq t\leq t_{n})+\sum_{n=1}^{n_1}N\left(\Delta+\sqrt{\frac{2}{n\pi}}\right) \nonumber \\
+\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\left(p^{-1}(\frac{p}{2})\right)^2}{32m^2\sigma^2}\right)\times Nn\left(\Delta+Nm\sqrt{\frac{2}{n_1\pi}}\right)+\sum_{n=1}^{n_1}N\left(\Delta+\sqrt{\frac{2}{n\pi}}\right) \nonumber
 \end{align}
 
-If we choose $g(n)=n$ and $\delta_{0}=p^{-1}(\frac{p}{2})$, then we have
+Denote $\delta_{0}=p^{-1}(\frac{p}{2})$, then we have
 \begin{align}
@@
 \end{align}
-We know the expected payment is bounded above by:
+Thus, $n_1=\max\{n_{0}, \frac{2}{p}+1\}$. We know the expected payment is bounded above by:
 \begin{align}
-E[C(T)] \leq 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2}+N(\max\{n_{0},(\frac{2}{p})+1\}). \nonumber
+E[C(T)] \leq 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2}\left(\Delta+Nm\sqrt{\frac{2}{n_1\pi}}\right)+\sum_{n=1}^{n_1}N\left(\Delta+\sqrt{\frac{2}{n\pi}}\right).
+\nonumber
 \end{align}
 
-Since we have $N$ arms in total, we know the $\mathbb{E}[C(T)]=O(N^2)$.\end{proof}
+Since we have $N$ arms in total, we know the $\mathbb{E}[C(T)]=O(N^3)$.
+
+Based on this analysis, we know the expected number of payments we need to make is less than
+\begin{align}
+&\sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\left(p^{-1}(\frac{p}{2})\right)^2}{32m^2\sigma^2}\right)\times Nn+Nn_{1} \nonumber \\
+=&24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2} + Nn_1, \nonumber
+\end{align}
+
+which we will use in the proof of Theorem~\ref{rst:regret}.
+
+\end{proof}
 
@@
 \begin{proof}
-For regret occurred in the first $n_0$ round, it is bounded above by $\sum_{n=1}^{n_{0}}NRg(n)$.
+For regret occurred in the first $n_0$ round, it is bounded above by $\sum_{n=1}^{n_{0}}NRn$.
 
@@
 =&E\left[\sum_{t=1}^{t_{n_{0}}} r(t) + \sum_{t=t_{n_{0}}}^{T}(r_1(t)+r_2(t))\right]  \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRg(n) + E\left[\sum_{t=t_{n_{0}}}^{T}r_1(t)\right]+ E\left[\sum_{t=t_{n_{0}}}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRg(n) + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRg(n) + \sum_{n=n_{0}}^{T}E\left[\sum_{t=t_{n}}^{t_{n+1}}24Nm\exp\left(-\frac{1.8n f(t)^2}{32 m^2\sigma^2}\right) R\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRg(n) + \sum_{n=n_{0}}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(t_n)^2}{32 m^2\sigma^2}\right)R \times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRg(n) + \sum_{n=1}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)R\times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRg(n) + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Ng(n)+ \sum_{t=1}^{T}Mf(t)^2 \nonumber
+\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{t=t_{n_{0}}}^{T}r_1(t)\right]+ E\left[\sum_{t=t_{n_{0}}}^{T}r_2(t)\right] \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{t=t_{n}}^{t_{n+1}}24Nm\exp\left(-\frac{1.8n f(t)^2}{32 m^2\sigma^2}\right) R\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(t_n)^2}{32 m^2\sigma^2}\right)R \times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)R\times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber
 \end{align}
 
-The expected regret occurred when we incentivize the agents is calculated in Theorem~\ref{rst:budget}. Thus if we set $g(n)=n$, the cumulative regret at time $T$ is bounded above by
+The expected regret occurred when we incentivize the agents is calculated in Theorem~\ref{rst:budget}. Thus the cumulative regret at time $T$ is bounded above by
 \begin{align}
@@
 
-For a fixed $T$, if we choose $f(n)=n^{-1/2+\frac{1}{2\log(T)}}$, we have
+If we set $f^2(t)=\frac{2\log(T)\times 32m^2\sigma^2}{1.8n}$, then
 \begin{align}
 &\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\ 
-\leq & \sum_{n=1}^{T} 24N^{2} Rmn\exp\left(-\frac{1.8n^{1/\log(T)}}{32 m^2\sigma^2}\right) + \left(\sum_{t=1}^{T} Mn^{-1}\right) \times T^{\frac{1}{\log(T)}} \nonumber \\
-= & + e(\log(T) + 1)
+\leq & \sum_{n=1}^{T} 24N^2 mnR \exp\left(-2\log(T)\right)  + \frac{64m^2\sigma^2 M\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{n} \nonumber \\
+\leq &  24N^2 m R\frac{T(T-1)}{2T^2}  + 35.56 m^2\sigma^2 M\log(T)(\log(T)+1) \nonumber \\
+\leq &  12 N^2 m R  + 35.56 m^2\sigma^2 M\log(T)(\log(T)+1). \nonumber
 \end{align}
 
+Thus, the cumulative expected regret is bounded by $O(N^2 m + M m^2\log(T))$.
 \end{proof}
@@
 In this section, we consider a special case of our problem, in which the agent's preference distribution $F(\cdot)$ satisfies $S(\delta)=0$ for $\delta<\delta^{'}$.
-Under this assumption, we still have $O(N^2)$ budget bound, however we get a better regret bound.
 The proof is similar to the proof of Theorem~\ref{rst:regret}, but for $t$ large enough, $S(f(t))=0$.
-Thus,
+In this case, with $O(N^3)$ payment budget, we can achieve $O(N^2)$ regret.
 
@@
 
-In our algorithm, we take ``pay what it takes'' strategy when we decided to incentivize the agent. However, as long as
+In our algorithm, we take ``pay whatever it takes'' strategy when we decided to incentivize the agent.
+In our proof, the only time we used ''pay whatever it takes'' is in Lemma~\ref{round:length}.
+Without loss of generality, suppose we want to incentivize arm $i$ at time $t$ at the $n^{th}$ round.
+Based on the proof of Lemma~\ref{round:length}, as long as we offer a payment $c_{i,t}$ such that arm $i$ will have at least $n^{-1}$ probability being pulled at time $t$, our results still hold true.
+We could compute this $c_{i,t}$ dynamically based on $F(\cdot)$ as well as our current estimate $u_{i,t}$.
+Here is the revised algorithm which would work well in practice:
+
+\begin{algorithm}
+\caption{Algorithm: Upper Bound}
+\label{Alg1}
+\begin{algorithmic}
+\STATE Set n = 1 to denote the round number;
+\FOR{ $t = 1, 2, 3, \cdots$}{
+	\IF{the myopic probability of pulling an arm $i$ is less than $n^{-1}$ and we haven’t pulled that arm $i$ in this round (if there are multiple such arms, pick one randomly)}
+	\STATE{Offer payment $c_{i,t}=\inf\{c: P(\theta\sim F: \theta\cdot u_{i,t}+c>max_{j}\theta\cdot u_{j,t})>n^{-1}\}$}\ELSE 
+		\STATE {let the agents play myopically}\ENDIF
+		\STATE $n = min_{i} N(i,t)$
+}\ENDFOR
+
+\end{algorithmic}
+\end{algorithm}
+
+The same proof would work and we can get the exact same results as ``pay whatever it takes'' strategy.
 

### 2017-11-09 paper.tex
did some edits of the paper

@@
 
-The intuition behind is that heterogeneity of a certain kind reduces but doesn't eliminate the need for incentivizing exploration --- basically that you get a certain amount of exploration for free via heterogeneity.
+The intuition behind is that heterogeneity of a certain kind reduces but doesn't eliminate the need for incentivizing exploration --- you get a certain amount of exploration for free via heterogeneity.
 
-We structure our paper as follows: In Section~\ref{sec:prob}, we state our problem formulation; In Section~\ref{sec:ub}, we state our algorithm and prove a upper bound for both the payment budget as well as the regret; In Section~\ref{sec:lb}, we construct an example to show that the regret bound is at least $O(\log(T))$ in the worst case example, regardless the payment budget.
+We structure our paper as follows: In Section~\ref{sec:prob}, we state our problem formulation; In Section~\ref{sec:ub}, we state our algorithm and prove with $O(N^3)$ payment budget, we can achieve $O(N^2+(\log(T))^2)$ regret; In Section~\ref{sec:lb}, we construct an example to show that the regret bound is at least $O(\log(T))$ in the worst case example, regardless the payment budget.
 
@@
 
-With money transfer: \cite{frazier2014incentivizing} considers a problem setting where the principal pays the agents extra money in order to incentivize them to explore.
+We broadly categorize the literature into two categories based on whether there is money transfer.
+
+\begin{itemize}
+\item With money transfer: \cite{frazier2014incentivizing} considers a problem setting where the principal pays the agents extra money in order to incentivize them to explore.
 In their paper, they assume all agents have equal value of money and provide a complete characterization of achievable reward with a fixed budget.
@@
 Under this setting, they proved a similar bound as in \cite{frazier2014incentivizing} which depends on the signal scheme.
-
-Without money transfer but using information asymmetry:
-\cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time.
+\item Without money transfer but using information asymmetry: \cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time.
 \cite{mansour2015bayesian} generalizes \cite{kremer2014implementing} by allowing finite number of actions at each time.
 \cite{mansour2016bayesian} considers a problem setting where there are multiple agents at each time and allow agents to interact with each other.
-At each time, the principal provides each agent an recommendation, which is Bayesian incentive-compatible.
+In these papers, the principal provides each agent an recommendation at each time, which is Bayesian incentive-compatible.
 They prove principal can achieve constant regret when utilities are deterministic and logarithmic regret when utilities are stochastic.
+\end{itemize}
 
@@
 The motivation of this project is to build a recommender system.
-Agent arrives to the system one at a time.
+Agents arrive to the system one at a time.
 Upon arrival, he/she receives a recommendation from the system and chooses a product based on the recommendation.
@@
 A stream of myopic selfish agents come to our system.
-Agent $t$ has linear preferences over attributes described by a vector $\theta_t \in \mathbb{R}^m$ that is unknown to the principal and drawn iid from a known distribution $F$.
+Agent $t$ has linear preferences over attributes described by a vector $\theta_t \in \mathbb{R}^m$ that is unknown to the principal and drawn i.i.d.
+from a known distribution $F(\cdot)$.
 We refer synonomously to an agent and that agent's preference vector: when we say ``an agent $\theta$'', we mean ``an agent with preference vector $\theta$.''
@@
 We assume that agent $t$ chooses to pull the arm that myopically maximizes the sum of this payment and an estimate of the utility obtained $\theta_t \cdot u_{i,t}$ where $u_{i,t}$ denotes the simple average of $O_s$ over all previous pulls of arm $i$ if it has been pulled at least once, or a default value of $0$ if not.
-That is, $u_{i,t} = \sum_{s<t} O_s 1\{A_s = i\} / \sum_{s<t} 1\{A_s = i\}$ if the denominator is strictly positive and $0$ otherwise; and $A_t=\argmax_{i}\{\theta_t\cdot u_{i,t}\}$, breaking ties in favor of the arm with the highest incentive.
+That is, $u_{i,t} = \sum_{s<t} O_s 1\{A_s = i\} / \sum_{s<t} 1\{A_s = i\}$ if the denominator is strictly positive and $0$ otherwise; and $A_t=\argmax_{i}\{\theta_t\cdot u_{i,t}+c_{i,t}\}$, breaking ties in favor of the arm with the highest incentive.
 We use $c_t=c_{A_{t},t}$ to denote the actual incentive payment at time $t$.
+For simplicity, we assume all arms have been pulled once at time $t=1$ in this paper (we can offer a large payment at the beginning to make this happen).
 \pfcomment{Bangrui, I assumed that $u(i,t)$ starts from $0$.
@@
 This behavior may be recovered if agents are Bayesian and share a common non-informative prior distribution that is constant over $\mathbb{R}^m$ and know $\sigma^2$.
-In this case, the posterior distribution on $u_{i}$ at time $t$ is multivariate normal with mean $u_{i,t}$, and the expected value of $\theta_t \cdot u_i$ under this posterior conditioned on $\theta_t$ is $\theta_t \cdot u_{i,t}$ \cite[equation 2.13 in section 2.5]{Ge04}.
+In this case, the posterior distribution on $u_{i}$ at time $t$ is multivariate normal with mean $u_{i,t}$, and the expected value of $\theta_t \cdot u_i$ under this posterior conditioned on $\theta_t$ is $\theta_t \cdot u_{i,t}$ (see equation $2.13$ in section $2.5$, \cite{Ge04}).
 Alternatively, one may simply take our assumption that agents use the average as their estimate of an attribute value directly without such a Bayesian justification.
@@
 To support later development, we define three additional pieces of notation.
-We let $B(\theta)$ refer to the index of the arm that is best for an agent with preference vector $\theta$, $B(\theta) \in \argmax_i \theta \cdot u_i$, breaking ties uniformly at random. 
-We use $\tau(i,t)$ to denote the set of times at which arm i was pulled up to time $t$,
-$\tau(i,t) = \{ s : 1 \le s \le t, A_s = i \}$.
+We let $B(\theta)$ and $\hat{B}(\theta)$ refer to the index of the arm that is best and second best for an agent with preference vector $\theta$, $B(\theta) \in \argmax_i \theta \cdot u_i$ and $\hat{B}(\theta)=\argmax_{i\neq B(\theta)}\theta\cdot u_{i}$, breaking ties uniformly at random.
 We let $N(i,t)$ denote the cardinality of $A_t$, i.e., the number of pulls of arm $i$ at times up to and including $t$.
-\pfcomment{Bangrui, if we don't use $\tau(i,t)$ or $N(i,t)$ later, we can drop them here.}
 
@@
 
+\subsection{Our Algorithm}
+Before we introduce our algorithm, we need to use the following definition:
+
+\begin{definition}
+We call time $t_{n}$ as the starting point of the $n^{th}$ round if $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$. We call the time period from $t_{n}$ to $t_{n+1}$ as the $n^{th}$ round.
+\end{definition}
+
+We consider an algorithm that offers incentive to an arm $i$ if and only if both of the following criterias are met:
+\begin{itemize}
+\item the myopic probability of pulling arm $i$ is low; 
+\item arm $i$ has not been played or incentivized before in this round.
+\end{itemize}
+We break ties randomly.
+If we decides to incentivize an arm, we use ``pay whatever it takes'' strategy (We use ``pay whatever it takes'' strategy mainly because of its simplicity.
+In Section~\ref{sec:pi}, we provide a more realistic algorithm which has the same payment budget bound and regret bound).
+This algorithm does not need to know $T$ in advance.
+The detailed algorithm is as follows:
+
+\begin{algorithm}
+\caption{Algorithm: Upper Bound}
+\label{Alg1}
+\begin{algorithmic}
+\STATE Set n = 1 to denote the round number;
+\FOR{ $t = 1, 2, 3, \cdots$}{
+	\IF{the myopic probability of pulling an arm is less than $n^{-1}$ and we haven’t pulled that arm in this round}
+	\STATE{ we pay whatever it takes to incentivize that arm}\ELSE 
+		\STATE {let the agents play myopically}\ENDIF
+		\STATE $n = min_{i} N(i,t)$
+}\ENDFOR
+
+\end{algorithmic}
+\end{algorithm}
+
 \subsection{Assumptions}
-Throughout this section, we use $F(\cdot)$ to denote the agent's preference distribution, which could either be a continuous distribution or a discrete distribution. Denote
+In this secion, we discuss several assumptions that we need to acheive our results.
+Throughout this paper, we use $F(\cdot)$ to denote the agent's preference distribution, which could either be a continuous distribution or a discrete distribution.
+Denote
 
@@
 
-\subsection{Our Algorithm}
-Before we introduce our algorithm, we need to use the following definition:
-
-\begin{definition}
-We call time $t_{n}$ as the starting point of the $n_{th}$ round if $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$. We call the time period from $t_{n}$ to $t_{n+1}$ as the $n_{th}$ round.
-\end{definition}
-
-In this setting, we consider an algorithm that offers incentive to an arm if and only if 
-\begin{itemize}
-\item there is no agents will play it anymore;
-\item this arm has not been played or incentivized before in this round.
-\end{itemize}
-We break ties randomly. If we decides to incentivize an arm, we use ``pay what it takes strategy''. This algorithm does not need to know $T$ in advance. The detailed algorithm is as follows:
-
-\begin{algorithm}
-\caption{Algorithm: Upper Bound}
-\label{Alg1}
-\begin{algorithmic}
-\STATE Set n = 1 to denote the round number;
-\FOR{ $t = 1, 2, 3, \cdots$}{
-	\IF{the myopic probability of pulling an arm is less than $n^{-1}$ and we haven’t pulled that arm in this round}
-	\STATE{ we pay whatever it takes to incentivize that arm}\ELSE 
-		\STATE {let the agents play myopically}\ENDIF
-		\STATE $n = min_{i} N(i,t)$
-}\ENDFOR
-
-\end{algorithmic}
-\end{algorithm}
-
 \subsection{General Results}
 
-Now we analyze the regret occurred by Algorithm~\ref{Alg1} and its payment budget.
+In this section, we prove using Algorithm~\ref{Alg1}, we can achieve $O(N^2+(\log(T))^2)$ regret bound with $O(N^3)$ payment budget.
+
 Before we start our analysis, we need the following notations.
-Denote $\hat{B}(\theta)=\arg\max_{i\neq B(\theta)}\{\theta\cdot u_{i}\}$ to the $\theta$'s second best arm.
-We use $S(\delta)$ to denote the proportion of user whose utility difference between their best arm and the second best arm is less than $\delta$.
+Denote $S(\delta)$ as the proportion of user whose utility difference between their best arm and the second best arm is less than $\delta$.
 Formally, $S(\delta)=P(\theta: \theta \cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}\leq \delta)$.
-Denote $\lambda(\delta)=\frac{\delta}{2m}$.
-Denote $p(\delta)=\min_{i}P(\{\theta:\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$ and we know $p(0)=p$.
+Denote $p(\delta)=\min_{i}P(\{\theta:\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$.
+Based on $p(\delta)$'s definition, we know $p(0)=p$.
 
-With the help of our assumptions and the above notations, we can prove the following main results:
+With the help of our assumptions and the above notations, we now state our main results:
 
@@
 
-The following lemma bounds the probability of making a mistake if we let the agents play myopically in the $n_{th}$ round, given that the utility difference between his/her best and second best arm is bounded below by a constant.
+The following lemma bounds the probability of making a mistake if we let the agents play myopically in the $n^{th}$ round, given that the utility difference between his/her best and second best arm is bounded below by a constant.
 
 \begin{lemma}
-For those user whose utility difference between their best arm and the second best arm is at least $2m\lambda$, the probability that myopic action can incur regret at any time $t\in [t_{n-1},t_{n}-1]$ in the $n_{th}$ round is bounded above by $24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
+For those user whose utility difference between their best arm and the second best arm is at least $2m\lambda$, the probability that myopic action can incur regret at any time $t\in [t_{n-1},t_{n}-1]$ in the $n^{th}$ round is bounded above by $24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
 \label{round:prob}
@@
 \begin{proof}
-In the $n_{th}$ round, we know all arms have been pulled at least $n$ times. Thus, the probability that myopic action can occur regret is bounded by
+In the $n^{th}$ round, we know all arms have been pulled at least $n$ times. Thus, the probability that myopic action can occur regret is bounded by
 \begin{align}
@@
 In each round, each arm needs to be pulled at least once.
-Denote $X_{i}$ to be the number of agents come to the system between $i-1$ different arms were pulled and the $i_{th}$ different arm was pulled.
+Denote $X_{i}$ to be the number of agents come to the system between $i-1$ different arms were pulled and the $i^{th}$ different arm was pulled.
 Then we know
@@
 
-Denote $t^{0}=t_{n-1}+\sum_{j=1}^{i-1}X_{j}$, then $X_{i}$ follows a ``geometric distribution'', which counts the total number of trials before the $i_{th}$ different arm were pulled at time $t=t^{0},t^{0}+1,\cdots$.
+Denote $t^{0}=t_{n-1}+\sum_{j=1}^{i-1}X_{j}$, then $X_{i}$ follows a ``geometric distribution'', which counts the total number of trials before the $i^{th}$ different arm were pulled at time $t=t^{0},t^{0}+1,\cdots$.
 At each time $t=t^{0}, t^{0}+1,\cdots$, there are two possibilities for a success trial:
@@
 \item If there exists an arm has not been pulled and the proportion of agents who would pull this arm is less than $n^{-1}$, then based on our algorithm, the principal will offer an payment for that arm and it will be pulled.
-In this case, the probability that the $i_{th}$ different arm will be pulled is 1.
+In this case, the probability that the $i^{th}$ different arm will be pulled is 1.
 \item There exists at least $n^{-1}$ proportion of agents who will choose an un-pulled arm as his/her myopic action.
 In this case, we know each type of agent shows up with probability at least $p$.
-Thus, the probability that the $i_{th}$ different arm will be pulled is at least $n^{-1}$.
+Thus, the probability that the $i^{th}$ different arm will be pulled is at least $n^{-1}$.
 \end{itemize}
@@
 Denote $\Delta=\sup_{\theta}\max_{i}\{\theta\cdot u_{B(\theta)}-\theta\cdot u_{i}\}$ to be the theoretical maximum payment with no noisy.
-We consider the expected payment in the $n_{th}$ round.
+We consider the expected payment in the $n^{th}$ round.
 Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$.
@@
 Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, and $n^{-1}<p/2$, we do not need to incentivize any arms.
-
+In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
+Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$.
 Denote
@@
 \end{align}
-
-The cumulative payment is bounded above by:
-
+Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).The cumulative payment is bounded above by:
 \begin{align}
@@
 \leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}\left(\Delta+Nm\sqrt{\frac{2}{n\pi}}\right)P(\text{myopic action occurs regret for agents with }\nonumber \\
-&\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq p^{-1}\left(\frac{p}{2}\right)\}|t_{n-1}\leq t\leq t_{n})P(t_{n-1}\leq t\leq t_{n})+\sum_{n=1}^{n_1}N\left(\Delta+\sqrt{\frac{2}{n\pi}}\right) \nonumber \\
-\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\left(p^{-1}(\frac{p}{2})\right)^2}{32m^2\sigma^2}\right)\times Nn\left(\Delta+Nm\sqrt{\frac{2}{n_1\pi}}\right)+\sum_{n=1}^{n_1}N\left(\Delta+\sqrt{\frac{2}{n\pi}}\right) \nonumber
+&\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq \delta_{0}\}|t_{n-1}\leq t\leq t_{n})P(t_{n-1}\leq t\leq t_{n})+\sum_{n=1}^{n_1}N\left(\Delta+\sqrt{\frac{2}{n\pi}}\right) \nonumber \\
+\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{32m^2\sigma^2}\right)\times Nn\left(\Delta+Nm\sqrt{\frac{2}{n_1\pi}}\right)+\sum_{n=1}^{n_1}N\left(\Delta+\sqrt{\frac{2}{n\pi}}\right) \nonumber
 \end{align}
 
-Denote $\delta_{0}=p^{-1}(\frac{p}{2})$, then we have
-\begin{align}
-\frac{1}{n}<\frac{p}{2} \implies n\geq (\frac{2}{p})+1. \nonumber
-\end{align}
-Thus, $n_1=\max\{n_{0}, \frac{2}{p}+1\}$. We know the expected payment is bounded above by:
+We know the expected payment is bounded above by:
 \begin{align}
@@
 Since we have $N$ arms in total, we know the $\mathbb{E}[C(T)]=O(N^3)$.
+\end{proof}
 
-Based on this analysis, we know the expected number of payments we need to make is less than
+Based on the proof of Theorem~\ref{rst:budget}, we know the expected number of payments we need to make is less than
 \begin{align}
-&\sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\left(p^{-1}(\frac{p}{2})\right)^2}{32m^2\sigma^2}\right)\times Nn+Nn_{1} \nonumber \\
+&\sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{32m^2\sigma^2}\right)\times Nn+Nn_{1} \nonumber \\
 =&24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2} + Nn_1, \nonumber
 \end{align}
-
-which we will use in the proof of Theorem~\ref{rst:regret}.
-
-\end{proof}
-
-Now we are ready to prove our second main result, Theorem~\ref{rst:regret}.
+which we will use in the proof of Theorem~\ref{rst:regret}. Now we are ready to prove our second main result, Theorem~\ref{rst:regret}.
 
@@
 \begin{itemize}
-\item For those user whose utility difference between their best and the second best arm is greater than $f(t)$: suppose it is at the $n(t)_{th}$ round, the probability of these user making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n(t) f(t)^2}{32 m^2\sigma^2}\right)$ at time $t$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n(t) f(t)^2}{32 m^2\sigma^2}\right)\times R$.
+\item For those user whose utility difference between their best and the second best arm is greater than $f(t)$: suppose it is at the $n(t)^{th}$ round, the probability of these user making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n(t) f(t)^2}{32 m^2\sigma^2}\right)$ at time $t$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n(t) f(t)^2}{32 m^2\sigma^2}\right)\times R$.
 We denote the regret occured by these agents as $r_1(t)$.
@@
 &\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-+ & 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2}+N(\max\{n_{0},(\frac{2}{p})+1\}). \nonumber
++ & 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2}+N(\max\{n_{0},\frac{2}{p}\}). \nonumber
 \end{align}
@@
 \subsection{Practical Issues}
+\label{sec:pi}
 
@@
 \caption{Algorithm: Upper Bound}
-\label{Alg1}
+\label{Alg2}
 \begin{algorithmic}
@@
 \begin{align}
-\lim_{n\rightarrow}\frac{E[r_n| z_{n,1}>0, z_{n,2}>0]}{n} = O(1). \nonumber
+\lim_{n\rightarrow\infty}\frac{E[r_n| z_{n,1}>0, z_{n,2}>0]}{n} = O(1). \nonumber
 \end{align}
@@
 
-Based on Wolframalpha, we know
+Based on Wolframalpha \bccomment{still not sure how to compute this by hand}, we know
 

### 2017-11-09 paper.tex
did some edits of the paper

@@
 \begin{algorithm}
-\caption{Algorithm: Upper Bound}
+\caption{Algorithm: Incentivizing Exploration}
 \label{Alg1}
@@
 For $t\in[t_n,t_{n+1}]$, the expected incentive payment $E[c(t)]$ is bounded above by $\Delta + Nm \sqrt{\frac{2}{n\pi}}$. 
+\label{lemma:payment}
 \end{lemma}
@@
 
-Now we are ready to prove our first main result, Theorem~\ref{rst:budget}.
+Now we are ready to prove our first main result, Theorem~\ref{rst:budget}. \bccomment{Not sure if I used Lemma~\ref{lemma:payment} correctly.}
 
@@
 If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2m\lambda\}$, they will correctly identify their best arm.
-Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, and $n^{-1}<p/2$, we do not need to incentivize any arms.
+Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms.
 In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
 Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$.
-Denote
-\begin{align}
-n_{1}=\max\bigg\{50, \frac{23.04\sigma^4}{\lambda\left(p^{-1}(\frac{p}{2})\right)^4},\min_{n}\{n:n^{-1}<\frac{p}{2}\}\bigg\}. \nonumber
-\end{align}
 Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).The cumulative payment is bounded above by:
@@
 &\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-+ & 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2}+N(\max\{n_{0},\frac{2}{p}\}). \nonumber
++ & 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2}+N\left(\max\left\{n_{0},\frac{2}{p}\right\}\right). \nonumber
 \end{align}
@@
 \begin{algorithm}
-\caption{Algorithm: Upper Bound}
+\caption{Algorithm: Incentivizing Exploration Revised}
 \label{Alg2}
@@
 For simplicity, we assume that the agents already know the true utility vector for arm $1$.
-Without loss of generality, denote $u_{t} = (0,1)+(z_{t1},z_{t,2}) = (0,1)+ (N(0,1/n),N(0,1/n))$ to be the estimate reward for arm $2$ (I assume the variance for the noise is $1$).
+Without loss of generality, denote $u_{t} = (0,1)+(z_{t1},z_{t,2}) = (0,1)+ (N(0,1/t),N(0,1/t))$ to be the estimate reward for arm $2$ (Without loss of generality, we assume the variance for the noise is $1$).
 
-At time $n$, suppose we know arm $1$ has utility vector $(0,0)$ and arm $2$ has utility vector $u_n\sim (N(0,\frac{1}{n}), N(1,\frac{1}{n}))$.
+At time $t$, suppose we know arm $1$ has utility vector $(0,0)$ and arm $2$ has utility vector $u_t\sim (N(0,\frac{1}{t}), N(1,\frac{1}{t}))$.
 Since we know $(z_{t,1}, z_{t,2})$ is symmetric around $(0,0)$, we know
@@
 \begin{align}
-&E[r_n] \nonumber \\
-= &E[r_n | z_{n,1}>0,z_{n,2}>0] \times P(z_{n,1}>0,z_{n,2}>0) + E[r_n |z_{n,1}>0,z_{n,2}<0] \times P(z_{n,1}>0,z_{n,2}<0) \nonumber \\
-= &E[r_n | z_{n,1}<0,z_{n,2}>0] \times P(z_{n,1}<0,z_{n,2}>0) + E[r_n |z_{n,1}<0,z_{n,2}<0] \times P(z_{n,1}<0,z_{n,2}<0) \nonumber \\
-\geq & 0.25 \times E[r_n | z_{n,1}>0, z_{n,2}>0]. \nonumber
+&E[r_t] \nonumber \\
+= &E[r_t | z_{t,1}>0,z_{t,2}>0] \times P(z_{t,1}>0,z_{t,2}>0) + E[r_t |z_{t,1}>0,z_{t,2}<0] \times P(z_{t,1}>0,z_{t,2}<0) \nonumber \\
+= &E[r_t | z_{t,1}<0,z_{t,2}>0] \times P(z_{t,1}<0,z_{n,2}>0) + E[r_t |z_{t,1}<0,z_{t,2}<0] \times P(z_{t,1}<0,z_{t,2}<0) \nonumber \\
+\geq & 0.25 \times E[r_t | z_{t,1}>0, z_{t,2}>0]. \nonumber
 \end{align}
 
-Given $z_{n,1}>0$ and $z_{n,2}>0$, we know the user between $(-1,0)$ and $(\frac{-1-z_{n,2}}{\sqrt{z_{n,1}^2+(1+z_{n,2})^2}}, \frac{z_{n,1}}{\sqrt{z_{n,1}^2+(1+z_{n,2})^2}})$ and the user between $(1,0)$ to $(\frac{1+z_{n,2}}{\sqrt{z_{n,1}^2+(1+z_{n,2})^2}}, \frac{-z_{n,1}}{\sqrt{z_{n,1}^2+(1+z_{n,2})^2}})$ will make a mistake.
+Given $z_{t,1}>0$ and $z_{t,2}>0$, we know the user between $(-1,0)$ and $\left(\frac{-1-z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ and the user between $(1,0)$ to $\left(\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{-z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ will make a mistake.
 And the regret is the absolute value of the second coordinate of the user's preference vector.
@@
 \begin{align}
-&E[r_n| z_{n,1}>0, z_{n,2}>0] \nonumber \\
-=& 4\times 2 \int_{0}^{\infty} \int_{0}^{\infty} \int_{0}^{\arctan(\frac{z_{n,1}}{1+z_{n,2}})}\frac{\sin(\theta)}{2\pi}d(\theta)\frac{e^{-\frac{n \times z_{n,1}^2}{2}}\sqrt{n}}{\sqrt{2\pi}}d(z_{n,1})\frac{e^{-\frac{n \times z_{n,2}^2}{2}}\sqrt{n}}{\sqrt{2\pi}}d(z_{n,2}) \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}n\times [1-\frac{1+z_{n,2}}{\sqrt{z_{n,1}^2+(1+z_{n,2})^2}}]e^{-\frac{n \times z_{n,1}^2}{2}}e^{-\frac{n \times z_{n,2}^2}{2}}d(z_{n,1})d(z_{n,2}) \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty} \left[1-\frac{\sqrt{n}+z_{n,2}}{\sqrt{z_{n,1}^2+(\sqrt{n}+z_{n,2})^2}}\right]e^{-\frac{z_{n,1}^2}{2}}e^{-\frac{z_{n,2}^2}{2}}d(z_{n,1})d(z_{n,2}) \nonumber
+&E[r_t| z_{t,1}>0, z_{t,2}>0] \nonumber \\
+=& 4\times 2 \int_{0}^{\infty} \int_{0}^{\infty} \int_{0}^{\arctan\left(\frac{z_{t,1}}{1+z_{t,2}}\right)}\frac{\sin(\theta)}{2\pi}d(\theta)\frac{e^{-\frac{t \times z_{t,1}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,1})\frac{e^{-\frac{t \times z_{t,2}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,2}) \nonumber \\
+=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}t\times \left[1-\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right]e^{-\frac{t \times z_{t,1}^2}{2}}e^{-\frac{t \times z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber \\
+=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty} \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber
 \end{align}
@@
 \begin{align}
-\lim_{n\rightarrow\infty}\frac{E[r_n| z_{n,1}>0, z_{n,2}>0]}{n} = O(1). \nonumber
+\lim_{t\rightarrow\infty}\frac{E[r_t| z_{t,1}>0, z_{t,2}>0]}{t} = O(1). \nonumber
 \end{align}
 
-Denote $d(n)=n\left[1-\frac{\sqrt{n}+z_{n,2}}{\sqrt{z_{n,1}^2+(\sqrt{n}+z_{n,2})^2}}\right]$.
+Denote $d(t)=t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]$.
 Since
 \begin{align}
-d^{'}(n)=\frac{-z_{n,1}^2(2z_{n,2}+3\sqrt{n})-2(z_{n,2}+\sqrt{n})^3}{2(z_{n,1}^2+(z_{n,2}+\sqrt{n})^2)^{3/2}}+1. \nonumber
+d^{'}(t)=\frac{-z_{t,1}^2(2z_{t,2}+3\sqrt{t})-2(z_{t,2}+\sqrt{t})^3}{2(z_{t,1}^2+(z_{t,2}+\sqrt{t})^2)^{3/2}}+1. \nonumber
 \end{align}
 
-and $\lim_{n\rightarrow \infty}d^{'}(n)=2$, we know for $n$ large enough, $d(n)$ is a increasing function in terms of n. Thus, based on the Monotone Convergence Theorem, we have
+and $\lim_{t\rightarrow \infty}d^{'}(t)=2$, we know for $n$ large enough, $d(t)$ is a increasing function in terms of t. Thus, based on the Monotone Convergence Theorem, we have
 
 \begin{align}
-&\lim_{n\rightarrow \infty}\frac{E[r_n| z_{n,1}>0, z_{n,2}>0]}{n} \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{n\rightarrow \infty}\left[ \left[1-\frac{\sqrt{n}+z_{n,2}}{\sqrt{z_{n,1}^2+(\sqrt{n}+z_{n,2})^2}}\right]e^{-\frac{z_{n,1}^2}{2}}e^{-\frac{z_{n,2}^2}{2}}\right]d(z_{n,1})d(z_{n,2}) \nonumber
+&\lim_{t\rightarrow \infty}\frac{E[r_t| z_{t,1}>0, z_{t,2}>0]}{t} \nonumber \\
+=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber
 \end{align}
@@
 \begin{align}
-\lim_{n\rightarrow \infty} d(n)=\frac{z_{n,1}^2}{2}. \nonumber
+\lim_{t\rightarrow \infty} d(t)=\frac{z_{t,1}^2}{2}. \nonumber
 \end{align}
@@
 \begin{align}
-&\lim_{n\rightarrow \infty}\frac{E[r_n| z_{n,1}>0, z_{n,2}>0]}{n} \nonumber \\
-=&\frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{n\rightarrow \infty}\left[ \frac{z_{n,1}^2}{2}e^{-\frac{z_{n,1}^2}{2}}e^{-\frac{z_{n,2}^2}{2}}\right]d(z_{n,1})d(z_{n,2}) = \frac{1}{2\pi}.
+&\lim_{t\rightarrow \infty}\frac{E[r_t| z_{t,1}>0, z_{t,2}>0]}{t} \nonumber \\
+=&\frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ \frac{z_{t,1}^2}{2}e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) = \frac{1}{2\pi}.
 \nonumber

### 2017-11-19 paper.tex
did some edits of the paper

@@
 \begin{theorem}
-The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^3)$.
+The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^3)$. \bccomment{Our current analysis of the cumulative expected payment is wrong. See the comments of Lemma 6 for details}
 \label{rst:budget}
@@
 \item There exists at least $n^{-1}$ proportion of agents who will choose an un-pulled arm as his/her myopic action.
-In this case, we know each type of agent shows up with probability at least $p$.
-Thus, the probability that the $i^{th}$ different arm will be pulled is at least $n^{-1}$.
+In this case, the probability that the $i^{th}$ different arm will be pulled is at least $n^{-1}$.
 \end{itemize}
@@
 \begin{lemma}
-For $t\in[t_n,t_{n+1}]$, the expected incentive payment $E[c(t)]$ is bounded above by $\Delta + Nm \sqrt{\frac{2}{n\pi}}$. 
+For $t\in[t_n,t_{n+1}]$, the expected incentive payment $E[c(t)]$ is bounded above by $\Delta + 2WNm \sqrt{\frac{2}{n\pi}}$. 
 \label{lemma:payment}
@@
 &E[c(t)] \nonumber \\
-\leq & \Delta \times P(c(t)>0) + E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\theta_t\cdot \epsilon_{B(\theta_t),t}1\{c(t)>0\}] \nonumber \\
-\leq & \Delta + E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\theta_t\cdot \epsilon_{B(\theta_t),t}] \nonumber \\
-\leq & \Delta + \sum_{j=1}^{m}E[\max_{i}|\epsilon_{i,t}^{j}|] \nonumber \\
-\leq & \Delta + \sum_{j=1}^{m}E\left[\sum_{i=1}^{N}|\epsilon_{i,t}^{j}|\right] \nonumber \\
-\leq & \Delta + Nm E[|\epsilon_{1,t}^{1}|] \nonumber \\
-\leq & \Delta + Nm \sqrt{\frac{2}{n\pi}} \nonumber
+\leq & \Delta \times P(c(t)>0) + E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\min_{j}\theta_t\cdot \epsilon_{j,t}1\{c(t)>0\}] \nonumber \\
+\leq & \Delta + E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\min_{j}\theta_t\cdot \epsilon_{j,t}] \nonumber \\
+\leq & \Delta + \sum_{j=1}^{m}2WE[\max_{i}|\epsilon_{i,t}^{j}|] \nonumber \\
+\leq & \Delta + 2W\sum_{j=1}^{m}E\left[\sum_{i=1}^{N}|\epsilon_{i,t}^{j}|\right] \nonumber \\
+\leq & \Delta + 2WNm E[|\epsilon_{1,t}^{1}|] \nonumber \\
+\leq & \Delta + 2WNm \sqrt{\frac{2}{n\pi}} \nonumber
 \end{align}
@@
 
-Now we are ready to prove our first main result, Theorem~\ref{rst:budget}. \bccomment{Not sure if I used Lemma~\ref{lemma:payment} correctly.}
+Now we are ready to prove our first main result, Theorem~\ref{rst:budget}.
+\bccomment{The current proof about the cumulative expected payment is wrong.
+We need to bound the $E[c(t)|\textit{our algorithm decides to incentivize}]$ instead of $E[c(t)]$.
+However, the analysis for the cumulative regret is correct}
 

### 2017-11-20 paper.tex
fixed a typo

@@
 \FOR{ $t = 1, 2, 3, \cdots$}{
-	\IF{the myopic probability of pulling an arm is less than $n^{-1}$ and we haven’t pulled that arm in this round}
+	\IF{the myopic probability of pulling an arm is less than $n^{-1}$ and no agents have pulled that arm in this round (break ties randomly)}
 	\STATE{ we pay whatever it takes to incentivize that arm}\ELSE 
@@
 \begin{theorem}
-The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2 m + M m^2\log(T))$.
+The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2 m + M m^2(\log(T))^2)$.
 \label{rst:regret}
@@
 \FOR{ $t = 1, 2, 3, \cdots$}{
-	\IF{the myopic probability of pulling an arm $i$ is less than $n^{-1}$ and we haven’t pulled that arm $i$ in this round (if there are multiple such arms, pick one randomly)}
+	\IF{the probability of pulling an arm $i$ is less than $n^{-1}$ and no agents have pulled that arm in this round (break ties randomly)}
 	\STATE{Offer payment $c_{i,t}=\inf\{c: P(\theta\sim F: \theta\cdot u_{i,t}+c>max_{j}\theta\cdot u_{j,t})>n^{-1}\}$}\ELSE 

### 2017-11-23 paper.tex
edits to the intro

@@
 \section{Introduction}
-In this paper, we study a variant of incentivizing exploration with heterogeneous agents' preferences, that generalizes \cite{frazier2014incentivizing} and \cite{han2015incentivizing}.
+In this paper, we study incentivizing exploration with heterogeneous agents' preferences.
+Arms have unknown multivariate attributes, and agents have heterogeneous linear utility functions drawn from a known probability distribution that map these attribute vectors onto utilities.
+Agents see noisy observations of the attributes of arms pulled by all previous agents, and estimate an arms' attribute vector by the simple average of these observations.
+Agents are selfish, and pull the arm with the largest estimated utility summed with an optional arm-specific incentivizing payment chosen by the principle.
 
-In our setting we have arms that have unknown multivariate attributes, and agents have heterogeneous utility functions that map these attribute vectors onto utilities.
-All agents see the attribute outcomes from previous agents.
-We study a simple policy that mostly exploits, and occasionally incentivizes exploration when an arm would be unpulled by all agent types given the current posterior.
+\pfcomment{Talk about application settings that are similar to our model.  You can take portions of your dissertation chapter.}
 
+We study a simple policy that usually exploits, incentivizing agents to pull an arm only when the set of agent utility functions that would pull this arm under current attribute estimates without incentives has probability below a time-varying threshold.
+\pfcomment{Say something about what we show for this policy.}
+
+\pfcomment{Talk about how our regret bounds compare to what our regret bounds would be in a homogenous preference setting, to clarify the following sentences.}
 The intuition behind is that heterogeneity of a certain kind reduces but doesn't eliminate the need for incentivizing exploration --- you get a certain amount of exploration for free via heterogeneity.

### 2017-11-23 paper.tex
more edits to intro

--- 2017-11-20 paper.tex
@@
 \section{Introduction}
-In this paper, we study a variant of incentivizing exploration with heterogeneous agents' preferences, that generalizes \cite{frazier2014incentivizing} and \cite{han2015incentivizing}.
+In this paper, we study incentivizing exploration with heterogeneous agent preferences.
+In this problem,   
+arms have unknown multivariate attributes, and agents have heterogeneous linear utility functions that map these attribute vectors onto utilities.
+Agents see noisy observations of attributes of arms pulled by all previous agents, and estimate an arms' attribute vector by the simple average of these observations.
+Agents are selfish, and pull the arm with the largest estimated utility summed with an optional arm-specific incentivizing payment chosen by the principle.
+We study strategies for choosing such incentive payments that seek to maximize the total utility derived by agents, subject to a limitation on the total incentive payment.
+To accomplish this goal, a strategy must induce sufficient exploration to reveal arms' attributes, while still letting agents select myopically and according to their preferences sufficiently often that high-utility arms are chosen and incentive payments are kept small.
 
-In our setting we have arms that have unknown multivariate attributes, and agents have heterogeneous utility functions that map these attribute vectors onto utilities.
-All agents see the attribute outcomes from previous agents.
-We study a simple policy that mostly exploits, and occasionally incentivizes exploration when an arm would be unpulled by all agent types given the current posterior.
+Our problem setting models online review aggregators like Amazon, Yelp, and Tripadvisor that host crowdsourced reviews that users use when selecting products, restaurants, and vacation destinations.
+Users of these websites wish to choose the product / restaurant / vacation (item) that is best according to their preference over attributes, and rely on previous users' reviews to estimate these attributes.
+These reviews provide not just cardinal feedback, but also a description of attributes that a user with different preferences may use to select their preferred item.
+An item with only a small number of reviews might have inaccurate attribute estimates, leading users to choose not to try it even though it may actually be the best choice for some subset of those users.
+Without incentives, this situation may persist and decrease welfare for the platform's user base.
+By offering incentives, either through price reductions by Amazon or coupons from Yelp or Tripadvisor, a platform may induce more reviews of unexplored items and provide more value over the long term.
 
-The intuition behind is that heterogeneity of a certain kind reduces but doesn't eliminate the need for incentivizing exploration --- you get a certain amount of exploration for free via heterogeneity.
+\pfcomment{Banguri, I'm a bit confused about the citizen science application --- let's leave it out of the dissertation, but leave it in the paper.
+Can you add some more detail?
+For example, with Galaxy Zoo, my understanding is that you are looking at galaxies on a computer screen and so there is no weather.
+Maybe you are talking about e-bird?
+Can you write something that clarifies this and then we can talk more?}
 
-We structure our paper as follows: In Section~\ref{sec:prob}, we state our problem formulation; In Section~\ref{sec:ub}, we state our algorithm and prove with $O(N^3)$ payment budget, we can achieve $O(N^2+(\log(T))^2)$ regret; In Section~\ref{sec:lb}, we construct an example to show that the regret bound is at least $O(\log(T))$ in the worst case example, regardless the payment budget.
+% \item \textit{Citizen Science}:  \cite{frazier2014incentivizing} mentioned for scientific organizations like Galaxy Zoo, they will guide the enthusiasts to explore the less-explored parts of domain.
+For each enthusiast, he/she may have different preference towards the location's sight-seeing, weather, distance and safety etc.
+Thus, as the organization, it needs to incentivize each person differently.
 
-\subsection{Related Work}
+\pfcomment{Bangrui, if you can come up with an example of an application with implicit attribute feedback, include it here.}
+
+% Something interesting to study would be to alter the search rankings to influence people
+% Also which items to spam people about reviewing
+
+In this problem context, we study a simple policy that usually exploits, incentivizing agents to pull an arm only when the set of agent utility functions that would pull this arm without incentives has probability below a time-varying threshold.
+\pfcomment{Say something about what we show for this policy.}
+
+\pfcomment{Talk about how our regret bounds compare to what our regret bounds would be in a homogenous preference setting, to clarify the following sentences.}
+These results suggest that heterogeneous agent preferences reduces but does not eliminate the need to incentive exploration, in relation to single-preference settings.
+Essentially, heterogeneity provides a certain amount of exploration for free.
+
+We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+(\log(T))^2)$ regret with $O(N^3)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is at least $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
+
+\section{Related Work}
 
@@
 
-\begin{itemize}
-\item With money transfer: \cite{frazier2014incentivizing} considers a problem setting where the principal pays the agents extra money in order to incentivize them to explore.
+With money transfer: \cite{frazier2014incentivizing} considers a problem setting where the principal pays the agents extra money in order to incentivize them to explore.
 In their paper, they assume all agents have equal value of money and provide a complete characterization of achievable reward with a fixed budget.
@@
 Under this setting, they proved a similar bound as in \cite{frazier2014incentivizing} which depends on the signal scheme.
-\item Without money transfer but using information asymmetry: \cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time.
+
+Without money transfer but using information asymmetry: \cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time.
 \cite{mansour2015bayesian} generalizes \cite{kremer2014implementing} by allowing finite number of actions at each time.
@@
 They prove principal can achieve constant regret when utilities are deterministic and logarithmic regret when utilities are stochastic.
-\end{itemize}
-
-\subsection{Applications}
-
-The motivation of this project is to build a recommender system.
-Agents arrive to the system one at a time.
-Upon arrival, he/she receives a recommendation from the system and chooses a product based on the recommendation.
-At the end, the agent provides some feedback about the product when he/she leaves the system.
-Here are a few applications where we can apply our framework:
-
-\begin{itemize}
-\item \textit{Recommender systems/Online Retailers}: For recommender systems such as Yelp, they want to find the best restaurants based on the user's review.
-As the system, it wants all restaurants to have as many reviews as possible so that it knows which restaurants are good.
-However, as a user, he/she may only want to try the restaurants with a large number of positive reviews.
-In this case, the system may incentivize the user to review the new restaurants by offering them extra money as a reward.
-As for users, they may have different utilities vectors about the restaurant's location, environment, service, queueing time etc, which could be the restaurant's attribute vector.
-This is also the case for online retailers such as Amazon.
-In this case, the attribute vector could be each item's quality, design and price etc.
-\item \textit{Citizen Science}:  \cite{frazier2014incentivizing} mentioned for scientific organizations like Galaxy Zoo, they will guide the enthusiasts to explore the less-explored parts of domain.
-For each enthusiast, he/she may have different preference towards the location's sight-seeing, weather, distance and safety etc.
-Thus, as the organization, it needs to incentivize each person differently.
-\end{itemize}
 

### 2017-11-23 paper.tex
a few more edits to the intro

@@
 
+% \item \textit{Citizen Science}:  \cite{frazier2014incentivizing} mentioned for scientific organizations like Galaxy Zoo, they will guide the enthusiasts to explore the less-explored parts of domain.
+For each enthusiast, he/she may have different preference towards the location's sight-seeing, weather, distance and safety etc.
+Thus, as the organization, it needs to incentivize each person differently.
+
 \pfcomment{Banguri, I'm a bit confused about the citizen science application --- let's leave it out of the dissertation, but leave it in the paper.
@@
 Maybe you are talking about e-bird?
-Can you write something that clarifies this and then we can talk more?}
-
-% \item \textit{Citizen Science}:  \cite{frazier2014incentivizing} mentioned for scientific organizations like Galaxy Zoo, they will guide the enthusiasts to explore the less-explored parts of domain.
-For each enthusiast, he/she may have different preference towards the location's sight-seeing, weather, distance and safety etc.
-Thus, as the organization, it needs to incentivize each person differently.
-
-\pfcomment{Bangrui, if you can come up with an example of an application with implicit attribute feedback, include it here.}
+Can you write something that clarifies this and then we can talk more?
+Also, if you can come up with an example of an application with implicit attribute feedback, include it here.}
 
@@
 
-We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+(\log(T))^2)$ regret with $O(N^3)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is at least $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
-
-\section{Related Work}
-
 We broadly categorize the literature into two categories based on whether there is money transfer.
-
-With money transfer: \cite{frazier2014incentivizing} considers a problem setting where the principal pays the agents extra money in order to incentivize them to explore.
+With money transfer, \cite{frazier2014incentivizing} considers a problem setting where the principal pays the agents extra money in order to incentivize them to explore.
 In their paper, they assume all agents have equal value of money and provide a complete characterization of achievable reward with a fixed budget.
@@
 
-Without money transfer but using information asymmetry: \cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time.
+Without money transfer but using information asymmetry, \cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time.
 \cite{mansour2015bayesian} generalizes \cite{kremer2014implementing} by allowing finite number of actions at each time.
@@
 They prove principal can achieve constant regret when utilities are deterministic and logarithmic regret when utilities are stochastic.
+
+We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+(\log(T))^2)$ regret with $O(N^3)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is at least $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
 

### 2017-11-24 paper.tex
addressed comments in the intro section

@@
 
-% \item \textit{Citizen Science}:  \cite{frazier2014incentivizing} mentioned for scientific organizations like Galaxy Zoo, they will guide the enthusiasts to explore the less-explored parts of domain.
+We can also apply our models to scientific organizations like eBird \cite{frazier2014incentivizing}.
+EBird is a website which guides the enthusiasts to explore and report their findings to the bird community.
+In each report, it contains information such as when, where and how they go birding as well as what kinds of birds they see and hear.
+As the orginization, EBird needs to incentivize the enthusiasts to explore the less-explored parts of domain.
 For each enthusiast, he/she may have different preference towards the location's sight-seeing, weather, distance and safety etc.
-Thus, as the organization, it needs to incentivize each person differently.
-
-\pfcomment{Banguri, I'm a bit confused about the citizen science application --- let's leave it out of the dissertation, but leave it in the paper.
-Can you add some more detail?
-For example, with Galaxy Zoo, my understanding is that you are looking at galaxies on a computer screen and so there is no weather.
-Maybe you are talking about e-bird?
-Can you write something that clarifies this and then we can talk more?
-Also, if you can come up with an example of an application with implicit attribute feedback, include it here.}
+By offering enthusiasts incentivies, eBirds can obtain more reports about the less-explored area and have more information for the bird community.\bccomment{How about this eBird application?}
 
@@
 In this problem context, we study a simple policy that usually exploits, incentivizing agents to pull an arm only when the set of agent utility functions that would pull this arm without incentives has probability below a time-varying threshold.
-\pfcomment{Say something about what we show for this policy.}
-
-\pfcomment{Talk about how our regret bounds compare to what our regret bounds would be in a homogenous preference setting, to clarify the following sentences.}
+In our paper, we assume all arms are some agents' best arm.
+Under this assumption, we prove with $O(N^2)$ payment budget, we can bound the cumulative expected regret by $O(N^2+M(\log(T))^2)$ where $M$ is the upper bound of the marginal density for those agents who are indifferent between their best and the second best arm.
+In the case that $M=0$, which typically happens when the user preference distribution is discrete, we can achieve constant cumulative expected regret $O(N^2)$.
+The key difference between our problem setting and the homogenous preference setting (or the traditional multi-armed bandits setting) is that we do not need to incentivize the agents to try a suboptimal arm very often since all arms are some agents's best arm.
 These results suggest that heterogeneous agent preferences reduces but does not eliminate the need to incentive exploration, in relation to single-preference settings.
 Essentially, heterogeneity provides a certain amount of exploration for free.
+\bccomment{How about now?}
 
@@
 We use $c_t=c_{A_{t},t}$ to denote the actual incentive payment at time $t$.
-For simplicity, we assume all arms have been pulled once at time $t=1$ in this paper (we can offer a large payment at the beginning to make this happen).
-\pfcomment{Bangrui, I assumed that $u(i,t)$ starts from $0$.
-Do you want to do this, or do you want to assume that every arm is pulled at least once?
-Or do you want to assume that they start from some general starting value?
-We could perhaps do the analysis assuming they start from $0$, but then comment that the proofs all carry through if they start from some other value.}
+For simplicity, we assume all arms have been pulled once at time $t=1$ in this paper, i.e.
+$u(i,0)=1$ for all $i$.
+\bccomment{Peter, is it ok that I assume $u(i,0)$ starts with 1?}
 

### 2017-11-24 paper.tex
a few small edits to the intro

@@
 
-Our problem setting models online review aggregators like Amazon, Yelp, and Tripadvisor that host crowdsourced reviews that users use when selecting products, restaurants, and vacation destinations.
-Users of these websites wish to choose the product / restaurant / vacation (item) that is best according to their preference over attributes, and rely on previous users' reviews to estimate these attributes.
-These reviews provide not just cardinal feedback, but also a description of attributes that a user with different preferences may use to select their preferred item.
-An item with only a small number of reviews might have inaccurate attribute estimates, leading users to choose not to try it even though it may actually be the best choice for some subset of those users.
+Our problem setting models online review aggregators like Amazon, Yelp, and Tripadvisor that host crowdsourced reviews.
+Users of these websites wish to use the reviews hosted there to choose the product / restaurant / vacation (generically referred to as an ``item'') that is best according to their preferences.
+These reviews provide not just cardinal feedback, but also a description of items' attributes that a user may consider together with their personal preferences to select their preferred item.
+An item with few reviews might have inaccurate attribute estimates, leading users to avoid it even though it may actually be their best choice.
 Without incentives, this situation may persist and decrease welfare for the platform's user base.
@@
 
-We can also apply our models to scientific organizations like eBird \cite{frazier2014incentivizing}.
-EBird is a website which guides the enthusiasts to explore and report their findings to the bird community.
-In each report, it contains information such as when, where and how they go birding as well as what kinds of birds they see and hear.
-As the orginization, EBird needs to incentivize the enthusiasts to explore the less-explored parts of domain.
-For each enthusiast, he/she may have different preference towards the location's sight-seeing, weather, distance and safety etc.
-By offering enthusiasts incentivies, eBirds can obtain more reports about the less-explored area and have more information for the bird community.\bccomment{How about this eBird application?}
+Our problem setting also applies to crowd science platforms like eBird \cite{frazier2014incentivizing}.
+\pfcomment{Can you also cite their website?} EBird guides birding enthusiasts through a website to explore and report their findings to the birding community.
+Each user report contains information about when, where and how they go birding and what birds they see and hear.
+EBird may wish to incentivize enthusiasts to explore less-explored birding locations and provide more accurate reports on these locations.
+Each enthusiast may have different preference over a location's attributes such as the diversity of bird species, weather, distance and safety.
+By offering enthusiasts incentivies to explore, eBird can create a more accurate body of reports and provide better value to the birding community.
 
@@
 In our paper, we assume all arms are some agents' best arm.
-Under this assumption, we prove with $O(N^2)$ payment budget, we can bound the cumulative expected regret by $O(N^2+M(\log(T))^2)$ where $M$ is the upper bound of the marginal density for those agents who are indifferent between their best and the second best arm.
-In the case that $M=0$, which typically happens when the user preference distribution is discrete, we can achieve constant cumulative expected regret $O(N^2)$.
-The key difference between our problem setting and the homogenous preference setting (or the traditional multi-armed bandits setting) is that we do not need to incentivize the agents to try a suboptimal arm very often since all arms are some agents's best arm.
-These results suggest that heterogeneous agent preferences reduces but does not eliminate the need to incentive exploration, in relation to single-preference settings.
-Essentially, heterogeneity provides a certain amount of exploration for free.
-\bccomment{How about now?}
+Under this assumption, we prove that with $O(N^2)$ payment budget, this policy has $O(N^2+M(\log(T))^2)$ cumulative expected regret where $M$ is an upper bound on the limiting marginal probability density of agent utilities that are nearly indifferent between their best and the second best arm.
+If $M=0$, which typically happens when the agent utility distribution is discrete, this policy achieve constant cumulative expected regret $O(N^2)$.
+The key difference between our problem setting and both the homogenous preference setting and the traditional multi-armed bandits setting is that we must incentivize agents to try suboptimal arms much less often, since all arms are some agents' best arm.
+Essentially, heterogeneity provides free exploration.
+These results suggest that heterogeneous agent preferences reduce but do not eliminate the need to incentive exploration, in relation to single-preference settings.
 
-We broadly categorize the literature into two categories based on whether there is money transfer.
-With money transfer, \cite{frazier2014incentivizing} considers a problem setting where the principal pays the agents extra money in order to incentivize them to explore.
-In their paper, they assume all agents have equal value of money and provide a complete characterization of achievable reward with a fixed budget.
-\cite{han2015incentivizing} generalizes this framework to allow agents have heterogeneous value of money.
-Further, it assumes there is a external signal scheme which provides partial information about each agent.
-Under this setting, they proved a similar bound as in \cite{frazier2014incentivizing} which depends on the signal scheme.
+We broadly categorize the relevant previous literature into two categories based on whether there is money transfer.
+With money transfer, \cite{frazier2014incentivizing} considers a problem setting where the principal pays agents money to explore.
+This work assumes all agents have equal value for money and provide a complete characterization of achievable reward with a fixed budget.
+\cite{han2015incentivizing} generalizes this framework to include agents with heterogeneous value for money, and to allow an external signal to provide partial information about this valuation.
+Under this setting, this work proves a bound on achievable reward as a function of the budget and the signal scheme.
 
 Without money transfer but using information asymmetry, \cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time.
-\cite{mansour2015bayesian} generalizes \cite{kremer2014implementing} by allowing finite number of actions at each time.
-\cite{mansour2016bayesian} considers a problem setting where there are multiple agents at each time and allow agents to interact with each other.
-In these papers, the principal provides each agent an recommendation at each time, which is Bayesian incentive-compatible.
-They prove principal can achieve constant regret when utilities are deterministic and logarithmic regret when utilities are stochastic.
+\cite{mansour2015bayesian} generalizes \cite{kremer2014implementing} by allowing a finite number of actions at each time.
+\cite{mansour2016bayesian} considers a problem setting where there are multiple agents at each time and agents may interact with each other.
+In these papers, the principal provides each agent a recommendation at each time that is Bayesian incentive-compatible.
+They prove the principal can achieve constant regret when utilities are deterministic and logarithmic regret when utilities are stochastic.
 
-We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+(\log(T))^2)$ regret with $O(N^3)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is at least $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
+We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+(\log(T))^2)$ regret with $O(N^3)$ incentive budget \pfcomment{This should be $N^2$, right?
+Also, do you want to add $M$ in here?}; Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
 

### 2017-11-24 paper.tex
minor edit in section 2
addressed comments in the intro section and fixed the notation of u(i,0) in section 2

@@
 
-Our problem setting also applies to crowd science platforms like eBird \cite{frazier2014incentivizing}.
-\pfcomment{Can you also cite their website?} EBird guides birding enthusiasts through a website to explore and report their findings to the birding community.
+Our problem setting also applies to crowd science platforms like eBird \cite{frazier2014incentivizing, sullivan2009ebird}.
+EBird guides birding enthusiasts through a website to explore and report their findings to the birding community.
 Each user report contains information about when, where and how they go birding and what birds they see and hear.
@@
 
-We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+(\log(T))^2)$ regret with $O(N^3)$ incentive budget \pfcomment{This should be $N^2$, right?
-Also, do you want to add $M$ in here?}; Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
+We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+M(\log(T))^2)$ regret with $O(N^2)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
 
@@
 We have $N$ arms. Arm $i$ has a fixed but unknown attribute vector $u_i\in \mathbb{R}^{m}$. 
-
 A stream of myopic selfish agents come to our system.
@@
 At each time $t$, for each arm $i$, we (the principal) offer a non-negative payment $c_{i,t}\geq 0$ based on previous observations.
-We assume that agent $t$ chooses to pull the arm that myopically maximizes the sum of this payment and an estimate of the utility obtained $\theta_t \cdot u_{i,t}$ where $u_{i,t}$ denotes the simple average of $O_s$ over all previous pulls of arm $i$ if it has been pulled at least once, or a default value of $0$ if not.
-That is, $u_{i,t} = \sum_{s<t} O_s 1\{A_s = i\} / \sum_{s<t} 1\{A_s = i\}$ if the denominator is strictly positive and $0$ otherwise; and $A_t=\argmax_{i}\{\theta_t\cdot u_{i,t}+c_{i,t}\}$, breaking ties in favor of the arm with the highest incentive.
+We assume that agent $t$ chooses to pull the arm that myopically maximizes the sum of this payment and an estimate of the utility obtained $\theta_t \cdot u_{i,t}$ where $u_{i,t}$ denotes the simple average of $O_s$ over all previous pulls of arm $i$.
+In this paper, we assume all arms have been pulled once at time $t=0$ and $u(i,0)$ denotes a random draw from the arm attribute vector.
+For $t>0$, denote $u_{i,t} = \frac{\sum_{s<t} O_s 1\{A_s = i\} + u(i,0)}{\sum_{s<t} 1\{A_s = i\}+1}$ and $A_t=\argmax_{i}\{\theta_t\cdot u_{i,t}+c_{i,t}\}$, breaking ties in favor of the arm with the highest incentive.
 We use $c_t=c_{A_{t},t}$ to denote the actual incentive payment at time $t$.
-For simplicity, we assume all arms have been pulled once at time $t=1$ in this paper, i.e.
-$u(i,0)=1$ for all $i$.
-\bccomment{Peter, is it ok that I assume $u(i,0)$ starts with 1?}
 

### 2017-11-24 paper.tex
edits to algo section

--- 2017-11-24 paper.tex
@@
 We have $N$ arms. Arm $i$ has a fixed but unknown attribute vector $u_i\in \mathbb{R}^{m}$. 
-
 A stream of myopic selfish agents come to our system.
 Agent $t$ has linear preferences over attributes described by a vector $\theta_t \in \mathbb{R}^m$ that is unknown to the principal and drawn i.i.d.
-from a known distribution $F(\cdot)$.
+from a known distribution $F(\cdot)$ with compact support.
 We refer synonomously to an agent and that agent's preference vector: when we say ``an agent $\theta$'', we mean ``an agent with preference vector $\theta$.''
@@
 
-To support later development, we define three additional pieces of notation.
+To support later development, we define some additional notation.
 We let $B(\theta)$ and $\hat{B}(\theta)$ refer to the index of the arm that is best and second best for an agent with preference vector $\theta$, $B(\theta) \in \argmax_i \theta \cdot u_i$ and $\hat{B}(\theta)=\argmax_{i\neq B(\theta)}\theta\cdot u_{i}$, breaking ties uniformly at random.
 We let $N(i,t)$ denote the cardinality of $A_t$, i.e., the number of pulls of arm $i$ at times up to and including $t$.
+We call time $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$ the {\it starting point of the $n^{th}$ round}. We call the set of times $[t_{n}, t_{n+1})$ the {\it $n^{th}$ round}.
 
-\section{Upper Bound}
+\section{Algorithm and Upper Bound}
 \label{sec:ub}
@@
 \subsection{Our Algorithm}
-Before we introduce our algorithm, we need to use the following definition:
+Our algorithm incentivizes pulling an arm $i$ at a time $t$ in round $n$ if and only if both of the following criteria are met:
+\begin{itemize}
+\item the probability of pulling arm $i$ would be below $n^{-1}$ without incentives; 
+\item arm $i$ has not been played previously in the current round.
+\end{itemize}
+Ties are broken randomly.  This algorithm does not need to know the horizon $T$ in advance.
 
-\begin{definition}
-We call time $t_{n}$ as the starting point of the $n^{th}$ round if $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$. We call the time period from $t_{n}$ to $t_{n+1}$ as the $n^{th}$ round.
-\end{definition}
+If our algorithm decides to incentivize an arm $i$, it uses the ``pay whatever it takes'' strategy in which the payment offered is $\max_{\theta,j} \theta \cdot (u_j - u_i)$.
+This maximum over $\theta$ is taken over the support of $F$, which we recall is assumed compact.
+(We use this ``pay whatever it takes'' strategy for its simplicity, and in Section~\ref{sec:pi} we provide an alternate and smaller incentive payment that achieves the same payment budget bound and regret bound).
 
-We consider an algorithm that offers incentive to an arm $i$ if and only if both of the following criterias are met:
-\begin{itemize}
-\item the myopic probability of pulling arm $i$ is low; 
-\item arm $i$ has not been played or incentivized before in this round.
-\end{itemize}
-We break ties randomly.
-If we decides to incentivize an arm, we use ``pay whatever it takes'' strategy (We use ``pay whatever it takes'' strategy mainly because of its simplicity.
-In Section~\ref{sec:pi}, we provide a more realistic algorithm which has the same payment budget bound and regret bound).
-This algorithm does not need to know $T$ in advance.
-The detailed algorithm is as follows:
+We describe our algorithm in detail as follows:
 
@@
 \FOR{ $t = 1, 2, 3, \cdots$}{
-	\IF{the myopic probability of pulling an arm is less than $n^{-1}$ and no agents have pulled that arm in this round (break ties randomly)}
-	\STATE{ we pay whatever it takes to incentivize that arm}\ELSE 
-		\STATE {let the agents play myopically}\ENDIF
-		\STATE $n = min_{i} N(i,t)$
+	\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
+  \IF {$S$ is non-empty}
+    \STATE{Choose an arm $i$ uniformly at random from $S$}
+    \STATE{Pay whatever it takes to incentivize pulling arm $i$, i.e., offer payment 
+    $c_{i,t} = \max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$ and $c_{j,t} = 0$ for $j \ne i$.}
+  \ELSE
+  \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
+  \ENDIF
+  \STATE Update $u_{i,t}$ and $N(i,t)$ for the pulled arm
+  \STATE Update the round number, $n = \min_{i} N(i,t)$
 }\ENDFOR
@@
 \subsection{Assumptions}
-In this secion, we discuss several assumptions that we need to acheive our results.
-Throughout this paper, we use $F(\cdot)$ to denote the agent's preference distribution, which could either be a continuous distribution or a discrete distribution.
-Denote
+In this secion, we discuss several assumptions that we need to acheive our results.  Denote
 
@@
 \begin{assumption}
-Denote $p=\min_{i}P(\{\theta: B(\theta)=i\})$. Throughout this paper, we assume $p>0$.
+Denote $p=\min_{i}P(\{\theta: B(\theta)=i\})$. We assume $p>0$.
 \label{A3}

### 2017-11-24 paper.tex
fixed the definitions of N(i,t) and u_{i,t}

--- 2017-11-24 paper.tex
@@
 We assume that agent $t$ chooses to pull the arm that myopically maximizes the sum of this payment and an estimate of the utility obtained $\theta_t \cdot u_{i,t}$ where $u_{i,t}$ denotes the simple average of $O_s$ over all previous pulls of arm $i$.
-In this paper, we assume all arms have been pulled once at time $t=0$ and $u(i,0)$ denotes a random draw from the arm attribute vector.
-For $t>0$, denote $u_{i,t} = \frac{\sum_{s<t} O_s 1\{A_s = i\} + u(i,0)}{\sum_{s<t} 1\{A_s = i\}+1}$ and $A_t=\argmax_{i}\{\theta_t\cdot u_{i,t}+c_{i,t}\}$, breaking ties in favor of the arm with the highest incentive.
+In this paper, we assume all arms have been pulled once at time $t=0$ and $u_{i,0}$ denotes a random draw from the arm attribute vector.
+For $t>0$, denote $u_{i,t} = \frac{\sum_{s<t} O_s 1\{A_s = i\} + u_{i,0}}{\sum_{s<t} 1\{A_s = i\}+1}$ and $A_t=\argmax_{i}\{\theta_t\cdot u_{i,t}+c_{i,t}\}$, breaking ties in favor of the arm with the highest incentive.
 We use $c_t=c_{A_{t},t}$ to denote the actual incentive payment at time $t$.
@@
 We let $B(\theta)$ and $\hat{B}(\theta)$ refer to the index of the arm that is best and second best for an agent with preference vector $\theta$, $B(\theta) \in \argmax_i \theta \cdot u_i$ and $\hat{B}(\theta)=\argmax_{i\neq B(\theta)}\theta\cdot u_{i}$, breaking ties uniformly at random.
-We let $N(i,t)$ denote the cardinality of $A_t$, i.e., the number of pulls of arm $i$ at times up to and including $t$.
+We let $N(i,t)$ denote the number of pulls of arm $i$ at times up to and including $t$ plus $1$ (because of the initial pull), i.e.
+$N(i,t)=\sum_{s<t} 1\{A_s = i\}+1$.
 

### 2017-11-24 paper.tex
Edits to section on assumptions

--- 2017-11-24 paper.tex
@@
 \subsection{Assumptions}
-In this secion, we discuss several assumptions that we need to acheive our results.  Denote
-
+In this secion, we state several assumptions assumed by our analysis.  First define
 \begin{align}
@@
 \end{align}
-which is the users whose best arm is arm $i$ and the second best arm is arm $j$. We need the following assumptions in our analysis:
+which is the set of agent preferences whose best arm is arm $i$ and second best arm is arm $j$. With this definition, our analysis makes the following assumptions:
 
@@
 For simplicity in our analysis, we use a slightly stronger condition below: $M=\max_{i,j}sup_{y\in R^{+}}f_{i,j}(y) <\infty$.
+\pfcomment{Let's state the assumption in terms of $M$, which is what our proof uses, and then if you want to say that we can also show similar results for $M'$ we can say that informally here.}
 
@@
 
-Throughout this write up, we use $R$ to denote the maximum regret it can occur at each time. We know $R<\infty$ due to Assumption~\ref{A2}.
+We use $R = \max_{\theta, i,j} \theta \cdot (u_i - u_j)$ to denote the maximum regret that can be incurred at each time.  Assumption~\ref{A2} shows that $R<\infty$.
 
@@
 
-Assumption~\ref{A3} means for each arm $i$, there exist a positive proportion of users whose best arm is $i$.
+Assumption~\ref{A3} means each arm $i$ has a strictly positive proportion of users for which that arm is best.
 

### 2017-11-24 paper.tex

--- 2017-11-24 paper.tex
@@
 We let $B(\theta)$ and $\hat{B}(\theta)$ refer to the index of the arm that is best and second best for an agent with preference vector $\theta$, $B(\theta) \in \argmax_i \theta \cdot u_i$ and $\hat{B}(\theta)=\argmax_{i\neq B(\theta)}\theta\cdot u_{i}$, breaking ties uniformly at random.
-We let $N(i,t)$ denote the cardinality of $A_t$, i.e., the number of pulls of arm $i$ at times up to and including $t$.
+We let $N(i,t)$ denote the number of pulls of arm $i$ at times up to and including $t$ plus $1$ (because of the initial pull), i.e.
+$N(i,t)=\sum_{s<t} 1\{A_s = i\}+1$.
 We call time $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$ the {\it starting point of the $n^{th}$ round}. We call the set of times $[t_{n}, t_{n+1})$ the {\it $n^{th}$ round}.
@@
 
-In this section, we propose a simple policy that mostly exploits, and occasionally incentivizes exploration when an arm would be unpulled by all agent types given the current posterior.
+In this section, we propose a simple policy that mostly exploits, and occasionally incentivizes exploration when the probability of an arm would be pulled by all agent types below a time-varying threshold given the current posterior.
 We prove that with the help of heterogeneous preferences, we can get a certain amount of exploration for free via heterogeneity.

### 2017-11-24 paper.tex
did some edits

@@
 
-If our algorithm decides to incentivize an arm $i$, it uses the ``pay whatever it takes'' strategy in which the payment offered is $\max_{\theta,j} \theta \cdot (u_j - u_i)$.
+If our algorithm decides to incentivize an arm $i$, it uses the ``pay whatever it takes'' strategy in which the payment offered is $\max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$.
 This maximum over $\theta$ is taken over the support of $F$, which we recall is assumed compact.
@@
 Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm.
-For simplicity in our analysis, we use a slightly stronger condition below: $M=\max_{i,j}sup_{y\in R^{+}}f_{i,j}(y) <\infty$.
-\pfcomment{Let's state the assumption in terms of $M$, which is what our proof uses, and then if you want to say that we can also show similar results for $M'$ we can say that informally here.}
 

### 2017-11-25 paper.tex
fixed a typo in algorithm 1 & edited the proof related to M

@@
 \begin{algorithmic}
-\STATE Set n = 1 to denote the round number;
+\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
 \FOR{ $t = 1, 2, 3, \cdots$}{
 	\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
-  \IF {$S$ is non-empty}
-    \STATE{Choose an arm $i$ uniformly at random from $S$}
+  \IF {$S\setminus V$ is non-empty}
+    \STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
     \STATE{Pay whatever it takes to incentivize pulling arm $i$, i.e., offer payment 
@@
   \ENDIF
-  \STATE Update $u_{i,t}$ and $N(i,t)$ for the pulled arm
+  \STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
+  \IF {$n\neq \min_{i}N(i,t)$} 
+  	\STATE $V=\emptyset$
+  \ENDIF
   \STATE Update the round number, $n = \min_{i} N(i,t)$
@@
 \begin{assumption} Let $f_{i,j}(y)$ be the marginal probability density function (or marginal probability mass function if $F(\cdot)$ is a discrete distribution) of $(u_i-u_j)\cdot\theta$ conditioned on $\theta \in \Omega_{i,j}$.
-We assume $M^{'}=\max_{i,j}\limsup_{y\rightarrow 0^{+}}f_{i,j}(y) <\infty$.
+We assume $\max_{i,j}\sup_{y}f_{i,j}(y)\leq M$.
 \label{A1}
@@
 
+As we can see later in our proof, we only need $\max_{i,j}\limsup_{y\rightarrow 0^{+}}f_{i,j}(y)$ to be finite.
 Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm.
@@
 
-\begin{lemma}
-For $t\in[t_n,t_{n+1}]$, the expected incentive payment $E[c(t)]$ is bounded above by $\Delta + 2WNm \sqrt{\frac{2}{n\pi}}$. 
-\label{lemma:payment}
-\end{lemma}
-
-\begin{proof}
-Denote $\Delta=\sup_{\theta}\max_{i}\{\theta\cdot u_{B(\theta)}-\theta\cdot u_{i}\}$ to be the theoretical maximum payment with no noisy.
-We consider the expected payment in the $n^{th}$ round.
-Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$.
-
-\begin{align}
-&E[c(t)] \nonumber \\
-\leq & \Delta \times P(c(t)>0) + E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\min_{j}\theta_t\cdot \epsilon_{j,t}1\{c(t)>0\}] \nonumber \\
-\leq & \Delta + E[\max_{i}\theta_t\cdot \epsilon_{i,t}-\min_{j}\theta_t\cdot \epsilon_{j,t}] \nonumber \\
-\leq & \Delta + \sum_{j=1}^{m}2WE[\max_{i}|\epsilon_{i,t}^{j}|] \nonumber \\
-\leq & \Delta + 2W\sum_{j=1}^{m}E\left[\sum_{i=1}^{N}|\epsilon_{i,t}^{j}|\right] \nonumber \\
-\leq & \Delta + 2WNm E[|\epsilon_{1,t}^{1}|] \nonumber \\
-\leq & \Delta + 2WNm \sqrt{\frac{2}{n\pi}} \nonumber
-\end{align}
-
-\end{proof}
-
-Now we are ready to prove our first main result, Theorem~\ref{rst:budget}.
-\bccomment{The current proof about the cumulative expected payment is wrong.
-We need to bound the $E[c(t)|\textit{our algorithm decides to incentivize}]$ instead of $E[c(t)]$.
-However, the analysis for the cumulative regret is correct}
+Now we are ready to prove our first main result, Theorem~\ref{rst:budget}. \bccomment{The proof below only bounds the cumulative expected number of payments}
 
@@
 Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$.
-Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).The cumulative payment is bounded above by:
+Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).The cumulative expected number of payments is bounded above by:
 \begin{align}
-&E[C(T)] \nonumber \\
-= & \sum_{t=1}^{\infty}E[c(t)\mathbbm{1}\{\text{need to offer payment to an arm}\}] \nonumber \\
-\leq &\sum_{n=1}^{\infty}\sum_{t=1}^{\infty}E[c(t)\mathbbm{1}\{t_{n-1}\leq t\leq t_{n}: \text{myopic action occurs regret for agents with } \nonumber \\
-&\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq p^{-1}(n^{-1})\}\}] \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}\left(\Delta+Nm\sqrt{\frac{2}{n\pi}}\right)P(\text{myopic action occurs regret for agents with }\nonumber \\
-&\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq \delta_{0}\}|t_{n-1}\leq t\leq t_{n})P(t_{n-1}\leq t\leq t_{n})+\sum_{n=1}^{n_1}N\left(\Delta+\sqrt{\frac{2}{n\pi}}\right) \nonumber \\
-\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{32m^2\sigma^2}\right)\times Nn\left(\Delta+Nm\sqrt{\frac{2}{n_1\pi}}\right)+\sum_{n=1}^{n_1}N\left(\Delta+\sqrt{\frac{2}{n\pi}}\right) \nonumber
+&E[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}] \nonumber \\
+\leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}P\left(\exists i,j:|u_{i}^{j}-u_{i,t}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2m}\right)+\sum_{n=1}^{n_1}N \nonumber \\
+\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{32m^2\sigma^2}\right)\times Nn+\sum_{n=1}^{n_1}N \nonumber  \\
+=&24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2} + Nn_1, \nonumber
 \end{align}
 
-We know the expected payment is bounded above by:
-\begin{align}
-E[C(T)] \leq 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2}\left(\Delta+Nm\sqrt{\frac{2}{n_1\pi}}\right)+\sum_{n=1}^{n_1}N\left(\Delta+\sqrt{\frac{2}{n\pi}}\right).
-\nonumber
-\end{align}
+Thus, we know the expected number of payments is bounded above by $O(N^2)$.
 
-Since we have $N$ arms in total, we know the $\mathbb{E}[C(T)]=O(N^3)$.
 \end{proof}
 
-Based on the proof of Theorem~\ref{rst:budget}, we know the expected number of payments we need to make is less than
-\begin{align}
-&\sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{32m^2\sigma^2}\right)\times Nn+Nn_{1} \nonumber \\
-=&24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2} + Nn_1, \nonumber
-\end{align}
-which we will use in the proof of Theorem~\ref{rst:regret}. Now we are ready to prove our second main result, Theorem~\ref{rst:regret}.
+Now we are ready to prove our second main result, Theorem~\ref{rst:regret}.
 
@@
 \leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)R\times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \label{equ:regret}
 \end{align}
@@
 &\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-+ & 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2}+N\left(\max\left\{n_{0},\frac{2}{p}\right\}\right). \nonumber
++ & 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2}R+N\left(\max\left\{n_{0},\frac{2}{p}\right\}\right)R. \nonumber
 \end{align}
@@
 
-If we set $f^2(t)=\frac{2\log(T)\times 32m^2\sigma^2}{1.8n}$, then
+If we set $f^2(t)=\frac{2\log(T)\times 32m^2\sigma^2}{1.8t}$, then
 \begin{align}
@@
 
-\subsection{Special Case}
+\begin{corollary}
+If $\exists \delta>0$ such that $f_{i,j}(y)=0$ for all $i,j$ and $y\in [0,\delta]$, then the cumulative expected regret is bounded by $O(N^2)$.
+\end{corollary}
 
-In this section, we consider a special case of our problem, in which the agent's preference distribution $F(\cdot)$ satisfies $S(\delta)=0$ for $\delta<\delta^{'}$.
-The proof is similar to the proof of Theorem~\ref{rst:regret}, but for $t$ large enough, $S(f(t))=0$.
-In this case, with $O(N^3)$ payment budget, we can achieve $O(N^2)$ regret.
+\begin{proof}
+The proof of this corollary is similar to the proof of Theorem~\ref{rst:regret}.
+If we set $f^2(t)=\frac{2\log(T)\times 32m^2\sigma^2}{1.8t}$, then there exists a $t_{0}$ such that for $t>t_{0}$, $S(f(t))=0$.
+Thus, similar to equation~\eqref{equ:regret}, we know the cumulative expected regret when we let the agents play myopically is bounded above by
+\begin{align}
+\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{t_{0}}Mf(t)^2 \nonumber
+\end{align}
+Therefore, based on the same analysis of Theorem~\ref{rst:regret}, we know the cumulative regret is bounded by $O(N^2)$.
+\end{proof}
 
@@
 \begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration Revised}
+\caption{Algorithm: Incentivizing Exploration}
 \label{Alg2}
 \begin{algorithmic}
-\STATE Set n = 1 to denote the round number;
+\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
 \FOR{ $t = 1, 2, 3, \cdots$}{
-	\IF{the probability of pulling an arm $i$ is less than $n^{-1}$ and no agents have pulled that arm in this round (break ties randomly)}
-	\STATE{Offer payment $c_{i,t}=\inf\{c: P(\theta\sim F: \theta\cdot u_{i,t}+c>max_{j}\theta\cdot u_{j,t})>n^{-1}\}$}\ELSE 
-		\STATE {let the agents play myopically}\ENDIF
-		\STATE $n = min_{i} N(i,t)$
+	\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
+  \IF {$S\setminus V$ is non-empty}
+    \STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
+	\STATE{Offer payment $c_{i,t}=\inf\{c: P(\theta\sim F: \theta\cdot u_{i,t}+c>max_{j}\theta\cdot u_{j,t})>n^{-1}\}$}
+  \ELSE
+  \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
+  \ENDIF
+  \STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
+  \IF {$n\neq \min_{i}N(i,t)$} 
+  	\STATE $V=\emptyset$
+  \ENDIF
+  \STATE Update the round number, $n = \min_{i} N(i,t)$
 }\ENDFOR
@@
 
-In this section, we assume $\theta$ follows a continuous distribution $F(\cdot)$. We provide a example to show the best possible lower bound is $O(N\log(T))$.
+In this section, we assume $\theta$ follows a continuous distribution $F(\cdot)$. We provide a example to show the best possible lower bound is $O(N\log(T))$ regardless of the incentivizing strategy.
 

### 2017-11-26 paper.tex
added the proof of the cumulative budget, will do more edits tomorrow

@@
 \begin{theorem}
-The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^3)$. \bccomment{Our current analysis of the cumulative expected payment is wrong. See the comments of Lemma 6 for details}
+The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^3)$. 
 \label{rst:budget}
@@
 
-Now we are ready to prove our first main result, Theorem~\ref{rst:budget}. \bccomment{The proof below only bounds the cumulative expected number of payments}
+Now we are ready to prove our first main result, Theorem~\ref{rst:budget}.
+
+\begin{proof}
+Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$. Denote $\epsilon_{i,t}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,t}$. Define
+\begin{align}
+W^{'}[l] = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n,l), \forall i,t,j\}\nonumber
+\end{align}
+where $g(n,l)$ is a function which we will define later.
+Define $W[1] = W^{'}[1]$ and $W[i] = W^{'}[i]\setminus W^{'}[i-1]$ for $i\geq 2$.
+Based on the definition of $W[l]$, we know if $\omega\in W[l]$, the maximum payment we need to offer is bounded above by $R+2Wmg(n,l)$.
+Thus,
+
+\begin{align}
+&\sum_{t=1}^{\infty}c(t) \nonumber \\
+=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}c(t)\mathbbm{1}\{\omega_{t}\in w[l]\} \nonumber \\
+=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}c(t)\mathbbm{1}\{\omega_{t}\in w[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
+\end{align}
+
+Set $g(n,l)$ to be $\frac{l}{n}$.
+Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2m\lambda\}$, they will correctly identify their best arm.
+Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{l}{n} \leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms.
+Denote $a_0=\frac{2m}{p^{-1}(\frac{p}{2})}$.
+In order to have $\frac{l}{n}\leq \frac{p^{-1}(\frac{p}{2})}{2m}$, we need $n\geq \lceil a_{0} l\rceil$.
+In order to hvae $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
+Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$.
+Thus, we know we can only occur regret in the $l^{th}$ envelope in the first $\max\{n_1,\lceil a_0 l\rceil\}$ rounds.
+
+Thus,
+\begin{align}
+\sum_{t=1}^{\infty}c(t)=\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}c(t)\mathbbm{1}\{\omega_{t}\in w[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
+\end{align}
+
+Therefore,
+
+\begin{align}
+&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
+=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}E[c(t)|\omega_t\in w[l],t\in [t_n,t_{n+1}))P(\omega_t\in w[l],t\in [t_n,t_{n+1})) \nonumber \\
+=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[r+2Wm\frac{l}{n}\right]P(\omega_t\in w[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
+=&\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[r+2Wm\frac{l}{n}\right]P(\omega_t\in w[l]|t\in [t_n,t_{n+1}))Nn. \nonumber
+\end{align}
+
+We now bound $P(\omega\in W[l]|t\in[t_{n},t_{n+1}))$. \bccomment{Is my calculation to bound this probability correct?}
+\begin{align}
+&P(\omega\in W[l]|t\in[t_{n},t_{n+1})) \nonumber \\
+=&P(\omega\in W^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in W^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
+=&P(|\epsilon_{i,t}^{j}|<\frac{l}{n}, \forall i,j|t\in[t_n,t_{n+1}))-P(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}, \forall i,j|t\in[t_n,t_{n+1})) \nonumber \\
+=&\Pi_{i=1}^{N}\Pi_{j=1}^{m}P\left(|\epsilon_{i,t}^{j}|<\frac{l}{n}|t\in[t_n,t_{n+1})\right)-\Pi_{i=1}^{N}\Pi_{j=1}^{m}P\left(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}|t\in[t_n,t_{n+1})\right).
+\label{prob:upper}
+\end{align}
+Since we are at round $n$, we know there exists at least one arm, which has been pulled exactly $n$ times. Without loss of generality, we assume it to be arm $1$. Then we know
+
+\begin{align}
+\eqref{prob:upper}&\leq P\left(|\epsilon_{1,t}^{1}|<\frac{l}{n}|t\in[t_n,t_{n+1})\right)-P\left(|\epsilon_{1,t}^{1}|<\frac{l-1}{n}|t\in[t_n,t_{n+1})\right) \nonumber \\
+=&P\left(\frac{l-1}{n}<|\epsilon_{1,t}^{1}|<\frac{l}{n}|t\in[t_n,t_{n+1})\right) \nonumber \\
+=&P\left(\frac{\sqrt{n}(l-1)}{n}<|N(0,1)|<\frac{\sqrt{n}l}{n}|t\in[t_n,t_{n+1})\right) \nonumber \\
+=&2\Phi\left(\frac{\sqrt{n}l}{n}\right)-2\Phi\left(\frac{\sqrt{n}(l-1)}{n}\right) \nonumber \\
+=&2 \frac{1}{\sqrt{2\pi}}exp\left(-\frac{(l-1)^2}{2n}\right)\times (\sqrt{n})^{-1}. \nonumber
+\end{align}
+
+Thus,
+\begin{align}
+&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
+\leq & \sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[R+2Wm\frac{l}{n}\right]\times 2 \frac{1}{\sqrt{2\pi}}exp\left(-\frac{(l-1)^2}{2n}\right)\times (\sqrt{n})^{-1}Nn.
+\nonumber \\
+\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[R+2Wml\right]exp\left(-\frac{(l-1)^2}{2n}\right)\sqrt{n}. \nonumber
+\end{align}
+
+Denote $k_n=\max\{n_1, \lceil a_0 l \rceil\}$. Then we know
+\begin{align}
+&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
+\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[R+2Wml\right]exp\left(-\frac{(l-1)^2}{2k_n}\right)\sqrt{k_n} \nonumber \\
+\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\left[R+2Wml\right]exp\left(-\frac{(l-1)^2}{2k_n}\right)(k_n)^{3/2}. \nonumber
+\end{align}
+
+\end{proof}
+
+\begin{lemma}
+Under our algorithm, the expected number of payments is bounded above by $O(N^2)$.
+\end{lemma}
 

### 2017-11-26 paper.tex
did some edtis

@@
 
-In this section, we prove using Algorithm~\ref{Alg1}, we can achieve $O(N^2+(\log(T))^2)$ regret bound with $O(N^3)$ payment budget.
+In this section, we prove using Algorithm~\ref{Alg1}, we can achieve $O(N^2+M(\log(T))^2)$ regret bound with $O(N)$ payment budget, where $M$ bounds the density of agents who are indifferent between their best and second best arm.
 
@@
 \begin{align}
-W^{'}[l] = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n,l), \forall i,t,j\}\nonumber
+W^{'}[l] = \{\omega_t:|\epsilon_{i,t}^{j}(\omega)|\leq g(n,l), \forall i,j\}\nonumber
 \end{align}
-where $g(n,l)$ is a function which we will define later.
-Define $W[1] = W^{'}[1]$ and $W[i] = W^{'}[i]\setminus W^{'}[i-1]$ for $i\geq 2$.
-Based on the definition of $W[l]$, we know if $\omega\in W[l]$, the maximum payment we need to offer is bounded above by $R+2Wmg(n,l)$.
-Thus,
+where $g(n,l)$ is a function which we will define later. Define $W[1] = W^{'}[1]$ and $W[i] = W^{'}[i]\setminus W^{'}[i-1]$ for $i\geq 2$. We call $W[l]$ the $l^{th}$ envelope.
+
+Based on the definition of $W[l]$, we know if $\omega_t\in W[l]$, the maximum payment we need to offer at time $t$ is bounded above by $R+2Wmg(n,l)$. Thus,
 
@@
 Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2m\lambda\}$, they will correctly identify their best arm.
-Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{l}{n} \leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms.
+Thus in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{l}{n} \leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, then for each arm, at least $\frac{p}{2}$ agents would pull that arm.
+Further, if our time-varying threshold $n^{-1}\leq p/2$, we do not need to incentivize any arms.
 Denote $a_0=\frac{2m}{p^{-1}(\frac{p}{2})}$.
@@
 \end{align}
-Since we are at round $n$, we know there exists at least one arm, which has been pulled exactly $n$ times. Without loss of generality, we assume it to be arm $1$. Then we know
+Since we are at round $n$, we know there exists at least one arm, which has been pulled exactly $n$ times.
+Without loss of generality, we assume it to be arm $1$.
+Since $P\left(|\epsilon_{i,t}^{j}|<\frac{l}{n}|t\in[t_n,t_{n+1})\right)> P\left(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}|t\in[t_n,t_{n+1})\right)$ for all $i,j$, we know
 
@@
 \leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[R+2Wml\right]exp\left(-\frac{(l-1)^2}{2k_n}\right)\sqrt{k_n} \nonumber \\
-\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\left[R+2Wml\right]exp\left(-\frac{(l-1)^2}{2k_n}\right)(k_n)^{3/2}. \nonumber
+\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\left[R+2Wml\right]exp\left(-\frac{(l-1)^2}{2k_n}\right)(k_n)^{3/2}=O(N). \nonumber
 \end{align}
@@
 
-In this section, we assume $\theta$ follows a continuous distribution $F(\cdot)$. We provide a example to show the best possible lower bound is $O(N\log(T))$ regardless of the incentivizing strategy.
+In this section, we assume $\theta$ follows a continuous distribution $F(\cdot)$. We provide a example to show the best possible lower bound is $O(\log(T))$ regardless of the incentivizing strategy.
 
-Suppose you have two arms.
-Arm $1$ has utility vector $(0,0)$ and arm $2$ has utility vector $(0,1)$.
+Suppose we have two arms.
+Arm $1$ has attribute vector $(0,0)$ and arm $2$ has attribute vector $(0,1)$.
 We assume the users' preference are uniformly distributed on the unit circle.
@@
 
-For simplicity, we assume that the agents already know the true utility vector for arm $1$.
-Without loss of generality, denote $u_{t} = (0,1)+(z_{t1},z_{t,2}) = (0,1)+ (N(0,1/t),N(0,1/t))$ to be the estimate reward for arm $2$ (Without loss of generality, we assume the variance for the noise is $1$).
+To lower bound the regret, we assume that the agents already know the true utility vector for arm $1$.
+Without loss of generality, denote $u_{2,t} = (0,1)+(z_{t,1},z_{t,2}) = (0,1)+ (N(0,1/t),N(0,1/t))$ to be the estimate reward for arm $2$ (Without loss of generality, we assume the variance for the noise is $1$).
 
-At time $t$, suppose we know arm $1$ has utility vector $(0,0)$ and arm $2$ has utility vector $u_t\sim (N(0,\frac{1}{t}), N(1,\frac{1}{t}))$.
-Since we know $(z_{t,1}, z_{t,2})$ is symmetric around $(0,0)$, we know
+Since $(z_{t,1}, z_{t,2})$ is symmetric around $(0,0)$, we know
 
 \begin{align}
-&E[r_t] \nonumber \\
-= &E[r_t | z_{t,1}>0,z_{t,2}>0] \times P(z_{t,1}>0,z_{t,2}>0) + E[r_t |z_{t,1}>0,z_{t,2}<0] \times P(z_{t,1}>0,z_{t,2}<0) \nonumber \\
-= &E[r_t | z_{t,1}<0,z_{t,2}>0] \times P(z_{t,1}<0,z_{n,2}>0) + E[r_t |z_{t,1}<0,z_{t,2}<0] \times P(z_{t,1}<0,z_{t,2}<0) \nonumber \\
-\geq & 0.25 \times E[r_t | z_{t,1}>0, z_{t,2}>0]. \nonumber
+&E[r(t)] \nonumber \\
+= &E[r(t) | z_{t,1}>0,z_{t,2}>0] \times P(z_{t,1}>0,z_{t,2}>0) + E[r(t) |z_{t,1}>0,z_{t,2}<0] \times P(z_{t,1}>0,z_{t,2}<0) \nonumber \\
+= &E[r(t) | z_{t,1}<0,z_{t,2}>0] \times P(z_{t,1}<0,z_{n,2}>0) + E[r(t) |z_{t,1}<0,z_{t,2}<0] \times P(z_{t,1}<0,z_{t,2}<0) \nonumber \\
+\geq & 0.25 \times E[r(t) | z_{t,1}>0, z_{t,2}>0]. \nonumber
 \end{align}
@@
 \begin{align}
-&E[r_t| z_{t,1}>0, z_{t,2}>0] \nonumber \\
+&E[r(t)| z_{t,1}>0, z_{t,2}>0] \nonumber \\
 =& 4\times 2 \int_{0}^{\infty} \int_{0}^{\infty} \int_{0}^{\arctan\left(\frac{z_{t,1}}{1+z_{t,2}}\right)}\frac{\sin(\theta)}{2\pi}d(\theta)\frac{e^{-\frac{t \times z_{t,1}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,1})\frac{e^{-\frac{t \times z_{t,2}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,2}) \nonumber \\
@@
 \begin{align}
-\lim_{t\rightarrow\infty}\frac{E[r_t| z_{t,1}>0, z_{t,2}>0]}{t} = O(1). \nonumber
+\lim_{t\rightarrow\infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} = O(1). \nonumber
 \end{align}
@@
 
-and $\lim_{t\rightarrow \infty}d^{'}(t)=2$, we know for $n$ large enough, $d(t)$ is a increasing function in terms of t. Thus, based on the Monotone Convergence Theorem, we have
+and $\lim_{t\rightarrow \infty}d^{'}(t)=2$, we know for $t$ large enough, $d(t)$ is a increasing function in terms of t. Thus, based on the Monotone Convergence Theorem, we have
 
 \begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r_t| z_{t,1}>0, z_{t,2}>0]}{t} \nonumber \\
+&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} \nonumber \\
 =& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber
@@
 \begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r_t| z_{t,1}>0, z_{t,2}>0]}{t} \nonumber \\
+&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} \nonumber \\
 =&\frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ \frac{z_{t,1}^2}{2}e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) = \frac{1}{2\pi}.

### 2017-11-26 paper.tex
did some edtis

@@
 In our paper, we assume all arms are some agents' best arm.
-Under this assumption, we prove that with $O(N^2)$ payment budget, this policy has $O(N^2+M(\log(T))^2)$ cumulative expected regret where $M$ is an upper bound on the limiting marginal probability density of agent utilities that are nearly indifferent between their best and the second best arm.
-If $M=0$, which typically happens when the agent utility distribution is discrete, this policy achieve constant cumulative expected regret $O(N^2)$.
+Under this assumption, we prove that with $O(N)$ payment budget, this policy has $O(N^2+M(\log(T))^2)$ cumulative expected regret where $M$ is an upper bound on the limiting marginal probability density of agent utilities that are nearly indifferent between their best and the second best arm.
+\bccomment{We need a stronger condition, see corralary 1} If $M=0$, which typically happens when the agent utility distribution is discrete, this policy achieve constant cumulative expected regret $O(N^2)$.
 The key difference between our problem setting and both the homogenous preference setting and the traditional multi-armed bandits setting is that we must incentivize agents to try suboptimal arms much less often, since all arms are some agents' best arm.
@@
 
-We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+M(\log(T))^2)$ regret with $O(N^2)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
+We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+M(\log(T))^2)$ regret with $O(N)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
 
@@
 \begin{theorem}
-The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^3)$. 
+The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N)$. 
 \label{rst:budget}

### 2017-11-27 paper.tex
Fix to proof of Lemma 1

@@
 \subsection{Assumptions}
-In this secion, we state several assumptions assumed by our analysis.  First define
+In this section, we state several assumptions assumed by our analysis.  First define
 \begin{align}
@@
 
-In this section, we prove using Algorithm~\ref{Alg1}, we can achieve $O(N^2+M(\log(T))^2)$ regret bound with $O(N)$ payment budget, where $M$ bounds the density of agents who are indifferent between their best and second best arm.
-
-Before we start our analysis, we need the following notations.
-Denote $S(\delta)$ as the proportion of user whose utility difference between their best arm and the second best arm is less than $\delta$.
-Formally, $S(\delta)=P(\theta: \theta \cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}\leq \delta)$.
-Denote $p(\delta)=\min_{i}P(\{\theta:\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$.
-Based on $p(\delta)$'s definition, we know $p(0)=p$.
-
-With the help of our assumptions and the above notations, we now state our main results:
+In this section, we prove Algorithm~\ref{Alg1} achieves $O(N^2+M(\log(T))^2)$ cumulative regret with $O(N)$ payment budget.
+This is stated in the following pair of theorems, which together constitute our main results.
 
@@
 
-Before we prove our main results, we need to prove several lemmas. First, based on Assumption~\ref{A1}, we can get the following bound for $S(\delta)$.
+Before we prove these two theorems, we must first introduce two additional pieces of notation, which will be used in preliminary lemmas.
+Let $S(\delta)$ be the proportion of users whose utility difference between their best and second best arm is less than $\delta$.
+Formally, $S(\delta)=P(\theta: \theta \cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}\leq \delta)$.
+Then, let $p(\delta)=\min_{i}P(\{\theta:\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$.
+We know $p(0)=p$.
+
+With this additional notation, we now prove several lemmas.
+First, based on Assumption~\ref{A1}, we have the following bound for $S(\delta)$.
 
@@
 \begin{proof}
-\begin{align}
-S(\delta)&=\sum_{B(\theta)=i}\sum_{\hat{B}(\theta)=j}P(\{\theta(u_{i}-u_{j})<\delta\}) \nonumber \\
-&=\sum_{B(\theta)=i}\sum_{\hat{B}(\theta)=j}P(\{\theta(u_{i}-u_{j})<\delta|\theta\in \Omega_{i,j}\})P(\theta\in \Omega_{i,j}) \nonumber \\
-&\leq \sum_{B(\theta)=i}\sum_{\hat{B}(\theta)=j}M\delta \times P(\theta\in \Omega_{i,j}) \nonumber \\
-&=M\delta \nonumber 
-\end{align}
+\begin{align*}
+S(\delta)
+&=\sum_{i,j}P(\theta\cdot(u_{i}-u_{j})<\delta|\theta\in \Omega_{i,j})P(\theta\in \Omega_{i,j}) \\
+&\leq \sum_{i,j}M\delta \times P(\theta\in \Omega_{i,j}) \\
+&=M\delta.
+\end{align*}
 \end{proof}

### 2017-11-27 paper.tex
Fix another minor issue in proof of Lemma 1
edits to language in proof of lemma 3

@@
 S(\delta)
-&=\sum_{i,j}P(\theta\cdot(u_{i}-u_{j})<\delta|\theta\in \Omega_{i,j})P(\theta\in \Omega_{i,j}) \\
+&=\sum_{i,j}P(\theta\cdot(u_{i}-u_{j})\le \delta|\theta\in \Omega_{i,j})P(\theta\in \Omega_{i,j}) \\
 &\leq \sum_{i,j}M\delta \times P(\theta\in \Omega_{i,j}) \\
@@
 \begin{lemma}
-For those user whose utility difference between their best arm and the second best arm is at least $2m\lambda$, the probability that myopic action can incur regret at any time $t\in [t_{n-1},t_{n}-1]$ in the $n^{th}$ round is bounded above by $24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
+For those users whose utility difference between their best arm and the second best arm is at least $2m\lambda$, the probability that a myopic action can incur regret at any time $t\in [t_{n-1},t_{n}-1]$ in the $n^{th}$ round is bounded above by $24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
 \label{round:prob}
@@
 
-In order to prove the original lemma, we just need to show for $n\geq n_{0}$, we have
+To prove the lemma, we just need to show for $n\geq n_{0}$, we have
 \begin{align}
@@
 \end{align}
-Inequality~(\ref{n0-equ}) is true because the following two observations:
+Inequality~(\ref{n0-equ}) is true because of the following two observations:
 \begin{itemize}
 \item for $n\geq 50$, we have $\frac{n}{3+\log(n)}\geq n^{0.5}$;
-\item $n\geq \frac{23.04\sigma^4}{\lambda^4}$ we have $n^{0.5}\geq {4.8\sigma^{2}}{\lambda^{2}}$.
+\item for $n\geq \frac{23.04\sigma^4}{\lambda^4}$, we have $n^{0.5}\geq {4.8\sigma^{2}}{\lambda^{2}}$.
 \end{itemize}
@@
 
-We also need to use an adaptive concentration inequality, which is introduce in \cite{zhao2016adaptive}. For reference, we state it as a Lemma.
+To prove Lemma~\ref{round:prob}, we also need to use an adaptive concentration inequality due to \cite{zhao2016adaptive}. For reference, we state it here as a Lemma.
 
@@
 
-Now we can get back to prove Lemma~\ref{round:prob}.
+We now prove Lemma~\ref{round:prob}.
 
-\begin{proof}
+\begin{proof}[Proof of Lemma~\ref{round:prob}]
 In the $n^{th}$ round, we know all arms have been pulled at least $n$ times. Thus, the probability that myopic action can occur regret is bounded by

### 2017-11-27 paper.tex
Fixing some grammar

@@
 \begin{lemma}[Corollary 1 in \cite{zhao2016adaptive}]
-Let $X_{i}$ be zero mean $1/2$-subgaussian random variables. $\{S_{n}=\sum_{i=1}^{n}X_{i},n\geq 1\}$ be a random walk. Let $J$ be any random variable taking value in $\mathbb{N}$. If
+Let $X_{i}$ be zero mean $1/2$-subgaussian random variables. $\{S_{n}=\sum_{i=1}^{n}X_{i},n\geq 1\}$ be a random walk. Let $J$ be any random variable taking values in $\mathbb{N}$. If
 \begin{align}
@@
 \begin{proof}[Proof of Lemma~\ref{round:prob}]
-In the $n^{th}$ round, we know all arms have been pulled at least $n$ times. Thus, the probability that myopic action can occur regret is bounded by
+In the $n^{th}$ round, we know all arms have been pulled at least $n$ times. Thus, the probability that a myopic action can incur regret is bounded by
 \begin{align}
@@
 Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$.
-Thus, we know we can only occur regret in the $l^{th}$ envelope in the first $\max\{n_1,\lceil a_0 l\rceil\}$ rounds.
+Thus, we know we can only incur regret in the $l^{th}$ envelope in the first $\max\{n_1,\lceil a_0 l\rceil\}$ rounds.
 
@@
 \begin{proof}
-For regret occurred in the first $n_0$ round, it is bounded above by $\sum_{n=1}^{n_{0}}NRn$.
+For regret incurred in the first $n_0$ round, it is bounded above by $\sum_{n=1}^{n_{0}}NRn$.
 
-For regret occurred after the first $n_0$ round, it has two different components: the regret occurred when we let the agents play myopically and the regret occured when we incentivize the agents.
-For the regret occurred when we let the agents play myopically at time t, it consists of the following two components:
+For regret incurred after the first $n_0$ round, it has two different components: the regret incurred when we let the agents play myopically and the regret incurred when we incentivize the agents.
+For the regret incurred when we let the agents play myopically at time t, it consists of the following two components:
 \begin{itemize}
 \item For those user whose utility difference between their best and the second best arm is greater than $f(t)$: suppose it is at the $n(t)^{th}$ round, the probability of these user making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n(t) f(t)^2}{32 m^2\sigma^2}\right)$ at time $t$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n(t) f(t)^2}{32 m^2\sigma^2}\right)\times R$.
-We denote the regret occured by these agents as $r_1(t)$.
+We denote the regret incurred by these agents as $r_1(t)$.
 \item For those user whose utility difference between their best and the second best arm is smaller than $f(t)$: this happens with probability $S(f(t))$ at each time and regret is bounded above by $S(f(t)) \times f(t)=Mf(t)^2$.
-We denote the regret occured by these agents as $r_2(t)$.
+We denote the regret incurred by these agents as $r_2(t)$.
 \end{itemize}
 
-Thus, the cumulative expected regret occured up to time $T$ when we let the agent play myopically is bounded above by:
+Thus, the cumulative expected regret incurred up to time $T$ when we let the agent play myopically is bounded above by:
 \begin{align}
@@
 
-The expected regret occurred when we incentivize the agents is calculated in Theorem~\ref{rst:budget}. Thus the cumulative regret at time $T$ is bounded above by
+The expected regret incurred when we incentivize the agents is calculated in Theorem~\ref{rst:budget}. Thus the cumulative regret at time $T$ is bounded above by
 \begin{align}

### 2017-11-27 paper.tex
edit lemma 1

--- 2017-11-27 paper.tex
@@
 \begin{lemma}
-For those user whose utility difference between their best arm and the second best arm is at least $2m\lambda$, the probability that myopic action can incur regret at any time $t\in [t_{n-1},t_{n}-1]$ in the $n^{th}$ round is bounded above by $24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
+$P(A_t\neq B(\theta_t)|t\in [t_n, t_{n+1}-1],\theta_t\cdot(u_{B(\theta_t)}-u_{\hat{B}(\theta_t)})\geq 2m\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
 \label{round:prob}

### 2017-11-27 paper.tex

--- 2017-11-27 paper.tex
@@
 \begin{lemma}
-For those users whose utility difference between their best arm and the second best arm is at least $2m\lambda$, the probability that a myopic action can incur regret at any time $t\in [t_{n-1},t_{n}-1]$ in the $n^{th}$ round is bounded above by $24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
+$P(A_t\neq B(\theta_t)|t\in [t_n, t_{n+1}-1],\theta_t\cdot(u_{B(\theta_t)}-u_{\hat{B}(\theta_t)})\geq 2m\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
 \label{round:prob}

### 2017-11-27 paper.tex
did some edtis on lemma 2-4

@@
 \begin{lemma}
-$P(A_t\neq B(\theta_t)|t\in [t_n, t_{n+1}-1],\theta_t\cdot(u_{B(\theta_t)}-u_{\hat{B}(\theta_t)})\geq 2m\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
+Define $\tau$ to be any random variable that is almost surely between $t_n$ and $t_{n+1}-1$, then for all the agents whose utility difference between their best and second best arm is at least $2m\lambda$, we have $P(A_{\tau}\neq B(\theta_{\tau}))\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
 \label{round:prob}
@@
 \begin{proof}[Proof of Lemma~\ref{round:prob}]
-In the $n^{th}$ round, we know all arms have been pulled at least $n$ times. Thus, the probability that a myopic action can incur regret is bounded by
+In the $n^{th}$ round, we know all arms have been pulled at least $n$ times.
+Thus, for all the agents whose utility difference between their best and second best arm is greater than $2m\lambda$, we have
 \begin{align}
-&P(\text{myopic action incurs regret})\nonumber \\
-\leq &P(\exists i, \exists j, |u_{i,t}^{j}-u_{i}^{j}|>\lambda) \nonumber \\
-\leq & \sum_{i}\sum_{j} P(|u_{i,t}^{j}-u_{i}^{j}|>\lambda) \nonumber \\
-= &  \sum_{i}\sum_{j} P\left(\bigg|\sum_{k\in \tau_{i,t}}\epsilon_{k}\bigg|>N(i,t)\lambda\right). \label{ACI}
+&P(A_{\tau}\neq B(\theta_{\tau}))\nonumber \\
+\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|>\lambda) \nonumber \\
+\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|>\lambda) \nonumber \\
+= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda). \label{ACI}
 \end{align}
@@
 \begin{align}
-S_{N(i,t)}=\sum_{k\in\tau_{i,t}}\frac{\epsilon_{k}}{\sqrt{2}\sigma}=\frac{1}{\sqrt{2}\sigma}\sum_{k\in\tau_{i,t}}\epsilon_{k}. \nonumber
+S_{N(i,\tau)}^{i,j}=\frac{\epsilon_{i,\tau}^{j}}{\sqrt{2}\sigma}. \nonumber
 \end{align}
@@
 
-Thus, if we set $b=\frac{n\lambda^2}{8\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,t)\geq n\geq n_{0}$, we have
+Thus, if we set $b=\frac{n\lambda^2}{8\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,\tau)\geq n\geq n_{0}$, we have
 \begin{align}
-\frac{N(i,t)\lambda}{\sqrt{2}\sigma}\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)}+\frac{\lambda}{2\sqrt{2}\sigma}\sqrt{n N(i,t)} \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+bN(i,t)}, \nonumber 
+\frac{N(i,\tau)\lambda}{\sqrt{2}\sigma}\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)}+\frac{\lambda}{2\sqrt{2}\sigma}\sqrt{n N(i,\tau)} \nonumber \\
+\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)+bN(i,\tau)}, \nonumber 
 \end{align}
@@
 \begin{align}
-&P\left(\bigg|\sum_{k\in \tau_{i,t}}\epsilon_{k}\bigg|>N(i,t)\lambda\right) \nonumber \\
-=&2P\left(S_{N(i,t)}>\frac{N(i,t)\lambda}{\sqrt{2}\sigma}\right) \nonumber \\
-\leq & 2P\left(S_{N(i,t)}> \sqrt{0.6 N_{i,t}\log(\log_{1.1}(N(i,t))+1)+b N(i,t)}\right) \nonumber \\
+&P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda) \nonumber \\
+=&2P\left(S_{N(i,\tau)}^{i,j}>\frac{N(i,\tau)\lambda}{\sqrt{2}\sigma}\right) \nonumber \\
+\leq & 2P\left(S_{N(i,\tau)}^{i,j}> \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\right) \nonumber \\
 \leq & 24\exp( -1.8b) \nonumber \\
@@
 \begin{align}
-&\sum_{i}\sum_{j} P\left(\bigg|\sum_{k\in \tau_{i,t}}\epsilon_{k}\bigg|>N(i,t)\lambda\right)  \nonumber \\
-=& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber
+&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda)  \nonumber \\
+\leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber
 \end{align}
@@
 \begin{proof}
-Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$. Denote $\epsilon_{i,t}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,t}$. Define
+Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$.
+Denote $\epsilon_{i,t}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,t}$.
+Denote $\omega$ to be a sample path and $n(t,\omega)$ to be the round number for sample path $\omega$ at time $t$.
+Define
 \begin{align}
-W^{'}[l] = \{\omega_t:|\epsilon_{i,t}^{j}(\omega)|\leq g(n,l), \forall i,j\}\nonumber
+W^{'}[l] = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n(t,\omega),l), \forall i,j\}\nonumber
 \end{align}

### 2017-11-27 paper.tex
Edits to lemma 5

@@
 \begin{proof}
-In each round, each arm needs to be pulled at least once.
-Denote $X_{i}$ to be the number of agents come to the system between $i-1$ different arms were pulled and the $i^{th}$ different arm was pulled.
+	A round completes when each arm is pulled at least once in that round.
+Let $X_{i}$ be the number of agents who come to the system between the time after the $i-1^{th}$ unique arm was pulled, up to and including the time when the $i^{th}$ unique arm was pulled.
 Then we know
-\begin{align}
-\mathbb{E}[t_{n}-t_{n-1}]=\sum_{i=1}^{N}E[X_{i}]. \nonumber
-\end{align}
+\begin{equation*}
+\mathbb{E}[t_{n}-t_{n-1}]=\sum_{i=1}^{N}E[X_{i}].
+\end{equation*}
 
-Denote $t^{0}=t_{n-1}+\sum_{j=1}^{i-1}X_{j}$, then $X_{i}$ follows a ``geometric distribution'', which counts the total number of trials before the $i^{th}$ different arm were pulled at time $t=t^{0},t^{0}+1,\cdots$.
-At each time $t=t^{0}, t^{0}+1,\cdots$, there are two possibilities for a success trial:
+Fix $i$.
+% and let $t^{0}=t_{n-1}+\sum_{j=1}^{i-1}X_{j}$.
+$X_{i}$ is a random variable that counts the number of trials before the $i^{th}$ unique arm is pulled, with trials occuring at times $t=t^{0},t^{0}+1,\cdots$.
+In bounding $X_i$, we think of agents as ``trials'', where each trial can result in a new unique arm being pulled (which we call a ``successful'' trial), or not.
+There are two ways a trial can be successful:
 \begin{itemize}
-\item If there exists an arm has not been pulled and the proportion of agents who would pull this arm is less than $n^{-1}$, then based on our algorithm, the principal will offer an payment for that arm and it will be pulled.
-In this case, the probability that the $i^{th}$ different arm will be pulled is 1.
-\item There exists at least $n^{-1}$ proportion of agents who will choose an un-pulled arm as his/her myopic action.
-In this case, the probability that the $i^{th}$ different arm will be pulled is at least $n^{-1}$.
+\item If there is at least one arm that has not been pulled and the probability of an agent utility function that would pull this arm without incentives is less than $n^{-1}$, then the principal will offer an incentive that causes this arm to be pulled (or one of these arms if there is more than one).
+In this case, the probability that the trial is succesful is $1$.
+\item The probability of an agent utility function that would pull each un-pulled arm without incentives is at least $n^{-1}$.
+In this case, the probability that the trial is successful is at least $n^{-1}$.
 \end{itemize}
 
-Since $X_{i}$ follows a ``geometric distribution'' with success probability at least $n^{-1}$ at each time, we know 
+Thus, $X_{i}$ is stochastically dominated below by a geometric random variable with success probability $n^{-1}$, the expected number of trials up to and including the first success, $E[X_i]$, is bounded above by $n$.
+Thus,
 \begin{align}
@@
 
-Based on the definition of $W[l]$, we know if $\omega_t\in W[l]$, the maximum payment we need to offer at time $t$ is bounded above by $R+2Wmg(n,l)$. Thus,
+Based on the definition of $W[l]$, we know if $\omega_t\in W[l]$, the maximum payment we need to offer at time $t$ is bounded above by $R+2Wmg(n,l)$.
+\pfcomment{Do we need the $W$ here?
+Can we drop it?} Thus,
 
@@
 \end{align}
+\pfcomment{Above, should $w$ be $W$?}
 

### 2017-11-27 paper.tex
did some edtis on lemma 2-4

@@
 \begin{lemma}
-Define $\tau$ to be any random variable that is almost surely between $t_n$ and $t_{n+1}-1$, then for all the agents whose utility difference between their best and second best arm is at least $2m\lambda$, we have $P(A_{\tau}\neq B(\theta_{\tau}))\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
+Define $\tau$ to be any random variable that is almost surely between $t_n$ and $t_{n+1}-1$, we have 
+\begin{align}
+P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right), \nonumber
+\end{align}
+for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
 \label{round:prob}
 \end{lemma}
+
+Denote $n(\tau)$ to be the round number of $\tau$, then we can restate the above lemma as
+\begin{align}
+P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n(\tau)\lambda^2}{8\sigma^2}\right), \nonumber
+\end{align}
+for $n(\tau)\geq n_{0}$. For simplicity, we use $n=n(\tau)$.
 
@@
 In the $n^{th}$ round, we know all arms have been pulled at least $n$ times.
-Thus, for all the agents whose utility difference between their best and second best arm is greater than $2m\lambda$, we have
+For all the agents $\theta$ whose utility difference between their best and second best arm is greater than $2mW\lambda$, denote $K(\theta)=\max_{i\neq B(\theta)}\{\theta\cdot u_{i,t}\}$.
+If $|u_{i,t}^{j}-u_{i}^{j}|\leq \lambda$ for all $i,j$, then
 \begin{align}
-&P(A_{\tau}\neq B(\theta_{\tau}))\nonumber \\
-\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|>\lambda) \nonumber \\
-\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|>\lambda) \nonumber \\
-= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda). \label{ACI}
+&\theta\cdot(u_{B(\theta),t}-u_{K(\theta),t}) \nonumber \\
+\geq & \theta\cdot(u_{B(\theta),t}-u_{B(\theta)}) + \theta\cdot(u_{K(\theta)}-u_{K(\theta),t}) + \theta\cdot(u_{B(\theta)}-u_{K(\theta)}) \nonumber \\
+\geq & -Wm\lambda - Wm\lambda + 2Wm\lambda = 0,\nonumber
+\end{align}
+which means their myopic action would occur no regret.
+
+Thus, we have
+\begin{align}
+&P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda)\nonumber \\
+\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|>\lambda)|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda \nonumber \\
+\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|>\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda) \nonumber \\
+= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda). \label{ACI}
 \end{align}
@@
 \begin{align}
-&P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda) \nonumber \\
-=&2P\left(S_{N(i,\tau)}^{i,j}>\frac{N(i,\tau)\lambda}{\sqrt{2}\sigma}\right) \nonumber \\
-\leq & 2P\left(S_{N(i,\tau)}^{i,j}> \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\right) \nonumber \\
+&P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda) \nonumber \\
+=&2P\left(S_{N(i,\tau)}^{i,j}>\frac{N(i,\tau)\lambda}{\sqrt{2}\sigma}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda) \nonumber \\
+\leq & 2P\left(S_{N(i,\tau)}^{i,j}> \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda) \nonumber \\
 \leq & 24\exp( -1.8b) \nonumber \\
@@
 \begin{align}
-&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda)  \nonumber \\
+&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda)  \nonumber \\
 \leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber

### 2017-11-27 paper.tex
rephrased lemma 2 and lemma 4

@@
 \begin{lemma}
-Define $\tau$ to be any random variable that is almost surely between $t_n$ and $t_{n+1}-1$, we have 
+Define $\tau$ to be any stopping time that is almost surely between $t_n$ and $t_{n+1}-1$ with respect to the filteration $\mathcal{F}_{t}=\sigma(A_1,\cdots,A_t,c_1,\cdots,c_t,O_1,\cdots,O_t)$, we have
 \begin{align}
@@
 \begin{lemma}[Corollary 1 in \cite{zhao2016adaptive}]
-Let $X_{i}$ be zero mean $1/2$-subgaussian random variables. $\{S_{n}=\sum_{i=1}^{n}X_{i},n\geq 1\}$ be a random walk. Let $J$ be any random variable taking values in $\mathbb{N}$. If
+Let $X_{i}$ be zero mean $1/2$-subgaussian random variables.
+$\{S_{n}=\sum_{i=1}^{n}X_{i},n\geq 1\}$ be a random walk.
+Let $J$ be any stopping time with respect to $\{X_1,X_2,\cdots\}$.
+We let $J$ take a special value $\infty$ where $P(J=\infty)=1-\lim_{n\rightarrow \infty}P(J\leq n)$.
+If
 \begin{align}
@@
 \begin{align}
-Pr[S_{J}\geq f(J)]\leq 12e^{-1.8b}. \nonumber
+Pr[\{S_{J}\geq f(J)\}\cap \{J<\infty\}]\leq 12e^{-1.8b}. \nonumber
 \end{align}

### 2017-11-28 paper.tex
minor edit
a few typo corrections and comments on the proof of lemma 2

@@
 \begin{lemma}
-Define $\tau$ to be any stopping time that is almost surely between $t_n$ and $t_{n+1}-1$ with respect to the filteration $\mathcal{F}_{t}=\sigma(A_1,\cdots,A_t,c_1,\cdots,c_t,O_1,\cdots,O_t)$, we have
+Define $\tau$ to be any stopping time that is almost surely between $t_n$ and $t_{n+1}-1$ with respect to the filtration $\mathcal{F}_{t}=\sigma(A_1,\cdots,A_t,c_1,\cdots,c_t,O_1,\cdots,O_t)$, we have
 \begin{align}
@@
 
-Denote $n(\tau)$ to be the round number of $\tau$, then we can restate the above lemma as
-\begin{align}
-P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n(\tau)\lambda^2}{8\sigma^2}\right), \nonumber
-\end{align}
-for $n(\tau)\geq n_{0}$. For simplicity, we use $n=n(\tau)$.
+% We don't need this
+% Denote $n(\tau)$ to be the round number of $\tau$, then we can restate the above lemma as
+%\begin{align}
+%P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n(\tau)\lambda^2}{8\sigma^2}\right), \nonumber
+%\end{align}
+%for $n(\tau)\geq n_{0}$. For simplicity, we use $n=n(\tau)$.
 
@@
 Let $J$ be any stopping time with respect to $\{X_1,X_2,\cdots\}$.
-We let $J$ take a special value $\infty$ where $P(J=\infty)=1-\lim_{n\rightarrow \infty}P(J\leq n)$.
+We allow $J$ to take the value of $\infty$ where $P(J=\infty)=1-\lim_{n\rightarrow \infty}P(J\leq n)$.
 If
@@
 \end{align}
-which means their myopic action would occur no regret.
+which means their myopic action would incur no regret.
+\pfcomment{If all of these are equality, can the agent choose a regret-incurring option?  Do we need strict inequalities?}
 
@@
 &P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda)\nonumber \\
-\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|>\lambda)|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda \nonumber \\
+\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|>\lambda |\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda) \nonumber \\
 \leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|>\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda) \nonumber \\
-= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda). \label{ACI}
+= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,\tau)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda). \label{ACI}
 \end{align}
 
-To bound equation~(\ref{ACI}), we need to use Lemma~\ref{ACI-inequality}. Similar to Lemma~\ref{ACI-inequality}, we define
+\pfcomment{where is $\epsilon^j_{i,\tau}$ defined?  has it been defined yet?}
+
+To bound equation~(\ref{ACI}), we use Lemma~\ref{ACI-inequality}. Similar to Lemma~\ref{ACI-inequality}, we define
 \begin{align}
@@
 
-Based on Lemma~\ref{n0-inequality}, we know there exists a $n_{0}=\max\{50, \frac{23.04\sigma^2}{\lambda^2}\}$ such that for $n\geq n_{0}$, we have
+Based on Lemma~\ref{n0-inequality}, for $n_{0}=\max\{50, \frac{23.04\sigma^2}{\lambda^2}\}$ and $n\geq n_{0}$, we have
 \begin{align}

### 2017-11-28 paper.tex
addressed comments on Peter's comments

@@
 \begin{align}
-P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right), \nonumber
+P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right), \nonumber
 \end{align}
@@
 \end{lemma}
-
-% We don't need this
-% Denote $n(\tau)$ to be the round number of $\tau$, then we can restate the above lemma as
-%\begin{align}
-%P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n(\tau)\lambda^2}{8\sigma^2}\right), \nonumber
-%\end{align}
-%for $n(\tau)\geq n_{0}$. For simplicity, we use $n=n(\tau)$.
 
@@
 \geq & \theta\cdot(u_{B(\theta),t}-u_{B(\theta)}) + \theta\cdot(u_{K(\theta)}-u_{K(\theta),t}) + \theta\cdot(u_{B(\theta)}-u_{K(\theta)}) \nonumber \\
-\geq & -Wm\lambda - Wm\lambda + 2Wm\lambda = 0,\nonumber
+> & -Wm\lambda - Wm\lambda + 2Wm\lambda = 0,\nonumber
 \end{align}
 which means their myopic action would incur no regret.
-\pfcomment{If all of these are equality, can the agent choose a regret-incurring option?  Do we need strict inequalities?}
 
-Thus, we have
+Define $\epsilon_{i,\tau}=u_{i,\tau}-u_i$ and $\epsilon_{i,\tau}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,\tau}$. Thus, we have
 \begin{align}
-&P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda)\nonumber \\
-\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|>\lambda |\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda) \nonumber \\
-\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|>\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda) \nonumber \\
-= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,\tau)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda). \label{ACI}
+&P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\nonumber \\
+\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|>\lambda |\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
+\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|>\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
+= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,\tau)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda). \label{ACI}
 \end{align}
-
-\pfcomment{where is $\epsilon^j_{i,\tau}$ defined?  has it been defined yet?}
 
@@
 \begin{align}
-&P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda) \nonumber \\
-=&2P\left(S_{N(i,\tau)}^{i,j}>\frac{N(i,\tau)\lambda}{\sqrt{2}\sigma}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda) \nonumber \\
-\leq & 2P\left(S_{N(i,\tau)}^{i,j}> \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda) \nonumber \\
-\leq & 24\exp( -1.8b) \nonumber \\
-= & 24\exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber
+&P(\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
+=&P\left(S_{N(i,\tau)}^{i,j}>\frac{N(i,\tau)\lambda}{\sqrt{2}\sigma}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
+\leq & P\left(S_{N(i,\tau)}^{i,j}> \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
+\leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber
+\end{align}
+Similarily, we can bound 
+\begin{align}
+&P(\epsilon_{i,\tau}^{j}<-N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
+=&P(-\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
+\leq & 12\exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber 
 \end{align}
 
+Therefore, we know $P(\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right)$.
 Thus, we know
 \begin{align}
-&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})\geq 2Wm\lambda)  \nonumber \\
+&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)  \nonumber \\
 \leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber
@@
 Fix $i$.
-% and let $t^{0}=t_{n-1}+\sum_{j=1}^{i-1}X_{j}$.
-$X_{i}$ is a random variable that counts the number of trials before the $i^{th}$ unique arm is pulled, with trials occuring at times $t=t^{0},t^{0}+1,\cdots$.
 In bounding $X_i$, we think of agents as ``trials'', where each trial can result in a new unique arm being pulled (which we call a ``successful'' trial), or not.
@@
 
-Based on the definition of $W[l]$, we know if $\omega_t\in W[l]$, the maximum payment we need to offer at time $t$ is bounded above by $R+2Wmg(n,l)$.
-\pfcomment{Do we need the $W$ here?
-Can we drop it?} Thus,
+Based on the definition of $W[l]$, we know if $\omega_t\in W[l]$, the maximum payment we need to offer at time $t$ is bounded above by 
+\begin{align}
+&\max_{i}\theta_t\cdot u_{i,t} - \min_{j}\theta_t\cdot u_{j,t} \nonumber \\
+= &\max_{i}\theta_t\cdot (\epsilon_{i,t}+u_i) - \min_{j}\theta_t\cdot (\epsilon_{j,t}+u_j) \nonumber \\
+\leq &\max_{i}\theta_t\cdot u_i - \min_{j}\theta_t\cdot u_j +\max_{i}\theta_t\cdot \epsilon_{i,t} - \min_{j}\theta_t\cdot \epsilon_{j,t}\nonumber \\
+\leq & R + 2Wmg(n,l). \nonumber
+\end{align}
+
+Thus,
 

### 2017-11-28 paper.tex
changed the notations in theorem 1

@@
 Denote $\omega$ to be a sample path and $n(t,\omega)$ to be the round number for sample path $\omega$ at time $t$.
-Define
+For a fixed time $t$, define
 \begin{align}
-W^{'}[l] = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n(t,\omega),l), \forall i,j\}\nonumber
+W^{'}[l](t) = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n(t,\omega),l), \forall i,j\}\nonumber
 \end{align}
-where $g(n,l)$ is a function which we will define later. Define $W[1] = W^{'}[1]$ and $W[i] = W^{'}[i]\setminus W^{'}[i-1]$ for $i\geq 2$. We call $W[l]$ the $l^{th}$ envelope.
+where $g(n,l)$ is a function which we will define later.
+Define $W[1](t) = W^{'}[1](t)$ and $W[i](t) = W^{'}[i](t)\setminus W^{'}[i-1](t)$ for $i\geq 2$.
+We call $W[l](t)$ the $l^{th}$ envelope at time $t$.
+We often simplify the notation and use $W[l]$ instead of $W[l](t)$ without confusion.
 
-Based on the definition of $W[l]$, we know if $\omega_t\in W[l]$, the maximum payment we need to offer at time $t$ is bounded above by 
+Based on the definition of $W[l]$, we know if $\omega\in W[l]$, the maximum payment we need to offer at time $t$ is bounded above by 
 \begin{align}
@@
 &\sum_{t=1}^{\infty}c(t) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}c(t)\mathbbm{1}\{\omega_{t}\in w[l]\} \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}c(t)\mathbbm{1}\{\omega_{t}\in w[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
+=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}c(t)\mathbbm{1}\{\omega\in w[l]\} \nonumber \\
+=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}c(t)\mathbbm{1}\{\omega\in w[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
 \end{align}
@@
 \begin{align}
-\sum_{t=1}^{\infty}c(t)=\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}c(t)\mathbbm{1}\{\omega_{t}\in w[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
+\sum_{t=1}^{\infty}c(t)=\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}c(t)\mathbbm{1}\{\omega\in w[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
 \end{align}
@@
 &E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}E[c(t)|\omega_t\in w[l],t\in [t_n,t_{n+1}))P(\omega_t\in w[l],t\in [t_n,t_{n+1})) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[r+2Wm\frac{l}{n}\right]P(\omega_t\in w[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[r+2Wm\frac{l}{n}\right]P(\omega_t\in w[l]|t\in [t_n,t_{n+1}))Nn. \nonumber
+=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}E[c(t)|\omega \in w[l],t\in [t_n,t_{n+1}))P(\omega\in w[l],t\in [t_n,t_{n+1})) \nonumber \\
+=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[r+2Wm\frac{l}{n}\right]P(\omega\in w[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
+=&\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[r+2Wm\frac{l}{n}\right]P(\omega\in w[l]|t\in [t_n,t_{n+1}))Nn. \nonumber
 \end{align}

### 2017-11-28 paper.tex
fixed a typo
minor edits to clarify

@@
 Formally, $S(\delta)=P(\theta: \theta \cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}\leq \delta)$.
-Then, let $p(\delta)=\min_{i}P(\{\theta:\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$.
+Then, let $p(\delta)=\min_{i}P(\{\theta:B(\theta)=i,\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$.
 We know $p(0)=p$.
@@
 Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2m\lambda\}$, they will correctly identify their best arm.
-Thus in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{l}{n} \leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, then for each arm, at least $\frac{p}{2}$ agents would pull that arm.
-Further, if our time-varying threshold $n^{-1}\leq p/2$, we do not need to incentivize any arms.
+Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{l}{n} \leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
+Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms.
 Denote $a_0=\frac{2m}{p^{-1}(\frac{p}{2})}$.

### 2017-11-28 paper.tex
minor edit

@@
 Denote $a_0=\frac{2m}{p^{-1}(\frac{p}{2})}$.
-In order to have $\frac{l}{n}\leq \frac{p^{-1}(\frac{p}{2})}{2m}$, we need $n\geq \lceil a_{0} l\rceil$.
-In order to hvae $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
+In order to have $\frac{l}{n}\leq \frac{p^{-1}(\frac{p}{2})}{2m}$, it is sufficient to have $n\geq \lceil a_{0} l\rceil$.
+In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
 Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$.
-Thus, we know we can only incur regret in the $l^{th}$ envelope in the first $\max\{n_1,\lceil a_0 l\rceil\}$ rounds.
+Thus, we know we can only incur regret for sample paths $\omega$ in the $l^{th}$ envelope in the first $\max\{n_1,\lceil a_0 l\rceil\}$ rounds.
 

### 2017-11-28 paper.tex
fixed some typos and changed envelope notations

@@
 \begin{align}
-W^{'}[l](t) = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n(t,\omega),l), \forall i,j\}\nonumber
+L^{'}[l](t) = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n(t,\omega),l), \forall i,j\}\nonumber
 \end{align}
 where $g(n,l)$ is a function which we will define later.
-Define $W[1](t) = W^{'}[1](t)$ and $W[i](t) = W^{'}[i](t)\setminus W^{'}[i-1](t)$ for $i\geq 2$.
-We call $W[l](t)$ the $l^{th}$ envelope at time $t$.
-We often simplify the notation and use $W[l]$ instead of $W[l](t)$ without confusion.
+Define $L[1](t) = L^{'}[1](t)$ and $L[i](t) = L^{'}[i](t)\setminus L^{'}[i-1](t)$ for $i\geq 2$.
+We call $L[l](t)$ the $l^{th}$ envelope at time $t$.
+We often simplify the notation and use $L[l]$ instead of $L[l](t)$ without confusion.
 
-Based on the definition of $W[l]$, we know if $\omega\in W[l]$, the maximum payment we need to offer at time $t$ is bounded above by 
+In the calculation below, we omit the dependency on $\omega$ when refering to variables $c(t)$ and $t_n$.
+Based on the definition of $L[l]$, we know if $\omega\in L[l]$, the maximum payment we need to offer at time $t$ is bounded above by
 \begin{align}
@@
 &\sum_{t=1}^{\infty}c(t) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}c(t)\mathbbm{1}\{\omega\in w[l]\} \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}c(t)\mathbbm{1}\{\omega\in w[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
+=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\} \nonumber \\
+=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
 \end{align}
-\pfcomment{Above, should $w$ be $W$?}
 
 Set $g(n,l)$ to be $\frac{l}{n}$.
-Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2m\lambda\}$, they will correctly identify their best arm.
-Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{l}{n} \leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
+Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2Wm\lambda\}$, they will correctly identify their best arm.
+Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{l}{n} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
 Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms.
-Denote $a_0=\frac{2m}{p^{-1}(\frac{p}{2})}$.
-In order to have $\frac{l}{n}\leq \frac{p^{-1}(\frac{p}{2})}{2m}$, it is sufficient to have $n\geq \lceil a_{0} l\rceil$.
+Denote $a_0=\frac{2Wm}{p^{-1}(\frac{p}{2})}$.
+In order to have $\frac{l}{n}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil a_{0} l\rceil$.
 In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
-Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$.
-Thus, we know we can only incur regret for sample paths $\omega$ in the $l^{th}$ envelope in the first $\max\{n_1,\lceil a_0 l\rceil\}$ rounds.
+Denote $n_2=\frac{2}{p}$.
+Thus, we know we can only incur regret for sample paths $\omega$ in the $l^{th}$ envelope in the first $\max\{n_2,\lceil a_0 l\rceil\}$ rounds.
 
@@
 \begin{align}
-\sum_{t=1}^{\infty}c(t)=\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}c(t)\mathbbm{1}\{\omega\in w[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
+\sum_{t=1}^{\infty}c(t)=\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
 \end{align}
@@
 &E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}E[c(t)|\omega \in w[l],t\in [t_n,t_{n+1}))P(\omega\in w[l],t\in [t_n,t_{n+1})) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[r+2Wm\frac{l}{n}\right]P(\omega\in w[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[r+2Wm\frac{l}{n}\right]P(\omega\in w[l]|t\in [t_n,t_{n+1}))Nn. \nonumber
+=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}E[c(t)|\omega \in L[l],t\in [t_n,t_{n+1}))P(\omega\in L[l],t\in [t_n,t_{n+1})) \nonumber \\
+=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}\left[R+2Wm\frac{l}{n}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
+=&\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}\left[R+2Wm\frac{l}{n}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))Nn. \nonumber
 \end{align}
 
-We now bound $P(\omega\in W[l]|t\in[t_{n},t_{n+1}))$. \bccomment{Is my calculation to bound this probability correct?}
+We now bound $P(\omega\in L[l]|t\in[t_{n},t_{n+1}))$. \bccomment{Is my calculation to bound this probability correct?}
 \begin{align}
-&P(\omega\in W[l]|t\in[t_{n},t_{n+1})) \nonumber \\
-=&P(\omega\in W^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in W^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
+&P(\omega\in L[l]|t\in[t_{n},t_{n+1})) \nonumber \\
+=&P(\omega\in L^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in L^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
 =&P(|\epsilon_{i,t}^{j}|<\frac{l}{n}, \forall i,j|t\in[t_n,t_{n+1}))-P(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}, \forall i,j|t\in[t_n,t_{n+1})) \nonumber \\
@@
 &E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
-\leq & \sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[R+2Wm\frac{l}{n}\right]\times 2 \frac{1}{\sqrt{2\pi}}exp\left(-\frac{(l-1)^2}{2n}\right)\times (\sqrt{n})^{-1}Nn.
+\leq & \sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}\left[R+2Wm\frac{l}{n}\right]\times 2 \frac{1}{\sqrt{2\pi}}exp\left(-\frac{(l-1)^2}{2n}\right)\times (\sqrt{n})^{-1}Nn.
 \nonumber \\
-\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[R+2Wml\right]exp\left(-\frac{(l-1)^2}{2n}\right)\sqrt{n}. \nonumber
+\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}\left[R+2Wml\right]exp\left(-\frac{(l-1)^2}{2n}\right)\sqrt{n}. \nonumber
 \end{align}
 
-Denote $k_n=\max\{n_1, \lceil a_0 l \rceil\}$. Then we know
+Denote $k_n=\max\{n_2, \lceil a_0 l \rceil\}$. Then we know
 \begin{align}
 &E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
-\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[R+2Wml\right]exp\left(-\frac{(l-1)^2}{2k_n}\right)\sqrt{k_n} \nonumber \\
-\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\left[R+2Wml\right]exp\left(-\frac{(l-1)^2}{2k_n}\right)(k_n)^{3/2}=O(N). \nonumber
+\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[R+2Wml\right]\exp\left(-\frac{(l-1)^2}{2k_n}\right)\sqrt{k_n} \nonumber \\
+\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\left[R+2Wml\right]\exp\left(-\frac{(l-1)^2}{2k_n}\right)(k_n)^{3/2}=O(N). \nonumber
 \end{align}

### 2017-11-28 paper.tex
fixed our assumption 1

@@
 
-\begin{assumption} Let $f_{i,j}(y)$ be the marginal probability density function (or marginal probability mass function if $F(\cdot)$ is a discrete distribution) of $(u_i-u_j)\cdot\theta$ conditioned on $\theta \in \Omega_{i,j}$.
-We assume $\max_{i,j}\sup_{y}f_{i,j}(y)\leq M$.
+\begin{assumption} Let $F_{i,j}(y)$ be the marginal cumulative density function (or cumulative mass function if $F(\cdot)$ is a discrete distribution) of $(u_i-u_j)\cdot\theta$ conditioned on $\theta \in \Omega_{i,j}$.
+We assume $F_{i,j}(y)\leq My$ for all $y\in R^{+}$, $\forall i,j$.
 \label{A1}
@@
 
-As we can see later in our proof, we only need $\max_{i,j}\limsup_{y\rightarrow 0^{+}}f_{i,j}(y)$ to be finite.
+As we can see later in our proof, we only need $\max_{i,j}\limsup_{y\rightarrow 0^{+}}\frac{F_{i,j}(y)}{y}$ to be finite.
 Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm.
@@
 \begin{corollary}
-If $\exists \delta>0$ such that $f_{i,j}(y)=0$ for all $i,j$ and $y\in [0,\delta]$, then the cumulative expected regret is bounded by $O(N^2)$.
+If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O(N^2)$.
 \end{corollary}

### 2017-11-28 paper.tex
fixed our assumption 1

@@
 
-In the calculation below, we omit the dependency on $\omega$ when refering to variables $c(t)$ and $t_n$.
+In the calculation below, we omit the dependency on $\omega$ when refering to variables $c(t)$, $\epsilon_{i,t}^{j}$ and $t_n$.
 Based on the definition of $L[l]$, we know if $\omega\in L[l]$, the maximum payment we need to offer at time $t$ is bounded above by
@@
 =&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}E[c(t)|\omega \in L[l],t\in [t_n,t_{n+1}))P(\omega\in L[l],t\in [t_n,t_{n+1})) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}\left[R+2Wm\frac{l}{n}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}\left[R+2Wm\frac{l}{n}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))Nn. \nonumber
+=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}\left[R+2Wm\frac{l}{n}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})). \nonumber
 \end{align}
 
-We now bound $P(\omega\in L[l]|t\in[t_{n},t_{n+1}))$. \bccomment{Is my calculation to bound this probability correct?}
+We now bound $P(\omega\in L[l]|t\in[t_{n},t_{n+1}))$.
 \begin{align}
@@
 =&P(\omega\in L^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in L^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
-=&P(|\epsilon_{i,t}^{j}|<\frac{l}{n}, \forall i,j|t\in[t_n,t_{n+1}))-P(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}, \forall i,j|t\in[t_n,t_{n+1})) \nonumber \\
-=&\Pi_{i=1}^{N}\Pi_{j=1}^{m}P\left(|\epsilon_{i,t}^{j}|<\frac{l}{n}|t\in[t_n,t_{n+1})\right)-\Pi_{i=1}^{N}\Pi_{j=1}^{m}P\left(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}|t\in[t_n,t_{n+1})\right).
-\label{prob:upper}
+\leq & 1-P(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}, \forall i,j|t\in[t_n,t_{n+1})) \nonumber \\
+=&P(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{l-1}{n}|t\in[t_n,t_{n+1})) \nonumber  \\
+=&\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{l-1}{n}|t\in[t_n,t_{n+1})) \nonumber \\
+=&\sum_{i,j}P(|S_{i,t}^{j}|\geq \frac{N(i,t)(l-1)}{n}|t\in[t_n,t_{n+1})) \nonumber 
 \end{align}
+
 Since we are at round $n$, we know there exists at least one arm, which has been pulled exactly $n$ times.

### 2017-11-29 paper.tex
fixed Lemma 6

@@
 
-Since we are at round $n$, we know there exists at least one arm, which has been pulled exactly $n$ times.
-Without loss of generality, we assume it to be arm $1$.
-Since $P\left(|\epsilon_{i,t}^{j}|<\frac{l}{n}|t\in[t_n,t_{n+1})\right)> P\left(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}|t\in[t_n,t_{n+1})\right)$ for all $i,j$, we know
-
-\begin{align}
-\eqref{prob:upper}&\leq P\left(|\epsilon_{1,t}^{1}|<\frac{l}{n}|t\in[t_n,t_{n+1})\right)-P\left(|\epsilon_{1,t}^{1}|<\frac{l-1}{n}|t\in[t_n,t_{n+1})\right) \nonumber \\
-=&P\left(\frac{l-1}{n}<|\epsilon_{1,t}^{1}|<\frac{l}{n}|t\in[t_n,t_{n+1})\right) \nonumber \\
-=&P\left(\frac{\sqrt{n}(l-1)}{n}<|N(0,1)|<\frac{\sqrt{n}l}{n}|t\in[t_n,t_{n+1})\right) \nonumber \\
-=&2\Phi\left(\frac{\sqrt{n}l}{n}\right)-2\Phi\left(\frac{\sqrt{n}(l-1)}{n}\right) \nonumber \\
-=&2 \frac{1}{\sqrt{2\pi}}exp\left(-\frac{(l-1)^2}{2n}\right)\times (\sqrt{n})^{-1}. \nonumber
-\end{align}
-
-Thus,
-\begin{align}
-&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
-\leq & \sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}\left[R+2Wm\frac{l}{n}\right]\times 2 \frac{1}{\sqrt{2\pi}}exp\left(-\frac{(l-1)^2}{2n}\right)\times (\sqrt{n})^{-1}Nn.
-\nonumber \\
-\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}\left[R+2Wml\right]exp\left(-\frac{(l-1)^2}{2n}\right)\sqrt{n}. \nonumber
-\end{align}
-
-Denote $k_n=\max\{n_2, \lceil a_0 l \rceil\}$. Then we know
-\begin{align}
-&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
-\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\sum_{n=1}^{\max\{n_1,\lceil a_0 l\rceil\}}\left[R+2Wml\right]\exp\left(-\frac{(l-1)^2}{2k_n}\right)\sqrt{k_n} \nonumber \\
-\leq & \frac{2N}{\sqrt{2\pi}}\sum_{l=1}^{\infty}\left[R+2Wml\right]\exp\left(-\frac{(l-1)^2}{2k_n}\right)(k_n)^{3/2}=O(N). \nonumber
-\end{align}
-
 \end{proof}
@@
 \begin{proof}
-If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2m\lambda\}$, they will correctly identify their best arm.
-Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2m}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms.
+If $|u_{i}^{j}-u_{i,t}^{j}|< \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2mW\lambda\}$, they will correctly identify their best arm.
+Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|< \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms.
 In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
@@
 Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).The cumulative expected number of payments is bounded above by:
+
+Define $\tau_{n}^{k}$ to be a stopping time which equals to the $k_{th}$ time period in the $n^{th}$ round. Then
+\begin{align}
+&\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\} \nonumber \\
+=&\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}\sum_{t=k}^{\infty}\mathbbm{1}\{c(t)>0\}\mathbbm{1}\{t=\tau_{n}^{k}\} \nonumber 
+\end{align}
+
+Thus, we know
 \begin{align}
 &E[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}] \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}P\left(\exists i,j:|u_{i}^{j}-u_{i,t}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2m}\right)+\sum_{n=1}^{n_1}N \nonumber \\
+\leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}\sum_{k=1}^{\infty}P\left(\exists i,j:|u_{i}^{j}-u_{i,\tau_{n}^{k}}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2Wm}\right)P(t=\tau_{n}^{k})+\sum_{n=1}^{n_1}N \nonumber \\
+\leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}\sum_{k=1}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{32m^2\sigma^2}\right)\times P(t=\tau_{n}^{k})+\sum_{n=1}^{n_1}N \nonumber \\
 \leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{32m^2\sigma^2}\right)\times Nn+\sum_{n=1}^{n_1}N \nonumber  \\

### 2017-11-29 paper.tex
fixed the proof of lemma 6
fixed an error related to 1/2 sub-gaussian

@@
 \begin{align}
-P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right), \nonumber
+P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{16\sigma^2}\right), \nonumber
 \end{align}
-for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
+for $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$.
 \label{round:prob}
@@
 \begin{lemma}
-For $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$, we have
+For $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$, we have
 \begin{align}
-\frac{n\lambda}{2\sqrt{2}\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
+\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
 \end{align}
@@
 \begin{align}
-&\frac{n\lambda}{2\sqrt{2}\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)} \nonumber \\
-\iff &\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{4.8\sigma^2}{\lambda^2}. \nonumber 
+&\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)} \nonumber \\
+\iff &\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{9.6\sigma^2}{\lambda^2}. \nonumber 
 \end{align}
@@
 \begin{align}
-\frac{n}{3+\log(n)}\geq \frac{4.8\sigma^2}{\lambda^2}. \label{n0-equ}
+\frac{n}{3+\log(n)}\geq \frac{9.6\sigma^2}{\lambda^2}. \label{n0-equ}
 \end{align}
@@
 \item for $n\geq 50$, we have $\frac{n}{3+\log(n)}\geq n^{0.5}$;
-\item for $n\geq \frac{23.04\sigma^4}{\lambda^4}$, we have $n^{0.5}\geq {4.8\sigma^{2}}{\lambda^{2}}$.
+\item for $n\geq \frac{92.16\sigma^4}{\lambda^4}$, we have $n^{0.5}\geq {9.6\sigma^{2}}{\lambda^{2}}$.
 \end{itemize}
@@
 \begin{align}
-S_{N(i,\tau)}^{i,j}=\frac{\epsilon_{i,\tau}^{j}}{\sqrt{2}\sigma}. \nonumber
+S_{N(i,\tau)}^{i,j}=\frac{\epsilon_{i,\tau}^{j}}{2\sigma}. \nonumber
 \end{align}
 
-Based on Lemma~\ref{n0-inequality}, for $n_{0}=\max\{50, \frac{23.04\sigma^2}{\lambda^2}\}$ and $n\geq n_{0}$, we have
+Based on Lemma~\ref{n0-inequality}, for $n_{0}=\max\{50, \frac{92.16\sigma^2}{\lambda^2}\}$ and $n\geq n_{0}$, we have
 \begin{align}
-\frac{n\lambda}{2\sqrt{2}\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
+\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
 \end{align}
 
-Thus, if we set $b=\frac{n\lambda^2}{8\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,\tau)\geq n\geq n_{0}$, we have
+Thus, if we set $b=\frac{n\lambda^2}{16\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,\tau)\geq n\geq n_{0}$, we have
 \begin{align}
-\frac{N(i,\tau)\lambda}{\sqrt{2}\sigma}\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)}+\frac{\lambda}{2\sqrt{2}\sigma}\sqrt{n N(i,\tau)} \nonumber \\
+\frac{N(i,\tau)\lambda}{2\sigma}\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)}+\frac{\lambda}{4\sigma}\sqrt{n N(i,\tau)} \nonumber \\
 \geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)+bN(i,\tau)}, \nonumber 
@@
 &P(\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P\left(S_{N(i,\tau)}^{i,j}>\frac{N(i,\tau)\lambda}{\sqrt{2}\sigma}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
+=&P\left(S_{N(i,\tau)}^{i,j}>\frac{N(i,\tau)\lambda}{2\sigma}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
 \leq & P\left(S_{N(i,\tau)}^{i,j}> \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber
+\leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
 \end{align}
@@
 =&P(-\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & 12\exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber 
+\leq & 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber 
 \end{align}
 
-Therefore, we know $P(\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right)$.
+Therefore, we know $P(\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right)$.
 Thus, we know
@@
 &\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)  \nonumber \\
-\leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{8\sigma^2}\right). \nonumber
+\leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
 \end{align}
@@
 
+We also need the following lemma in part of the proof of Theorem~\ref{rst:budget}.
+\begin{lemma}
+For all $n\geq 1$ and $l\geq 2$, we have
+\begin{align}
+0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}. \nonumber
+\end{align}
+\label{lemma:cal2}
+\end{lemma}
+\begin{proof}
+\begin{align}
+&0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)} \nonumber \\
+\iff & 0.81 n^{5/3} \geq 0.6n \log(\log_{1.1}(n)+1) \nonumber \\
+\Longleftarrow &  1.3 n^{2/3} \geq  \log(\log_{1.1}(n)+1) \nonumber
+\end{align}
+\end{proof}
+
 Now we are ready to prove our first main result, Theorem~\ref{rst:budget}.
@@
 
-Thus,
-
+We know
 \begin{align}
@@
 
-Set $g(n,l)$ to be $\frac{l}{n}$.
+Set $g(n,l)$ to be $\frac{2\sigma l}{n^{1/6}}$.
 Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2Wm\lambda\}$, they will correctly identify their best arm.
-Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{l}{n} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
+Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{2\sigma l}{n^{1/6}} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
 Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms.
-Denote $a_0=\frac{2Wm}{p^{-1}(\frac{p}{2})}$.
-In order to have $\frac{l}{n}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil a_{0} l\rceil$.
+Denote $a_0=\frac{4Wm\sigma}{p^{-1}(\frac{p}{2})}$.
+In order to have $\frac{2\sigma l}{n^{1/6}}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil (a_{0} l)^6 \rceil$.
 In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
 Denote $n_2=\frac{2}{p}$.
-Thus, we know we can only incur regret for sample paths $\omega$ in the $l^{th}$ envelope in the first $\max\{n_2,\lceil a_0 l\rceil\}$ rounds.
+Thus, we know we can only incur regret for sample paths $\omega$ in the $l^{th}$ envelope in the first $\max\{n_2,\lceil (a_0 l)^6 \rceil\}$ rounds.
 
@@
 \begin{align}
-\sum_{t=1}^{\infty}c(t)=\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
+\sum_{t=1}^{\infty}c(t)=\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
 \end{align}
@@
 &E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}E[c(t)|\omega \in L[l],t\in [t_n,t_{n+1}))P(\omega\in L[l],t\in [t_n,t_{n+1})) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil a_0 l\rceil\}}\left[R+2Wm\frac{l}{n}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})). \nonumber
+=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}E[c(t)|\omega \in L[l],t\in [t_n,t_{n+1}))P(\omega\in L[l],t\in [t_n,t_{n+1})) \nonumber \\
+=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+2Wm\frac{2\sigma l}{n^{1/6}}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
+=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})). \nonumber
 \end{align}
 
-We now bound $P(\omega\in L[l]|t\in[t_{n},t_{n+1}))$.
+We now bound $P(\omega\in L[l]|t\in[t_{n},t_{n+1}))$ for $n\geq n_0$ and $l\geq 2$.
 \begin{align}
@@
 =&P(\omega\in L^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in L^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
-\leq & 1-P(|\epsilon_{i,t}^{j}|<\frac{l-1}{n}, \forall i,j|t\in[t_n,t_{n+1})) \nonumber \\
-=&P(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{l-1}{n}|t\in[t_n,t_{n+1})) \nonumber  \\
-=&\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{l-1}{n}|t\in[t_n,t_{n+1})) \nonumber \\
-=&\sum_{i,j}P(|S_{i,t}^{j}|\geq \frac{N(i,t)(l-1)}{n}|t\in[t_n,t_{n+1})) \nonumber 
+\leq & 1-P(|\epsilon_{i,t}^{j}|<\frac{2\sigma (l-1)}{n^{1/6}}, \forall i,j|t\in[t_n,t_{n+1})) \nonumber \\
+=&P(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber  \\
+=&\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber
+\end{align}
+
+Define $S_{i,t}^{j}=\frac{N(i,t)\epsilon_{i,t}^{j}}{2\sigma}$, then we know $S_{i,t}^{j}$ is a summation of $1/2$ gaussian random numbers. Therefore,
+
+\begin{align}
+&\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{l-1}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber \\ 
+=&\sum_{i,j}P(|S_{i,t}^{j}|\geq \frac{N(i,t)(l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})). \nonumber \\
+\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})). \nonumber
+\end{align}
+
+Based on Lemma~\ref{lemma:cal2}, we know
+\begin{align}
+&N(i,t)^{5/6}(l-1) \nonumber \\
+=& 0.9N(i,t)^{5/6} + N(i,t)^{5/6}(l-1.9) \nonumber \\
+\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)} + \sqrt{(l-1.9)^2 N(i,t)} \nonumber \\
+\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+(l-1.9)^2 N(i,t)}. \nonumber
+\end{align}
+
+Based on Lemma~\ref{ACI-inequality}, we know
+\begin{align}
+&\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})) \nonumber \\
+\leq & \sum_{i,j}24e^{-1.8(l-1.9)^2} = 24Nme^{-1.8(l-1.9)^2}. \nonumber
+\end{align}
+
+Thus,
+\begin{align}
+&\sum_{t=1}^{\infty}c(t) \nonumber \\
+\leq&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+2Wm\frac{2\sigma l}{n^{1/6}}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
+\leq& \sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(\omega\in L[1]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
++&\sum_{l=2}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
+\leq& \sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(t\in [t_n,t_{n+1})) \nonumber \\
++&\sum_{l=2}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]24Nme^{-1.8(l-1.9)^2}P(t\in [t_n,t_{n+1})) \nonumber \\
+\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]Nn +\sum_{l=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]24Nme^{-1.8(l-1.9)^2}Nn \nonumber \\
+\leq & \left[R+4Wm\sigma \right]N (\max\{n_2,\lceil (a_0)^6 \rceil\})^2+\sum_{l=2}^{\infty}24N^2 m[R+4Wml\sigma](\max\{n_2,\lceil (a_0 l)^6 \rceil\})^2 e^{-1.8(l-1.9)^2} \nonumber \\
+=& O(N^2). \nonumber
 \end{align}
@@
 Under our algorithm, the expected number of payments is bounded above by $O(N^2)$.
+\label{lemma:numP}
 \end{lemma}
@@
 \begin{proof}
-If $|u_{i}^{j}-u_{i,t}^{j}|< \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}\geq 2mW\lambda\}$, they will correctly identify their best arm.
+If $|u_{i}^{j}-u_{i,t}^{j}|< \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2mW\lambda\}$, they will correctly identify their best arm.
 Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|< \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms.
@@
 
-Define $\tau_{n}^{k}$ to be a stopping time which equals to the $k_{th}$ time period in the $n^{th}$ round. Then
+Define $\tau_{n}^{i}$ to be the first time we pull arm $i$ in the $n^{th}$ round. Then
 \begin{align}
-&\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\} \nonumber \\
-=&\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}\sum_{t=k}^{\infty}\mathbbm{1}\{c(t)>0\}\mathbbm{1}\{t=\tau_{n}^{k}\} \nonumber 
+\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\} =\sum_{n=1}^{\infty}\sum_{i=1}^{N}\mathbbm{1}\{c(\tau_{n}^{i})>0\}. \nonumber
 \end{align}
@@
 &E[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}] \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}\sum_{k=1}^{\infty}P\left(\exists i,j:|u_{i}^{j}-u_{i,\tau_{n}^{k}}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2Wm}\right)P(t=\tau_{n}^{k})+\sum_{n=1}^{n_1}N \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{t=1}^{\infty}\sum_{k=1}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{32m^2\sigma^2}\right)\times P(t=\tau_{n}^{k})+\sum_{n=1}^{n_1}N \nonumber \\
-\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{32m^2\sigma^2}\right)\times Nn+\sum_{n=1}^{n_1}N \nonumber  \\
-=&24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2} + Nn_1, \nonumber
+=&\sum_{n=1}^{\infty}\sum_{i=1}^{N}P(c(\tau_{n}^{i})>0) \nonumber \\
+\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}P\left(\exists i,j:|u_{i}^{j}-u_{i,\tau_{n}^{i}}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2Wm}\right)+\sum_{n=1}^{n_1}N \nonumber \\
+\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right) +\sum_{n=1}^{n_1}N \nonumber \\
+\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right)\times N+\sum_{n=1}^{n_1}N \nonumber  \\
+\leq&24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1, \nonumber
 \end{align}
@@
 For regret incurred after the first $n_0$ round, it has two different components: the regret incurred when we let the agents play myopically and the regret incurred when we incentivize the agents.
-For the regret incurred when we let the agents play myopically at time t, it consists of the following two components:
+Using Lemma~\ref{lemma:numP}, the expected regret incurred when we incentivize the agents is bounded above by: $\left[24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{32W^2 m^2\sigma^2})-1} + Nn_1\right]R$.
+
+For the regret incurred when we let the agents play myopically at time $t\geq t_{n_0}$, it consists of the following two components:
 \begin{itemize}
-\item For those user whose utility difference between their best and the second best arm is greater than $f(t)$: suppose it is at the $n(t)^{th}$ round, the probability of these user making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n(t) f(t)^2}{32 m^2\sigma^2}\right)$ at time $t$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n(t) f(t)^2}{32 m^2\sigma^2}\right)\times R$.
-We denote the regret incurred by these agents as $r_1(t)$.
+\item For those users whose utility difference between their best and the second best arm is greater than $f(t)$: we define a sequence of stopping time $\tau_{n}^{k}=t_n+k$.
+For the regret occurred at each stopping time $\tau(k)$,  the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau(k))^2}{32 W^2 m^2\sigma^2}\right)$ at stopping time $\tau(k)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau(k))^2}{32 W^2 m^2\sigma^2}\right)\times R$.
+We denote the regret incurred by these agents as $r_1(\tau(k))$.
 \item For those user whose utility difference between their best and the second best arm is smaller than $f(t)$: this happens with probability $S(f(t))$ at each time and regret is bounded above by $S(f(t)) \times f(t)=Mf(t)^2$.
@@
 =&E\left[\sum_{t=1}^{t_{n_{0}}} r(t) + \sum_{t=t_{n_{0}}}^{T}(r_1(t)+r_2(t))\right]  \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{t=t_{n_{0}}}^{T}r_1(t)\right]+ E\left[\sum_{t=t_{n_{0}}}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{t=t_{n}}^{t_{n+1}}24Nm\exp\left(-\frac{1.8n f(t)^2}{32 m^2\sigma^2}\right) R\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}-1}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\mathbbm{1}\{k\leq t_{n+1}-t_n\}\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{t=t_{n}}^{t_{n+1}-1}24Nm\exp\left(-\frac{1.8n f(t)^2}{32 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
 \leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(t_n)^2}{32 m^2\sigma^2}\right)R \times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
@@
 
-The expected regret incurred when we incentivize the agents is calculated in Theorem~\ref{rst:budget}. Thus the cumulative regret at time $T$ is bounded above by
+ Thus the cumulative regret at time $T$ is bounded above by
 \begin{align}

### 2017-11-29 paper.tex
fixed the proof of Theorem 1

@@
 \begin{lemma}
-For all $n\geq 1$ and $l\geq 2$, we have
+For all $n\geq 1$, we have
 \begin{align}
@@
 \iff & 0.81 n^{5/3} \geq 0.6n \log(\log_{1.1}(n)+1) \nonumber \\
-\Longleftarrow &  1.3 n^{2/3} \geq  \log(\log_{1.1}(n)+1) \nonumber
+\iff &  \frac{81}{60} n^{2/3} \geq  \log(\log_{1.1}(n)+1) \nonumber
 \end{align}
+
+Denote $f(x) = \frac{81}{60}x^{2/3} - \log(\log_{1.1}(x)+1)$.
+It's easy to compute $f^{'}(x)=0$ has a unique solution $x_{0}=e^{2/3w(\frac{20e^{20000/314763}}{27})-\frac{10000}{104921}}$ (here $w(\cdot)$ is the Lambert W-Function) and it is the global minimum.
+Since $f(x_{0})\approx 0.0252 >0$, we know $f(x)>0$ for all $x\geq 1$.
+Thus, our lemma holds true.
 \end{proof}
@@
 For regret incurred after the first $n_0$ round, it has two different components: the regret incurred when we let the agents play myopically and the regret incurred when we incentivize the agents.
-Using Lemma~\ref{lemma:numP}, the expected regret incurred when we incentivize the agents is bounded above by: $\left[24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{32W^2 m^2\sigma^2})-1} + Nn_1\right]R$.
+Using Lemma~\ref{lemma:numP}, the expected regret incurred when we incentivize the agents is bounded above by: $\left[24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1\right]R$.
 
@@
 \item For those users whose utility difference between their best and the second best arm is greater than $f(t)$: we define a sequence of stopping time $\tau_{n}^{k}=t_n+k$.
-For the regret occurred at each stopping time $\tau(k)$,  the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau(k))^2}{32 W^2 m^2\sigma^2}\right)$ at stopping time $\tau(k)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau(k))^2}{32 W^2 m^2\sigma^2}\right)\times R$.
+For the regret occurred at each stopping time $\tau(k)$,  the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau(k))^2}{64 W^2 m^2\sigma^2}\right)$ at stopping time $\tau(k)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau(k))^2}{64 W^2 m^2\sigma^2}\right)\times R$.
 We denote the regret incurred by these agents as $r_1(\tau(k))$.
@@
 \leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\mathbbm{1}\{k\leq t_{n+1}-t_n\}\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{t=t_{n}}^{t_{n+1}-1}24Nm\exp\left(-\frac{1.8n f(t)^2}{32 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(t_n)^2}{32 m^2\sigma^2}\right)R \times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)R\times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \label{equ:regret}
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{t=t_{n}}^{t_{n+1}-1}24Nm\exp\left(-\frac{1.8n f(t)^2}{64 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(t_n)^2}{64 m^2\sigma^2}\right)R \times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(n)^2}{64 m^2\sigma^2}\right)R\times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \label{equ:regret}
 \end{align}
@@
 \begin{align}
-&\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-+ & 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{32m^2\sigma^2}}-1)^2}R+N\left(\max\left\{n_{0},\frac{2}{p}\right\}\right)R. \nonumber
+&\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
++ & 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{64 m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{64m^2\sigma^2}}-1)^2}R+N\left(\max\left\{n_{0},\frac{2}{p}\right\}\right)R. \nonumber
 \end{align}
@@
 \begin{align}
-\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2.
+\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2.
 \end{align}
 
-If we set $f^2(t)=\frac{2\log(T)\times 32m^2\sigma^2}{1.8t}$, then
+If we set $f^2(t)=\frac{2\log(T)\times 64m^2\sigma^2}{1.8t}$, then
 \begin{align}
-&\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\ 
+&\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\ 
 \leq & \sum_{n=1}^{T} 24N^2 mnR \exp\left(-2\log(T)\right)  + \frac{64m^2\sigma^2 M\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{n} \nonumber \\
@@
 The proof of this corollary is similar to the proof of Theorem~\ref{rst:regret}.
-If we set $f^2(t)=\frac{2\log(T)\times 32m^2\sigma^2}{1.8t}$, then there exists a $t_{0}$ such that for $t>t_{0}$, $S(f(t))=0$.
+If we set $f^2(t)=\frac{2\log(T)\times 64m^2\sigma^2}{1.8t}$, then there exists a $t_{0}$ such that for $t>t_{0}$, $S(f(t))=0$.
 Thus, similar to equation~\eqref{equ:regret}, we know the cumulative expected regret when we let the agents play myopically is bounded above by
 \begin{align}
-\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{32 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{t_{0}}Mf(t)^2 \nonumber
+\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{t_{0}}Mf(t)^2 \nonumber
 \end{align}

### 2017-11-29 paper.tex
fixed the proof of Theorem 2

@@
 In our paper, we assume all arms are some agents' best arm.
-Under this assumption, we prove that with $O(N)$ payment budget, this policy has $O(N^2+M(\log(T))^2)$ cumulative expected regret where $M$ is an upper bound on the limiting marginal probability density of agent utilities that are nearly indifferent between their best and the second best arm.
+Under this assumption, we prove that with $O(N^2)$ payment budget, this policy has $O(N^2+M(\log(T))^2)$ cumulative expected regret where $M$ is an upper bound on the limiting marginal probability density of agent utilities that are nearly indifferent between their best and the second best arm.
 \bccomment{We need a stronger condition, see corralary 1} If $M=0$, which typically happens when the agent utility distribution is discrete, this policy achieve constant cumulative expected regret $O(N^2)$.
@@
 
-We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+M(\log(T))^2)$ regret with $O(N)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
+We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+M(\log(T))^2)$ regret with $O(N^2)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
 
@@
 
-In this section, we prove Algorithm~\ref{Alg1} achieves $O(N^2+M(\log(T))^2)$ cumulative regret with $O(N)$ payment budget.
+In this section, we prove Algorithm~\ref{Alg1} achieves $O(N^2+M(\log(T))^2)$ cumulative regret with $O(N^2)$ payment budget.
 This is stated in the following pair of theorems, which together constitute our main results.
@@
 \begin{theorem}
-The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N)$. 
+The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$. 
 \label{rst:budget}
@@
 \begin{itemize}
-\item For those users whose utility difference between their best and the second best arm is greater than $f(t)$: we define a sequence of stopping time $\tau_{n}^{k}=t_n+k$.
-For the regret occurred at each stopping time $\tau(k)$,  the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau(k))^2}{64 W^2 m^2\sigma^2}\right)$ at stopping time $\tau(k)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau(k))^2}{64 W^2 m^2\sigma^2}\right)\times R$.
-We denote the regret incurred by these agents as $r_1(\tau(k))$.
+\item For those users whose utility difference between their best and the second best arm is greater than $f(t)$: condition on $t\in [t_n,t_{n+1})$, the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(t)^2}{64 W^2 m^2\sigma^2}\right)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(t)^2}{64 W^2 m^2\sigma^2}\right)\times R$.
+We denote the regret incurred by these agents as $r_1(t)$.
 \item For those user whose utility difference between their best and the second best arm is smaller than $f(t)$: this happens with probability $S(f(t))$ at each time and regret is bounded above by $S(f(t)) \times f(t)=Mf(t)^2$.
@@
 \leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}-1}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\mathbbm{1}\{k\leq t_{n+1}-t_n\}\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{t=t_{n}}^{t_{n+1}-1}24Nm\exp\left(-\frac{1.8n f(t)^2}{64 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(t_n)^2}{64 m^2\sigma^2}\right)R \times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T}E\left[24Nm\exp\left(-\frac{1.8n f(n)^2}{64 m^2\sigma^2}\right)R\times (t_{n+1}-t_{n})\right]+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \label{equ:regret}
+&\bccomment{\text{is the following conditional expectation correct?}} \nonumber \\
+= & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}-1}E[r_1(t)|t\in [t_n,t_{n+1}-1)]\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{t=t_{n}}^{t_{n+1}-1}24Nm\exp\left(-\frac{1.8n f(t)^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \label{equ:regret}
 \end{align}
@@
 \begin{align}
-&\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-+ & 24N^2 m \frac{e^{\frac{1.8\delta_{0}}{64 m^2\sigma^2}}}{(e^{\frac{1.8\delta_{0}}{64m^2\sigma^2}}-1)^2}R+N\left(\max\left\{n_{0},\frac{2}{p}\right\}\right)R. \nonumber
+&\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
++ & 24N^2 m \frac{1}{e^{\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2}}-1}R+N\left(\max\left\{n_{0},\frac{2}{p}\right\}\right)R. \nonumber
 \end{align}
@@
 \begin{align}
-\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2.
+\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2.
 \end{align}
 
-If we set $f^2(t)=\frac{2\log(T)\times 64m^2\sigma^2}{1.8t}$, then
+If we set $f^2(t)=\frac{2\log(T)\times 64W^2 m^2\sigma^2}{1.8t}$, then
 \begin{align}
-&\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\ 
-\leq & \sum_{n=1}^{T} 24N^2 mnR \exp\left(-2\log(T)\right)  + \frac{64m^2\sigma^2 M\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{n} \nonumber \\
-\leq &  24N^2 m R\frac{T(T-1)}{2T^2}  + 35.56 m^2\sigma^2 M\log(T)(\log(T)+1) \nonumber \\
-\leq &  12 N^2 m R  + 35.56 m^2\sigma^2 M\log(T)(\log(T)+1). \nonumber
+&\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\ 
+\leq & \sum_{n=1}^{T} 24N^2 mnR \exp\left(-2\log(T)\right)  + \frac{128W^2 m^2\sigma^2 M\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{n} \nonumber \\
+\leq &  24N^2 m R\frac{T(T-1)}{2T^2}  + 71.12 W^2 m^2\sigma^2 M\log(T)(\log(T)+1) \nonumber \\
+\leq &  12 N^2 m R  + 71.12 W^2 m^2\sigma^2 M\log(T)(\log(T)+1). \nonumber
 \end{align}
@@
 The proof of this corollary is similar to the proof of Theorem~\ref{rst:regret}.
-If we set $f^2(t)=\frac{2\log(T)\times 64m^2\sigma^2}{1.8t}$, then there exists a $t_{0}$ such that for $t>t_{0}$, $S(f(t))=0$.
+If we set $f^2(t)=\frac{2\log(T)\times 64W^2 m^2\sigma^2}{1.8t}$, then there exists a $t_{0}$ such that for $t>t_{0}$, $S(f(t))=0$.
 Thus, similar to equation~\eqref{equ:regret}, we know the cumulative expected regret when we let the agents play myopically is bounded above by
 \begin{align}
-\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{t_{0}}Mf(t)^2 \nonumber
+\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{t_{0}}Mf(t)^2 \nonumber
 \end{align}
@@
 
-Based on Wolframalpha \bccomment{still not sure how to compute this by hand}, we know
+Based on our calculation, we know
 

### 2017-11-29 paper.tex
edited the proof of Theorem 2

@@
 \begin{itemize}
-\item For those users whose utility difference between their best and the second best arm is greater than $f(t)$: condition on $t\in [t_n,t_{n+1})$, the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(t)^2}{64 W^2 m^2\sigma^2}\right)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(t)^2}{64 W^2 m^2\sigma^2}\right)\times R$.
-We denote the regret incurred by these agents as $r_1(t)$.
+\item For those users whose utility difference between their best and the second best arm is greater than $f(t)$: we define a sequence of stopping time $\tau_{n}^{k}$ to be the $k^{th}$ time period in the $n^{th}$ round.
+For $\tau_{n}^{k}=t$, the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)\times R$.
+We denote the regret incurred by these agents as $r_1(\tau_{n}^{k})$.
 \item For those user whose utility difference between their best and the second best arm is smaller than $f(t)$: this happens with probability $S(f(t))$ at each time and regret is bounded above by $S(f(t)) \times f(t)=Mf(t)^2$.
@@
 \leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}-1}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-&\bccomment{\text{is the following conditional expectation correct?}} \nonumber \\
-= & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}-1}E[r_1(t)|t\in [t_n,t_{n+1}-1)]\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{t=t_{n}}^{t_{n+1}-1}24Nm\exp\left(-\frac{1.8n f(t)^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
+&\bccomment{\text{is the following proof correct?}} \nonumber \\
+= & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{t_{n+1}-t_{n}}r_1(\tau_{n}^{k})\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{k=1}^{t_{n+1}-t_n}24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{k=1}^{t_{n+1}-t_n}24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
 \leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \label{equ:regret}

### 2017-11-29 paper.tex
did some edits

@@
 Under this assumption, we prove that with $O(N^2)$ payment budget, this policy has $O(N^2+M(\log(T))^2)$ cumulative expected regret where $M$ is an upper bound on the limiting marginal probability density of agent utilities that are nearly indifferent between their best and the second best arm.
-\bccomment{We need a stronger condition, see corralary 1} If $M=0$, which typically happens when the agent utility distribution is discrete, this policy achieve constant cumulative expected regret $O(N^2)$.
+If all agents' utility difference between their best and second best arm is bounded below by a positive number, which typically happens when the agent utility distribution is discrete, this policy achieve constant cumulative expected regret $O(N^2)$.
 The key difference between our problem setting and both the homogenous preference setting and the traditional multi-armed bandits setting is that we must incentivize agents to try suboptimal arms much less often, since all arms are some agents' best arm.
@@
 &P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\nonumber \\
-\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|>\lambda |\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|>\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,\tau)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda). \label{ACI}
+\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda |\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
+\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
+= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda). \label{ACI}
 \end{align}
 
-To bound equation~(\ref{ACI}), we use Lemma~\ref{ACI-inequality}. Similar to Lemma~\ref{ACI-inequality}, we define
+To bound equation~(\ref{ACI}), we use Lemma~\ref{ACI-inequality}. Define
 \begin{align}
@@
 \begin{align}
-&P(\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P\left(S_{N(i,\tau)}^{i,j}>\frac{N(i,\tau)\lambda}{2\sigma}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & P\left(S_{N(i,\tau)}^{i,j}> \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
+&P(\epsilon_{i,\tau}^{j}\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
+=&P\left(S_{N(i,\tau)}^{i,j}\geq \frac{N(i,\tau)\lambda}{2\sigma}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
+\leq & P\left(S_{N(i,\tau)}^{i,j}\geq \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
 \leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
@@
 \begin{align}
-&P(\epsilon_{i,\tau}^{j}<-N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P(-\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
+&P(\epsilon_{i,\tau}^{j}\leq-\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
+=&P(-\epsilon_{i,\tau}^{j}\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
 \leq & 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber 
@@
 
-Therefore, we know $P(\epsilon_{i,\tau}^{j}>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right)$.
+Therefore, we know $P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right)$.
 Thus, we know
 \begin{align}
-&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|>N(i,t)\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)  \nonumber \\
+&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)  \nonumber \\
 \leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
@@
 \begin{lemma}
-Using our algorithm, we have $\mathbb{E}[t_{n}-t_{n-1}]\leq Nn$, $\forall n\geq 1$.
+Using our algorithm, we have $\mathbb{E}[t_{n+1}-t_{n}]\leq Nn$, $\forall n\geq 1$.
 \label{round:length}
@@
 	A round completes when each arm is pulled at least once in that round.
-Let $X_{i}$ be the number of agents who come to the system between the time after the $i-1^{th}$ unique arm was pulled, up to and including the time when the $i^{th}$ unique arm was pulled.
+Let $X_{i}$ be the number of agents who come to the system between the time after the $(i-1)^{th}$ unique arm was pulled, up to and including the time when the $i^{th}$ unique arm was pulled.
 Then we know
 \begin{equation*}
-\mathbb{E}[t_{n}-t_{n-1}]=\sum_{i=1}^{N}E[X_{i}].
+\mathbb{E}[t_{n+1}-t_{n}]=\sum_{i=1}^{N}E[X_{i}].
 \end{equation*}
@@
 \begin{align}
-E[t_{n}-t_{n-1}]\leq Nn. \nonumber
+E[t_{n+1}-t_{n}]\leq Nn. \nonumber
 \end{align}
@@
 
-We know
+Based on the above notations, we can rewrite the cumulative payment as follows:
 \begin{align}
@@
 =&P(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber  \\
-=&\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber
+\leq &\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber
 \end{align}
@@
 \begin{align}
-&\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{l-1}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber \\ 
+&\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma(l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber \\ 
 =&\sum_{i,j}P(|S_{i,t}^{j}|\geq \frac{N(i,t)(l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})). \nonumber \\
@@
 \begin{lemma}
-Under our algorithm, the expected number of payments is bounded above by $O(N^2)$.
+The expected number of payments for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$.
 \label{lemma:numP}
@@
 \begin{proof}
-If $|u_{i}^{j}-u_{i,t}^{j}|< \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2mW\lambda\}$, they will correctly identify their best arm.
-Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|< \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms.
+If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2mW\lambda\}$, they will correctly identify their best arm.
+Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms.
 In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
 Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$.
-Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).The cumulative expected number of payments is bounded above by:
+Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).
 
@@
 
-Thus, we know
+The cumulative expected number of payments is bounded above by:
 \begin{align}
-&E[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}] \nonumber \\
+&E\left[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}\right] \nonumber \\
 =&\sum_{n=1}^{\infty}\sum_{i=1}^{N}P(c(\tau_{n}^{i})>0) \nonumber \\
@@
 \leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}-1}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-&\bccomment{\text{is the following proof correct?}} \nonumber \\
+&\bccomment{\text{is the following proof correct? I think it might be wrong}} \nonumber \\
 = & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{t_{n+1}-t_{n}}r_1(\tau_{n}^{k})\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
@@
 
-For a fixed $T$, we only need to minimizing the following two terms since all others are constant:
+For a fixed $T$, we only need to minimize the following two terms since all others are constant:
 

### 2017-12-01 paper.tex
did some edits
Update paper.tex
fixed some typos and did some edits

@@
 &P(\epsilon_{i,\tau}^{j}\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P\left(S_{N(i,\tau)}^{i,j}\geq \frac{N(i,\tau)\lambda}{2\sigma}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & P\left(S_{N(i,\tau)}^{i,j}\geq \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\right|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
+=&P\left(S_{N(i,\tau)}^{i,j}\geq \frac{N(i,\tau)\lambda}{2\sigma}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
+\leq & P\left(S_{N(i,\tau)}^{i,j}\geq \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
 \leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
@@
 =&P(\omega\in L^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in L^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
-\leq & 1-P(|\epsilon_{i,t}^{j}|<\frac{2\sigma (l-1)}{n^{1/6}}, \forall i,j|t\in[t_n,t_{n+1})) \nonumber \\
-=&P(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber  \\
-\leq &\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber
+\leq & 1-P\left(|\epsilon_{i,t}^{j}|<\frac{2\sigma (l-1)}{n^{1/6}}, \forall i,j|t\in[t_n,t_{n+1})\right) \nonumber \\
+=&P\left(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})\right) \nonumber  \\
+\leq &\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})\right) \nonumber
 \end{align}
@@
 \begin{align}
-&\sum_{i,j}P(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma(l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})) \nonumber \\ 
-=&\sum_{i,j}P(|S_{i,t}^{j}|\geq \frac{N(i,t)(l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})). \nonumber \\
+&\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma(l-1)}{n^{1/6}}\bigg|t\in[t_n,t_{n+1})\right) \nonumber \\ 
+=&\sum_{i,j}P\left(|S_{i,t}^{j}|\geq \frac{N(i,t)(l-1)}{n^{1/6}}\bigg|t\in[t_n,t_{n+1})\right) \nonumber \\
 \leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})). \nonumber
@@
 
-In our algorithm, we take ``pay whatever it takes'' strategy when we decided to incentivize the agent.
-In our proof, the only time we used ''pay whatever it takes'' is in Lemma~\ref{round:length}.
+In Algorithm~\ref{chap5:Alg1}, we use ``pay whatever it takes'' strategy when we decide to incentivize the agent.
+However, ''pay whatever it takes'' only shows up in the proof of Lemma~\ref{chap5:round:length}.
 Without loss of generality, suppose we want to incentivize arm $i$ at time $t$ at the $n^{th}$ round.
-Based on the proof of Lemma~\ref{round:length}, as long as we offer a payment $c_{i,t}$ such that arm $i$ will have at least $n^{-1}$ probability being pulled at time $t$, our results still hold true.
+Based on the proof of Lemma~\ref{chap5:round:length}, as long as we offer a payment $c_{i,t}$ such that arm $i$ has at least $n^{-1}$ probability being pulled at time $t$, our results still hold true.
 We could compute this $c_{i,t}$ dynamically based on $F(\cdot)$ as well as our current estimate $u_{i,t}$.
@@
 
-The same proof would work and we can get the exact same results as ``pay whatever it takes'' strategy.
+The same proof would work and we can get the exact same results as Algorithm~\ref{chap5:Alg1}.
 
-\section{Lower Bound $O(\log(T))$}
+\section{Lower Bound $\Omega(\log(T))$}
 \label{sec:lb}
 
-In this section, we assume $\theta$ follows a continuous distribution $F(\cdot)$. We provide a example to show the best possible lower bound is $O(\log(T))$ regardless of the incentivizing strategy.
+In this section, we assume $\theta$ follows a continuous distribution $F(\cdot)$.
+We provide an example to show the best possible lower bound is $\Omega(\log(T))$ regardless of the incentivizing strategy.
 
@@
 We assume the users' preference are uniformly distributed on the unit circle.
-If the user knows the true reward for both arms, then the users with preference on the bottom half circle will choose arm $1$ and the users with preference on the top half circle will choose arm $2$.
+If the user knows the exact attribute vectors for both arms, then the users with preference on the bottom half circle will choose arm $1$ and the users with preference on the top half circle will choose arm $2$.
 
@@
 
-To lower bound the regret, we assume that the agents already know the true utility vector for arm $1$.
-Without loss of generality, denote $u_{2,t} = (0,1)+(z_{t,1},z_{t,2}) = (0,1)+ (N(0,1/t),N(0,1/t))$ to be the estimate reward for arm $2$ (Without loss of generality, we assume the variance for the noise is $1$).
+To lower bound the regret, we assume that the agents already know the true attribute vector for arm $1$.
+Without loss of generality, denote $u_{2,t} = (0,1)+(z_{t,1},z_{t,2}) = (0,1)+ (N(0,1/t),N(0,1/t))$ to be the estimate attribute vector for arm $2$ (Without loss of generality, we assume the variance for the noise is $1$).
 
@@
 = &E[r(t) | z_{t,1}>0,z_{t,2}>0] \times P(z_{t,1}>0,z_{t,2}>0) + E[r(t) |z_{t,1}>0,z_{t,2}<0] \times P(z_{t,1}>0,z_{t,2}<0) \nonumber \\
-= &E[r(t) | z_{t,1}<0,z_{t,2}>0] \times P(z_{t,1}<0,z_{n,2}>0) + E[r(t) |z_{t,1}<0,z_{t,2}<0] \times P(z_{t,1}<0,z_{t,2}<0) \nonumber \\
+&+E[r(t) | z_{t,1}<0,z_{t,2}>0] \times P(z_{t,1}<0,z_{n,2}>0) + E[r(t) |z_{t,1}<0,z_{t,2}<0] \times P(z_{t,1}<0,z_{t,2}<0) \nonumber \\
 \geq & 0.25 \times E[r(t) | z_{t,1}>0, z_{t,2}>0]. \nonumber
@@
 
-Given $z_{t,1}>0$ and $z_{t,2}>0$, we know the user between $(-1,0)$ and $\left(\frac{-1-z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ and the user between $(1,0)$ to $\left(\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{-z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ will make a mistake.
-And the regret is the absolute value of the second coordinate of the user's preference vector.
+Given $z_{t,1}>0$ and $z_{t,2}>0$, we know users whose preference vector between $(-1,0)$ and $\left(\frac{-1-z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ as well as users whose preference vector between $(1,0)$ and $\left(\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{-z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ will make a mistake.
+The regret is the absolute value of the second coordinate of the user's preference vector.
 Thus, we know
@@
 \begin{align}
-\lim_{t\rightarrow\infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} = O(1). \nonumber
+\lim_{t\rightarrow\infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} = O(1), \nonumber
 \end{align}
+and use the fact that $\sum_{n=1}^{T}\frac{1}{n}=O(\log(T))$ to show the regret is at least $\Omega(\log(T))$.
 
@@
 
-Thus, the cumulative expected regret is at least $O(\log(T))$.
+Thus, the cumulative expected regret is at least $\Omega(\log(T))$.
 
 \section{Conclusion}
+In this paper, we study the incentivizing exploration problem with heterogeneous user preferences, which generalize the problem setting studied by \citet{frazier2014incentivizing} and \citet{han2015incentivizing}.
+We propose a simple policy that mostly exploits and occasionally incentivizing exploration, which can achieve $O(N^2+M(\log(T))^2)$ cumulative expected regret with $O(N^2)$ payment budget.
 

### 2017-12-04 paper.tex
fixed a citation error

@@
 \section{Conclusion}
-In this paper, we study the incentivizing exploration problem with heterogeneous user preferences, which generalize the problem setting studied by \citet{frazier2014incentivizing} and \citet{han2015incentivizing}.
+In this paper, we study the incentivizing exploration problem with heterogeneous user preferences, which generalize the problem setting studied by \cite{frazier2014incentivizing} and \cite{han2015incentivizing}.
 We propose a simple policy that mostly exploits and occasionally incentivizing exploration, which can achieve $O(N^2+M(\log(T))^2)$ cumulative expected regret with $O(N^2)$ payment budget.

### 2017-12-04 paper.tex
fixed a citation error

@@
 
-In Algorithm~\ref{chap5:Alg1}, we use ``pay whatever it takes'' strategy when we decide to incentivize the agent.
-However, ''pay whatever it takes'' only shows up in the proof of Lemma~\ref{chap5:round:length}.
+In Algorithm~\ref{Alg1}, we use ``pay whatever it takes'' strategy when we decide to incentivize the agent.
+However, ''pay whatever it takes'' only shows up in the proof of Lemma~\ref{round:length}.
 Without loss of generality, suppose we want to incentivize arm $i$ at time $t$ at the $n^{th}$ round.
-Based on the proof of Lemma~\ref{chap5:round:length}, as long as we offer a payment $c_{i,t}$ such that arm $i$ has at least $n^{-1}$ probability being pulled at time $t$, our results still hold true.
+Based on the proof of Lemma~\ref{round:length}, as long as we offer a payment $c_{i,t}$ such that arm $i$ has at least $n^{-1}$ probability being pulled at time $t$, our results still hold true.
 We could compute this $c_{i,t}$ dynamically based on $F(\cdot)$ as well as our current estimate $u_{i,t}$.
@@
 
-The same proof would work and we can get the exact same results as Algorithm~\ref{chap5:Alg1}.
+The same proof would work and we can get the exact same results as Algorithm~\ref{Alg1}.
 

### 2017-12-04 paper.tex
Update paper.tex
Fixed the proof of theorem 2.

@@
 \begin{itemize}
-\item For those users whose utility difference between their best and the second best arm is greater than $f(t)$: we define a sequence of stopping time $\tau_{n}^{k}$ to be the $k^{th}$ time period in the $n^{th}$ round.
+For those users whose utility difference between their best and the second best arm is greater than $f(t)$: we define a sequence of stopping time $\tau_{n}^{k}$ to be the $k^{th}$ time period in the $n^{th}$ round.
+For $k>t_{n+1}-t_{n}$, we define $\tau_{n}^{k}=\infty$.
 For $\tau_{n}^{k}=t$, the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)\times R$.
 We denote the regret incurred by these agents as $r_1(\tau_{n}^{k})$.
+For $k>t_{n+1}-t_{n}$, we define $r_1(\tau_{n}^{k})=0$.
 \item For those user whose utility difference between their best and the second best arm is smaller than $f(t)$: this happens with probability $S(f(t))$ at each time and regret is bounded above by $S(f(t)) \times f(t)=Mf(t)^2$.
@@
 \leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}-1}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-&\bccomment{\text{is the following proof correct? I think it might be wrong}} \nonumber \\
-= & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{t_{n+1}-t_{n}}r_1(\tau_{n}^{k})\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{k=1}^{t_{n+1}-t_n}24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{k=1}^{t_{n+1}-t_n}24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \label{equ:regret}
+=& \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right]. \label{chap5:equ:r1}
+\end{align}
+Since
+\begin{align}
+& E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\right] \nonumber\\
+= &  \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})] \nonumber \\
+= &  \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}(E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty)+E[r_1(\tau_{n}^{k})|\tau_{n}^{k}=\infty]\times P(\tau_{n}^{k}=\infty)) \nonumber \\
+= & \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty), \nonumber
+\end{align}
+
+we have
+\begin{align}
+\eqref{chap5:equ:r1}= & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty) + E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}\left[\sum_{k=1}^{\infty}24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right) R\times P(\tau_{n}^{k}<\infty) \right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R \times Nn+ \sum_{t=1}^{T}Mf(t)^2. \label{chap5:equ:regret}
 \end{align}

### 2018-01-24 colt.tex
edited the payment proof & put our paper in the colt template

--- 2017-12-04 paper.tex
@@
-\documentclass{article}
-\usepackage[utf8]{inputenc}
+\documentclass[twoside,11pt]{article}
+\usepackage{jmlr2e}
 
-\usepackage[english]{babel}
-
-\usepackage{blindtext}
-\usepackage{amssymb}
+% Any additional packages needed should be included after jmlr2e.
+% Note that jmlr2e.sty includes epsfig, amssymb, natbib and graphicx,
+% and defines many common macros, such as 'proof' and 'example'.
+%
+% It also sets the bibliographystyle to plainnat; for more information on
+% natbib citation styles, see the natbib documentation, a copy of which
+% is archived at http://www.jmlr.org/format/natbib.pdf
 
@@
 \usepackage[]{algorithmic}
+
+\usepackage[utf8]{inputenc} % allow utf-8 input
 \usepackage[T1]{fontenc}    % use 8-bit T1 fonts
 \usepackage{xr} 
+\usepackage{url}            % simple URL typesetting
 \usepackage{amsfonts}       % blackboard math symbols
@@
 \usepackage{comment}
-\usepackage{graphicx}
 \usepackage{subcaption}
@@
 \usepackage{amsmath}
-\usepackage{dblfloatfix}
-\usepackage{bbm}
-
-\newcommand{\IE}{IE} 
+\usepackage{float}
+\newcommand{\CTB}{CTB} % This is the acronym for our CTB algorithm
+\newcommand{\CTBone}{CTB$-1$} % This is the acronym for our Bayes CTB algorithm
+\newcommand{\CTBtwo}{CTB$-2$} % This is the acronym for our Bayes CTB algorithm
+\newcommand{\CTBthree}{CTB$-3$}
 \newcommand{\argmax}{\mathop{\mathrm{argmax}}}
+\usepackage{mathtools}
 
@@
 
+\newcommand{\argmax}{\mathop{\mathrm{argmax}}}
+
 \newcommand{\bccomment}[1]{{\color{blue}BC: #1}}
@@
 
+\newtheorem{assumption}{Assumption}
 \newtheorem{definition}{Definition}[section]
@@
 \newtheorem{corollary}{Corollary}
-\newtheorem{assumption}{Assumption}
+
+% Definitions of handy macros can go here
+
+\newcommand{\dataset}{{\cal D}}
+\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
+
+% Heading arguments are {volume}{year}{pages}{date submitted}{date published}{paper id}{author-full-names}
+
+\jmlrheading{1}{2000}{1-48}{4/00}{10/00}{meila00a}{Marina Meil\u{a} and Michael I. Jordan}
+
+% Short headings should be running head and authors last names
+
+\ShortHeadings{Incentivizing Exploration with Heterogeneous Utilities}{Chen, Frazier and Kempe}
+\firstpageno{1}
+
+\begin{document}
 
@@
 
-\begin{document}
+\author{\name Bangrui Chen \email bc496@cornell.edu \\
+\name Peter I.\ Frazier \email pf98@cornell.edu \\
+\addr Operations Research and Information Engineering\\
+Cornell University\\
+New York, NY 14850, USA
+\AND
+\name David Kempe \email david.m.kempe@gmail.com  \\
+\addr Department of Computer Science\\
+University of Southern California\\
+Los Angeles, CA 90089, USA}
+
+\editor{}
 
 \maketitle
+
+\begin{abstract}
+sdafsd
+\end{abstract}
+
+\begin{keywords}
+Incentivizing Exploration
+\end{keywords}
 
@@
 
-We also need the following lemma in part of the proof of Theorem~\ref{rst:budget}.
-\begin{lemma}
-For all $n\geq 1$, we have
-\begin{align}
-0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-\label{lemma:cal2}
-\end{lemma}
-\begin{proof}
-\begin{align}
-&0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)} \nonumber \\
-\iff & 0.81 n^{5/3} \geq 0.6n \log(\log_{1.1}(n)+1) \nonumber \\
-\iff &  \frac{81}{60} n^{2/3} \geq  \log(\log_{1.1}(n)+1) \nonumber
-\end{align}
-
-Denote $f(x) = \frac{81}{60}x^{2/3} - \log(\log_{1.1}(x)+1)$.
-It's easy to compute $f^{'}(x)=0$ has a unique solution $x_{0}=e^{2/3w(\frac{20e^{20000/314763}}{27})-\frac{10000}{104921}}$ (here $w(\cdot)$ is the Lambert W-Function) and it is the global minimum.
-Since $f(x_{0})\approx 0.0252 >0$, we know $f(x)>0$ for all $x\geq 1$.
-Thus, our lemma holds true.
-\end{proof}
-
-Now we are ready to prove our first main result, Theorem~\ref{rst:budget}.
-
-\begin{proof}
-Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$.
-Denote $\epsilon_{i,t}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,t}$.
-Denote $\omega$ to be a sample path and $n(t,\omega)$ to be the round number for sample path $\omega$ at time $t$.
-For a fixed time $t$, define
-\begin{align}
-L^{'}[l](t) = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n(t,\omega),l), \forall i,j\}\nonumber
-\end{align}
-where $g(n,l)$ is a function which we will define later.
-Define $L[1](t) = L^{'}[1](t)$ and $L[i](t) = L^{'}[i](t)\setminus L^{'}[i-1](t)$ for $i\geq 2$.
-We call $L[l](t)$ the $l^{th}$ envelope at time $t$.
-We often simplify the notation and use $L[l]$ instead of $L[l](t)$ without confusion.
-
-In the calculation below, we omit the dependency on $\omega$ when refering to variables $c(t)$, $\epsilon_{i,t}^{j}$ and $t_n$.
-Based on the definition of $L[l]$, we know if $\omega\in L[l]$, the maximum payment we need to offer at time $t$ is bounded above by
-\begin{align}
-&\max_{i}\theta_t\cdot u_{i,t} - \min_{j}\theta_t\cdot u_{j,t} \nonumber \\
-= &\max_{i}\theta_t\cdot (\epsilon_{i,t}+u_i) - \min_{j}\theta_t\cdot (\epsilon_{j,t}+u_j) \nonumber \\
-\leq &\max_{i}\theta_t\cdot u_i - \min_{j}\theta_t\cdot u_j +\max_{i}\theta_t\cdot \epsilon_{i,t} - \min_{j}\theta_t\cdot \epsilon_{j,t}\nonumber \\
-\leq & R + 2Wmg(n,l). \nonumber
-\end{align}
-
-Based on the above notations, we can rewrite the cumulative payment as follows:
-\begin{align}
-&\sum_{t=1}^{\infty}c(t) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\} \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
-\end{align}
-
-Set $g(n,l)$ to be $\frac{2\sigma l}{n^{1/6}}$.
-Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2Wm\lambda\}$, they will correctly identify their best arm.
-Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{2\sigma l}{n^{1/6}} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
-Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms.
-Denote $a_0=\frac{4Wm\sigma}{p^{-1}(\frac{p}{2})}$.
-In order to have $\frac{2\sigma l}{n^{1/6}}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil (a_{0} l)^6 \rceil$.
-In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
-Denote $n_2=\frac{2}{p}$.
-Thus, we know we can only incur regret for sample paths $\omega$ in the $l^{th}$ envelope in the first $\max\{n_2,\lceil (a_0 l)^6 \rceil\}$ rounds.
-
-Thus,
-\begin{align}
-\sum_{t=1}^{\infty}c(t)=\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
-\end{align}
-
-Therefore,
-
-\begin{align}
-&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}E[c(t)|\omega \in L[l],t\in [t_n,t_{n+1}))P(\omega\in L[l],t\in [t_n,t_{n+1})) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+2Wm\frac{2\sigma l}{n^{1/6}}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})). \nonumber
-\end{align}
-
-We now bound $P(\omega\in L[l]|t\in[t_{n},t_{n+1}))$ for $n\geq n_0$ and $l\geq 2$.
-\begin{align}
-&P(\omega\in L[l]|t\in[t_{n},t_{n+1})) \nonumber \\
-=&P(\omega\in L^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in L^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
-\leq & 1-P\left(|\epsilon_{i,t}^{j}|<\frac{2\sigma (l-1)}{n^{1/6}}, \forall i,j|t\in[t_n,t_{n+1})\right) \nonumber \\
-=&P\left(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})\right) \nonumber  \\
-\leq &\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})\right) \nonumber
-\end{align}
-
-Define $S_{i,t}^{j}=\frac{N(i,t)\epsilon_{i,t}^{j}}{2\sigma}$, then we know $S_{i,t}^{j}$ is a summation of $1/2$ gaussian random numbers. Therefore,
-
-\begin{align}
-&\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma(l-1)}{n^{1/6}}\bigg|t\in[t_n,t_{n+1})\right) \nonumber \\ 
-=&\sum_{i,j}P\left(|S_{i,t}^{j}|\geq \frac{N(i,t)(l-1)}{n^{1/6}}\bigg|t\in[t_n,t_{n+1})\right) \nonumber \\
-\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})). \nonumber
-\end{align}
-
-Based on Lemma~\ref{lemma:cal2}, we know
-\begin{align}
-&N(i,t)^{5/6}(l-1) \nonumber \\
-=& 0.9N(i,t)^{5/6} + N(i,t)^{5/6}(l-1.9) \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)} + \sqrt{(l-1.9)^2 N(i,t)} \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+(l-1.9)^2 N(i,t)}. \nonumber
-\end{align}
-
-Based on Lemma~\ref{ACI-inequality}, we know
-\begin{align}
-&\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})) \nonumber \\
-\leq & \sum_{i,j}24e^{-1.8(l-1.9)^2} = 24Nme^{-1.8(l-1.9)^2}. \nonumber
-\end{align}
-
-Thus,
-\begin{align}
-&\sum_{t=1}^{\infty}c(t) \nonumber \\
-\leq&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+2Wm\frac{2\sigma l}{n^{1/6}}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-\leq& \sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(\omega\in L[1]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-+&\sum_{l=2}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-\leq& \sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(t\in [t_n,t_{n+1})) \nonumber \\
-+&\sum_{l=2}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]24Nme^{-1.8(l-1.9)^2}P(t\in [t_n,t_{n+1})) \nonumber \\
-\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]Nn +\sum_{l=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]24Nme^{-1.8(l-1.9)^2}Nn \nonumber \\
-\leq & \left[R+4Wm\sigma \right]N (\max\{n_2,\lceil (a_0)^6 \rceil\})^2+\sum_{l=2}^{\infty}24N^2 m[R+4Wml\sigma](\max\{n_2,\lceil (a_0 l)^6 \rceil\})^2 e^{-1.8(l-1.9)^2} \nonumber \\
-=& O(N^2). \nonumber
-\end{align}
-
-\end{proof}
-
 \begin{lemma}
@@
 \begin{itemize}
-For those users whose utility difference between their best and the second best arm is greater than $f(t)$: we define a sequence of stopping time $\tau_{n}^{k}$ to be the $k^{th}$ time period in the $n^{th}$ round.
+\item For those users whose utility difference between their best and the second best arm is greater than $f(t)$: we define a sequence of stopping time $\tau_{n}^{k}$ to be the $k^{th}$ time period in the $n^{th}$ round.
 For $k>t_{n+1}-t_{n}$, we define $\tau_{n}^{k}=\infty$.
@@
 \begin{align}
-\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2.
+\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2. \label{equ:regret}
 \end{align}
@@
 \begin{align}
-\lim_{t\rightarrow\infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} = O(1), \nonumber
+\lim_{t\rightarrow\infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{\frac{1}{t}} = O(1), \nonumber
 \end{align}
@@
 \begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber
+&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{\frac{1}{t}} \nonumber \\
+=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber
 \end{align}
@@
 \begin{align}
-\lim_{t\rightarrow \infty} d(t)=\frac{z_{t,1}^2}{2}. \nonumber
+\lim_{t\rightarrow \infty} d(t)=\frac{z_{t,1}^2}{2}. \label{ex:limit}
 \end{align}
@@
 \begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} \nonumber \\
-=&\frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ \frac{z_{t,1}^2}{2}e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) = \frac{1}{2\pi}.
-\nonumber
+&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{\frac{1}{t}} \nonumber \\
+=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber  \\
+=&\frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\left[ \frac{z_{t,1}^2}{2}e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) = \frac{1}{2\pi}. \nonumber
 \end{align}
@@
 
-\bibliography{reference}{}
-\bibliographystyle{plain}
+\newpage
 
+\appendix
+\section*{Proof of Theorem~\ref{rst:budget}}
+
+We also need the following lemma in part of the proof of Theorem~\ref{rst:budget}.
+\begin{lemma}
+For all $n\geq 1$, we have
+\begin{align}
+0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}. \nonumber
+\end{align}
+\label{lemma:cal2}
+\end{lemma}
+\begin{proof}
+\begin{align}
+&0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)} \nonumber \\
+\iff & 0.81 n^{5/3} \geq 0.6n \log(\log_{1.1}(n)+1) \nonumber \\
+\iff &  \frac{81}{60} n^{2/3} \geq  \log(\log_{1.1}(n)+1) \nonumber
+\end{align}
+
+Denote $f(x) = \frac{81}{60}x^{2/3} - \log(\log_{1.1}(x)+1)$.
+It's easy to compute $f^{'}(x)=0$ has a unique solution $x_{0}=e^{2/3w(\frac{20e^{20000/314763}}{27})-\frac{10000}{104921}}$ (here $w(\cdot)$ is the Lambert W-Function) and it is the global minimum.
+Since $f(x_{0})\approx 0.0252 >0$, we know $f(x)>0$ for all $x\geq 1$.
+Thus, our lemma holds true.
+\end{proof}
+
+Now we are ready to prove our first main result, Theorem~\ref{rst:budget}.
+
+\begin{proof}
+
+\noindent\textbf{Step 1: Categorize measurement errors into different radius envelopes}
+
+Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$.
+Denote $\epsilon_{i,t}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,t}$.
+Denote $\omega$ to be a sample path and $n(t,\omega)$ to be the round number for sample path $\omega$ at time $t$.
+For a fixed time $t$, define
+\begin{align}
+L^{'}[\ell](t) = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n(t,\omega),\ell), \forall i,j\}\nonumber
+\end{align}
+where $g(n,\ell)$ is a function which we will define later.
+Define $L[1](t) = L^{'}[1](t)$ and $L[i](t) = L^{'}[i](t)\setminus L^{'}[i-1](t)$ for $i\geq 2$.
+We call $L[\ell](t)$ the $\ell^{th}$ envelope at time $t$.
+We often simplify the notation and use $L[\ell]$ instead of $L[\ell](t)$ without confusion.
+
+In the calculation below, we omit the dependency on $\omega$ when refering to variables $c(t)$, $\epsilon_{i,t}^{j}$ and $t_n$.
+Based on the definition of $L[\ell]$, we know if $\omega\in L[\ell]$, the maximum payment we need to offer at time $t$ is bounded above by
+\begin{align}
+&\max_{i}\theta_t\cdot u_{i,t} - \min_{j}\theta_t\cdot u_{j,t} \nonumber \\
+= &\max_{i}\theta_t\cdot (\epsilon_{i,t}+u_i) - \min_{j}\theta_t\cdot (\epsilon_{j,t}+u_j) \nonumber \\
+\leq &\max_{i}\theta_t\cdot u_i - \min_{j}\theta_t\cdot u_j +\max_{i}\theta_t\cdot \epsilon_{i,t} - \min_{j}\theta_t\cdot \epsilon_{j,t}\nonumber \\
+\leq & R + 2Wmg(n,\ell). \nonumber
+\end{align}
+
+We denote $\bar{c}(n,\ell)=R + 2Wmg(n,\ell)$ as the upper bound of payment for round $n$ if our measurement error lie in the $\ell^{th}$ envelope.
+
+\noindent\textbf{Step 2: Introduce a new stochastic process which bounds the total payment in a round}
+
+Denote $\mathcal{F}_t$ as the filtration up to time $t$. Based on our algorithm, we know
+
+\[ P(\text{play a new arm}|\mathcal{F}_t) =
+  \begin{cases}
+    1       & \quad \text{if we incentivize}\\
+    \sum_{i\notin (V\cup S)} P(\theta \cdot u_{i,t}>\theta\cdot u_{j,t} \forall j\neq i)  & \quad \text{if }  S\setminus V\neq \emptyset 
+  \end{cases} \label{dom_stoc}
+\] 
+\hspace{1cm}$\geq (n-|V|)\times \frac{1}{n}=1-\frac{|V|}{n}$.
+
+Let $(Z_{n,v,m}:m\geq 0)$ be a sequence of independent Bernoulli random variable with success probability $(1-\frac{v}{n})$.
+We will construct an alternative stochastic process for selecting which arm gets played that has the same distribution as the original process, but under which
+\begin{align}
+t_{n+1}-t_{n}\leq \bar{T}_{n}:=\sum_{v=0}^{N-1}\bar{T}_{n,v}, \nonumber 
+\end{align}
+where $\bar{T}_{n,v}:=\inf\{m\geq 0: Z_{n,v,m}=1\}+1$.
+
+The new stochastic process will have the property that whenever $Z_{n,v(n,t),m(n,t)}=1$, we will play a new arm at time t for $t\in [t_{n}, t_{n+1}]$, where $v(n,t)$ is the number of unique arms played in round $n$ strictly before time $t$, and $m(n,t)$ is the number of times we have pulled a previously pulled arm for the current value of $v(n,t)$.
+At time $t$, to determine what arm to pull, calculate \eqref{dom_stoc} and let $q_t$ be the probability computed.
+Note $q_t\geq 1-\frac{v(n,t)}{n}$.
+
+If $Z_{n,v(n,t),m(n,t)}$ is 1, decide to play a new arm.
+Otherwise, draw a second Bernoulli random variable with probability $\frac{q_t-(1-\frac{v(n,t)}{n})}{1-(1-\frac{v(n,t)}{n})}$, and if it is 1, decide to play a new arm, and otherwise decide to play an old arm.
+Note that
+
+\begin{align}
+P(\text{play a new arm}|\mathcal{F}_{t})=\left[1-\frac{v(n,t)}{n}\right]+\left[1-(1-\frac{v(n,t)}{n})\right]\times \frac{q_t-(1-\frac{v(n,t)}{n})}{1-(1-\frac{v(n,t)}{n})}=q_t.
+\end{align}
+
+Since we pull a new arm only when $Z_{n,v(n,t),m(n,t)}=1$, the number of times we pull an arm when $v(n,t)=v$ is bounded above by $\bar{T}_{n,v}$. Thus,
+
+\begin{align}
+t_{n+1}-t_{n}\leq \sum_{v=0}^{n-1}\bar{T}_{n,v}=\bar{T}_{n}.
+\end{align}
+Finally, we want to bound $\sum_{t}E[c(t)]$. Let $C(n)$ be the cost incurred in round $n$. Thus $\sum_{t}E[c(t)]=\sum_{n}E[C(n)]$. We know
+\begin{align}
+C(n)&=\sum_{t=t_n}^{t_{n+1}-1}c(t)=\sum_{t=t_{n}}^{t_{n+1}-1}\sum_{\ell}\mathbbm{1}\{\omega\in L(\ell)\}c(t) \nonumber \\
+&\leq \sum_{t=t_{n}}^{t_{n+1}-1}\sum_{l}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell) \nonumber \\
+&\leq (t_{n+1}-t_{n})\sum_{\ell} \mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell) \nonumber \\
+&\leq \bar{T}_{n}\sum_{l}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell). \nonumber
+\end{align}
+
+Since $\bar{T}_{n}$ is independent of $\omega$, we know
+
+\begin{align}
+E[C(n)]\leq E[\bar{T}_{n}]\sum_{\ell}P(\omega\in L(\ell))\bar{c}(n,\omega). \nonumber
+\end{align}
+
+\noindent\textbf{Step 3: Rewrite the total payment expression}.
+
+Based on the above notations, we can rewrite the cumulative payment as follows:
+\begin{align}
+\sum_{t=1}^{\infty}c(t) =\sum_{n=1}^{\infty}C(n)
+\leq  \sum_{n=1}^{\infty}\sum_{\ell=1}^{\infty}\bar{T}_{n}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell). \nonumber
+\end{align}
+
+Set $g(n,\ell)$ to be $\frac{2\sigma \ell}{n^{1/6}}$.
+Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2Wm\lambda\}$, they will correctly identify their best arm.
+Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{2\sigma l}{n^{1/6}} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
+Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms.
+Denote $a_0=\frac{4Wm\sigma}{p^{-1}(\frac{p}{2})}$.
+In order to have $\frac{2\sigma l}{n^{1/6}}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil (a_{0} l)^6 \rceil$.
+In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
+Denote $n_2=\frac{2}{p}$.
+Thus, we know we can only incur regret for sample paths $\omega$ in the $\ell^{th}$ envelope in the first $\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}$ rounds.
+
+Thus,
+\begin{align}
+\sum_{t=1}^{\infty}c(t)\leq\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\bar{c}(n,\ell)\mathbbm{1}\{\omega\in L[\ell]\}\bar{T}_{n}. \nonumber
+\end{align}
+
+Therefore,
+
+\begin{align}
+&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
+\leq &\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\bar{c}(n,\omega)P(\omega \in L(\ell))E[\bar{T}_{n}] \nonumber \\
+=&\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+2Wm\frac{2\sigma \ell}{n^{1/6}}\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
+\leq &\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[\ell])E[\bar{T}_{n}]. \nonumber
+\end{align}
+
+\noindent\textbf{Step 4: Bound $P(\omega\in L(\ell))$}.
+
+We now bound $P(\omega\in L[\ell])$ for $n\geq n_0$ and $\ell\geq 2$. As a reminder, we omit the dependency between $\epsilon_{i,t}^{j}$, $n$ and $\omega$. We know 
+\begin{align}
+&P(\omega\in L[\ell]) \nonumber \\
+=&P(\omega\in L^{'}[\ell])- P(\omega\in L^{'}[\ell-1]) \nonumber \\
+\leq & 1-P\left(|\epsilon_{i,t}^{j}|<\frac{2\sigma (\ell-1)}{n^{1/6}}, \forall i,j\right) \nonumber \\
+=&P\left(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (\ell-1)}{n^{1/6}}\right) \nonumber  \\
+\leq &\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (\ell-1)}{n^{1/6}}\right) \nonumber
+\end{align}
+
+Define $S_{i,t}^{j}=\frac{N(i,t)\epsilon_{i,t}^{j}}{2\sigma}$, then we know $S_{i,t}^{j}$ is a summation of $1/2$ gaussian random numbers. Therefore,
+
+\begin{align}
+&\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma(\ell-1)}{n^{1/6}}\right) \nonumber \\ 
+=&\sum_{i,j}P\left(|S_{i,t}^{j}|\geq \frac{N(i,t)(\ell-1)}{n^{1/6}}\right) \nonumber \\
+\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(\ell-1)). \nonumber
+\end{align}
+
+Based on Lemma~\ref{lemma:cal2}, we know
+\begin{align}
+&N(i,t)^{5/6}(\ell-1) \nonumber \\
+=& 0.9N(i,t)^{5/6} + N(i,t)^{5/6}(\ell-1.9) \nonumber \\
+\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)} + \sqrt{(\ell-1.9)^2 N(i,t)} \nonumber \\
+\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+(\ell-1.9)^2 N(i,t)}. \nonumber
+\end{align}
+
+Based on Lemma~\ref{ACI-inequality}, we know
+\begin{align}
+& P(\omega\in L(\ell) \nonumber \\
+\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(\ell-1)) \nonumber \\
+\leq & \sum_{i,j}24e^{-1.8(\ell-1.9)^2} = 24Nme^{-1.8(\ell-1.9)^2}. \nonumber
+\end{align}
+
+\noindent\textbf{Step 5: Final Step}
+
+Thus,
+\begin{align}
+&\sum_{t=1}^{\infty}c(t) \nonumber \\
+\leq&\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
+\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(\omega\in L[1])E[\bar{T}_{n}] +\sum_{l=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
+\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]E[\bar{T}_{n}] +\sum_{\ell=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]24Nme^{-1.8(\ell-1.9)^2}E[\bar{T}_{n}]\nonumber \\
+\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]Nn +\sum_{\ell=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]24Nme^{-1.8(\ell-1.9)^2}Nn \nonumber \\
+\leq & \left[R+4Wm\sigma \right]N (\max\{n_2,\lceil (a_0)^6 \rceil\})^2+\sum_{\ell=2}^{\infty}24N^2 m[R+4Wm\ell\sigma](\max\{n_2,\lceil (a_0 \ell)^6 \rceil\})^2 e^{-1.8(\ell-1.9)^2} \nonumber \\
+=& O(N^2). \nonumber
+\end{align}
+
+\end{proof}
+
+\section*{Calculation for Equation~\eqref{ex:limit}}
+
+In this section, we prove
+
+\vskip 0.2in
+
+\bibliography{reference}
 \end{document}

### 2018-01-25 colt.tex
editted the proof in equation (6)

@@
 
-Denote $d(t)=t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]$.
-Since
-\begin{align}
-d^{'}(t)=\frac{-z_{t,1}^2(2z_{t,2}+3\sqrt{t})-2(z_{t,2}+\sqrt{t})^3}{2(z_{t,1}^2+(z_{t,2}+\sqrt{t})^2)^{3/2}}+1. \nonumber
-\end{align}
-
-and $\lim_{t\rightarrow \infty}d^{'}(t)=2$, we know for $t$ large enough, $d(t)$ is a increasing function in terms of t. Thus, based on the Monotone Convergence Theorem, we have
-
-\begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{\frac{1}{t}} \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber
-\end{align}
-
-Based on our calculation, we know
+Denote $d(t)=t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]$. Based on our calculation (see appendix for details), we know
 
@@
 In this section, we prove
+\begin{align}
+\lim_{t\rightarrow\infty} t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]=\frac{z_{t,1}^2}{2}. \nonumber 
+\end{align}
+
+Denote $w(x)=\sqrt{x}$. Then $w(x+y)=\sqrt{x} + y\frac{1}{2\sqrt{x}}+O(x^{-3/2})$. Thus, we know
+
+\begin{align}
+&\lim_{t\rightarrow\infty} t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right] \nonumber \\
+=& \lim_{t\rightarrow\infty} t\left[\frac{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}-\sqrt{t}-z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]  \nonumber \\
+= & \lim_{t\rightarrow\infty} t\left[\frac{\sqrt{t}+z_{t,2}+z_{t,1}^{2}\frac{1}{2\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}+O((z_{t,1}^2+(\sqrt{t}+z_{t,2})^2)^{-3/2})-\sqrt{t}-z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]  \nonumber \\
+= & \lim_{t\rightarrow\infty} t \times \frac{z_{t,1}^2}{2(z_{t,1}^2+(\sqrt{t}+z_{t,2})^2)} \rightarrow \frac{z_{t,1}^2}{2}. \nonumber 
+\end{align}
+
+Therefore, we know Equation~\eqref{ex:limit} holds true.
 

### 2018-01-26 colt.tex
editted the proof in equation (6)
fixing double defs of argmax
Fixing compile errors
used the original jmlr2e.sty
added the 2by2 table into the introduction

@@
 \usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+%\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
 \usepackage{xr} 
@@
 \usepackage{microtype}      % microtypography
-\usepackage{amsthm}
+%\usepackage{amsthm}
 \usepackage{comment}
@@
 \usepackage{float}
-\newcommand{\CTB}{CTB} % This is the acronym for our CTB algorithm
-\newcommand{\CTBone}{CTB$-1$} % This is the acronym for our Bayes CTB algorithm
-\newcommand{\CTBtwo}{CTB$-2$} % This is the acronym for our Bayes CTB algorithm
-\newcommand{\CTBthree}{CTB$-3$}
+\usepackage{bbm}
+
 \newcommand{\argmax}{\mathop{\mathrm{argmax}}}
@@
 
-\newcommand{\argmax}{\mathop{\mathrm{argmax}}}
-
 \newcommand{\bccomment}[1]{{\color{blue}BC: #1}}
@@
 \newtheorem{assumption}{Assumption}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
 
@@
 \section{Introduction}
+
+Here we pursue an alternate direction to our analysis of incentivizing exploration with heterogeneous preferences: we consider approximation-style results comparing achievable algorithm performance across four different problem settings, described in the table below.
+
+\begin{center}
+\begin{tabular}{ c|c|c| } 
+ \hline
+     & Pulls arms directly & Needs to incentivize \\ 
+\hline
+ Perfect Info on Preferences & $C11$: The ``God'' Policy & $C12$ \\ 
+ Partial Info on Preferences & $C21$ & $C22$: actual algorithm \\ 
+ \hline
+\end{tabular}
+\end{center}
+
+Columns indicate whether the principal pulls arms directly (left column) or incentivizes agents who in turn actually pull the arms.
+Rows indicate whether the principal knows the preferences of the agents (top row) or not (bottom row).
+Problem settings correspond to cells and are described by the names C11, C12, and so on.
+An optimal algorithm for problem setting C11 has the best performance possible.
+
+We wish to make two high-level points through this analysis:
+
+\begin{itemize}
+\item First, better performance is possible in setting C22 than in setting C21, in the sense we can find tight approximation guarantees relative to C11 that are better for C22 than for C21.
+This is achieved by setting up incentives in C22 that still allow agents to select arms aligned with their preferences, providing selections of arms that contain more information than in C21.
+\item Second, heterogeneity in preferences improves performance over what can be achieved in a setting with homogeneous preferences.
+This would be in the spirit of David K.'s results that heterogeneity in preference for money can be exploited to reduce the budget required.
+\end{itemize}
+
 In this paper, we study incentivizing exploration with heterogeneous agent preferences.

### 2018-01-26 algorithm.tex
divide the paper into sections

--- 2018-01-24 colt.tex
@@
-\documentclass[twoside,11pt]{article}
-\usepackage{jmlr2e}
-
-% Any additional packages needed should be included after jmlr2e.
-% Note that jmlr2e.sty includes epsfig, amssymb, natbib and graphicx,
-% and defines many common macros, such as 'proof' and 'example'.
-%
-% It also sets the bibliographystyle to plainnat; for more information on
-% natbib citation styles, see the natbib documentation, a copy of which
-% is archived at http://www.jmlr.org/format/natbib.pdf
-
-\usepackage[]{algorithm}
-\usepackage[]{algorithmic}
-
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{xr} 
-\usepackage{url}            % simple URL typesetting
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{amsthm}
-\usepackage{comment}
-\usepackage{subcaption}
-\usepackage{xcolor}
-\usepackage{amsmath}
-\usepackage{float}
-\newcommand{\CTB}{CTB} % This is the acronym for our CTB algorithm
-\newcommand{\CTBone}{CTB$-1$} % This is the acronym for our Bayes CTB algorithm
-\newcommand{\CTBtwo}{CTB$-2$} % This is the acronym for our Bayes CTB algorithm
-\newcommand{\CTBthree}{CTB$-3$}
-\newcommand{\argmax}{\mathop{\mathrm{argmax}}}
-\usepackage{mathtools}
-
-\newcommand\floor[1]{\lfloor#1\rfloor}
-\newcommand\ceil[1]{\lceil#1\rceil}
-
-\newcommand{\argmax}{\mathop{\mathrm{argmax}}}
-
-\newcommand{\bccomment}[1]{{\color{blue}BC: #1}}
-\newcommand{\pfcomment}[1]{{\color{blue}PF: #1}}
-
-\newtheorem{assumption}{Assumption}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-
-% Definitions of handy macros can go here
-
-\newcommand{\dataset}{{\cal D}}
-\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
-
-% Heading arguments are {volume}{year}{pages}{date submitted}{date published}{paper id}{author-full-names}
-
-\jmlrheading{1}{2000}{1-48}{4/00}{10/00}{meila00a}{Marina Meil\u{a} and Michael I. Jordan}
-
-% Short headings should be running head and authors last names
-
-\ShortHeadings{Incentivizing Exploration with Heterogeneous Utilities}{Chen, Frazier and Kempe}
-\firstpageno{1}
-
-\begin{document}
-
-\title{Incentivizing Exploration with Heterogeneous Utilities}
-
-\author{\name Bangrui Chen \email bc496@cornell.edu \\
-\name Peter I.\ Frazier \email pf98@cornell.edu \\
-\addr Operations Research and Information Engineering\\
-Cornell University\\
-New York, NY 14850, USA
-\AND
-\name David Kempe \email david.m.kempe@gmail.com  \\
-\addr Department of Computer Science\\
-University of Southern California\\
-Los Angeles, CA 90089, USA}
-
-\editor{}
-
-\maketitle
-
-\begin{abstract}
-sdafsd
-\end{abstract}
-
-\begin{keywords}
-Incentivizing Exploration
-\end{keywords}
-
-\section{Introduction}
-In this paper, we study incentivizing exploration with heterogeneous agent preferences.
-In this problem,   
-arms have unknown multivariate attributes, and agents have heterogeneous linear utility functions that map these attribute vectors onto utilities.
-Agents see noisy observations of attributes of arms pulled by all previous agents, and estimate an arms' attribute vector by the simple average of these observations.
-Agents are selfish, and pull the arm with the largest estimated utility summed with an optional arm-specific incentivizing payment chosen by the principle.
-We study strategies for choosing such incentive payments that seek to maximize the total utility derived by agents, subject to a limitation on the total incentive payment.
-To accomplish this goal, a strategy must induce sufficient exploration to reveal arms' attributes, while still letting agents select myopically and according to their preferences sufficiently often that high-utility arms are chosen and incentive payments are kept small.
-
-Our problem setting models online review aggregators like Amazon, Yelp, and Tripadvisor that host crowdsourced reviews.
-Users of these websites wish to use the reviews hosted there to choose the product / restaurant / vacation (generically referred to as an ``item'') that is best according to their preferences.
-These reviews provide not just cardinal feedback, but also a description of items' attributes that a user may consider together with their personal preferences to select their preferred item.
-An item with few reviews might have inaccurate attribute estimates, leading users to avoid it even though it may actually be their best choice.
-Without incentives, this situation may persist and decrease welfare for the platform's user base.
-By offering incentives, either through price reductions by Amazon or coupons from Yelp or Tripadvisor, a platform may induce more reviews of unexplored items and provide more value over the long term.
-
-Our problem setting also applies to crowd science platforms like eBird \cite{frazier2014incentivizing, sullivan2009ebird}.
-EBird guides birding enthusiasts through a website to explore and report their findings to the birding community.
-Each user report contains information about when, where and how they go birding and what birds they see and hear.
-EBird may wish to incentivize enthusiasts to explore less-explored birding locations and provide more accurate reports on these locations.
-Each enthusiast may have different preference over a location's attributes such as the diversity of bird species, weather, distance and safety.
-By offering enthusiasts incentivies to explore, eBird can create a more accurate body of reports and provide better value to the birding community.
-
-% Something interesting to study would be to alter the search rankings to influence people
-% Also which items to spam people about reviewing
-
-In this problem context, we study a simple policy that usually exploits, incentivizing agents to pull an arm only when the set of agent utility functions that would pull this arm without incentives has probability below a time-varying threshold.
-In our paper, we assume all arms are some agents' best arm.
-Under this assumption, we prove that with $O(N^2)$ payment budget, this policy has $O(N^2+M(\log(T))^2)$ cumulative expected regret where $M$ is an upper bound on the limiting marginal probability density of agent utilities that are nearly indifferent between their best and the second best arm.
-If all agents' utility difference between their best and second best arm is bounded below by a positive number, which typically happens when the agent utility distribution is discrete, this policy achieve constant cumulative expected regret $O(N^2)$.
-The key difference between our problem setting and both the homogenous preference setting and the traditional multi-armed bandits setting is that we must incentivize agents to try suboptimal arms much less often, since all arms are some agents' best arm.
-Essentially, heterogeneity provides free exploration.
-These results suggest that heterogeneous agent preferences reduce but do not eliminate the need to incentive exploration, in relation to single-preference settings.
-
-We broadly categorize the relevant previous literature into two categories based on whether there is money transfer.
-With money transfer, \cite{frazier2014incentivizing} considers a problem setting where the principal pays agents money to explore.
-This work assumes all agents have equal value for money and provide a complete characterization of achievable reward with a fixed budget.
-\cite{han2015incentivizing} generalizes this framework to include agents with heterogeneous value for money, and to allow an external signal to provide partial information about this valuation.
-Under this setting, this work proves a bound on achievable reward as a function of the budget and the signal scheme.
-
-Without money transfer but using information asymmetry, \cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time.
-\cite{mansour2015bayesian} generalizes \cite{kremer2014implementing} by allowing a finite number of actions at each time.
-\cite{mansour2016bayesian} considers a problem setting where there are multiple agents at each time and agents may interact with each other.
-In these papers, the principal provides each agent a recommendation at each time that is Bayesian incentive-compatible.
-They prove the principal can achieve constant regret when utilities are deterministic and logarithmic regret when utilities are stochastic.
-
-We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+M(\log(T))^2)$ regret with $O(N^2)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
-
-\section{Problem Setting}
-\label{sec:prob}
-
-We have $N$ arms. Arm $i$ has a fixed but unknown attribute vector $u_i\in \mathbb{R}^{m}$. 
-A stream of myopic selfish agents come to our system.
-Agent $t$ has linear preferences over attributes described by a vector $\theta_t \in \mathbb{R}^m$ that is unknown to the principal and drawn i.i.d.
-from a known distribution $F(\cdot)$ with compact support.
-We refer synonomously to an agent and that agent's preference vector: when we say ``an agent $\theta$'', we mean ``an agent with preference vector $\theta$.''
-
-Each agent $t$ chooses an arm to pull $A_t$, according to a process described below, and obtains utility $\theta_t \cdot u_{A_{t}}$.
-The principal and all agents then see a noisy observation of the attribute vector of the pulled arm of the form $O_t=u_{A_{t}}+\epsilon_{t}$, where $\epsilon_t\sim N(0, \sigma^2 I_{m})$ is independent normally distributed noise, and $I_m$ denotes an $m$-dimensional identity matrix.
-Although we assume a common variance across attributes for simplicity of presentation, our theoretical results hold if the variance differs.
-
-At each time $t$, for each arm $i$, we (the principal) offer a non-negative payment $c_{i,t}\geq 0$ based on previous observations.
-We assume that agent $t$ chooses to pull the arm that myopically maximizes the sum of this payment and an estimate of the utility obtained $\theta_t \cdot u_{i,t}$ where $u_{i,t}$ denotes the simple average of $O_s$ over all previous pulls of arm $i$.
-In this paper, we assume all arms have been pulled once at time $t=0$ and $u_{i,0}$ denotes a random draw from the arm attribute vector.
-For $t>0$, denote $u_{i,t} = \frac{\sum_{s<t} O_s 1\{A_s = i\} + u_{i,0}}{\sum_{s<t} 1\{A_s = i\}+1}$ and $A_t=\argmax_{i}\{\theta_t\cdot u_{i,t}+c_{i,t}\}$, breaking ties in favor of the arm with the highest incentive.
-We use $c_t=c_{A_{t},t}$ to denote the actual incentive payment at time $t$.
-
-This behavior may be recovered if agents are Bayesian and share a common non-informative prior distribution that is constant over $\mathbb{R}^m$ and know $\sigma^2$.
-In this case, the posterior distribution on $u_{i}$ at time $t$ is multivariate normal with mean $u_{i,t}$, and the expected value of $\theta_t \cdot u_i$ under this posterior conditioned on $\theta_t$ is $\theta_t \cdot u_{i,t}$ (see equation $2.13$ in section $2.5$, \cite{Ge04}).
-Alternatively, one may simply take our assumption that agents use the average as their estimate of an attribute value directly without such a Bayesian justification.
-
-We define the regret at time $t$ as $r(t)=\max_{i}\{\theta_{t}\cdot u_{i}\}-\theta_t\cdot u_{A_t}$, and the cumulative regret up to time T as $R(T)=\sum_{t=1}^{T}r(t)$.
-Define the cumulative payment up to time T similarly as $C(t)=\sum_{t=1}^{T}c(t)$.
-As the principal, we want to find a strategy $\mathcal{A}$ under which both the cumulative expected regret $\mathbb{E}_{\mathcal{A}}[R(T)]$ and the cumulative expected payment $\mathbb{E}_{\mathcal{A}}[C(T)]$ are small.
-
-To support later development, we define some additional notation.
-We let $B(\theta)$ and $\hat{B}(\theta)$ refer to the index of the arm that is best and second best for an agent with preference vector $\theta$, $B(\theta) \in \argmax_i \theta \cdot u_i$ and $\hat{B}(\theta)=\argmax_{i\neq B(\theta)}\theta\cdot u_{i}$, breaking ties uniformly at random.
-We let $N(i,t)$ denote the number of pulls of arm $i$ at times up to and including $t$ plus $1$ (because of the initial pull), i.e.
-$N(i,t)=\sum_{s<t} 1\{A_s = i\}+1$.
-We call time $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$ the {\it starting point of the $n^{th}$ round}. We call the set of times $[t_{n}, t_{n+1})$ the {\it $n^{th}$ round}.
-
 \section{Algorithm and Upper Bound}
@@
 The same proof would work and we can get the exact same results as Algorithm~\ref{Alg1}.
-
-\section{Lower Bound $\Omega(\log(T))$}
-\label{sec:lb}
-
-In this section, we assume $\theta$ follows a continuous distribution $F(\cdot)$.
-We provide an example to show the best possible lower bound is $\Omega(\log(T))$ regardless of the incentivizing strategy.
-
-Suppose we have two arms.
-Arm $1$ has attribute vector $(0,0)$ and arm $2$ has attribute vector $(0,1)$.
-We assume the users' preference are uniformly distributed on the unit circle.
-If the user knows the exact attribute vectors for both arms, then the users with preference on the bottom half circle will choose arm $1$ and the users with preference on the top half circle will choose arm $2$.
-
-Consider the following algorithm: at each step, let the agents play myopically; however, they are going to see the noisy rewards for both arms.
-
-To lower bound the regret, we assume that the agents already know the true attribute vector for arm $1$.
-Without loss of generality, denote $u_{2,t} = (0,1)+(z_{t,1},z_{t,2}) = (0,1)+ (N(0,1/t),N(0,1/t))$ to be the estimate attribute vector for arm $2$ (Without loss of generality, we assume the variance for the noise is $1$).
-
-Since $(z_{t,1}, z_{t,2})$ is symmetric around $(0,0)$, we know
-
-\begin{align}
-&E[r(t)] \nonumber \\
-= &E[r(t) | z_{t,1}>0,z_{t,2}>0] \times P(z_{t,1}>0,z_{t,2}>0) + E[r(t) |z_{t,1}>0,z_{t,2}<0] \times P(z_{t,1}>0,z_{t,2}<0) \nonumber \\
-&+E[r(t) | z_{t,1}<0,z_{t,2}>0] \times P(z_{t,1}<0,z_{n,2}>0) + E[r(t) |z_{t,1}<0,z_{t,2}<0] \times P(z_{t,1}<0,z_{t,2}<0) \nonumber \\
-\geq & 0.25 \times E[r(t) | z_{t,1}>0, z_{t,2}>0]. \nonumber
-\end{align}
-
-Given $z_{t,1}>0$ and $z_{t,2}>0$, we know users whose preference vector between $(-1,0)$ and $\left(\frac{-1-z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ as well as users whose preference vector between $(1,0)$ and $\left(\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{-z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ will make a mistake.
-The regret is the absolute value of the second coordinate of the user's preference vector.
-Thus, we know
-
-\begin{align}
-&E[r(t)| z_{t,1}>0, z_{t,2}>0] \nonumber \\
-=& 4\times 2 \int_{0}^{\infty} \int_{0}^{\infty} \int_{0}^{\arctan\left(\frac{z_{t,1}}{1+z_{t,2}}\right)}\frac{\sin(\theta)}{2\pi}d(\theta)\frac{e^{-\frac{t \times z_{t,1}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,1})\frac{e^{-\frac{t \times z_{t,2}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,2}) \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}t\times \left[1-\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right]e^{-\frac{t \times z_{t,1}^2}{2}}e^{-\frac{t \times z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty} \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber
-\end{align}
-
-Below, we want to show 
-\begin{align}
-\lim_{t\rightarrow\infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{\frac{1}{t}} = O(1), \nonumber
-\end{align}
-and use the fact that $\sum_{n=1}^{T}\frac{1}{n}=O(\log(T))$ to show the regret is at least $\Omega(\log(T))$.
-
-Denote $d(t)=t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]$.
-Since
-\begin{align}
-d^{'}(t)=\frac{-z_{t,1}^2(2z_{t,2}+3\sqrt{t})-2(z_{t,2}+\sqrt{t})^3}{2(z_{t,1}^2+(z_{t,2}+\sqrt{t})^2)^{3/2}}+1. \nonumber
-\end{align}
-
-and $\lim_{t\rightarrow \infty}d^{'}(t)=2$, we know for $t$ large enough, $d(t)$ is a increasing function in terms of t. Thus, based on the Monotone Convergence Theorem, we have
-
-\begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{\frac{1}{t}} \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber
-\end{align}
-
-Based on our calculation, we know
-
-\begin{align}
-\lim_{t\rightarrow \infty} d(t)=\frac{z_{t,1}^2}{2}. \label{ex:limit}
-\end{align}
-Thus,
-\begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{\frac{1}{t}} \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber  \\
-=&\frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\left[ \frac{z_{t,1}^2}{2}e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) = \frac{1}{2\pi}. \nonumber
-\end{align}
-
-Thus, the cumulative expected regret is at least $\Omega(\log(T))$.
-
-\section{Conclusion}
-In this paper, we study the incentivizing exploration problem with heterogeneous user preferences, which generalize the problem setting studied by \cite{frazier2014incentivizing} and \cite{han2015incentivizing}.
-We propose a simple policy that mostly exploits and occasionally incentivizing exploration, which can achieve $O(N^2+M(\log(T))^2)$ cumulative expected regret with $O(N^2)$ payment budget.
-
-\newpage
-
-\appendix
-\section*{Proof of Theorem~\ref{rst:budget}}
-
-We also need the following lemma in part of the proof of Theorem~\ref{rst:budget}.
-\begin{lemma}
-For all $n\geq 1$, we have
-\begin{align}
-0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-\label{lemma:cal2}
-\end{lemma}
-\begin{proof}
-\begin{align}
-&0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)} \nonumber \\
-\iff & 0.81 n^{5/3} \geq 0.6n \log(\log_{1.1}(n)+1) \nonumber \\
-\iff &  \frac{81}{60} n^{2/3} \geq  \log(\log_{1.1}(n)+1) \nonumber
-\end{align}
-
-Denote $f(x) = \frac{81}{60}x^{2/3} - \log(\log_{1.1}(x)+1)$.
-It's easy to compute $f^{'}(x)=0$ has a unique solution $x_{0}=e^{2/3w(\frac{20e^{20000/314763}}{27})-\frac{10000}{104921}}$ (here $w(\cdot)$ is the Lambert W-Function) and it is the global minimum.
-Since $f(x_{0})\approx 0.0252 >0$, we know $f(x)>0$ for all $x\geq 1$.
-Thus, our lemma holds true.
-\end{proof}
-
-Now we are ready to prove our first main result, Theorem~\ref{rst:budget}.
-
-\begin{proof}
-
-\noindent\textbf{Step 1: Categorize measurement errors into different radius envelopes}
-
-Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$.
-Denote $\epsilon_{i,t}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,t}$.
-Denote $\omega$ to be a sample path and $n(t,\omega)$ to be the round number for sample path $\omega$ at time $t$.
-For a fixed time $t$, define
-\begin{align}
-L^{'}[\ell](t) = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n(t,\omega),\ell), \forall i,j\}\nonumber
-\end{align}
-where $g(n,\ell)$ is a function which we will define later.
-Define $L[1](t) = L^{'}[1](t)$ and $L[i](t) = L^{'}[i](t)\setminus L^{'}[i-1](t)$ for $i\geq 2$.
-We call $L[\ell](t)$ the $\ell^{th}$ envelope at time $t$.
-We often simplify the notation and use $L[\ell]$ instead of $L[\ell](t)$ without confusion.
-
-In the calculation below, we omit the dependency on $\omega$ when refering to variables $c(t)$, $\epsilon_{i,t}^{j}$ and $t_n$.
-Based on the definition of $L[\ell]$, we know if $\omega\in L[\ell]$, the maximum payment we need to offer at time $t$ is bounded above by
-\begin{align}
-&\max_{i}\theta_t\cdot u_{i,t} - \min_{j}\theta_t\cdot u_{j,t} \nonumber \\
-= &\max_{i}\theta_t\cdot (\epsilon_{i,t}+u_i) - \min_{j}\theta_t\cdot (\epsilon_{j,t}+u_j) \nonumber \\
-\leq &\max_{i}\theta_t\cdot u_i - \min_{j}\theta_t\cdot u_j +\max_{i}\theta_t\cdot \epsilon_{i,t} - \min_{j}\theta_t\cdot \epsilon_{j,t}\nonumber \\
-\leq & R + 2Wmg(n,\ell). \nonumber
-\end{align}
-
-We denote $\bar{c}(n,\ell)=R + 2Wmg(n,\ell)$ as the upper bound of payment for round $n$ if our measurement error lie in the $\ell^{th}$ envelope.
-
-\noindent\textbf{Step 2: Introduce a new stochastic process which bounds the total payment in a round}
-
-Denote $\mathcal{F}_t$ as the filtration up to time $t$. Based on our algorithm, we know
-
-\[ P(\text{play a new arm}|\mathcal{F}_t) =
-  \begin{cases}
-    1       & \quad \text{if we incentivize}\\
-    \sum_{i\notin (V\cup S)} P(\theta \cdot u_{i,t}>\theta\cdot u_{j,t} \forall j\neq i)  & \quad \text{if }  S\setminus V\neq \emptyset 
-  \end{cases} \label{dom_stoc}
-\] 
-\hspace{1cm}$\geq (n-|V|)\times \frac{1}{n}=1-\frac{|V|}{n}$.
-
-Let $(Z_{n,v,m}:m\geq 0)$ be a sequence of independent Bernoulli random variable with success probability $(1-\frac{v}{n})$.
-We will construct an alternative stochastic process for selecting which arm gets played that has the same distribution as the original process, but under which
-\begin{align}
-t_{n+1}-t_{n}\leq \bar{T}_{n}:=\sum_{v=0}^{N-1}\bar{T}_{n,v}, \nonumber 
-\end{align}
-where $\bar{T}_{n,v}:=\inf\{m\geq 0: Z_{n,v,m}=1\}+1$.
-
-The new stochastic process will have the property that whenever $Z_{n,v(n,t),m(n,t)}=1$, we will play a new arm at time t for $t\in [t_{n}, t_{n+1}]$, where $v(n,t)$ is the number of unique arms played in round $n$ strictly before time $t$, and $m(n,t)$ is the number of times we have pulled a previously pulled arm for the current value of $v(n,t)$.
-At time $t$, to determine what arm to pull, calculate \eqref{dom_stoc} and let $q_t$ be the probability computed.
-Note $q_t\geq 1-\frac{v(n,t)}{n}$.
-
-If $Z_{n,v(n,t),m(n,t)}$ is 1, decide to play a new arm.
-Otherwise, draw a second Bernoulli random variable with probability $\frac{q_t-(1-\frac{v(n,t)}{n})}{1-(1-\frac{v(n,t)}{n})}$, and if it is 1, decide to play a new arm, and otherwise decide to play an old arm.
-Note that
-
-\begin{align}
-P(\text{play a new arm}|\mathcal{F}_{t})=\left[1-\frac{v(n,t)}{n}\right]+\left[1-(1-\frac{v(n,t)}{n})\right]\times \frac{q_t-(1-\frac{v(n,t)}{n})}{1-(1-\frac{v(n,t)}{n})}=q_t.
-\end{align}
-
-Since we pull a new arm only when $Z_{n,v(n,t),m(n,t)}=1$, the number of times we pull an arm when $v(n,t)=v$ is bounded above by $\bar{T}_{n,v}$. Thus,
-
-\begin{align}
-t_{n+1}-t_{n}\leq \sum_{v=0}^{n-1}\bar{T}_{n,v}=\bar{T}_{n}.
-\end{align}
-Finally, we want to bound $\sum_{t}E[c(t)]$. Let $C(n)$ be the cost incurred in round $n$. Thus $\sum_{t}E[c(t)]=\sum_{n}E[C(n)]$. We know
-\begin{align}
-C(n)&=\sum_{t=t_n}^{t_{n+1}-1}c(t)=\sum_{t=t_{n}}^{t_{n+1}-1}\sum_{\ell}\mathbbm{1}\{\omega\in L(\ell)\}c(t) \nonumber \\
-&\leq \sum_{t=t_{n}}^{t_{n+1}-1}\sum_{l}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell) \nonumber \\
-&\leq (t_{n+1}-t_{n})\sum_{\ell} \mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell) \nonumber \\
-&\leq \bar{T}_{n}\sum_{l}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell). \nonumber
-\end{align}
-
-Since $\bar{T}_{n}$ is independent of $\omega$, we know
-
-\begin{align}
-E[C(n)]\leq E[\bar{T}_{n}]\sum_{\ell}P(\omega\in L(\ell))\bar{c}(n,\omega). \nonumber
-\end{align}
-
-\noindent\textbf{Step 3: Rewrite the total payment expression}.
-
-Based on the above notations, we can rewrite the cumulative payment as follows:
-\begin{align}
-\sum_{t=1}^{\infty}c(t) =\sum_{n=1}^{\infty}C(n)
-\leq  \sum_{n=1}^{\infty}\sum_{\ell=1}^{\infty}\bar{T}_{n}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell). \nonumber
-\end{align}
-
-Set $g(n,\ell)$ to be $\frac{2\sigma \ell}{n^{1/6}}$.
-Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2Wm\lambda\}$, they will correctly identify their best arm.
-Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{2\sigma l}{n^{1/6}} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
-Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms.
-Denote $a_0=\frac{4Wm\sigma}{p^{-1}(\frac{p}{2})}$.
-In order to have $\frac{2\sigma l}{n^{1/6}}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil (a_{0} l)^6 \rceil$.
-In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
-Denote $n_2=\frac{2}{p}$.
-Thus, we know we can only incur regret for sample paths $\omega$ in the $\ell^{th}$ envelope in the first $\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}$ rounds.
-
-Thus,
-\begin{align}
-\sum_{t=1}^{\infty}c(t)\leq\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\bar{c}(n,\ell)\mathbbm{1}\{\omega\in L[\ell]\}\bar{T}_{n}. \nonumber
-\end{align}
-
-Therefore,
-
-\begin{align}
-&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
-\leq &\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\bar{c}(n,\omega)P(\omega \in L(\ell))E[\bar{T}_{n}] \nonumber \\
-=&\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+2Wm\frac{2\sigma \ell}{n^{1/6}}\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
-\leq &\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[\ell])E[\bar{T}_{n}]. \nonumber
-\end{align}
-
-\noindent\textbf{Step 4: Bound $P(\omega\in L(\ell))$}.
-
-We now bound $P(\omega\in L[\ell])$ for $n\geq n_0$ and $\ell\geq 2$. As a reminder, we omit the dependency between $\epsilon_{i,t}^{j}$, $n$ and $\omega$. We know 
-\begin{align}
-&P(\omega\in L[\ell]) \nonumber \\
-=&P(\omega\in L^{'}[\ell])- P(\omega\in L^{'}[\ell-1]) \nonumber \\
-\leq & 1-P\left(|\epsilon_{i,t}^{j}|<\frac{2\sigma (\ell-1)}{n^{1/6}}, \forall i,j\right) \nonumber \\
-=&P\left(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (\ell-1)}{n^{1/6}}\right) \nonumber  \\
-\leq &\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (\ell-1)}{n^{1/6}}\right) \nonumber
-\end{align}
-
-Define $S_{i,t}^{j}=\frac{N(i,t)\epsilon_{i,t}^{j}}{2\sigma}$, then we know $S_{i,t}^{j}$ is a summation of $1/2$ gaussian random numbers. Therefore,
-
-\begin{align}
-&\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma(\ell-1)}{n^{1/6}}\right) \nonumber \\ 
-=&\sum_{i,j}P\left(|S_{i,t}^{j}|\geq \frac{N(i,t)(\ell-1)}{n^{1/6}}\right) \nonumber \\
-\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(\ell-1)). \nonumber
-\end{align}
-
-Based on Lemma~\ref{lemma:cal2}, we know
-\begin{align}
-&N(i,t)^{5/6}(\ell-1) \nonumber \\
-=& 0.9N(i,t)^{5/6} + N(i,t)^{5/6}(\ell-1.9) \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)} + \sqrt{(\ell-1.9)^2 N(i,t)} \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+(\ell-1.9)^2 N(i,t)}. \nonumber
-\end{align}
-
-Based on Lemma~\ref{ACI-inequality}, we know
-\begin{align}
-& P(\omega\in L(\ell) \nonumber \\
-\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(\ell-1)) \nonumber \\
-\leq & \sum_{i,j}24e^{-1.8(\ell-1.9)^2} = 24Nme^{-1.8(\ell-1.9)^2}. \nonumber
-\end{align}
-
-\noindent\textbf{Step 5: Final Step}
-
-Thus,
-\begin{align}
-&\sum_{t=1}^{\infty}c(t) \nonumber \\
-\leq&\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
-\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(\omega\in L[1])E[\bar{T}_{n}] +\sum_{l=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
-\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]E[\bar{T}_{n}] +\sum_{\ell=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]24Nme^{-1.8(\ell-1.9)^2}E[\bar{T}_{n}]\nonumber \\
-\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]Nn +\sum_{\ell=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]24Nme^{-1.8(\ell-1.9)^2}Nn \nonumber \\
-\leq & \left[R+4Wm\sigma \right]N (\max\{n_2,\lceil (a_0)^6 \rceil\})^2+\sum_{\ell=2}^{\infty}24N^2 m[R+4Wm\ell\sigma](\max\{n_2,\lceil (a_0 \ell)^6 \rceil\})^2 e^{-1.8(\ell-1.9)^2} \nonumber \\
-=& O(N^2). \nonumber
-\end{align}
-
-\end{proof}
-
-\section*{Calculation for Equation~\eqref{ex:limit}}
-
-In this section, we prove
-
-\vskip 0.2in
-
-\bibliography{reference}
-\end{document}

### 2018-01-26 appendix.tex
divide the paper into sections

--- 2018-01-25 colt.tex
@@
-\documentclass[twoside,11pt]{article}
-\usepackage{jmlr2e}
-
-% Any additional packages needed should be included after jmlr2e.
-% Note that jmlr2e.sty includes epsfig, amssymb, natbib and graphicx,
-% and defines many common macros, such as 'proof' and 'example'.
-%
-% It also sets the bibliographystyle to plainnat; for more information on
-% natbib citation styles, see the natbib documentation, a copy of which
-% is archived at http://www.jmlr.org/format/natbib.pdf
-
-\usepackage[]{algorithm}
-\usepackage[]{algorithmic}
-
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{xr} 
-\usepackage{url}            % simple URL typesetting
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{amsthm}
-\usepackage{comment}
-\usepackage{subcaption}
-\usepackage{xcolor}
-\usepackage{amsmath}
-\usepackage{float}
-\newcommand{\CTB}{CTB} % This is the acronym for our CTB algorithm
-\newcommand{\CTBone}{CTB$-1$} % This is the acronym for our Bayes CTB algorithm
-\newcommand{\CTBtwo}{CTB$-2$} % This is the acronym for our Bayes CTB algorithm
-\newcommand{\CTBthree}{CTB$-3$}
-\newcommand{\argmax}{\mathop{\mathrm{argmax}}}
-\usepackage{mathtools}
-
-\newcommand\floor[1]{\lfloor#1\rfloor}
-\newcommand\ceil[1]{\lceil#1\rceil}
-
-\newcommand{\argmax}{\mathop{\mathrm{argmax}}}
-
-\newcommand{\bccomment}[1]{{\color{blue}BC: #1}}
-\newcommand{\pfcomment}[1]{{\color{blue}PF: #1}}
-
-\newtheorem{assumption}{Assumption}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-
-% Definitions of handy macros can go here
-
-\newcommand{\dataset}{{\cal D}}
-\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
-
-% Heading arguments are {volume}{year}{pages}{date submitted}{date published}{paper id}{author-full-names}
-
-\jmlrheading{1}{2000}{1-48}{4/00}{10/00}{meila00a}{Marina Meil\u{a} and Michael I. Jordan}
-
-% Short headings should be running head and authors last names
-
-\ShortHeadings{Incentivizing Exploration with Heterogeneous Utilities}{Chen, Frazier and Kempe}
-\firstpageno{1}
-
-\begin{document}
-
-\title{Incentivizing Exploration with Heterogeneous Utilities}
-
-\author{\name Bangrui Chen \email bc496@cornell.edu \\
-\name Peter I.\ Frazier \email pf98@cornell.edu \\
-\addr Operations Research and Information Engineering\\
-Cornell University\\
-New York, NY 14850, USA
-\AND
-\name David Kempe \email david.m.kempe@gmail.com  \\
-\addr Department of Computer Science\\
-University of Southern California\\
-Los Angeles, CA 90089, USA}
-
-\editor{}
-
-\maketitle
-
-\begin{abstract}
-sdafsd
-\end{abstract}
-
-\begin{keywords}
-Incentivizing Exploration
-\end{keywords}
-
-\section{Introduction}
-In this paper, we study incentivizing exploration with heterogeneous agent preferences.
-In this problem,   
-arms have unknown multivariate attributes, and agents have heterogeneous linear utility functions that map these attribute vectors onto utilities.
-Agents see noisy observations of attributes of arms pulled by all previous agents, and estimate an arms' attribute vector by the simple average of these observations.
-Agents are selfish, and pull the arm with the largest estimated utility summed with an optional arm-specific incentivizing payment chosen by the principle.
-We study strategies for choosing such incentive payments that seek to maximize the total utility derived by agents, subject to a limitation on the total incentive payment.
-To accomplish this goal, a strategy must induce sufficient exploration to reveal arms' attributes, while still letting agents select myopically and according to their preferences sufficiently often that high-utility arms are chosen and incentive payments are kept small.
-
-Our problem setting models online review aggregators like Amazon, Yelp, and Tripadvisor that host crowdsourced reviews.
-Users of these websites wish to use the reviews hosted there to choose the product / restaurant / vacation (generically referred to as an ``item'') that is best according to their preferences.
-These reviews provide not just cardinal feedback, but also a description of items' attributes that a user may consider together with their personal preferences to select their preferred item.
-An item with few reviews might have inaccurate attribute estimates, leading users to avoid it even though it may actually be their best choice.
-Without incentives, this situation may persist and decrease welfare for the platform's user base.
-By offering incentives, either through price reductions by Amazon or coupons from Yelp or Tripadvisor, a platform may induce more reviews of unexplored items and provide more value over the long term.
-
-Our problem setting also applies to crowd science platforms like eBird \cite{frazier2014incentivizing, sullivan2009ebird}.
-EBird guides birding enthusiasts through a website to explore and report their findings to the birding community.
-Each user report contains information about when, where and how they go birding and what birds they see and hear.
-EBird may wish to incentivize enthusiasts to explore less-explored birding locations and provide more accurate reports on these locations.
-Each enthusiast may have different preference over a location's attributes such as the diversity of bird species, weather, distance and safety.
-By offering enthusiasts incentivies to explore, eBird can create a more accurate body of reports and provide better value to the birding community.
-
-% Something interesting to study would be to alter the search rankings to influence people
-% Also which items to spam people about reviewing
-
-In this problem context, we study a simple policy that usually exploits, incentivizing agents to pull an arm only when the set of agent utility functions that would pull this arm without incentives has probability below a time-varying threshold.
-In our paper, we assume all arms are some agents' best arm.
-Under this assumption, we prove that with $O(N^2)$ payment budget, this policy has $O(N^2+M(\log(T))^2)$ cumulative expected regret where $M$ is an upper bound on the limiting marginal probability density of agent utilities that are nearly indifferent between their best and the second best arm.
-If all agents' utility difference between their best and second best arm is bounded below by a positive number, which typically happens when the agent utility distribution is discrete, this policy achieve constant cumulative expected regret $O(N^2)$.
-The key difference between our problem setting and both the homogenous preference setting and the traditional multi-armed bandits setting is that we must incentivize agents to try suboptimal arms much less often, since all arms are some agents' best arm.
-Essentially, heterogeneity provides free exploration.
-These results suggest that heterogeneous agent preferences reduce but do not eliminate the need to incentive exploration, in relation to single-preference settings.
-
-We broadly categorize the relevant previous literature into two categories based on whether there is money transfer.
-With money transfer, \cite{frazier2014incentivizing} considers a problem setting where the principal pays agents money to explore.
-This work assumes all agents have equal value for money and provide a complete characterization of achievable reward with a fixed budget.
-\cite{han2015incentivizing} generalizes this framework to include agents with heterogeneous value for money, and to allow an external signal to provide partial information about this valuation.
-Under this setting, this work proves a bound on achievable reward as a function of the budget and the signal scheme.
-
-Without money transfer but using information asymmetry, \cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time.
-\cite{mansour2015bayesian} generalizes \cite{kremer2014implementing} by allowing a finite number of actions at each time.
-\cite{mansour2016bayesian} considers a problem setting where there are multiple agents at each time and agents may interact with each other.
-In these papers, the principal provides each agent a recommendation at each time that is Bayesian incentive-compatible.
-They prove the principal can achieve constant regret when utilities are deterministic and logarithmic regret when utilities are stochastic.
-
-We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+M(\log(T))^2)$ regret with $O(N^2)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
-
-\section{Problem Setting}
-\label{sec:prob}
-
-We have $N$ arms. Arm $i$ has a fixed but unknown attribute vector $u_i\in \mathbb{R}^{m}$. 
-A stream of myopic selfish agents come to our system.
-Agent $t$ has linear preferences over attributes described by a vector $\theta_t \in \mathbb{R}^m$ that is unknown to the principal and drawn i.i.d.
-from a known distribution $F(\cdot)$ with compact support.
-We refer synonomously to an agent and that agent's preference vector: when we say ``an agent $\theta$'', we mean ``an agent with preference vector $\theta$.''
-
-Each agent $t$ chooses an arm to pull $A_t$, according to a process described below, and obtains utility $\theta_t \cdot u_{A_{t}}$.
-The principal and all agents then see a noisy observation of the attribute vector of the pulled arm of the form $O_t=u_{A_{t}}+\epsilon_{t}$, where $\epsilon_t\sim N(0, \sigma^2 I_{m})$ is independent normally distributed noise, and $I_m$ denotes an $m$-dimensional identity matrix.
-Although we assume a common variance across attributes for simplicity of presentation, our theoretical results hold if the variance differs.
-
-At each time $t$, for each arm $i$, we (the principal) offer a non-negative payment $c_{i,t}\geq 0$ based on previous observations.
-We assume that agent $t$ chooses to pull the arm that myopically maximizes the sum of this payment and an estimate of the utility obtained $\theta_t \cdot u_{i,t}$ where $u_{i,t}$ denotes the simple average of $O_s$ over all previous pulls of arm $i$.
-In this paper, we assume all arms have been pulled once at time $t=0$ and $u_{i,0}$ denotes a random draw from the arm attribute vector.
-For $t>0$, denote $u_{i,t} = \frac{\sum_{s<t} O_s 1\{A_s = i\} + u_{i,0}}{\sum_{s<t} 1\{A_s = i\}+1}$ and $A_t=\argmax_{i}\{\theta_t\cdot u_{i,t}+c_{i,t}\}$, breaking ties in favor of the arm with the highest incentive.
-We use $c_t=c_{A_{t},t}$ to denote the actual incentive payment at time $t$.
-
-This behavior may be recovered if agents are Bayesian and share a common non-informative prior distribution that is constant over $\mathbb{R}^m$ and know $\sigma^2$.
-In this case, the posterior distribution on $u_{i}$ at time $t$ is multivariate normal with mean $u_{i,t}$, and the expected value of $\theta_t \cdot u_i$ under this posterior conditioned on $\theta_t$ is $\theta_t \cdot u_{i,t}$ (see equation $2.13$ in section $2.5$, \cite{Ge04}).
-Alternatively, one may simply take our assumption that agents use the average as their estimate of an attribute value directly without such a Bayesian justification.
-
-We define the regret at time $t$ as $r(t)=\max_{i}\{\theta_{t}\cdot u_{i}\}-\theta_t\cdot u_{A_t}$, and the cumulative regret up to time T as $R(T)=\sum_{t=1}^{T}r(t)$.
-Define the cumulative payment up to time T similarly as $C(t)=\sum_{t=1}^{T}c(t)$.
-As the principal, we want to find a strategy $\mathcal{A}$ under which both the cumulative expected regret $\mathbb{E}_{\mathcal{A}}[R(T)]$ and the cumulative expected payment $\mathbb{E}_{\mathcal{A}}[C(T)]$ are small.
-
-To support later development, we define some additional notation.
-We let $B(\theta)$ and $\hat{B}(\theta)$ refer to the index of the arm that is best and second best for an agent with preference vector $\theta$, $B(\theta) \in \argmax_i \theta \cdot u_i$ and $\hat{B}(\theta)=\argmax_{i\neq B(\theta)}\theta\cdot u_{i}$, breaking ties uniformly at random.
-We let $N(i,t)$ denote the number of pulls of arm $i$ at times up to and including $t$ plus $1$ (because of the initial pull), i.e.
-$N(i,t)=\sum_{s<t} 1\{A_s = i\}+1$.
-We call time $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$ the {\it starting point of the $n^{th}$ round}. We call the set of times $[t_{n}, t_{n+1})$ the {\it $n^{th}$ round}.
-
-\section{Algorithm and Upper Bound}
-\label{sec:ub}
-
-In this section, we propose a simple policy that mostly exploits, and occasionally incentivizes exploration when the probability of an arm would be pulled by all agent types below a time-varying threshold given the current posterior.
-We prove that with the help of heterogeneous preferences, we can get a certain amount of exploration for free via heterogeneity.
-
-\subsection{Our Algorithm}
-Our algorithm incentivizes pulling an arm $i$ at a time $t$ in round $n$ if and only if both of the following criteria are met:
-\begin{itemize}
-\item the probability of pulling arm $i$ would be below $n^{-1}$ without incentives; 
-\item arm $i$ has not been played previously in the current round.
-\end{itemize}
-Ties are broken randomly.  This algorithm does not need to know the horizon $T$ in advance.
-
-If our algorithm decides to incentivize an arm $i$, it uses the ``pay whatever it takes'' strategy in which the payment offered is $\max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$.
-This maximum over $\theta$ is taken over the support of $F$, which we recall is assumed compact.
-(We use this ``pay whatever it takes'' strategy for its simplicity, and in Section~\ref{sec:pi} we provide an alternate and smaller incentive payment that achieves the same payment budget bound and regret bound).
-
-We describe our algorithm in detail as follows:
-
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration}
-\label{Alg1}
-\begin{algorithmic}
-\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
-\FOR{ $t = 1, 2, 3, \cdots$}{
-	\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
-  \IF {$S\setminus V$ is non-empty}
-    \STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
-    \STATE{Pay whatever it takes to incentivize pulling arm $i$, i.e., offer payment 
-    $c_{i,t} = \max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$ and $c_{j,t} = 0$ for $j \ne i$.}
-  \ELSE
-  \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
-  \ENDIF
-  \STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
-  \IF {$n\neq \min_{i}N(i,t)$} 
-  	\STATE $V=\emptyset$
-  \ENDIF
-  \STATE Update the round number, $n = \min_{i} N(i,t)$
-}\ENDFOR
-
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{Assumptions}
-In this section, we state several assumptions assumed by our analysis.  First define
-\begin{align}
-\Omega_{i,j}=\{\theta:B(\theta)=i, \hat{B}(\theta)=j\}, \nonumber 
-\end{align}
-which is the set of agent preferences whose best arm is arm $i$ and second best arm is arm $j$. With this definition, our analysis makes the following assumptions:
-
-\begin{assumption} Let $F_{i,j}(y)$ be the marginal cumulative density function (or cumulative mass function if $F(\cdot)$ is a discrete distribution) of $(u_i-u_j)\cdot\theta$ conditioned on $\theta \in \Omega_{i,j}$.
-We assume $F_{i,j}(y)\leq My$ for all $y\in R^{+}$, $\forall i,j$.
-\label{A1}
-\end{assumption}
-
-As we can see later in our proof, we only need $\max_{i,j}\limsup_{y\rightarrow 0^{+}}\frac{F_{i,j}(y)}{y}$ to be finite.
-Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm.
-
-\begin{assumption} We assume $F$ has a compact support set. Without loss of generality, we assume $\theta\in [0,W]^m$.
-\label{A2}
-\end{assumption}
-
-We use $R = \max_{\theta, i,j} \theta \cdot (u_i - u_j)$ to denote the maximum regret that can be incurred at each time.  Assumption~\ref{A2} shows that $R<\infty$.
-
-\begin{assumption}
-Denote $p=\min_{i}P(\{\theta: B(\theta)=i\})$. We assume $p>0$.
-\label{A3}
-\end{assumption}
-
-Assumption~\ref{A3} means each arm $i$ has a strictly positive proportion of users for which that arm is best.
-
-\subsection{General Results}
-
-In this section, we prove Algorithm~\ref{Alg1} achieves $O(N^2+M(\log(T))^2)$ cumulative regret with $O(N^2)$ payment budget.
-This is stated in the following pair of theorems, which together constitute our main results.
-
-\begin{theorem}
-The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$. 
-\label{rst:budget}
-\end{theorem}
-
-\begin{theorem}
-The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2 m + M m^2(\log(T))^2)$.
-\label{rst:regret}
-\end{theorem}
-
-Before we prove these two theorems, we must first introduce two additional pieces of notation, which will be used in preliminary lemmas.
-Let $S(\delta)$ be the proportion of users whose utility difference between their best and second best arm is less than $\delta$.
-Formally, $S(\delta)=P(\theta: \theta \cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}\leq \delta)$.
-Then, let $p(\delta)=\min_{i}P(\{\theta:B(\theta)=i,\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$.
-We know $p(0)=p$.
-
-With this additional notation, we now prove several lemmas.
-First, based on Assumption~\ref{A1}, we have the following bound for $S(\delta)$.
-
-\begin{lemma}
-$S(\delta)\leq M\delta$.
-\label{lemma:sdelta}
-\end{lemma}
-
-\begin{proof}
-\begin{align*}
-S(\delta)
-&=\sum_{i,j}P(\theta\cdot(u_{i}-u_{j})\le \delta|\theta\in \Omega_{i,j})P(\theta\in \Omega_{i,j}) \\
-&\leq \sum_{i,j}M\delta \times P(\theta\in \Omega_{i,j}) \\
-&=M\delta.
-\end{align*}
-\end{proof}
-
-The following lemma bounds the probability of making a mistake if we let the agents play myopically in the $n^{th}$ round, given that the utility difference between his/her best and second best arm is bounded below by a constant.
-
-\begin{lemma}
-Define $\tau$ to be any stopping time that is almost surely between $t_n$ and $t_{n+1}-1$ with respect to the filtration $\mathcal{F}_{t}=\sigma(A_1,\cdots,A_t,c_1,\cdots,c_t,O_1,\cdots,O_t)$, we have
-\begin{align}
-P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{16\sigma^2}\right), \nonumber
-\end{align}
-for $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$.
-\label{round:prob}
-\end{lemma}
-
-We need the following lemma in order to prove Lemma~\ref{round:prob}.
-
-\begin{lemma}
-For $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$, we have
-\begin{align}
-\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-\label{n0-inequality}
-\end{lemma}
-
-\begin{proof}
-First, we observe that
-\begin{align}
-&\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)} \nonumber \\
-\iff &\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{9.6\sigma^2}{\lambda^2}. \nonumber 
-\end{align}
-Since $\log(x)\leq x-1$ for $x>0$, we know 
-\begin{align}
-\log(\log_{1.1}(n)+1)=\log\left(\frac{\log(n)}{\log(1.1)}+1\right)\leq \log(11\log(n)+1)\leq \log(11n)\leq 3+\log(n). \nonumber
-\end{align}
-
-Thus, we know
-\begin{align}
-\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{n}{3+\log(n)}. \nonumber 
-\end{align}
-
-To prove the lemma, we just need to show for $n\geq n_{0}$, we have
-\begin{align}
-\frac{n}{3+\log(n)}\geq \frac{9.6\sigma^2}{\lambda^2}. \label{n0-equ}
-\end{align}
-Inequality~(\ref{n0-equ}) is true because of the following two observations:
-\begin{itemize}
-\item for $n\geq 50$, we have $\frac{n}{3+\log(n)}\geq n^{0.5}$;
-\item for $n\geq \frac{92.16\sigma^4}{\lambda^4}$, we have $n^{0.5}\geq {9.6\sigma^{2}}{\lambda^{2}}$.
-\end{itemize}
-
-Thus, we know our lemma is true.
-
-\end{proof}
-
-To prove Lemma~\ref{round:prob}, we also need to use an adaptive concentration inequality due to \cite{zhao2016adaptive}. For reference, we state it here as a Lemma.
-
-\begin{lemma}[Corollary 1 in \cite{zhao2016adaptive}]
-Let $X_{i}$ be zero mean $1/2$-subgaussian random variables.
-$\{S_{n}=\sum_{i=1}^{n}X_{i},n\geq 1\}$ be a random walk.
-Let $J$ be any stopping time with respect to $\{X_1,X_2,\cdots\}$.
-We allow $J$ to take the value of $\infty$ where $P(J=\infty)=1-\lim_{n\rightarrow \infty}P(J\leq n)$.
-If
-\begin{align}
-f(n)=\sqrt{0.6n\log(\log_{1.1}(n)+1)+bn}, \nonumber
-\end{align}
-then
-\begin{align}
-Pr[\{S_{J}\geq f(J)\}\cap \{J<\infty\}]\leq 12e^{-1.8b}. \nonumber
-\end{align}
-\label{ACI-inequality}
-\end{lemma}
-
-We now prove Lemma~\ref{round:prob}.
-
-\begin{proof}[Proof of Lemma~\ref{round:prob}]
-In the $n^{th}$ round, we know all arms have been pulled at least $n$ times.
-For all the agents $\theta$ whose utility difference between their best and second best arm is greater than $2mW\lambda$, denote $K(\theta)=\max_{i\neq B(\theta)}\{\theta\cdot u_{i,t}\}$.
-If $|u_{i,t}^{j}-u_{i}^{j}|\leq \lambda$ for all $i,j$, then
-\begin{align}
-&\theta\cdot(u_{B(\theta),t}-u_{K(\theta),t}) \nonumber \\
-\geq & \theta\cdot(u_{B(\theta),t}-u_{B(\theta)}) + \theta\cdot(u_{K(\theta)}-u_{K(\theta),t}) + \theta\cdot(u_{B(\theta)}-u_{K(\theta)}) \nonumber \\
-> & -Wm\lambda - Wm\lambda + 2Wm\lambda = 0,\nonumber
-\end{align}
-which means their myopic action would incur no regret.
-
-Define $\epsilon_{i,\tau}=u_{i,\tau}-u_i$ and $\epsilon_{i,\tau}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,\tau}$. Thus, we have
-\begin{align}
-&P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\nonumber \\
-\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda |\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda). \label{ACI}
-\end{align}
-
-To bound equation~(\ref{ACI}), we use Lemma~\ref{ACI-inequality}. Define
-\begin{align}
-S_{N(i,\tau)}^{i,j}=\frac{\epsilon_{i,\tau}^{j}}{2\sigma}. \nonumber
-\end{align}
-
-Based on Lemma~\ref{n0-inequality}, for $n_{0}=\max\{50, \frac{92.16\sigma^2}{\lambda^2}\}$ and $n\geq n_{0}$, we have
-\begin{align}
-\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-
-Thus, if we set $b=\frac{n\lambda^2}{16\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,\tau)\geq n\geq n_{0}$, we have
-\begin{align}
-\frac{N(i,\tau)\lambda}{2\sigma}\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)}+\frac{\lambda}{4\sigma}\sqrt{n N(i,\tau)} \nonumber \\
-\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)+bN(i,\tau)}, \nonumber 
-\end{align}
-where the last inequality is because $\sqrt{x}+\sqrt{y}\geq \sqrt{x+y}$. Thus, we have
-\begin{align}
-&P(\epsilon_{i,\tau}^{j}\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P\left(S_{N(i,\tau)}^{i,j}\geq \frac{N(i,\tau)\lambda}{2\sigma}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
-\leq & P\left(S_{N(i,\tau)}^{i,j}\geq \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
-\leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
-\end{align}
-Similarily, we can bound 
-\begin{align}
-&P(\epsilon_{i,\tau}^{j}\leq-\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P(-\epsilon_{i,\tau}^{j}\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber 
-\end{align}
-
-Therefore, we know $P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right)$.
-Thus, we know
-\begin{align}
-&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)  \nonumber \\
-\leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
-\end{align}
-
-\end{proof}
-
-Before we start analyzing the cumulative regret, we first prove the following lemma which bounds the expected length of each round.
-
-\begin{lemma}
-Using our algorithm, we have $\mathbb{E}[t_{n+1}-t_{n}]\leq Nn$, $\forall n\geq 1$.
-\label{round:length}
-\end{lemma}
-
-\begin{proof}
-	A round completes when each arm is pulled at least once in that round.
-Let $X_{i}$ be the number of agents who come to the system between the time after the $(i-1)^{th}$ unique arm was pulled, up to and including the time when the $i^{th}$ unique arm was pulled.
-Then we know
-\begin{equation*}
-\mathbb{E}[t_{n+1}-t_{n}]=\sum_{i=1}^{N}E[X_{i}].
-\end{equation*}
-
-Fix $i$.
-In bounding $X_i$, we think of agents as ``trials'', where each trial can result in a new unique arm being pulled (which we call a ``successful'' trial), or not.
-There are two ways a trial can be successful:
-\begin{itemize}
-\item If there is at least one arm that has not been pulled and the probability of an agent utility function that would pull this arm without incentives is less than $n^{-1}$, then the principal will offer an incentive that causes this arm to be pulled (or one of these arms if there is more than one).
-In this case, the probability that the trial is succesful is $1$.
-\item The probability of an agent utility function that would pull each un-pulled arm without incentives is at least $n^{-1}$.
-In this case, the probability that the trial is successful is at least $n^{-1}$.
-\end{itemize}
-
-Thus, $X_{i}$ is stochastically dominated below by a geometric random variable with success probability $n^{-1}$, the expected number of trials up to and including the first success, $E[X_i]$, is bounded above by $n$.
-Thus,
-\begin{align}
-E[t_{n+1}-t_{n}]\leq Nn. \nonumber
-\end{align}
-\end{proof}
-
-\begin{lemma}
-The expected number of payments for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$.
-\label{lemma:numP}
-\end{lemma}
-
-\begin{proof}
-If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2mW\lambda\}$, they will correctly identify their best arm.
-Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms.
-In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
-Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$.
-Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).
-
-Define $\tau_{n}^{i}$ to be the first time we pull arm $i$ in the $n^{th}$ round. Then
-\begin{align}
-\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\} =\sum_{n=1}^{\infty}\sum_{i=1}^{N}\mathbbm{1}\{c(\tau_{n}^{i})>0\}. \nonumber
-\end{align}
-
-The cumulative expected number of payments is bounded above by:
-\begin{align}
-&E\left[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}\right] \nonumber \\
-=&\sum_{n=1}^{\infty}\sum_{i=1}^{N}P(c(\tau_{n}^{i})>0) \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}P\left(\exists i,j:|u_{i}^{j}-u_{i,\tau_{n}^{i}}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2Wm}\right)+\sum_{n=1}^{n_1}N \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right) +\sum_{n=1}^{n_1}N \nonumber \\
-\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right)\times N+\sum_{n=1}^{n_1}N \nonumber  \\
-\leq&24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1, \nonumber
-\end{align}
-
-Thus, we know the expected number of payments is bounded above by $O(N^2)$.
-
-\end{proof}
-
-Now we are ready to prove our second main result, Theorem~\ref{rst:regret}.
-
-\begin{proof}
-For regret incurred in the first $n_0$ round, it is bounded above by $\sum_{n=1}^{n_{0}}NRn$.
-
-For regret incurred after the first $n_0$ round, it has two different components: the regret incurred when we let the agents play myopically and the regret incurred when we incentivize the agents.
-Using Lemma~\ref{lemma:numP}, the expected regret incurred when we incentivize the agents is bounded above by: $\left[24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1\right]R$.
-
-For the regret incurred when we let the agents play myopically at time $t\geq t_{n_0}$, it consists of the following two components:
-\begin{itemize}
-\item For those users whose utility difference between their best and the second best arm is greater than $f(t)$: we define a sequence of stopping time $\tau_{n}^{k}$ to be the $k^{th}$ time period in the $n^{th}$ round.
-For $k>t_{n+1}-t_{n}$, we define $\tau_{n}^{k}=\infty$.
-For $\tau_{n}^{k}=t$, the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)\times R$.
-We denote the regret incurred by these agents as $r_1(\tau_{n}^{k})$.
-For $k>t_{n+1}-t_{n}$, we define $r_1(\tau_{n}^{k})=0$.
-\item For those user whose utility difference between their best and the second best arm is smaller than $f(t)$: this happens with probability $S(f(t))$ at each time and regret is bounded above by $S(f(t)) \times f(t)=Mf(t)^2$.
-We denote the regret incurred by these agents as $r_2(t)$.
-\end{itemize}
-
-Thus, the cumulative expected regret incurred up to time $T$ when we let the agent play myopically is bounded above by:
-\begin{align}
-&E\left[\sum_{t=1}^{T}r(t)\right] \nonumber \\
-=&E\left[\sum_{t=1}^{t_{n_{0}}} r(t) + \sum_{t=t_{n_{0}}}^{T}(r_1(t)+r_2(t))\right]  \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}-1}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-=& \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right]. \label{chap5:equ:r1}
-\end{align}
-Since
-\begin{align}
-& E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\right] \nonumber\\
-= &  \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})] \nonumber \\
-= &  \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}(E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty)+E[r_1(\tau_{n}^{k})|\tau_{n}^{k}=\infty]\times P(\tau_{n}^{k}=\infty)) \nonumber \\
-= & \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty), \nonumber
-\end{align}
-
-we have
-\begin{align}
-\eqref{chap5:equ:r1}= & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty) + E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}\left[\sum_{k=1}^{\infty}24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right) R\times P(\tau_{n}^{k}<\infty) \right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R \times Nn+ \sum_{t=1}^{T}Mf(t)^2. \label{chap5:equ:regret}
-\end{align}
-
- Thus the cumulative regret at time $T$ is bounded above by
-\begin{align}
-&\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-+ & 24N^2 m \frac{1}{e^{\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2}}-1}R+N\left(\max\left\{n_{0},\frac{2}{p}\right\}\right)R. \nonumber
-\end{align}
-
-For a fixed $T$, we only need to minimize the following two terms since all others are constant:
-
-\begin{align}
-\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2. \label{equ:regret}
-\end{align}
-
-If we set $f^2(t)=\frac{2\log(T)\times 64W^2 m^2\sigma^2}{1.8t}$, then
-\begin{align}
-&\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\ 
-\leq & \sum_{n=1}^{T} 24N^2 mnR \exp\left(-2\log(T)\right)  + \frac{128W^2 m^2\sigma^2 M\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{n} \nonumber \\
-\leq &  24N^2 m R\frac{T(T-1)}{2T^2}  + 71.12 W^2 m^2\sigma^2 M\log(T)(\log(T)+1) \nonumber \\
-\leq &  12 N^2 m R  + 71.12 W^2 m^2\sigma^2 M\log(T)(\log(T)+1). \nonumber
-\end{align}
-
-Thus, the cumulative expected regret is bounded by $O(N^2 m + M m^2\log(T))$.
-\end{proof}
-
-\begin{corollary}
-If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O(N^2)$.
-\end{corollary}
-
-\begin{proof}
-The proof of this corollary is similar to the proof of Theorem~\ref{rst:regret}.
-If we set $f^2(t)=\frac{2\log(T)\times 64W^2 m^2\sigma^2}{1.8t}$, then there exists a $t_{0}$ such that for $t>t_{0}$, $S(f(t))=0$.
-Thus, similar to equation~\eqref{equ:regret}, we know the cumulative expected regret when we let the agents play myopically is bounded above by
-\begin{align}
-\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{t_{0}}Mf(t)^2 \nonumber
-\end{align}
-Therefore, based on the same analysis of Theorem~\ref{rst:regret}, we know the cumulative regret is bounded by $O(N^2)$.
-\end{proof}
-
-\subsection{Practical Issues}
-\label{sec:pi}
-
-In Algorithm~\ref{Alg1}, we use ``pay whatever it takes'' strategy when we decide to incentivize the agent.
-However, ''pay whatever it takes'' only shows up in the proof of Lemma~\ref{round:length}.
-Without loss of generality, suppose we want to incentivize arm $i$ at time $t$ at the $n^{th}$ round.
-Based on the proof of Lemma~\ref{round:length}, as long as we offer a payment $c_{i,t}$ such that arm $i$ has at least $n^{-1}$ probability being pulled at time $t$, our results still hold true.
-We could compute this $c_{i,t}$ dynamically based on $F(\cdot)$ as well as our current estimate $u_{i,t}$.
-Here is the revised algorithm which would work well in practice:
-
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration}
-\label{Alg2}
-\begin{algorithmic}
-\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
-\FOR{ $t = 1, 2, 3, \cdots$}{
-	\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
-  \IF {$S\setminus V$ is non-empty}
-    \STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
-	\STATE{Offer payment $c_{i,t}=\inf\{c: P(\theta\sim F: \theta\cdot u_{i,t}+c>max_{j}\theta\cdot u_{j,t})>n^{-1}\}$}
-  \ELSE
-  \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
-  \ENDIF
-  \STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
-  \IF {$n\neq \min_{i}N(i,t)$} 
-  	\STATE $V=\emptyset$
-  \ENDIF
-  \STATE Update the round number, $n = \min_{i} N(i,t)$
-}\ENDFOR
-
-\end{algorithmic}
-\end{algorithm}
-
-The same proof would work and we can get the exact same results as Algorithm~\ref{Alg1}.
-
-\section{Lower Bound $\Omega(\log(T))$}
-\label{sec:lb}
-
-In this section, we assume $\theta$ follows a continuous distribution $F(\cdot)$.
-We provide an example to show the best possible lower bound is $\Omega(\log(T))$ regardless of the incentivizing strategy.
-
-Suppose we have two arms.
-Arm $1$ has attribute vector $(0,0)$ and arm $2$ has attribute vector $(0,1)$.
-We assume the users' preference are uniformly distributed on the unit circle.
-If the user knows the exact attribute vectors for both arms, then the users with preference on the bottom half circle will choose arm $1$ and the users with preference on the top half circle will choose arm $2$.
-
-Consider the following algorithm: at each step, let the agents play myopically; however, they are going to see the noisy rewards for both arms.
-
-To lower bound the regret, we assume that the agents already know the true attribute vector for arm $1$.
-Without loss of generality, denote $u_{2,t} = (0,1)+(z_{t,1},z_{t,2}) = (0,1)+ (N(0,1/t),N(0,1/t))$ to be the estimate attribute vector for arm $2$ (Without loss of generality, we assume the variance for the noise is $1$).
-
-Since $(z_{t,1}, z_{t,2})$ is symmetric around $(0,0)$, we know
-
-\begin{align}
-&E[r(t)] \nonumber \\
-= &E[r(t) | z_{t,1}>0,z_{t,2}>0] \times P(z_{t,1}>0,z_{t,2}>0) + E[r(t) |z_{t,1}>0,z_{t,2}<0] \times P(z_{t,1}>0,z_{t,2}<0) \nonumber \\
-&+E[r(t) | z_{t,1}<0,z_{t,2}>0] \times P(z_{t,1}<0,z_{n,2}>0) + E[r(t) |z_{t,1}<0,z_{t,2}<0] \times P(z_{t,1}<0,z_{t,2}<0) \nonumber \\
-\geq & 0.25 \times E[r(t) | z_{t,1}>0, z_{t,2}>0]. \nonumber
-\end{align}
-
-Given $z_{t,1}>0$ and $z_{t,2}>0$, we know users whose preference vector between $(-1,0)$ and $\left(\frac{-1-z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ as well as users whose preference vector between $(1,0)$ and $\left(\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{-z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ will make a mistake.
-The regret is the absolute value of the second coordinate of the user's preference vector.
-Thus, we know
-
-\begin{align}
-&E[r(t)| z_{t,1}>0, z_{t,2}>0] \nonumber \\
-=& 4\times 2 \int_{0}^{\infty} \int_{0}^{\infty} \int_{0}^{\arctan\left(\frac{z_{t,1}}{1+z_{t,2}}\right)}\frac{\sin(\theta)}{2\pi}d(\theta)\frac{e^{-\frac{t \times z_{t,1}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,1})\frac{e^{-\frac{t \times z_{t,2}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,2}) \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}t\times \left[1-\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right]e^{-\frac{t \times z_{t,1}^2}{2}}e^{-\frac{t \times z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty} \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber
-\end{align}
-
-Below, we want to show 
-\begin{align}
-\lim_{t\rightarrow\infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{\frac{1}{t}} = O(1), \nonumber
-\end{align}
-and use the fact that $\sum_{n=1}^{T}\frac{1}{n}=O(\log(T))$ to show the regret is at least $\Omega(\log(T))$.
-
-Denote $d(t)=t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]$. Based on our calculation (see appendix for details), we know
-
-\begin{align}
-\lim_{t\rightarrow \infty} d(t)=\frac{z_{t,1}^2}{2}. \label{ex:limit}
-\end{align}
-Thus,
-\begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{\frac{1}{t}} \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber  \\
-=&\frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\left[ \frac{z_{t,1}^2}{2}e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) = \frac{1}{2\pi}. \nonumber
-\end{align}
-
-Thus, the cumulative expected regret is at least $\Omega(\log(T))$.
-
-\section{Conclusion}
-In this paper, we study the incentivizing exploration problem with heterogeneous user preferences, which generalize the problem setting studied by \cite{frazier2014incentivizing} and \cite{han2015incentivizing}.
-We propose a simple policy that mostly exploits and occasionally incentivizing exploration, which can achieve $O(N^2+M(\log(T))^2)$ cumulative expected regret with $O(N^2)$ payment budget.
-
-\newpage
-
-\appendix
 \section*{Proof of Theorem~\ref{rst:budget}}
@@
             Therefore, we know Equation~\eqref{ex:limit} holds true.
-
-\vskip 0.2in
-
-\bibliography{reference}
-\end{document}

### 2018-01-26 colt.tex
divide the paper into sections

--- 2018-01-24 colt.tex
@@
 
-\section{Introduction}
-In this paper, we study incentivizing exploration with heterogeneous agent preferences.
-In this problem,   
-arms have unknown multivariate attributes, and agents have heterogeneous linear utility functions that map these attribute vectors onto utilities.
-Agents see noisy observations of attributes of arms pulled by all previous agents, and estimate an arms' attribute vector by the simple average of these observations.
-Agents are selfish, and pull the arm with the largest estimated utility summed with an optional arm-specific incentivizing payment chosen by the principle.
-We study strategies for choosing such incentive payments that seek to maximize the total utility derived by agents, subject to a limitation on the total incentive payment.
-To accomplish this goal, a strategy must induce sufficient exploration to reveal arms' attributes, while still letting agents select myopically and according to their preferences sufficiently often that high-utility arms are chosen and incentive payments are kept small.
+\input{introduction.tex}
 
-Our problem setting models online review aggregators like Amazon, Yelp, and Tripadvisor that host crowdsourced reviews.
-Users of these websites wish to use the reviews hosted there to choose the product / restaurant / vacation (generically referred to as an ``item'') that is best according to their preferences.
-These reviews provide not just cardinal feedback, but also a description of items' attributes that a user may consider together with their personal preferences to select their preferred item.
-An item with few reviews might have inaccurate attribute estimates, leading users to avoid it even though it may actually be their best choice.
-Without incentives, this situation may persist and decrease welfare for the platform's user base.
-By offering incentives, either through price reductions by Amazon or coupons from Yelp or Tripadvisor, a platform may induce more reviews of unexplored items and provide more value over the long term.
+\input{problem_setting.tex}
 
-Our problem setting also applies to crowd science platforms like eBird \cite{frazier2014incentivizing, sullivan2009ebird}.
-EBird guides birding enthusiasts through a website to explore and report their findings to the birding community.
-Each user report contains information about when, where and how they go birding and what birds they see and hear.
-EBird may wish to incentivize enthusiasts to explore less-explored birding locations and provide more accurate reports on these locations.
-Each enthusiast may have different preference over a location's attributes such as the diversity of bird species, weather, distance and safety.
-By offering enthusiasts incentivies to explore, eBird can create a more accurate body of reports and provide better value to the birding community.
+\input{algorithm.tex}
 
-% Something interesting to study would be to alter the search rankings to influence people
-% Also which items to spam people about reviewing
+\input{lower_bound.tex}
 
-In this problem context, we study a simple policy that usually exploits, incentivizing agents to pull an arm only when the set of agent utility functions that would pull this arm without incentives has probability below a time-varying threshold.
-In our paper, we assume all arms are some agents' best arm.
-Under this assumption, we prove that with $O(N^2)$ payment budget, this policy has $O(N^2+M(\log(T))^2)$ cumulative expected regret where $M$ is an upper bound on the limiting marginal probability density of agent utilities that are nearly indifferent between their best and the second best arm.
-If all agents' utility difference between their best and second best arm is bounded below by a positive number, which typically happens when the agent utility distribution is discrete, this policy achieve constant cumulative expected regret $O(N^2)$.
-The key difference between our problem setting and both the homogenous preference setting and the traditional multi-armed bandits setting is that we must incentivize agents to try suboptimal arms much less often, since all arms are some agents' best arm.
-Essentially, heterogeneity provides free exploration.
-These results suggest that heterogeneous agent preferences reduce but do not eliminate the need to incentive exploration, in relation to single-preference settings.
-
-We broadly categorize the relevant previous literature into two categories based on whether there is money transfer.
-With money transfer, \cite{frazier2014incentivizing} considers a problem setting where the principal pays agents money to explore.
-This work assumes all agents have equal value for money and provide a complete characterization of achievable reward with a fixed budget.
-\cite{han2015incentivizing} generalizes this framework to include agents with heterogeneous value for money, and to allow an external signal to provide partial information about this valuation.
-Under this setting, this work proves a bound on achievable reward as a function of the budget and the signal scheme.
-
-Without money transfer but using information asymmetry, \cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time.
-\cite{mansour2015bayesian} generalizes \cite{kremer2014implementing} by allowing a finite number of actions at each time.
-\cite{mansour2016bayesian} considers a problem setting where there are multiple agents at each time and agents may interact with each other.
-In these papers, the principal provides each agent a recommendation at each time that is Bayesian incentive-compatible.
-They prove the principal can achieve constant regret when utilities are deterministic and logarithmic regret when utilities are stochastic.
-
-We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+M(\log(T))^2)$ regret with $O(N^2)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
-
-\section{Problem Setting}
-\label{sec:prob}
-
-We have $N$ arms. Arm $i$ has a fixed but unknown attribute vector $u_i\in \mathbb{R}^{m}$. 
-A stream of myopic selfish agents come to our system.
-Agent $t$ has linear preferences over attributes described by a vector $\theta_t \in \mathbb{R}^m$ that is unknown to the principal and drawn i.i.d.
-from a known distribution $F(\cdot)$ with compact support.
-We refer synonomously to an agent and that agent's preference vector: when we say ``an agent $\theta$'', we mean ``an agent with preference vector $\theta$.''
-
-Each agent $t$ chooses an arm to pull $A_t$, according to a process described below, and obtains utility $\theta_t \cdot u_{A_{t}}$.
-The principal and all agents then see a noisy observation of the attribute vector of the pulled arm of the form $O_t=u_{A_{t}}+\epsilon_{t}$, where $\epsilon_t\sim N(0, \sigma^2 I_{m})$ is independent normally distributed noise, and $I_m$ denotes an $m$-dimensional identity matrix.
-Although we assume a common variance across attributes for simplicity of presentation, our theoretical results hold if the variance differs.
-
-At each time $t$, for each arm $i$, we (the principal) offer a non-negative payment $c_{i,t}\geq 0$ based on previous observations.
-We assume that agent $t$ chooses to pull the arm that myopically maximizes the sum of this payment and an estimate of the utility obtained $\theta_t \cdot u_{i,t}$ where $u_{i,t}$ denotes the simple average of $O_s$ over all previous pulls of arm $i$.
-In this paper, we assume all arms have been pulled once at time $t=0$ and $u_{i,0}$ denotes a random draw from the arm attribute vector.
-For $t>0$, denote $u_{i,t} = \frac{\sum_{s<t} O_s 1\{A_s = i\} + u_{i,0}}{\sum_{s<t} 1\{A_s = i\}+1}$ and $A_t=\argmax_{i}\{\theta_t\cdot u_{i,t}+c_{i,t}\}$, breaking ties in favor of the arm with the highest incentive.
-We use $c_t=c_{A_{t},t}$ to denote the actual incentive payment at time $t$.
-
-This behavior may be recovered if agents are Bayesian and share a common non-informative prior distribution that is constant over $\mathbb{R}^m$ and know $\sigma^2$.
-In this case, the posterior distribution on $u_{i}$ at time $t$ is multivariate normal with mean $u_{i,t}$, and the expected value of $\theta_t \cdot u_i$ under this posterior conditioned on $\theta_t$ is $\theta_t \cdot u_{i,t}$ (see equation $2.13$ in section $2.5$, \cite{Ge04}).
-Alternatively, one may simply take our assumption that agents use the average as their estimate of an attribute value directly without such a Bayesian justification.
-
-We define the regret at time $t$ as $r(t)=\max_{i}\{\theta_{t}\cdot u_{i}\}-\theta_t\cdot u_{A_t}$, and the cumulative regret up to time T as $R(T)=\sum_{t=1}^{T}r(t)$.
-Define the cumulative payment up to time T similarly as $C(t)=\sum_{t=1}^{T}c(t)$.
-As the principal, we want to find a strategy $\mathcal{A}$ under which both the cumulative expected regret $\mathbb{E}_{\mathcal{A}}[R(T)]$ and the cumulative expected payment $\mathbb{E}_{\mathcal{A}}[C(T)]$ are small.
-
-To support later development, we define some additional notation.
-We let $B(\theta)$ and $\hat{B}(\theta)$ refer to the index of the arm that is best and second best for an agent with preference vector $\theta$, $B(\theta) \in \argmax_i \theta \cdot u_i$ and $\hat{B}(\theta)=\argmax_{i\neq B(\theta)}\theta\cdot u_{i}$, breaking ties uniformly at random.
-We let $N(i,t)$ denote the number of pulls of arm $i$ at times up to and including $t$ plus $1$ (because of the initial pull), i.e.
-$N(i,t)=\sum_{s<t} 1\{A_s = i\}+1$.
-We call time $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$ the {\it starting point of the $n^{th}$ round}. We call the set of times $[t_{n}, t_{n+1})$ the {\it $n^{th}$ round}.
-
-\section{Algorithm and Upper Bound}
-\label{sec:ub}
-
-In this section, we propose a simple policy that mostly exploits, and occasionally incentivizes exploration when the probability of an arm would be pulled by all agent types below a time-varying threshold given the current posterior.
-We prove that with the help of heterogeneous preferences, we can get a certain amount of exploration for free via heterogeneity.
-
-\subsection{Our Algorithm}
-Our algorithm incentivizes pulling an arm $i$ at a time $t$ in round $n$ if and only if both of the following criteria are met:
-\begin{itemize}
-\item the probability of pulling arm $i$ would be below $n^{-1}$ without incentives; 
-\item arm $i$ has not been played previously in the current round.
-\end{itemize}
-Ties are broken randomly.  This algorithm does not need to know the horizon $T$ in advance.
-
-If our algorithm decides to incentivize an arm $i$, it uses the ``pay whatever it takes'' strategy in which the payment offered is $\max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$.
-This maximum over $\theta$ is taken over the support of $F$, which we recall is assumed compact.
-(We use this ``pay whatever it takes'' strategy for its simplicity, and in Section~\ref{sec:pi} we provide an alternate and smaller incentive payment that achieves the same payment budget bound and regret bound).
-
-We describe our algorithm in detail as follows:
-
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration}
-\label{Alg1}
-\begin{algorithmic}
-\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
-\FOR{ $t = 1, 2, 3, \cdots$}{
-	\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
-  \IF {$S\setminus V$ is non-empty}
-    \STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
-    \STATE{Pay whatever it takes to incentivize pulling arm $i$, i.e., offer payment 
-    $c_{i,t} = \max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$ and $c_{j,t} = 0$ for $j \ne i$.}
-  \ELSE
-  \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
-  \ENDIF
-  \STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
-  \IF {$n\neq \min_{i}N(i,t)$} 
-  	\STATE $V=\emptyset$
-  \ENDIF
-  \STATE Update the round number, $n = \min_{i} N(i,t)$
-}\ENDFOR
-
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{Assumptions}
-In this section, we state several assumptions assumed by our analysis.  First define
-\begin{align}
-\Omega_{i,j}=\{\theta:B(\theta)=i, \hat{B}(\theta)=j\}, \nonumber 
-\end{align}
-which is the set of agent preferences whose best arm is arm $i$ and second best arm is arm $j$. With this definition, our analysis makes the following assumptions:
-
-\begin{assumption} Let $F_{i,j}(y)$ be the marginal cumulative density function (or cumulative mass function if $F(\cdot)$ is a discrete distribution) of $(u_i-u_j)\cdot\theta$ conditioned on $\theta \in \Omega_{i,j}$.
-We assume $F_{i,j}(y)\leq My$ for all $y\in R^{+}$, $\forall i,j$.
-\label{A1}
-\end{assumption}
-
-As we can see later in our proof, we only need $\max_{i,j}\limsup_{y\rightarrow 0^{+}}\frac{F_{i,j}(y)}{y}$ to be finite.
-Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm.
-
-\begin{assumption} We assume $F$ has a compact support set. Without loss of generality, we assume $\theta\in [0,W]^m$.
-\label{A2}
-\end{assumption}
-
-We use $R = \max_{\theta, i,j} \theta \cdot (u_i - u_j)$ to denote the maximum regret that can be incurred at each time.  Assumption~\ref{A2} shows that $R<\infty$.
-
-\begin{assumption}
-Denote $p=\min_{i}P(\{\theta: B(\theta)=i\})$. We assume $p>0$.
-\label{A3}
-\end{assumption}
-
-Assumption~\ref{A3} means each arm $i$ has a strictly positive proportion of users for which that arm is best.
-
-\subsection{General Results}
-
-In this section, we prove Algorithm~\ref{Alg1} achieves $O(N^2+M(\log(T))^2)$ cumulative regret with $O(N^2)$ payment budget.
-This is stated in the following pair of theorems, which together constitute our main results.
-
-\begin{theorem}
-The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$. 
-\label{rst:budget}
-\end{theorem}
-
-\begin{theorem}
-The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2 m + M m^2(\log(T))^2)$.
-\label{rst:regret}
-\end{theorem}
-
-Before we prove these two theorems, we must first introduce two additional pieces of notation, which will be used in preliminary lemmas.
-Let $S(\delta)$ be the proportion of users whose utility difference between their best and second best arm is less than $\delta$.
-Formally, $S(\delta)=P(\theta: \theta \cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}\leq \delta)$.
-Then, let $p(\delta)=\min_{i}P(\{\theta:B(\theta)=i,\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$.
-We know $p(0)=p$.
-
-With this additional notation, we now prove several lemmas.
-First, based on Assumption~\ref{A1}, we have the following bound for $S(\delta)$.
-
-\begin{lemma}
-$S(\delta)\leq M\delta$.
-\label{lemma:sdelta}
-\end{lemma}
-
-\begin{proof}
-\begin{align*}
-S(\delta)
-&=\sum_{i,j}P(\theta\cdot(u_{i}-u_{j})\le \delta|\theta\in \Omega_{i,j})P(\theta\in \Omega_{i,j}) \\
-&\leq \sum_{i,j}M\delta \times P(\theta\in \Omega_{i,j}) \\
-&=M\delta.
-\end{align*}
-\end{proof}
-
-The following lemma bounds the probability of making a mistake if we let the agents play myopically in the $n^{th}$ round, given that the utility difference between his/her best and second best arm is bounded below by a constant.
-
-\begin{lemma}
-Define $\tau$ to be any stopping time that is almost surely between $t_n$ and $t_{n+1}-1$ with respect to the filtration $\mathcal{F}_{t}=\sigma(A_1,\cdots,A_t,c_1,\cdots,c_t,O_1,\cdots,O_t)$, we have
-\begin{align}
-P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{16\sigma^2}\right), \nonumber
-\end{align}
-for $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$.
-\label{round:prob}
-\end{lemma}
-
-We need the following lemma in order to prove Lemma~\ref{round:prob}.
-
-\begin{lemma}
-For $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$, we have
-\begin{align}
-\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-\label{n0-inequality}
-\end{lemma}
-
-\begin{proof}
-First, we observe that
-\begin{align}
-&\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)} \nonumber \\
-\iff &\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{9.6\sigma^2}{\lambda^2}. \nonumber 
-\end{align}
-Since $\log(x)\leq x-1$ for $x>0$, we know 
-\begin{align}
-\log(\log_{1.1}(n)+1)=\log\left(\frac{\log(n)}{\log(1.1)}+1\right)\leq \log(11\log(n)+1)\leq \log(11n)\leq 3+\log(n). \nonumber
-\end{align}
-
-Thus, we know
-\begin{align}
-\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{n}{3+\log(n)}. \nonumber 
-\end{align}
-
-To prove the lemma, we just need to show for $n\geq n_{0}$, we have
-\begin{align}
-\frac{n}{3+\log(n)}\geq \frac{9.6\sigma^2}{\lambda^2}. \label{n0-equ}
-\end{align}
-Inequality~(\ref{n0-equ}) is true because of the following two observations:
-\begin{itemize}
-\item for $n\geq 50$, we have $\frac{n}{3+\log(n)}\geq n^{0.5}$;
-\item for $n\geq \frac{92.16\sigma^4}{\lambda^4}$, we have $n^{0.5}\geq {9.6\sigma^{2}}{\lambda^{2}}$.
-\end{itemize}
-
-Thus, we know our lemma is true.
-
-\end{proof}
-
-To prove Lemma~\ref{round:prob}, we also need to use an adaptive concentration inequality due to \cite{zhao2016adaptive}. For reference, we state it here as a Lemma.
-
-\begin{lemma}[Corollary 1 in \cite{zhao2016adaptive}]
-Let $X_{i}$ be zero mean $1/2$-subgaussian random variables.
-$\{S_{n}=\sum_{i=1}^{n}X_{i},n\geq 1\}$ be a random walk.
-Let $J$ be any stopping time with respect to $\{X_1,X_2,\cdots\}$.
-We allow $J$ to take the value of $\infty$ where $P(J=\infty)=1-\lim_{n\rightarrow \infty}P(J\leq n)$.
-If
-\begin{align}
-f(n)=\sqrt{0.6n\log(\log_{1.1}(n)+1)+bn}, \nonumber
-\end{align}
-then
-\begin{align}
-Pr[\{S_{J}\geq f(J)\}\cap \{J<\infty\}]\leq 12e^{-1.8b}. \nonumber
-\end{align}
-\label{ACI-inequality}
-\end{lemma}
-
-We now prove Lemma~\ref{round:prob}.
-
-\begin{proof}[Proof of Lemma~\ref{round:prob}]
-In the $n^{th}$ round, we know all arms have been pulled at least $n$ times.
-For all the agents $\theta$ whose utility difference between their best and second best arm is greater than $2mW\lambda$, denote $K(\theta)=\max_{i\neq B(\theta)}\{\theta\cdot u_{i,t}\}$.
-If $|u_{i,t}^{j}-u_{i}^{j}|\leq \lambda$ for all $i,j$, then
-\begin{align}
-&\theta\cdot(u_{B(\theta),t}-u_{K(\theta),t}) \nonumber \\
-\geq & \theta\cdot(u_{B(\theta),t}-u_{B(\theta)}) + \theta\cdot(u_{K(\theta)}-u_{K(\theta),t}) + \theta\cdot(u_{B(\theta)}-u_{K(\theta)}) \nonumber \\
-> & -Wm\lambda - Wm\lambda + 2Wm\lambda = 0,\nonumber
-\end{align}
-which means their myopic action would incur no regret.
-
-Define $\epsilon_{i,\tau}=u_{i,\tau}-u_i$ and $\epsilon_{i,\tau}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,\tau}$. Thus, we have
-\begin{align}
-&P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\nonumber \\
-\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda |\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda). \label{ACI}
-\end{align}
-
-To bound equation~(\ref{ACI}), we use Lemma~\ref{ACI-inequality}. Define
-\begin{align}
-S_{N(i,\tau)}^{i,j}=\frac{\epsilon_{i,\tau}^{j}}{2\sigma}. \nonumber
-\end{align}
-
-Based on Lemma~\ref{n0-inequality}, for $n_{0}=\max\{50, \frac{92.16\sigma^2}{\lambda^2}\}$ and $n\geq n_{0}$, we have
-\begin{align}
-\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-
-Thus, if we set $b=\frac{n\lambda^2}{16\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,\tau)\geq n\geq n_{0}$, we have
-\begin{align}
-\frac{N(i,\tau)\lambda}{2\sigma}\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)}+\frac{\lambda}{4\sigma}\sqrt{n N(i,\tau)} \nonumber \\
-\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)+bN(i,\tau)}, \nonumber 
-\end{align}
-where the last inequality is because $\sqrt{x}+\sqrt{y}\geq \sqrt{x+y}$. Thus, we have
-\begin{align}
-&P(\epsilon_{i,\tau}^{j}\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P\left(S_{N(i,\tau)}^{i,j}\geq \frac{N(i,\tau)\lambda}{2\sigma}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
-\leq & P\left(S_{N(i,\tau)}^{i,j}\geq \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
-\leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
-\end{align}
-Similarily, we can bound 
-\begin{align}
-&P(\epsilon_{i,\tau}^{j}\leq-\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P(-\epsilon_{i,\tau}^{j}\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber 
-\end{align}
-
-Therefore, we know $P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right)$.
-Thus, we know
-\begin{align}
-&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)  \nonumber \\
-\leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
-\end{align}
-
-\end{proof}
-
-Before we start analyzing the cumulative regret, we first prove the following lemma which bounds the expected length of each round.
-
-\begin{lemma}
-Using our algorithm, we have $\mathbb{E}[t_{n+1}-t_{n}]\leq Nn$, $\forall n\geq 1$.
-\label{round:length}
-\end{lemma}
-
-\begin{proof}
-	A round completes when each arm is pulled at least once in that round.
-Let $X_{i}$ be the number of agents who come to the system between the time after the $(i-1)^{th}$ unique arm was pulled, up to and including the time when the $i^{th}$ unique arm was pulled.
-Then we know
-\begin{equation*}
-\mathbb{E}[t_{n+1}-t_{n}]=\sum_{i=1}^{N}E[X_{i}].
-\end{equation*}
-
-Fix $i$.
-In bounding $X_i$, we think of agents as ``trials'', where each trial can result in a new unique arm being pulled (which we call a ``successful'' trial), or not.
-There are two ways a trial can be successful:
-\begin{itemize}
-\item If there is at least one arm that has not been pulled and the probability of an agent utility function that would pull this arm without incentives is less than $n^{-1}$, then the principal will offer an incentive that causes this arm to be pulled (or one of these arms if there is more than one).
-In this case, the probability that the trial is succesful is $1$.
-\item The probability of an agent utility function that would pull each un-pulled arm without incentives is at least $n^{-1}$.
-In this case, the probability that the trial is successful is at least $n^{-1}$.
-\end{itemize}
-
-Thus, $X_{i}$ is stochastically dominated below by a geometric random variable with success probability $n^{-1}$, the expected number of trials up to and including the first success, $E[X_i]$, is bounded above by $n$.
-Thus,
-\begin{align}
-E[t_{n+1}-t_{n}]\leq Nn. \nonumber
-\end{align}
-\end{proof}
-
-\begin{lemma}
-The expected number of payments for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$.
-\label{lemma:numP}
-\end{lemma}
-
-\begin{proof}
-If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2mW\lambda\}$, they will correctly identify their best arm.
-Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms.
-In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
-Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$.
-Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).
-
-Define $\tau_{n}^{i}$ to be the first time we pull arm $i$ in the $n^{th}$ round. Then
-\begin{align}
-\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\} =\sum_{n=1}^{\infty}\sum_{i=1}^{N}\mathbbm{1}\{c(\tau_{n}^{i})>0\}. \nonumber
-\end{align}
-
-The cumulative expected number of payments is bounded above by:
-\begin{align}
-&E\left[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}\right] \nonumber \\
-=&\sum_{n=1}^{\infty}\sum_{i=1}^{N}P(c(\tau_{n}^{i})>0) \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}P\left(\exists i,j:|u_{i}^{j}-u_{i,\tau_{n}^{i}}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2Wm}\right)+\sum_{n=1}^{n_1}N \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right) +\sum_{n=1}^{n_1}N \nonumber \\
-\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right)\times N+\sum_{n=1}^{n_1}N \nonumber  \\
-\leq&24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1, \nonumber
-\end{align}
-
-Thus, we know the expected number of payments is bounded above by $O(N^2)$.
-
-\end{proof}
-
-Now we are ready to prove our second main result, Theorem~\ref{rst:regret}.
-
-\begin{proof}
-For regret incurred in the first $n_0$ round, it is bounded above by $\sum_{n=1}^{n_{0}}NRn$.
-
-For regret incurred after the first $n_0$ round, it has two different components: the regret incurred when we let the agents play myopically and the regret incurred when we incentivize the agents.
-Using Lemma~\ref{lemma:numP}, the expected regret incurred when we incentivize the agents is bounded above by: $\left[24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1\right]R$.
-
-For the regret incurred when we let the agents play myopically at time $t\geq t_{n_0}$, it consists of the following two components:
-\begin{itemize}
-\item For those users whose utility difference between their best and the second best arm is greater than $f(t)$: we define a sequence of stopping time $\tau_{n}^{k}$ to be the $k^{th}$ time period in the $n^{th}$ round.
-For $k>t_{n+1}-t_{n}$, we define $\tau_{n}^{k}=\infty$.
-For $\tau_{n}^{k}=t$, the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)\times R$.
-We denote the regret incurred by these agents as $r_1(\tau_{n}^{k})$.
-For $k>t_{n+1}-t_{n}$, we define $r_1(\tau_{n}^{k})=0$.
-\item For those user whose utility difference between their best and the second best arm is smaller than $f(t)$: this happens with probability $S(f(t))$ at each time and regret is bounded above by $S(f(t)) \times f(t)=Mf(t)^2$.
-We denote the regret incurred by these agents as $r_2(t)$.
-\end{itemize}
-
-Thus, the cumulative expected regret incurred up to time $T$ when we let the agent play myopically is bounded above by:
-\begin{align}
-&E\left[\sum_{t=1}^{T}r(t)\right] \nonumber \\
-=&E\left[\sum_{t=1}^{t_{n_{0}}} r(t) + \sum_{t=t_{n_{0}}}^{T}(r_1(t)+r_2(t))\right]  \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}-1}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-=& \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right]. \label{chap5:equ:r1}
-\end{align}
-Since
-\begin{align}
-& E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\right] \nonumber\\
-= &  \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})] \nonumber \\
-= &  \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}(E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty)+E[r_1(\tau_{n}^{k})|\tau_{n}^{k}=\infty]\times P(\tau_{n}^{k}=\infty)) \nonumber \\
-= & \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty), \nonumber
-\end{align}
-
-we have
-\begin{align}
-\eqref{chap5:equ:r1}= & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty) + E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}\left[\sum_{k=1}^{\infty}24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right) R\times P(\tau_{n}^{k}<\infty) \right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R \times Nn+ \sum_{t=1}^{T}Mf(t)^2. \label{chap5:equ:regret}
-\end{align}
-
- Thus the cumulative regret at time $T$ is bounded above by
-\begin{align}
-&\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-+ & 24N^2 m \frac{1}{e^{\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2}}-1}R+N\left(\max\left\{n_{0},\frac{2}{p}\right\}\right)R. \nonumber
-\end{align}
-
-For a fixed $T$, we only need to minimize the following two terms since all others are constant:
-
-\begin{align}
-\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2. \label{equ:regret}
-\end{align}
-
-If we set $f^2(t)=\frac{2\log(T)\times 64W^2 m^2\sigma^2}{1.8t}$, then
-\begin{align}
-&\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\ 
-\leq & \sum_{n=1}^{T} 24N^2 mnR \exp\left(-2\log(T)\right)  + \frac{128W^2 m^2\sigma^2 M\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{n} \nonumber \\
-\leq &  24N^2 m R\frac{T(T-1)}{2T^2}  + 71.12 W^2 m^2\sigma^2 M\log(T)(\log(T)+1) \nonumber \\
-\leq &  12 N^2 m R  + 71.12 W^2 m^2\sigma^2 M\log(T)(\log(T)+1). \nonumber
-\end{align}
-
-Thus, the cumulative expected regret is bounded by $O(N^2 m + M m^2\log(T))$.
-\end{proof}
-
-\begin{corollary}
-If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O(N^2)$.
-\end{corollary}
-
-\begin{proof}
-The proof of this corollary is similar to the proof of Theorem~\ref{rst:regret}.
-If we set $f^2(t)=\frac{2\log(T)\times 64W^2 m^2\sigma^2}{1.8t}$, then there exists a $t_{0}$ such that for $t>t_{0}$, $S(f(t))=0$.
-Thus, similar to equation~\eqref{equ:regret}, we know the cumulative expected regret when we let the agents play myopically is bounded above by
-\begin{align}
-\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{t_{0}}Mf(t)^2 \nonumber
-\end{align}
-Therefore, based on the same analysis of Theorem~\ref{rst:regret}, we know the cumulative regret is bounded by $O(N^2)$.
-\end{proof}
-
-\subsection{Practical Issues}
-\label{sec:pi}
-
-In Algorithm~\ref{Alg1}, we use ``pay whatever it takes'' strategy when we decide to incentivize the agent.
-However, ''pay whatever it takes'' only shows up in the proof of Lemma~\ref{round:length}.
-Without loss of generality, suppose we want to incentivize arm $i$ at time $t$ at the $n^{th}$ round.
-Based on the proof of Lemma~\ref{round:length}, as long as we offer a payment $c_{i,t}$ such that arm $i$ has at least $n^{-1}$ probability being pulled at time $t$, our results still hold true.
-We could compute this $c_{i,t}$ dynamically based on $F(\cdot)$ as well as our current estimate $u_{i,t}$.
-Here is the revised algorithm which would work well in practice:
-
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration}
-\label{Alg2}
-\begin{algorithmic}
-\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
-\FOR{ $t = 1, 2, 3, \cdots$}{
-	\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
-  \IF {$S\setminus V$ is non-empty}
-    \STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
-	\STATE{Offer payment $c_{i,t}=\inf\{c: P(\theta\sim F: \theta\cdot u_{i,t}+c>max_{j}\theta\cdot u_{j,t})>n^{-1}\}$}
-  \ELSE
-  \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
-  \ENDIF
-  \STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
-  \IF {$n\neq \min_{i}N(i,t)$} 
-  	\STATE $V=\emptyset$
-  \ENDIF
-  \STATE Update the round number, $n = \min_{i} N(i,t)$
-}\ENDFOR
-
-\end{algorithmic}
-\end{algorithm}
-
-The same proof would work and we can get the exact same results as Algorithm~\ref{Alg1}.
-
-\section{Lower Bound $\Omega(\log(T))$}
-\label{sec:lb}
-
-In this section, we assume $\theta$ follows a continuous distribution $F(\cdot)$.
-We provide an example to show the best possible lower bound is $\Omega(\log(T))$ regardless of the incentivizing strategy.
-
-Suppose we have two arms.
-Arm $1$ has attribute vector $(0,0)$ and arm $2$ has attribute vector $(0,1)$.
-We assume the users' preference are uniformly distributed on the unit circle.
-If the user knows the exact attribute vectors for both arms, then the users with preference on the bottom half circle will choose arm $1$ and the users with preference on the top half circle will choose arm $2$.
-
-Consider the following algorithm: at each step, let the agents play myopically; however, they are going to see the noisy rewards for both arms.
-
-To lower bound the regret, we assume that the agents already know the true attribute vector for arm $1$.
-Without loss of generality, denote $u_{2,t} = (0,1)+(z_{t,1},z_{t,2}) = (0,1)+ (N(0,1/t),N(0,1/t))$ to be the estimate attribute vector for arm $2$ (Without loss of generality, we assume the variance for the noise is $1$).
-
-Since $(z_{t,1}, z_{t,2})$ is symmetric around $(0,0)$, we know
-
-\begin{align}
-&E[r(t)] \nonumber \\
-= &E[r(t) | z_{t,1}>0,z_{t,2}>0] \times P(z_{t,1}>0,z_{t,2}>0) + E[r(t) |z_{t,1}>0,z_{t,2}<0] \times P(z_{t,1}>0,z_{t,2}<0) \nonumber \\
-&+E[r(t) | z_{t,1}<0,z_{t,2}>0] \times P(z_{t,1}<0,z_{n,2}>0) + E[r(t) |z_{t,1}<0,z_{t,2}<0] \times P(z_{t,1}<0,z_{t,2}<0) \nonumber \\
-\geq & 0.25 \times E[r(t) | z_{t,1}>0, z_{t,2}>0]. \nonumber
-\end{align}
-
-Given $z_{t,1}>0$ and $z_{t,2}>0$, we know users whose preference vector between $(-1,0)$ and $\left(\frac{-1-z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ as well as users whose preference vector between $(1,0)$ and $\left(\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{-z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ will make a mistake.
-The regret is the absolute value of the second coordinate of the user's preference vector.
-Thus, we know
-
-\begin{align}
-&E[r(t)| z_{t,1}>0, z_{t,2}>0] \nonumber \\
-=& 4\times 2 \int_{0}^{\infty} \int_{0}^{\infty} \int_{0}^{\arctan\left(\frac{z_{t,1}}{1+z_{t,2}}\right)}\frac{\sin(\theta)}{2\pi}d(\theta)\frac{e^{-\frac{t \times z_{t,1}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,1})\frac{e^{-\frac{t \times z_{t,2}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,2}) \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}t\times \left[1-\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right]e^{-\frac{t \times z_{t,1}^2}{2}}e^{-\frac{t \times z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty} \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber
-\end{align}
-
-Below, we want to show 
-\begin{align}
-\lim_{t\rightarrow\infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{\frac{1}{t}} = O(1), \nonumber
-\end{align}
-and use the fact that $\sum_{n=1}^{T}\frac{1}{n}=O(\log(T))$ to show the regret is at least $\Omega(\log(T))$.
-
-Denote $d(t)=t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]$.
-Since
-\begin{align}
-d^{'}(t)=\frac{-z_{t,1}^2(2z_{t,2}+3\sqrt{t})-2(z_{t,2}+\sqrt{t})^3}{2(z_{t,1}^2+(z_{t,2}+\sqrt{t})^2)^{3/2}}+1. \nonumber
-\end{align}
-
-and $\lim_{t\rightarrow \infty}d^{'}(t)=2$, we know for $t$ large enough, $d(t)$ is a increasing function in terms of t. Thus, based on the Monotone Convergence Theorem, we have
-
-\begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{\frac{1}{t}} \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber
-\end{align}
-
-Based on our calculation, we know
-
-\begin{align}
-\lim_{t\rightarrow \infty} d(t)=\frac{z_{t,1}^2}{2}. \label{ex:limit}
-\end{align}
-Thus,
-\begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{\frac{1}{t}} \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber  \\
-=&\frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\left[ \frac{z_{t,1}^2}{2}e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) = \frac{1}{2\pi}. \nonumber
-\end{align}
-
-Thus, the cumulative expected regret is at least $\Omega(\log(T))$.
-
-\section{Conclusion}
-In this paper, we study the incentivizing exploration problem with heterogeneous user preferences, which generalize the problem setting studied by \cite{frazier2014incentivizing} and \cite{han2015incentivizing}.
-We propose a simple policy that mostly exploits and occasionally incentivizing exploration, which can achieve $O(N^2+M(\log(T))^2)$ cumulative expected regret with $O(N^2)$ payment budget.
+\input{conclusion.tex}
 
@@
 \appendix
-\section*{Proof of Theorem~\ref{rst:budget}}
 
-We also need the following lemma in part of the proof of Theorem~\ref{rst:budget}.
-\begin{lemma}
-For all $n\geq 1$, we have
-\begin{align}
-0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-\label{lemma:cal2}
-\end{lemma}
-\begin{proof}
-\begin{align}
-&0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)} \nonumber \\
-\iff & 0.81 n^{5/3} \geq 0.6n \log(\log_{1.1}(n)+1) \nonumber \\
-\iff &  \frac{81}{60} n^{2/3} \geq  \log(\log_{1.1}(n)+1) \nonumber
-\end{align}
-
-Denote $f(x) = \frac{81}{60}x^{2/3} - \log(\log_{1.1}(x)+1)$.
-It's easy to compute $f^{'}(x)=0$ has a unique solution $x_{0}=e^{2/3w(\frac{20e^{20000/314763}}{27})-\frac{10000}{104921}}$ (here $w(\cdot)$ is the Lambert W-Function) and it is the global minimum.
-Since $f(x_{0})\approx 0.0252 >0$, we know $f(x)>0$ for all $x\geq 1$.
-Thus, our lemma holds true.
-\end{proof}
-
-Now we are ready to prove our first main result, Theorem~\ref{rst:budget}.
-
-\begin{proof}
-
-\noindent\textbf{Step 1: Categorize measurement errors into different radius envelopes}
-
-Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$.
-Denote $\epsilon_{i,t}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,t}$.
-Denote $\omega$ to be a sample path and $n(t,\omega)$ to be the round number for sample path $\omega$ at time $t$.
-For a fixed time $t$, define
-\begin{align}
-L^{'}[\ell](t) = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n(t,\omega),\ell), \forall i,j\}\nonumber
-\end{align}
-where $g(n,\ell)$ is a function which we will define later.
-Define $L[1](t) = L^{'}[1](t)$ and $L[i](t) = L^{'}[i](t)\setminus L^{'}[i-1](t)$ for $i\geq 2$.
-We call $L[\ell](t)$ the $\ell^{th}$ envelope at time $t$.
-We often simplify the notation and use $L[\ell]$ instead of $L[\ell](t)$ without confusion.
-
-In the calculation below, we omit the dependency on $\omega$ when refering to variables $c(t)$, $\epsilon_{i,t}^{j}$ and $t_n$.
-Based on the definition of $L[\ell]$, we know if $\omega\in L[\ell]$, the maximum payment we need to offer at time $t$ is bounded above by
-\begin{align}
-&\max_{i}\theta_t\cdot u_{i,t} - \min_{j}\theta_t\cdot u_{j,t} \nonumber \\
-= &\max_{i}\theta_t\cdot (\epsilon_{i,t}+u_i) - \min_{j}\theta_t\cdot (\epsilon_{j,t}+u_j) \nonumber \\
-\leq &\max_{i}\theta_t\cdot u_i - \min_{j}\theta_t\cdot u_j +\max_{i}\theta_t\cdot \epsilon_{i,t} - \min_{j}\theta_t\cdot \epsilon_{j,t}\nonumber \\
-\leq & R + 2Wmg(n,\ell). \nonumber
-\end{align}
-
-We denote $\bar{c}(n,\ell)=R + 2Wmg(n,\ell)$ as the upper bound of payment for round $n$ if our measurement error lie in the $\ell^{th}$ envelope.
-
-\noindent\textbf{Step 2: Introduce a new stochastic process which bounds the total payment in a round}
-
-Denote $\mathcal{F}_t$ as the filtration up to time $t$. Based on our algorithm, we know
-
-\[ P(\text{play a new arm}|\mathcal{F}_t) =
-  \begin{cases}
-    1       & \quad \text{if we incentivize}\\
-    \sum_{i\notin (V\cup S)} P(\theta \cdot u_{i,t}>\theta\cdot u_{j,t} \forall j\neq i)  & \quad \text{if }  S\setminus V\neq \emptyset 
-  \end{cases} \label{dom_stoc}
-\] 
-\hspace{1cm}$\geq (n-|V|)\times \frac{1}{n}=1-\frac{|V|}{n}$.
-
-Let $(Z_{n,v,m}:m\geq 0)$ be a sequence of independent Bernoulli random variable with success probability $(1-\frac{v}{n})$.
-We will construct an alternative stochastic process for selecting which arm gets played that has the same distribution as the original process, but under which
-\begin{align}
-t_{n+1}-t_{n}\leq \bar{T}_{n}:=\sum_{v=0}^{N-1}\bar{T}_{n,v}, \nonumber 
-\end{align}
-where $\bar{T}_{n,v}:=\inf\{m\geq 0: Z_{n,v,m}=1\}+1$.
-
-The new stochastic process will have the property that whenever $Z_{n,v(n,t),m(n,t)}=1$, we will play a new arm at time t for $t\in [t_{n}, t_{n+1}]$, where $v(n,t)$ is the number of unique arms played in round $n$ strictly before time $t$, and $m(n,t)$ is the number of times we have pulled a previously pulled arm for the current value of $v(n,t)$.
-At time $t$, to determine what arm to pull, calculate \eqref{dom_stoc} and let $q_t$ be the probability computed.
-Note $q_t\geq 1-\frac{v(n,t)}{n}$.
-
-If $Z_{n,v(n,t),m(n,t)}$ is 1, decide to play a new arm.
-Otherwise, draw a second Bernoulli random variable with probability $\frac{q_t-(1-\frac{v(n,t)}{n})}{1-(1-\frac{v(n,t)}{n})}$, and if it is 1, decide to play a new arm, and otherwise decide to play an old arm.
-Note that
-
-\begin{align}
-P(\text{play a new arm}|\mathcal{F}_{t})=\left[1-\frac{v(n,t)}{n}\right]+\left[1-(1-\frac{v(n,t)}{n})\right]\times \frac{q_t-(1-\frac{v(n,t)}{n})}{1-(1-\frac{v(n,t)}{n})}=q_t.
-\end{align}
-
-Since we pull a new arm only when $Z_{n,v(n,t),m(n,t)}=1$, the number of times we pull an arm when $v(n,t)=v$ is bounded above by $\bar{T}_{n,v}$. Thus,
-
-\begin{align}
-t_{n+1}-t_{n}\leq \sum_{v=0}^{n-1}\bar{T}_{n,v}=\bar{T}_{n}.
-\end{align}
-Finally, we want to bound $\sum_{t}E[c(t)]$. Let $C(n)$ be the cost incurred in round $n$. Thus $\sum_{t}E[c(t)]=\sum_{n}E[C(n)]$. We know
-\begin{align}
-C(n)&=\sum_{t=t_n}^{t_{n+1}-1}c(t)=\sum_{t=t_{n}}^{t_{n+1}-1}\sum_{\ell}\mathbbm{1}\{\omega\in L(\ell)\}c(t) \nonumber \\
-&\leq \sum_{t=t_{n}}^{t_{n+1}-1}\sum_{l}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell) \nonumber \\
-&\leq (t_{n+1}-t_{n})\sum_{\ell} \mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell) \nonumber \\
-&\leq \bar{T}_{n}\sum_{l}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell). \nonumber
-\end{align}
-
-Since $\bar{T}_{n}$ is independent of $\omega$, we know
-
-\begin{align}
-E[C(n)]\leq E[\bar{T}_{n}]\sum_{\ell}P(\omega\in L(\ell))\bar{c}(n,\omega). \nonumber
-\end{align}
-
-\noindent\textbf{Step 3: Rewrite the total payment expression}.
-
-Based on the above notations, we can rewrite the cumulative payment as follows:
-\begin{align}
-\sum_{t=1}^{\infty}c(t) =\sum_{n=1}^{\infty}C(n)
-\leq  \sum_{n=1}^{\infty}\sum_{\ell=1}^{\infty}\bar{T}_{n}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell). \nonumber
-\end{align}
-
-Set $g(n,\ell)$ to be $\frac{2\sigma \ell}{n^{1/6}}$.
-Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2Wm\lambda\}$, they will correctly identify their best arm.
-Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{2\sigma l}{n^{1/6}} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
-Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms.
-Denote $a_0=\frac{4Wm\sigma}{p^{-1}(\frac{p}{2})}$.
-In order to have $\frac{2\sigma l}{n^{1/6}}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil (a_{0} l)^6 \rceil$.
-In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
-Denote $n_2=\frac{2}{p}$.
-Thus, we know we can only incur regret for sample paths $\omega$ in the $\ell^{th}$ envelope in the first $\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}$ rounds.
-
-Thus,
-\begin{align}
-\sum_{t=1}^{\infty}c(t)\leq\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\bar{c}(n,\ell)\mathbbm{1}\{\omega\in L[\ell]\}\bar{T}_{n}. \nonumber
-\end{align}
-
-Therefore,
-
-\begin{align}
-&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
-\leq &\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\bar{c}(n,\omega)P(\omega \in L(\ell))E[\bar{T}_{n}] \nonumber \\
-=&\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+2Wm\frac{2\sigma \ell}{n^{1/6}}\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
-\leq &\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[\ell])E[\bar{T}_{n}]. \nonumber
-\end{align}
-
-\noindent\textbf{Step 4: Bound $P(\omega\in L(\ell))$}.
-
-We now bound $P(\omega\in L[\ell])$ for $n\geq n_0$ and $\ell\geq 2$. As a reminder, we omit the dependency between $\epsilon_{i,t}^{j}$, $n$ and $\omega$. We know 
-\begin{align}
-&P(\omega\in L[\ell]) \nonumber \\
-=&P(\omega\in L^{'}[\ell])- P(\omega\in L^{'}[\ell-1]) \nonumber \\
-\leq & 1-P\left(|\epsilon_{i,t}^{j}|<\frac{2\sigma (\ell-1)}{n^{1/6}}, \forall i,j\right) \nonumber \\
-=&P\left(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (\ell-1)}{n^{1/6}}\right) \nonumber  \\
-\leq &\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (\ell-1)}{n^{1/6}}\right) \nonumber
-\end{align}
-
-Define $S_{i,t}^{j}=\frac{N(i,t)\epsilon_{i,t}^{j}}{2\sigma}$, then we know $S_{i,t}^{j}$ is a summation of $1/2$ gaussian random numbers. Therefore,
-
-\begin{align}
-&\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma(\ell-1)}{n^{1/6}}\right) \nonumber \\ 
-=&\sum_{i,j}P\left(|S_{i,t}^{j}|\geq \frac{N(i,t)(\ell-1)}{n^{1/6}}\right) \nonumber \\
-\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(\ell-1)). \nonumber
-\end{align}
-
-Based on Lemma~\ref{lemma:cal2}, we know
-\begin{align}
-&N(i,t)^{5/6}(\ell-1) \nonumber \\
-=& 0.9N(i,t)^{5/6} + N(i,t)^{5/6}(\ell-1.9) \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)} + \sqrt{(\ell-1.9)^2 N(i,t)} \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+(\ell-1.9)^2 N(i,t)}. \nonumber
-\end{align}
-
-Based on Lemma~\ref{ACI-inequality}, we know
-\begin{align}
-& P(\omega\in L(\ell) \nonumber \\
-\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(\ell-1)) \nonumber \\
-\leq & \sum_{i,j}24e^{-1.8(\ell-1.9)^2} = 24Nme^{-1.8(\ell-1.9)^2}. \nonumber
-\end{align}
-
-\noindent\textbf{Step 5: Final Step}
-
-Thus,
-\begin{align}
-&\sum_{t=1}^{\infty}c(t) \nonumber \\
-\leq&\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
-\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(\omega\in L[1])E[\bar{T}_{n}] +\sum_{l=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
-\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]E[\bar{T}_{n}] +\sum_{\ell=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]24Nme^{-1.8(\ell-1.9)^2}E[\bar{T}_{n}]\nonumber \\
-\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]Nn +\sum_{\ell=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]24Nme^{-1.8(\ell-1.9)^2}Nn \nonumber \\
-\leq & \left[R+4Wm\sigma \right]N (\max\{n_2,\lceil (a_0)^6 \rceil\})^2+\sum_{\ell=2}^{\infty}24N^2 m[R+4Wm\ell\sigma](\max\{n_2,\lceil (a_0 \ell)^6 \rceil\})^2 e^{-1.8(\ell-1.9)^2} \nonumber \\
-=& O(N^2). \nonumber
-\end{align}
-
-\end{proof}
-
-\section*{Calculation for Equation~\eqref{ex:limit}}
-
-In this section, we prove
+\input{appendix.tex}
 

### 2018-01-26 conclusion.tex
divide the paper into sections

--- 2017-12-04 paper.tex
@@
-\documentclass{article}
-\usepackage[utf8]{inputenc}
-
-\usepackage[english]{babel}
-
-\usepackage{blindtext}
-\usepackage{amssymb}
-
-\usepackage[]{algorithm}
-\usepackage[]{algorithmic}
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{xr} 
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{amsthm}
-\usepackage{comment}
-\usepackage{graphicx}
-\usepackage{subcaption}
-\usepackage{xcolor}
-\usepackage{amsmath}
-\usepackage{dblfloatfix}
-\usepackage{bbm}
-
-\newcommand{\IE}{IE} 
-\newcommand{\argmax}{\mathop{\mathrm{argmax}}}
-
-\newcommand\floor[1]{\lfloor#1\rfloor}
-\newcommand\ceil[1]{\lceil#1\rceil}
-
-\newcommand{\bccomment}[1]{{\color{blue}BC: #1}}
-\newcommand{\pfcomment}[1]{{\color{blue}PF: #1}}
-
-\newtheorem{definition}{Definition}[section]
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-\newtheorem{assumption}{Assumption}
-
-\title{Incentivizing Exploration with Heterogeneous Utilities}
-
-\begin{document}
-
-\maketitle
-
-\section{Introduction}
-In this paper, we study incentivizing exploration with heterogeneous agent preferences.
-In this problem,   
-arms have unknown multivariate attributes, and agents have heterogeneous linear utility functions that map these attribute vectors onto utilities.
-Agents see noisy observations of attributes of arms pulled by all previous agents, and estimate an arms' attribute vector by the simple average of these observations.
-Agents are selfish, and pull the arm with the largest estimated utility summed with an optional arm-specific incentivizing payment chosen by the principle.
-We study strategies for choosing such incentive payments that seek to maximize the total utility derived by agents, subject to a limitation on the total incentive payment.
-To accomplish this goal, a strategy must induce sufficient exploration to reveal arms' attributes, while still letting agents select myopically and according to their preferences sufficiently often that high-utility arms are chosen and incentive payments are kept small.
-
-Our problem setting models online review aggregators like Amazon, Yelp, and Tripadvisor that host crowdsourced reviews.
-Users of these websites wish to use the reviews hosted there to choose the product / restaurant / vacation (generically referred to as an ``item'') that is best according to their preferences.
-These reviews provide not just cardinal feedback, but also a description of items' attributes that a user may consider together with their personal preferences to select their preferred item.
-An item with few reviews might have inaccurate attribute estimates, leading users to avoid it even though it may actually be their best choice.
-Without incentives, this situation may persist and decrease welfare for the platform's user base.
-By offering incentives, either through price reductions by Amazon or coupons from Yelp or Tripadvisor, a platform may induce more reviews of unexplored items and provide more value over the long term.
-
-Our problem setting also applies to crowd science platforms like eBird \cite{frazier2014incentivizing, sullivan2009ebird}.
-EBird guides birding enthusiasts through a website to explore and report their findings to the birding community.
-Each user report contains information about when, where and how they go birding and what birds they see and hear.
-EBird may wish to incentivize enthusiasts to explore less-explored birding locations and provide more accurate reports on these locations.
-Each enthusiast may have different preference over a location's attributes such as the diversity of bird species, weather, distance and safety.
-By offering enthusiasts incentivies to explore, eBird can create a more accurate body of reports and provide better value to the birding community.
-
-% Something interesting to study would be to alter the search rankings to influence people
-% Also which items to spam people about reviewing
-
-In this problem context, we study a simple policy that usually exploits, incentivizing agents to pull an arm only when the set of agent utility functions that would pull this arm without incentives has probability below a time-varying threshold.
-In our paper, we assume all arms are some agents' best arm.
-Under this assumption, we prove that with $O(N^2)$ payment budget, this policy has $O(N^2+M(\log(T))^2)$ cumulative expected regret where $M$ is an upper bound on the limiting marginal probability density of agent utilities that are nearly indifferent between their best and the second best arm.
-If all agents' utility difference between their best and second best arm is bounded below by a positive number, which typically happens when the agent utility distribution is discrete, this policy achieve constant cumulative expected regret $O(N^2)$.
-The key difference between our problem setting and both the homogenous preference setting and the traditional multi-armed bandits setting is that we must incentivize agents to try suboptimal arms much less often, since all arms are some agents' best arm.
-Essentially, heterogeneity provides free exploration.
-These results suggest that heterogeneous agent preferences reduce but do not eliminate the need to incentive exploration, in relation to single-preference settings.
-
-We broadly categorize the relevant previous literature into two categories based on whether there is money transfer.
-With money transfer, \cite{frazier2014incentivizing} considers a problem setting where the principal pays agents money to explore.
-This work assumes all agents have equal value for money and provide a complete characterization of achievable reward with a fixed budget.
-\cite{han2015incentivizing} generalizes this framework to include agents with heterogeneous value for money, and to allow an external signal to provide partial information about this valuation.
-Under this setting, this work proves a bound on achievable reward as a function of the budget and the signal scheme.
-
-Without money transfer but using information asymmetry, \cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time.
-\cite{mansour2015bayesian} generalizes \cite{kremer2014implementing} by allowing a finite number of actions at each time.
-\cite{mansour2016bayesian} considers a problem setting where there are multiple agents at each time and agents may interact with each other.
-In these papers, the principal provides each agent a recommendation at each time that is Bayesian incentive-compatible.
-They prove the principal can achieve constant regret when utilities are deterministic and logarithmic regret when utilities are stochastic.
-
-We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+M(\log(T))^2)$ regret with $O(N^2)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
-
-\section{Problem Setting}
-\label{sec:prob}
-
-We have $N$ arms. Arm $i$ has a fixed but unknown attribute vector $u_i\in \mathbb{R}^{m}$. 
-A stream of myopic selfish agents come to our system.
-Agent $t$ has linear preferences over attributes described by a vector $\theta_t \in \mathbb{R}^m$ that is unknown to the principal and drawn i.i.d.
-from a known distribution $F(\cdot)$ with compact support.
-We refer synonomously to an agent and that agent's preference vector: when we say ``an agent $\theta$'', we mean ``an agent with preference vector $\theta$.''
-
-Each agent $t$ chooses an arm to pull $A_t$, according to a process described below, and obtains utility $\theta_t \cdot u_{A_{t}}$.
-The principal and all agents then see a noisy observation of the attribute vector of the pulled arm of the form $O_t=u_{A_{t}}+\epsilon_{t}$, where $\epsilon_t\sim N(0, \sigma^2 I_{m})$ is independent normally distributed noise, and $I_m$ denotes an $m$-dimensional identity matrix.
-Although we assume a common variance across attributes for simplicity of presentation, our theoretical results hold if the variance differs.
-
-At each time $t$, for each arm $i$, we (the principal) offer a non-negative payment $c_{i,t}\geq 0$ based on previous observations.
-We assume that agent $t$ chooses to pull the arm that myopically maximizes the sum of this payment and an estimate of the utility obtained $\theta_t \cdot u_{i,t}$ where $u_{i,t}$ denotes the simple average of $O_s$ over all previous pulls of arm $i$.
-In this paper, we assume all arms have been pulled once at time $t=0$ and $u_{i,0}$ denotes a random draw from the arm attribute vector.
-For $t>0$, denote $u_{i,t} = \frac{\sum_{s<t} O_s 1\{A_s = i\} + u_{i,0}}{\sum_{s<t} 1\{A_s = i\}+1}$ and $A_t=\argmax_{i}\{\theta_t\cdot u_{i,t}+c_{i,t}\}$, breaking ties in favor of the arm with the highest incentive.
-We use $c_t=c_{A_{t},t}$ to denote the actual incentive payment at time $t$.
-
-This behavior may be recovered if agents are Bayesian and share a common non-informative prior distribution that is constant over $\mathbb{R}^m$ and know $\sigma^2$.
-In this case, the posterior distribution on $u_{i}$ at time $t$ is multivariate normal with mean $u_{i,t}$, and the expected value of $\theta_t \cdot u_i$ under this posterior conditioned on $\theta_t$ is $\theta_t \cdot u_{i,t}$ (see equation $2.13$ in section $2.5$, \cite{Ge04}).
-Alternatively, one may simply take our assumption that agents use the average as their estimate of an attribute value directly without such a Bayesian justification.
-
-We define the regret at time $t$ as $r(t)=\max_{i}\{\theta_{t}\cdot u_{i}\}-\theta_t\cdot u_{A_t}$, and the cumulative regret up to time T as $R(T)=\sum_{t=1}^{T}r(t)$.
-Define the cumulative payment up to time T similarly as $C(t)=\sum_{t=1}^{T}c(t)$.
-As the principal, we want to find a strategy $\mathcal{A}$ under which both the cumulative expected regret $\mathbb{E}_{\mathcal{A}}[R(T)]$ and the cumulative expected payment $\mathbb{E}_{\mathcal{A}}[C(T)]$ are small.
-
-To support later development, we define some additional notation.
-We let $B(\theta)$ and $\hat{B}(\theta)$ refer to the index of the arm that is best and second best for an agent with preference vector $\theta$, $B(\theta) \in \argmax_i \theta \cdot u_i$ and $\hat{B}(\theta)=\argmax_{i\neq B(\theta)}\theta\cdot u_{i}$, breaking ties uniformly at random.
-We let $N(i,t)$ denote the number of pulls of arm $i$ at times up to and including $t$ plus $1$ (because of the initial pull), i.e.
-$N(i,t)=\sum_{s<t} 1\{A_s = i\}+1$.
-We call time $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$ the {\it starting point of the $n^{th}$ round}. We call the set of times $[t_{n}, t_{n+1})$ the {\it $n^{th}$ round}.
-
-\section{Algorithm and Upper Bound}
-\label{sec:ub}
-
-In this section, we propose a simple policy that mostly exploits, and occasionally incentivizes exploration when the probability of an arm would be pulled by all agent types below a time-varying threshold given the current posterior.
-We prove that with the help of heterogeneous preferences, we can get a certain amount of exploration for free via heterogeneity.
-
-\subsection{Our Algorithm}
-Our algorithm incentivizes pulling an arm $i$ at a time $t$ in round $n$ if and only if both of the following criteria are met:
-\begin{itemize}
-\item the probability of pulling arm $i$ would be below $n^{-1}$ without incentives; 
-\item arm $i$ has not been played previously in the current round.
-\end{itemize}
-Ties are broken randomly.  This algorithm does not need to know the horizon $T$ in advance.
-
-If our algorithm decides to incentivize an arm $i$, it uses the ``pay whatever it takes'' strategy in which the payment offered is $\max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$.
-This maximum over $\theta$ is taken over the support of $F$, which we recall is assumed compact.
-(We use this ``pay whatever it takes'' strategy for its simplicity, and in Section~\ref{sec:pi} we provide an alternate and smaller incentive payment that achieves the same payment budget bound and regret bound).
-
-We describe our algorithm in detail as follows:
-
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration}
-\label{Alg1}
-\begin{algorithmic}
-\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
-\FOR{ $t = 1, 2, 3, \cdots$}{
-	\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
-  \IF {$S\setminus V$ is non-empty}
-    \STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
-    \STATE{Pay whatever it takes to incentivize pulling arm $i$, i.e., offer payment 
-    $c_{i,t} = \max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$ and $c_{j,t} = 0$ for $j \ne i$.}
-  \ELSE
-  \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
-  \ENDIF
-  \STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
-  \IF {$n\neq \min_{i}N(i,t)$} 
-  	\STATE $V=\emptyset$
-  \ENDIF
-  \STATE Update the round number, $n = \min_{i} N(i,t)$
-}\ENDFOR
-
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{Assumptions}
-In this section, we state several assumptions assumed by our analysis.  First define
-\begin{align}
-\Omega_{i,j}=\{\theta:B(\theta)=i, \hat{B}(\theta)=j\}, \nonumber 
-\end{align}
-which is the set of agent preferences whose best arm is arm $i$ and second best arm is arm $j$. With this definition, our analysis makes the following assumptions:
-
-\begin{assumption} Let $F_{i,j}(y)$ be the marginal cumulative density function (or cumulative mass function if $F(\cdot)$ is a discrete distribution) of $(u_i-u_j)\cdot\theta$ conditioned on $\theta \in \Omega_{i,j}$.
-We assume $F_{i,j}(y)\leq My$ for all $y\in R^{+}$, $\forall i,j$.
-\label{A1}
-\end{assumption}
-
-As we can see later in our proof, we only need $\max_{i,j}\limsup_{y\rightarrow 0^{+}}\frac{F_{i,j}(y)}{y}$ to be finite.
-Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm.
-
-\begin{assumption} We assume $F$ has a compact support set. Without loss of generality, we assume $\theta\in [0,W]^m$.
-\label{A2}
-\end{assumption}
-
-We use $R = \max_{\theta, i,j} \theta \cdot (u_i - u_j)$ to denote the maximum regret that can be incurred at each time.  Assumption~\ref{A2} shows that $R<\infty$.
-
-\begin{assumption}
-Denote $p=\min_{i}P(\{\theta: B(\theta)=i\})$. We assume $p>0$.
-\label{A3}
-\end{assumption}
-
-Assumption~\ref{A3} means each arm $i$ has a strictly positive proportion of users for which that arm is best.
-
-\subsection{General Results}
-
-In this section, we prove Algorithm~\ref{Alg1} achieves $O(N^2+M(\log(T))^2)$ cumulative regret with $O(N^2)$ payment budget.
-This is stated in the following pair of theorems, which together constitute our main results.
-
-\begin{theorem}
-The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$. 
-\label{rst:budget}
-\end{theorem}
-
-\begin{theorem}
-The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2 m + M m^2(\log(T))^2)$.
-\label{rst:regret}
-\end{theorem}
-
-Before we prove these two theorems, we must first introduce two additional pieces of notation, which will be used in preliminary lemmas.
-Let $S(\delta)$ be the proportion of users whose utility difference between their best and second best arm is less than $\delta$.
-Formally, $S(\delta)=P(\theta: \theta \cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}\leq \delta)$.
-Then, let $p(\delta)=\min_{i}P(\{\theta:B(\theta)=i,\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$.
-We know $p(0)=p$.
-
-With this additional notation, we now prove several lemmas.
-First, based on Assumption~\ref{A1}, we have the following bound for $S(\delta)$.
-
-\begin{lemma}
-$S(\delta)\leq M\delta$.
-\label{lemma:sdelta}
-\end{lemma}
-
-\begin{proof}
-\begin{align*}
-S(\delta)
-&=\sum_{i,j}P(\theta\cdot(u_{i}-u_{j})\le \delta|\theta\in \Omega_{i,j})P(\theta\in \Omega_{i,j}) \\
-&\leq \sum_{i,j}M\delta \times P(\theta\in \Omega_{i,j}) \\
-&=M\delta.
-\end{align*}
-\end{proof}
-
-The following lemma bounds the probability of making a mistake if we let the agents play myopically in the $n^{th}$ round, given that the utility difference between his/her best and second best arm is bounded below by a constant.
-
-\begin{lemma}
-Define $\tau$ to be any stopping time that is almost surely between $t_n$ and $t_{n+1}-1$ with respect to the filtration $\mathcal{F}_{t}=\sigma(A_1,\cdots,A_t,c_1,\cdots,c_t,O_1,\cdots,O_t)$, we have
-\begin{align}
-P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{16\sigma^2}\right), \nonumber
-\end{align}
-for $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$.
-\label{round:prob}
-\end{lemma}
-
-We need the following lemma in order to prove Lemma~\ref{round:prob}.
-
-\begin{lemma}
-For $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$, we have
-\begin{align}
-\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-\label{n0-inequality}
-\end{lemma}
-
-\begin{proof}
-First, we observe that
-\begin{align}
-&\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)} \nonumber \\
-\iff &\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{9.6\sigma^2}{\lambda^2}. \nonumber 
-\end{align}
-Since $\log(x)\leq x-1$ for $x>0$, we know 
-\begin{align}
-\log(\log_{1.1}(n)+1)=\log\left(\frac{\log(n)}{\log(1.1)}+1\right)\leq \log(11\log(n)+1)\leq \log(11n)\leq 3+\log(n). \nonumber
-\end{align}
-
-Thus, we know
-\begin{align}
-\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{n}{3+\log(n)}. \nonumber 
-\end{align}
-
-To prove the lemma, we just need to show for $n\geq n_{0}$, we have
-\begin{align}
-\frac{n}{3+\log(n)}\geq \frac{9.6\sigma^2}{\lambda^2}. \label{n0-equ}
-\end{align}
-Inequality~(\ref{n0-equ}) is true because of the following two observations:
-\begin{itemize}
-\item for $n\geq 50$, we have $\frac{n}{3+\log(n)}\geq n^{0.5}$;
-\item for $n\geq \frac{92.16\sigma^4}{\lambda^4}$, we have $n^{0.5}\geq {9.6\sigma^{2}}{\lambda^{2}}$.
-\end{itemize}
-
-Thus, we know our lemma is true.
-
-\end{proof}
-
-To prove Lemma~\ref{round:prob}, we also need to use an adaptive concentration inequality due to \cite{zhao2016adaptive}. For reference, we state it here as a Lemma.
-
-\begin{lemma}[Corollary 1 in \cite{zhao2016adaptive}]
-Let $X_{i}$ be zero mean $1/2$-subgaussian random variables.
-$\{S_{n}=\sum_{i=1}^{n}X_{i},n\geq 1\}$ be a random walk.
-Let $J$ be any stopping time with respect to $\{X_1,X_2,\cdots\}$.
-We allow $J$ to take the value of $\infty$ where $P(J=\infty)=1-\lim_{n\rightarrow \infty}P(J\leq n)$.
-If
-\begin{align}
-f(n)=\sqrt{0.6n\log(\log_{1.1}(n)+1)+bn}, \nonumber
-\end{align}
-then
-\begin{align}
-Pr[\{S_{J}\geq f(J)\}\cap \{J<\infty\}]\leq 12e^{-1.8b}. \nonumber
-\end{align}
-\label{ACI-inequality}
-\end{lemma}
-
-We now prove Lemma~\ref{round:prob}.
-
-\begin{proof}[Proof of Lemma~\ref{round:prob}]
-In the $n^{th}$ round, we know all arms have been pulled at least $n$ times.
-For all the agents $\theta$ whose utility difference between their best and second best arm is greater than $2mW\lambda$, denote $K(\theta)=\max_{i\neq B(\theta)}\{\theta\cdot u_{i,t}\}$.
-If $|u_{i,t}^{j}-u_{i}^{j}|\leq \lambda$ for all $i,j$, then
-\begin{align}
-&\theta\cdot(u_{B(\theta),t}-u_{K(\theta),t}) \nonumber \\
-\geq & \theta\cdot(u_{B(\theta),t}-u_{B(\theta)}) + \theta\cdot(u_{K(\theta)}-u_{K(\theta),t}) + \theta\cdot(u_{B(\theta)}-u_{K(\theta)}) \nonumber \\
-> & -Wm\lambda - Wm\lambda + 2Wm\lambda = 0,\nonumber
-\end{align}
-which means their myopic action would incur no regret.
-
-Define $\epsilon_{i,\tau}=u_{i,\tau}-u_i$ and $\epsilon_{i,\tau}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,\tau}$. Thus, we have
-\begin{align}
-&P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\nonumber \\
-\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda |\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda). \label{ACI}
-\end{align}
-
-To bound equation~(\ref{ACI}), we use Lemma~\ref{ACI-inequality}. Define
-\begin{align}
-S_{N(i,\tau)}^{i,j}=\frac{\epsilon_{i,\tau}^{j}}{2\sigma}. \nonumber
-\end{align}
-
-Based on Lemma~\ref{n0-inequality}, for $n_{0}=\max\{50, \frac{92.16\sigma^2}{\lambda^2}\}$ and $n\geq n_{0}$, we have
-\begin{align}
-\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-
-Thus, if we set $b=\frac{n\lambda^2}{16\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,\tau)\geq n\geq n_{0}$, we have
-\begin{align}
-\frac{N(i,\tau)\lambda}{2\sigma}\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)}+\frac{\lambda}{4\sigma}\sqrt{n N(i,\tau)} \nonumber \\
-\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)+bN(i,\tau)}, \nonumber 
-\end{align}
-where the last inequality is because $\sqrt{x}+\sqrt{y}\geq \sqrt{x+y}$. Thus, we have
-\begin{align}
-&P(\epsilon_{i,\tau}^{j}\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P\left(S_{N(i,\tau)}^{i,j}\geq \frac{N(i,\tau)\lambda}{2\sigma}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
-\leq & P\left(S_{N(i,\tau)}^{i,j}\geq \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
-\leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
-\end{align}
-Similarily, we can bound 
-\begin{align}
-&P(\epsilon_{i,\tau}^{j}\leq-\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P(-\epsilon_{i,\tau}^{j}\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber 
-\end{align}
-
-Therefore, we know $P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right)$.
-Thus, we know
-\begin{align}
-&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)  \nonumber \\
-\leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
-\end{align}
-
-\end{proof}
-
-Before we start analyzing the cumulative regret, we first prove the following lemma which bounds the expected length of each round.
-
-\begin{lemma}
-Using our algorithm, we have $\mathbb{E}[t_{n+1}-t_{n}]\leq Nn$, $\forall n\geq 1$.
-\label{round:length}
-\end{lemma}
-
-\begin{proof}
-	A round completes when each arm is pulled at least once in that round.
-Let $X_{i}$ be the number of agents who come to the system between the time after the $(i-1)^{th}$ unique arm was pulled, up to and including the time when the $i^{th}$ unique arm was pulled.
-Then we know
-\begin{equation*}
-\mathbb{E}[t_{n+1}-t_{n}]=\sum_{i=1}^{N}E[X_{i}].
-\end{equation*}
-
-Fix $i$.
-In bounding $X_i$, we think of agents as ``trials'', where each trial can result in a new unique arm being pulled (which we call a ``successful'' trial), or not.
-There are two ways a trial can be successful:
-\begin{itemize}
-\item If there is at least one arm that has not been pulled and the probability of an agent utility function that would pull this arm without incentives is less than $n^{-1}$, then the principal will offer an incentive that causes this arm to be pulled (or one of these arms if there is more than one).
-In this case, the probability that the trial is succesful is $1$.
-\item The probability of an agent utility function that would pull each un-pulled arm without incentives is at least $n^{-1}$.
-In this case, the probability that the trial is successful is at least $n^{-1}$.
-\end{itemize}
-
-Thus, $X_{i}$ is stochastically dominated below by a geometric random variable with success probability $n^{-1}$, the expected number of trials up to and including the first success, $E[X_i]$, is bounded above by $n$.
-Thus,
-\begin{align}
-E[t_{n+1}-t_{n}]\leq Nn. \nonumber
-\end{align}
-\end{proof}
-
-We also need the following lemma in part of the proof of Theorem~\ref{rst:budget}.
-\begin{lemma}
-For all $n\geq 1$, we have
-\begin{align}
-0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-\label{lemma:cal2}
-\end{lemma}
-\begin{proof}
-\begin{align}
-&0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)} \nonumber \\
-\iff & 0.81 n^{5/3} \geq 0.6n \log(\log_{1.1}(n)+1) \nonumber \\
-\iff &  \frac{81}{60} n^{2/3} \geq  \log(\log_{1.1}(n)+1) \nonumber
-\end{align}
-
-Denote $f(x) = \frac{81}{60}x^{2/3} - \log(\log_{1.1}(x)+1)$.
-It's easy to compute $f^{'}(x)=0$ has a unique solution $x_{0}=e^{2/3w(\frac{20e^{20000/314763}}{27})-\frac{10000}{104921}}$ (here $w(\cdot)$ is the Lambert W-Function) and it is the global minimum.
-Since $f(x_{0})\approx 0.0252 >0$, we know $f(x)>0$ for all $x\geq 1$.
-Thus, our lemma holds true.
-\end{proof}
-
-Now we are ready to prove our first main result, Theorem~\ref{rst:budget}.
-
-\begin{proof}
-Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$.
-Denote $\epsilon_{i,t}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,t}$.
-Denote $\omega$ to be a sample path and $n(t,\omega)$ to be the round number for sample path $\omega$ at time $t$.
-For a fixed time $t$, define
-\begin{align}
-L^{'}[l](t) = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n(t,\omega),l), \forall i,j\}\nonumber
-\end{align}
-where $g(n,l)$ is a function which we will define later.
-Define $L[1](t) = L^{'}[1](t)$ and $L[i](t) = L^{'}[i](t)\setminus L^{'}[i-1](t)$ for $i\geq 2$.
-We call $L[l](t)$ the $l^{th}$ envelope at time $t$.
-We often simplify the notation and use $L[l]$ instead of $L[l](t)$ without confusion.
-
-In the calculation below, we omit the dependency on $\omega$ when refering to variables $c(t)$, $\epsilon_{i,t}^{j}$ and $t_n$.
-Based on the definition of $L[l]$, we know if $\omega\in L[l]$, the maximum payment we need to offer at time $t$ is bounded above by
-\begin{align}
-&\max_{i}\theta_t\cdot u_{i,t} - \min_{j}\theta_t\cdot u_{j,t} \nonumber \\
-= &\max_{i}\theta_t\cdot (\epsilon_{i,t}+u_i) - \min_{j}\theta_t\cdot (\epsilon_{j,t}+u_j) \nonumber \\
-\leq &\max_{i}\theta_t\cdot u_i - \min_{j}\theta_t\cdot u_j +\max_{i}\theta_t\cdot \epsilon_{i,t} - \min_{j}\theta_t\cdot \epsilon_{j,t}\nonumber \\
-\leq & R + 2Wmg(n,l). \nonumber
-\end{align}
-
-Based on the above notations, we can rewrite the cumulative payment as follows:
-\begin{align}
-&\sum_{t=1}^{\infty}c(t) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\} \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
-\end{align}
-
-Set $g(n,l)$ to be $\frac{2\sigma l}{n^{1/6}}$.
-Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2Wm\lambda\}$, they will correctly identify their best arm.
-Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{2\sigma l}{n^{1/6}} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
-Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms.
-Denote $a_0=\frac{4Wm\sigma}{p^{-1}(\frac{p}{2})}$.
-In order to have $\frac{2\sigma l}{n^{1/6}}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil (a_{0} l)^6 \rceil$.
-In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
-Denote $n_2=\frac{2}{p}$.
-Thus, we know we can only incur regret for sample paths $\omega$ in the $l^{th}$ envelope in the first $\max\{n_2,\lceil (a_0 l)^6 \rceil\}$ rounds.
-
-Thus,
-\begin{align}
-\sum_{t=1}^{\infty}c(t)=\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
-\end{align}
-
-Therefore,
-
-\begin{align}
-&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}E[c(t)|\omega \in L[l],t\in [t_n,t_{n+1}))P(\omega\in L[l],t\in [t_n,t_{n+1})) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+2Wm\frac{2\sigma l}{n^{1/6}}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})). \nonumber
-\end{align}
-
-We now bound $P(\omega\in L[l]|t\in[t_{n},t_{n+1}))$ for $n\geq n_0$ and $l\geq 2$.
-\begin{align}
-&P(\omega\in L[l]|t\in[t_{n},t_{n+1})) \nonumber \\
-=&P(\omega\in L^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in L^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
-\leq & 1-P\left(|\epsilon_{i,t}^{j}|<\frac{2\sigma (l-1)}{n^{1/6}}, \forall i,j|t\in[t_n,t_{n+1})\right) \nonumber \\
-=&P\left(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})\right) \nonumber  \\
-\leq &\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})\right) \nonumber
-\end{align}
-
-Define $S_{i,t}^{j}=\frac{N(i,t)\epsilon_{i,t}^{j}}{2\sigma}$, then we know $S_{i,t}^{j}$ is a summation of $1/2$ gaussian random numbers. Therefore,
-
-\begin{align}
-&\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma(l-1)}{n^{1/6}}\bigg|t\in[t_n,t_{n+1})\right) \nonumber \\ 
-=&\sum_{i,j}P\left(|S_{i,t}^{j}|\geq \frac{N(i,t)(l-1)}{n^{1/6}}\bigg|t\in[t_n,t_{n+1})\right) \nonumber \\
-\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})). \nonumber
-\end{align}
-
-Based on Lemma~\ref{lemma:cal2}, we know
-\begin{align}
-&N(i,t)^{5/6}(l-1) \nonumber \\
-=& 0.9N(i,t)^{5/6} + N(i,t)^{5/6}(l-1.9) \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)} + \sqrt{(l-1.9)^2 N(i,t)} \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+(l-1.9)^2 N(i,t)}. \nonumber
-\end{align}
-
-Based on Lemma~\ref{ACI-inequality}, we know
-\begin{align}
-&\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})) \nonumber \\
-\leq & \sum_{i,j}24e^{-1.8(l-1.9)^2} = 24Nme^{-1.8(l-1.9)^2}. \nonumber
-\end{align}
-
-Thus,
-\begin{align}
-&\sum_{t=1}^{\infty}c(t) \nonumber \\
-\leq&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+2Wm\frac{2\sigma l}{n^{1/6}}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-\leq& \sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(\omega\in L[1]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-+&\sum_{l=2}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-\leq& \sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(t\in [t_n,t_{n+1})) \nonumber \\
-+&\sum_{l=2}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]24Nme^{-1.8(l-1.9)^2}P(t\in [t_n,t_{n+1})) \nonumber \\
-\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]Nn +\sum_{l=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]24Nme^{-1.8(l-1.9)^2}Nn \nonumber \\
-\leq & \left[R+4Wm\sigma \right]N (\max\{n_2,\lceil (a_0)^6 \rceil\})^2+\sum_{l=2}^{\infty}24N^2 m[R+4Wml\sigma](\max\{n_2,\lceil (a_0 l)^6 \rceil\})^2 e^{-1.8(l-1.9)^2} \nonumber \\
-=& O(N^2). \nonumber
-\end{align}
-
-\end{proof}
-
-\begin{lemma}
-The expected number of payments for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$.
-\label{lemma:numP}
-\end{lemma}
-
-\begin{proof}
-If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2mW\lambda\}$, they will correctly identify their best arm.
-Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms.
-In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
-Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$.
-Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).
-
-Define $\tau_{n}^{i}$ to be the first time we pull arm $i$ in the $n^{th}$ round. Then
-\begin{align}
-\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\} =\sum_{n=1}^{\infty}\sum_{i=1}^{N}\mathbbm{1}\{c(\tau_{n}^{i})>0\}. \nonumber
-\end{align}
-
-The cumulative expected number of payments is bounded above by:
-\begin{align}
-&E\left[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}\right] \nonumber \\
-=&\sum_{n=1}^{\infty}\sum_{i=1}^{N}P(c(\tau_{n}^{i})>0) \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}P\left(\exists i,j:|u_{i}^{j}-u_{i,\tau_{n}^{i}}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2Wm}\right)+\sum_{n=1}^{n_1}N \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right) +\sum_{n=1}^{n_1}N \nonumber \\
-\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right)\times N+\sum_{n=1}^{n_1}N \nonumber  \\
-\leq&24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1, \nonumber
-\end{align}
-
-Thus, we know the expected number of payments is bounded above by $O(N^2)$.
-
-\end{proof}
-
-Now we are ready to prove our second main result, Theorem~\ref{rst:regret}.
-
-\begin{proof}
-For regret incurred in the first $n_0$ round, it is bounded above by $\sum_{n=1}^{n_{0}}NRn$.
-
-For regret incurred after the first $n_0$ round, it has two different components: the regret incurred when we let the agents play myopically and the regret incurred when we incentivize the agents.
-Using Lemma~\ref{lemma:numP}, the expected regret incurred when we incentivize the agents is bounded above by: $\left[24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1\right]R$.
-
-For the regret incurred when we let the agents play myopically at time $t\geq t_{n_0}$, it consists of the following two components:
-\begin{itemize}
-\item For those users whose utility difference between their best and the second best arm is greater than $f(t)$: we define a sequence of stopping time $\tau_{n}^{k}$ to be the $k^{th}$ time period in the $n^{th}$ round.
-For $\tau_{n}^{k}=t$, the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)\times R$.
-We denote the regret incurred by these agents as $r_1(\tau_{n}^{k})$.
-\item For those user whose utility difference between their best and the second best arm is smaller than $f(t)$: this happens with probability $S(f(t))$ at each time and regret is bounded above by $S(f(t)) \times f(t)=Mf(t)^2$.
-We denote the regret incurred by these agents as $r_2(t)$.
-\end{itemize}
-
-Thus, the cumulative expected regret incurred up to time $T$ when we let the agent play myopically is bounded above by:
-\begin{align}
-&E\left[\sum_{t=1}^{T}r(t)\right] \nonumber \\
-=&E\left[\sum_{t=1}^{t_{n_{0}}} r(t) + \sum_{t=t_{n_{0}}}^{T}(r_1(t)+r_2(t))\right]  \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}-1}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-&\bccomment{\text{is the following proof correct? I think it might be wrong}} \nonumber \\
-= & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{t_{n+1}-t_{n}}r_1(\tau_{n}^{k})\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{k=1}^{t_{n+1}-t_n}24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{k=1}^{t_{n+1}-t_n}24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \label{equ:regret}
-\end{align}
-
- Thus the cumulative regret at time $T$ is bounded above by
-\begin{align}
-&\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-+ & 24N^2 m \frac{1}{e^{\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2}}-1}R+N\left(\max\left\{n_{0},\frac{2}{p}\right\}\right)R. \nonumber
-\end{align}
-
-For a fixed $T$, we only need to minimize the following two terms since all others are constant:
-
-\begin{align}
-\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2.
-\end{align}
-
-If we set $f^2(t)=\frac{2\log(T)\times 64W^2 m^2\sigma^2}{1.8t}$, then
-\begin{align}
-&\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\ 
-\leq & \sum_{n=1}^{T} 24N^2 mnR \exp\left(-2\log(T)\right)  + \frac{128W^2 m^2\sigma^2 M\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{n} \nonumber \\
-\leq &  24N^2 m R\frac{T(T-1)}{2T^2}  + 71.12 W^2 m^2\sigma^2 M\log(T)(\log(T)+1) \nonumber \\
-\leq &  12 N^2 m R  + 71.12 W^2 m^2\sigma^2 M\log(T)(\log(T)+1). \nonumber
-\end{align}
-
-Thus, the cumulative expected regret is bounded by $O(N^2 m + M m^2\log(T))$.
-\end{proof}
-
-\begin{corollary}
-If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O(N^2)$.
-\end{corollary}
-
-\begin{proof}
-The proof of this corollary is similar to the proof of Theorem~\ref{rst:regret}.
-If we set $f^2(t)=\frac{2\log(T)\times 64W^2 m^2\sigma^2}{1.8t}$, then there exists a $t_{0}$ such that for $t>t_{0}$, $S(f(t))=0$.
-Thus, similar to equation~\eqref{equ:regret}, we know the cumulative expected regret when we let the agents play myopically is bounded above by
-\begin{align}
-\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{t_{0}}Mf(t)^2 \nonumber
-\end{align}
-Therefore, based on the same analysis of Theorem~\ref{rst:regret}, we know the cumulative regret is bounded by $O(N^2)$.
-\end{proof}
-
-\subsection{Practical Issues}
-\label{sec:pi}
-
-In Algorithm~\ref{Alg1}, we use ``pay whatever it takes'' strategy when we decide to incentivize the agent.
-However, ''pay whatever it takes'' only shows up in the proof of Lemma~\ref{round:length}.
-Without loss of generality, suppose we want to incentivize arm $i$ at time $t$ at the $n^{th}$ round.
-Based on the proof of Lemma~\ref{round:length}, as long as we offer a payment $c_{i,t}$ such that arm $i$ has at least $n^{-1}$ probability being pulled at time $t$, our results still hold true.
-We could compute this $c_{i,t}$ dynamically based on $F(\cdot)$ as well as our current estimate $u_{i,t}$.
-Here is the revised algorithm which would work well in practice:
-
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration}
-\label{Alg2}
-\begin{algorithmic}
-\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
-\FOR{ $t = 1, 2, 3, \cdots$}{
-	\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
-  \IF {$S\setminus V$ is non-empty}
-    \STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
-	\STATE{Offer payment $c_{i,t}=\inf\{c: P(\theta\sim F: \theta\cdot u_{i,t}+c>max_{j}\theta\cdot u_{j,t})>n^{-1}\}$}
-  \ELSE
-  \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
-  \ENDIF
-  \STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
-  \IF {$n\neq \min_{i}N(i,t)$} 
-  	\STATE $V=\emptyset$
-  \ENDIF
-  \STATE Update the round number, $n = \min_{i} N(i,t)$
-}\ENDFOR
-
-\end{algorithmic}
-\end{algorithm}
-
-The same proof would work and we can get the exact same results as Algorithm~\ref{Alg1}.
-
-\section{Lower Bound $\Omega(\log(T))$}
-\label{sec:lb}
-
-In this section, we assume $\theta$ follows a continuous distribution $F(\cdot)$.
-We provide an example to show the best possible lower bound is $\Omega(\log(T))$ regardless of the incentivizing strategy.
-
-Suppose we have two arms.
-Arm $1$ has attribute vector $(0,0)$ and arm $2$ has attribute vector $(0,1)$.
-We assume the users' preference are uniformly distributed on the unit circle.
-If the user knows the exact attribute vectors for both arms, then the users with preference on the bottom half circle will choose arm $1$ and the users with preference on the top half circle will choose arm $2$.
-
-Consider the following algorithm: at each step, let the agents play myopically; however, they are going to see the noisy rewards for both arms.
-
-To lower bound the regret, we assume that the agents already know the true attribute vector for arm $1$.
-Without loss of generality, denote $u_{2,t} = (0,1)+(z_{t,1},z_{t,2}) = (0,1)+ (N(0,1/t),N(0,1/t))$ to be the estimate attribute vector for arm $2$ (Without loss of generality, we assume the variance for the noise is $1$).
-
-Since $(z_{t,1}, z_{t,2})$ is symmetric around $(0,0)$, we know
-
-\begin{align}
-&E[r(t)] \nonumber \\
-= &E[r(t) | z_{t,1}>0,z_{t,2}>0] \times P(z_{t,1}>0,z_{t,2}>0) + E[r(t) |z_{t,1}>0,z_{t,2}<0] \times P(z_{t,1}>0,z_{t,2}<0) \nonumber \\
-&+E[r(t) | z_{t,1}<0,z_{t,2}>0] \times P(z_{t,1}<0,z_{n,2}>0) + E[r(t) |z_{t,1}<0,z_{t,2}<0] \times P(z_{t,1}<0,z_{t,2}<0) \nonumber \\
-\geq & 0.25 \times E[r(t) | z_{t,1}>0, z_{t,2}>0]. \nonumber
-\end{align}
-
-Given $z_{t,1}>0$ and $z_{t,2}>0$, we know users whose preference vector between $(-1,0)$ and $\left(\frac{-1-z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ as well as users whose preference vector between $(1,0)$ and $\left(\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{-z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ will make a mistake.
-The regret is the absolute value of the second coordinate of the user's preference vector.
-Thus, we know
-
-\begin{align}
-&E[r(t)| z_{t,1}>0, z_{t,2}>0] \nonumber \\
-=& 4\times 2 \int_{0}^{\infty} \int_{0}^{\infty} \int_{0}^{\arctan\left(\frac{z_{t,1}}{1+z_{t,2}}\right)}\frac{\sin(\theta)}{2\pi}d(\theta)\frac{e^{-\frac{t \times z_{t,1}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,1})\frac{e^{-\frac{t \times z_{t,2}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,2}) \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}t\times \left[1-\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right]e^{-\frac{t \times z_{t,1}^2}{2}}e^{-\frac{t \times z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty} \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber
-\end{align}
-
-Below, we want to show 
-\begin{align}
-\lim_{t\rightarrow\infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} = O(1), \nonumber
-\end{align}
-and use the fact that $\sum_{n=1}^{T}\frac{1}{n}=O(\log(T))$ to show the regret is at least $\Omega(\log(T))$.
-
-Denote $d(t)=t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]$.
-Since
-\begin{align}
-d^{'}(t)=\frac{-z_{t,1}^2(2z_{t,2}+3\sqrt{t})-2(z_{t,2}+\sqrt{t})^3}{2(z_{t,1}^2+(z_{t,2}+\sqrt{t})^2)^{3/2}}+1. \nonumber
-\end{align}
-
-and $\lim_{t\rightarrow \infty}d^{'}(t)=2$, we know for $t$ large enough, $d(t)$ is a increasing function in terms of t. Thus, based on the Monotone Convergence Theorem, we have
-
-\begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber
-\end{align}
-
-Based on our calculation, we know
-
-\begin{align}
-\lim_{t\rightarrow \infty} d(t)=\frac{z_{t,1}^2}{2}. \nonumber
-\end{align}
-Thus,
-\begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} \nonumber \\
-=&\frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ \frac{z_{t,1}^2}{2}e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) = \frac{1}{2\pi}.
-\nonumber
-\end{align}
-
-Thus, the cumulative expected regret is at least $\Omega(\log(T))$.
-
 \section{Conclusion}
@@
 We propose a simple policy that mostly exploits and occasionally incentivizing exploration, which can achieve $O(N^2+M(\log(T))^2)$ cumulative expected regret with $O(N^2)$ payment budget.
-
-\bibliography{reference}{}
-\bibliographystyle{plain}
-
-\end{document}

### 2018-01-26 introduction.tex
divide the paper into sections

--- 2017-12-04 paper.tex
@@
-\documentclass{article}
-\usepackage[utf8]{inputenc}
+\section{Introduction}
 
-\usepackage[english]{babel}
+Here we pursue an alternate direction to our analysis of incentivizing exploration with heterogeneous preferences: we consider approximation-style results comparing achievable algorithm performance across four different problem settings, described in the table below.
 
-\usepackage{blindtext}
-\usepackage{amssymb}
+\begin{center}
+\begin{tabular}{ c|c|c| } 
+ \hline
+     & Pulls arms directly & Needs to incentivize \\ 
+\hline
+ Perfect Info on Preferences & $C11$: The ``God'' Policy & $C12$ \\ 
+ Partial Info on Preferences & $C21$ & $C22$: actual algorithm \\ 
+ \hline
+\end{tabular}
+\end{center}
 
-\usepackage[]{algorithm}
-\usepackage[]{algorithmic}
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{xr} 
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{amsthm}
-\usepackage{comment}
-\usepackage{graphicx}
-\usepackage{subcaption}
-\usepackage{xcolor}
-\usepackage{amsmath}
-\usepackage{dblfloatfix}
-\usepackage{bbm}
+Columns indicate whether the principal pulls arms directly (left column) or incentivizes agents who in turn actually pull the arms.
+Rows indicate whether the principal knows the preferences of the agents (top row) or not (bottom row).
+Problem settings correspond to cells and are described by the names C11, C12, and so on.
+An optimal algorithm for problem setting C11 has the best performance possible.
 
-\newcommand{\IE}{IE} 
-\newcommand{\argmax}{\mathop{\mathrm{argmax}}}
+We wish to make two high-level points through this analysis:
 
-\newcommand\floor[1]{\lfloor#1\rfloor}
-\newcommand\ceil[1]{\lceil#1\rceil}
+\begin{itemize}
+\item First, better performance is possible in setting C22 than in setting C21, in the sense we can find tight approximation guarantees relative to C11 that are better for C22 than for C21.
+This is achieved by setting up incentives in C22 that still allow agents to select arms aligned with their preferences, providing selections of arms that contain more information than in C21.
+\item Second, heterogeneity in preferences improves performance over what can be achieved in a setting with homogeneous preferences.
+This would be in the spirit of David K.'s results that heterogeneity in preference for money can be exploited to reduce the budget required.
+\end{itemize}
 
-\newcommand{\bccomment}[1]{{\color{blue}BC: #1}}
-\newcommand{\pfcomment}[1]{{\color{blue}PF: #1}}
-
-\newtheorem{definition}{Definition}[section]
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-\newtheorem{assumption}{Assumption}
-
-\title{Incentivizing Exploration with Heterogeneous Utilities}
-
-\begin{document}
-
-\maketitle
-
-\section{Introduction}
 In this paper, we study incentivizing exploration with heterogeneous agent preferences.
@@
 We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+M(\log(T))^2)$ regret with $O(N^2)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
-
-\section{Problem Setting}
-\label{sec:prob}
-
-We have $N$ arms. Arm $i$ has a fixed but unknown attribute vector $u_i\in \mathbb{R}^{m}$. 
-A stream of myopic selfish agents come to our system.
-Agent $t$ has linear preferences over attributes described by a vector $\theta_t \in \mathbb{R}^m$ that is unknown to the principal and drawn i.i.d.
-from a known distribution $F(\cdot)$ with compact support.
-We refer synonomously to an agent and that agent's preference vector: when we say ``an agent $\theta$'', we mean ``an agent with preference vector $\theta$.''
-
-Each agent $t$ chooses an arm to pull $A_t$, according to a process described below, and obtains utility $\theta_t \cdot u_{A_{t}}$.
-The principal and all agents then see a noisy observation of the attribute vector of the pulled arm of the form $O_t=u_{A_{t}}+\epsilon_{t}$, where $\epsilon_t\sim N(0, \sigma^2 I_{m})$ is independent normally distributed noise, and $I_m$ denotes an $m$-dimensional identity matrix.
-Although we assume a common variance across attributes for simplicity of presentation, our theoretical results hold if the variance differs.
-
-At each time $t$, for each arm $i$, we (the principal) offer a non-negative payment $c_{i,t}\geq 0$ based on previous observations.
-We assume that agent $t$ chooses to pull the arm that myopically maximizes the sum of this payment and an estimate of the utility obtained $\theta_t \cdot u_{i,t}$ where $u_{i,t}$ denotes the simple average of $O_s$ over all previous pulls of arm $i$.
-In this paper, we assume all arms have been pulled once at time $t=0$ and $u_{i,0}$ denotes a random draw from the arm attribute vector.
-For $t>0$, denote $u_{i,t} = \frac{\sum_{s<t} O_s 1\{A_s = i\} + u_{i,0}}{\sum_{s<t} 1\{A_s = i\}+1}$ and $A_t=\argmax_{i}\{\theta_t\cdot u_{i,t}+c_{i,t}\}$, breaking ties in favor of the arm with the highest incentive.
-We use $c_t=c_{A_{t},t}$ to denote the actual incentive payment at time $t$.
-
-This behavior may be recovered if agents are Bayesian and share a common non-informative prior distribution that is constant over $\mathbb{R}^m$ and know $\sigma^2$.
-In this case, the posterior distribution on $u_{i}$ at time $t$ is multivariate normal with mean $u_{i,t}$, and the expected value of $\theta_t \cdot u_i$ under this posterior conditioned on $\theta_t$ is $\theta_t \cdot u_{i,t}$ (see equation $2.13$ in section $2.5$, \cite{Ge04}).
-Alternatively, one may simply take our assumption that agents use the average as their estimate of an attribute value directly without such a Bayesian justification.
-
-We define the regret at time $t$ as $r(t)=\max_{i}\{\theta_{t}\cdot u_{i}\}-\theta_t\cdot u_{A_t}$, and the cumulative regret up to time T as $R(T)=\sum_{t=1}^{T}r(t)$.
-Define the cumulative payment up to time T similarly as $C(t)=\sum_{t=1}^{T}c(t)$.
-As the principal, we want to find a strategy $\mathcal{A}$ under which both the cumulative expected regret $\mathbb{E}_{\mathcal{A}}[R(T)]$ and the cumulative expected payment $\mathbb{E}_{\mathcal{A}}[C(T)]$ are small.
-
-To support later development, we define some additional notation.
-We let $B(\theta)$ and $\hat{B}(\theta)$ refer to the index of the arm that is best and second best for an agent with preference vector $\theta$, $B(\theta) \in \argmax_i \theta \cdot u_i$ and $\hat{B}(\theta)=\argmax_{i\neq B(\theta)}\theta\cdot u_{i}$, breaking ties uniformly at random.
-We let $N(i,t)$ denote the number of pulls of arm $i$ at times up to and including $t$ plus $1$ (because of the initial pull), i.e.
-$N(i,t)=\sum_{s<t} 1\{A_s = i\}+1$.
-We call time $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$ the {\it starting point of the $n^{th}$ round}. We call the set of times $[t_{n}, t_{n+1})$ the {\it $n^{th}$ round}.
-
-\section{Algorithm and Upper Bound}
-\label{sec:ub}
-
-In this section, we propose a simple policy that mostly exploits, and occasionally incentivizes exploration when the probability of an arm would be pulled by all agent types below a time-varying threshold given the current posterior.
-We prove that with the help of heterogeneous preferences, we can get a certain amount of exploration for free via heterogeneity.
-
-\subsection{Our Algorithm}
-Our algorithm incentivizes pulling an arm $i$ at a time $t$ in round $n$ if and only if both of the following criteria are met:
-\begin{itemize}
-\item the probability of pulling arm $i$ would be below $n^{-1}$ without incentives; 
-\item arm $i$ has not been played previously in the current round.
-\end{itemize}
-Ties are broken randomly.  This algorithm does not need to know the horizon $T$ in advance.
-
-If our algorithm decides to incentivize an arm $i$, it uses the ``pay whatever it takes'' strategy in which the payment offered is $\max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$.
-This maximum over $\theta$ is taken over the support of $F$, which we recall is assumed compact.
-(We use this ``pay whatever it takes'' strategy for its simplicity, and in Section~\ref{sec:pi} we provide an alternate and smaller incentive payment that achieves the same payment budget bound and regret bound).
-
-We describe our algorithm in detail as follows:
-
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration}
-\label{Alg1}
-\begin{algorithmic}
-\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
-\FOR{ $t = 1, 2, 3, \cdots$}{
-	\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
-  \IF {$S\setminus V$ is non-empty}
-    \STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
-    \STATE{Pay whatever it takes to incentivize pulling arm $i$, i.e., offer payment 
-    $c_{i,t} = \max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$ and $c_{j,t} = 0$ for $j \ne i$.}
-  \ELSE
-  \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
-  \ENDIF
-  \STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
-  \IF {$n\neq \min_{i}N(i,t)$} 
-  	\STATE $V=\emptyset$
-  \ENDIF
-  \STATE Update the round number, $n = \min_{i} N(i,t)$
-}\ENDFOR
-
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{Assumptions}
-In this section, we state several assumptions assumed by our analysis.  First define
-\begin{align}
-\Omega_{i,j}=\{\theta:B(\theta)=i, \hat{B}(\theta)=j\}, \nonumber 
-\end{align}
-which is the set of agent preferences whose best arm is arm $i$ and second best arm is arm $j$. With this definition, our analysis makes the following assumptions:
-
-\begin{assumption} Let $F_{i,j}(y)$ be the marginal cumulative density function (or cumulative mass function if $F(\cdot)$ is a discrete distribution) of $(u_i-u_j)\cdot\theta$ conditioned on $\theta \in \Omega_{i,j}$.
-We assume $F_{i,j}(y)\leq My$ for all $y\in R^{+}$, $\forall i,j$.
-\label{A1}
-\end{assumption}
-
-As we can see later in our proof, we only need $\max_{i,j}\limsup_{y\rightarrow 0^{+}}\frac{F_{i,j}(y)}{y}$ to be finite.
-Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm.
-
-\begin{assumption} We assume $F$ has a compact support set. Without loss of generality, we assume $\theta\in [0,W]^m$.
-\label{A2}
-\end{assumption}
-
-We use $R = \max_{\theta, i,j} \theta \cdot (u_i - u_j)$ to denote the maximum regret that can be incurred at each time.  Assumption~\ref{A2} shows that $R<\infty$.
-
-\begin{assumption}
-Denote $p=\min_{i}P(\{\theta: B(\theta)=i\})$. We assume $p>0$.
-\label{A3}
-\end{assumption}
-
-Assumption~\ref{A3} means each arm $i$ has a strictly positive proportion of users for which that arm is best.
-
-\subsection{General Results}
-
-In this section, we prove Algorithm~\ref{Alg1} achieves $O(N^2+M(\log(T))^2)$ cumulative regret with $O(N^2)$ payment budget.
-This is stated in the following pair of theorems, which together constitute our main results.
-
-\begin{theorem}
-The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$. 
-\label{rst:budget}
-\end{theorem}
-
-\begin{theorem}
-The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2 m + M m^2(\log(T))^2)$.
-\label{rst:regret}
-\end{theorem}
-
-Before we prove these two theorems, we must first introduce two additional pieces of notation, which will be used in preliminary lemmas.
-Let $S(\delta)$ be the proportion of users whose utility difference between their best and second best arm is less than $\delta$.
-Formally, $S(\delta)=P(\theta: \theta \cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}\leq \delta)$.
-Then, let $p(\delta)=\min_{i}P(\{\theta:B(\theta)=i,\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$.
-We know $p(0)=p$.
-
-With this additional notation, we now prove several lemmas.
-First, based on Assumption~\ref{A1}, we have the following bound for $S(\delta)$.
-
-\begin{lemma}
-$S(\delta)\leq M\delta$.
-\label{lemma:sdelta}
-\end{lemma}
-
-\begin{proof}
-\begin{align*}
-S(\delta)
-&=\sum_{i,j}P(\theta\cdot(u_{i}-u_{j})\le \delta|\theta\in \Omega_{i,j})P(\theta\in \Omega_{i,j}) \\
-&\leq \sum_{i,j}M\delta \times P(\theta\in \Omega_{i,j}) \\
-&=M\delta.
-\end{align*}
-\end{proof}
-
-The following lemma bounds the probability of making a mistake if we let the agents play myopically in the $n^{th}$ round, given that the utility difference between his/her best and second best arm is bounded below by a constant.
-
-\begin{lemma}
-Define $\tau$ to be any stopping time that is almost surely between $t_n$ and $t_{n+1}-1$ with respect to the filtration $\mathcal{F}_{t}=\sigma(A_1,\cdots,A_t,c_1,\cdots,c_t,O_1,\cdots,O_t)$, we have
-\begin{align}
-P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{16\sigma^2}\right), \nonumber
-\end{align}
-for $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$.
-\label{round:prob}
-\end{lemma}
-
-We need the following lemma in order to prove Lemma~\ref{round:prob}.
-
-\begin{lemma}
-For $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$, we have
-\begin{align}
-\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-\label{n0-inequality}
-\end{lemma}
-
-\begin{proof}
-First, we observe that
-\begin{align}
-&\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)} \nonumber \\
-\iff &\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{9.6\sigma^2}{\lambda^2}. \nonumber 
-\end{align}
-Since $\log(x)\leq x-1$ for $x>0$, we know 
-\begin{align}
-\log(\log_{1.1}(n)+1)=\log\left(\frac{\log(n)}{\log(1.1)}+1\right)\leq \log(11\log(n)+1)\leq \log(11n)\leq 3+\log(n). \nonumber
-\end{align}
-
-Thus, we know
-\begin{align}
-\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{n}{3+\log(n)}. \nonumber 
-\end{align}
-
-To prove the lemma, we just need to show for $n\geq n_{0}$, we have
-\begin{align}
-\frac{n}{3+\log(n)}\geq \frac{9.6\sigma^2}{\lambda^2}. \label{n0-equ}
-\end{align}
-Inequality~(\ref{n0-equ}) is true because of the following two observations:
-\begin{itemize}
-\item for $n\geq 50$, we have $\frac{n}{3+\log(n)}\geq n^{0.5}$;
-\item for $n\geq \frac{92.16\sigma^4}{\lambda^4}$, we have $n^{0.5}\geq {9.6\sigma^{2}}{\lambda^{2}}$.
-\end{itemize}
-
-Thus, we know our lemma is true.
-
-\end{proof}
-
-To prove Lemma~\ref{round:prob}, we also need to use an adaptive concentration inequality due to \cite{zhao2016adaptive}. For reference, we state it here as a Lemma.
-
-\begin{lemma}[Corollary 1 in \cite{zhao2016adaptive}]
-Let $X_{i}$ be zero mean $1/2$-subgaussian random variables.
-$\{S_{n}=\sum_{i=1}^{n}X_{i},n\geq 1\}$ be a random walk.
-Let $J$ be any stopping time with respect to $\{X_1,X_2,\cdots\}$.
-We allow $J$ to take the value of $\infty$ where $P(J=\infty)=1-\lim_{n\rightarrow \infty}P(J\leq n)$.
-If
-\begin{align}
-f(n)=\sqrt{0.6n\log(\log_{1.1}(n)+1)+bn}, \nonumber
-\end{align}
-then
-\begin{align}
-Pr[\{S_{J}\geq f(J)\}\cap \{J<\infty\}]\leq 12e^{-1.8b}. \nonumber
-\end{align}
-\label{ACI-inequality}
-\end{lemma}
-
-We now prove Lemma~\ref{round:prob}.
-
-\begin{proof}[Proof of Lemma~\ref{round:prob}]
-In the $n^{th}$ round, we know all arms have been pulled at least $n$ times.
-For all the agents $\theta$ whose utility difference between their best and second best arm is greater than $2mW\lambda$, denote $K(\theta)=\max_{i\neq B(\theta)}\{\theta\cdot u_{i,t}\}$.
-If $|u_{i,t}^{j}-u_{i}^{j}|\leq \lambda$ for all $i,j$, then
-\begin{align}
-&\theta\cdot(u_{B(\theta),t}-u_{K(\theta),t}) \nonumber \\
-\geq & \theta\cdot(u_{B(\theta),t}-u_{B(\theta)}) + \theta\cdot(u_{K(\theta)}-u_{K(\theta),t}) + \theta\cdot(u_{B(\theta)}-u_{K(\theta)}) \nonumber \\
-> & -Wm\lambda - Wm\lambda + 2Wm\lambda = 0,\nonumber
-\end{align}
-which means their myopic action would incur no regret.
-
-Define $\epsilon_{i,\tau}=u_{i,\tau}-u_i$ and $\epsilon_{i,\tau}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,\tau}$. Thus, we have
-\begin{align}
-&P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\nonumber \\
-\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda |\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda). \label{ACI}
-\end{align}
-
-To bound equation~(\ref{ACI}), we use Lemma~\ref{ACI-inequality}. Define
-\begin{align}
-S_{N(i,\tau)}^{i,j}=\frac{\epsilon_{i,\tau}^{j}}{2\sigma}. \nonumber
-\end{align}
-
-Based on Lemma~\ref{n0-inequality}, for $n_{0}=\max\{50, \frac{92.16\sigma^2}{\lambda^2}\}$ and $n\geq n_{0}$, we have
-\begin{align}
-\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-
-Thus, if we set $b=\frac{n\lambda^2}{16\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,\tau)\geq n\geq n_{0}$, we have
-\begin{align}
-\frac{N(i,\tau)\lambda}{2\sigma}\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)}+\frac{\lambda}{4\sigma}\sqrt{n N(i,\tau)} \nonumber \\
-\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)+bN(i,\tau)}, \nonumber 
-\end{align}
-where the last inequality is because $\sqrt{x}+\sqrt{y}\geq \sqrt{x+y}$. Thus, we have
-\begin{align}
-&P(\epsilon_{i,\tau}^{j}\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P\left(S_{N(i,\tau)}^{i,j}\geq \frac{N(i,\tau)\lambda}{2\sigma}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
-\leq & P\left(S_{N(i,\tau)}^{i,j}\geq \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
-\leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
-\end{align}
-Similarily, we can bound 
-\begin{align}
-&P(\epsilon_{i,\tau}^{j}\leq-\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P(-\epsilon_{i,\tau}^{j}\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber 
-\end{align}
-
-Therefore, we know $P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right)$.
-Thus, we know
-\begin{align}
-&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)  \nonumber \\
-\leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
-\end{align}
-
-\end{proof}
-
-Before we start analyzing the cumulative regret, we first prove the following lemma which bounds the expected length of each round.
-
-\begin{lemma}
-Using our algorithm, we have $\mathbb{E}[t_{n+1}-t_{n}]\leq Nn$, $\forall n\geq 1$.
-\label{round:length}
-\end{lemma}
-
-\begin{proof}
-	A round completes when each arm is pulled at least once in that round.
-Let $X_{i}$ be the number of agents who come to the system between the time after the $(i-1)^{th}$ unique arm was pulled, up to and including the time when the $i^{th}$ unique arm was pulled.
-Then we know
-\begin{equation*}
-\mathbb{E}[t_{n+1}-t_{n}]=\sum_{i=1}^{N}E[X_{i}].
-\end{equation*}
-
-Fix $i$.
-In bounding $X_i$, we think of agents as ``trials'', where each trial can result in a new unique arm being pulled (which we call a ``successful'' trial), or not.
-There are two ways a trial can be successful:
-\begin{itemize}
-\item If there is at least one arm that has not been pulled and the probability of an agent utility function that would pull this arm without incentives is less than $n^{-1}$, then the principal will offer an incentive that causes this arm to be pulled (or one of these arms if there is more than one).
-In this case, the probability that the trial is succesful is $1$.
-\item The probability of an agent utility function that would pull each un-pulled arm without incentives is at least $n^{-1}$.
-In this case, the probability that the trial is successful is at least $n^{-1}$.
-\end{itemize}
-
-Thus, $X_{i}$ is stochastically dominated below by a geometric random variable with success probability $n^{-1}$, the expected number of trials up to and including the first success, $E[X_i]$, is bounded above by $n$.
-Thus,
-\begin{align}
-E[t_{n+1}-t_{n}]\leq Nn. \nonumber
-\end{align}
-\end{proof}
-
-We also need the following lemma in part of the proof of Theorem~\ref{rst:budget}.
-\begin{lemma}
-For all $n\geq 1$, we have
-\begin{align}
-0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-\label{lemma:cal2}
-\end{lemma}
-\begin{proof}
-\begin{align}
-&0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)} \nonumber \\
-\iff & 0.81 n^{5/3} \geq 0.6n \log(\log_{1.1}(n)+1) \nonumber \\
-\iff &  \frac{81}{60} n^{2/3} \geq  \log(\log_{1.1}(n)+1) \nonumber
-\end{align}
-
-Denote $f(x) = \frac{81}{60}x^{2/3} - \log(\log_{1.1}(x)+1)$.
-It's easy to compute $f^{'}(x)=0$ has a unique solution $x_{0}=e^{2/3w(\frac{20e^{20000/314763}}{27})-\frac{10000}{104921}}$ (here $w(\cdot)$ is the Lambert W-Function) and it is the global minimum.
-Since $f(x_{0})\approx 0.0252 >0$, we know $f(x)>0$ for all $x\geq 1$.
-Thus, our lemma holds true.
-\end{proof}
-
-Now we are ready to prove our first main result, Theorem~\ref{rst:budget}.
-
-\begin{proof}
-Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$.
-Denote $\epsilon_{i,t}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,t}$.
-Denote $\omega$ to be a sample path and $n(t,\omega)$ to be the round number for sample path $\omega$ at time $t$.
-For a fixed time $t$, define
-\begin{align}
-L^{'}[l](t) = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n(t,\omega),l), \forall i,j\}\nonumber
-\end{align}
-where $g(n,l)$ is a function which we will define later.
-Define $L[1](t) = L^{'}[1](t)$ and $L[i](t) = L^{'}[i](t)\setminus L^{'}[i-1](t)$ for $i\geq 2$.
-We call $L[l](t)$ the $l^{th}$ envelope at time $t$.
-We often simplify the notation and use $L[l]$ instead of $L[l](t)$ without confusion.
-
-In the calculation below, we omit the dependency on $\omega$ when refering to variables $c(t)$, $\epsilon_{i,t}^{j}$ and $t_n$.
-Based on the definition of $L[l]$, we know if $\omega\in L[l]$, the maximum payment we need to offer at time $t$ is bounded above by
-\begin{align}
-&\max_{i}\theta_t\cdot u_{i,t} - \min_{j}\theta_t\cdot u_{j,t} \nonumber \\
-= &\max_{i}\theta_t\cdot (\epsilon_{i,t}+u_i) - \min_{j}\theta_t\cdot (\epsilon_{j,t}+u_j) \nonumber \\
-\leq &\max_{i}\theta_t\cdot u_i - \min_{j}\theta_t\cdot u_j +\max_{i}\theta_t\cdot \epsilon_{i,t} - \min_{j}\theta_t\cdot \epsilon_{j,t}\nonumber \\
-\leq & R + 2Wmg(n,l). \nonumber
-\end{align}
-
-Based on the above notations, we can rewrite the cumulative payment as follows:
-\begin{align}
-&\sum_{t=1}^{\infty}c(t) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\} \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
-\end{align}
-
-Set $g(n,l)$ to be $\frac{2\sigma l}{n^{1/6}}$.
-Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2Wm\lambda\}$, they will correctly identify their best arm.
-Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{2\sigma l}{n^{1/6}} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
-Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms.
-Denote $a_0=\frac{4Wm\sigma}{p^{-1}(\frac{p}{2})}$.
-In order to have $\frac{2\sigma l}{n^{1/6}}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil (a_{0} l)^6 \rceil$.
-In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
-Denote $n_2=\frac{2}{p}$.
-Thus, we know we can only incur regret for sample paths $\omega$ in the $l^{th}$ envelope in the first $\max\{n_2,\lceil (a_0 l)^6 \rceil\}$ rounds.
-
-Thus,
-\begin{align}
-\sum_{t=1}^{\infty}c(t)=\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
-\end{align}
-
-Therefore,
-
-\begin{align}
-&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}E[c(t)|\omega \in L[l],t\in [t_n,t_{n+1}))P(\omega\in L[l],t\in [t_n,t_{n+1})) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+2Wm\frac{2\sigma l}{n^{1/6}}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})). \nonumber
-\end{align}
-
-We now bound $P(\omega\in L[l]|t\in[t_{n},t_{n+1}))$ for $n\geq n_0$ and $l\geq 2$.
-\begin{align}
-&P(\omega\in L[l]|t\in[t_{n},t_{n+1})) \nonumber \\
-=&P(\omega\in L^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in L^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
-\leq & 1-P\left(|\epsilon_{i,t}^{j}|<\frac{2\sigma (l-1)}{n^{1/6}}, \forall i,j|t\in[t_n,t_{n+1})\right) \nonumber \\
-=&P\left(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})\right) \nonumber  \\
-\leq &\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})\right) \nonumber
-\end{align}
-
-Define $S_{i,t}^{j}=\frac{N(i,t)\epsilon_{i,t}^{j}}{2\sigma}$, then we know $S_{i,t}^{j}$ is a summation of $1/2$ gaussian random numbers. Therefore,
-
-\begin{align}
-&\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma(l-1)}{n^{1/6}}\bigg|t\in[t_n,t_{n+1})\right) \nonumber \\ 
-=&\sum_{i,j}P\left(|S_{i,t}^{j}|\geq \frac{N(i,t)(l-1)}{n^{1/6}}\bigg|t\in[t_n,t_{n+1})\right) \nonumber \\
-\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})). \nonumber
-\end{align}
-
-Based on Lemma~\ref{lemma:cal2}, we know
-\begin{align}
-&N(i,t)^{5/6}(l-1) \nonumber \\
-=& 0.9N(i,t)^{5/6} + N(i,t)^{5/6}(l-1.9) \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)} + \sqrt{(l-1.9)^2 N(i,t)} \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+(l-1.9)^2 N(i,t)}. \nonumber
-\end{align}
-
-Based on Lemma~\ref{ACI-inequality}, we know
-\begin{align}
-&\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})) \nonumber \\
-\leq & \sum_{i,j}24e^{-1.8(l-1.9)^2} = 24Nme^{-1.8(l-1.9)^2}. \nonumber
-\end{align}
-
-Thus,
-\begin{align}
-&\sum_{t=1}^{\infty}c(t) \nonumber \\
-\leq&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+2Wm\frac{2\sigma l}{n^{1/6}}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-\leq& \sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(\omega\in L[1]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-+&\sum_{l=2}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-\leq& \sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(t\in [t_n,t_{n+1})) \nonumber \\
-+&\sum_{l=2}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]24Nme^{-1.8(l-1.9)^2}P(t\in [t_n,t_{n+1})) \nonumber \\
-\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]Nn +\sum_{l=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]24Nme^{-1.8(l-1.9)^2}Nn \nonumber \\
-\leq & \left[R+4Wm\sigma \right]N (\max\{n_2,\lceil (a_0)^6 \rceil\})^2+\sum_{l=2}^{\infty}24N^2 m[R+4Wml\sigma](\max\{n_2,\lceil (a_0 l)^6 \rceil\})^2 e^{-1.8(l-1.9)^2} \nonumber \\
-=& O(N^2). \nonumber
-\end{align}
-
-\end{proof}
-
-\begin{lemma}
-The expected number of payments for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$.
-\label{lemma:numP}
-\end{lemma}
-
-\begin{proof}
-If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2mW\lambda\}$, they will correctly identify their best arm.
-Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms.
-In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
-Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$.
-Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).
-
-Define $\tau_{n}^{i}$ to be the first time we pull arm $i$ in the $n^{th}$ round. Then
-\begin{align}
-\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\} =\sum_{n=1}^{\infty}\sum_{i=1}^{N}\mathbbm{1}\{c(\tau_{n}^{i})>0\}. \nonumber
-\end{align}
-
-The cumulative expected number of payments is bounded above by:
-\begin{align}
-&E\left[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}\right] \nonumber \\
-=&\sum_{n=1}^{\infty}\sum_{i=1}^{N}P(c(\tau_{n}^{i})>0) \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}P\left(\exists i,j:|u_{i}^{j}-u_{i,\tau_{n}^{i}}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2Wm}\right)+\sum_{n=1}^{n_1}N \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right) +\sum_{n=1}^{n_1}N \nonumber \\
-\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right)\times N+\sum_{n=1}^{n_1}N \nonumber  \\
-\leq&24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1, \nonumber
-\end{align}
-
-Thus, we know the expected number of payments is bounded above by $O(N^2)$.
-
-\end{proof}
-
-Now we are ready to prove our second main result, Theorem~\ref{rst:regret}.
-
-\begin{proof}
-For regret incurred in the first $n_0$ round, it is bounded above by $\sum_{n=1}^{n_{0}}NRn$.
-
-For regret incurred after the first $n_0$ round, it has two different components: the regret incurred when we let the agents play myopically and the regret incurred when we incentivize the agents.
-Using Lemma~\ref{lemma:numP}, the expected regret incurred when we incentivize the agents is bounded above by: $\left[24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1\right]R$.
-
-For the regret incurred when we let the agents play myopically at time $t\geq t_{n_0}$, it consists of the following two components:
-\begin{itemize}
-\item For those users whose utility difference between their best and the second best arm is greater than $f(t)$: we define a sequence of stopping time $\tau_{n}^{k}$ to be the $k^{th}$ time period in the $n^{th}$ round.
-For $\tau_{n}^{k}=t$, the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)\times R$.
-We denote the regret incurred by these agents as $r_1(\tau_{n}^{k})$.
-\item For those user whose utility difference between their best and the second best arm is smaller than $f(t)$: this happens with probability $S(f(t))$ at each time and regret is bounded above by $S(f(t)) \times f(t)=Mf(t)^2$.
-We denote the regret incurred by these agents as $r_2(t)$.
-\end{itemize}
-
-Thus, the cumulative expected regret incurred up to time $T$ when we let the agent play myopically is bounded above by:
-\begin{align}
-&E\left[\sum_{t=1}^{T}r(t)\right] \nonumber \\
-=&E\left[\sum_{t=1}^{t_{n_{0}}} r(t) + \sum_{t=t_{n_{0}}}^{T}(r_1(t)+r_2(t))\right]  \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}-1}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-&\bccomment{\text{is the following proof correct? I think it might be wrong}} \nonumber \\
-= & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{t_{n+1}-t_{n}}r_1(\tau_{n}^{k})\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{k=1}^{t_{n+1}-t_n}24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{k=1}^{t_{n+1}-t_n}24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \label{equ:regret}
-\end{align}
-
- Thus the cumulative regret at time $T$ is bounded above by
-\begin{align}
-&\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-+ & 24N^2 m \frac{1}{e^{\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2}}-1}R+N\left(\max\left\{n_{0},\frac{2}{p}\right\}\right)R. \nonumber
-\end{align}
-
-For a fixed $T$, we only need to minimize the following two terms since all others are constant:
-
-\begin{align}
-\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2.
-\end{align}
-
-If we set $f^2(t)=\frac{2\log(T)\times 64W^2 m^2\sigma^2}{1.8t}$, then
-\begin{align}
-&\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\ 
-\leq & \sum_{n=1}^{T} 24N^2 mnR \exp\left(-2\log(T)\right)  + \frac{128W^2 m^2\sigma^2 M\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{n} \nonumber \\
-\leq &  24N^2 m R\frac{T(T-1)}{2T^2}  + 71.12 W^2 m^2\sigma^2 M\log(T)(\log(T)+1) \nonumber \\
-\leq &  12 N^2 m R  + 71.12 W^2 m^2\sigma^2 M\log(T)(\log(T)+1). \nonumber
-\end{align}
-
-Thus, the cumulative expected regret is bounded by $O(N^2 m + M m^2\log(T))$.
-\end{proof}
-
-\begin{corollary}
-If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O(N^2)$.
-\end{corollary}
-
-\begin{proof}
-The proof of this corollary is similar to the proof of Theorem~\ref{rst:regret}.
-If we set $f^2(t)=\frac{2\log(T)\times 64W^2 m^2\sigma^2}{1.8t}$, then there exists a $t_{0}$ such that for $t>t_{0}$, $S(f(t))=0$.
-Thus, similar to equation~\eqref{equ:regret}, we know the cumulative expected regret when we let the agents play myopically is bounded above by
-\begin{align}
-\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{t_{0}}Mf(t)^2 \nonumber
-\end{align}
-Therefore, based on the same analysis of Theorem~\ref{rst:regret}, we know the cumulative regret is bounded by $O(N^2)$.
-\end{proof}
-
-\subsection{Practical Issues}
-\label{sec:pi}
-
-In Algorithm~\ref{Alg1}, we use ``pay whatever it takes'' strategy when we decide to incentivize the agent.
-However, ''pay whatever it takes'' only shows up in the proof of Lemma~\ref{round:length}.
-Without loss of generality, suppose we want to incentivize arm $i$ at time $t$ at the $n^{th}$ round.
-Based on the proof of Lemma~\ref{round:length}, as long as we offer a payment $c_{i,t}$ such that arm $i$ has at least $n^{-1}$ probability being pulled at time $t$, our results still hold true.
-We could compute this $c_{i,t}$ dynamically based on $F(\cdot)$ as well as our current estimate $u_{i,t}$.
-Here is the revised algorithm which would work well in practice:
-
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration}
-\label{Alg2}
-\begin{algorithmic}
-\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
-\FOR{ $t = 1, 2, 3, \cdots$}{
-	\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
-  \IF {$S\setminus V$ is non-empty}
-    \STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
-	\STATE{Offer payment $c_{i,t}=\inf\{c: P(\theta\sim F: \theta\cdot u_{i,t}+c>max_{j}\theta\cdot u_{j,t})>n^{-1}\}$}
-  \ELSE
-  \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
-  \ENDIF
-  \STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
-  \IF {$n\neq \min_{i}N(i,t)$} 
-  	\STATE $V=\emptyset$
-  \ENDIF
-  \STATE Update the round number, $n = \min_{i} N(i,t)$
-}\ENDFOR
-
-\end{algorithmic}
-\end{algorithm}
-
-The same proof would work and we can get the exact same results as Algorithm~\ref{Alg1}.
-
-\section{Lower Bound $\Omega(\log(T))$}
-\label{sec:lb}
-
-In this section, we assume $\theta$ follows a continuous distribution $F(\cdot)$.
-We provide an example to show the best possible lower bound is $\Omega(\log(T))$ regardless of the incentivizing strategy.
-
-Suppose we have two arms.
-Arm $1$ has attribute vector $(0,0)$ and arm $2$ has attribute vector $(0,1)$.
-We assume the users' preference are uniformly distributed on the unit circle.
-If the user knows the exact attribute vectors for both arms, then the users with preference on the bottom half circle will choose arm $1$ and the users with preference on the top half circle will choose arm $2$.
-
-Consider the following algorithm: at each step, let the agents play myopically; however, they are going to see the noisy rewards for both arms.
-
-To lower bound the regret, we assume that the agents already know the true attribute vector for arm $1$.
-Without loss of generality, denote $u_{2,t} = (0,1)+(z_{t,1},z_{t,2}) = (0,1)+ (N(0,1/t),N(0,1/t))$ to be the estimate attribute vector for arm $2$ (Without loss of generality, we assume the variance for the noise is $1$).
-
-Since $(z_{t,1}, z_{t,2})$ is symmetric around $(0,0)$, we know
-
-\begin{align}
-&E[r(t)] \nonumber \\
-= &E[r(t) | z_{t,1}>0,z_{t,2}>0] \times P(z_{t,1}>0,z_{t,2}>0) + E[r(t) |z_{t,1}>0,z_{t,2}<0] \times P(z_{t,1}>0,z_{t,2}<0) \nonumber \\
-&+E[r(t) | z_{t,1}<0,z_{t,2}>0] \times P(z_{t,1}<0,z_{n,2}>0) + E[r(t) |z_{t,1}<0,z_{t,2}<0] \times P(z_{t,1}<0,z_{t,2}<0) \nonumber \\
-\geq & 0.25 \times E[r(t) | z_{t,1}>0, z_{t,2}>0]. \nonumber
-\end{align}
-
-Given $z_{t,1}>0$ and $z_{t,2}>0$, we know users whose preference vector between $(-1,0)$ and $\left(\frac{-1-z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ as well as users whose preference vector between $(1,0)$ and $\left(\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{-z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ will make a mistake.
-The regret is the absolute value of the second coordinate of the user's preference vector.
-Thus, we know
-
-\begin{align}
-&E[r(t)| z_{t,1}>0, z_{t,2}>0] \nonumber \\
-=& 4\times 2 \int_{0}^{\infty} \int_{0}^{\infty} \int_{0}^{\arctan\left(\frac{z_{t,1}}{1+z_{t,2}}\right)}\frac{\sin(\theta)}{2\pi}d(\theta)\frac{e^{-\frac{t \times z_{t,1}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,1})\frac{e^{-\frac{t \times z_{t,2}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,2}) \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}t\times \left[1-\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right]e^{-\frac{t \times z_{t,1}^2}{2}}e^{-\frac{t \times z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty} \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber
-\end{align}
-
-Below, we want to show 
-\begin{align}
-\lim_{t\rightarrow\infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} = O(1), \nonumber
-\end{align}
-and use the fact that $\sum_{n=1}^{T}\frac{1}{n}=O(\log(T))$ to show the regret is at least $\Omega(\log(T))$.
-
-Denote $d(t)=t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]$.
-Since
-\begin{align}
-d^{'}(t)=\frac{-z_{t,1}^2(2z_{t,2}+3\sqrt{t})-2(z_{t,2}+\sqrt{t})^3}{2(z_{t,1}^2+(z_{t,2}+\sqrt{t})^2)^{3/2}}+1. \nonumber
-\end{align}
-
-and $\lim_{t\rightarrow \infty}d^{'}(t)=2$, we know for $t$ large enough, $d(t)$ is a increasing function in terms of t. Thus, based on the Monotone Convergence Theorem, we have
-
-\begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber
-\end{align}
-
-Based on our calculation, we know
-
-\begin{align}
-\lim_{t\rightarrow \infty} d(t)=\frac{z_{t,1}^2}{2}. \nonumber
-\end{align}
-Thus,
-\begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} \nonumber \\
-=&\frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ \frac{z_{t,1}^2}{2}e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) = \frac{1}{2\pi}.
-\nonumber
-\end{align}
-
-Thus, the cumulative expected regret is at least $\Omega(\log(T))$.
-
-\section{Conclusion}
-In this paper, we study the incentivizing exploration problem with heterogeneous user preferences, which generalize the problem setting studied by \cite{frazier2014incentivizing} and \cite{han2015incentivizing}.
-We propose a simple policy that mostly exploits and occasionally incentivizing exploration, which can achieve $O(N^2+M(\log(T))^2)$ cumulative expected regret with $O(N^2)$ payment budget.
-
-\bibliography{reference}{}
-\bibliographystyle{plain}
-
-\end{document}

### 2018-01-26 lower_bound.tex
divide the paper into sections

--- 2017-12-04 paper.tex
@@
-\documentclass{article}
-\usepackage[utf8]{inputenc}
-
-\usepackage[english]{babel}
-
-\usepackage{blindtext}
-\usepackage{amssymb}
-
-\usepackage[]{algorithm}
-\usepackage[]{algorithmic}
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{xr} 
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{amsthm}
-\usepackage{comment}
-\usepackage{graphicx}
-\usepackage{subcaption}
-\usepackage{xcolor}
-\usepackage{amsmath}
-\usepackage{dblfloatfix}
-\usepackage{bbm}
-
-\newcommand{\IE}{IE} 
-\newcommand{\argmax}{\mathop{\mathrm{argmax}}}
-
-\newcommand\floor[1]{\lfloor#1\rfloor}
-\newcommand\ceil[1]{\lceil#1\rceil}
-
-\newcommand{\bccomment}[1]{{\color{blue}BC: #1}}
-\newcommand{\pfcomment}[1]{{\color{blue}PF: #1}}
-
-\newtheorem{definition}{Definition}[section]
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-\newtheorem{assumption}{Assumption}
-
-\title{Incentivizing Exploration with Heterogeneous Utilities}
-
-\begin{document}
-
-\maketitle
-
-\section{Introduction}
-In this paper, we study incentivizing exploration with heterogeneous agent preferences.
-In this problem,   
-arms have unknown multivariate attributes, and agents have heterogeneous linear utility functions that map these attribute vectors onto utilities.
-Agents see noisy observations of attributes of arms pulled by all previous agents, and estimate an arms' attribute vector by the simple average of these observations.
-Agents are selfish, and pull the arm with the largest estimated utility summed with an optional arm-specific incentivizing payment chosen by the principle.
-We study strategies for choosing such incentive payments that seek to maximize the total utility derived by agents, subject to a limitation on the total incentive payment.
-To accomplish this goal, a strategy must induce sufficient exploration to reveal arms' attributes, while still letting agents select myopically and according to their preferences sufficiently often that high-utility arms are chosen and incentive payments are kept small.
-
-Our problem setting models online review aggregators like Amazon, Yelp, and Tripadvisor that host crowdsourced reviews.
-Users of these websites wish to use the reviews hosted there to choose the product / restaurant / vacation (generically referred to as an ``item'') that is best according to their preferences.
-These reviews provide not just cardinal feedback, but also a description of items' attributes that a user may consider together with their personal preferences to select their preferred item.
-An item with few reviews might have inaccurate attribute estimates, leading users to avoid it even though it may actually be their best choice.
-Without incentives, this situation may persist and decrease welfare for the platform's user base.
-By offering incentives, either through price reductions by Amazon or coupons from Yelp or Tripadvisor, a platform may induce more reviews of unexplored items and provide more value over the long term.
-
-Our problem setting also applies to crowd science platforms like eBird \cite{frazier2014incentivizing, sullivan2009ebird}.
-EBird guides birding enthusiasts through a website to explore and report their findings to the birding community.
-Each user report contains information about when, where and how they go birding and what birds they see and hear.
-EBird may wish to incentivize enthusiasts to explore less-explored birding locations and provide more accurate reports on these locations.
-Each enthusiast may have different preference over a location's attributes such as the diversity of bird species, weather, distance and safety.
-By offering enthusiasts incentivies to explore, eBird can create a more accurate body of reports and provide better value to the birding community.
-
-% Something interesting to study would be to alter the search rankings to influence people
-% Also which items to spam people about reviewing
-
-In this problem context, we study a simple policy that usually exploits, incentivizing agents to pull an arm only when the set of agent utility functions that would pull this arm without incentives has probability below a time-varying threshold.
-In our paper, we assume all arms are some agents' best arm.
-Under this assumption, we prove that with $O(N^2)$ payment budget, this policy has $O(N^2+M(\log(T))^2)$ cumulative expected regret where $M$ is an upper bound on the limiting marginal probability density of agent utilities that are nearly indifferent between their best and the second best arm.
-If all agents' utility difference between their best and second best arm is bounded below by a positive number, which typically happens when the agent utility distribution is discrete, this policy achieve constant cumulative expected regret $O(N^2)$.
-The key difference between our problem setting and both the homogenous preference setting and the traditional multi-armed bandits setting is that we must incentivize agents to try suboptimal arms much less often, since all arms are some agents' best arm.
-Essentially, heterogeneity provides free exploration.
-These results suggest that heterogeneous agent preferences reduce but do not eliminate the need to incentive exploration, in relation to single-preference settings.
-
-We broadly categorize the relevant previous literature into two categories based on whether there is money transfer.
-With money transfer, \cite{frazier2014incentivizing} considers a problem setting where the principal pays agents money to explore.
-This work assumes all agents have equal value for money and provide a complete characterization of achievable reward with a fixed budget.
-\cite{han2015incentivizing} generalizes this framework to include agents with heterogeneous value for money, and to allow an external signal to provide partial information about this valuation.
-Under this setting, this work proves a bound on achievable reward as a function of the budget and the signal scheme.
-
-Without money transfer but using information asymmetry, \cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time.
-\cite{mansour2015bayesian} generalizes \cite{kremer2014implementing} by allowing a finite number of actions at each time.
-\cite{mansour2016bayesian} considers a problem setting where there are multiple agents at each time and agents may interact with each other.
-In these papers, the principal provides each agent a recommendation at each time that is Bayesian incentive-compatible.
-They prove the principal can achieve constant regret when utilities are deterministic and logarithmic regret when utilities are stochastic.
-
-We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+M(\log(T))^2)$ regret with $O(N^2)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
-
-\section{Problem Setting}
-\label{sec:prob}
-
-We have $N$ arms. Arm $i$ has a fixed but unknown attribute vector $u_i\in \mathbb{R}^{m}$. 
-A stream of myopic selfish agents come to our system.
-Agent $t$ has linear preferences over attributes described by a vector $\theta_t \in \mathbb{R}^m$ that is unknown to the principal and drawn i.i.d.
-from a known distribution $F(\cdot)$ with compact support.
-We refer synonomously to an agent and that agent's preference vector: when we say ``an agent $\theta$'', we mean ``an agent with preference vector $\theta$.''
-
-Each agent $t$ chooses an arm to pull $A_t$, according to a process described below, and obtains utility $\theta_t \cdot u_{A_{t}}$.
-The principal and all agents then see a noisy observation of the attribute vector of the pulled arm of the form $O_t=u_{A_{t}}+\epsilon_{t}$, where $\epsilon_t\sim N(0, \sigma^2 I_{m})$ is independent normally distributed noise, and $I_m$ denotes an $m$-dimensional identity matrix.
-Although we assume a common variance across attributes for simplicity of presentation, our theoretical results hold if the variance differs.
-
-At each time $t$, for each arm $i$, we (the principal) offer a non-negative payment $c_{i,t}\geq 0$ based on previous observations.
-We assume that agent $t$ chooses to pull the arm that myopically maximizes the sum of this payment and an estimate of the utility obtained $\theta_t \cdot u_{i,t}$ where $u_{i,t}$ denotes the simple average of $O_s$ over all previous pulls of arm $i$.
-In this paper, we assume all arms have been pulled once at time $t=0$ and $u_{i,0}$ denotes a random draw from the arm attribute vector.
-For $t>0$, denote $u_{i,t} = \frac{\sum_{s<t} O_s 1\{A_s = i\} + u_{i,0}}{\sum_{s<t} 1\{A_s = i\}+1}$ and $A_t=\argmax_{i}\{\theta_t\cdot u_{i,t}+c_{i,t}\}$, breaking ties in favor of the arm with the highest incentive.
-We use $c_t=c_{A_{t},t}$ to denote the actual incentive payment at time $t$.
-
-This behavior may be recovered if agents are Bayesian and share a common non-informative prior distribution that is constant over $\mathbb{R}^m$ and know $\sigma^2$.
-In this case, the posterior distribution on $u_{i}$ at time $t$ is multivariate normal with mean $u_{i,t}$, and the expected value of $\theta_t \cdot u_i$ under this posterior conditioned on $\theta_t$ is $\theta_t \cdot u_{i,t}$ (see equation $2.13$ in section $2.5$, \cite{Ge04}).
-Alternatively, one may simply take our assumption that agents use the average as their estimate of an attribute value directly without such a Bayesian justification.
-
-We define the regret at time $t$ as $r(t)=\max_{i}\{\theta_{t}\cdot u_{i}\}-\theta_t\cdot u_{A_t}$, and the cumulative regret up to time T as $R(T)=\sum_{t=1}^{T}r(t)$.
-Define the cumulative payment up to time T similarly as $C(t)=\sum_{t=1}^{T}c(t)$.
-As the principal, we want to find a strategy $\mathcal{A}$ under which both the cumulative expected regret $\mathbb{E}_{\mathcal{A}}[R(T)]$ and the cumulative expected payment $\mathbb{E}_{\mathcal{A}}[C(T)]$ are small.
-
-To support later development, we define some additional notation.
-We let $B(\theta)$ and $\hat{B}(\theta)$ refer to the index of the arm that is best and second best for an agent with preference vector $\theta$, $B(\theta) \in \argmax_i \theta \cdot u_i$ and $\hat{B}(\theta)=\argmax_{i\neq B(\theta)}\theta\cdot u_{i}$, breaking ties uniformly at random.
-We let $N(i,t)$ denote the number of pulls of arm $i$ at times up to and including $t$ plus $1$ (because of the initial pull), i.e.
-$N(i,t)=\sum_{s<t} 1\{A_s = i\}+1$.
-We call time $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$ the {\it starting point of the $n^{th}$ round}. We call the set of times $[t_{n}, t_{n+1})$ the {\it $n^{th}$ round}.
-
-\section{Algorithm and Upper Bound}
-\label{sec:ub}
-
-In this section, we propose a simple policy that mostly exploits, and occasionally incentivizes exploration when the probability of an arm would be pulled by all agent types below a time-varying threshold given the current posterior.
-We prove that with the help of heterogeneous preferences, we can get a certain amount of exploration for free via heterogeneity.
-
-\subsection{Our Algorithm}
-Our algorithm incentivizes pulling an arm $i$ at a time $t$ in round $n$ if and only if both of the following criteria are met:
-\begin{itemize}
-\item the probability of pulling arm $i$ would be below $n^{-1}$ without incentives; 
-\item arm $i$ has not been played previously in the current round.
-\end{itemize}
-Ties are broken randomly.  This algorithm does not need to know the horizon $T$ in advance.
-
-If our algorithm decides to incentivize an arm $i$, it uses the ``pay whatever it takes'' strategy in which the payment offered is $\max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$.
-This maximum over $\theta$ is taken over the support of $F$, which we recall is assumed compact.
-(We use this ``pay whatever it takes'' strategy for its simplicity, and in Section~\ref{sec:pi} we provide an alternate and smaller incentive payment that achieves the same payment budget bound and regret bound).
-
-We describe our algorithm in detail as follows:
-
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration}
-\label{Alg1}
-\begin{algorithmic}
-\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
-\FOR{ $t = 1, 2, 3, \cdots$}{
-	\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
-  \IF {$S\setminus V$ is non-empty}
-    \STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
-    \STATE{Pay whatever it takes to incentivize pulling arm $i$, i.e., offer payment 
-    $c_{i,t} = \max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$ and $c_{j,t} = 0$ for $j \ne i$.}
-  \ELSE
-  \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
-  \ENDIF
-  \STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
-  \IF {$n\neq \min_{i}N(i,t)$} 
-  	\STATE $V=\emptyset$
-  \ENDIF
-  \STATE Update the round number, $n = \min_{i} N(i,t)$
-}\ENDFOR
-
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{Assumptions}
-In this section, we state several assumptions assumed by our analysis.  First define
-\begin{align}
-\Omega_{i,j}=\{\theta:B(\theta)=i, \hat{B}(\theta)=j\}, \nonumber 
-\end{align}
-which is the set of agent preferences whose best arm is arm $i$ and second best arm is arm $j$. With this definition, our analysis makes the following assumptions:
-
-\begin{assumption} Let $F_{i,j}(y)$ be the marginal cumulative density function (or cumulative mass function if $F(\cdot)$ is a discrete distribution) of $(u_i-u_j)\cdot\theta$ conditioned on $\theta \in \Omega_{i,j}$.
-We assume $F_{i,j}(y)\leq My$ for all $y\in R^{+}$, $\forall i,j$.
-\label{A1}
-\end{assumption}
-
-As we can see later in our proof, we only need $\max_{i,j}\limsup_{y\rightarrow 0^{+}}\frac{F_{i,j}(y)}{y}$ to be finite.
-Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm.
-
-\begin{assumption} We assume $F$ has a compact support set. Without loss of generality, we assume $\theta\in [0,W]^m$.
-\label{A2}
-\end{assumption}
-
-We use $R = \max_{\theta, i,j} \theta \cdot (u_i - u_j)$ to denote the maximum regret that can be incurred at each time.  Assumption~\ref{A2} shows that $R<\infty$.
-
-\begin{assumption}
-Denote $p=\min_{i}P(\{\theta: B(\theta)=i\})$. We assume $p>0$.
-\label{A3}
-\end{assumption}
-
-Assumption~\ref{A3} means each arm $i$ has a strictly positive proportion of users for which that arm is best.
-
-\subsection{General Results}
-
-In this section, we prove Algorithm~\ref{Alg1} achieves $O(N^2+M(\log(T))^2)$ cumulative regret with $O(N^2)$ payment budget.
-This is stated in the following pair of theorems, which together constitute our main results.
-
-\begin{theorem}
-The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$. 
-\label{rst:budget}
-\end{theorem}
-
-\begin{theorem}
-The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2 m + M m^2(\log(T))^2)$.
-\label{rst:regret}
-\end{theorem}
-
-Before we prove these two theorems, we must first introduce two additional pieces of notation, which will be used in preliminary lemmas.
-Let $S(\delta)$ be the proportion of users whose utility difference between their best and second best arm is less than $\delta$.
-Formally, $S(\delta)=P(\theta: \theta \cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}\leq \delta)$.
-Then, let $p(\delta)=\min_{i}P(\{\theta:B(\theta)=i,\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$.
-We know $p(0)=p$.
-
-With this additional notation, we now prove several lemmas.
-First, based on Assumption~\ref{A1}, we have the following bound for $S(\delta)$.
-
-\begin{lemma}
-$S(\delta)\leq M\delta$.
-\label{lemma:sdelta}
-\end{lemma}
-
-\begin{proof}
-\begin{align*}
-S(\delta)
-&=\sum_{i,j}P(\theta\cdot(u_{i}-u_{j})\le \delta|\theta\in \Omega_{i,j})P(\theta\in \Omega_{i,j}) \\
-&\leq \sum_{i,j}M\delta \times P(\theta\in \Omega_{i,j}) \\
-&=M\delta.
-\end{align*}
-\end{proof}
-
-The following lemma bounds the probability of making a mistake if we let the agents play myopically in the $n^{th}$ round, given that the utility difference between his/her best and second best arm is bounded below by a constant.
-
-\begin{lemma}
-Define $\tau$ to be any stopping time that is almost surely between $t_n$ and $t_{n+1}-1$ with respect to the filtration $\mathcal{F}_{t}=\sigma(A_1,\cdots,A_t,c_1,\cdots,c_t,O_1,\cdots,O_t)$, we have
-\begin{align}
-P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{16\sigma^2}\right), \nonumber
-\end{align}
-for $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$.
-\label{round:prob}
-\end{lemma}
-
-We need the following lemma in order to prove Lemma~\ref{round:prob}.
-
-\begin{lemma}
-For $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$, we have
-\begin{align}
-\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-\label{n0-inequality}
-\end{lemma}
-
-\begin{proof}
-First, we observe that
-\begin{align}
-&\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)} \nonumber \\
-\iff &\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{9.6\sigma^2}{\lambda^2}. \nonumber 
-\end{align}
-Since $\log(x)\leq x-1$ for $x>0$, we know 
-\begin{align}
-\log(\log_{1.1}(n)+1)=\log\left(\frac{\log(n)}{\log(1.1)}+1\right)\leq \log(11\log(n)+1)\leq \log(11n)\leq 3+\log(n). \nonumber
-\end{align}
-
-Thus, we know
-\begin{align}
-\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{n}{3+\log(n)}. \nonumber 
-\end{align}
-
-To prove the lemma, we just need to show for $n\geq n_{0}$, we have
-\begin{align}
-\frac{n}{3+\log(n)}\geq \frac{9.6\sigma^2}{\lambda^2}. \label{n0-equ}
-\end{align}
-Inequality~(\ref{n0-equ}) is true because of the following two observations:
-\begin{itemize}
-\item for $n\geq 50$, we have $\frac{n}{3+\log(n)}\geq n^{0.5}$;
-\item for $n\geq \frac{92.16\sigma^4}{\lambda^4}$, we have $n^{0.5}\geq {9.6\sigma^{2}}{\lambda^{2}}$.
-\end{itemize}
-
-Thus, we know our lemma is true.
-
-\end{proof}
-
-To prove Lemma~\ref{round:prob}, we also need to use an adaptive concentration inequality due to \cite{zhao2016adaptive}. For reference, we state it here as a Lemma.
-
-\begin{lemma}[Corollary 1 in \cite{zhao2016adaptive}]
-Let $X_{i}$ be zero mean $1/2$-subgaussian random variables.
-$\{S_{n}=\sum_{i=1}^{n}X_{i},n\geq 1\}$ be a random walk.
-Let $J$ be any stopping time with respect to $\{X_1,X_2,\cdots\}$.
-We allow $J$ to take the value of $\infty$ where $P(J=\infty)=1-\lim_{n\rightarrow \infty}P(J\leq n)$.
-If
-\begin{align}
-f(n)=\sqrt{0.6n\log(\log_{1.1}(n)+1)+bn}, \nonumber
-\end{align}
-then
-\begin{align}
-Pr[\{S_{J}\geq f(J)\}\cap \{J<\infty\}]\leq 12e^{-1.8b}. \nonumber
-\end{align}
-\label{ACI-inequality}
-\end{lemma}
-
-We now prove Lemma~\ref{round:prob}.
-
-\begin{proof}[Proof of Lemma~\ref{round:prob}]
-In the $n^{th}$ round, we know all arms have been pulled at least $n$ times.
-For all the agents $\theta$ whose utility difference between their best and second best arm is greater than $2mW\lambda$, denote $K(\theta)=\max_{i\neq B(\theta)}\{\theta\cdot u_{i,t}\}$.
-If $|u_{i,t}^{j}-u_{i}^{j}|\leq \lambda$ for all $i,j$, then
-\begin{align}
-&\theta\cdot(u_{B(\theta),t}-u_{K(\theta),t}) \nonumber \\
-\geq & \theta\cdot(u_{B(\theta),t}-u_{B(\theta)}) + \theta\cdot(u_{K(\theta)}-u_{K(\theta),t}) + \theta\cdot(u_{B(\theta)}-u_{K(\theta)}) \nonumber \\
-> & -Wm\lambda - Wm\lambda + 2Wm\lambda = 0,\nonumber
-\end{align}
-which means their myopic action would incur no regret.
-
-Define $\epsilon_{i,\tau}=u_{i,\tau}-u_i$ and $\epsilon_{i,\tau}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,\tau}$. Thus, we have
-\begin{align}
-&P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\nonumber \\
-\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda |\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda). \label{ACI}
-\end{align}
-
-To bound equation~(\ref{ACI}), we use Lemma~\ref{ACI-inequality}. Define
-\begin{align}
-S_{N(i,\tau)}^{i,j}=\frac{\epsilon_{i,\tau}^{j}}{2\sigma}. \nonumber
-\end{align}
-
-Based on Lemma~\ref{n0-inequality}, for $n_{0}=\max\{50, \frac{92.16\sigma^2}{\lambda^2}\}$ and $n\geq n_{0}$, we have
-\begin{align}
-\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-
-Thus, if we set $b=\frac{n\lambda^2}{16\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,\tau)\geq n\geq n_{0}$, we have
-\begin{align}
-\frac{N(i,\tau)\lambda}{2\sigma}\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)}+\frac{\lambda}{4\sigma}\sqrt{n N(i,\tau)} \nonumber \\
-\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)+bN(i,\tau)}, \nonumber 
-\end{align}
-where the last inequality is because $\sqrt{x}+\sqrt{y}\geq \sqrt{x+y}$. Thus, we have
-\begin{align}
-&P(\epsilon_{i,\tau}^{j}\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P\left(S_{N(i,\tau)}^{i,j}\geq \frac{N(i,\tau)\lambda}{2\sigma}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
-\leq & P\left(S_{N(i,\tau)}^{i,j}\geq \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
-\leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
-\end{align}
-Similarily, we can bound 
-\begin{align}
-&P(\epsilon_{i,\tau}^{j}\leq-\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P(-\epsilon_{i,\tau}^{j}\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber 
-\end{align}
-
-Therefore, we know $P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right)$.
-Thus, we know
-\begin{align}
-&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)  \nonumber \\
-\leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
-\end{align}
-
-\end{proof}
-
-Before we start analyzing the cumulative regret, we first prove the following lemma which bounds the expected length of each round.
-
-\begin{lemma}
-Using our algorithm, we have $\mathbb{E}[t_{n+1}-t_{n}]\leq Nn$, $\forall n\geq 1$.
-\label{round:length}
-\end{lemma}
-
-\begin{proof}
-	A round completes when each arm is pulled at least once in that round.
-Let $X_{i}$ be the number of agents who come to the system between the time after the $(i-1)^{th}$ unique arm was pulled, up to and including the time when the $i^{th}$ unique arm was pulled.
-Then we know
-\begin{equation*}
-\mathbb{E}[t_{n+1}-t_{n}]=\sum_{i=1}^{N}E[X_{i}].
-\end{equation*}
-
-Fix $i$.
-In bounding $X_i$, we think of agents as ``trials'', where each trial can result in a new unique arm being pulled (which we call a ``successful'' trial), or not.
-There are two ways a trial can be successful:
-\begin{itemize}
-\item If there is at least one arm that has not been pulled and the probability of an agent utility function that would pull this arm without incentives is less than $n^{-1}$, then the principal will offer an incentive that causes this arm to be pulled (or one of these arms if there is more than one).
-In this case, the probability that the trial is succesful is $1$.
-\item The probability of an agent utility function that would pull each un-pulled arm without incentives is at least $n^{-1}$.
-In this case, the probability that the trial is successful is at least $n^{-1}$.
-\end{itemize}
-
-Thus, $X_{i}$ is stochastically dominated below by a geometric random variable with success probability $n^{-1}$, the expected number of trials up to and including the first success, $E[X_i]$, is bounded above by $n$.
-Thus,
-\begin{align}
-E[t_{n+1}-t_{n}]\leq Nn. \nonumber
-\end{align}
-\end{proof}
-
-We also need the following lemma in part of the proof of Theorem~\ref{rst:budget}.
-\begin{lemma}
-For all $n\geq 1$, we have
-\begin{align}
-0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-\label{lemma:cal2}
-\end{lemma}
-\begin{proof}
-\begin{align}
-&0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)} \nonumber \\
-\iff & 0.81 n^{5/3} \geq 0.6n \log(\log_{1.1}(n)+1) \nonumber \\
-\iff &  \frac{81}{60} n^{2/3} \geq  \log(\log_{1.1}(n)+1) \nonumber
-\end{align}
-
-Denote $f(x) = \frac{81}{60}x^{2/3} - \log(\log_{1.1}(x)+1)$.
-It's easy to compute $f^{'}(x)=0$ has a unique solution $x_{0}=e^{2/3w(\frac{20e^{20000/314763}}{27})-\frac{10000}{104921}}$ (here $w(\cdot)$ is the Lambert W-Function) and it is the global minimum.
-Since $f(x_{0})\approx 0.0252 >0$, we know $f(x)>0$ for all $x\geq 1$.
-Thus, our lemma holds true.
-\end{proof}
-
-Now we are ready to prove our first main result, Theorem~\ref{rst:budget}.
-
-\begin{proof}
-Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$.
-Denote $\epsilon_{i,t}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,t}$.
-Denote $\omega$ to be a sample path and $n(t,\omega)$ to be the round number for sample path $\omega$ at time $t$.
-For a fixed time $t$, define
-\begin{align}
-L^{'}[l](t) = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n(t,\omega),l), \forall i,j\}\nonumber
-\end{align}
-where $g(n,l)$ is a function which we will define later.
-Define $L[1](t) = L^{'}[1](t)$ and $L[i](t) = L^{'}[i](t)\setminus L^{'}[i-1](t)$ for $i\geq 2$.
-We call $L[l](t)$ the $l^{th}$ envelope at time $t$.
-We often simplify the notation and use $L[l]$ instead of $L[l](t)$ without confusion.
-
-In the calculation below, we omit the dependency on $\omega$ when refering to variables $c(t)$, $\epsilon_{i,t}^{j}$ and $t_n$.
-Based on the definition of $L[l]$, we know if $\omega\in L[l]$, the maximum payment we need to offer at time $t$ is bounded above by
-\begin{align}
-&\max_{i}\theta_t\cdot u_{i,t} - \min_{j}\theta_t\cdot u_{j,t} \nonumber \\
-= &\max_{i}\theta_t\cdot (\epsilon_{i,t}+u_i) - \min_{j}\theta_t\cdot (\epsilon_{j,t}+u_j) \nonumber \\
-\leq &\max_{i}\theta_t\cdot u_i - \min_{j}\theta_t\cdot u_j +\max_{i}\theta_t\cdot \epsilon_{i,t} - \min_{j}\theta_t\cdot \epsilon_{j,t}\nonumber \\
-\leq & R + 2Wmg(n,l). \nonumber
-\end{align}
-
-Based on the above notations, we can rewrite the cumulative payment as follows:
-\begin{align}
-&\sum_{t=1}^{\infty}c(t) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\} \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
-\end{align}
-
-Set $g(n,l)$ to be $\frac{2\sigma l}{n^{1/6}}$.
-Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2Wm\lambda\}$, they will correctly identify their best arm.
-Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{2\sigma l}{n^{1/6}} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
-Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms.
-Denote $a_0=\frac{4Wm\sigma}{p^{-1}(\frac{p}{2})}$.
-In order to have $\frac{2\sigma l}{n^{1/6}}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil (a_{0} l)^6 \rceil$.
-In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
-Denote $n_2=\frac{2}{p}$.
-Thus, we know we can only incur regret for sample paths $\omega$ in the $l^{th}$ envelope in the first $\max\{n_2,\lceil (a_0 l)^6 \rceil\}$ rounds.
-
-Thus,
-\begin{align}
-\sum_{t=1}^{\infty}c(t)=\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
-\end{align}
-
-Therefore,
-
-\begin{align}
-&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}E[c(t)|\omega \in L[l],t\in [t_n,t_{n+1}))P(\omega\in L[l],t\in [t_n,t_{n+1})) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+2Wm\frac{2\sigma l}{n^{1/6}}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})). \nonumber
-\end{align}
-
-We now bound $P(\omega\in L[l]|t\in[t_{n},t_{n+1}))$ for $n\geq n_0$ and $l\geq 2$.
-\begin{align}
-&P(\omega\in L[l]|t\in[t_{n},t_{n+1})) \nonumber \\
-=&P(\omega\in L^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in L^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
-\leq & 1-P\left(|\epsilon_{i,t}^{j}|<\frac{2\sigma (l-1)}{n^{1/6}}, \forall i,j|t\in[t_n,t_{n+1})\right) \nonumber \\
-=&P\left(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})\right) \nonumber  \\
-\leq &\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})\right) \nonumber
-\end{align}
-
-Define $S_{i,t}^{j}=\frac{N(i,t)\epsilon_{i,t}^{j}}{2\sigma}$, then we know $S_{i,t}^{j}$ is a summation of $1/2$ gaussian random numbers. Therefore,
-
-\begin{align}
-&\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma(l-1)}{n^{1/6}}\bigg|t\in[t_n,t_{n+1})\right) \nonumber \\ 
-=&\sum_{i,j}P\left(|S_{i,t}^{j}|\geq \frac{N(i,t)(l-1)}{n^{1/6}}\bigg|t\in[t_n,t_{n+1})\right) \nonumber \\
-\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})). \nonumber
-\end{align}
-
-Based on Lemma~\ref{lemma:cal2}, we know
-\begin{align}
-&N(i,t)^{5/6}(l-1) \nonumber \\
-=& 0.9N(i,t)^{5/6} + N(i,t)^{5/6}(l-1.9) \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)} + \sqrt{(l-1.9)^2 N(i,t)} \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+(l-1.9)^2 N(i,t)}. \nonumber
-\end{align}
-
-Based on Lemma~\ref{ACI-inequality}, we know
-\begin{align}
-&\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})) \nonumber \\
-\leq & \sum_{i,j}24e^{-1.8(l-1.9)^2} = 24Nme^{-1.8(l-1.9)^2}. \nonumber
-\end{align}
-
-Thus,
-\begin{align}
-&\sum_{t=1}^{\infty}c(t) \nonumber \\
-\leq&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+2Wm\frac{2\sigma l}{n^{1/6}}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-\leq& \sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(\omega\in L[1]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-+&\sum_{l=2}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-\leq& \sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(t\in [t_n,t_{n+1})) \nonumber \\
-+&\sum_{l=2}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]24Nme^{-1.8(l-1.9)^2}P(t\in [t_n,t_{n+1})) \nonumber \\
-\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]Nn +\sum_{l=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]24Nme^{-1.8(l-1.9)^2}Nn \nonumber \\
-\leq & \left[R+4Wm\sigma \right]N (\max\{n_2,\lceil (a_0)^6 \rceil\})^2+\sum_{l=2}^{\infty}24N^2 m[R+4Wml\sigma](\max\{n_2,\lceil (a_0 l)^6 \rceil\})^2 e^{-1.8(l-1.9)^2} \nonumber \\
-=& O(N^2). \nonumber
-\end{align}
-
-\end{proof}
-
-\begin{lemma}
-The expected number of payments for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$.
-\label{lemma:numP}
-\end{lemma}
-
-\begin{proof}
-If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2mW\lambda\}$, they will correctly identify their best arm.
-Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms.
-In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
-Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$.
-Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).
-
-Define $\tau_{n}^{i}$ to be the first time we pull arm $i$ in the $n^{th}$ round. Then
-\begin{align}
-\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\} =\sum_{n=1}^{\infty}\sum_{i=1}^{N}\mathbbm{1}\{c(\tau_{n}^{i})>0\}. \nonumber
-\end{align}
-
-The cumulative expected number of payments is bounded above by:
-\begin{align}
-&E\left[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}\right] \nonumber \\
-=&\sum_{n=1}^{\infty}\sum_{i=1}^{N}P(c(\tau_{n}^{i})>0) \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}P\left(\exists i,j:|u_{i}^{j}-u_{i,\tau_{n}^{i}}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2Wm}\right)+\sum_{n=1}^{n_1}N \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right) +\sum_{n=1}^{n_1}N \nonumber \\
-\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right)\times N+\sum_{n=1}^{n_1}N \nonumber  \\
-\leq&24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1, \nonumber
-\end{align}
-
-Thus, we know the expected number of payments is bounded above by $O(N^2)$.
-
-\end{proof}
-
-Now we are ready to prove our second main result, Theorem~\ref{rst:regret}.
-
-\begin{proof}
-For regret incurred in the first $n_0$ round, it is bounded above by $\sum_{n=1}^{n_{0}}NRn$.
-
-For regret incurred after the first $n_0$ round, it has two different components: the regret incurred when we let the agents play myopically and the regret incurred when we incentivize the agents.
-Using Lemma~\ref{lemma:numP}, the expected regret incurred when we incentivize the agents is bounded above by: $\left[24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1\right]R$.
-
-For the regret incurred when we let the agents play myopically at time $t\geq t_{n_0}$, it consists of the following two components:
-\begin{itemize}
-\item For those users whose utility difference between their best and the second best arm is greater than $f(t)$: we define a sequence of stopping time $\tau_{n}^{k}$ to be the $k^{th}$ time period in the $n^{th}$ round.
-For $\tau_{n}^{k}=t$, the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)\times R$.
-We denote the regret incurred by these agents as $r_1(\tau_{n}^{k})$.
-\item For those user whose utility difference between their best and the second best arm is smaller than $f(t)$: this happens with probability $S(f(t))$ at each time and regret is bounded above by $S(f(t)) \times f(t)=Mf(t)^2$.
-We denote the regret incurred by these agents as $r_2(t)$.
-\end{itemize}
-
-Thus, the cumulative expected regret incurred up to time $T$ when we let the agent play myopically is bounded above by:
-\begin{align}
-&E\left[\sum_{t=1}^{T}r(t)\right] \nonumber \\
-=&E\left[\sum_{t=1}^{t_{n_{0}}} r(t) + \sum_{t=t_{n_{0}}}^{T}(r_1(t)+r_2(t))\right]  \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}-1}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-&\bccomment{\text{is the following proof correct? I think it might be wrong}} \nonumber \\
-= & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{t_{n+1}-t_{n}}r_1(\tau_{n}^{k})\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{k=1}^{t_{n+1}-t_n}24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{k=1}^{t_{n+1}-t_n}24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \label{equ:regret}
-\end{align}
-
- Thus the cumulative regret at time $T$ is bounded above by
-\begin{align}
-&\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-+ & 24N^2 m \frac{1}{e^{\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2}}-1}R+N\left(\max\left\{n_{0},\frac{2}{p}\right\}\right)R. \nonumber
-\end{align}
-
-For a fixed $T$, we only need to minimize the following two terms since all others are constant:
-
-\begin{align}
-\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2.
-\end{align}
-
-If we set $f^2(t)=\frac{2\log(T)\times 64W^2 m^2\sigma^2}{1.8t}$, then
-\begin{align}
-&\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\ 
-\leq & \sum_{n=1}^{T} 24N^2 mnR \exp\left(-2\log(T)\right)  + \frac{128W^2 m^2\sigma^2 M\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{n} \nonumber \\
-\leq &  24N^2 m R\frac{T(T-1)}{2T^2}  + 71.12 W^2 m^2\sigma^2 M\log(T)(\log(T)+1) \nonumber \\
-\leq &  12 N^2 m R  + 71.12 W^2 m^2\sigma^2 M\log(T)(\log(T)+1). \nonumber
-\end{align}
-
-Thus, the cumulative expected regret is bounded by $O(N^2 m + M m^2\log(T))$.
-\end{proof}
-
-\begin{corollary}
-If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O(N^2)$.
-\end{corollary}
-
-\begin{proof}
-The proof of this corollary is similar to the proof of Theorem~\ref{rst:regret}.
-If we set $f^2(t)=\frac{2\log(T)\times 64W^2 m^2\sigma^2}{1.8t}$, then there exists a $t_{0}$ such that for $t>t_{0}$, $S(f(t))=0$.
-Thus, similar to equation~\eqref{equ:regret}, we know the cumulative expected regret when we let the agents play myopically is bounded above by
-\begin{align}
-\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{t_{0}}Mf(t)^2 \nonumber
-\end{align}
-Therefore, based on the same analysis of Theorem~\ref{rst:regret}, we know the cumulative regret is bounded by $O(N^2)$.
-\end{proof}
-
-\subsection{Practical Issues}
-\label{sec:pi}
-
-In Algorithm~\ref{Alg1}, we use ``pay whatever it takes'' strategy when we decide to incentivize the agent.
-However, ''pay whatever it takes'' only shows up in the proof of Lemma~\ref{round:length}.
-Without loss of generality, suppose we want to incentivize arm $i$ at time $t$ at the $n^{th}$ round.
-Based on the proof of Lemma~\ref{round:length}, as long as we offer a payment $c_{i,t}$ such that arm $i$ has at least $n^{-1}$ probability being pulled at time $t$, our results still hold true.
-We could compute this $c_{i,t}$ dynamically based on $F(\cdot)$ as well as our current estimate $u_{i,t}$.
-Here is the revised algorithm which would work well in practice:
-
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration}
-\label{Alg2}
-\begin{algorithmic}
-\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
-\FOR{ $t = 1, 2, 3, \cdots$}{
-	\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
-  \IF {$S\setminus V$ is non-empty}
-    \STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
-	\STATE{Offer payment $c_{i,t}=\inf\{c: P(\theta\sim F: \theta\cdot u_{i,t}+c>max_{j}\theta\cdot u_{j,t})>n^{-1}\}$}
-  \ELSE
-  \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
-  \ENDIF
-  \STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
-  \IF {$n\neq \min_{i}N(i,t)$} 
-  	\STATE $V=\emptyset$
-  \ENDIF
-  \STATE Update the round number, $n = \min_{i} N(i,t)$
-}\ENDFOR
-
-\end{algorithmic}
-\end{algorithm}
-
-The same proof would work and we can get the exact same results as Algorithm~\ref{Alg1}.
-
 \section{Lower Bound $\Omega(\log(T))$}
@@
 
-Denote $d(t)=t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]$.
-Since
-\begin{align}
-d^{'}(t)=\frac{-z_{t,1}^2(2z_{t,2}+3\sqrt{t})-2(z_{t,2}+\sqrt{t})^3}{2(z_{t,1}^2+(z_{t,2}+\sqrt{t})^2)^{3/2}}+1. \nonumber
-\end{align}
-
-and $\lim_{t\rightarrow \infty}d^{'}(t)=2$, we know for $t$ large enough, $d(t)$ is a increasing function in terms of t. Thus, based on the Monotone Convergence Theorem, we have
+Denote $d(t)=t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]$. Based on our calculation (see appendix for details), we know
 
 \begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber
-\end{align}
-
-Based on our calculation, we know
-
-\begin{align}
-\lim_{t\rightarrow \infty} d(t)=\frac{z_{t,1}^2}{2}. \nonumber
+\lim_{t\rightarrow \infty} d(t)=\frac{z_{t,1}^2}{2}. \label{ex:limit}
 \end{align}
@@
 Thus, the cumulative expected regret is at least $\Omega(\log(T))$.
-
-\section{Conclusion}
-In this paper, we study the incentivizing exploration problem with heterogeneous user preferences, which generalize the problem setting studied by \cite{frazier2014incentivizing} and \cite{han2015incentivizing}.
-We propose a simple policy that mostly exploits and occasionally incentivizing exploration, which can achieve $O(N^2+M(\log(T))^2)$ cumulative expected regret with $O(N^2)$ payment budget.
-
-\bibliography{reference}{}
-\bibliographystyle{plain}
-
-\end{document}

### 2018-01-26 problem_setting.tex
divide the paper into sections

--- 2017-12-04 paper.tex
@@
-\documentclass{article}
-\usepackage[utf8]{inputenc}
-
-\usepackage[english]{babel}
-
-\usepackage{blindtext}
-\usepackage{amssymb}
-
-\usepackage[]{algorithm}
-\usepackage[]{algorithmic}
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{xr} 
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{amsthm}
-\usepackage{comment}
-\usepackage{graphicx}
-\usepackage{subcaption}
-\usepackage{xcolor}
-\usepackage{amsmath}
-\usepackage{dblfloatfix}
-\usepackage{bbm}
-
-\newcommand{\IE}{IE} 
-\newcommand{\argmax}{\mathop{\mathrm{argmax}}}
-
-\newcommand\floor[1]{\lfloor#1\rfloor}
-\newcommand\ceil[1]{\lceil#1\rceil}
-
-\newcommand{\bccomment}[1]{{\color{blue}BC: #1}}
-\newcommand{\pfcomment}[1]{{\color{blue}PF: #1}}
-
-\newtheorem{definition}{Definition}[section]
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{corollary}{Corollary}
-\newtheorem{assumption}{Assumption}
-
-\title{Incentivizing Exploration with Heterogeneous Utilities}
-
-\begin{document}
-
-\maketitle
-
-\section{Introduction}
-In this paper, we study incentivizing exploration with heterogeneous agent preferences.
-In this problem,   
-arms have unknown multivariate attributes, and agents have heterogeneous linear utility functions that map these attribute vectors onto utilities.
-Agents see noisy observations of attributes of arms pulled by all previous agents, and estimate an arms' attribute vector by the simple average of these observations.
-Agents are selfish, and pull the arm with the largest estimated utility summed with an optional arm-specific incentivizing payment chosen by the principle.
-We study strategies for choosing such incentive payments that seek to maximize the total utility derived by agents, subject to a limitation on the total incentive payment.
-To accomplish this goal, a strategy must induce sufficient exploration to reveal arms' attributes, while still letting agents select myopically and according to their preferences sufficiently often that high-utility arms are chosen and incentive payments are kept small.
-
-Our problem setting models online review aggregators like Amazon, Yelp, and Tripadvisor that host crowdsourced reviews.
-Users of these websites wish to use the reviews hosted there to choose the product / restaurant / vacation (generically referred to as an ``item'') that is best according to their preferences.
-These reviews provide not just cardinal feedback, but also a description of items' attributes that a user may consider together with their personal preferences to select their preferred item.
-An item with few reviews might have inaccurate attribute estimates, leading users to avoid it even though it may actually be their best choice.
-Without incentives, this situation may persist and decrease welfare for the platform's user base.
-By offering incentives, either through price reductions by Amazon or coupons from Yelp or Tripadvisor, a platform may induce more reviews of unexplored items and provide more value over the long term.
-
-Our problem setting also applies to crowd science platforms like eBird \cite{frazier2014incentivizing, sullivan2009ebird}.
-EBird guides birding enthusiasts through a website to explore and report their findings to the birding community.
-Each user report contains information about when, where and how they go birding and what birds they see and hear.
-EBird may wish to incentivize enthusiasts to explore less-explored birding locations and provide more accurate reports on these locations.
-Each enthusiast may have different preference over a location's attributes such as the diversity of bird species, weather, distance and safety.
-By offering enthusiasts incentivies to explore, eBird can create a more accurate body of reports and provide better value to the birding community.
-
-% Something interesting to study would be to alter the search rankings to influence people
-% Also which items to spam people about reviewing
-
-In this problem context, we study a simple policy that usually exploits, incentivizing agents to pull an arm only when the set of agent utility functions that would pull this arm without incentives has probability below a time-varying threshold.
-In our paper, we assume all arms are some agents' best arm.
-Under this assumption, we prove that with $O(N^2)$ payment budget, this policy has $O(N^2+M(\log(T))^2)$ cumulative expected regret where $M$ is an upper bound on the limiting marginal probability density of agent utilities that are nearly indifferent between their best and the second best arm.
-If all agents' utility difference between their best and second best arm is bounded below by a positive number, which typically happens when the agent utility distribution is discrete, this policy achieve constant cumulative expected regret $O(N^2)$.
-The key difference between our problem setting and both the homogenous preference setting and the traditional multi-armed bandits setting is that we must incentivize agents to try suboptimal arms much less often, since all arms are some agents' best arm.
-Essentially, heterogeneity provides free exploration.
-These results suggest that heterogeneous agent preferences reduce but do not eliminate the need to incentive exploration, in relation to single-preference settings.
-
-We broadly categorize the relevant previous literature into two categories based on whether there is money transfer.
-With money transfer, \cite{frazier2014incentivizing} considers a problem setting where the principal pays agents money to explore.
-This work assumes all agents have equal value for money and provide a complete characterization of achievable reward with a fixed budget.
-\cite{han2015incentivizing} generalizes this framework to include agents with heterogeneous value for money, and to allow an external signal to provide partial information about this valuation.
-Under this setting, this work proves a bound on achievable reward as a function of the budget and the signal scheme.
-
-Without money transfer but using information asymmetry, \cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time.
-\cite{mansour2015bayesian} generalizes \cite{kremer2014implementing} by allowing a finite number of actions at each time.
-\cite{mansour2016bayesian} considers a problem setting where there are multiple agents at each time and agents may interact with each other.
-In these papers, the principal provides each agent a recommendation at each time that is Bayesian incentive-compatible.
-They prove the principal can achieve constant regret when utilities are deterministic and logarithmic regret when utilities are stochastic.
-
-We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+M(\log(T))^2)$ regret with $O(N^2)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
-
 \section{Problem Setting}
@@
 We call time $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$ the {\it starting point of the $n^{th}$ round}. We call the set of times $[t_{n}, t_{n+1})$ the {\it $n^{th}$ round}.
-
-\section{Algorithm and Upper Bound}
-\label{sec:ub}
-
-In this section, we propose a simple policy that mostly exploits, and occasionally incentivizes exploration when the probability of an arm would be pulled by all agent types below a time-varying threshold given the current posterior.
-We prove that with the help of heterogeneous preferences, we can get a certain amount of exploration for free via heterogeneity.
-
-\subsection{Our Algorithm}
-Our algorithm incentivizes pulling an arm $i$ at a time $t$ in round $n$ if and only if both of the following criteria are met:
-\begin{itemize}
-\item the probability of pulling arm $i$ would be below $n^{-1}$ without incentives; 
-\item arm $i$ has not been played previously in the current round.
-\end{itemize}
-Ties are broken randomly.  This algorithm does not need to know the horizon $T$ in advance.
-
-If our algorithm decides to incentivize an arm $i$, it uses the ``pay whatever it takes'' strategy in which the payment offered is $\max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$.
-This maximum over $\theta$ is taken over the support of $F$, which we recall is assumed compact.
-(We use this ``pay whatever it takes'' strategy for its simplicity, and in Section~\ref{sec:pi} we provide an alternate and smaller incentive payment that achieves the same payment budget bound and regret bound).
-
-We describe our algorithm in detail as follows:
-
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration}
-\label{Alg1}
-\begin{algorithmic}
-\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
-\FOR{ $t = 1, 2, 3, \cdots$}{
-	\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
-  \IF {$S\setminus V$ is non-empty}
-    \STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
-    \STATE{Pay whatever it takes to incentivize pulling arm $i$, i.e., offer payment 
-    $c_{i,t} = \max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$ and $c_{j,t} = 0$ for $j \ne i$.}
-  \ELSE
-  \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
-  \ENDIF
-  \STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
-  \IF {$n\neq \min_{i}N(i,t)$} 
-  	\STATE $V=\emptyset$
-  \ENDIF
-  \STATE Update the round number, $n = \min_{i} N(i,t)$
-}\ENDFOR
-
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{Assumptions}
-In this section, we state several assumptions assumed by our analysis.  First define
-\begin{align}
-\Omega_{i,j}=\{\theta:B(\theta)=i, \hat{B}(\theta)=j\}, \nonumber 
-\end{align}
-which is the set of agent preferences whose best arm is arm $i$ and second best arm is arm $j$. With this definition, our analysis makes the following assumptions:
-
-\begin{assumption} Let $F_{i,j}(y)$ be the marginal cumulative density function (or cumulative mass function if $F(\cdot)$ is a discrete distribution) of $(u_i-u_j)\cdot\theta$ conditioned on $\theta \in \Omega_{i,j}$.
-We assume $F_{i,j}(y)\leq My$ for all $y\in R^{+}$, $\forall i,j$.
-\label{A1}
-\end{assumption}
-
-As we can see later in our proof, we only need $\max_{i,j}\limsup_{y\rightarrow 0^{+}}\frac{F_{i,j}(y)}{y}$ to be finite.
-Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm.
-
-\begin{assumption} We assume $F$ has a compact support set. Without loss of generality, we assume $\theta\in [0,W]^m$.
-\label{A2}
-\end{assumption}
-
-We use $R = \max_{\theta, i,j} \theta \cdot (u_i - u_j)$ to denote the maximum regret that can be incurred at each time.  Assumption~\ref{A2} shows that $R<\infty$.
-
-\begin{assumption}
-Denote $p=\min_{i}P(\{\theta: B(\theta)=i\})$. We assume $p>0$.
-\label{A3}
-\end{assumption}
-
-Assumption~\ref{A3} means each arm $i$ has a strictly positive proportion of users for which that arm is best.
-
-\subsection{General Results}
-
-In this section, we prove Algorithm~\ref{Alg1} achieves $O(N^2+M(\log(T))^2)$ cumulative regret with $O(N^2)$ payment budget.
-This is stated in the following pair of theorems, which together constitute our main results.
-
-\begin{theorem}
-The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$. 
-\label{rst:budget}
-\end{theorem}
-
-\begin{theorem}
-The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2 m + M m^2(\log(T))^2)$.
-\label{rst:regret}
-\end{theorem}
-
-Before we prove these two theorems, we must first introduce two additional pieces of notation, which will be used in preliminary lemmas.
-Let $S(\delta)$ be the proportion of users whose utility difference between their best and second best arm is less than $\delta$.
-Formally, $S(\delta)=P(\theta: \theta \cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}\leq \delta)$.
-Then, let $p(\delta)=\min_{i}P(\{\theta:B(\theta)=i,\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$.
-We know $p(0)=p$.
-
-With this additional notation, we now prove several lemmas.
-First, based on Assumption~\ref{A1}, we have the following bound for $S(\delta)$.
-
-\begin{lemma}
-$S(\delta)\leq M\delta$.
-\label{lemma:sdelta}
-\end{lemma}
-
-\begin{proof}
-\begin{align*}
-S(\delta)
-&=\sum_{i,j}P(\theta\cdot(u_{i}-u_{j})\le \delta|\theta\in \Omega_{i,j})P(\theta\in \Omega_{i,j}) \\
-&\leq \sum_{i,j}M\delta \times P(\theta\in \Omega_{i,j}) \\
-&=M\delta.
-\end{align*}
-\end{proof}
-
-The following lemma bounds the probability of making a mistake if we let the agents play myopically in the $n^{th}$ round, given that the utility difference between his/her best and second best arm is bounded below by a constant.
-
-\begin{lemma}
-Define $\tau$ to be any stopping time that is almost surely between $t_n$ and $t_{n+1}-1$ with respect to the filtration $\mathcal{F}_{t}=\sigma(A_1,\cdots,A_t,c_1,\cdots,c_t,O_1,\cdots,O_t)$, we have
-\begin{align}
-P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{16\sigma^2}\right), \nonumber
-\end{align}
-for $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$.
-\label{round:prob}
-\end{lemma}
-
-We need the following lemma in order to prove Lemma~\ref{round:prob}.
-
-\begin{lemma}
-For $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$, we have
-\begin{align}
-\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-\label{n0-inequality}
-\end{lemma}
-
-\begin{proof}
-First, we observe that
-\begin{align}
-&\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)} \nonumber \\
-\iff &\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{9.6\sigma^2}{\lambda^2}. \nonumber 
-\end{align}
-Since $\log(x)\leq x-1$ for $x>0$, we know 
-\begin{align}
-\log(\log_{1.1}(n)+1)=\log\left(\frac{\log(n)}{\log(1.1)}+1\right)\leq \log(11\log(n)+1)\leq \log(11n)\leq 3+\log(n). \nonumber
-\end{align}
-
-Thus, we know
-\begin{align}
-\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{n}{3+\log(n)}. \nonumber 
-\end{align}
-
-To prove the lemma, we just need to show for $n\geq n_{0}$, we have
-\begin{align}
-\frac{n}{3+\log(n)}\geq \frac{9.6\sigma^2}{\lambda^2}. \label{n0-equ}
-\end{align}
-Inequality~(\ref{n0-equ}) is true because of the following two observations:
-\begin{itemize}
-\item for $n\geq 50$, we have $\frac{n}{3+\log(n)}\geq n^{0.5}$;
-\item for $n\geq \frac{92.16\sigma^4}{\lambda^4}$, we have $n^{0.5}\geq {9.6\sigma^{2}}{\lambda^{2}}$.
-\end{itemize}
-
-Thus, we know our lemma is true.
-
-\end{proof}
-
-To prove Lemma~\ref{round:prob}, we also need to use an adaptive concentration inequality due to \cite{zhao2016adaptive}. For reference, we state it here as a Lemma.
-
-\begin{lemma}[Corollary 1 in \cite{zhao2016adaptive}]
-Let $X_{i}$ be zero mean $1/2$-subgaussian random variables.
-$\{S_{n}=\sum_{i=1}^{n}X_{i},n\geq 1\}$ be a random walk.
-Let $J$ be any stopping time with respect to $\{X_1,X_2,\cdots\}$.
-We allow $J$ to take the value of $\infty$ where $P(J=\infty)=1-\lim_{n\rightarrow \infty}P(J\leq n)$.
-If
-\begin{align}
-f(n)=\sqrt{0.6n\log(\log_{1.1}(n)+1)+bn}, \nonumber
-\end{align}
-then
-\begin{align}
-Pr[\{S_{J}\geq f(J)\}\cap \{J<\infty\}]\leq 12e^{-1.8b}. \nonumber
-\end{align}
-\label{ACI-inequality}
-\end{lemma}
-
-We now prove Lemma~\ref{round:prob}.
-
-\begin{proof}[Proof of Lemma~\ref{round:prob}]
-In the $n^{th}$ round, we know all arms have been pulled at least $n$ times.
-For all the agents $\theta$ whose utility difference between their best and second best arm is greater than $2mW\lambda$, denote $K(\theta)=\max_{i\neq B(\theta)}\{\theta\cdot u_{i,t}\}$.
-If $|u_{i,t}^{j}-u_{i}^{j}|\leq \lambda$ for all $i,j$, then
-\begin{align}
-&\theta\cdot(u_{B(\theta),t}-u_{K(\theta),t}) \nonumber \\
-\geq & \theta\cdot(u_{B(\theta),t}-u_{B(\theta)}) + \theta\cdot(u_{K(\theta)}-u_{K(\theta),t}) + \theta\cdot(u_{B(\theta)}-u_{K(\theta)}) \nonumber \\
-> & -Wm\lambda - Wm\lambda + 2Wm\lambda = 0,\nonumber
-\end{align}
-which means their myopic action would incur no regret.
-
-Define $\epsilon_{i,\tau}=u_{i,\tau}-u_i$ and $\epsilon_{i,\tau}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,\tau}$. Thus, we have
-\begin{align}
-&P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\nonumber \\
-\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda |\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda). \label{ACI}
-\end{align}
-
-To bound equation~(\ref{ACI}), we use Lemma~\ref{ACI-inequality}. Define
-\begin{align}
-S_{N(i,\tau)}^{i,j}=\frac{\epsilon_{i,\tau}^{j}}{2\sigma}. \nonumber
-\end{align}
-
-Based on Lemma~\ref{n0-inequality}, for $n_{0}=\max\{50, \frac{92.16\sigma^2}{\lambda^2}\}$ and $n\geq n_{0}$, we have
-\begin{align}
-\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-
-Thus, if we set $b=\frac{n\lambda^2}{16\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,\tau)\geq n\geq n_{0}$, we have
-\begin{align}
-\frac{N(i,\tau)\lambda}{2\sigma}\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)}+\frac{\lambda}{4\sigma}\sqrt{n N(i,\tau)} \nonumber \\
-\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)+bN(i,\tau)}, \nonumber 
-\end{align}
-where the last inequality is because $\sqrt{x}+\sqrt{y}\geq \sqrt{x+y}$. Thus, we have
-\begin{align}
-&P(\epsilon_{i,\tau}^{j}\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P\left(S_{N(i,\tau)}^{i,j}\geq \frac{N(i,\tau)\lambda}{2\sigma}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
-\leq & P\left(S_{N(i,\tau)}^{i,j}\geq \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
-\leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
-\end{align}
-Similarily, we can bound 
-\begin{align}
-&P(\epsilon_{i,\tau}^{j}\leq-\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P(-\epsilon_{i,\tau}^{j}\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber 
-\end{align}
-
-Therefore, we know $P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right)$.
-Thus, we know
-\begin{align}
-&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)  \nonumber \\
-\leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
-\end{align}
-
-\end{proof}
-
-Before we start analyzing the cumulative regret, we first prove the following lemma which bounds the expected length of each round.
-
-\begin{lemma}
-Using our algorithm, we have $\mathbb{E}[t_{n+1}-t_{n}]\leq Nn$, $\forall n\geq 1$.
-\label{round:length}
-\end{lemma}
-
-\begin{proof}
-	A round completes when each arm is pulled at least once in that round.
-Let $X_{i}$ be the number of agents who come to the system between the time after the $(i-1)^{th}$ unique arm was pulled, up to and including the time when the $i^{th}$ unique arm was pulled.
-Then we know
-\begin{equation*}
-\mathbb{E}[t_{n+1}-t_{n}]=\sum_{i=1}^{N}E[X_{i}].
-\end{equation*}
-
-Fix $i$.
-In bounding $X_i$, we think of agents as ``trials'', where each trial can result in a new unique arm being pulled (which we call a ``successful'' trial), or not.
-There are two ways a trial can be successful:
-\begin{itemize}
-\item If there is at least one arm that has not been pulled and the probability of an agent utility function that would pull this arm without incentives is less than $n^{-1}$, then the principal will offer an incentive that causes this arm to be pulled (or one of these arms if there is more than one).
-In this case, the probability that the trial is succesful is $1$.
-\item The probability of an agent utility function that would pull each un-pulled arm without incentives is at least $n^{-1}$.
-In this case, the probability that the trial is successful is at least $n^{-1}$.
-\end{itemize}
-
-Thus, $X_{i}$ is stochastically dominated below by a geometric random variable with success probability $n^{-1}$, the expected number of trials up to and including the first success, $E[X_i]$, is bounded above by $n$.
-Thus,
-\begin{align}
-E[t_{n+1}-t_{n}]\leq Nn. \nonumber
-\end{align}
-\end{proof}
-
-We also need the following lemma in part of the proof of Theorem~\ref{rst:budget}.
-\begin{lemma}
-For all $n\geq 1$, we have
-\begin{align}
-0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-\label{lemma:cal2}
-\end{lemma}
-\begin{proof}
-\begin{align}
-&0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)} \nonumber \\
-\iff & 0.81 n^{5/3} \geq 0.6n \log(\log_{1.1}(n)+1) \nonumber \\
-\iff &  \frac{81}{60} n^{2/3} \geq  \log(\log_{1.1}(n)+1) \nonumber
-\end{align}
-
-Denote $f(x) = \frac{81}{60}x^{2/3} - \log(\log_{1.1}(x)+1)$.
-It's easy to compute $f^{'}(x)=0$ has a unique solution $x_{0}=e^{2/3w(\frac{20e^{20000/314763}}{27})-\frac{10000}{104921}}$ (here $w(\cdot)$ is the Lambert W-Function) and it is the global minimum.
-Since $f(x_{0})\approx 0.0252 >0$, we know $f(x)>0$ for all $x\geq 1$.
-Thus, our lemma holds true.
-\end{proof}
-
-Now we are ready to prove our first main result, Theorem~\ref{rst:budget}.
-
-\begin{proof}
-Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$.
-Denote $\epsilon_{i,t}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,t}$.
-Denote $\omega$ to be a sample path and $n(t,\omega)$ to be the round number for sample path $\omega$ at time $t$.
-For a fixed time $t$, define
-\begin{align}
-L^{'}[l](t) = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n(t,\omega),l), \forall i,j\}\nonumber
-\end{align}
-where $g(n,l)$ is a function which we will define later.
-Define $L[1](t) = L^{'}[1](t)$ and $L[i](t) = L^{'}[i](t)\setminus L^{'}[i-1](t)$ for $i\geq 2$.
-We call $L[l](t)$ the $l^{th}$ envelope at time $t$.
-We often simplify the notation and use $L[l]$ instead of $L[l](t)$ without confusion.
-
-In the calculation below, we omit the dependency on $\omega$ when refering to variables $c(t)$, $\epsilon_{i,t}^{j}$ and $t_n$.
-Based on the definition of $L[l]$, we know if $\omega\in L[l]$, the maximum payment we need to offer at time $t$ is bounded above by
-\begin{align}
-&\max_{i}\theta_t\cdot u_{i,t} - \min_{j}\theta_t\cdot u_{j,t} \nonumber \\
-= &\max_{i}\theta_t\cdot (\epsilon_{i,t}+u_i) - \min_{j}\theta_t\cdot (\epsilon_{j,t}+u_j) \nonumber \\
-\leq &\max_{i}\theta_t\cdot u_i - \min_{j}\theta_t\cdot u_j +\max_{i}\theta_t\cdot \epsilon_{i,t} - \min_{j}\theta_t\cdot \epsilon_{j,t}\nonumber \\
-\leq & R + 2Wmg(n,l). \nonumber
-\end{align}
-
-Based on the above notations, we can rewrite the cumulative payment as follows:
-\begin{align}
-&\sum_{t=1}^{\infty}c(t) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\} \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\infty}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
-\end{align}
-
-Set $g(n,l)$ to be $\frac{2\sigma l}{n^{1/6}}$.
-Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2Wm\lambda\}$, they will correctly identify their best arm.
-Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{2\sigma l}{n^{1/6}} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
-Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms.
-Denote $a_0=\frac{4Wm\sigma}{p^{-1}(\frac{p}{2})}$.
-In order to have $\frac{2\sigma l}{n^{1/6}}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil (a_{0} l)^6 \rceil$.
-In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
-Denote $n_2=\frac{2}{p}$.
-Thus, we know we can only incur regret for sample paths $\omega$ in the $l^{th}$ envelope in the first $\max\{n_2,\lceil (a_0 l)^6 \rceil\}$ rounds.
-
-Thus,
-\begin{align}
-\sum_{t=1}^{\infty}c(t)=\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}c(t)\mathbbm{1}\{\omega\in L[l]\}\mathbbm{1}\{t\in [t_n,t_{n+1})\}. \nonumber
-\end{align}
-
-Therefore,
-
-\begin{align}
-&E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}E[c(t)|\omega \in L[l],t\in [t_n,t_{n+1}))P(\omega\in L[l],t\in [t_n,t_{n+1})) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+2Wm\frac{2\sigma l}{n^{1/6}}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-=&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})). \nonumber
-\end{align}
-
-We now bound $P(\omega\in L[l]|t\in[t_{n},t_{n+1}))$ for $n\geq n_0$ and $l\geq 2$.
-\begin{align}
-&P(\omega\in L[l]|t\in[t_{n},t_{n+1})) \nonumber \\
-=&P(\omega\in L^{'}[l]|t\in[t_{n},t_{n+1}))- P(\omega\in L^{'}[l-1]|t\in[t_{n},t_{n+1})) \nonumber \\
-\leq & 1-P\left(|\epsilon_{i,t}^{j}|<\frac{2\sigma (l-1)}{n^{1/6}}, \forall i,j|t\in[t_n,t_{n+1})\right) \nonumber \\
-=&P\left(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})\right) \nonumber  \\
-\leq &\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (l-1)}{n^{1/6}}|t\in[t_n,t_{n+1})\right) \nonumber
-\end{align}
-
-Define $S_{i,t}^{j}=\frac{N(i,t)\epsilon_{i,t}^{j}}{2\sigma}$, then we know $S_{i,t}^{j}$ is a summation of $1/2$ gaussian random numbers. Therefore,
-
-\begin{align}
-&\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma(l-1)}{n^{1/6}}\bigg|t\in[t_n,t_{n+1})\right) \nonumber \\ 
-=&\sum_{i,j}P\left(|S_{i,t}^{j}|\geq \frac{N(i,t)(l-1)}{n^{1/6}}\bigg|t\in[t_n,t_{n+1})\right) \nonumber \\
-\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})). \nonumber
-\end{align}
-
-Based on Lemma~\ref{lemma:cal2}, we know
-\begin{align}
-&N(i,t)^{5/6}(l-1) \nonumber \\
-=& 0.9N(i,t)^{5/6} + N(i,t)^{5/6}(l-1.9) \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)} + \sqrt{(l-1.9)^2 N(i,t)} \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+(l-1.9)^2 N(i,t)}. \nonumber
-\end{align}
-
-Based on Lemma~\ref{ACI-inequality}, we know
-\begin{align}
-&\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(l-1)|t\in[t_n,t_{n+1})) \nonumber \\
-\leq & \sum_{i,j}24e^{-1.8(l-1.9)^2} = 24Nme^{-1.8(l-1.9)^2}. \nonumber
-\end{align}
-
-Thus,
-\begin{align}
-&\sum_{t=1}^{\infty}c(t) \nonumber \\
-\leq&\sum_{l=1}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+2Wm\frac{2\sigma l}{n^{1/6}}\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-\leq& \sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(\omega\in L[1]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-+&\sum_{l=2}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[l]|t\in [t_n,t_{n+1}))P(t\in [t_n,t_{n+1})) \nonumber \\
-\leq& \sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(t\in [t_n,t_{n+1})) \nonumber \\
-+&\sum_{l=2}^{\infty}\sum_{t=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]24Nme^{-1.8(l-1.9)^2}P(t\in [t_n,t_{n+1})) \nonumber \\
-\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]Nn +\sum_{l=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 l)^6 \rceil\}}\left[R+4Wm\sigma l\right]24Nme^{-1.8(l-1.9)^2}Nn \nonumber \\
-\leq & \left[R+4Wm\sigma \right]N (\max\{n_2,\lceil (a_0)^6 \rceil\})^2+\sum_{l=2}^{\infty}24N^2 m[R+4Wml\sigma](\max\{n_2,\lceil (a_0 l)^6 \rceil\})^2 e^{-1.8(l-1.9)^2} \nonumber \\
-=& O(N^2). \nonumber
-\end{align}
-
-\end{proof}
-
-\begin{lemma}
-The expected number of payments for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$.
-\label{lemma:numP}
-\end{lemma}
-
-\begin{proof}
-If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2mW\lambda\}$, they will correctly identify their best arm.
-Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms.
-In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
-Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$.
-Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).
-
-Define $\tau_{n}^{i}$ to be the first time we pull arm $i$ in the $n^{th}$ round. Then
-\begin{align}
-\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\} =\sum_{n=1}^{\infty}\sum_{i=1}^{N}\mathbbm{1}\{c(\tau_{n}^{i})>0\}. \nonumber
-\end{align}
-
-The cumulative expected number of payments is bounded above by:
-\begin{align}
-&E\left[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}\right] \nonumber \\
-=&\sum_{n=1}^{\infty}\sum_{i=1}^{N}P(c(\tau_{n}^{i})>0) \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}P\left(\exists i,j:|u_{i}^{j}-u_{i,\tau_{n}^{i}}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2Wm}\right)+\sum_{n=1}^{n_1}N \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right) +\sum_{n=1}^{n_1}N \nonumber \\
-\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right)\times N+\sum_{n=1}^{n_1}N \nonumber  \\
-\leq&24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1, \nonumber
-\end{align}
-
-Thus, we know the expected number of payments is bounded above by $O(N^2)$.
-
-\end{proof}
-
-Now we are ready to prove our second main result, Theorem~\ref{rst:regret}.
-
-\begin{proof}
-For regret incurred in the first $n_0$ round, it is bounded above by $\sum_{n=1}^{n_{0}}NRn$.
-
-For regret incurred after the first $n_0$ round, it has two different components: the regret incurred when we let the agents play myopically and the regret incurred when we incentivize the agents.
-Using Lemma~\ref{lemma:numP}, the expected regret incurred when we incentivize the agents is bounded above by: $\left[24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1\right]R$.
-
-For the regret incurred when we let the agents play myopically at time $t\geq t_{n_0}$, it consists of the following two components:
-\begin{itemize}
-\item For those users whose utility difference between their best and the second best arm is greater than $f(t)$: we define a sequence of stopping time $\tau_{n}^{k}$ to be the $k^{th}$ time period in the $n^{th}$ round.
-For $\tau_{n}^{k}=t$, the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)\times R$.
-We denote the regret incurred by these agents as $r_1(\tau_{n}^{k})$.
-\item For those user whose utility difference between their best and the second best arm is smaller than $f(t)$: this happens with probability $S(f(t))$ at each time and regret is bounded above by $S(f(t)) \times f(t)=Mf(t)^2$.
-We denote the regret incurred by these agents as $r_2(t)$.
-\end{itemize}
-
-Thus, the cumulative expected regret incurred up to time $T$ when we let the agent play myopically is bounded above by:
-\begin{align}
-&E\left[\sum_{t=1}^{T}r(t)\right] \nonumber \\
-=&E\left[\sum_{t=1}^{t_{n_{0}}} r(t) + \sum_{t=t_{n_{0}}}^{T}(r_1(t)+r_2(t))\right]  \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}-1}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-&\bccomment{\text{is the following proof correct? I think it might be wrong}} \nonumber \\
-= & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{t_{n+1}-t_{n}}r_1(\tau_{n}^{k})\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{k=1}^{t_{n+1}-t_n}24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}E\left[\sum_{k=1}^{t_{n+1}-t_n}24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R\right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \label{equ:regret}
-\end{align}
-
- Thus the cumulative regret at time $T$ is bounded above by
-\begin{align}
-&\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-+ & 24N^2 m \frac{1}{e^{\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2}}-1}R+N\left(\max\left\{n_{0},\frac{2}{p}\right\}\right)R. \nonumber
-\end{align}
-
-For a fixed $T$, we only need to minimize the following two terms since all others are constant:
-
-\begin{align}
-\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2.
-\end{align}
-
-If we set $f^2(t)=\frac{2\log(T)\times 64W^2 m^2\sigma^2}{1.8t}$, then
-\begin{align}
-&\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\ 
-\leq & \sum_{n=1}^{T} 24N^2 mnR \exp\left(-2\log(T)\right)  + \frac{128W^2 m^2\sigma^2 M\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{n} \nonumber \\
-\leq &  24N^2 m R\frac{T(T-1)}{2T^2}  + 71.12 W^2 m^2\sigma^2 M\log(T)(\log(T)+1) \nonumber \\
-\leq &  12 N^2 m R  + 71.12 W^2 m^2\sigma^2 M\log(T)(\log(T)+1). \nonumber
-\end{align}
-
-Thus, the cumulative expected regret is bounded by $O(N^2 m + M m^2\log(T))$.
-\end{proof}
-
-\begin{corollary}
-If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O(N^2)$.
-\end{corollary}
-
-\begin{proof}
-The proof of this corollary is similar to the proof of Theorem~\ref{rst:regret}.
-If we set $f^2(t)=\frac{2\log(T)\times 64W^2 m^2\sigma^2}{1.8t}$, then there exists a $t_{0}$ such that for $t>t_{0}$, $S(f(t))=0$.
-Thus, similar to equation~\eqref{equ:regret}, we know the cumulative expected regret when we let the agents play myopically is bounded above by
-\begin{align}
-\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{t_{0}}Mf(t)^2 \nonumber
-\end{align}
-Therefore, based on the same analysis of Theorem~\ref{rst:regret}, we know the cumulative regret is bounded by $O(N^2)$.
-\end{proof}
-
-\subsection{Practical Issues}
-\label{sec:pi}
-
-In Algorithm~\ref{Alg1}, we use ``pay whatever it takes'' strategy when we decide to incentivize the agent.
-However, ''pay whatever it takes'' only shows up in the proof of Lemma~\ref{round:length}.
-Without loss of generality, suppose we want to incentivize arm $i$ at time $t$ at the $n^{th}$ round.
-Based on the proof of Lemma~\ref{round:length}, as long as we offer a payment $c_{i,t}$ such that arm $i$ has at least $n^{-1}$ probability being pulled at time $t$, our results still hold true.
-We could compute this $c_{i,t}$ dynamically based on $F(\cdot)$ as well as our current estimate $u_{i,t}$.
-Here is the revised algorithm which would work well in practice:
-
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration}
-\label{Alg2}
-\begin{algorithmic}
-\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
-\FOR{ $t = 1, 2, 3, \cdots$}{
-	\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
-  \IF {$S\setminus V$ is non-empty}
-    \STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
-	\STATE{Offer payment $c_{i,t}=\inf\{c: P(\theta\sim F: \theta\cdot u_{i,t}+c>max_{j}\theta\cdot u_{j,t})>n^{-1}\}$}
-  \ELSE
-  \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
-  \ENDIF
-  \STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
-  \IF {$n\neq \min_{i}N(i,t)$} 
-  	\STATE $V=\emptyset$
-  \ENDIF
-  \STATE Update the round number, $n = \min_{i} N(i,t)$
-}\ENDFOR
-
-\end{algorithmic}
-\end{algorithm}
-
-The same proof would work and we can get the exact same results as Algorithm~\ref{Alg1}.
-
-\section{Lower Bound $\Omega(\log(T))$}
-\label{sec:lb}
-
-In this section, we assume $\theta$ follows a continuous distribution $F(\cdot)$.
-We provide an example to show the best possible lower bound is $\Omega(\log(T))$ regardless of the incentivizing strategy.
-
-Suppose we have two arms.
-Arm $1$ has attribute vector $(0,0)$ and arm $2$ has attribute vector $(0,1)$.
-We assume the users' preference are uniformly distributed on the unit circle.
-If the user knows the exact attribute vectors for both arms, then the users with preference on the bottom half circle will choose arm $1$ and the users with preference on the top half circle will choose arm $2$.
-
-Consider the following algorithm: at each step, let the agents play myopically; however, they are going to see the noisy rewards for both arms.
-
-To lower bound the regret, we assume that the agents already know the true attribute vector for arm $1$.
-Without loss of generality, denote $u_{2,t} = (0,1)+(z_{t,1},z_{t,2}) = (0,1)+ (N(0,1/t),N(0,1/t))$ to be the estimate attribute vector for arm $2$ (Without loss of generality, we assume the variance for the noise is $1$).
-
-Since $(z_{t,1}, z_{t,2})$ is symmetric around $(0,0)$, we know
-
-\begin{align}
-&E[r(t)] \nonumber \\
-= &E[r(t) | z_{t,1}>0,z_{t,2}>0] \times P(z_{t,1}>0,z_{t,2}>0) + E[r(t) |z_{t,1}>0,z_{t,2}<0] \times P(z_{t,1}>0,z_{t,2}<0) \nonumber \\
-&+E[r(t) | z_{t,1}<0,z_{t,2}>0] \times P(z_{t,1}<0,z_{n,2}>0) + E[r(t) |z_{t,1}<0,z_{t,2}<0] \times P(z_{t,1}<0,z_{t,2}<0) \nonumber \\
-\geq & 0.25 \times E[r(t) | z_{t,1}>0, z_{t,2}>0]. \nonumber
-\end{align}
-
-Given $z_{t,1}>0$ and $z_{t,2}>0$, we know users whose preference vector between $(-1,0)$ and $\left(\frac{-1-z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ as well as users whose preference vector between $(1,0)$ and $\left(\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{-z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ will make a mistake.
-The regret is the absolute value of the second coordinate of the user's preference vector.
-Thus, we know
-
-\begin{align}
-&E[r(t)| z_{t,1}>0, z_{t,2}>0] \nonumber \\
-=& 4\times 2 \int_{0}^{\infty} \int_{0}^{\infty} \int_{0}^{\arctan\left(\frac{z_{t,1}}{1+z_{t,2}}\right)}\frac{\sin(\theta)}{2\pi}d(\theta)\frac{e^{-\frac{t \times z_{t,1}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,1})\frac{e^{-\frac{t \times z_{t,2}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,2}) \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}t\times \left[1-\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right]e^{-\frac{t \times z_{t,1}^2}{2}}e^{-\frac{t \times z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty} \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber
-\end{align}
-
-Below, we want to show 
-\begin{align}
-\lim_{t\rightarrow\infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} = O(1), \nonumber
-\end{align}
-and use the fact that $\sum_{n=1}^{T}\frac{1}{n}=O(\log(T))$ to show the regret is at least $\Omega(\log(T))$.
-
-Denote $d(t)=t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]$.
-Since
-\begin{align}
-d^{'}(t)=\frac{-z_{t,1}^2(2z_{t,2}+3\sqrt{t})-2(z_{t,2}+\sqrt{t})^3}{2(z_{t,1}^2+(z_{t,2}+\sqrt{t})^2)^{3/2}}+1. \nonumber
-\end{align}
-
-and $\lim_{t\rightarrow \infty}d^{'}(t)=2$, we know for $t$ large enough, $d(t)$ is a increasing function in terms of t. Thus, based on the Monotone Convergence Theorem, we have
-
-\begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber
-\end{align}
-
-Based on our calculation, we know
-
-\begin{align}
-\lim_{t\rightarrow \infty} d(t)=\frac{z_{t,1}^2}{2}. \nonumber
-\end{align}
-Thus,
-\begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{t} \nonumber \\
-=&\frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ \frac{z_{t,1}^2}{2}e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) = \frac{1}{2\pi}.
-\nonumber
-\end{align}
-
-Thus, the cumulative expected regret is at least $\Omega(\log(T))$.
-
-\section{Conclusion}
-In this paper, we study the incentivizing exploration problem with heterogeneous user preferences, which generalize the problem setting studied by \cite{frazier2014incentivizing} and \cite{han2015incentivizing}.
-We propose a simple policy that mostly exploits and occasionally incentivizing exploration, which can achieve $O(N^2+M(\log(T))^2)$ cumulative expected regret with $O(N^2)$ payment budget.
-
-\bibliography{reference}{}
-\bibliographystyle{plain}
-
-\end{document}

### 2018-01-28 appendix.tex
did some minor changes to the lower bound section as well as the appendix

@@
 
-            In this section, we prove
-            \begin{align}
-            \lim_{t\rightarrow\infty} t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]=\frac{z_{t,1}^2}{2}. \nonumber 
-            \end{align}
-
-            Denote $w(x)=\sqrt{x}$. Then $w(x+y)=\sqrt{x} + y\frac{1}{2\sqrt{x}}+O(x^{-3/2})$. Thus, we know
+            In this section, we prove $d(t)\leq \frac{z_{t,1}^{2}}{2}$ and $\lim_{t\rightarrow\infty}d(t)=\frac{z_{t,1}^2}{2}$.
+Denote $w(x)=\sqrt{x}$.
+Then we know $w(x+y)\leq \sqrt{x} + y\frac{1}{2\sqrt{x}}$ and $w(x+y)\geq \sqrt{x} + y\frac{1}{2\sqrt{x+y}}$ for $y\geq 0$.
+Thus, we know
 
@@
             =& \lim_{t\rightarrow\infty} t\left[\frac{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}-\sqrt{t}-z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]  \nonumber \\
-            = & \lim_{t\rightarrow\infty} t\left[\frac{\sqrt{t}+z_{t,2}+z_{t,1}^{2}\frac{1}{2\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}+O((z_{t,1}^2+(\sqrt{t}+z_{t,2})^2)^{-3/2})-\sqrt{t}-z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]  \nonumber \\
+            \geq & \lim_{t\rightarrow\infty} t\left[\frac{\sqrt{t}+z_{t,2}+z_{t,1}^{2}\frac{1}{2\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}-\sqrt{t}-z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]  \nonumber \\
             = & \lim_{t\rightarrow\infty} t \times \frac{z_{t,1}^2}{2(z_{t,1}^2+(\sqrt{t}+z_{t,2})^2)} \rightarrow \frac{z_{t,1}^2}{2}. \nonumber 
             \end{align}
-
-            Therefore, we know Equation~\eqref{ex:limit} holds true.
+and
+            \begin{align}
+            &\lim_{t\rightarrow\infty} t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right] \nonumber \\
+            =& \lim_{t\rightarrow\infty} t\left[\frac{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}-\sqrt{t}-z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]  \nonumber \\
+            \leq & \lim_{t\rightarrow\infty} t\left[\frac{\sqrt{t}+z_{t,2}+z_{t,1}^{2}\frac{1}{2\sqrt{(\sqrt{t}+z_{t,2})^2}}-\sqrt{t}-z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]  \nonumber \\
+            = & \lim_{t\rightarrow\infty} t \times \frac{z_{t,1}^2}{2\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}(\sqrt{t}+z_{t,2})} \rightarrow \frac{z_{t,1}^2}{2}. \label{inequ:dct}
+            \end{align}   
+Based on inequality~\eqref{inequ:dct}, we know $d(t)\leq \frac{z_{t,1}^{2}}{2}$ and $\lim_{t\rightarrow\infty}d(t)=\frac{z_{t,1}^2}{2}$.

### 2018-01-28 lower_bound.tex
did some minor changes to the lower bound section as well as the appendix

@@
 Arm $1$ has attribute vector $(0,0)$ and arm $2$ has attribute vector $(0,1)$.
-We assume the users' preference are uniformly distributed on the unit circle.
+We assume the users' preference are uniformly distributed on the two dimensional unit circle.
 If the user knows the exact attribute vectors for both arms, then the users with preference on the bottom half circle will choose arm $1$ and the users with preference on the top half circle will choose arm $2$.
+It is easy to check that all our assumptions hold true in this example.
 
@@
 =& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}t\times \left[1-\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right]e^{-\frac{t \times z_{t,1}^2}{2}}e^{-\frac{t \times z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty} \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber
+=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty} \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}).
+\nonumber
 \end{align}
@@
 
-Denote $d(t)=t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]$. Based on our calculation (see appendix for details), we know
+Denote $d(t)=t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]$. Based on our calculation (see appendix for details), we know $d(t)\leq \frac{z_{t,1}^2}{2}$ and
 
@@
 \end{align}
-Thus,
+Based on the dominated convergence theorem, we know
 \begin{align}

### 2018-01-29 algorithm.tex
did some minor edits to our paper

@@
 \begin{align*}
-S(\delta)
-  &=\sum_{i,j}P(\theta\cdot(u_{i}-u_{j})\le \delta|\theta\in \Omega_{i,j})P(\theta\in \Omega_{i,j}) \\
+S(\delta)&=\sum_{i,j}P(\theta\cdot(u_{i}-u_{j})\le \delta|\theta\in \Omega_{i,j})P(\theta\in \Omega_{i,j}) \\
 &\leq \sum_{i,j}M\delta \times P(\theta\in \Omega_{i,j}) \\
@@
 
-    We need the following lemma in order to prove Lemma~\ref{round:prob}.
+We need the following lemma in order to prove Lemma~\ref{round:prob} and we include the proof in the appendix.
 
@@
 \end{lemma}
-
-    \begin{proof}
-    First, we observe that
-    \begin{align}
-    &\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)} \nonumber \\
-      \iff &\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{9.6\sigma^2}{\lambda^2}. \nonumber 
-      \end{align}
-      Since $\log(x)\leq x-1$ for $x>0$, we know 
-      \begin{align}
-      \log(\log_{1.1}(n)+1)=\log\left(\frac{\log(n)}{\log(1.1)}+1\right)\leq \log(11\log(n)+1)\leq \log(11n)\leq 3+\log(n). \nonumber
-      \end{align}
-
-      Thus, we know
-      \begin{align}
-      \frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{n}{3+\log(n)}. \nonumber 
-      \end{align}
-
-      To prove the lemma, we just need to show for $n\geq n_{0}$, we have
-      \begin{align}
-      \frac{n}{3+\log(n)}\geq \frac{9.6\sigma^2}{\lambda^2}. \label{n0-equ}
-      \end{align}
-      Inequality~(\ref{n0-equ}) is true because of the following two observations:
-      \begin{itemize}
-      \item for $n\geq 50$, we have $\frac{n}{3+\log(n)}\geq n^{0.5}$;
-      \item for $n\geq \frac{92.16\sigma^4}{\lambda^4}$, we have $n^{0.5}\geq {9.6\sigma^{2}}{\lambda^{2}}$.
-      \end{itemize}
-
-      Thus, we know our lemma is true.
-
-      \end{proof}
 
@@
 
-          Based on Lemma~\ref{n0-inequality}, for $n_{0}=\max\{50, \frac{92.16\sigma^2}{\lambda^2}\}$ and $n\geq n_{0}$, we have
+Based on Lemma~\ref{n0-inequality}, for $n_{0}=\max\{50,\frac{92.16\sigma^2}{\lambda^2}\}$ and $n\geq n_{0}$, we have
 \begin{align}
@@
 \end{align}
-
 \end{proof}
@@
 Before we start analyzing the cumulative regret, we first prove the following lemma which bounds the expected length of each round.
-
 \begin{lemma}
@@
 \end{lemma}
-
 \begin{proof}
@@
 
+Using the above lemmas, we are ready to prove Theorem~\ref{rst:budget}.
+We include the proof of Theorem~\ref{rst:budget} in the appendix.
+Below, we bound the expected number of payments for our algorithm.
 \begin{lemma}
@@
 Now we are ready to prove our second main result, Theorem~\ref{rst:regret}.
-
 \begin{proof}
@@
 
-                              Thus, the cumulative expected regret is bounded by $O(N^2 m + M m^2\log(T))$.
+Thus, the cumulative expected regret is bounded by $O(N^2 m + M m^2(\log(T))^2)$.
 \end{proof}
@@
 \label{sec:pi}
-
 In Algorithm~\ref{Alg1}, we use ``pay whatever it takes'' strategy when we decide to incentivize the agent.

### 2018-01-29 appendix.tex
did some minor edits to our paper

@@
+\section*{Proof of Lemma~\ref{n0-inequality}}
+
+\begin{proof}
+First, we observe that
+\begin{align}
+&\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)} \nonumber \\
+\iff &\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{9.6\sigma^2}{\lambda^2}. \nonumber 
+\end{align}
+Since $\log(x)\leq x-1$ for $x>0$, we know 
+\begin{align}
+\log(\log_{1.1}(n)+1)=\log\left(\frac{\log(n)}{\log(1.1)}+1\right)\leq \log(11\log(n)+1)\leq \log(11n)\leq 3+\log(n). \nonumber
+\end{align}
+
+Thus, we know
+\begin{align}
+\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{n}{3+\log(n)}. \nonumber 
+\end{align}
+
+To prove the lemma, we just need to show for $n\geq n_{0}$, we have
+\begin{align}
+\frac{n}{3+\log(n)}\geq \frac{9.6\sigma^2}{\lambda^2}. \label{n0-equ}
+\end{align}
+Inequality~(\ref{n0-equ}) is true because of the following two observations:
+\begin{itemize}
+\item for $n\geq 50$, we have $\frac{n}{3+\log(n)}\geq n^{0.5}$;
+\item for $n\geq \frac{92.16\sigma^4}{\lambda^4}$, we have $n^{0.5}\geq {9.6\sigma^{2}}{\lambda^{2}}$.
+\end{itemize}
+
+Thus, we know our lemma is true.
+
+\end{proof}
+
 \section*{Proof of Theorem~\ref{rst:budget}}
 
-We also need the following lemma in part of the proof of Theorem~\ref{rst:budget}.
+We need the following lemma in part of the proof of Theorem~\ref{rst:budget}.
 \begin{lemma}
@@
 Since $\bar{T}_{n}$ is independent of $\omega$, we know
-
 \begin{align}
@@
 \end{align}
-
 \noindent\textbf{Step 3: Rewrite the total payment expression}.
@@
 Define $S_{i,t}^{j}=\frac{N(i,t)\epsilon_{i,t}^{j}}{2\sigma}$, then we know $S_{i,t}^{j}$ is a summation of $1/2$ gaussian random numbers. Therefore,
-
 \begin{align}

### 2018-02-02 algorithm.tex
wrote intro and preliminaries

@@
 
-\subsection{Assumptions}
-In this section, we state several assumptions assumed by our analysis.  First define
-\begin{align}
-\Omega_{i,j}=\{\theta:B(\theta)=i, \hat{B}(\theta)=j\}, \nonumber 
-\end{align}
-which is the set of agent preferences whose best arm is arm $i$ and second best arm is arm $j$. With this definition, our analysis makes the following assumptions:
+\dkcomment{I moved the assumptions to an earlier section.
+I am saving here some text that was in that subsection.}
 
-\begin{assumption} Let $F_{i,j}(y)$ be the marginal cumulative density function (or cumulative mass function if $F(\cdot)$ is a discrete distribution) of $(u_i-u_j)\cdot\theta$ conditioned on $\theta \in \Omega_{i,j}$.
-We assume $F_{i,j}(y)\leq My$ for all $y\in R^{+}$, $\forall i,j$.
-\label{A1}
-\end{assumption}
+We use $R = \max_{\theta, i,j} \theta \cdot (u_i - u_j)$ to denote the
+maximum regret that can be incurred at each time.
+Assumption~\ref{A2} implies that the maximum regret or payment
+incurred in any one round is finite.
 
@@
 Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm.
-
-\begin{assumption} We assume $F$ has a compact support set. Without loss of generality, we assume $\theta\in [0,W]^m$.
-\label{A2}
-\end{assumption}
-
-We use $R = \max_{\theta, i,j} \theta \cdot (u_i - u_j)$ to denote the maximum regret that can be incurred at each time.  Assumption~\ref{A2} shows that $R<\infty$.
-
-\begin{assumption}
-Denote $p=\min_{i}P(\{\theta: B(\theta)=i\})$. We assume $p>0$.
-\label{A3}
-\end{assumption}
-
-Assumption~\ref{A3} means each arm $i$ has a strictly positive proportion of users for which that arm is best.
 

### 2018-02-02 introduction.tex
wrote intro and preliminaries

@@
 
-Here we pursue an alternate direction to our analysis of incentivizing exploration with heterogeneous preferences: we consider approximation-style results comparing achievable algorithm performance across four different problem settings, described in the table below.
+A large number of sites are designed to facilitate joint discovery,
+sharing, and recommendations of content by large numbers of users.
+Such sites include news, photo, or video sharing sites,
+sites to review restaurants, hotels, or travel experiences,
+online stores at which users write reviews (such as Amazon),
+and citizen science projects
+(such as eBird \citep{sullivan2009ebird} or Galaxy Zoo).
+\dkcomment{Insert citations.}
+By learning from the experiences of other users, individuals can make
+better choices to improve their own experience.
 
-\begin{center}
-\begin{tabular}{ c|c|c| } 
- \hline
-     & Pulls arms directly & Needs to incentivize \\ 
-\hline
- Perfect Info on Preferences & $C11$: The ``God'' Policy & $C12$ \\ 
- Partial Info on Preferences & $C21$ & $C22$: actual algorithm \\ 
- \hline
-\end{tabular}
-\end{center}
+Viewed more abstractly, the users are jointly exploring a space of
+many options (products, news stories, photos, birdwatching sites,
+patches of sky to train their telescopes on, $\ldots$),
+with the implicit goal of identifying the ``best'' ones.
+Therefore, such scenarios can be fruitfully modeled in a bandit
+learning framework.
+However, contrary to standard bandit settings, the utilities of the
+decision makers (the users) are not aligned with the overall utility.
+Societally (i.e., in a suitable aggregate over all users),
+it would be desirable to engage in considerable exploration of
+different options, so as to provide higher rewards for a large number
+of future users.
+However, individual users only interact with the site a limited number
+of times, and therefore have little incentive for exploration.
+A particular clean model is obtained when each user interacts with the
+site only once, and hence has no intrinsic utility for exploration. 
+This model has been the subject of prior work, and forms the basis of
+the present submission.
 
-Columns indicate whether the principal pulls arms directly (left column) or incentivizes agents who in turn actually pull the arms.
-Rows indicate whether the principal knows the preferences of the agents (top row) or not (bottom row).
-Problem settings correspond to cells and are described by the names C11, C12, and so on.
-An optimal algorithm for problem setting C11 has the best performance possible.
+In order to effect an outcome which is close to societally optimal,
+it is necessary to provide exploration incentives to the individual users.
+This was noted in two recent lines of work:
+\citet{kremer2014implementing}
+and \citet{mansour2015bayesian,mansour2016bayesian}
+assume that the site (also called the \emph{principal}) has an
+informational advantage in being the only one to observe the results
+of past arm pulls.
+(Such an assumption applies, for instance, to route recommendations in
+driving.)
+The principal can exploit this advantage and make recommendations to
+the individual agents which it is in their best interest to follow.
+\citet{frazier2014incentivizing} and 
+\citet{han2015incentivizing} instead assume that the results of all
+past arm pulls are publicly observable
+(such as reviews on an online retail site).
+They instead allow payments which the principal can offer to users as
+a reward for pulling particular arms.
+We follow the model of \citet{frazier2014incentivizing,han2015incentivizing}
+and consider a multi-armed bandit model in which the principal can
+offer payments to the users for pulling particular arms.
 
-We wish to make two high-level points through this analysis:
+Past work has assumed that users are homogeneous, i.e., the expected
+reward a user derives from an arm is the same for all users.%
+\footnote{\citet{han2015incentivizing} assume that users are
+heterogeneous in their tradeoff between utility derived from arm pulls
+and utility derived from the principal's payment.}
+In reality, users will have different preferences, e.g., gastronomic,
+political, aesthetic, practical, etc.,
+and the preferences can typically not be observed by the principal.
+This heterogeneity presents both a challenge and an opportunity.
+On the one hand, it necessitates the exploration of more arms,
+so as to let all users discover their best option.
+On the other hand, the heterogeneity also provides exploration
+``for free,'' as users will not simply herd on one ``best'' arm.
+\emph{Our goal is to explore the impact of user heterogeneity
+on the tradeoff between societal utility and the principal's payments.}
 
-\begin{itemize}
-\item First, better performance is possible in setting C22 than in setting C21, in the sense we can find tight approximation guarantees relative to C11 that are better for C22 than for C21.
-This is achieved by setting up incentives in C22 that still allow agents to select arms aligned with their preferences, providing selections of arms that contain more information than in C21.
-\item Second, heterogeneity in preferences improves performance over what can be achieved in a setting with homogeneous preferences.
-This would be in the spirit of David K.'s results that heterogeneity in preference for money can be exploited to reduce the budget required.
-\end{itemize}
+At a high level, we model the setting as follows.
+(Formal definitions are given in Section~\ref{sec:prob}.)
+Arms and users (or \emph{agents}) are characterized by payoff-relevant
+\emph{attribute} (or \emph{feature}) vectors,
+both drawn from known distributions.
+An agent's reward from pulling an arm is the inner product of their
+vectors (plus noise).
+When an arm is pulled, a noisy version of its attribute vector is
+observed by everyone.
+Agents are myopic and will pull the arm whose expected attribute
+vector (based on past noisy observations) maximizes their reward.
+The principal can incentivize agents to pull particular arms by
+offering rewards for the specific arm.
+The principal's goal is to keep the cumulative regret across all
+agents small, while incurring only small total payments.
+Our main theorm can be stated informally as follows:
 
-In this paper, we study incentivizing exploration with heterogeneous agent preferences.
-In this problem,   
-arms have unknown multivariate attributes, and agents have heterogeneous linear utility functions that map these attribute vectors onto utilities.
-Agents see noisy observations of attributes of arms pulled by all previous agents, and estimate an arms' attribute vector by the simple average of these observations.
-Agents are selfish, and pull the arm with the largest estimated utility summed with an optional arm-specific incentivizing payment chosen by the principle.
-We study strategies for choosing such incentive payments that seek to maximize the total utility derived by agents, subject to a limitation on the total incentive payment.
-To accomplish this goal, a strategy must induce sufficient exploration to reveal arms' attributes, while still letting agents select myopically and according to their preferences sufficiently often that high-utility arms are chosen and incentive payments are kept small.
+\begin{theorem} \label{thm:main-intro}
+Assume that for each arm, at least a constant fraction of the
+population likes this arm best.
+If furthermore, the density of ties in agent preferences between arms
+vanishes (in a sense made precise in Section~\ref{sec:ub}),
+there is a policy that achieves constant
+expected regret $C$ and constant%
+\footnote{The constants $C,C'$ depend on the number of arms and the
+  smallest fraction preferring any one arm.} expected payment $C'$.
+If near-ties have non-zero density,
+then the regret is bounded by $O(C + C'' \log^2(T))$,
+while the expected payment is still bounded by $C'$;
+here, $C''$ depends on the ``tie density.''
+\end{theorem}
 
-Our problem setting models online review aggregators like Amazon, Yelp, and Tripadvisor that host crowdsourced reviews.
-Users of these websites wish to use the reviews hosted there to choose the product / restaurant / vacation (generically referred to as an ``item'') that is best according to their preferences.
-These reviews provide not just cardinal feedback, but also a description of items' attributes that a user may consider together with their personal preferences to select their preferred item.
-An item with few reviews might have inaccurate attribute estimates, leading users to avoid it even though it may actually be their best choice.
-Without incentives, this situation may persist and decrease welfare for the platform's user base.
-By offering incentives, either through price reductions by Amazon or coupons from Yelp or Tripadvisor, a platform may induce more reviews of unexplored items and provide more value over the long term.
+The policy achieving the result of Theorem~\ref{thm:main-intro} is
+quite simple: it mostly lets agents exploit arms, but incentivizes
+them to explore when arms that appear close enough to being tied are
+underexplored. It is presented in detail in Section~\ref{sec:ub}.
+The result can be smoothly extended when there some arms that are not
+preferred by any agents.
 
-Our problem setting also applies to crowd science platforms like eBird \cite{frazier2014incentivizing, sullivan2009ebird}.
-EBird guides birding enthusiasts through a website to explore and report their findings to the birding community.
-Each user report contains information about when, where and how they go birding and what birds they see and hear.
-EBird may wish to incentivize enthusiasts to explore less-explored birding locations and provide more accurate reports on these locations.
-Each enthusiast may have different preference over a location's attributes such as the diversity of bird species, weather, distance and safety.
-By offering enthusiasts incentivies to explore, eBird can create a more accurate body of reports and provide better value to the birding community.
-
-% Something interesting to study would be to alter the search rankings to influence people
-% Also which items to spam people about reviewing
-
-In this problem context, we study a simple policy that usually exploits, incentivizing agents to pull an arm only when the set of agent utility functions that would pull this arm without incentives has probability below a time-varying threshold.
-In our paper, we assume all arms are some agents' best arm.
-Under this assumption, we prove that with $O(N^2)$ payment budget, this policy has $O(N^2+M(\log(T))^2)$ cumulative expected regret where $M$ is an upper bound on the limiting marginal probability density of agent utilities that are nearly indifferent between their best and the second best arm.
-If all agents' utility difference between their best and second best arm is bounded below by a positive number, which typically happens when the agent utility distribution is discrete, this policy achieve constant cumulative expected regret $O(N^2)$.
-The key difference between our problem setting and both the homogenous preference setting and the traditional multi-armed bandits setting is that we must incentivize agents to try suboptimal arms much less often, since all arms are some agents' best arm.
-Essentially, heterogeneity provides free exploration.
-These results suggest that heterogeneous agent preferences reduce but do not eliminate the need to incentive exploration, in relation to single-preference settings.
-
-We broadly categorize the relevant previous literature into two categories based on whether there is money transfer.
-With money transfer, \cite{frazier2014incentivizing} considers a problem setting where the principal pays agents money to explore.
-This work assumes all agents have equal value for money and provide a complete characterization of achievable reward with a fixed budget.
-\cite{han2015incentivizing} generalizes this framework to include agents with heterogeneous value for money, and to allow an external signal to provide partial information about this valuation.
-Under this setting, this work proves a bound on achievable reward as a function of the budget and the signal scheme.
-
-Without money transfer but using information asymmetry, \cite{kremer2014implementing} considers a simple model where agents arrive to the principal one by one and there are only two actions at each time.
-\cite{mansour2015bayesian} generalizes \cite{kremer2014implementing} by allowing a finite number of actions at each time.
-\cite{mansour2016bayesian} considers a problem setting where there are multiple agents at each time and agents may interact with each other.
-In these papers, the principal provides each agent a recommendation at each time that is Bayesian incentive-compatible.
-They prove the principal can achieve constant regret when utilities are deterministic and logarithmic regret when utilities are stochastic.
-
-We structure our paper as follows: Section~\ref{sec:prob} formulates our problem; Section~\ref{sec:ub} states our algorithm and proves that we can achieve $O(N^2+M(\log(T))^2)$ regret with $O(N^2)$ incentive budget; Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
+\dkcomment{I strongly dislike the ``Table of contents'' paragraph, and
+  much prefer weaving pointers into the main text.}

### 2018-02-02 problem_setting.tex
wrote intro and preliminaries

@@
-\section{Problem Setting}
+\section{Preliminaries}
 \label{sec:prob}
 
-We have $N$ arms. Arm $i$ has a fixed but unknown attribute vector $u_i\in \mathbb{R}^{m}$. 
-A stream of myopic selfish agents come to our system.
-Agent $t$ has linear preferences over attributes described by a vector $\theta_t \in \mathbb{R}^m$ that is unknown to the principal and drawn i.i.d.
-from a known distribution $F(\cdot)$ with compact support.
-We refer synonomously to an agent and that agent's preference vector: when we say ``an agent $\theta$'', we mean ``an agent with preference vector $\theta$.''
+We consider a MAB setting with \ARMNUM arms.
+Arm payoffs are determined by $d$ \emph{attributes} or \emph{features};
+hence, arms can be identified with vectors $\ArmV{i} \in \R^d$.
+The \ArmV{i} are (adversarially) fixed, but unknown to the agents
+or the principal.
+Whenever arm $i$ is pulled, its current utility-relevant features are
+determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero
+Gaussian%
+\footnote{For simplicity of notation, we assume that the variance
+  $\sigma^2$ is uniform across time steps. This is not material for
+  the analysis.}
+noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.
+\dkcomment{Clarify if we can handle more general noise.}
+Here, $I_d$ denotes the $d \times d$ identity matrix.
 
-Each agent $t$ chooses an arm to pull $A_t$, according to a process described below, and obtains utility $\theta_t \cdot u_{A_{t}}$.
-The principal and all agents then see a noisy observation of the attribute vector of the pulled arm of the form $O_t=u_{A_{t}}+\epsilon_{t}$, where $\epsilon_t\sim N(0, \sigma^2 I_{m})$ is independent normally distributed noise, and $I_m$ denotes an $m$-dimensional identity matrix.
-Although we assume a common variance across attributes for simplicity of presentation, our theoretical results hold if the variance differs.
+At each time $t$, a new user (or \emph{agent}) arrives,
+whose feature vector (which we also call his%
+\footnote{We use male pronouns to refer to users and female pronouns
+  to refer to the principal. 
+  \dkcomment{Feel free to switch if you prefer it the other way.}}
+\emph{type}) $\AgentV{t} \in \R^d$ is drawn from a known distribution
+\AgentDist.
+Depending on context, we will identify a agents with their arrival time
+$t$ or their type \AgentV{t}.
+When agent $t$ pulls arm $\Pull{t} := i$,
+he and all future agents observe a vector
+$\ObsV{t} = \ArmV{i} + \NoiseV[t]$ for arm $i$,
+and his reward is $\AgentV{t} \cdot \ObsV{t}$,
+i.e., agents have linear preferences.
 
-At each time $t$, for each arm $i$, we (the principal) offer a non-negative payment $c_{i,t}\geq 0$ based on previous observations.
-We assume that agent $t$ chooses to pull the arm that myopically maximizes the sum of this payment and an estimate of the utility obtained $\theta_t \cdot u_{i,t}$ where $u_{i,t}$ denotes the simple average of $O_s$ over all previous pulls of arm $i$.
-In this paper, we assume all arms have been pulled once at time $t=0$ and $u_{i,0}$ denotes a random draw from the arm attribute vector.
-For $t>0$, denote $u_{i,t} = \frac{\sum_{s<t} O_s 1\{A_s = i\} + u_{i,0}}{\sum_{s<t} 1\{A_s = i\}+1}$ and $A_t=\argmax_{i}\{\theta_t\cdot u_{i,t}+c_{i,t}\}$, breaking ties in favor of the arm with the highest incentive.
-We use $c_t=c_{A_{t},t}$ to denote the actual incentive payment at time $t$.
+For each time $t$ and arm $i$, let \NumPull{t}{i} be the number of
+times that arm $i$ has been pulled (strictly) before time $t$.
+An agent at time $t$ estimates arm $i$'s attribute vector as the
+average of vectors observed during past pulls of the arm:
+$\ArmEV{t}{i} = \frac{1}{\NumPull{t}{i}+1} \cdot
+(\ArmEV{0}{i} + \sum_{t'<t: \Pull{t'} = i} \ObsV{t'})$;
+here, \ArmEV{i}{0} is a single draw $\ArmV{i} + \NoiseV$ for arm $i$.
+(In other words, we assume that each arm is pulled once for free at time 0.)
 
-This behavior may be recovered if agents are Bayesian and share a common non-informative prior distribution that is constant over $\mathbb{R}^m$ and know $\sigma^2$.
-In this case, the posterior distribution on $u_{i}$ at time $t$ is multivariate normal with mean $u_{i,t}$, and the expected value of $\theta_t \cdot u_i$ under this posterior conditioned on $\theta_t$ is $\theta_t \cdot u_{i,t}$ (see equation $2.13$ in section $2.5$, \cite{Ge04}).
-Alternatively, one may simply take our assumption that agents use the average as their estimate of an attribute value directly without such a Bayesian justification.
+Since each user only pulls an arm once, users are \emph{myopic}:
+in the absence of incentives, user $t$ will pull an arm from
+$\argmax_i \AgentV{t} \cdot \ArmEV{t}{i}$.
+To incentivize users to explore more, the principal can offer
+\emph{payments} $\Pay{t}{i}$ to user $t$ for pulling arm $i$.
+Then, user $t$ will pull an\footnote{We assume that ties are broken in
+  favor of an arm with largest payment \Pay{t}{i}; this assumption is
+  only for notational convenience, and can of course be avoided by
+  raising payments infinitesimally.} arm $i$ maximizing
+$\argmax_i (\Pay{t}{i} + \AgentV{t} \cdot \ArmEV{t}{i})$.
+The principal cannot observe \AgentV{t},
+and only knows the distribution \AgentDist from which it is drawn.
+Her goal is to achieve a good tradeoff between the cumulative
+\emph{regret} experienced by all users up to time $T$,
+and the total \emph{payment} she makes to the users.
 
-We define the regret at time $t$ as $r(t)=\max_{i}\{\theta_{t}\cdot u_{i}\}-\theta_t\cdot u_{A_t}$, and the cumulative regret up to time T as $R(T)=\sum_{t=1}^{T}r(t)$.
-Define the cumulative payment up to time T similarly as $C(t)=\sum_{t=1}^{T}c(t)$.
-As the principal, we want to find a strategy $\mathcal{A}$ under which both the cumulative expected regret $\mathbb{E}_{\mathcal{A}}[R(T)]$ and the cumulative expected payment $\mathbb{E}_{\mathcal{A}}[C(T)]$ are small.
+We define the regret at time $t$ as
+$\Regret{t} = (\max_{i} \AgentV{t} \cdot \ArmV{i}) - \AgentV{t} \cdot \ArmV{\Pull{t}}$,
+and the cumulative regret up to time $T$ as
+$\TotalRegret{T} = \sum_{t=1}^{T} \Regret{t}$.
+Similarly, $\PayA{t} = \Pay{t}{\Pull{t}}$ is the actual incentive
+payment at time $t$,
+and the cumulative payment up to time $T$ is
+$\TotalPay{T} = \sum_{t=1}^{T} \PayA{t}$.
+More formally, the principal's goal is to find a policy
+\POLICY for offering payments under which both the cumulative expected
+regret
+$\Expect[\POLICY]{\TotalRegret{T}}$ the cumulative expected payment
+$\Expect[\POLICY]{\TotalPay{T}}$ are small.
 
-To support later development, we define some additional notation.
-We let $B(\theta)$ and $\hat{B}(\theta)$ refer to the index of the arm that is best and second best for an agent with preference vector $\theta$, $B(\theta) \in \argmax_i \theta \cdot u_i$ and $\hat{B}(\theta)=\argmax_{i\neq B(\theta)}\theta\cdot u_{i}$, breaking ties uniformly at random.
-We let $N(i,t)$ denote the number of pulls of arm $i$ at times up to and including $t$ plus $1$ (because of the initial pull), i.e.
-$N(i,t)=\sum_{s<t} 1\{A_s = i\}+1$.
-We call time $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$ the {\it starting point of the $n^{th}$ round}. We call the set of times $[t_{n}, t_{n+1})$ the {\it $n^{th}$ round}.
+To support the formulation of our results and the analysis,
+we define the following additional notation.
+We let
+$\Best{\AgentV{}} \in \argmax_i \AgentV{} \cdot \ArmV{i}$
+and
+$ \Second{\AgentV{}} \in \argmax_{i \neq \Best{\AgentV{}}} \AgentV{} \cdot \ArmV{i}$
+denote the (indices of) the best and second-best arms for an agent
+with attribute vector \AgentV{};
+\dkdelete{breaking ties uniformly at random}.
+\dkcomment{What would it mean to break ties at random in a
+  definition?}
+
+\dkcomment{Do we need this definition here?}
+We call time $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$ the
+\emph{starting point of the $n^{th}$ round}.
+We call the set of times $[t_{n}, t_{n+1})$ the
+\emph{$n^{th}$ round}.
+
+\dkdelete{This behavior may be recovered if agents are Bayesian and
+  share a common non-informative prior distribution that is constant
+  over $\mathbb{R}^m$ and know $\sigma^2$.  In this case, the
+  posterior distribution on $u_{i}$ at time $t$ is multivariate normal
+  with mean $u_{i,t}$, and the expected value of $\theta_t \cdot u_i$
+  under this posterior conditioned on $\theta_t$ is $\theta_t \cdot
+  u_{i,t}$ (see Equation 2.13 in Section 2.5, \cite{Ge04}).
+  Alternatively, one may simply take our assumption that agents use
+  the average as their estimate of an attribute value directly without
+  such a Bayesian justification.}
+\dkcomment{I wonder what's the best way to discuss this.}
+
+\subsection{Properties of \AgentDist}
+Our algorithms rely on a few assumptions about the agent distribution
+\AgentDist.
+
+\begin{assumption}[Compact Support] \label{A2}
+\AgentDist has a compact support set contained in $[0,\Diam]^d$.
+\end{assumption}
+
+Let $\MinProb = \min_{i} \Prob[\AgentDist]{\Set{\AgentV{}}{\Best{\AgentV{}} = i}}$
+denote the minimum (over all arms) fraction of users that prefer any
+particular arm.
+
+\begin{assumption}[Every arm is someone's best] \label{A3}
+Each arm $i$ has a strictly positive proportion of users for whom $i$
+is the best arm; that is, $\MinProb > 0$.
+\end{assumption}
+
+Let 
+\begin{align*}
+\FirstTwo{i}{i'}
+  & = \Set{\AgentV{}}{\Best{\AgentV{}} = i, \Second{\AgentV{}} = i'}
+\end{align*}
+be the set of agent attribute vectors whose best arm is $i$ and
+second-best arm is $i'$.
+Let $F_{i,i'}$ be the marginal cumulative density function
+(or cumulative mass function if $\AgentDist(\cdot)$ is a discrete distribution)
+of $(\ArmV{i}-\ArmV{i'}) \cdot AgentV{}$,
+conditioned on $\theta \in \Omega_{i,j}$.
+In words, $F_{i,i'}$ is the distribution of the \emph{strength} of the
+preference of a random agent for arm $i$ over arm $i'$, given that
+$i$ and $i'$ are the agent's first and second choices.
+
+\begin{assumption}[Not too many near-ties] \label{A1}
+Near-ties have vanishing probability; 
+that is, there exists a constant \TieDensity such that
+for all pairs $i,i$ of arms and all $z \in \R^+$,
+we have $F_{i,i'}(z) \leq \TieDensity \cdot z$.
+\end{assumption}

### 2018-02-02 result_discussion.tex
wrote intro and preliminaries

\section{Problem Setup and Overview of Results}
\dkcomment{I envision this section doing the following:
\begin{enumerate}
\item State the main theorem(s) formally.
\item Discuss lower bounds or impossibility results.
\item Discuss extensions.
\item Discuss the justification or comparison to standard bandits.
\item Discuss the comparison in the 2x2 square.
\end{enumerate}
}

\dkcomment{For now, I am just copying over material from various other
  parts that Bangrui/Peter wrote or I had written in earlier
  iterations.}

\begin{theorem} \label{thm:main-intro}
Under some technical assumptions, 
there exists a policy which pays at most $O(\ARMNUM^2)$ in expectation,
and achieves regret at most $O(\ARMNUM^2 + \log^2(T))$.
\dkcomment{Omitting the density here.}
\end{theorem}

As we discuss in more detail in Section~\ref{sec:main-discussion},
the reason we obtain stronger regret bounds than in the standard bandit
setting is that the agents' heterogeneity in preferences will
naturally lead to exploration.

Here we pursue an alternate direction to our analysis of incentivizing exploration with heterogeneous preferences: we consider approximation-style results comparing achievable algorithm performance across four different problem settings, described in the table below.

\begin{center}
\begin{tabular}{ c|c|c| } 
 \hline
     & Pulls arms directly & Needs to incentivize \\ 
\hline
 Perfect Info on Preferences & $C11$: The ``God'' Policy & $C12$ \\ 
 Partial Info on Preferences & $C21$ & $C22$: actual algorithm \\ 
 \hline
\end{tabular}
\end{center}

Columns indicate whether the principal pulls arms directly (left column) or incentivizes agents who in turn actually pull the arms. Rows indicate whether the principal knows the preferences of the agents (top row) or not (bottom row).   Problem settings correspond to cells and are described by the names C11, C12, and so on. An optimal algorithm for problem setting C11 has the best performance possible.

We wish to make two high-level points through this analysis:

\begin{itemize}
\item First, better performance is possible in setting C22 than in setting C21, in the sense we can find tight approximation guarantees relative to C11 that are better for C22 than for C21.  This is achieved by setting up incentives in C22 that still allow agents to select arms aligned with their preferences, providing selections of arms that contain more information than in C21.
\item Second, heterogeneity in preferences improves performance over what can be achieved in a setting with homogeneous preferences.  This would be in the spirit of David K.'s results that heterogeneity in preference for money can be exploited to reduce the budget required.
\end{itemize}

Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.

### 2018-02-05 appendix.tex
editted the payment proof

@@
 \begin{align}
-0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}. \nonumber
+5n^{3/5} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}. \nonumber
 \end{align}
@@
 \begin{align}
-&0.9n^{5/6} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)} \nonumber \\
-\iff & 0.81 n^{5/3} \geq 0.6n \log(\log_{1.1}(n)+1) \nonumber \\
-\iff &  \frac{81}{60} n^{2/3} \geq  \log(\log_{1.1}(n)+1) \nonumber
+&5 n^{3/5} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)} \nonumber \\
+\Longleftarrow &  25 n^{6/5} \geq n \log(\log_{1.1}(n)+1) \nonumber  \\
+\Longleftarrow &  25 n^{1/5} \geq \log(\log_{1.1}(n)+1) \nonumber \\
+\Longleftarrow &  25 n^{1/5} \geq \log_{1.1}(n)+1. \nonumber 
 \end{align}
 
-Denote $f(x) = \frac{81}{60}x^{2/3} - \log(\log_{1.1}(x)+1)$.
-It's easy to compute $f^{'}(x)=0$ has a unique solution $x_{0}=e^{2/3w(\frac{20e^{20000/314763}}{27})-\frac{10000}{104921}}$ (here $w(\cdot)$ is the Lambert W-Function) and it is the global minimum.
-Since $f(x_{0})\approx 0.0252 >0$, we know $f(x)>0$ for all $x\geq 1$.
-Thus, our lemma holds true.
+Denote $f(x) = 25x^{1/5} - \log_{1.1}(x)-1$. Set it's first derivate to $0$, we get its global mimumum at $x_0=\frac{161051}{3125}$ and $f(x_0)> 0$. Thus, our Lemma holds true.
+
 \end{proof}
@@
 
-Set $g(n,\ell)$ to be $\frac{2\sigma \ell}{n^{1/6}}$.
+Set $g(n,\ell)$ to be $\frac{12\sigma \ell}{n^{2/5}}$.
 Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2Wm\lambda\}$, they will correctly identify their best arm.
-Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{2\sigma l}{n^{1/6}} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
+Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{12\sigma l}{n^{2/5}} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
 Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms.
-Denote $a_0=\frac{4Wm\sigma}{p^{-1}(\frac{p}{2})}$.
-In order to have $\frac{2\sigma l}{n^{1/6}}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil (a_{0} l)^6 \rceil$.
+Denote $a_0=\frac{24Wm\sigma}{p^{-1}(\frac{p}{2})}$.
+In order to have $\frac{12\sigma l}{n^{2/5}}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil (a_{0} l)^\frac{5}{2} \rceil$.
 In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
 Denote $n_2=\frac{2}{p}$.
-Thus, we know we can only incur regret for sample paths $\omega$ in the $\ell^{th}$ envelope in the first $\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}$ rounds.
+Thus, we know we can only incur regret for sample paths $\omega$ in the $\ell^{th}$ envelope in the first $\max\{n_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}$ rounds.
 
@@
 \begin{align}
-\sum_{t=1}^{\infty}c(t)\leq\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\bar{c}(n,\ell)\mathbbm{1}\{\omega\in L[\ell]\}\bar{T}_{n}. \nonumber
+\sum_{t=1}^{\infty}c(t)\leq\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(n,\ell)\mathbbm{1}\{\omega\in L[\ell]\}\bar{T}_{n}. \nonumber
 \end{align}
@@
 &E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
-\leq &\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\bar{c}(n,\omega)P(\omega \in L(\ell))E[\bar{T}_{n}] \nonumber \\
-=&\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+2Wm\frac{2\sigma \ell}{n^{1/6}}\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
-\leq &\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma l\right]P(\omega\in L[\ell])E[\bar{T}_{n}]. \nonumber
+\leq &\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(n,\omega)P(\omega \in L(\ell))E[\bar{T}_{n}] \nonumber \\
+=&\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[R+2Wm\frac{12\sigma \ell}{n^{2/5}}\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
+\leq &\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[R+24Wm\sigma l\right]P(\omega\in L[\ell])E[\bar{T}_{n}]. \nonumber
 \end{align}
@@
 =&P(\omega\in L^{'}[\ell])- P(\omega\in L^{'}[\ell-1]) \nonumber \\
-\leq & 1-P\left(|\epsilon_{i,t}^{j}|<\frac{2\sigma (\ell-1)}{n^{1/6}}, \forall i,j\right) \nonumber \\
-=&P\left(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{2\sigma (\ell-1)}{n^{1/6}}\right) \nonumber  \\
-\leq &\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma (\ell-1)}{n^{1/6}}\right) \nonumber
+\leq & 1-P\left(|\epsilon_{i,t}^{j}|<\frac{12\sigma (\ell-1)}{n^{2/5}}, \forall i,j\right) \nonumber \\
+=&P\left(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{12\sigma (\ell-1)}{n^{2/5}}\right) \nonumber  \\
+\leq &\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{12\sigma (\ell-1)}{n^{2/5}}\right) \nonumber
 \end{align}
@@
 \begin{align}
-&\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{2\sigma(\ell-1)}{n^{1/6}}\right) \nonumber \\ 
-=&\sum_{i,j}P\left(|S_{i,t}^{j}|\geq \frac{N(i,t)(\ell-1)}{n^{1/6}}\right) \nonumber \\
-\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(\ell-1)). \nonumber
+&\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{12\sigma(\ell-1)}{n^{2/5}}\right) \nonumber \\ 
+=&\sum_{i,j}P\left(|S_{i,t}^{j}|\geq \frac{6N(i,t)(\ell-1)}{n^{2/5}}\right) \nonumber \\
+\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq 6N(i,t)^{3/5}(\ell-1)). \nonumber
 \end{align}
@@
 \begin{align}
-&N(i,t)^{5/6}(\ell-1) \nonumber \\
-=& 0.9N(i,t)^{5/6} + N(i,t)^{5/6}(\ell-1.9) \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)} + \sqrt{(\ell-1.9)^2 N(i,t)} \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+(\ell-1.9)^2 N(i,t)}. \nonumber
+&6N(i,t)^{3/5}(\ell-1) \nonumber \\
+=& 5N(i,t)^{3/5} + N(i,t)^{3/5}(\ell-1) \nonumber \\
+\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)} + \sqrt{(\ell-1)^2 N(i,t)} \nonumber \\
+\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+(\ell-1)^2 N(i,t)}. \nonumber
 \end{align}
@@
 & P(\omega\in L(\ell) \nonumber \\
-\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq N(i,t)^{5/6}(\ell-1)) \nonumber \\
-\leq & \sum_{i,j}24e^{-1.8(\ell-1.9)^2} = 24Nme^{-1.8(\ell-1.9)^2}. \nonumber
+\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq 6N(i,t)^{3/5}(\ell-1)) \nonumber \\
+\leq & \sum_{i,j}24e^{-1.8(\ell-1)^2} = 24Nme^{-1.8(\ell-1)^2}. \nonumber
 \end{align}
@@
 &\sum_{t=1}^{\infty}c(t) \nonumber \\
-\leq&\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
-\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]P(\omega\in L[1])E[\bar{T}_{n}] +\sum_{l=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
-\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]E[\bar{T}_{n}] +\sum_{\ell=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]24Nme^{-1.8(\ell-1.9)^2}E[\bar{T}_{n}]\nonumber \\
-\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^6 \rceil\}}\left[R+4Wm\sigma \right]Nn +\sum_{\ell=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^6 \rceil\}}\left[R+4Wm\sigma \ell\right]24Nme^{-1.8(\ell-1.9)^2}Nn \nonumber \\
-\leq & \left[R+4Wm\sigma \right]N (\max\{n_2,\lceil (a_0)^6 \rceil\})^2+\sum_{\ell=2}^{\infty}24N^2 m[R+4Wm\ell\sigma](\max\{n_2,\lceil (a_0 \ell)^6 \rceil\})^2 e^{-1.8(\ell-1.9)^2} \nonumber \\
-=& O(N^2). \nonumber
+\leq&\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[R+24Wm\sigma \ell\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
+\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24Wm\sigma \right]P(\omega\in L[1])E[\bar{T}_{n}] +\sum_{l=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[R+24Wm\sigma \ell\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
+\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24Wm\sigma \right]E[\bar{T}_{n}] +\sum_{\ell=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[R+24Wm\sigma \ell\right]24Nme^{-1.8(\ell-1.9)^2}E[\bar{T}_{n}]\nonumber \\
+\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24Wm\sigma \right]Nn +\sum_{\ell=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[R+24Wm\sigma \ell\right]24Nme^{-1.8(\ell-1.9)^2}Nn \nonumber \\
+\leq & \left[R+24Wm\sigma \right]N (\max\{n_2,\lceil (a_0)^{5/2} \rceil\})^2+\sum_{\ell=2}^{\infty}24N^2 m[R+24Wm\ell\sigma](\max\{n_2,\lceil (a_0 \ell)^{5/2} \rceil\})^2 e^{-1.8(\ell-1.9)^2} \nonumber \\
+=& O(\frac{N}{p^5}+ \frac{N^2}{p^5}). \nonumber
 \end{align}

### 2018-02-05 algorithm.tex
significant edits to algorithm section

@@
-\section{Algorithm and Upper Bound}
+% move to colt.tex eventually
+
+\newcommand{\e}{\mathrm{e}}
+\providecommand{\Kth}[1]{\ensuremath{{#1}^{\rm th}}}
+
+\def\QED{{\phantom{x}} \hfill \ensuremath{\rule{1.3ex}{1.3ex}}}
+
+\newcommand{\extraproof}[1]{\rm \trivlist \item[\hskip \labelsep{\bf Proof of #1. }]}
+\def\endextraproof{\QED \endtrivlist}
+
+\def\emptyproof{\rm \trivlist \item[\hskip \labelsep{\bf Proof. }]}
+\def\endemptyproof{\endtrivlist}
+
+\section{Main Algorithm and Analysis}
 \label{sec:ub}
 
-In this section, we propose a simple policy that mostly exploits, and occasionally incentivizes exploration when the probability of an arm would be pulled by all agent types below a time-varying threshold given the current posterior.
-We prove that with the help of heterogeneous preferences, we can get a certain amount of exploration for free via heterogeneity.
+The algorithm achieving the claimed bounds of
+Theorem~\ref{thm:main-overview} is fairly simple.
+It mostly allows agents to exploits, but when an arm is estimated to
+be extremely unlikely to be pulled by any agents,
+the algorithm incentivizes such an arm with a payment that is so high
+that the next agent is guaranteed to pull the arm.
+This way, the algorithm ensures that each arm is pulled at least a
+certain minimum number of times.
 
-\subsection{Our Algorithm}
-Our algorithm incentivizes pulling an arm $i$ at a time $t$ in round $n$ if and only if both of the following criteria are met:
+More precisely, the algorithm divides time into \emph{phases}
+$s = 1, 2, 3, \ldots$.
+Phase $s$ ends when each arm has been pulled at least $s$ times.
+An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
+if both of the following hold:
+
 \begin{itemize}
-\item the probability of pulling arm $i$ would be below $n^{-1}$ without incentives; 
-\item arm $i$ has not been played previously in the current round.
+\item $i$ has been pulled at most%
+\footnote{in fact: exactly, since the algorithm entered phase $s$}
+$s-1$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s-1$.
+\item Based on the current estimates \ArmEV{t}{i'} of all arms'
+attribute vectors, the probability of pulling arm $i$ is less than $1/s$.
+Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
+  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
+be the probability that arm $i$ will be pulled
+by the next (random) agent based on the current estimates. 
+Then, the second criterion for payment-eligibility is that
+$\PullProb{t}{i} < 1/s$.
 \end{itemize}
-Ties are broken randomly.  This algorithm does not need to know the horizon $T$ in advance.
 
-If our algorithm decides to incentivize an arm $i$, it uses the ``pay whatever it takes'' strategy in which the payment offered is $\max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$.
-This maximum over $\theta$ is taken over the support of $F$, which we recall is assumed compact.
-(We use this ``pay whatever it takes'' strategy for its simplicity, and in Section~\ref{sec:pi} we provide an alternate and smaller incentive payment that achieves the same payment budget bound and regret bound).
+When multiple arms are payment-eligible, the algorithm picks one
+uniformly at random to incentivize.
+When the algorithm decides to incentivize an arm $i$,
+it offers ``whatever it takes,'' i.e., offers a payment of
+$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$.
+The maximum for \AgV is taken over the support of \AgentDist;
+recall that we assumed this support to be compact.
+The payment \Pay{t}{i} may appear unnecessarily high.
+Indeed, we show in Section~\ref{sec:pi} that it suffices to
+incentivize only a $1/s$ fraction of the agents.
+\dkcomment{Given that we don't prove anything there, is ``show'' the
+  right word?}
+Here, we focus on the higher payments for simplicity of analysis.
 
-We describe our algorithm in detail as follows:
+Notice that \PullProb{t}{i} depends on the estimates for \emph{all}
+arms; thus, by pulling some other arm $i'$, an arm $i$ may become
+payment-eligible, or cease to be so.
+Algorithm~\ref{alg:basic-incentivizing} gives the full details.
 
 \begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration}
-\label{Alg1}
+\caption{Algorithm: Incentivizing Exploration \label{alg:basic-incentivizing}}
 \begin{algorithmic}
-\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
-\FOR{ $t = 1, 2, 3, \cdots$}{
-  \STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
-    \IF {$S\setminus V$ is non-empty}
-  \STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
-  \STATE{Pay whatever it takes to incentivize pulling arm $i$, i.e., offer payment 
-    $c_{i,t} = \max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$ and $c_{j,t} = 0$ for $j \ne i$.}
+\STATE Set the current phase number $s = 1$.
+\FOR{time steps $t = 1, 2, 3, \ldots$}
+\IF{$\NumPull{t}{i} \geq s$ for all arms $i$}
+\STATE Increment the phase $s = s + 1$.
+\ENDIF
+\IF{there is a payment-eligible arm $i$}
+\STATE Let $i$ be a uniformly random payment-eligible arm.
+\STATE Offer payment
+$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$
+for pulling arm $i$
+(and payment 0 for all other arms).
 \ELSE
-    \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
+\STATE Let agent $t$ play myopically, i.e., offer payments 0 for all arms.
 \ENDIF
-    \STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
-    \IF {$n\neq \min_{i}N(i,t)$} 
-  \STATE $V=\emptyset$
-    \ENDIF
-    \STATE Update the round number, $n = \min_{i} N(i,t)$
-}\ENDFOR
-
+\ENDFOR
 \end{algorithmic}
 \end{algorithm}
+
+The high-level idea of the proof of Theorem~\ref{thm:main-overview}
+is the following.
+Because the algorithm ensures that each arm is pulled
+``frequently enough,''
+the estimates \ArmEV{t}{i} become exponentially more accurate in the
+phase number $s$.
+Thus, the fraction of agents who misidentify their best arm decreases
+exponentially as well.
+Because for each arm, enough agents have a true preference for this
+arm, once the arms' attribute vectors are learned well enough,
+the algorithm will not need to incentivize any arm pulls any more,
+resulting in a payment bound independent of $T$.
+Similarly, the regret will decrease exponentially, and mostly accrue
+due to agents close to the border making mistakes in their arm choices.
+The detailed analysis following this outline is somewhat subtle, though,
+due to the dependencies between the agents' arm pulls and the
+estimates which in turn are based on past arm pulls.
+We begin with several technical lemmas that are used for both the
+payment and regret bounds.
+
+To capture the probability masses of problematic and non-problematic
+agents, we define the following:
+$\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
+\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
+is the total probability mass (across all arms) of agents
+whose (actual) preference for their best arm over their second-best
+arm is at most $\delta$.
+The minimum probability mass of users who prefer their best arm
+sufficiently strongly over their second-best arm is denoted by
+$\ClearPref{\delta} = \min_{i}
+\Prob[\AgV \sim \AgentDist]{\Best{\AgV}=i,%
+\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > \delta}$.
+Notice that while \AlmostTied{\delta} (being a measure of problematic
+agents) is defined as a sum over all arms,
+while  \ClearPref{\delta} (being a measure of non-problematic agents)
+is defined as a minimum over arms.
+Also notice that $\ClearPref{0} = \MinProb$.
+\dkcomment{We should stress somewhere that we assume that actual ties
+  have measure 0.}
 
@@
 
-We use $R = \max_{\theta, i,j} \theta \cdot (u_i - u_j)$ to denote the
+We use $R = \max_{\AgV, i,j} \AgV \cdot (u_i - u_j)$ to denote the
 maximum regret that can be incurred at each time.
@@
 
-\subsection{General Results}
-
-In this section, we prove Algorithm~\ref{Alg1} achieves $O(N^2+M(\log(T))^2)$ cumulative regret with $O(N^2)$ payment budget.
+In this section, we prove Algorithm~\ref{alg:basic-incentivizing} achieves $O(\ARMNUM^2+\TieDensity(\log(T))^2)$ cumulative regret with $O(\ARMNUM^2)$ payment budget.
 This is stated in the following pair of theorems, which together constitute our main results.
@@
 \begin{theorem}
-The payment budget for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$. 
+The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by $O(\ARMNUM^2)$. 
 \label{rst:budget}
@@
 \begin{theorem}
-The cumulative regret for Algorithm~\ref{Alg1} is bounded above by $O(N^2 m + M m^2(\log(T))^2)$.
+The cumulative regret for Algorithm~\ref{alg:basic-incentivizing}
+is bounded above by $O(\ARMNUM^2 d + \TieDensity d^2(\log(T))^2)$.
 \label{rst:regret}
 \end{theorem}
-
-Before we prove these two theorems, we must first introduce two additional pieces of notation, which will be used in preliminary lemmas.
-Let $S(\delta)$ be the proportion of users whose utility difference between their best and second best arm is less than $\delta$.
-Formally, $S(\delta)=P(\theta: \theta \cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}\leq \delta)$.
-Then, let $p(\delta)=\min_{i}P(\{\theta:B(\theta)=i,\theta\cdot u_{B(\theta)}-\theta\cdot u_{\hat{B}(\theta)}>\delta\})$.
-We know $p(0)=p$.
 
@@
 
-\begin{lemma}
-$S(\delta)\leq M\delta$.
-\label{lemma:sdelta}
+Notation: $t_s$ is end time for phase $s$.
+
+\subsection{General Lemmas}
+
+We begin by showing that under our assumptions, the measure of
+problematic arms cannot be too large.
+
+\begin{lemma} \label{lem:sdelta}
+$\AlmostTied{\delta} \leq \TieDensity \cdot \delta$ for all $\delta$.
+\end{lemma}
+
+\begin{emptyproof}
+Using the upper bound from Assumption~\ref{A1}, we can bound
+
+\begin{align*}
+\AlmostTied{\delta}
+& = \sum_{i,i'} \ProbC{\AgV \cdot (\ArmV{i} - \ArmV{i'}) \leq \delta}%
+    {\AgV \in \FirstTwo{i}{i'}}
+  \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}\\
+& \leq \sum_{i,i'} \TieDensity \cdot \delta
+    \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}
+\; = \; \TieDensity \cdot \delta. \QED
+\end{align*}
+\end{emptyproof}
+
+We next bound the length of any phase, which will be useful to bound
+the cumulative regret of the early rounds
+(before tail bounds have kicked in).
+
+\begin{lemma} \label{lem:phase-length}
+For any $s$, the expected length of phase $s$ is at most
+$\ARMNUM \cdot s$ time steps.
 \end{lemma}
@@
 \begin{proof}
-\begin{align*}
-S(\delta)&=\sum_{i,j}P(\theta\cdot(u_{i}-u_{j})\le \delta|\theta\in \Omega_{i,j})P(\theta\in \Omega_{i,j}) \\
-&\leq \sum_{i,j}M\delta \times P(\theta\in \Omega_{i,j}) \\
-&=M\delta.
-\end{align*}
+Let $S$ be the set of arms that have been pulled at most
+$s-1$ times at the start of phase $s$.
+Thus, phase $s$ ends when each $i \in S$ has been pulled at least once.
+Consider any time step $t$.
+If $S$ contains at least one payment-eligible arm $i$,
+then some payment-eligible arm will be pulled with probability 1,
+and every payment-eligible arm is in $S$.
+In particular, the size of $S$ decreases with probability 1.
+If $S$ contains no payment-eligible arm,
+then by definition of payment-eligibility,
+each arm $i \in S$ has probability at least $1/s$ of being pulled.
+In particular, the size of $S$ decreases with probability at least $1/s$.
+
+In either case, the expected number of time steps until
+$|S|$ decreases is at most $s$,
+so the expected number of steps until $S$ is empty is at most
+$\ARMNUM \cdot s$.
+\dkcomment{If we wanted, this bound could probably be improved using a
+  coupon collector argument. But it would look uglier.}
 \end{proof}
 
-The following lemma bounds the probability of making a mistake if we let the agents play myopically in the $n^{th}$ round, given that the utility difference between his/her best and second best arm is bounded below by a constant.
+The key technical lemma bounds the probability of mistakes in myopic play.
+Intuitively, because estimates of the arms' attribute vectors become
+exponentially more accurate with increasing phases $s$,
+errors from myopic play should decrease exponentially.
+That intuition is captured by the following lemma.
 
-\begin{lemma}
-Define $\tau$ to be any stopping time that is almost surely between $t_n$ and $t_{n+1}-1$ with respect to the filtration $\mathcal{F}_{t}=\sigma(A_1,\cdots,A_t,c_1,\cdots,c_t,O_1,\cdots,O_t)$, we have
-\begin{align}
-P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24Nm\exp\left(-\frac{1.8n\lambda^2}{16\sigma^2}\right), \nonumber
-\end{align}
-for $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$.
-\label{round:prob}
+\begin{lemma} \label{lem:round-prob}
+Let $x > 0$ be arbitrary.
+Recall that $\sigma$ is the standard deviation of the Gaussian noise.
+Let $\LatePhase \geq \max \SET{50, \frac{92.16 \sigma^4}{x^4}}$.
+
+\dkcomment{Is it problematic that we use $\sigma$ for two things here?}
+Let $\tau$ be any stopping time that is almost surely \dkcomment{What
+  exactly do we mean by this here?} in phase $s$,
+with respect to the filtration
+$\mathcal{F}_{t} = \sigma (\Pull{1}, \ldots, \Pull{t},
+                          \PayA{1}, \ldots, \PayA{t},
+                          \ObsV{1}, \ldots, \ObsV{t})$.
+Then, for all $s \geq \LatePhase$,
+\begin{align*}
+  \ProbC[\AgV \sim \AgentDist]{%
+  \argmax \SET{\AgentV{\tau} \cdot \ArmEV{\tau}{i}} \neq \Best{\AgentV{\tau}}}{%
+  \AgentV{\tau} \cdot (\ArmV{\Best{\AgentV{\tau}}} - \ArmV{\Second{\AgentV{\tau}}})
+  > 2\Diam d x}
+& \leq 24 \ARMNUM d \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right).
+\end{align*}
 \end{lemma}
 
-We need the following lemma in order to prove Lemma~\ref{round:prob} and we include the proof in the appendix.
+The proof of Lemma~\ref{lem:round-prob} is based on an adaptive
+concentration inequality due to \cite{zhao2016adaptive},
+given as Lemma~\ref{lem:ACI-inequality}.
 
-\begin{lemma}
-For $n\geq n_{0}=\max\{50, \frac{92.16\sigma^4}{\lambda^4}\}$, we have
-\begin{align}
-\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-\label{n0-inequality}
+\begin{lemma}[Corollary 1 of \cite{zhao2016adaptive}]
+\label{lem:ACI-inequality}
+Let $X_i$ be zero-mean $1/2$-subgaussian random variables,
+and $\SET{S_n = \sum_{i=1}^n X_i, n \geq 1}$ the corresponding random walk.
+Let $J$ be any stopping time with respect to $\SET{X_1, X_2, \ldots}$.
+(We allow $J$ to take the value $\infty$,
+defining $\Prob{J = \infty} = 1 - \lim_{n \to \infty} \Prob{J \leq n}$.)
+Define \dkcomment{I'm making the dependence of $b$ on $n$ explicit,
+  since that's how we're using it.}
+\begin{align*}
+g(n) & = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b(n)}.
+\end{align*}
+Then, 
+\begin{align*}
+\Prob{J < \infty \mbox{ and } S_J \geq g(J)} \leq 12 \e^{-1.8 b(n)}.
+\end{align*}
 \end{lemma}
 
-To prove Lemma~\ref{round:prob}, we also need to use an adaptive concentration inequality due to \cite{zhao2016adaptive}. For reference, we state it here as a Lemma.
+\begin{extraproof}{Lemma~\ref{lem:round-prob}}
+Consider any agent type \AgentV{\tau} at the (random) time $\tau$ such that
+$\AgentV{\tau} \cdot (\ArmV{\Best{\AgentV{\tau}}} - \ArmV{\Second{\AgentV{\tau}}})
+> 2\Diam d x$.
+We will use Lemma~\ref{lem:ACI-inequality} to show that
+for any arm $i$ and attribute $j = 1, \ldots, d$,
+with probability at least
+$1 - 24 \exp \left( \frac{-1.8 s x^2}{16\sigma^2} \right)$,
+the estimated attribute $j$ for arm $i$ is close enough to the true attribute: 
+$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$.
+By a union bound over all $i, j$, this bound holds simultaneously for all
+arms and coordinates with probability at least
+$1 - 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16\sigma^2} \right)$.
 
-\begin{lemma}[Corollary 1 in \cite{zhao2016adaptive}]
-Let $X_{i}$ be zero mean $1/2$-subgaussian random variables.
-$\{S_{n}=\sum_{i=1}^{n}X_{i},n\geq 1\}$ be a random walk.
-Let $J$ be any stopping time with respect to $\{X_1,X_2,\cdots\}$.
-We allow $J$ to take the value of $\infty$ where $P(J=\infty)=1-\lim_{n\rightarrow \infty}P(J\leq n)$.
-If
-\begin{align}
-f(n)=\sqrt{0.6n\log(\log_{1.1}(n)+1)+bn}, \nonumber
-\end{align}
-then
-\begin{align}
-Pr[\{S_{J}\geq f(J)\}\cap \{J<\infty\}]\leq 12e^{-1.8b}. \nonumber
-\end{align}
-\label{ACI-inequality}
+Then, consider any type $\AgV = \AgentV{\tau}$ in the high-probability event,
+and let $i \neq \Best{\AgentV{\tau}}$ be any other arm.
+By the conditioning of \AgentV{\tau}, the true reward from arm $i$ is
+much smaller than from the best arm:
+$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
+Because each coordinate of \ArmEV{\tau}{\Best{\AgV}} and of
+\ArmEV{\tau}{i} is estimated accurately to within $x$, 
+we get that 
+$\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
+\geq - \Diam d x$
+and
+$\AgV \cdot (\ArmEV{\tau}{i} - \ArmV{i}) \leq \Diam d x$.
+Hence,
+
+\begin{align*}
+\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmEV{\tau}{i})
+& =
+\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
++ \AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i})
++ \AgV \cdot (\ArmV{i} - \ArmEV{\tau}{i})\\
+& > -\Diam d x + 2 \Diam d x - \Diam d x
+\; = \; 0,
+\end{align*}
+which means that the agent with type \AgV will in fact choose
+the optimal arm in the high-probability event.
+
+It remains to prove that with high probability, all arms' coordinates
+are estimated sufficiently accurately for type \AgentV{\tau}.
+Thereto, fix an arm $i$ and attribute $j$.
+For any $n \geq 1$, let $k_s$ be the time step right after arm $i$ has
+been pulled for the \Kth{n} time.
+\dkcomment{I'm writing $n$ instead of $s$ here because $S_s$ would
+  look ugly, and $n$ is consistent with the lemma.
+  Or we could rename $S$ to something else.}
+Define
+$S_n := \frac{n \cdot (\ArmE{k_n}{i}{j} - \Arm{i}{j})}{2 \sigma}$
+to be the sum of all attribute-$j$ noise components up to and
+including the \Kth{n} pull of arm $i$,
+\dkcomment{I'm not sure if we have defined the notation for components
+  of vectors in the \emph{superscript}. Let's make sure not to forget it.}
+renormalized to have standard deviation $1/2$.
+\dkcomment{Is this the correct scaling.}
+The $S_n$ define an unbiased half-subgaussian random walk,
+and we can therefore apply Lemma~\ref{lem:ACI-inequality} to them.
+Specifically, we set $b(n) = \frac{n x^2}{16 \sigma^2}$,
+and obtain that
+
+\begin{align*}
+\Prob{J < \infty \mbox{ and } S_J \geq 
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}}
+& \leq 12 \exp \left( \frac{-1.8 J x^2}{16 \sigma^2} \right).
+\end{align*}
+
+Applying Lemma~\ref{lem:ACI-inequality} to $-S_n$ with the same choice
+of $b(n)$, and taking a union bound over both cases, we obtain that
+
+\begin{align*}
+\Prob{J < \infty \mbox{ and } |S_J| \geq 
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}}
+& \leq 24 \exp \left( \frac{-1.8 J x^2}{16 \sigma^2} \right).
+\end{align*}
+
+In the high-probability case
+$|S_J| \leq
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}$,
+we first use that $\sqrt{\cdot}$ is sublinear to bound
+$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}
+\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$.
+Then, we use the following technical Lemma~\ref{lem:n0-inequality}
+(whose proof is given in the appendix, and whose precondition we verify
+momentarily) to bound the first term,
+giving us an overall upper bound of
+$|S_J| \leq \frac{J x}{2 \sigma}$.
+
+\begin{lemma} \label{lem:n0-inequality}
+For any $n \geq \LatePhase = \max (50, \frac{92.16 \sigma^4}{x^4})$, 
+\begin{align*}
+\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} & \leq \frac{n x}{4 \sigma}. 
+\end{align*}
 \end{lemma}
 
-We now prove Lemma~\ref{round:prob}.
+Substituting the definition of $S_J$ and canceling common terms,
+the inequality implies that
+$|\ArmE{k_J}{i}{j} - \Arm{i}{j}| \leq x$.
+By the assumptions of the lemma,
+the stopping time $\tau$ is such that almost surely, each arm --- and
+in particular arm $i$ --- has been pulled at least
+$s \geq \LatePhase$ times at time $\tau$.
+Defining $J$ to be the number of times that $i$ has been pulled at
+time $\tau$, we obtain that $J$ satisfies the precondition of
+Lemma~\ref{lem:n0-inequality}.
+Furthermore, with probability 1, $J$ will be finite, meaning that
+\begin{align*}
+& \Prob{S_J \geq 
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16
+    \sigma^2}}}\\
+= & \Prob{J < \infty \mbox{ and } S_J \geq 
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16
+    \sigma^2}}}.
+\end{align*}
 
-\begin{proof}[Proof of Lemma~\ref{round:prob}]
-In the $n^{th}$ round, we know all arms have been pulled at least $n$ times.
-For all the agents $\theta$ whose utility difference between their best and second best arm is greater than $2mW\lambda$, denote $K(\theta)=\max_{i\neq B(\theta)}\{\theta\cdot u_{i,t}\}$.
-If $|u_{i,t}^{j}-u_{i}^{j}|\leq \lambda$ for all $i,j$, then
-\begin{align}
-&\theta\cdot(u_{B(\theta),t}-u_{K(\theta),t}) \nonumber \\
-\geq & \theta\cdot(u_{B(\theta),t}-u_{B(\theta)}) + \theta\cdot(u_{K(\theta)}-u_{K(\theta),t}) + \theta\cdot(u_{B(\theta)}-u_{K(\theta)}) \nonumber \\
-> & -Wm\lambda - Wm\lambda + 2Wm\lambda = 0,\nonumber
-\end{align}
-which means their myopic action would incur no regret.
+Finally, this choice of $J$ ensures that
+$\ArmE{k_J}{i}{j} = \ArmE{\tau}{i}{j}$,
+and we have thus shown that
+$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$ for all $i,j$.
+\end{extraproof}
 
-Define $\epsilon_{i,\tau}=u_{i,\tau}-u_i$ and $\epsilon_{i,\tau}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,\tau}$. Thus, we have
-\begin{align}
-&P(\arg\max\{\theta_{\tau}\cdot u_{i,\tau}\}\neq B(\theta_{\tau})|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\nonumber \\
-\leq &P(\exists i, \exists j, |u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda |\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & \sum_{i}\sum_{j} P(|u_{i,\tau}^{j}-u_{i}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-= &  \sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda). \label{ACI}
-\end{align}
-
-To bound equation~(\ref{ACI}), we use Lemma~\ref{ACI-inequality}. Define
-\begin{align}
-S_{N(i,\tau)}^{i,j}=\frac{\epsilon_{i,\tau}^{j}}{2\sigma}. \nonumber
-\end{align}
-
-Based on Lemma~\ref{n0-inequality}, for $n_{0}=\max\{50,\frac{92.16\sigma^2}{\lambda^2}\}$ and $n\geq n_{0}$, we have
-\begin{align}
-\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)}. \nonumber
-\end{align}
-
-Thus, if we set $b=\frac{n\lambda^2}{16\sigma^2}$ in Lemma~\ref{ACI-inequality}, for any $N(i,\tau)\geq n\geq n_{0}$, we have
-\begin{align}
-\frac{N(i,\tau)\lambda}{2\sigma}\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)}+\frac{\lambda}{4\sigma}\sqrt{n N(i,\tau)} \nonumber \\
-\geq & \sqrt{0.6N(i,\tau)\log(\log_{1.1}(N(i,\tau))+1)+bN(i,\tau)}, \nonumber 
-\end{align}
-where the last inequality is because $\sqrt{x}+\sqrt{y}\geq \sqrt{x+y}$. Thus, we have
-\begin{align}
-&P(\epsilon_{i,\tau}^{j}\geq\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P\left(S_{N(i,\tau)}^{i,j}\geq \frac{N(i,\tau)\lambda}{2\sigma}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
-\leq & P\left(S_{N(i,\tau)}^{i,j}\geq \sqrt{0.6 N_{i,\tau}\log(\log_{1.1}(N(i,\tau))+1)+b N(i,\tau)}\bigg|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda\right) \nonumber \\
-\leq & 12\exp( -1.8b) = 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
-\end{align}
-Similarily, we can bound 
-\begin{align}
-&P(\epsilon_{i,\tau}^{j}\leq-\lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-=&P(-\epsilon_{i,\tau}^{j}\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda) \nonumber \\
-\leq & 12\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber 
-\end{align}
-
-Therefore, we know $P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)\leq 24\exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right)$.
-Thus, we know
-\begin{align}
-&\sum_{i}\sum_{j} P(|\epsilon_{i,\tau}^{j}|\geq \lambda|\theta_{\tau}\cdot(u_{B(\theta_{\tau})}-u_{\hat{B}(\theta_{\tau})})> 2Wm\lambda)  \nonumber \\
-\leq& 24Nm \exp\left(\frac{-1.8 n\lambda^2}{16\sigma^2}\right). \nonumber
-\end{align}
-\end{proof}
-
-Before we start analyzing the cumulative regret, we first prove the following lemma which bounds the expected length of each round.
-\begin{lemma}
-Using our algorithm, we have $\mathbb{E}[t_{n+1}-t_{n}]\leq Nn$, $\forall n\geq 1$.
-\label{round:length}
-\end{lemma}
-\begin{proof}
-A round completes when each arm is pulled at least once in that round.
-Let $X_{i}$ be the number of agents who come to the system between the time after the $(i-1)^{th}$ unique arm was pulled, up to and including the time when the $i^{th}$ unique arm was pulled.
-Then we know
-\begin{equation*}
-\mathbb{E}[t_{n+1}-t_{n}]=\sum_{i=1}^{N}E[X_{i}].
-\end{equation*}
-
-Fix $i$.
-In bounding $X_i$, we think of agents as ``trials'', where each trial can result in a new unique arm being pulled (which we call a ``successful'' trial), or not.
-There are two ways a trial can be successful:
-\begin{itemize}
-\item If there is at least one arm that has not been pulled and the probability of an agent utility function that would pull this arm without incentives is less than $n^{-1}$, then the principal will offer an incentive that causes this arm to be pulled (or one of these arms if there is more than one).
-In this case, the probability that the trial is succesful is $1$.
-\item The probability of an agent utility function that would pull each un-pulled arm without incentives is at least $n^{-1}$.
-In this case, the probability that the trial is successful is at least $n^{-1}$.
-\end{itemize}
-
-Thus, $X_{i}$ is stochastically dominated below by a geometric random variable with success probability $n^{-1}$, the expected number of trials up to and including the first success, $E[X_i]$, is bounded above by $n$.
-Thus,
-\begin{align}
-E[t_{n+1}-t_{n}]\leq Nn. \nonumber
-\end{align}
-\end{proof}
+\subsection{Bounding the Total Payment}
 
@@
 \begin{lemma}
-The expected number of payments for Algorithm~\ref{Alg1} is bounded above by $O(N^2)$.
+The expected number of payments for Algorithm~\ref{Alg1} is bounded above by $O(\ARMNUM^2)$.
 \label{lemma:numP}
@@
 \begin{proof}
-If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2mW\lambda\}$, they will correctly identify their best arm.
-Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms.
+If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\AgV\in \{\AgV:\AgV\cdot u_{B(\AgV)}-\max_{j\neq B(\AgV)}\{\AgV \cdot u_{j}\}> 2mW\lambda\}$, they will correctly identify their best arm.
+Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2 \Diam d}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms.
 In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
@@
 =&\sum_{n=1}^{\infty}\sum_{i=1}^{N}P(c(\tau_{n}^{i})>0) \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}P\left(\exists i,j:|u_{i}^{j}-u_{i,\tau_{n}^{i}}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2Wm}\right)+\sum_{n=1}^{n_1}N \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right) +\sum_{n=1}^{n_1}N \nonumber \\
-\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64W^2 m^2\sigma^2}\right)\times N+\sum_{n=1}^{n_1}N \nonumber  \\
-\leq&24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1, \nonumber
+\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}P\left(\exists i,j:|u_{i}^{j}-u_{i,\tau_{n}^{i}}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2 \Diam d}\right)+\sum_{n=1}^{n_1}\ARMNUM \nonumber \\
+\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}24 \ARMNUM d
+       \exp\left(\frac{-1.8 n\delta_{0}^2}{64 \Diam^2 d^2\sigma^2}\right) +\sum_{n=1}^{n_1}\ARMNUM \nonumber \\
+\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64\Diam^2 d^2\sigma^2}\right)\times \ARMNUM+\sum_{n=1}^{n_1}\ARMNUM \nonumber  \\
+\leq&24 \ARMNUM^2 d \frac{1}{\exp(\frac{1.8\delta_{0}}{64\Diam^2 d^2\sigma^2})-1} + Nn_1, \nonumber
 \end{align}
 
-Thus, we know the expected number of payments is bounded above by $O(N^2)$.
+Thus, we know the expected number of payments is bounded above by $O(\ARMNUM^2)$.
 
@@
 
+\subsection{Bounding the Total Regret}
+
 Now we are ready to prove our second main result, Theorem~\ref{rst:regret}.
+
 \begin{proof}
@@
 For regret incurred after the first $n_0$ round, it has two different components: the regret incurred when we let the agents play myopically and the regret incurred when we incentivize the agents.
-Using Lemma~\ref{lemma:numP}, the expected regret incurred when we incentivize the agents is bounded above by: $\left[24N^2 m \frac{1}{\exp(\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2})-1} + Nn_1\right]R$.
+Using Lemma~\ref{lemma:numP}, the expected regret incurred when we incentivize the agents is bounded above by: $\left[24\ARMNUM^2 d \frac{1}{\exp(\frac{1.8\delta_{0}}{64\Diam^2 d^2\sigma^2})-1} + Nn_1\right]R$.
 
@@
 For $k>t_{n+1}-t_{n}$, we define $\tau_{n}^{k}=\infty$.
-For $\tau_{n}^{k}=t$, the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right)\times R$.
+For $\tau_{n}^{k}=t$, the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)\times R$.
 We denote the regret incurred by these agents as $r_1(\tau_{n}^{k})$.
@@
 \eqref{chap5:equ:r1}= & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty) + E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}\left[\sum_{k=1}^{\infty}24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 W^2 m^2\sigma^2}\right) R\times P(\tau_{n}^{k}<\infty) \right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right) R \times Nn+ \sum_{t=1}^{T}Mf(t)^2. \label{chap5:equ:regret}
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}\left[\sum_{k=1}^{\infty}24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right) R\times P(\tau_{n}^{k}<\infty) \right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
+\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 \Diam^2 d^2\sigma^2}\right) R \times Nn+ \sum_{t=1}^{T}Mf(t)^2. \label{chap5:equ:regret}
 \end{align}
@@
 \begin{align}
-&\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-+ & 24N^2 m \frac{1}{e^{\frac{1.8\delta_{0}}{64W^2 m^2\sigma^2}}-1}R+N\left(\max\left\{n_{0},\frac{2}{p}\right\}\right)R. \nonumber
+&\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 \Diam^2 d^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
++ & 24\ARMNUM^2 d \frac{1}{e^{\frac{1.8\delta_{0}}{64\Diam^2 d^2\sigma^2}}-1}R+\ARMNUM\left(\max\left\{n_{0},\frac{2}{p}\right\}\right)R. \nonumber
 \end{align}
@@
 \begin{align}
-\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2. \label{equ:regret}
+\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 \Diam^2 d^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2. \label{equ:regret}
 \end{align}
 
-If we set $f^2(t)=\frac{2\log(T)\times 64W^2 m^2\sigma^2}{1.8t}$, then
+If we set $f^2(t)=\frac{2\log(T)\times 64\Diam^2 d^2\sigma^2}{1.8t}$, then
 \begin{align}
-&\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\ 
-\leq & \sum_{n=1}^{T} 24N^2 mnR \exp\left(-2\log(T)\right)  + \frac{128W^2 m^2\sigma^2 M\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{n} \nonumber \\
-\leq &  24N^2 m R\frac{T(T-1)}{2T^2}  + 71.12 W^2 m^2\sigma^2 M\log(T)(\log(T)+1) \nonumber \\
-\leq &  12 N^2 m R  + 71.12 W^2 m^2\sigma^2 M\log(T)(\log(T)+1). \nonumber
+&\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 \Diam^2 d^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\ 
+\leq & \sum_{n=1}^{T} 24\ARMNUM^2 mnR \exp\left(-2\log(T)\right)  + \frac{128\Diam^2 d^2\sigma^2 \TieDensity\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{n} \nonumber \\
+\leq &  24\ARMNUM^2 d R\frac{T(T-1)}{2T^2}  + 71.12 \Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1) \nonumber \\
+\leq &  12 \ARMNUM^2 d R  + 71.12 \Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1). \nonumber
 \end{align}
 
-Thus, the cumulative expected regret is bounded by $O(N^2 m + M m^2(\log(T))^2)$.
+Thus, the cumulative expected regret is bounded by $O(\ARMNUM^2 d + \TieDensity d^2(\log(T))^2)$.
 \end{proof}
@@
 \begin{corollary}
-If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O(N^2)$.
+If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O(\ARMNUM^2)$.
 \end{corollary}
@@
 The proof of this corollary is similar to the proof of Theorem~\ref{rst:regret}.
-If we set $f^2(t)=\frac{2\log(T)\times 64W^2 m^2\sigma^2}{1.8t}$, then there exists a $t_{0}$ such that for $t>t_{0}$, $S(f(t))=0$.
+If we set $f^2(t)=\frac{2\log(T)\times 64\Diam^2 d^2\sigma^2}{1.8t}$, then there exists a $t_{0}$ such that for $t>t_{0}$, $S(f(t))=0$.
 Thus, similar to equation~\eqref{equ:regret}, we know the cumulative expected regret when we let the agents play myopically is bounded above by
 \begin{align}
-\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 W^2 m^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{t_{0}}Mf(t)^2 \nonumber
+\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 \Diam^2 d^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{t_{0}}Mf(t)^2 \nonumber
 \end{align}
-Therefore, based on the same analysis of Theorem~\ref{rst:regret}, we know the cumulative regret is bounded by $O(N^2)$.
+Therefore, based on the same analysis of Theorem~\ref{rst:regret}, we know the cumulative regret is bounded by $O(\ARMNUM^2)$.
 \end{proof}
 
-\subsection{Practical Issues}
-\label{sec:pi}
-In Algorithm~\ref{Alg1}, we use ``pay whatever it takes'' strategy when we decide to incentivize the agent.
-However, ''pay whatever it takes'' only shows up in the proof of Lemma~\ref{round:length}.
-Without loss of generality, suppose we want to incentivize arm $i$ at time $t$ at the $n^{th}$ round.
-Based on the proof of Lemma~\ref{round:length}, as long as we offer a payment $c_{i,t}$ such that arm $i$ has at least $n^{-1}$ probability being pulled at time $t$, our results still hold true.
-We could compute this $c_{i,t}$ dynamically based on $F(\cdot)$ as well as our current estimate $u_{i,t}$.
-Here is the revised algorithm which would work well in practice:
+\subsection{Decreasing the Payment} \label{sec:pi}
+\dkcomment{Does this really need a whole subsection now?}
 
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration}
-\label{Alg2}
-\begin{algorithmic}
-\STATE Set n = 1 to denote the round number; Let $V=\emptyset$ be the set of arms that were pulled in the current round;
-\FOR{ $t = 1, 2, 3, \cdots$}{
-\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
-\IF {$S\setminus V$ is non-empty}
-\STATE{Choose an arm $i$ uniformly at random from $S\setminus V$}
-\STATE{Offer payment $c_{i,t}=\inf\{c: P(\theta\sim F: \theta\cdot u_{i,t}+c>max_{j}\theta\cdot u_{j,t})>n^{-1}\}$}
-\ELSE
-\STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
-\ENDIF
-\STATE Denote $A_t$ as the pulled arm, update $V=V\cup\{A_t\}$, $u_{A_t,t}$ and $N(A_t,t)$
-\IF {$n\neq \min_{i}N(i,t)$} 
-\STATE $V=\emptyset$
-\ENDIF
-\STATE Update the round number, $n = \min_{i} N(i,t)$
-}\ENDFOR
-
-\end{algorithmic}
-\end{algorithm}
-
-The same proof would work and we can get the exact same results as Algorithm~\ref{Alg1}.
+In Algorithm~\ref{alg:basic-incentivizing},
+the payment \Pay{t}{i} offered for pulling payment-eligible arms $i$
+is high enough to ensure that arm $i$ will be pulled with probability 1.
+However, as can be seen in the proof of Lemma~\ref{lem:phase-length},
+we then lower-bound this probability by $1/s$.
+Thus, the bounds we prove do not deteriorate as long as the payment is
+high enough such that arm $i$ is pulled with probability at least $1/s$.
+A sufficient payment would be defined as
+$\Pay{t}{i} = \sup \Set{c \geq 0}{%
+  \Prob[\AgV \sim \AgentDist]{c + \AgV \cdot \ArmEV{t}{i} \leq \AgV \cdot \ArmEV{t}{i'}}}$.
+Except for offering different payments, the algorithm remains unchanged.
+Then, the exact same analysis shows that the modified algorithm
+provides the same guarantees.

### 2018-02-05 result_discussion.tex
changes to COLT
significant edits to algorithm section

@@
-\section{Problem Setup and Overview of Results}
+\section{Overview of Results and Discussion}
 \dkcomment{I envision this section doing the following:
@@
 
-\begin{theorem} \label{thm:main-intro}
+\dkcomment{In the results discussion clarify which results need to
+  know $T$ and which don't.}
+
+\begin{theorem} \label{thm:main-overview}
 Under some technical assumptions, 

### 2018-02-05 algorithm.tex
finished edits up to payment

@@
-% move to colt.tex eventually
-
-\newcommand{\e}{\mathrm{e}}
-\providecommand{\Kth}[1]{\ensuremath{{#1}^{\rm th}}}
-
-\def\QED{{\phantom{x}} \hfill \ensuremath{\rule{1.3ex}{1.3ex}}}
-
-\newcommand{\extraproof}[1]{\rm \trivlist \item[\hskip \labelsep{\bf Proof of #1. }]}
-\def\endextraproof{\QED \endtrivlist}
-
-\def\emptyproof{\rm \trivlist \item[\hskip \labelsep{\bf Proof. }]}
-\def\endemptyproof{\endtrivlist}
-
 \section{Main Algorithm and Analysis}
@@
 
-\dkcomment{I moved the assumptions to an earlier section.
-I am saving here some text that was in that subsection.}
-
-We use $R = \max_{\AgV, i,j} \AgV \cdot (u_i - u_j)$ to denote the
-maximum regret that can be incurred at each time.
-Assumption~\ref{A2} implies that the maximum regret or payment
-incurred in any one round is finite.
-
-As we can see later in our proof, we only need $\max_{i,j}\limsup_{y\rightarrow 0^{+}}\frac{F_{i,j}(y)}{y}$ to be finite.
-Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm.
-
 In this section, we prove Algorithm~\ref{alg:basic-incentivizing} achieves $O(\ARMNUM^2+\TieDensity(\log(T))^2)$ cumulative regret with $O(\ARMNUM^2)$ payment budget.
@@
 
-The key technical lemma bounds the probability of mistakes in myopic play.
-Intuitively, because estimates of the arms' attribute vectors become
-exponentially more accurate with increasing phases $s$,
-errors from myopic play should decrease exponentially.
+The key technical lemma captures the intuition that
+the estimates of the arms' attribute vectors become
+exponentially more accurate with increasing phases $s$.
 That intuition is captured by the following lemma.
@@
                           \ObsV{1}, \ldots, \ObsV{t})$.
-Then, for all $s \geq \LatePhase$,
-\begin{align*}
-  \ProbC[\AgV \sim \AgentDist]{%
-  \argmax \SET{\AgentV{\tau} \cdot \ArmEV{\tau}{i}} \neq \Best{\AgentV{\tau}}}{%
-  \AgentV{\tau} \cdot (\ArmV{\Best{\AgentV{\tau}}} - \ArmV{\Second{\AgentV{\tau}}})
-  > 2\Diam d x}
-& \leq 24 \ARMNUM d \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right).
-\end{align*}
+Then, for all phases $s \geq \LatePhase$,
+with probability at least 
+$1- 24 \ARMNUM d \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$,
+the following holds for all arms $i$ and attributes $j$
+simultaneously:
+$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$.
+\dkcomment{We should clarify what the probability is over. It seems to
+  be over the entire past history, but not the current type.}
 \end{lemma}
@@
 \begin{extraproof}{Lemma~\ref{lem:round-prob}}
-Consider any agent type \AgentV{\tau} at the (random) time $\tau$ such that
-$\AgentV{\tau} \cdot (\ArmV{\Best{\AgentV{\tau}}} - \ArmV{\Second{\AgentV{\tau}}})
-> 2\Diam d x$.
-We will use Lemma~\ref{lem:ACI-inequality} to show that
-for any arm $i$ and attribute $j = 1, \ldots, d$,
-with probability at least
-$1 - 24 \exp \left( \frac{-1.8 s x^2}{16\sigma^2} \right)$,
-the estimated attribute $j$ for arm $i$ is close enough to the true attribute: 
-$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$.
-By a union bound over all $i, j$, this bound holds simultaneously for all
-arms and coordinates with probability at least
-$1 - 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16\sigma^2} \right)$.
-
-Then, consider any type $\AgV = \AgentV{\tau}$ in the high-probability event,
-and let $i \neq \Best{\AgentV{\tau}}$ be any other arm.
-By the conditioning of \AgentV{\tau}, the true reward from arm $i$ is
-much smaller than from the best arm:
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
-Because each coordinate of \ArmEV{\tau}{\Best{\AgV}} and of
-\ArmEV{\tau}{i} is estimated accurately to within $x$, 
-we get that 
-$\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
-\geq - \Diam d x$
-and
-$\AgV \cdot (\ArmEV{\tau}{i} - \ArmV{i}) \leq \Diam d x$.
-Hence,
-
-\begin{align*}
-\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmEV{\tau}{i})
-& =
-\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
-+ \AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i})
-+ \AgV \cdot (\ArmV{i} - \ArmEV{\tau}{i})\\
-& > -\Diam d x + 2 \Diam d x - \Diam d x
-\; = \; 0,
-\end{align*}
-which means that the agent with type \AgV will in fact choose
-the optimal arm in the high-probability event.
-
-It remains to prove that with high probability, all arms' coordinates
-are estimated sufficiently accurately for type \AgentV{\tau}.
-Thereto, fix an arm $i$ and attribute $j$.
-For any $n \geq 1$, let $k_s$ be the time step right after arm $i$ has
+Fix an arm $i$ and attribute $j$.
+For any $n \geq 1$, let $k_n$ be the time step right after arm $i$ has
 been pulled for the \Kth{n} time.
@@
 $|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$ for all $i,j$.
+The lemma now follows by a union bound over all \ARMNUM arms and $d$
+attributes.
 \end{extraproof}
+
+Lemma~\ref{lem:round-prob} implies that errors from myopic play
+decrease exponentially in the phase number $s$.
+
+\begin{corollary} \label{cor:right-choice}
+Let $x > 0$ be arbitrary.
+Let $\LatePhase \geq \max (50, \frac{92.16 \sigma^4}{x^4})$.
+
+Let $\tau$ be any stopping time that is almost surely \dkcomment{What
+  exactly do we mean by this here?} in phase $s$,
+with respect to the filtration
+$\mathcal{F}_{t} = \sigma (\Pull{1}, \ldots, \Pull{t},
+                          \PayA{1}, \ldots, \PayA{t},
+                          \ObsV{1}, \ldots, \ObsV{t})$.
+Then, for all $s \geq \LatePhase$,
+with probability (over the past history) at least 
+$1 - 24 \ARMNUM d \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$,
+\dkcomment{We should clarify what the probability is over. It seems to
+  be over the past history, but not the current agent.}
+all agent types $\AgV = \AgentV{\tau}$ with
+$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > 2\Diam d x$
+will pull their best arm, i.e.,
+$\argmax \SET{\AgV \cdot \ArmEV{\tau}{i}} = \Best{\AgV}$
+\end{corollary}
+
+\begin{proof}
+Let $\tau$ be a (random) time.
+By Lemma~\ref{lem:round-prob},
+with probability at least
+$1 - 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16\sigma^2} \right)$,
+for all arms $i$ and attributes $j = 1, \ldots, d$ simultaneously,
+the estimated attribute $j$ for arm $i$ is close enough to the true attribute: 
+$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$.
+Condition on this high-probability event.
+
+Consider any agent type $\AgV = \AgentV{\tau}$ at the (random) time
+$\tau$ such that
+$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > 2\Diam d x$.
+Let $i \neq \Best{\AgV}$ be any other arm;
+its true reward is much smaller than from the best arm:
+$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
+Because each coordinate of \ArmEV{\tau}{\Best{\AgV}} and of
+\ArmEV{\tau}{i} is estimated accurately to within $x$, 
+we get that 
+$\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
+\geq - \Diam d x$
+and
+$\AgV \cdot (\ArmEV{\tau}{i} - \ArmV{i}) \leq \Diam d x$.
+Hence,
+
+\begin{align*}
+\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmEV{\tau}{i})
+& =
+\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
++ \AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i})
++ \AgV \cdot (\ArmV{i} - \ArmEV{\tau}{i})\\
+& > -\Diam d x + 2 \Diam d x - \Diam d x
+\; = \; 0,
+\end{align*}
+which means that the agent with type \AgV will in fact choose
+the optimal arm in the high-probability event.
+\end{proof}
 
@@
 
-Using the above lemmas, we are ready to prove Theorem~\ref{rst:budget}.
-We include the proof of Theorem~\ref{rst:budget} in the appendix.
-Below, we bound the expected number of payments for our algorithm.
-\begin{lemma}
-The expected number of payments for Algorithm~\ref{Alg1} is bounded above by $O(\ARMNUM^2)$.
-\label{lemma:numP}
+Towards bounding the algorithm's total payment, we first bound the
+\emph{number} of rounds in which the algorithm makes a payment by a
+constant.
+This bound also turns out to be useful for bounding the total regret.
+
+\begin{lemma} \label{lem:numP}
+The expected number of time steps in which
+Algorithm~\ref{alg:basic-incentivizing}
+makes any payment is at most $O(\ARMNUM^2)$.
 \end{lemma}
+
 \begin{proof}
-If $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\AgV\in \{\AgV:\AgV\cdot u_{B(\AgV)}-\max_{j\neq B(\AgV)}\{\AgV \cdot u_{j}\}> 2mW\lambda\}$, they will correctly identify their best arm.
-Thus we know, in the $n^{th}$ round, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{p^{-1}(\frac{p}{2})}{2 \Diam d}$ $\forall i$ and $\forall j$, and $n^{-1}\leq p/2$, we do not need to incentivize any arms.
-In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
-Denote $n_1=\max\{n_{0}, \frac{2}{p}\}$.
-Denote $\delta_{0}=p^{-1}(\frac{p}{2})>0$ (because of Assumption~\ref{A1}).
+We partition phases into early and late phases.
+For each of the early phases,
+we crudely bound the number of payments by \ARMNUM,
+using that each arm is incentivized at most once per phase.
+For later phases,
+we use that arms are payment-eligible only if their myopic pulling
+probability is less than $1/s$.
+Since at least a \MinProb fraction of agents would prefer arm $i$ if
+given accurate estimates, this would require misestimates that make a
+significant fraction of agents pull the wrong arm.
+But in later phases, such misestimates are unlikely by
+Corollary~\ref{cor:right-choice}.
 
-Define $\tau_{n}^{i}$ to be the first time we pull arm $i$ in the $n^{th}$ round. Then
-\begin{align}
-\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\} =\sum_{n=1}^{\infty}\sum_{i=1}^{N}\mathbbm{1}\{c(\tau_{n}^{i})>0\}. \nonumber
-\end{align}
+To make this intuition precise, we set
+$\delta = \frac{\MinProb}{2 \TieDensity}$,
+and $x = \frac{\delta}{2 \Diam d}$.
+The cutoff point between early and late phases is now set to
+$\EvenLaterPhase = \max(50, \frac{92.16 \sigma^4}{x^4}, \frac{2}{\MinProb})$.
+Consider the \Kth{s} pull of an arm $i$, for $s \geq \EvenLaterPhase$.
+If this pull occurs before phase $s$, it was definitely not incentivized.
+So we condition on the pull occurring in phase $s$,
+and let $\tau$ be the time step when this pull occurred; notice that
+this means that this must be the first pull of arm $i$ in phase $s$.
+We can now apply Corollary~\ref{cor:right-choice}
+with this choice of $x$,
+and obtain that with probability at least 
+$1 - 24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$,
+all agent types \AgV with
+$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}})
+> 2\Diam d x = \delta$
+will pull their best arm \Best{\AgV}.
+\dkcomment{We are losing a factor \ARMNUM here.
+We already took a union bound over all arms in the lemma, and
+we now apply it only to one arm, then sum over all arms.}
 
-The cumulative expected number of payments is bounded above by:
-\begin{align}
-&E\left[\sum_{t=1}^{\infty}\mathbbm{1}\{c(t)>0\}\right] \nonumber \\
-=&\sum_{n=1}^{\infty}\sum_{i=1}^{N}P(c(\tau_{n}^{i})>0) \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}P\left(\exists i,j:|u_{i}^{j}-u_{i,\tau_{n}^{i}}^{j}|>\frac{p^{-1}(\frac{p}{2})}{2 \Diam d}\right)+\sum_{n=1}^{n_1}\ARMNUM \nonumber \\
-\leq &\sum_{n=n_{1}}^{\infty}\sum_{i=1}^{N}24 \ARMNUM d
-       \exp\left(\frac{-1.8 n\delta_{0}^2}{64 \Diam^2 d^2\sigma^2}\right) +\sum_{n=1}^{n_1}\ARMNUM \nonumber \\
-\leq & \sum_{n=n_{1}}^{\infty}24Nm \exp\left(\frac{-1.8 n\delta_{0}^2}{64\Diam^2 d^2\sigma^2}\right)\times \ARMNUM+\sum_{n=1}^{n_1}\ARMNUM \nonumber  \\
-\leq&24 \ARMNUM^2 d \frac{1}{\exp(\frac{1.8\delta_{0}}{64\Diam^2 d^2\sigma^2})-1} + Nn_1, \nonumber
-\end{align}
+By Lemma~\ref{lem:sdelta}, the \emph{total} measure of agents (across
+all arms) whose best and second-best arm differ in utility by less
+than $\delta$ is at most $\TieDensity \delta = \frac{\MinProb}{2}$.
+In particular, this bound holds for agents whose best arm is $i$.
+By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
+as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
+has arm $i$ as their preferred arm by at least $\delta$ over any other
+arm $i'$.
+In the high-probability event, all such agents would myopically pull
+the arm $i$, and as a result, in the high-probability event,
+arm $i$ is not payment-eligible.
 
-Thus, we know the expected number of payments is bounded above by $O(\ARMNUM^2)$.
-
+Thus, for any phase $s \geq \EvenLaterPhase$
+Algorithm~\ref{alg:basic-incentivizing} incentivizes any given arm $i$
+with probability at most
+$24 \ARMNUM d \cdot \exp \left(
+  -\frac{1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+\right)$.
+Summing over all arms and phases $s$,
+and adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
+the first \EvenLaterPhase phases, 
+the expected total number of arm incentivizations is at most
+\begin{align*}
+\ARMNUM \EvenLaterPhase
+  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
+    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)}
+& = O\left( \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+  + \frac{\ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} \right).
+\end{align*}
+\dkcomment{It seems like with our choice of $x$ (which may be
+  unavoidable), we get quite large factors, in particular with the
+  fourth power.
+  Also, it would be nice if we could simplify the $\frac{1}{1-\exp()}$
+  term. Unfortunately, I think that the inequality goes the wrong way
+  for applying the standard $\exp(-x) \geq 1-x$ bound.}
 \end{proof}
 
+It would be desirable to simply identify a constant upper bound on the
+payment made each time.
+Unfortunately, while the agent types are drawn from a bounded support,
+the noise in arm locations is not;
+hence, with small probability, arm locations may be grossly
+misestimated, resulting in high incentive payments.
+As a result, the actual analysis of the total payment is significantly more
+intricate, and hence,
+the proof of Theorem~\ref{rst:budget} is given in the appendix.
+
 \subsection{Bounding the Total Regret}
+\dkcomment{Edited up to here so far.}
 
 Now we are ready to prove our second main result, Theorem~\ref{rst:regret}.
+
+We use $R = \max_{\AgV, i,j} \AgV \cdot (u_i - u_j)$ to denote the
+maximum regret that can be incurred at each time.
+Assumption~\ref{A2} implies that the maximum regret or payment
+incurred in any one round is finite.
+
+As we can see later in our proof, we only need $\max_{i,j}\limsup_{y\rightarrow 0^{+}}\frac{F_{i,j}(y)}{y}$ to be finite.
+Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm.
 

### 2018-02-05 problem_setting.tex
finished edits up to payment

@@
 We let
-$\Best{\AgentV{}} \in \argmax_i \AgentV{} \cdot \ArmV{i}$
+$\Best{\AgV} \in \argmax_i \AgV \cdot \ArmV{i}$
 and
-$ \Second{\AgentV{}} \in \argmax_{i \neq \Best{\AgentV{}}} \AgentV{} \cdot \ArmV{i}$
+$ \Second{\AgV} \in \argmax_{i \neq \Best{\AgV}} \AgV \cdot \ArmV{i}$
 denote the (indices of) the best and second-best arms for an agent
-with attribute vector \AgentV{};
+with attribute vector \AgV;
 \dkdelete{breaking ties uniformly at random}.
@@
 
-Let $\MinProb = \min_{i} \Prob[\AgentDist]{\Set{\AgentV{}}{\Best{\AgentV{}} = i}}$
+Let $\MinProb = \min_{i} \Prob[\AgentDist]{\Set{\AgV}{\Best{\AgV} = i}}$
 denote the minimum (over all arms) fraction of users that prefer any
@@
 
-Let 
-\begin{align*}
-\FirstTwo{i}{i'}
-  & = \Set{\AgentV{}}{\Best{\AgentV{}} = i, \Second{\AgentV{}} = i'}
-\end{align*}
+Let $\FirstTwo{i}{i'} = \Set{\AgV}{\Best{\AgV} = i, \Second{\AgV} = i'}$
 be the set of agent attribute vectors whose best arm is $i$ and
@@
 (or cumulative mass function if $\AgentDist(\cdot)$ is a discrete distribution)
-of $(\ArmV{i}-\ArmV{i'}) \cdot AgentV{}$,
-conditioned on $\theta \in \Omega_{i,j}$.
+of $(\ArmV{i}-\ArmV{i'}) \cdot \AgV$,
+conditioned on $\AgV \in \Omega_{i,j}$.
 In words, $F_{i,i'}$ is the distribution of the \emph{strength} of the
@@
 that is, there exists a constant \TieDensity such that
-for all pairs $i,i$ of arms and all $z \in \R^+$,
+for all pairs $i,i'$ of arms and all $z \in \R^+$,
 we have $F_{i,i'}(z) \leq \TieDensity \cdot z$.

### 2018-02-06 algorithm.tex
partial edits on regret proof

@@
 
-With this additional notation, we now prove several lemmas.
-First, based on Assumption~\ref{A1}, we have the following bound for $S(\delta)$.
-
+\dkcomment{Keeping this around for now.}
 Notation: $t_s$ is end time for phase $s$.
@@
   for applying the standard $\exp(-x) \geq 1-x$ bound.}
+
+\dkcomment{I'm leaving in all the dependencies on ``constant''
+  parameters for now. We can decide later which ones to absorb into
+  big-$O$.}
 \end{proof}
@@
 \subsection{Bounding the Total Regret}
-\dkcomment{Edited up to here so far.}
-
-Now we are ready to prove our second main result, Theorem~\ref{rst:regret}.
-
-We use $R = \max_{\AgV, i,j} \AgV \cdot (u_i - u_j)$ to denote the
-maximum regret that can be incurred at each time.
-Assumption~\ref{A2} implies that the maximum regret or payment
-incurred in any one round is finite.
+In bounding the total regret, because agents' types are from a compact
+set by Assumption~\ref{A2}, the maximum regret in any one round is
+bounded by a constant.
+We use $\MAXR = \max_{\AgV, i,i'} \AgV \cdot (\ArmV{i} - \ArmV{i'})$
+to denote this constant upper bound on the maximum regret that can be
+incurred in any one time step.
 
@@
 \begin{proof}
-For regret incurred in the first $n_0$ round, it is bounded above by $\sum_{n=1}^{n_{0}}NRn$.
+As before, let $\LatePhase = \max (50, \frac{92.16 \sigma^4}{x^4})$.
+By Lemma~\ref{lem:phase-length}, each phase $s = 1, \ldots, \LatePhase$
+in expectation lasts at most $\ARMNUM s$ steps,
+so the total expected regret incurred in these phases is at most
+$\sum_{s=1}^{\LatePhase} \ARMNUM \MAXR s = O(\ARMNUM \MAXR \LatePhase^2)$.
 
-For regret incurred after the first $n_0$ round, it has two different components: the regret incurred when we let the agents play myopically and the regret incurred when we incentivize the agents.
-Using Lemma~\ref{lemma:numP}, the expected regret incurred when we incentivize the agents is bounded above by: $\left[24\ARMNUM^2 d \frac{1}{\exp(\frac{1.8\delta_{0}}{64\Diam^2 d^2\sigma^2})-1} + Nn_1\right]R$.
+Regret incurred after the first \LatePhase phases can arise in two ways:
+(1) an agent was incentivized to pull a suboptimal arm, or
+(2) an agent myopically pulled a suboptimal arm.
+By Lemma~\ref{lem:numP}, Algorithm~\ref{alg:basic-incentivizing}
+incentivizes agents at most 
+$O \left( \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+  + \frac{\ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} \right)$
+times in expectation, each time causing regret at most \MAXR,
+for a total expected regret of at most
+$O \left( \frac{\MAXR \ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} \right)$.
+For the rest of the proof, we focus on the regret incurred when agents
+pull arms myopically and make mistakes.
+
+We distinguish two types of agents, based on whether their preference
+for their best arm over the second-best arm is ``large'' or ``small''.
+To be more precise, we will define (with hindsight) a phase-dependent
+cutoff $g(s)$, and for any agent type $\AgV \in \FirstTwo{i}{i'}$,
+distinguish whether $\AgV \cdot (\ArmV{i} - \ArmV{i'}) \geq g(s)$ or not.
+
+By Lemma~\ref{lem:sdelta}, the total measure of agents whose
+preference is ``small'' in this sense is at most
+$\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$ for all $\delta$.
+\dkcomment{Put here whatever upper bound we use for these agents.}
+
+\dkcomment{I edited up to this point. Some notation has been replaced
+  below with query-replace, but not all of it.}
 
@@
 \begin{itemize}
-\item For those users whose utility difference between their best and the second best arm is greater than $f(t)$: we define a sequence of stopping time $\tau_{n}^{k}$ to be the $k^{th}$ time period in the $n^{th}$ round.
-For $k>t_{n+1}-t_{n}$, we define $\tau_{n}^{k}=\infty$.
-For $\tau_{n}^{k}=t$, the probability of these users making a mistake is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)$ and the expected regret is bounded above by $24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)\times R$.
-We denote the regret incurred by these agents as $r_1(\tau_{n}^{k})$.
-For $k>t_{n+1}-t_{n}$, we define $r_1(\tau_{n}^{k})=0$.
-\item For those user whose utility difference between their best and the second best arm is smaller than $f(t)$: this happens with probability $S(f(t))$ at each time and regret is bounded above by $S(f(t)) \times f(t)=Mf(t)^2$.
+\item For those users whose utility difference between their best and
+the second best arm is greater than $g(t)$:
+we define a sequence of stopping time $\tau_{s}^{k}$ to be the \Kth{k}
+time period in the \Kth{s} phase.
+For $k > t_{s+1}-t_{s}$, we define $\tau_{s}^{k}=\infty$.
+For $\tau_{s}^{k}=t$, the probability of these users making a mistake
+is bounded above by
+$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)$,
+and the expected regret is bounded above by
+$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR$.
+We denote the regret incurred by these agents by $r_1(\tau_{s}^{k})$.
+For $k > t_{s+1}-t_{s}$, we define $r_1(\tau_{s}^{k})=0$.
+
+\item For those user whose utility difference between their best and
+the second best arm is smaller than $g(t)$:
+this happens with probability \AlmostTied{g(t)} at each time,
+and the regret is bounded above by
+$\AlmostTied{g(t)} \cdot f(t) \leq \TieDensity f(t)^2$.
 We denote the regret incurred by these agents as $r_2(t)$.
@@
 
-Thus, the cumulative expected regret incurred up to time $T$ when we let the agent play myopically is bounded above by:
+Thus, the cumulative expected regret incurred up to time $T$ when we
+let the agent play myopically is bounded above by:
 \begin{align}
-&E\left[\sum_{t=1}^{T}r(t)\right] \nonumber \\
-=&E\left[\sum_{t=1}^{t_{n_{0}}} r(t) + \sum_{t=t_{n_{0}}}^{T}(r_1(t)+r_2(t))\right]  \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{t=t_{n}}^{t_{n+1}-1}r_1(t)\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-=& \sum_{n=1}^{n_{0}}NRn + E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\right]+ E\left[\sum_{t=1}^{T}r_2(t)\right]. \label{chap5:equ:r1}
+\Expect{\sum_{t=1}^{T}r(t)} 
+& = \Expect{\sum_{t=1}^{t_{\LatePhase}} r(t) + \sum_{t=t_{\LatePhase}}^{T}(r_1(t)+r_2(t))}  \nonumber \\
+& \leq \sum_{s=1}^{\LatePhase} \ARMNUM \MAXR s
+     + \Expect{\sum_{s=\LatePhase}^{T}\sum_{t=t_{s}}^{t_{s+1}-1}r_1(t)}
+     + \Expect{\sum_{t=1}^{T}r_2(t)} \nonumber \\
+& = \sum_{s=1}^{\LatePhase} \ARMNUM \MAXR s
+     + \Expect{\sum_{s=\LatePhase}^{T} \sum_{k=1}^{\infty}r_1(\tau_{s}^{k})}
+     + \Expect{\sum_{t=1}^{T}r_2(t)}. \label{chap5:equ:r1}
 \end{align}

### 2018-02-06 lower_bound.tex
edited lower bound up to first integral

@@
-\section{Lower Bound $\Omega(\log(T))$}
-\label{sec:lb}
+\newcommand{\dd}{\mathrm{d}}
+\newcommand{\quarter}{\ensuremath{\frac{1}{4}}\xspace}
 
-In this section, we assume $\theta$ follows a continuous distribution $F(\cdot)$.
-We provide an example to show the best possible lower bound is $\Omega(\log(T))$ regardless of the incentivizing strategy.
+\section{A Lower Bound of $\Omega(\log(T))$} \label{sec:lb}
 
-Suppose we have two arms.
-Arm $1$ has attribute vector $(0,0)$ and arm $2$ has attribute vector $(0,1)$.
-We assume the users' preference are uniformly distributed on the two dimensional unit circle.
-If the user knows the exact attribute vectors for both arms, then the users with preference on the bottom half circle will choose arm $1$ and the users with preference on the top half circle will choose arm $2$.
-It is easy to check that all our assumptions hold true in this example.
+We saw in Corollary~\dkcomment{assign a label and insert here} that
+when agent preferences for their best arm are sufficiently clear,
+in the sense that $\TieDensity = 0$, the regret of
+Algorithm~\ref{alg:basic-incentivizing} is bounded by a constant.
+One may conjecture that this should hold more generally,
+in that that regret of the (fewer and fewer) agents on the boundary
+between close arms should go to 0, while their fraction also goes to 0.
+In this section, we establish a lower bound,
+showing that even in very simple settings, a (logarithmic) dependence
+on $T$ is typicaly unavoidable for \emph{any} incentivization strategy.
 
-Consider the following algorithm: at each step, let the agents play myopically; however, they are going to see the noisy rewards for both arms.
+We consider an instance with two arms,
+whose attribute vectors are $(0,0)$ and $(0,1)$, respectively.
+Agents types are distributed uniformly on the two-dimensional unit circle%
+\footnote{While our model technically assumed that all agent coordinates are
+non-negative, we could simply shift the unit circle.
+The present choice is solely for ease of notation.}  
+$\Set{\AgV}{|| \AgV ||_2 \leq 1}$.
+Because $\AgV \cdot (0,0) = 0$ and $\AgV \cdot (0,1) = \Ag{2}$,
+\dkcomment{modify macro to do this correctly}
+the best choice for agent \AgV is arm $(0,1)$ iff $\Ag{2} > 0$,
+i.e., the top half of the unit circle prefers the arm $(0,1)$,
+and the bottom half prefers the arm $(0,0)$.
 
-To lower bound the regret, we assume that the agents already know the true attribute vector for arm $1$.
-Without loss of generality, denote $u_{2,t} = (0,1)+(z_{t,1},z_{t,2}) = (0,1)+ (N(0,1/t),N(0,1/t))$ to be the estimate attribute vector for arm $2$ (Without loss of generality, we assume the variance for the noise is $1$).
+Since we are proving a lower bound, we give the algorithm the
+following extra two advantages:
+(1) there is no noise in the observations of the arm $(0,0)$,
+and all agents know its location deterministically.
+(2) in each time step, regardless of which arm is pulled, the algorithm
+and all agents observe a pull from arm $(0,1)$.
+For simplicity of notation, we set the standard deviation of the arm
+$(0,1)$ to $\sigma = 1$; different values only lead to a scaling of
+the results.
 
-Since $(z_{t,1}, z_{t,2})$ is symmetric around $(0,0)$, we know
+Under these advantages, myopic play is clearly optimal, so it suffices
+to bound the regret of the myopic algorithm which never incentivizes
+agents. \dkcomment{This feels ``clear'', but is it?}
 
-\begin{align}
-&E[r(t)] \nonumber \\
-= &E[r(t) | z_{t,1}>0,z_{t,2}>0] \times P(z_{t,1}>0,z_{t,2}>0) + E[r(t) |z_{t,1}>0,z_{t,2}<0] \times P(z_{t,1}>0,z_{t,2}<0) \nonumber \\
-&+E[r(t) | z_{t,1}<0,z_{t,2}>0] \times P(z_{t,1}<0,z_{n,2}>0) + E[r(t) |z_{t,1}<0,z_{t,2}<0] \times P(z_{t,1}<0,z_{t,2}<0) \nonumber \\
-\geq & 0.25 \times E[r(t) | z_{t,1}>0, z_{t,2}>0]. \nonumber
-\end{align}
+Because a pull of arm $(0,1)$ is observed in each time step,
+after $t$ rounds, the estimate \ArmEV{t+1}{(0,1)} is of the form
+$(0,1) + (\Noise[t]{1}, \Noise[t]{2})$,
+where $\Noise[t]{1} \sim \Normal{0}{1/t}$
+and $\Noise[t]{2} \sim \Normal{0}{1/t})$.
+We lower-bound the regret in step $t$ by focusing on the event that
+both normal noise coordinates are non-negative,
+which by symmetry has probability \quarter:
+
+\begin{align*}
+\Expect{\Regret{t}} 
+  & \geq \ExpectC{\Regret{t}}{\Noise[t]{1} > 0, \Noise[t]{2} > 0}
+         \cdot \Prob{\Noise[t]{1} > 0, \Noise[t]{2} > 0}
+  \; = \; \quarter \ExpectC{\Regret{t}}{\Noise[t]{1} > 0, \Noise[t]{2} > 0}.
+\end{align*}
+
+For the moment, focus on some time step $t$,
+and write $\NoiseV = \NoiseV[t]$.
+Then, there are two types of agents who pull the wrong arm and incur
+regret:
+\begin{enumerate}
+\item If $\Ag{2} > 0$ and $\Ag{1} \Noise{1} + \Ag{2} (1+\Noise{2}) < 0$
+then \Ag should pull $(0,1)$,
+but will wrongly pull $(0,0)$ and incur regret \Ag{2}.
+The region
+$\Ag{2} > 0$ and $\Ag{1} < \frac{-(1+\Noise{2})}{\Noise{1}} \cdot \Ag{2}$
+defines a wedge.
+For any particular value of \Ag{2},
+the length of the interval of corresponding \Ag{1} is
+\begin{align*}
+  \sqrt{1-\Ag{2}^2} - \frac{1+\Noise{2}}{\Noise{1}} \cdot \Ag{2}
+  & \geq 1 - \Ag{2} - \frac{1+\Noise{2}}{\Noise{1}} \cdot \Ag{2}
+  \; = \; 1 - \frac{1+\Noise{1}+\Noise{2}}{\Noise{1}} \cdot \Ag{2}.
+\end{align*}
+
+\item If $\Ag{2} < 0$ and $\Ag{1} \Noise{1} + \Ag{2} (1+\Noise{2}) > 0$,
+then \Ag should pull $(0,0)$,
+but will wrongly pull $(0,1)$ and incur regret $-\Ag{2}$.
+This region and its regret are rotationally symmetric to the previous
+case.
+\end{enumerate}
+
+Hence, the expected regret for given \Noise{1}, \Noise{2} is at least
+\begin{align*}
+  2 \int_0^{\frac{\Noise{1}}{1+\Noise{1}+\Noise{2}}}
+  \left( 1 - \frac{1+\Noise{1}+\Noise{2}}{\Noise{1}} \cdot \Ag{2} \right)
+  \cdot \Ag{2} \cdot \frac{1}{\pi} \dd \Ag{2}
+& =
+\frac{1}{\pi} \cdot \left(\frac{1+\Noise{1}+\Noise{2}}{\Noise{1}}\right)^2
+- \frac{2}{3 \pi} \cdot \left(\frac{1+\Noise{1}+\Noise{2}}{\Noise{1}}\right)^2
+\\ & =
+\frac{1}{3 \pi} \cdot \left(\frac{1+\Noise{1}+\Noise{2}}{\Noise{1}}\right)^2.
+\end{align*}
+
+\dkcomment{I edited up to here. Waiting for some feedback about
+  whether my calculations are way off.
+  I did use one bound of $\sqrt{1-\Ag{2}^2} \geq 1-\Ag{2}$, but since
+  we are looking at small values of \Ag{2}, I cannot imagine that this
+  lost much. One can compute the integral without this simplification,
+  but it will be quite a bit uglier.}
 

### 2018-02-06 algorithm.tex

@@
 for their best arm over the second-best arm is ``large'' or ``small''.
-To be more precise, we will define (with hindsight) a phase-dependent
-cutoff $g(s)$, and for any agent type $\AgV \in \FirstTwo{i}{i'}$,
-distinguish whether $\AgV \cdot (\ArmV{i} - \ArmV{i'}) \geq g(s)$ or not.
+To be more precise, we will define (with hindsight) a time-dependent
+cutoff $g(t)$, and for any agent type $\AgV \in \FirstTwo{i}{i'}$,
+distinguish whether $\AgV \cdot (\ArmV{i} - \ArmV{i'}) \geq g(t)$ or not.
 
@@
 preference is ``small'' in this sense is at most
-$\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$ for all $\delta$.
+$\AlmostTied{g(t)} \leq \TieDensity \cdot g(t)$ for all $t$.
 \dkcomment{Put here whatever upper bound we use for these agents.}
@@
 
-For the regret incurred when we let the agents play myopically at time $t\geq t_{n_0}$, it consists of the following two components:
+For the regret incurred when we let the agents play myopically at time $t$ in the $s\geq s_0$ phase, it consists of the following two components:
 \begin{itemize}
@@
 time period in the \Kth{s} phase.
-For $k > t_{s+1}-t_{s}$, we define $\tau_{s}^{k}=\infty$.
+For $k > t_{s}-t_{s-1}$, we define $\tau_{s}^{k}=\infty$.
 For $\tau_{s}^{k}=t$, the probability of these users making a mistake
@@
 We denote the regret incurred by these agents by $r_1(\tau_{s}^{k})$.
-For $k > t_{s+1}-t_{s}$, we define $r_1(\tau_{s}^{k})=0$.
+For $k > t_{s}-t_{s-1}$, we define $r_1(\tau_{s}^{k})=0$.
 
@@
 and the regret is bounded above by
-$\AlmostTied{g(t)} \cdot f(t) \leq \TieDensity f(t)^2$.
+$\AlmostTied{g(t)} \cdot \MAXR \leq \TieDensity\MAXR\cdot f(t)$.
 We denote the regret incurred by these agents as $r_2(t)$.
@@
 \begin{align}
-\Expect{\sum_{t=1}^{T}r(t)} 
-& = \Expect{\sum_{t=1}^{t_{\LatePhase}} r(t) + \sum_{t=t_{\LatePhase}}^{T}(r_1(t)+r_2(t))}  \nonumber \\
+\Expect{\sum_{t=1}^{T}\Regret{t}} 
+& = \Expect{\sum_{t=1}^{t_{\LatePhase}} \Regret{t} + \sum_{t=t_{\LatePhase}}^{T}(r_1(t)+r_2(t))}  \nonumber \\
 & \leq \sum_{s=1}^{\LatePhase} \ARMNUM \MAXR s
@@
 \begin{align}
-& E\left[\sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\right] \nonumber\\
-= &  \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})] \nonumber \\
-= &  \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}(E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty)+E[r_1(\tau_{n}^{k})|\tau_{n}^{k}=\infty]\times P(\tau_{n}^{k}=\infty)) \nonumber \\
-= & \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty), \nonumber
+& E\left[\sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\right] \nonumber\\
+= &  \sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{s}^{k})] \nonumber \\
+= &  \sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}(E[r_1(\tau_{s}^{k})|\tau_{s}^{k}<\infty]\times P(\tau_{s}^{k}<\infty)+E[r_1(\tau_{s}^{k})|\tau_{s}^{k}=\infty]\times P(\tau_{s}^{k}=\infty)) \nonumber \\
+= & \sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{s}^{k})|\tau_{s}^{k}<\infty]\times P(\tau_{s}^{k}<\infty), \nonumber
 \end{align}
@@
 \begin{align}
-\eqref{chap5:equ:r1}= & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{n}^{k})|\tau_{n}^{k}<\infty]\times P(\tau_{n}^{k}<\infty) + E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=n_{0}}^{T}\left[\sum_{k=1}^{\infty}24Nm\exp\left(-\frac{1.8n f(\tau_{n}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right) R\times P(\tau_{n}^{k}<\infty) \right]+ \sum_{k=1}^{T}Mf(t)^2 \nonumber \\
-\leq & \sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 \Diam^2 d^2\sigma^2}\right) R \times Nn+ \sum_{t=1}^{T}Mf(t)^2. \label{chap5:equ:regret}
+\eqref{chap5:equ:r1}= & \sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{s}^{k})|\tau_{s}^{k}<\infty]\times P(\tau_{s}^{k}<\infty) + E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
+\leq & \sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=\LatePhase}^{T}\left[\sum_{k=1}^{\infty}24\ARMNUM d\exp\left(-\frac{1.8s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right) R\times P(\tau_{s}^{k}<\infty) \right]+ \sum_{t=1}^{T}\TieDensity\MAXR \cdot f(t) \nonumber \\
+\leq & \sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=1}^{T} 24 \ARMNUM  d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right) \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\MAXR\cdot f(t).
+\label{chap5:equ:regret}
 \end{align}
@@
 \begin{align}
-&\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 \Diam^2 d^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\
-+ & 24\ARMNUM^2 d \frac{1}{e^{\frac{1.8\delta_{0}}{64\Diam^2 d^2\sigma^2}}-1}R+\ARMNUM\left(\max\left\{n_{0},\frac{2}{p}\right\}\right)R. \nonumber
+&\sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\MAXR \cdot f(t)  +\nonumber \\
+&O \left( \frac{\MAXR \ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} \right). \nonumber 
 \end{align}
@@
 \begin{align}
-\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 \Diam^2 d^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2. \label{equ:regret}
+\sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\MAXR \cdot f(t). \label{equ:regret}
 \end{align}
@@
 \begin{align}
-&\sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 \Diam^2 d^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{T}Mf(t)^2 \nonumber \\ 
-\leq & \sum_{n=1}^{T} 24\ARMNUM^2 mnR \exp\left(-2\log(T)\right)  + \frac{128\Diam^2 d^2\sigma^2 \TieDensity\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{n} \nonumber \\
+&\sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\MAXR \cdot f(t) \nonumber \\ 
+\leq & \sum_{s=1}^{T} 24\ARMNUM^2 d s \MAXR \exp\left(-2\log(T)\right)  + \frac{128\Diam^2 d^2\sigma^2 \TieDensity\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{t} \nonumber \\
 \leq &  24\ARMNUM^2 d R\frac{T(T-1)}{2T^2}  + 71.12 \Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1) \nonumber \\

### 2018-02-06 problem_setting.tex

@@
 \dkcomment{Do we need this definition here?}
-We call time $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$ the
+We call time $t_{n}=\min_{t}\{\forall i, \NumPull{t}{i} \geq n\}$ the
 \emph{starting point of the $n^{th}$ round}.
@@
 of $(\ArmV{i}-\ArmV{i'}) \cdot \AgV$,
-conditioned on $\AgV \in \Omega_{i,j}$.
+conditioned on $\AgV \in \Omega_{i,i^{'}}$.
 In words, $F_{i,i'}$ is the distribution of the \emph{strength} of the

### 2018-02-06 algorithm.tex
editted the regret proof

@@
 
-\begin{align*}
+\begin{align}
 \AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmEV{\tau}{i})
@@
 + \AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i})
-+ \AgV \cdot (\ArmV{i} - \ArmEV{\tau}{i})\\
++ \AgV \cdot (\ArmV{i} - \ArmEV{\tau}{i}) \nonumber\\
 & > -\Diam d x + 2 \Diam d x - \Diam d x
-\; = \; 0,
-\end{align*}
+\; = \; 0, \label{equ:choice}
+\end{align}
 which means that the agent with type \AgV will in fact choose
@@
 \begin{itemize}
-\item For those users whose utility difference between their best and
-the second best arm is greater than $g(t)$:
-we define a sequence of stopping time $\tau_{s}^{k}$ to be the \Kth{k}
+\item For those user who will pull an arm that occurs regret greater than $g(t)$: if all arms estimation errors are within $\frac{g(t)}{2\Diam d}$, then based on the same argument as \eqref{equ:choice}, this will never happen.
+We define a sequence of stopping time $\tau_{s}^{k}$ to be the \Kth{k}
 time period in the \Kth{s} phase.
 For $k > t_{s}-t_{s-1}$, we define $\tau_{s}^{k}=\infty$.
-For $\tau_{s}^{k}=t$, the probability of these users making a mistake
-is bounded above by
+For $\tau_{s}^{k}=t$, the probability of users occur regret greater than $g(t)$ is bounded above by
 $24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)$,
@@
 
-\item For those user whose utility difference between their best and
-the second best arm is smaller than $g(t)$:
-this happens with probability \AlmostTied{g(t)} at each time,
+\item For those user who will pull an arm that occurs regret smaller than $g(t)$: if the user pulls his/her best arm, no regret occurs.
+Otherwise, we know his/her utility difference between best and second best arm is smaller than $g(t)$.
+Further, we know this happens with probability \AlmostTied{g(t)} at each time,
 and the regret is bounded above by
-$\AlmostTied{g(t)} \cdot \MAXR \leq \TieDensity\MAXR\cdot f(t)$.
+$\AlmostTied{g(t)} \cdot g(t) \leq \TieDensity \cdot (g(t))^2$.
 We denote the regret incurred by these agents as $r_2(t)$.
@@
 \eqref{chap5:equ:r1}= & \sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{s}^{k})|\tau_{s}^{k}<\infty]\times P(\tau_{s}^{k}<\infty) + E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=\LatePhase}^{T}\left[\sum_{k=1}^{\infty}24\ARMNUM d\exp\left(-\frac{1.8s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right) R\times P(\tau_{s}^{k}<\infty) \right]+ \sum_{t=1}^{T}\TieDensity\MAXR \cdot f(t) \nonumber \\
-\leq & \sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=1}^{T} 24 \ARMNUM  d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right) \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\MAXR\cdot f(t).
+\leq & \sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=\LatePhase}^{T}\left[\sum_{k=1}^{\infty}24\ARMNUM d\exp\left(-\frac{1.8s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right) R\times P(\tau_{s}^{k}<\infty) \right]+ \sum_{t=1}^{T}\TieDensity\cdot (g(t))^2 \nonumber \\
+\leq & \sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=1}^{T} 24 \ARMNUM  d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right) \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\cdot (g(t))^2.
 \label{chap5:equ:regret}
@@
 \begin{align}
-&\sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\MAXR \cdot f(t)  +\nonumber \\
+&\sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity \cdot (g(t))^2  +\nonumber \\
 &O \left( \frac{\MAXR \ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
@@
 \begin{align}
-\sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\MAXR \cdot f(t). \label{equ:regret}
+\sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity \cdot (g(t))^2. \label{equ:regret}
 \end{align}
 
-If we set $f^2(t)=\frac{2\log(T)\times 64\Diam^2 d^2\sigma^2}{1.8t}$, then
+If we set $g^2(t)=\frac{2\log(T)\times 64\Diam^2 d^2\sigma^2}{1.8t}$, then
 \begin{align}
-&\sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\MAXR \cdot f(t) \nonumber \\ 
+&\sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\cdot (g(t))^2 \nonumber \\ 
 \leq & \sum_{s=1}^{T} 24\ARMNUM^2 d s \MAXR \exp\left(-2\log(T)\right)  + \frac{128\Diam^2 d^2\sigma^2 \TieDensity\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{t} \nonumber \\
@@
 The proof of this corollary is similar to the proof of Theorem~\ref{rst:regret}.
-If we set $f^2(t)=\frac{2\log(T)\times 64\Diam^2 d^2\sigma^2}{1.8t}$, then there exists a $t_{0}$ such that for $t>t_{0}$, $S(f(t))=0$.
+If we set $g^2(t)=\frac{2\log(T)\times 64\Diam^2 d^2\sigma^2}{1.8t}$, then there exists a $t^{0}$ such that for $t>t_{0}$, $q(g(t))=0$.
 Thus, similar to equation~\eqref{equ:regret}, we know the cumulative expected regret when we let the agents play myopically is bounded above by
 \begin{align}
-\sum_{n=1}^{n_{0}}NRn + \sum_{n=1}^{T} 24Nm\exp\left(-\frac{1.8n f(n)^2}{64 \Diam^2 d^2\sigma^2}\right)\times R \times Nn+ \sum_{t=1}^{t_{0}}Mf(t)^2 \nonumber
+\sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{t^{0}}\TieDensity g(t)^2 \nonumber
 \end{align}

### 2018-02-06 algorithm.tex
almost finished regret proof

@@
 \end{theorem}
-
-\dkcomment{Keeping this around for now.}
-Notation: $t_s$ is end time for phase $s$.
 
@@
   be over the past history, but not the current agent.}
-all agent types $\AgV = \AgentV{\tau}$ with
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > 2\Diam d x$
-will pull their best arm, i.e.,
-$\argmax \SET{\AgV \cdot \ArmEV{\tau}{i}} = \Best{\AgV}$
+an agent of type $\AgV = \AgentV{\tau}$ 
+will not pull a highly suboptimal arm, i.e., an arm $i$ with 
+$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
 \end{corollary}
@@
 Consider any agent type $\AgV = \AgentV{\tau}$ at the (random) time
-$\tau$ such that
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > 2\Diam d x$.
-Let $i \neq \Best{\AgV}$ be any other arm;
-its true reward is much smaller than from the best arm:
+$\tau$.
+Let $i \neq \Best{\AgV}$ be any arm
+with much smaller true reward than the best arm:
 $\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
@@
 \end{align}
-which means that the agent with type \AgV will in fact choose
-the optimal arm in the high-probability event.
+which means that the agent with type \AgV will not pull arm $i$
+under the high-probability event.
 \end{proof}
@@
 
-As we can see later in our proof, we only need $\max_{i,j}\limsup_{y\rightarrow 0^{+}}\frac{F_{i,j}(y)}{y}$ to be finite.
-Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm.
+\dkcomment{The following paragraph is from Bangrui's version. It may
+  move to an earlier section, go away, or become a part somewhere.}
+As we can see later in our proof, we only need
+$\max_{i,j}\limsup_{y\rightarrow 0^{+}}\frac{F_{i,j}(y)}{y}$ to be
+finite.
+Intuitively, Assumption~\ref{A1} states that there are not many agents
+who are indifferent between their best arm and the second best arm.
 
@@
 
-We distinguish two types of agents, based on whether their preference
-for their best arm over the second-best arm is ``large'' or ``small''.
+We distinguish between agents incurring large regret
+(which requires severe misestimates of arm locations;
+such misestimated are exponentially unlikely to occur), 
+and agents incurring small positive regret,
+which requires these agents to be almost tied in their preference for
+the best arm.
 To be more precise, we will define (with hindsight) a time-dependent
-cutoff $g(t)$, and for any agent type $\AgV \in \FirstTwo{i}{i'}$,
-distinguish whether $\AgV \cdot (\ArmV{i} - \ArmV{i'}) \geq g(t)$ or not.
+cutoff $g(t)$, and consider a regret exceeding $g(t)$ large.
 
-By Lemma~\ref{lem:sdelta}, the total measure of agents whose
-preference is ``small'' in this sense is at most
-$\AlmostTied{g(t)} \leq \TieDensity \cdot g(t)$ for all $t$.
-\dkcomment{Put here whatever upper bound we use for these agents.}
+We first consider agents \AgV incurring positive regret less than $g(t)$.
+The second-best arm \Second{\AgV} of \AgV must satisfy
+$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(t)$.
+By Lemma~\ref{lem:sdelta}, the total measure of such agents
+is $\AlmostTied{g(t)} \leq \TieDensity \cdot g(t)$,
+and each incurs regret at most $g(t)$.
+Summing over all time steps, the total regret from such agents is at most
+$\sum_{t = 1}^T \TieDensity \cdot g^2(t)$.
 
-\dkcomment{I edited up to this point. Some notation has been replaced
-  below with query-replace, but not all of it.}
+To bound the regret incurred in time steps with large regret,
+let the random variable $t_s$ be the final time step in phase $s$,
+for each $s$.
+\dkcomment{Is $t_s$ better or $T_s$?}
+Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
+time step in the \Kth{s} phase,
+with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
+i.e., $k > t_{s}-t_{s-1}$.
+For $t = \tau_{s}^{k}$, by Corollary~\ref{cor:right-choice}
+(applied with $x = \frac{g^2(\tau_s^k)}{4 \Diam^2 d^2}$),
+the probability of incurring regret exceeding $g(t)$ is at most
+$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)$.
+Because each arm must have been pulled at least $s$ times by the time
+the algorithm reaches phase $s$,
+\dkcomment{Really only $s-1$; we have to be careful with those $\pm 1$.}
+we can bound $\tau_{s}^{k} \geq s$.
+\dkcomment{We could bound it by $\ARMNUM s$, if that helps get
+  slightly better bounds.}
+Because the regret never exceeds \MAXR,
+the expected (large) regret for the \Kth{k} time step of phase $s$
+is bounded above by
+$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(s)^2}{64 \Diam^2 d^2\sigma^2}\right) \cdot \MAXR$.
+Summing over all time steps $t$, we get that the total regret from
+large-regret steps is at most
 
-For the regret incurred when we let the agents play myopically at time $t$ in the $s\geq s_0$ phase, it consists of the following two components:
-\begin{itemize}
-\item For those user who will pull an arm that occurs regret greater than $g(t)$: if all arms estimation errors are within $\frac{g(t)}{2\Diam d}$, then based on the same argument as \eqref{equ:choice}, this will never happen.
-We define a sequence of stopping time $\tau_{s}^{k}$ to be the \Kth{k}
-time period in the \Kth{s} phase.
-For $k > t_{s}-t_{s-1}$, we define $\tau_{s}^{k}=\infty$.
-For $\tau_{s}^{k}=t$, the probability of users occur regret greater than $g(t)$ is bounded above by
-$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)$,
-and the expected regret is bounded above by
-$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR$.
-We denote the regret incurred by these agents by $r_1(\tau_{s}^{k})$.
-For $k > t_{s}-t_{s-1}$, we define $r_1(\tau_{s}^{k})=0$.
+\begin{align*}
+\lefteqn{\sum_{s = \LatePhase}^T \sum_{t=t_s}^{t_{s+1}-1}
+  24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g^2(s)}{64 \Diam^2 d^2\sigma^2}\right) \cdot \MAXR}
+\\ & =
+\sum_{s = \LatePhase}^T 
+  24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g^2(s)}{64 \Diam^2 d^2\sigma^2}\right) \cdot \MAXR
+  \cdot \Expect{\mbox{Length of phase } s}
+\\ & \leq
+\sum_{s = \LatePhase}^T 
+  24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g^2(s)}{64 \Diam^2 d^2\sigma^2}\right) \cdot \MAXR
+  \cdot \ARMNUM s,
+\end{align*}
+where the inequality was an application of Lemma~\ref{lem:phase-length}.
+Adding all four terms, and starting the sum at 1 instead of \LatePhase,
+the cumulative regret up to time $T$ is at most
 
-\item For those user who will pull an arm that occurs regret smaller than $g(t)$: if the user pulls his/her best arm, no regret occurs.
-Otherwise, we know his/her utility difference between best and second best arm is smaller than $g(t)$.
-Further, we know this happens with probability \AlmostTied{g(t)} at each time,
-and the regret is bounded above by
-$\AlmostTied{g(t)} \cdot g(t) \leq \TieDensity \cdot (g(t))^2$.
-We denote the regret incurred by these agents as $r_2(t)$.
-\end{itemize}
-
-Thus, the cumulative expected regret incurred up to time $T$ when we
-let the agent play myopically is bounded above by:
-\begin{align}
-\Expect{\sum_{t=1}^{T}\Regret{t}} 
-& = \Expect{\sum_{t=1}^{t_{\LatePhase}} \Regret{t} + \sum_{t=t_{\LatePhase}}^{T}(r_1(t)+r_2(t))}  \nonumber \\
-& \leq \sum_{s=1}^{\LatePhase} \ARMNUM \MAXR s
-     + \Expect{\sum_{s=\LatePhase}^{T}\sum_{t=t_{s}}^{t_{s+1}-1}r_1(t)}
-     + \Expect{\sum_{t=1}^{T}r_2(t)} \nonumber \\
-& = \sum_{s=1}^{\LatePhase} \ARMNUM \MAXR s
-     + \Expect{\sum_{s=\LatePhase}^{T} \sum_{k=1}^{\infty}r_1(\tau_{s}^{k})}
-     + \Expect{\sum_{t=1}^{T}r_2(t)}. \label{chap5:equ:r1}
-\end{align}
-Since
-\begin{align}
-& E\left[\sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\right] \nonumber\\
-= &  \sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{s}^{k})] \nonumber \\
-= &  \sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}(E[r_1(\tau_{s}^{k})|\tau_{s}^{k}<\infty]\times P(\tau_{s}^{k}<\infty)+E[r_1(\tau_{s}^{k})|\tau_{s}^{k}=\infty]\times P(\tau_{s}^{k}=\infty)) \nonumber \\
-= & \sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{s}^{k})|\tau_{s}^{k}<\infty]\times P(\tau_{s}^{k}<\infty), \nonumber
-\end{align}
-
-we have
-\begin{align}
-\eqref{chap5:equ:r1}= & \sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{s}^{k})|\tau_{s}^{k}<\infty]\times P(\tau_{s}^{k}<\infty) + E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
-\leq & \sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=\LatePhase}^{T}\left[\sum_{k=1}^{\infty}24\ARMNUM d\exp\left(-\frac{1.8s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right) R\times P(\tau_{s}^{k}<\infty) \right]+ \sum_{t=1}^{T}\TieDensity\cdot (g(t))^2 \nonumber \\
-\leq & \sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=1}^{T} 24 \ARMNUM  d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right) \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\cdot (g(t))^2.
-\label{chap5:equ:regret}
-\end{align}
-
-Thus the cumulative regret at time $T$ is bounded above by
-\begin{align}
-&\sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity \cdot (g(t))^2  +\nonumber \\
-&O \left( \frac{\MAXR \ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+\begin{multline*}
+O(\ARMNUM \MAXR \LatePhase^2) + 
+O \left( \frac{\MAXR \ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
   + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
     \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right). \nonumber 
-\end{align}
+  \right)} \right) +
+\\
++ \sum_{s = 1}^T 
+  24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g^2(s)}{64 \Diam^2 d^2\sigma^2}\right) \cdot \MAXR
+  \cdot \ARMNUM s,
++ \sum_{t=1}^{T}\TieDensity \cdot g^2(t).
+\end{multline*}
 
-For a fixed $T$, we only need to minimize the following two terms since all others are constant:
+The first line is independent of $T$, and we now choose
+$g^2(t) = \frac{2\log(T) \cdot 64 \Diam^2 d^2 \sigma^2}{1.8 t}$
+with the goal of minimizing the second line.
+With this choice, the second line becomes
 
-\begin{align}
-\sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity \cdot (g(t))^2. \label{equ:regret}
-\end{align}
+\begin{align*}
+\lefteqn{\sum_{s=1}^{T} 24\ARMNUM^2 d s \MAXR \exp\left(-2\log(T)\right)  +
+          \frac{128\Diam^2 d^2\sigma^2
+          \TieDensity\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{t}}
+\\ & \leq
+24\ARMNUM^2 d R\frac{T(T-1)}{2T^2}  + 71.12 \Diam^2 d^2\sigma^2
+          \TieDensity\log(T)(\log(T)+1)
+  \\ & \leq
+12 \ARMNUM^2 d R  + 71.12 \Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1). 
+\end{align*}
 
-If we set $g^2(t)=\frac{2\log(T)\times 64\Diam^2 d^2\sigma^2}{1.8t}$, then
-\begin{align}
-&\sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\cdot (g(t))^2 \nonumber \\ 
-\leq & \sum_{s=1}^{T} 24\ARMNUM^2 d s \MAXR \exp\left(-2\log(T)\right)  + \frac{128\Diam^2 d^2\sigma^2 \TieDensity\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{t} \nonumber \\
-\leq &  24\ARMNUM^2 d R\frac{T(T-1)}{2T^2}  + 71.12 \Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1) \nonumber \\
-\leq &  12 \ARMNUM^2 d R  + 71.12 \Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1). \nonumber
-\end{align}
+Adding all terms, and substituting the definition of
+$\LatePhase = O(\frac{\sigma^4}{x^4})$
+now gives an upper bound of
 
-Thus, the cumulative expected regret is bounded by $O(\ARMNUM^2 d + \TieDensity d^2(\log(T))^2)$.
+\begin{multline*}
+O(\ARMNUM \MAXR \LatePhase^2) + 
+O \left( \frac{\MAXR \ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} \right) +
+O(\Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1)) 
+\end{multline*}
+
+on the cumulative expected regret.
+\dkcomment{I see a problem here: What's the value of $x$ in the
+  definition of \LatePhase? Presumably, we need to make $x$ small
+  enough that any $x$ we use in any application of Lemma 7 (or
+  Corollary 10) works. But notice that we use $x =
+  \Theta(g^2(\tau_s^k))$,
+  and in particular for the last step, I don't see how we can make
+  $\tau_s^k$ much smaller than $T$.
+  But then, we get that $x = O(\frac{\log T}{T})$, which would give
+  linear regret. How to handle this?}
 \end{proof}
 
-\begin{corollary}
+\dkcomment{Edited up to here.}
+
+\begin{corollary} \label{cor:constant-regret}
 If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O(\ARMNUM^2)$.

### 2018-02-06 lower_bound.tex
almost finished regret proof

@@
-\newcommand{\dd}{\mathrm{d}}
-\newcommand{\quarter}{\ensuremath{\frac{1}{4}}\xspace}
-
 \section{A Lower Bound of $\Omega(\log(T))$} \label{sec:lb}
 
-We saw in Corollary~\dkcomment{assign a label and insert here} that
+We saw in Corollary~\ref{cor:constant-regret} that
 when agent preferences for their best arm are sufficiently clear,
@@
 Because $\AgV \cdot (0,0) = 0$ and $\AgV \cdot (0,1) = \Ag{2}$,
-\dkcomment{modify macro to do this correctly}
 the best choice for agent \AgV is arm $(0,1)$ iff $\Ag{2} > 0$,
@@
 Because a pull of arm $(0,1)$ is observed in each time step,
-after $t$ rounds, the estimate \ArmEV{t+1}{(0,1)} is of the form
+after $t$ rounds, the estimate \ArmEV{t}{(0,1)} is of the form
 $(0,1) + (\Noise[t]{1}, \Noise[t]{2})$,
-where $\Noise[t]{1} \sim \Normal{0}{1/t}$
-and $\Noise[t]{2} \sim \Normal{0}{1/t})$.
+where $\Noise[t]{1} \sim \Normal{0}{\sqrt{1/t}}$
+and $\Noise[t]{2} \sim \Normal{0}{\sqrt{1/t}})$.
+\dkcomment{I think we define this to be the estimates at the beginning
+  of round $t$, so we may be off by 1 here and in other places.}
 We lower-bound the regret in step $t$ by focusing on the event that
@@
 \item If $\Ag{2} > 0$ and $\Ag{1} \Noise{1} + \Ag{2} (1+\Noise{2}) < 0$
-then \Ag should pull $(0,1)$,
+then \AgV should pull $(0,1)$,
 but will wrongly pull $(0,0)$ and incur regret \Ag{2}.
@@
 & =
-\frac{1}{\pi} \cdot \left(\frac{1+\Noise{1}+\Noise{2}}{\Noise{1}}\right)^2
-- \frac{2}{3 \pi} \cdot \left(\frac{1+\Noise{1}+\Noise{2}}{\Noise{1}}\right)^2
+\frac{1}{\pi} \cdot \left(\frac{\Noise{1}}{1+\Noise{1}+\Noise{2}}\right)^2
+- \frac{2}{3 \pi} \cdot \left(\frac{\Noise{1}}{1+\Noise{1}+\Noise{2}}\right)^2
 \\ & =
-\frac{1}{3 \pi} \cdot \left(\frac{1+\Noise{1}+\Noise{2}}{\Noise{1}}\right)^2.
+\frac{1}{3 \pi} \cdot \left(\frac{\Noise{1}}{1+\Noise{1}+\Noise{2}}\right)^2.
 \end{align*}

### 2018-02-07 algorithm.tex
changed some notations in the appendix and did some edits for the regret proof (not fixed)

@@
 \begin{proof}
-As before, let $\LatePhase = \max (50, \frac{92.16 \sigma^4}{x^4})$.
-By Lemma~\ref{lem:phase-length}, each phase $s = 1, \ldots, \LatePhase$
-in expectation lasts at most $\ARMNUM s$ steps,
-so the total expected regret incurred in these phases is at most
-$\sum_{s=1}^{\LatePhase} \ARMNUM \MAXR s = O(\ARMNUM \MAXR \LatePhase^2)$.
-
-Regret incurred after the first \LatePhase phases can arise in two ways:
+Regret can arise in two ways:
 (1) an agent was incentivized to pull a suboptimal arm, or
@@
 the best arm.
-To be more precise, we will define (with hindsight) a time-dependent
-cutoff $g(t)$, and consider a regret exceeding $g(t)$ large.
+To be more precise, we will define (with hindsight) a phase-dependent
+cutoff $g(s)$, and consider a regret exceeding $g(s)$ large.
 
-We first consider agents \AgV incurring positive regret less than $g(t)$.
+We first consider agents \AgV incurring positive regret less than $g(s)$.
 The second-best arm \Second{\AgV} of \AgV must satisfy
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(t)$.
+$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(s)$.
 By Lemma~\ref{lem:sdelta}, the total measure of such agents
-is $\AlmostTied{g(t)} \leq \TieDensity \cdot g(t)$,
-and each incurs regret at most $g(t)$.
-Summing over all time steps, the total regret from such agents is at most
-$\sum_{t = 1}^T \TieDensity \cdot g^2(t)$.
+is $\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$,
+and each incurs regret at most $g(s)$.
+Summing over all time steps, the expected total regret from such agents is at most
+\begin{align}
+&E[\sum_{s=1}^{T}\sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)] \leq \sum_{s=1}^{T}\TieDensity\cdot g^2(s)Ns. \nonumber 
+\end{align}
 
@@
 i.e., $k > t_{s}-t_{s-1}$.
-For $t = \tau_{s}^{k}$, by Corollary~\ref{cor:right-choice}
-(applied with $x = \frac{g^2(\tau_s^k)}{4 \Diam^2 d^2}$),
-the probability of incurring regret exceeding $g(t)$ is at most
-$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)$.
-Because each arm must have been pulled at least $s$ times by the time
-the algorithm reaches phase $s$,
-\dkcomment{Really only $s-1$; we have to be careful with those $\pm 1$.}
-we can bound $\tau_{s}^{k} \geq s$.
-\dkcomment{We could bound it by $\ARMNUM s$, if that helps get
-  slightly better bounds.}
+For $t = \tau_{s}^{k}$, we know
+\begin{align}
+&\Prob{\text{incur regret exceeding g(s)}} \nonumber \\
+\leq & \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}}.\nonumber 
+\end{align}
+
 Because the regret never exceeds \MAXR,
@@
 is bounded above by
-$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(s)^2}{64 \Diam^2 d^2\sigma^2}\right) \cdot \MAXR$.
+$\Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR$.
 Summing over all time steps $t$, we get that the total regret from
@@
 \begin{align*}
-\lefteqn{\sum_{s = \LatePhase}^T \sum_{t=t_s}^{t_{s+1}-1}
-  24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g^2(s)}{64 \Diam^2 d^2\sigma^2}\right) \cdot \MAXR}
+\lefteqn{\sum_{s = 1}^T \sum_{t=t_s}^{t_{s+1}-1}
+  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR}
 \\ & =
-\sum_{s = \LatePhase}^T 
-  24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g^2(s)}{64 \Diam^2 d^2\sigma^2}\right) \cdot \MAXR
+\sum_{s = 1}^T 
+  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
   \cdot \Expect{\mbox{Length of phase } s}
 \\ & \leq
-\sum_{s = \LatePhase}^T 
-  24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g^2(s)}{64 \Diam^2 d^2\sigma^2}\right) \cdot \MAXR
+\sum_{s = 1}^T 
+ \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
   \cdot \ARMNUM s,
@@
 where the inequality was an application of Lemma~\ref{lem:phase-length}.
-Adding all four terms, and starting the sum at 1 instead of \LatePhase,
+Adding all three terms,
 the cumulative regret up to time $T$ is at most
 
-\begin{multline*}
-O(\ARMNUM \MAXR \LatePhase^2) + 
-O \left( \frac{\MAXR \ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+\begin{align*}
+&O \left( \frac{\MAXR \ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
   + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
     \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right) +
+  \right)} \right)
 \\
-+ \sum_{s = 1}^T 
-  24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g^2(s)}{64 \Diam^2 d^2\sigma^2}\right) \cdot \MAXR
++ & \sum_{s = 1}^T 
+  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
   \cdot \ARMNUM s,
-+ \sum_{t=1}^{T}\TieDensity \cdot g^2(t).
-\end{multline*}
++ \sum_{s=1}^{T}\TieDensity \cdot g^2(s)\cdot Ns.
+\end{align*}
 
 The first line is independent of $T$, and we now choose
-$g^2(t) = \frac{2\log(T) \cdot 64 \Diam^2 d^2 \sigma^2}{1.8 t}$
+$g^2(s) = \frac{288\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$
 with the goal of minimizing the second line.
-With this choice, the second line becomes
+With this choice and same definition of $S_{s}$ as in the proof of Lemma~\ref{lem:round-prob}, 
+\begin{align*}
+&\Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \\
+\leq &\sum_{i,j}\Prob{|S_s|\geq 3\sqrt{\frac{2}{1.8}s\log(T)}} \\
+\leq &\sum_{i,j}\Prob{|S_s|\geq \sqrt{0.6s\log(\log_{1.1}(s)+1)+\frac{2}{1.8}\log(T)s}} \leq 24\ARMNUM d \cdot \exp(-2\log(T)),
+\end{align*}
+where the second to last inequality is because the following technical inequality, whose proof we include in the appendix.
+
+\begin{lemma} \label{lem:n1-inequality}
+For $2\leq s\leq T$, we have $3\sqrt{\frac{2}{1.8}s\log(T)} \geq \sqrt{0.6s\log(\log_{1.1}(s)+1)+\frac{2}{1.8}\log(T)s}$.
+\end{lemma}
+
+\bccomment{I believe the calculation up to this line should be correct now. The final equation we want to minimize is $\sum_{s=1}^{T}[\exp(-s*g^2(s))+g^2(s)*s]$, what should be our choice of $g(s)$?}
+
+Therefore, the second line becomes
 
@@
           \frac{128\Diam^2 d^2\sigma^2
-          \TieDensity\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{t}}
+          \TieDensity\log(T)}{1.8}\sum_{s=1}^{T}\frac{1}{s}}
 \\ & \leq

### 2018-02-07 appendix.tex
changed some notations in the appendix and did some edits for the regret proof (not fixed)

@@
-\section*{Proof of Lemma~\ref{n0-inequality}}
+\section*{Proof of Lemma~\ref{lem:n0-inequality}}
 
@@
 \begin{align}
-&\frac{n\lambda}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)} \nonumber \\
-\iff &\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{9.6\sigma^2}{\lambda^2}. \nonumber 
+&\frac{nx}{4\sigma}\geq \sqrt{0.6n\log(\log_{1.1}(n)+1)} \nonumber \\
+\iff &\frac{n}{\log(\log_{1.1}(n)+1)}\geq \frac{9.6\sigma^2}{x^2}. \nonumber 
 \end{align}
@@
 
-To prove the lemma, we just need to show for $n\geq n_{0}$, we have
+To prove the lemma, we just need to show for $n\geq s_{0}$, we have
 \begin{align}
-\frac{n}{3+\log(n)}\geq \frac{9.6\sigma^2}{\lambda^2}. \label{n0-equ}
+\frac{n}{3+\log(n)}\geq \frac{9.6\sigma^2}{x^2}. \label{n0-equ}
 \end{align}
@@
 \item for $n\geq 50$, we have $\frac{n}{3+\log(n)}\geq n^{0.5}$;
-\item for $n\geq \frac{92.16\sigma^4}{\lambda^4}$, we have $n^{0.5}\geq {9.6\sigma^{2}}{\lambda^{2}}$.
+\item for $n\geq \frac{92.16\sigma^4}{x^4}$, we have $n^{0.5}\geq {9.6\sigma^{2}}{x^{2}}$.
 \end{itemize}
@@
 
-Denote $\epsilon_{i,t}=u_{i,t}-u_{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$.
+Denote $\epsilon_{i,t}=\ArmEV{t}{i}-\ArmV{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$.
 Denote $\epsilon_{i,t}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,t}$.
@@
 \begin{align}
-&\max_{i}\theta_t\cdot u_{i,t} - \min_{j}\theta_t\cdot u_{j,t} \nonumber \\
-= &\max_{i}\theta_t\cdot (\epsilon_{i,t}+u_i) - \min_{j}\theta_t\cdot (\epsilon_{j,t}+u_j) \nonumber \\
-\leq &\max_{i}\theta_t\cdot u_i - \min_{j}\theta_t\cdot u_j +\max_{i}\theta_t\cdot \epsilon_{i,t} - \min_{j}\theta_t\cdot \epsilon_{j,t}\nonumber \\
-\leq & R + 2Wmg(n,\ell). \nonumber
+&\max_{i}\AgentV{t}\cdot \ArmEV{t}{i} - \min_{j}\AgentV{t}\cdot \ArmEV{t}{j} \nonumber \\
+= &\max_{i}\AgentV{t}\cdot (\epsilon_{i,t}+\ArmV{i}) - \min_{j}\AgentV{t}\cdot (\epsilon_{j,t}+\ArmV{j}) \nonumber \\
+\leq &\max_{i}\AgentV{t}\cdot \ArmV{i} - \min_{j}\AgentV{t}\cdot \ArmV{j} +\max_{i}\AgentV{t}\cdot \epsilon_{i,t} - \min_{j}\AgentV{t}\cdot \epsilon_{j,t}\nonumber \\
+\leq & R + 2\Diam dg(n,\ell). \nonumber
 \end{align}
 
-We denote $\bar{c}(n,\ell)=R + 2Wmg(n,\ell)$ as the upper bound of payment for round $n$ if our measurement error lie in the $\ell^{th}$ envelope.
+We denote $\bar{c}(n,\ell)=R + 2\Diam dg(n,\ell)$ as the upper bound of payment for round $n$ if our measurement error lie in the $\ell^{th}$ envelope.
 
@@
 
-\[ P(\text{play a new arm}|\mathcal{F}_t) =
+\[ \Prob{\text{play a new arm}|\mathcal{F}_t} =
 \begin{cases}
 1       & \quad \text{if we incentivize}\\
-\sum_{i\notin (V\cup S)} P(\theta \cdot u_{i,t}>\theta\cdot u_{j,t} \forall j\neq i)  & \quad \text{if }  S\setminus V\neq \emptyset 
+\sum_{i\notin (V\cup S)} P(\AgentV{t} \cdot \ArmEV{t}{i}>\AgentV{t}\cdot \ArmEV{t}{j} \forall j\neq i)  & \quad \text{if }  S\setminus V\neq \emptyset 
 \end{cases} \label{dom_stoc}
@@
 
-Let $(Z_{n,v,m}:m\geq 0)$ be a sequence of independent Bernoulli random variable with success probability $(1-\frac{v}{n})$.
+Let $(Z_{s,v,m}:m\geq 0)$ be a sequence of independent Bernoulli random variable with success probability $(1-\frac{v}{s})$.
 We will construct an alternative stochastic process for selecting which arm gets played that has the same distribution as the original process, but under which
 \begin{align}
-t_{n+1}-t_{n}\leq \bar{T}_{n}:=\sum_{v=0}^{N-1}\bar{T}_{n,v}, \nonumber 
+t_{s+1}-t_{s}\leq \bar{T}_{s}:=\sum_{v=0}^{\ARMNUM-1}\bar{T}_{s,v}, \nonumber 
 \end{align}
-where $\bar{T}_{n,v}:=\inf\{m\geq 0: Z_{n,v,m}=1\}+1$.
+where $\bar{T}_{s,v}:=\inf\{m\geq 0: Z_{s,v,m}=1\}+1$.
 
-The new stochastic process will have the property that whenever $Z_{n,v(n,t),m(n,t)}=1$, we will play a new arm at time t for $t\in [t_{n}, t_{n+1}]$, where $v(n,t)$ is the number of unique arms played in round $n$ strictly before time $t$, and $m(n,t)$ is the number of times we have pulled a previously pulled arm for the current value of $v(n,t)$.
+The new stochastic process will have the property that whenever $Z_{s,v(s,t),m(s,t)}=1$, we will play a new arm at time t for $t\in [t_{s-1}, t_{s}]$, where $v(s,t)$ is the number of unique arms played in round $s$ strictly before time $t$, and $m(s,t)$ is the number of times we have pulled a previously pulled arm for the current value of $v(s,t)$.
 At time $t$, to determine what arm to pull, calculate \eqref{dom_stoc} and let $q_t$ be the probability computed.
-Note $q_t\geq 1-\frac{v(n,t)}{n}$.
+Note $q_t\geq 1-\frac{v(s,t)}{s}$.
 
-If $Z_{n,v(n,t),m(n,t)}$ is 1, decide to play a new arm.
-Otherwise, draw a second Bernoulli random variable with probability $\frac{q_t-(1-\frac{v(n,t)}{n})}{1-(1-\frac{v(n,t)}{n})}$, and if it is 1, decide to play a new arm, and otherwise decide to play an old arm.
+If $Z_{s,v(s,t),m(s,t)}$ is 1, decide to play a new arm.
+Otherwise, draw a second Bernoulli random variable with probability $\frac{q_t-(1-\frac{v(s,t)}{s})}{1-(1-\frac{v(s,t)}{s})}$, and if it is 1, decide to play a new arm, and otherwise decide to play an old arm.
 Note that
@@
 \begin{align}
-P(\text{play a new arm}|\mathcal{F}_{t})=\left[1-\frac{v(n,t)}{n}\right]+\left[1-(1-\frac{v(n,t)}{n})\right]\times \frac{q_t-(1-\frac{v(n,t)}{n})}{1-(1-\frac{v(n,t)}{n})}=q_t.
+\Prob{\text{play a new arm}|\mathcal{F}_{t}}=\left[1-\frac{v(s,t)}{s}\right]+\left[1-(1-\frac{v(s,t)}{s})\right]\times \frac{q_t-(1-\frac{v(s,t)}{s})}{1-(1-\frac{v(s,t)}{s})}=q_t.
 \end{align}
 
-Since we pull a new arm only when $Z_{n,v(n,t),m(n,t)}=1$, the number of times we pull an arm when $v(n,t)=v$ is bounded above by $\bar{T}_{n,v}$. Thus,
+Since we pull a new arm only when $Z_{s,v(s,t),m(s,t)}=1$, the number of times we pull an arm when $v(s,t)=v$ is bounded above by $\bar{T}_{s,v}$. Thus,
 
 \begin{align}
-t_{n+1}-t_{n}\leq \sum_{v=0}^{n-1}\bar{T}_{n,v}=\bar{T}_{n}.
+t_{s+1}-t_{s}\leq \sum_{v=0}^{\ARMNUM-1}\bar{T}_{s,v}=\bar{T}_{s}.
 \end{align}
-Finally, we want to bound $\sum_{t}E[c(t)]$. Let $C(n)$ be the cost incurred in round $n$. Thus $\sum_{t}E[c(t)]=\sum_{n}E[C(n)]$. We know
+Finally, we want to bound $\sum_{t}E[c(t)]$. Let $C(s)$ be the cost incurred in phase $s$. Thus $\sum_{t}E[c(t)]=\sum_{s}E[C(s)]$. We know
 \begin{align}
-C(n)&=\sum_{t=t_n}^{t_{n+1}-1}c(t)=\sum_{t=t_{n}}^{t_{n+1}-1}\sum_{\ell}\mathbbm{1}\{\omega\in L(\ell)\}c(t) \nonumber \\
-&\leq \sum_{t=t_{n}}^{t_{n+1}-1}\sum_{l}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell) \nonumber \\
-&\leq (t_{n+1}-t_{n})\sum_{\ell} \mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell) \nonumber \\
-&\leq \bar{T}_{n}\sum_{l}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell). \nonumber
+C(s)&=\sum_{t=t_s}^{t_{s+1}-1}c(t)=\sum_{t=t_{s}}^{t_{s+1}-1}\sum_{\ell}\mathbbm{1}\{\omega\in L(\ell)\}c(t) \nonumber \\
+&\leq \sum_{t=t_{s}}^{t_{s+1}-1}\sum_{l}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell) \nonumber \\
+&\leq (t_{s+1}-t_{s})\sum_{\ell} \mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(s,\ell) \nonumber \\
+&\leq \bar{T}_{s}\sum_{l}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(s,\ell). \nonumber
 \end{align}
 
-Since $\bar{T}_{n}$ is independent of $\omega$, we know
+Since $\bar{T}_{s}$ is independent of $\omega$, we know
 \begin{align}
-E[C(n)]\leq E[\bar{T}_{n}]\sum_{\ell}P(\omega\in L(\ell))\bar{c}(n,\omega). \nonumber
+E[C(s)]\leq E[\bar{T}_{s}]\sum_{\ell}\Prob{\omega\in L(\ell)}\bar{c}(s,\omega). \nonumber
 \end{align}
@@
 \begin{align}
-\sum_{t=1}^{\infty}c(t) =\sum_{n=1}^{\infty}C(n)
-\leq  \sum_{n=1}^{\infty}\sum_{\ell=1}^{\infty}\bar{T}_{n}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell). \nonumber
+\sum_{t=1}^{\infty}c(t) =\sum_{s=1}^{\infty}C(s)
+\leq  \sum_{s=1}^{\infty}\sum_{\ell=1}^{\infty}\bar{T}_{s}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(s,\ell). \nonumber
 \end{align}
 
-Set $g(n,\ell)$ to be $\frac{12\sigma \ell}{n^{2/5}}$.
-Since if $|u_{i}^{j}-u_{i,t}^{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\theta\in \{\theta:\theta\cdot u_{B(\theta)}-\max_{j\neq B(\theta)}\{\theta \cdot u_{j}\}> 2Wm\lambda\}$, they will correctly identify their best arm.
-Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{12\sigma l}{n^{2/5}} \leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
-Further, if time $t$ is in a round $n$ that satisfies $n^{-1}\leq p/2$, then our algorithm will not incentivize pulling any arms.
-Denote $a_0=\frac{24Wm\sigma}{p^{-1}(\frac{p}{2})}$.
-In order to have $\frac{12\sigma l}{n^{2/5}}\leq \frac{p^{-1}(\frac{p}{2})}{2Wm}$, it is sufficient to have $n\geq \lceil (a_{0} l)^\frac{5}{2} \rceil$.
-In order to have $n^{-1}\leq \frac{p}{2}$, we need $n\geq \frac{2}{p}$.
-Denote $n_2=\frac{2}{p}$.
-Thus, we know we can only incur regret for sample paths $\omega$ in the $\ell^{th}$ envelope in the first $\max\{n_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}$ rounds.
+Set $g(s,\ell)$ to be $\frac{12\sigma \ell}{s^{2/5}}$.
+Since if $|\Arm{i}{j}-\ArmE{t}{i}{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\AgV\in \{\AgV:\AgV\cdot \ArmV{\Best{\AgV}}-\AgV \cdot \ArmV{\Second{\AgV}}> 2\Diam d\lambda\}$, they will correctly identify their best arm.
+Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{12\sigma l}{s^{2/5}} \leq \frac{p^{-1}(\frac{\MinProb}{2})}{2\Diam d}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
+Further, if time $t$ is in a phase $s$ that satisfies $s^{-1}\leq \MinProb/2$, then our algorithm will not incentivize pulling any arms.
+Denote $a_0=\frac{24\Diam d\sigma}{p^{-1}(\frac{\MinProb}{2})}$.
+In order to have $\frac{12\sigma l}{s^{2/5}}\leq \frac{p^{-1}(\frac{\MinProb}{2})}{2\Diam d}$, it is sufficient to have $s\geq \lceil (a_{0} l)^\frac{5}{2} \rceil$.
+In order to have $s^{-1}\leq \frac{\MinProb}{2}$, we need $s\geq \frac{2}{\MinProb}$.
+Denote $s_2=\frac{2}{\MinProb}$.
+Thus, we know we can only incur regret for sample paths $\omega$ in the $\ell^{th}$ envelope in the first $\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}$ rounds.
 
@@
 \begin{align}
-\sum_{t=1}^{\infty}c(t)\leq\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(n,\ell)\mathbbm{1}\{\omega\in L[\ell]\}\bar{T}_{n}. \nonumber
+\sum_{t=1}^{\infty}c(t)\leq\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(s,\ell)\mathbbm{1}\{\omega\in L[\ell]\}\bar{T}_{s}. \nonumber
 \end{align}
@@
 &E\left[\sum_{t=1}^{\infty}c(t)\right] \nonumber\\
-\leq &\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(n,\omega)P(\omega \in L(\ell))E[\bar{T}_{n}] \nonumber \\
-=&\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[R+2Wm\frac{12\sigma \ell}{n^{2/5}}\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
-\leq &\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[R+24Wm\sigma l\right]P(\omega\in L[\ell])E[\bar{T}_{n}]. \nonumber
+\leq &\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(s,\omega)\Prob{\omega \in L(\ell)}E[\bar{T}_{s}] \nonumber \\
+=&\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[\MAXR+2\Diam d\frac{12\sigma \ell}{s^{2/5}}\right]\Prob(\omega\in L[\ell])E[\bar{T}_{s}] \nonumber \\
+\leq &\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[\MAXR+24\Diam d\sigma l\right]\Prob(\omega\in L[\ell])E[\bar{T}_{s}]. \nonumber
 \end{align}
 
-\noindent\textbf{Step 4: Bound $P(\omega\in L(\ell))$}.
+\noindent\textbf{Step 4: Bound $\Prob{\omega\in L(\ell)}$}.
 
-We now bound $P(\omega\in L[\ell])$ for $n\geq n_0$ and $\ell\geq 2$. As a reminder, we omit the dependency between $\epsilon_{i,t}^{j}$, $n$ and $\omega$. We know 
+We now bound $\Prob{\omega\in L[\ell]}$ for $n\geq n_0$ and $\ell\geq 2$. As a reminder, we omit the dependency between $\epsilon_{i,t}^{j}$, $n$ and $\omega$. We know 
 \begin{align}
-&P(\omega\in L[\ell]) \nonumber \\
-=&P(\omega\in L^{'}[\ell])- P(\omega\in L^{'}[\ell-1]) \nonumber \\
-\leq & 1-P\left(|\epsilon_{i,t}^{j}|<\frac{12\sigma (\ell-1)}{n^{2/5}}, \forall i,j\right) \nonumber \\
-=&P\left(\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{12\sigma (\ell-1)}{n^{2/5}}\right) \nonumber  \\
-\leq &\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{12\sigma (\ell-1)}{n^{2/5}}\right) \nonumber
+&\Prob{\omega\in L[\ell]} \nonumber \\
+=&\Prob{\omega\in L^{'}[\ell]}- \Prob{\omega\in L^{'}[\ell-1]} \nonumber \\
+\leq & 1-\Prob{|\epsilon_{i,t}^{j}|<\frac{12\sigma (\ell-1)}{n^{2/5}}, \forall i,j} \nonumber \\
+=&\Prob{\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{12\sigma (\ell-1)}{n^{2/5}}} \nonumber  \\
+\leq &\sum_{i,j}\Prob{|\epsilon_{i,t}^{j}|\geq \frac{12\sigma (\ell-1)}{n^{2/5}}} \nonumber
 \end{align}
 
-Define $S_{i,t}^{j}=\frac{N(i,t)\epsilon_{i,t}^{j}}{2\sigma}$, then we know $S_{i,t}^{j}$ is a summation of $1/2$ gaussian random numbers. Therefore,
+Define $S_{i,t}^{j}=\frac{\NumPull{t}{i}\epsilon_{i,t}^{j}}{2\sigma}$, then we know $S_{i,t}^{j}$ is a summation of $1/2$ gaussian random numbers. Therefore,
 \begin{align}
-&\sum_{i,j}P\left(|\epsilon_{i,t}^{j}|\geq \frac{12\sigma(\ell-1)}{n^{2/5}}\right) \nonumber \\ 
-=&\sum_{i,j}P\left(|S_{i,t}^{j}|\geq \frac{6N(i,t)(\ell-1)}{n^{2/5}}\right) \nonumber \\
-\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq 6N(i,t)^{3/5}(\ell-1)). \nonumber
+&\sum_{i,j}\Prob{|\epsilon_{i,t}^{j}|\geq \frac{12\sigma(\ell-1)}{n^{2/5}}} \nonumber \\ 
+=&\sum_{i,j}\Prob{|S_{i,t}^{j}|\geq \frac{6\NumPull{t}{i}(\ell-1)}{n^{2/5}}} \nonumber \\
+\leq &\sum_{i,j}\Prob{|S_{i,t}^{j}|\geq 6\NumPull{t}{i}^{3/5}(\ell-1)}. \nonumber
 \end{align}
@@
 \begin{align}
-&6N(i,t)^{3/5}(\ell-1) \nonumber \\
-=& 5N(i,t)^{3/5} + N(i,t)^{3/5}(\ell-1) \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)} + \sqrt{(\ell-1)^2 N(i,t)} \nonumber \\
-\geq & \sqrt{0.6N(i,t)\log(\log_{1.1}(N(i,t))+1)+(\ell-1)^2 N(i,t)}. \nonumber
+&6\NumPull{t}{i}^{3/5}(\ell-1) \nonumber \\
+=& 5\NumPull{t}{i}^{3/5} + \NumPull{t}{i}^{3/5}(\ell-1) \nonumber \\
+\geq & \sqrt{0.6\NumPull{t}{i}\log(\log_{1.1}(\NumPull{t}{i})+1)} + \sqrt{(\ell-1)^2 \NumPull{t}{i}} \nonumber \\
+\geq & \sqrt{0.6\NumPull{t}{i}\log(\log_{1.1}(\NumPull{t}{i})+1)+(\ell-1)^2 \NumPull{t}{i}}. \nonumber
 \end{align}
 
-Based on Lemma~\ref{ACI-inequality}, we know
+Based on Lemma~\ref{lem:ACI-inequality}, we know
 \begin{align}
-& P(\omega\in L(\ell) \nonumber \\
-\leq &\sum_{i,j}P(|S_{i,t}^{j}|\geq 6N(i,t)^{3/5}(\ell-1)) \nonumber \\
-\leq & \sum_{i,j}24e^{-1.8(\ell-1)^2} = 24Nme^{-1.8(\ell-1)^2}. \nonumber
+& \Prob{\omega\in L(\ell)} \nonumber \\
+\leq &\sum_{i,j}\Prob{|S_{i,t}^{j}|\geq 6\NumPull{t}{i}^{3/5}(\ell-1)} \nonumber \\
+\leq & \sum_{i,j}24e^{-1.8(\ell-1)^2} = 24\ARMNUM d\exp(-1.8(\ell-1)^2). \nonumber
 \end{align}
@@
 &\sum_{t=1}^{\infty}c(t) \nonumber \\
-\leq&\sum_{\ell=1}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[R+24Wm\sigma \ell\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
-\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24Wm\sigma \right]P(\omega\in L[1])E[\bar{T}_{n}] +\sum_{l=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[R+24Wm\sigma \ell\right]P(\omega\in L[\ell])E[\bar{T}_{n}] \nonumber \\
-\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24Wm\sigma \right]E[\bar{T}_{n}] +\sum_{\ell=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[R+24Wm\sigma \ell\right]24Nme^{-1.8(\ell-1.9)^2}E[\bar{T}_{n}]\nonumber \\
-\leq& \sum_{n=1}^{\max\{n_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24Wm\sigma \right]Nn +\sum_{\ell=2}^{\infty}\sum_{n=1}^{\max\{n_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[R+24Wm\sigma \ell\right]24Nme^{-1.8(\ell-1.9)^2}Nn \nonumber \\
-\leq & \left[R+24Wm\sigma \right]N (\max\{n_2,\lceil (a_0)^{5/2} \rceil\})^2+\sum_{\ell=2}^{\infty}24N^2 m[R+24Wm\ell\sigma](\max\{n_2,\lceil (a_0 \ell)^{5/2} \rceil\})^2 e^{-1.8(\ell-1.9)^2} \nonumber \\
-=& O(\frac{N}{p^5}+ \frac{N^2}{p^5}). \nonumber
+\leq&\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]\Prob{\omega\in L[\ell])E[\bar{T}_{s}} \nonumber \\
+\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\Prob{\omega\in L[1]}E[\bar{T}_{s}] +\sum_{l=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]\Prob{\omega\in L[\ell]}E[\bar{T}_{s}] \nonumber \\
+\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24\Diam d\sigma \right]E[\bar{T}_{s}] +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24\ARMNUM d e^{-1.8(\ell-1.9)^2}E[\bar{T}_{s}]\nonumber \\
+\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\ARMNUM s +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24 \ARMNUM d e^{-1.8(\ell-1.9)^2}\ARMNUM s \nonumber \\
+\leq & \left[\MAXR+24\Diam d\sigma \right]\ARMNUM (\max\{s_2,\lceil (a_0)^{5/2} \rceil\})^2+\sum_{\ell=2}^{\infty}24\ARMNUM^2 d[\MAXR+24\Diam d\ell\sigma](\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\})^2 e^{-1.8(\ell-1.9)^2} \nonumber \\
+=& O(\frac{N}{\MinProb^5}+ \frac{\ARMNUM^2}{\MinProb^5}). \nonumber
 \end{align}
@@
 Based on inequality~\eqref{inequ:dct}, we know $d(t)\leq \frac{z_{t,1}^{2}}{2}$ and $\lim_{t\rightarrow\infty}d(t)=\frac{z_{t,1}^2}{2}$.
+
+\section*{Proof of Lemma~\ref{lem:n1-inequality}}
+
+\begin{proof}
+We first prove $2\sqrt{\frac{2}{1.8}s\log(T)}\geq \sqrt{0.6s\log(\log_{1.1}(s)+1)}$ for $s\geq 2$. This is true because
+\begin{align}
+&2\sqrt{\frac{2}{1.8}s\log(T)}\geq \sqrt{0.6s\log(\log_{1.1}(s)+1)} \nonumber \\
+\Longleftarrow & 2\sqrt{s\log(T)}\geq \sqrt{s\log(\log_{1.1}(s)+1)} \nonumber \\
+\Longleftarrow & 4\log(T)\geq \log(\log_{1.1}(s)+1) \nonumber \\
+\Longleftarrow & T^4 \geq \log_{1.1}(s)+1 \nonumber \\
+\Longleftarrow & s^4 \geq \log_{1.1}(s)+1, \nonumber
+\end{align}
+the derivative of $s^4-\log_{1.1}(s)-1$ is positive for $s\geq 2$ and $2^4-\log_{1.1}(s)-1>0$.
+
+Therefore, we know
+\begin{align}
+&3\sqrt{\frac{2}{1.8}s\log(T)} \nonumber \\
+= & 2\sqrt{\frac{2}{1.8}s\log(T)} + \sqrt{\frac{2}{1.8}s\log(T)} \nonumber \\
+\geq & \sqrt{0.6s\log(\log_{1.1}(s)+1)}+\sqrt{\frac{2}{1.8}s\log(T)} \nonumber \\
+\geq & \sqrt{0.6s\log(\log_{1.1}(s)+1)+\frac{2}{1.8}\log(T)s}. \nonumber 
+\end{align}
+
+\end{proof}

### 2018-02-08 appendix.tex
editted the appendix

@@
 
-Denote $\epsilon_{i,t}=\ArmEV{t}{i}-\ArmV{i}$ to be the estimation error for the attribute vector $u_i$ at time $t$.
+Denote $\epsilon_{i,t}=\ArmEV{t}{i}-\ArmV{i}$ to be the estimation error for the attribute vector $\ArmV{i}$ at time $t$.
 Denote $\epsilon_{i,t}^{j}$ to be the $j^{th}$ component of $\epsilon_{i,t}$.
-Denote $\omega$ to be a sample path and $n(t,\omega)$ to be the round number for sample path $\omega$ at time $t$.
+Denote $\omega$ to be a sample path and $s(t,\omega)$ to be the phase number for sample path $\omega$ at time $t$.
 For a fixed time $t$, define
 \begin{align}
-L^{'}[\ell](t) = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(n(t,\omega),\ell), \forall i,j\}\nonumber
+L^{'}[\ell](t) = \{\omega:|\epsilon_{i,t}^{j}(\omega)|\leq g(s(t,\omega),\ell), \forall i,j\}\nonumber
 \end{align}
-where $g(n,\ell)$ is a function which we will define later.
+where $g(s,\ell)$ is a function which we will define later.
 Define $L[1](t) = L^{'}[1](t)$ and $L[i](t) = L^{'}[i](t)\setminus L^{'}[i-1](t)$ for $i\geq 2$.
@@
 
-In the calculation below, we omit the dependency on $\omega$ when refering to variables $c(t)$, $\epsilon_{i,t}^{j}$ and $t_n$.
+In the calculation below, we omit the dependency on $\omega$ when refering to variables $c(t)$, $\epsilon_{i,t}^{j}$ and $t_s$.
 Based on the definition of $L[\ell]$, we know if $\omega\in L[\ell]$, the maximum payment we need to offer at time $t$ is bounded above by
@@
 \leq &\max_{i}\AgentV{t}\cdot \ArmV{i} - \min_{j}\AgentV{t}\cdot \ArmV{j} +\max_{i}\AgentV{t}\cdot \epsilon_{i,t} - \min_{j}\AgentV{t}\cdot \epsilon_{j,t}\nonumber \\
-\leq & R + 2\Diam dg(n,\ell). \nonumber
+\leq & R + 2\Diam d\cdot g(s,\ell). \nonumber
 \end{align}
 
-We denote $\bar{c}(n,\ell)=R + 2\Diam dg(n,\ell)$ as the upper bound of payment for round $n$ if our measurement error lie in the $\ell^{th}$ envelope.
+We denote $\bar{c}(s,\ell)=R + 2\Diam d\cdot g(s,\ell)$ as the upper bound of payment for phase $s$ if our measurement error lie in the $\ell^{th}$ envelope.
 
-\noindent\textbf{Step 2: Introduce a new stochastic process which bounds the total payment in a round}
+\noindent\textbf{Step 2: Introduce a new stochastic process which bounds the total payment in a phase}
 
-Denote $\mathcal{F}_t$ as the filtration up to time $t$. Based on our algorithm, we know
+Denote $\mathcal{F}_t$ as the filtration up to time $t$. Denote $V_t$ as the set of arms that we need to pull, but haven't pulled yet in this phase. Based on our algorithm, we know
 
@@
 1       & \quad \text{if we incentivize}\\
-\sum_{i\notin (V\cup S)} P(\AgentV{t} \cdot \ArmEV{t}{i}>\AgentV{t}\cdot \ArmEV{t}{j} \forall j\neq i)  & \quad \text{if }  S\setminus V\neq \emptyset 
+\sum_{i\in V} P(\AgentV{t} \cdot \ArmEV{t}{i}>\AgentV{t}\cdot \ArmEV{t}{j} \forall j\neq i)  & \quad \text{otherwise}  
 \end{cases} \label{dom_stoc}
@@
 \hspace{1cm}$\geq (n-|V|)\times \frac{1}{n}=1-\frac{|V|}{n}$.
+\bccomment{Wait for Peter to address this}
 
@@
 \begin{align}
-t_{s+1}-t_{s}\leq \bar{T}_{s}:=\sum_{v=0}^{\ARMNUM-1}\bar{T}_{s,v}, \nonumber 
+t_{s}-t_{s-1}\leq \bar{T}_{s}:=\sum_{v=0}^{\ARMNUM-1}\bar{T}_{s,v}, \nonumber 
 \end{align}
@@
 
-The new stochastic process will have the property that whenever $Z_{s,v(s,t),m(s,t)}=1$, we will play a new arm at time t for $t\in [t_{s-1}, t_{s}]$, where $v(s,t)$ is the number of unique arms played in round $s$ strictly before time $t$, and $m(s,t)$ is the number of times we have pulled a previously pulled arm for the current value of $v(s,t)$.
+The new stochastic process will have the property that whenever $Z_{s,v(s,t),m(s,t)}=1$, we will play a new arm at time t for $t\in [t_{s-1}, t_{s}]$, where $v(s,t)$ is the number of unique arms played in phase $s$ strictly before time $t$, and $m(s,t)$ is the number of times we have pulled a previously pulled arm for the current value of $v(s,t)$.
 At time $t$, to determine what arm to pull, calculate \eqref{dom_stoc} and let $q_t$ be the probability computed.
@@
 \begin{align}
-t_{s+1}-t_{s}\leq \sum_{v=0}^{\ARMNUM-1}\bar{T}_{s,v}=\bar{T}_{s}.
+t_{s}-t_{s-1}\leq \sum_{v=0}^{\ARMNUM-1}\bar{T}_{s,v}=\bar{T}_{s}.
 \end{align}
@@
 \begin{align}
-C(s)&=\sum_{t=t_s}^{t_{s+1}-1}c(t)=\sum_{t=t_{s}}^{t_{s+1}-1}\sum_{\ell}\mathbbm{1}\{\omega\in L(\ell)\}c(t) \nonumber \\
-&\leq \sum_{t=t_{s}}^{t_{s+1}-1}\sum_{l}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(n,\ell) \nonumber \\
-&\leq (t_{s+1}-t_{s})\sum_{\ell} \mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(s,\ell) \nonumber \\
+C(s)&=\sum_{t=t_{s-1}+1}^{t_{s}}c(t)=\sum_{t=t_{s-1}+1}^{t_{s}}\sum_{\ell}\mathbbm{1}\{\omega\in L(\ell)\}c(t) \nonumber \\
+&\leq \sum_{t=t_{s-1}+1}^{t_{s}}\sum_{l}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(s,\ell) \nonumber \\
+&\leq (t_{s}-t_{s-1})\sum_{\ell} \mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(s,\ell) \nonumber \\
 &\leq \bar{T}_{s}\sum_{l}\mathbbm{1}\{\omega\in L(\ell)\}\bar{c}(s,\ell). \nonumber
@@
 Since if $|\Arm{i}{j}-\ArmE{t}{i}{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\AgV\in \{\AgV:\AgV\cdot \ArmV{\Best{\AgV}}-\AgV \cdot \ArmV{\Second{\AgV}}> 2\Diam d\lambda\}$, they will correctly identify their best arm.
-Thus, if $|u_{i}^{j}-u_{i,t}^{j}|\leq \frac{12\sigma l}{s^{2/5}} \leq \frac{p^{-1}(\frac{\MinProb}{2})}{2\Diam d}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
+Thus, if $|\Arm{i}{j}-\ArmE{t}{i}{j}|\leq \frac{12\sigma l}{s^{2/5}} \leq \frac{p^{-1}(\frac{\MinProb}{2})}{2\Diam d}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
 Further, if time $t$ is in a phase $s$ that satisfies $s^{-1}\leq \MinProb/2$, then our algorithm will not incentivize pulling any arms.
@@
 Denote $s_2=\frac{2}{\MinProb}$.
-Thus, we know we can only incur regret for sample paths $\omega$ in the $\ell^{th}$ envelope in the first $\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}$ rounds.
+Thus, we know we can only incur regret for sample paths $\omega$ in the $\ell^{th}$ envelope in the first $\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}$ phases.
 
@@
 
-We now bound $\Prob{\omega\in L[\ell]}$ for $n\geq n_0$ and $\ell\geq 2$. As a reminder, we omit the dependency between $\epsilon_{i,t}^{j}$, $n$ and $\omega$. We know 
+We now bound $\Prob{\omega\in L[\ell]}$ for $\ell\geq 2$. As a reminder, we omit the dependency between $\epsilon_{i,t}^{j}$, $s$ and $\omega$. We know 
 \begin{align}
@@
 =&\Prob{\omega\in L^{'}[\ell]}- \Prob{\omega\in L^{'}[\ell-1]} \nonumber \\
-\leq & 1-\Prob{|\epsilon_{i,t}^{j}|<\frac{12\sigma (\ell-1)}{n^{2/5}}, \forall i,j} \nonumber \\
-=&\Prob{\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{12\sigma (\ell-1)}{n^{2/5}}} \nonumber  \\
-\leq &\sum_{i,j}\Prob{|\epsilon_{i,t}^{j}|\geq \frac{12\sigma (\ell-1)}{n^{2/5}}} \nonumber
+\leq & 1-\Prob{|\epsilon_{i,t}^{j}|<\frac{12\sigma (\ell-1)}{s^{2/5}}, \forall i,j} \nonumber \\
+=&\Prob{\exists i,j, s.t. |\epsilon_{i,t}^{j}|\geq \frac{12\sigma (\ell-1)}{s^{2/5}}} \nonumber  \\
+\leq &\sum_{i,j}\Prob{|\epsilon_{i,t}^{j}|\geq \frac{12\sigma (\ell-1)}{s^{2/5}}} \nonumber
 \end{align}
@@
 \leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\Prob{\omega\in L[1]}E[\bar{T}_{s}] +\sum_{l=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]\Prob{\omega\in L[\ell]}E[\bar{T}_{s}] \nonumber \\
-\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24\Diam d\sigma \right]E[\bar{T}_{s}] +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24\ARMNUM d e^{-1.8(\ell-1.9)^2}E[\bar{T}_{s}]\nonumber \\
-\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\ARMNUM s +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24 \ARMNUM d e^{-1.8(\ell-1.9)^2}\ARMNUM s \nonumber \\
-\leq & \left[\MAXR+24\Diam d\sigma \right]\ARMNUM (\max\{s_2,\lceil (a_0)^{5/2} \rceil\})^2+\sum_{\ell=2}^{\infty}24\ARMNUM^2 d[\MAXR+24\Diam d\ell\sigma](\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\})^2 e^{-1.8(\ell-1.9)^2} \nonumber \\
+\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24\Diam d\sigma \right]E[\bar{T}_{s}] +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24\ARMNUM d e^{-1.8(\ell-1)^2}E[\bar{T}_{s}]\nonumber \\
+\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\ARMNUM s +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24 \ARMNUM d e^{-1.8(\ell-1)^2}\ARMNUM s \nonumber \\
+\leq & \left[\MAXR+24\Diam d\sigma \right]\ARMNUM (\max\{s_2,\lceil (a_0)^{5/2} \rceil\})^2+\sum_{\ell=2}^{\infty}24\ARMNUM^2 d[\MAXR+24\Diam d\ell\sigma](\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\})^2 e^{-1.8(\ell-1)^2} \nonumber \\
 =& O(\frac{N}{\MinProb^5}+ \frac{\ARMNUM^2}{\MinProb^5}). \nonumber

### 2018-02-09 algorithm.tex
edited the payment, regret and lower bound proof

@@
 \item Based on the current estimates \ArmEV{t}{i'} of all arms'
-attribute vectors, the probability of pulling arm $i$ is less than $1/s$.
+attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s)$. \bccomment{Do we need to mention what if $\frac{1}{\log(s)}>1$? }
 Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
@@
 Then, the second criterion for payment-eligibility is that
-$\PullProb{t}{i} < 1/s$.
+$\PullProb{t}{i} < 1/\log(s)$.
 \end{itemize}
@@
 Indeed, we show in Section~\ref{sec:pi} that it suffices to
-incentivize only a $1/s$ fraction of the agents.
+incentivize only a $1/\log(s)$ fraction of the agents.
 \dkcomment{Given that we don't prove anything there, is ``show'' the
@@
 then by definition of payment-eligibility,
-each arm $i \in S$ has probability at least $1/s$ of being pulled.
-In particular, the size of $S$ decreases with probability at least $1/s$.
+each arm $i \in S$ has probability at least $1/\log(s)$ of being pulled.
+In particular, the size of $S$ decreases with probability at least $1/\log(s)$.
 
@@
 so the expected number of steps until $S$ is empty is at most
-$\ARMNUM \cdot s$.
+$\ARMNUM \cdot \log(s)$.
 \dkcomment{If we wanted, this bound could probably be improved using a
@@
 we use that arms are payment-eligible only if their myopic pulling
-probability is less than $1/s$.
+probability is less than $1/\log(s)$.
 Since at least a \MinProb fraction of agents would prefer arm $i$ if
@@
 The cutoff point between early and late phases is now set to
-$\EvenLaterPhase = \max(50, \frac{92.16 \sigma^4}{x^4}, \frac{2}{\MinProb})$.
+$\EvenLaterPhase = \max(50, \frac{92.16 \sigma^4}{x^4}, \exp(\frac{2}{\MinProb}))$.
 Consider the \Kth{s} pull of an arm $i$, for $s \geq \EvenLaterPhase$.
@@
   \right)}
-& = O\left( \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+& = O\left( \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
   + \frac{\ARMNUM^2 d}{1 - \exp \left(
@@
 incentivizes agents at most 
-$O \left( \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+$O \left( \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
   + \frac{\ARMNUM^2 d}{1 - \exp \left(
@@
 for a total expected regret of at most
-$O \left( \frac{\MAXR \ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+$O \left(\MAXR\cdot\max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
   + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
@@
 \begin{align}
-&E[\sum_{s=1}^{T}\sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)] \leq \sum_{s=1}^{T}\TieDensity\cdot g^2(s)Ns. \nonumber 
+&E[\sum_{s=1}^{T}\sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)] \leq \sum_{s=1}^{T}\TieDensity\cdot g^2(s)N\log(s). \nonumber 
 \end{align}
@@
 
-\begin{align*}
-&O \left( \frac{\MAXR \ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+\begin{align}
+&O \left( \MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
   + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
@@
   \cdot \ARMNUM s,
-+ \sum_{s=1}^{T}\TieDensity \cdot g^2(s)\cdot Ns.
-\end{align*}
++ \sum_{s=1}^{T}\TieDensity \cdot g^2(s)\cdot N\log(s). \label{thm:equ}
+\end{align}
 
@@
 \lefteqn{\sum_{s=1}^{T} 24\ARMNUM^2 d s \MAXR \exp\left(-2\log(T)\right)  +
-          \frac{128\Diam^2 d^2\sigma^2
-          \TieDensity\log(T)}{1.8}\sum_{s=1}^{T}\frac{1}{s}}
+          \frac{288\ARMNUM\Diam^2 d^2\sigma^2
+          \TieDensity\log(T)}{1.8}\sum_{s=1}^{T}\frac{\log(s)}{s}}
 \\ & \leq
-24\ARMNUM^2 d R\frac{T(T-1)}{2T^2}  + 71.12 \Diam^2 d^2\sigma^2
-          \TieDensity\log(T)(\log(T)+1)
+24\ARMNUM^2 d R\frac{T(T-1)}{2T^2}  + 160 \ARMNUM \Diam^2 d^2\sigma^2
+          \TieDensity(\log(T))^2(\log(T)+1)
   \\ & \leq
-12 \ARMNUM^2 d R  + 71.12 \Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1). 
+12 \ARMNUM^2 d R  + 160 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^2(\log(T)+1). 
 \end{align*}
 
-Adding all terms, and substituting the definition of
-$\LatePhase = O(\frac{\sigma^4}{x^4})$
-now gives an upper bound of
+Adding all terms gives an upper bound of
 
 \begin{multline*}
-O(\ARMNUM \MAXR \LatePhase^2) + 
-O \left( \frac{\MAXR \ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+O \left(\MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
   + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
@@
   \right)} \right) +
-O(\Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1)) 
+O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3) 
 \end{multline*}
@@
 The proof of this corollary is similar to the proof of Theorem~\ref{rst:regret}.
-If we set $g^2(t)=\frac{2\log(T)\times 64\Diam^2 d^2\sigma^2}{1.8t}$, then there exists a $t^{0}$ such that for $t>t_{0}$, $q(g(t))=0$.
-Thus, similar to equation~\eqref{equ:regret}, we know the cumulative expected regret when we let the agents play myopically is bounded above by
+If we set $g^2(s) = \frac{288\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$, then there exists a $s^{0}$ such that for $s>s_{0}$, $q(g(s))=0$.
+Thus, similar to equation~\eqref{thm:equ}, we know the cumulative expected regret when we let the agents play myopically is bounded above by
 \begin{align}
-\sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{t^{0}}\TieDensity g(t)^2 \nonumber
+\sum_{s=1}^{T} 24\ARMNUM^2 d s \MAXR \exp\left(-2\log(T)\right)+ \sum_{s=1}^{s^{0}}\TieDensity g(s)^2\ARMNUM\log(s) \nonumber
 \end{align}

### 2018-02-09 appendix.tex
edited the payment, regret and lower bound proof

@@
 \] 
-\hspace{1cm}$\geq (n-|V|)\times \frac{1}{n}=1-\frac{|V|}{n}$.
-\bccomment{Wait for Peter to address this}
-
-Let $(Z_{s,v,m}:m\geq 0)$ be a sequence of independent Bernoulli random variable with success probability $(1-\frac{v}{s})$.
+\hspace{1cm}$\geq (\ARMNUM-|V_t|)\times \frac{1}{\log(s)}$.
+\bccomment{probably we need to be more careful about $\frac{1}{\log(s)}$}.
+Let $(Z_{s,v,m}:m\geq 0)$ be a sequence of independent Bernoulli random variable with success probability $\frac{\ARMNUM-v}{\log(s)}$.
 We will construct an alternative stochastic process for selecting which arm gets played that has the same distribution as the original process, but under which
@@
 The new stochastic process will have the property that whenever $Z_{s,v(s,t),m(s,t)}=1$, we will play a new arm at time t for $t\in [t_{s-1}, t_{s}]$, where $v(s,t)$ is the number of unique arms played in phase $s$ strictly before time $t$, and $m(s,t)$ is the number of times we have pulled a previously pulled arm for the current value of $v(s,t)$.
-At time $t$, to determine what arm to pull, calculate \eqref{dom_stoc} and let $q_t$ be the probability computed.
-Note $q_t\geq 1-\frac{v(s,t)}{s}$.
+At time $t$, to determine what arm to pull, calculate \eqref{dom_stoc} \bccomment{why this eqref does not work properly?
+}and let $q_t$ be the probability computed.
+Note $q_t\geq \frac{\ARMNUM-v(s,t)}{\log(s)}$.
 
@@
 \begin{align}
-\Prob{\text{play a new arm}|\mathcal{F}_{t}}=\left[1-\frac{v(s,t)}{s}\right]+\left[1-(1-\frac{v(s,t)}{s})\right]\times \frac{q_t-(1-\frac{v(s,t)}{s})}{1-(1-\frac{v(s,t)}{s})}=q_t.
+\Prob{\text{play a new arm}|\mathcal{F}_{t}}=\frac{\ARMNUM-v}{\log(s)}+\left[1-\frac{\ARMNUM-v}{\log(s)}\right]\times \frac{q_t-\frac{\ARMNUM-v}{\log(s)}}{1-\frac{\ARMNUM-v}{\log(s)}}=q_t.
 \end{align}
@@
 Thus, if $|\Arm{i}{j}-\ArmE{t}{i}{j}|\leq \frac{12\sigma l}{s^{2/5}} \leq \frac{p^{-1}(\frac{\MinProb}{2})}{2\Diam d}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
-Further, if time $t$ is in a phase $s$ that satisfies $s^{-1}\leq \MinProb/2$, then our algorithm will not incentivize pulling any arms.
+Further, if time $t$ is in a phase $s$ that satisfies $1/log(s)\leq \MinProb/2$, then our algorithm will not incentivize pulling any arms.
 Denote $a_0=\frac{24\Diam d\sigma}{p^{-1}(\frac{\MinProb}{2})}$.
 In order to have $\frac{12\sigma l}{s^{2/5}}\leq \frac{p^{-1}(\frac{\MinProb}{2})}{2\Diam d}$, it is sufficient to have $s\geq \lceil (a_{0} l)^\frac{5}{2} \rceil$.
-In order to have $s^{-1}\leq \frac{\MinProb}{2}$, we need $s\geq \frac{2}{\MinProb}$.
-Denote $s_2=\frac{2}{\MinProb}$.
+In order to have $1/\log(s)\leq \frac{\MinProb}{2}$, we need $s\geq \exp(\frac{2}{\MinProb})$.
+Denote $s_2=\exp(\frac{2}{\MinProb})$.
 Thus, we know we can only incur regret for sample paths $\omega$ in the $\ell^{th}$ envelope in the first $\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}$ phases.
@@
 \leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24\Diam d\sigma \right]E[\bar{T}_{s}] +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24\ARMNUM d e^{-1.8(\ell-1)^2}E[\bar{T}_{s}]\nonumber \\
-\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\ARMNUM s +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24 \ARMNUM d e^{-1.8(\ell-1)^2}\ARMNUM s \nonumber \\
+\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\ARMNUM \log(s) +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24 \ARMNUM d e^{-1.8(\ell-1)^2}\ARMNUM \log(s) \nonumber \\
 \leq & \left[\MAXR+24\Diam d\sigma \right]\ARMNUM (\max\{s_2,\lceil (a_0)^{5/2} \rceil\})^2+\sum_{\ell=2}^{\infty}24\ARMNUM^2 d[\MAXR+24\Diam d\ell\sigma](\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\})^2 e^{-1.8(\ell-1)^2} \nonumber \\
-=& O(\frac{N}{\MinProb^5}+ \frac{\ARMNUM^2}{\MinProb^5}). \nonumber
+=& O(\max\{\frac{\ARMNUM^2}{\MinProb^5},\ARMNUM^2\exp(\frac{4}{\MinProb})\}). \nonumber
 \end{align}
 
+\bccomment{in the second to last inequality, I use $s\leq \log(s)$, probably a very loose bound.}
 \end{proof}
-
-\section*{Calculation for Equation~\eqref{ex:limit}}
-
-In this section, we prove $d(t)\leq \frac{z_{t,1}^{2}}{2}$ and $\lim_{t\rightarrow\infty}d(t)=\frac{z_{t,1}^2}{2}$.
-Denote $w(x)=\sqrt{x}$.
-Then we know $w(x+y)\leq \sqrt{x} + y\frac{1}{2\sqrt{x}}$ and $w(x+y)\geq \sqrt{x} + y\frac{1}{2\sqrt{x+y}}$ for $y\geq 0$.
-Thus, we know
-
-\begin{align}
-&\lim_{t\rightarrow\infty} t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right] \nonumber \\
-=& \lim_{t\rightarrow\infty} t\left[\frac{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}-\sqrt{t}-z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]  \nonumber \\
-\geq & \lim_{t\rightarrow\infty} t\left[\frac{\sqrt{t}+z_{t,2}+z_{t,1}^{2}\frac{1}{2\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}-\sqrt{t}-z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]  \nonumber \\
-= & \lim_{t\rightarrow\infty} t \times \frac{z_{t,1}^2}{2(z_{t,1}^2+(\sqrt{t}+z_{t,2})^2)} \rightarrow \frac{z_{t,1}^2}{2}. \nonumber 
-\end{align}
-and
-\begin{align}
-&\lim_{t\rightarrow\infty} t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right] \nonumber \\
-=& \lim_{t\rightarrow\infty} t\left[\frac{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}-\sqrt{t}-z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]  \nonumber \\
-\leq & \lim_{t\rightarrow\infty} t\left[\frac{\sqrt{t}+z_{t,2}+z_{t,1}^{2}\frac{1}{2\sqrt{(\sqrt{t}+z_{t,2})^2}}-\sqrt{t}-z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]  \nonumber \\
-= & \lim_{t\rightarrow\infty} t \times \frac{z_{t,1}^2}{2\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}(\sqrt{t}+z_{t,2})} \rightarrow \frac{z_{t,1}^2}{2}. \label{inequ:dct}
-\end{align}   
-Based on inequality~\eqref{inequ:dct}, we know $d(t)\leq \frac{z_{t,1}^{2}}{2}$ and $\lim_{t\rightarrow\infty}d(t)=\frac{z_{t,1}^2}{2}$.
 

### 2018-02-09 lower_bound.tex
editted the lower bound
edited the payment, regret and lower bound proof

@@
 
+\begin{align}
+&E[r(t)| \Noise{1}>0, \Noise{2}>0] \nonumber \\
+\geq & 4\times \frac{1}{3\pi} \int_{0}^{\infty} \int_{0}^{\infty} (\frac{\Noise{1}}{1+\Noise{1}+\Noise{2}})^2\frac{e^{-\frac{t \times \Noise{1}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(\Noise{1})\frac{e^{-\frac{t \times \Noise{2}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(\Noise{2}) \nonumber \\
+= & \frac{1}{3\pi^3} \int_{0}^{\infty} \int_{0}^{\infty} (\frac{\Noise{1}}{\sqrt{t}+\Noise{1}+\Noise{2}})^2e^{-\frac{\Noise{1}^2}{2}}d(\Noise{1})e^{-\frac{\Noise{2}^2}{2}}d(\Noise{2}) \nonumber 
+\end{align}
+
+Below, we want to show 
+\begin{align}
+\lim_{t\rightarrow\infty}\frac{E[r(t)| \Noise{1}>0, \Noise{2}>0]}{\frac{1}{t}} = \Omega(1), \nonumber
+\end{align}
+and use the fact that $\sum_{n=1}^{T}\frac{1}{n}=O(\log(T))$ to show the regret is at least $\Omega(\log(T))$. Since
+\begin{align}
+&\lim_{t\rightarrow \infty}\frac{E[r(t)| \Noise{1}>0, \Noise{2}>0]}{\frac{1}{t}} \nonumber \\
+\geq & \lim_{t\rightarrow \infty}\frac{1}{3\pi^3}\int_{0}^{\infty} \int_{0}^{\infty}\left[ t(\frac{\Noise{1}}{\sqrt{t}+\Noise{1}+\Noise{2}})^2\right]e^{-\frac{\Noise{1}^2}{2}}e^{-\frac{\Noise{2}^2}{2}}d(\Noise{1})d(\Noise{2}) \nonumber  \\
+= & \frac{1}{3\pi^3}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ t(\frac{\Noise{1}}{\sqrt{t}+\Noise{1}+\Noise{2}})^2\right]e^{-\frac{\Noise{1}^2}{2}}e^{-\frac{\Noise{2}^2}{2}}d(\Noise{1})d(\Noise{2}) \nonumber  \\
+=&\frac{1}{3\pi^3}\int_{0}^{\infty} \int_{0}^{\infty}e^{-\frac{\Noise{1}^2}{2}}e^{-\frac{\Noise{2}^2}{2}}d(\Noise{1})d(\Noise{2}) = \frac{1}{3\pi^3}, \nonumber
+\end{align}
+
+where the third line is due to monotone convergence theorem since the derivative of $t(\frac{\Noise{1}}{\sqrt{t}+\Noise{1}+\Noise{2}})^2$ is greater than $0$.
+
 \dkcomment{I edited up to here. Waiting for some feedback about
@@
   but it will be quite a bit uglier.}
-
-Given $z_{t,1}>0$ and $z_{t,2}>0$, we know users whose preference vector between $(-1,0)$ and $\left(\frac{-1-z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ as well as users whose preference vector between $(1,0)$ and $\left(\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{-z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ will make a mistake.
-The regret is the absolute value of the second coordinate of the user's preference vector.
-Thus, we know
-
-\begin{align}
-&E[r(t)| z_{t,1}>0, z_{t,2}>0] \nonumber \\
-=& 4\times 2 \int_{0}^{\infty} \int_{0}^{\infty} \int_{0}^{\arctan\left(\frac{z_{t,1}}{1+z_{t,2}}\right)}\frac{\sin(\theta)}{2\pi}d(\theta)\frac{e^{-\frac{t \times z_{t,1}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,1})\frac{e^{-\frac{t \times z_{t,2}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,2}) \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}t\times \left[1-\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right]e^{-\frac{t \times z_{t,1}^2}{2}}e^{-\frac{t \times z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty} \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}).
-\nonumber
-\end{align}
-
-Below, we want to show 
-\begin{align}
-\lim_{t\rightarrow\infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{\frac{1}{t}} = O(1), \nonumber
-\end{align}
-and use the fact that $\sum_{n=1}^{T}\frac{1}{n}=O(\log(T))$ to show the regret is at least $\Omega(\log(T))$.
-
-Denote $d(t)=t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]$. Based on our calculation (see appendix for details), we know $d(t)\leq \frac{z_{t,1}^2}{2}$ and
-
-\begin{align}
-\lim_{t\rightarrow \infty} d(t)=\frac{z_{t,1}^2}{2}. \label{ex:limit}
-\end{align}
-Based on the dominated convergence theorem, we know
-\begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{\frac{1}{t}} \nonumber \\
-=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber  \\
-=&\frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\left[ \frac{z_{t,1}^2}{2}e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) = \frac{1}{2\pi}. \nonumber
-\end{align}
-
-Thus, the cumulative expected regret is at least $\Omega(\log(T))$.

### 2018-02-12 algorithm.tex
did some minor changes to the paper

@@
 \begin{lemma} \label{lem:phase-length}
-For any $s$, the expected length of phase $s$ is at most
-$\ARMNUM \cdot s$ time steps.
+For any $s\geq 3$, the expected length of phase $s$ is at most
+$\ARMNUM \cdot \log(s)$ time steps.
 \end{lemma}
@@
 \leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$.
+
+\bccomment{If $b(n)$ is a constant, here we know $\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}
+\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{\sqrt{J} x}{4 \sigma}\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$.}
+
 Then, we use the following technical Lemma~\ref{lem:n0-inequality}
@@
  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
-  \cdot \ARMNUM s,
+  \cdot \ARMNUM \log(s),
 \end{align*}
@@
   \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
-  \cdot \ARMNUM s,
+  \cdot \ARMNUM \log(s),
 + \sum_{s=1}^{T}\TieDensity \cdot g^2(s)\cdot N\log(s). \label{thm:equ}
@@
 \begin{align*}
-\lefteqn{\sum_{s=1}^{T} 24\ARMNUM^2 d s \MAXR \exp\left(-2\log(T)\right)  +
+\lefteqn{\sum_{s=1}^{T} 24\ARMNUM^2 d \log(s) \MAXR \exp\left(-2\log(T)\right)  +
           \frac{288\ARMNUM\Diam^2 d^2\sigma^2
@@
 \begin{corollary} \label{cor:constant-regret}
-If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O(\ARMNUM^2)$.
+If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O \left(\MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
+  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} \right) $.
 \end{corollary}
@@
 \end{align}
-Therefore, based on the same analysis of Theorem~\ref{rst:regret}, we know the cumulative regret is bounded by $O(\ARMNUM^2)$.
+Therefore, based on the same analysis of Theorem~\ref{rst:regret}, we know the cumulative regret is bounded by $O \left(\MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
+  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} \right) $.
 \end{proof}
@@
 However, as can be seen in the proof of Lemma~\ref{lem:phase-length},
-we then lower-bound this probability by $1/s$.
+we then lower-bound this probability by $1/\log(s)$.
 Thus, the bounds we prove do not deteriorate as long as the payment is
-high enough such that arm $i$ is pulled with probability at least $1/s$.
+high enough such that arm $i$ is pulled with probability at least $1/\log(s)$.
 A sufficient payment would be defined as

### 2018-02-12 appendix.tex
did some minor changes to the paper

@@
 
-Denote $\mathcal{F}_t$ as the filtration up to time $t$. Denote $V_t$ as the set of arms that we need to pull, but haven't pulled yet in this phase. Based on our algorithm, we know
+Denote $\mathcal{F}_t$ as the filtration up to time $t$. Denote $V_t$ as the set of arms that have been pulled at least $s$ times at time $t$ in phase $s$. Based on our algorithm, we know
 
@@
 1       & \quad \text{if we incentivize}\\
-\sum_{i\in V} P(\AgentV{t} \cdot \ArmEV{t}{i}>\AgentV{t}\cdot \ArmEV{t}{j} \forall j\neq i)  & \quad \text{otherwise}  
+\sum_{i\in \{1,\cdots,\ARMNUM\}\setminus V_t} P(\AgentV{t} \cdot \ArmEV{t}{i}>\AgentV{t}\cdot \ArmEV{t}{j} \forall j\neq i)  & \quad \text{otherwise}  
 \end{cases} \label{dom_stoc}
@@
 If $Z_{s,v(s,t),m(s,t)}$ is 1, decide to play a new arm.
-Otherwise, draw a second Bernoulli random variable with probability $\frac{q_t-(1-\frac{v(s,t)}{s})}{1-(1-\frac{v(s,t)}{s})}$, and if it is 1, decide to play a new arm, and otherwise decide to play an old arm.
+Otherwise, draw a second Bernoulli random variable with probability $\frac{q_t-\frac{\ARMNUM-v(s,t)}{\log(s)}}{1-\frac{\ARMNUM-v(s,t)}{\log(s)}}$, and if it is 1, decide to play a new arm, and otherwise decide to play an old arm.
 Note that

### 2018-02-12 introduction.tex
edits to intro

@@
 
-A large number of sites are designed to facilitate joint discovery,
-sharing, and recommendations of content by large numbers of users.
-Such sites include news, photo, or video sharing sites,
+\pfedit{Many websites and apps} are designed to facilitate joint discovery,
+sharing, and recommendations of content\pfdelete{by large numbers of users}.
+Such sites include news, photo, \pfedit{and} video sharing sites,
 sites to review restaurants, hotels, or travel experiences,
@@
 \dkcomment{Insert citations.}
-By learning from the experiences of other users, individuals can make
-better choices to improve their own experience.
+By learning from the experiences of other users, individuals can \pfdelete{make
+better choices to }improve their own experience.
 
-Viewed more abstractly, the users are jointly exploring a space of
+Viewed more abstractly, users jointly explore a space of
 many options (products, news stories, photos, birdwatching sites,
@@
 
-In order to effect an outcome which is close to societally optimal,
+\pfdelete{In order }To effect an outcome \pfdelete{which is }close to societally optimal,
 it is necessary to provide exploration incentives to the individual users.
@@
 and utility derived from the principal's payment.}
-In reality, users will have different preferences, e.g., gastronomic,
-political, aesthetic, practical, etc.,
-and the preferences can typically not be observed by the principal.
-This heterogeneity presents both a challenge and an opportunity.
-On the one hand, it necessitates the exploration of more arms,
-so as to let all users discover their best option.
-On the other hand, the heterogeneity also provides exploration
-``for free,'' as users will not simply herd on one ``best'' arm.
-\emph{Our goal is to explore the impact of user heterogeneity
+In reality, users have different preferences, e.g., gastronomic,
+political, aesthetic, practical, etc.
+\pfedit{
+Indeed, the websites and mobile apps most widely used for joint discovery,
+sharing, and recommendation of content tend to concern products and items 
+with large amounts of heterogeneity in preferences (movies, restaurants,
+videos, travel experiences), and not items which have a universally
+agreed-on best order. \pfcomment{can we think of items with agreement?}
+This is perhaps because regimes with heterogeneous preferences are the
+ones where discovery of the best items is the most difficult for people, and
+where the number of items to consider is largest, and thus where online
+platforms tend to provide the greatest value.  Thus, we see an appropriate
+accounting for heterogeneity as critical to an understanding of incentivizing
+exploration in online communities.
+
+Heterogeneity presents both a challenge and an opportunity.
+On the one hand, it hides critical information about an agent's preferences
+from the principal.  This presents the principal with a path to social
+optimality that requires giving up control, allowing the agent to reveal these
+preferences through action and not obscuring them with incentives.  However,
+the principal cannot give up control completely, and must use these incentives
+to force agents to explore against their preferences, for the greater good.
+Thus, heterogeneity presents a challenge.
+
+On the other hand, heterogeneity also presents an opportunity, through the
+possibilty of ``free exploration''.  Even when left unincentivized, agents will
+play a variety of arms, revealing information about these arms' attributes.
+This stands in sharp constrast to the case of homogeneous preferences, where 
+unincentized agents will hard onto a single apparently best arm, and providing
+essentially any exploration at all requires incentives.
+}
+
+With these challenges and opportunities in mind, our goal is to understand the
+impact of user heterogeneity on our ability to achieve high social utility with
+low incentive payments, and on the best approaches for doing so.  We wish to
+understand whether incentivizing exploration with heterogeneous preferences  is
+``harder'' or ``easier'' than with homogenous ones, and to understand how 
+exploration strategies that do well in the heterogeneous preference setting
+differ from those in the homogenous one.
+
+\pfdelete{\emph{Our goal is to explore the impact of user heterogeneity
 on the tradeoff between societal utility and the principal's payments.}
+Heterogeneity in a bandit also offers a new perspective on bandit problems.
+}
 
-At a high level, we model the setting as follows.
-(Formal definitions are given in Section~\ref{sec:prob}.)
+Toward that end, we model our setting as follows.
+(We describe our model at a high level here,
+with formal definitions given in Section~\ref{sec:prob}.)
 Arms and users (or \emph{agents}) are characterized by payoff-relevant

### 2018-02-13 algorithm.tex
small edits mostly to the problem setting section, but also to other sections

@@
 Theorem~\ref{thm:main-overview} is fairly simple.
-It mostly allows agents to exploits, but when an arm is estimated to
-be extremely unlikely to be pulled by any agents,
-the algorithm incentivizes such an arm with a payment that is so high
-that the next agent is guaranteed to pull the arm.
+It mostly allows agents to exploit, but when an arm is \pfdelete{estimated to
+be extremely} \pfedit{sufficiently} unlikely to be pulled\pfdelete{by any agents},
+the algorithm incentivizes this arm with a payment high enough
+to guarantee that the next agent pulls it.
 This way, the algorithm ensures that each arm is pulled at least a

### 2018-02-13 problem_setting.tex
edits to intro
small edits mostly to the problem setting section, but also to other sections

--- 2018-02-05 problem_setting.tex
@@
 Whenever arm $i$ is pulled, its current utility-relevant features are
-determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero
+determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero \pfedit{independent} 
 Gaussian%
@@
 \footnote{We use male pronouns to refer to users and female pronouns
-  to refer to the principal. 
-  \dkcomment{Feel free to switch if you prefer it the other way.}}
+  to refer to the principal.}
 \emph{type}) $\AgentV{t} \in \R^d$ is drawn from a known distribution
 \AgentDist.
-Depending on context, we will identify a agents with their arrival time
+Depending on context, we will identify agents with their arrival time
 $t$ or their type \AgentV{t}.
@@
   only for notational convenience, and can of course be avoided by
-  raising payments infinitesimally.} arm $i$ maximizing
+  raising payments infinitesimally.
+  \pfcomment{In the finite preference setting this is clear, but it's a little bit delicate when there are continuum preferences, since regardless of the payment we offer there may always be support within our preference distribution for a $\theta$ that causes a tie.
+In this continuum setting it should instead be possible to perturb infinitessimally so that we avoid ties with probability 1.}
+  } arm $i$ maximizing
 $\argmax_i (\Pay{t}{i} + \AgentV{t} \cdot \ArmEV{t}{i})$.
@@
   definition?}
+\pfcomment{Perhaps we should say instead ``breaking ties arbitrarily'' if our results don't depend on how we break ties.}
 
-\dkcomment{Do we need this definition here?}
-We call time $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$ the
-\emph{starting point of the $n^{th}$ round}.
+\dkcomment{Do we need this definition here?}\pfcomment{I agree that we can move the definition of phase to where we define our algorithm.}
+We call time $t_{n}=\min_{t}\{\forall i, \NumPull{t}{i} \geq n\}$ the
+\emph{starting point of the $n^{th}$ phase}.
 We call the set of times $[t_{n}, t_{n+1})$ the
@@
 (or cumulative mass function if $\AgentDist(\cdot)$ is a discrete distribution)
+\pfcomment{Maybe this should just be the conditional cumulative distribution function, 
+$F_{i,i'}(z) = \Prob[\AgentDist]{(\ArmV{i}-\ArmV{i'}) \cdot \AgV \le z \mid \AgV \in \Omega_{i,i^{'}}}$?}
 of $(\ArmV{i}-\ArmV{i'}) \cdot \AgV$,
-conditioned on $\AgV \in \Omega_{i,j}$.
+conditioned on $\AgV \in \Omega_{i,i^{'}}$.
 In words, $F_{i,i'}$ is the distribution of the \emph{strength} of the
@@
 $i$ and $i'$ are the agent's first and second choices.
+\pfcomment{We should say something about what $F_{i,i'}$ is when $\Prob[\AgentDist]{\AgV \in \Omega_{i,i^{'}}}=0$.
+We know that arm $i$ is someone's best arm, but it doesn't have to be possible for $i'$ to be someone's second best arm when $i$ is best.
+Maybe we can just set $F_{i,i'}$ to be $0$ in that case.}
 

### 2018-02-13 algorithm.tex
minor edits

--- 2018-02-12 algorithm.tex
@@
 Theorem~\ref{thm:main-overview} is fairly simple.
-It mostly allows agents to exploits, but when an arm is estimated to
-be extremely unlikely to be pulled by any agents,
-the algorithm incentivizes such an arm with a payment that is so high
-that the next agent is guaranteed to pull the arm.
-This way, the algorithm ensures that each arm is pulled at least a
-certain minimum number of times.
+It mostly allows agents to exploit, but when an arm is \pfdelete{estimated to
+be extremely} \pfedit{sufficiently} unlikely to be pulled\pfdelete{by any agents},
+the algorithm incentivizes this arm with a payment high enough
+to guarantee the next agent pulls it.
+This way the algorithm ensures each arm is pulled often enough.
 
@@
 $s = 1, 2, 3, \ldots$.
-Phase $s$ ends when each arm has been pulled at least $s$ times.
+Phase $s$ \pfcomment{starts?} ends when each arm has been pulled at least $s$ times.
+We indicate the start time of phase $s$ by $t_s$.
+\pfcomment{According to the notation we had before, in the .tex file below here,
+phase $s$ starts when I have $s$ pulls of each arm.  Also, we should make sure things are clear regarding the free pull at time $0$.}
 An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
 if both of the following hold:
+\pfdelete{
+We call time $t_{s}=\min_{t}\{\forall i, \NumPull{t}{i} \geq s\}$ the
+\emph{starting point of the $s^{th}$ phase}.
+We call the set of times $[t_{s}, t_{s+1})$ the
+\emph{$n^{th}$ phase}.
+}
 
@@
 $\PullProb{t}{i} < 1/\log(s)$.
+\pfedit{$1/\log(1)$ is treated as $\infty$, and if $1/\log(s) \ge 1$ then this condition is automatically met.}
 \end{itemize}
@@
 arm, once the arms' attribute vectors are learned well enough,
-the algorithm will not need to incentivize any arm pulls any more,
+the algorithm will not need to incentivize any more,
 resulting in a payment bound independent of $T$.
 Similarly, the regret will decrease exponentially, and mostly accrue
-due to agents close to the border making mistakes in their arm choices.
+due to agents close to the border \pfcomment{we could clarify what border} making mistakes in their arm choices.
 The detailed analysis following this outline is somewhat subtle, though,
@@
 To capture the probability masses of problematic and non-problematic
-agents, we define the following:
+agents \pfcomment{in another pass we could seek to clarify what we mean by being problematic in the context of the border statement above}, we define the following:
 $\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
@@
 arm is at most $\delta$.
+\pfcomment{We can check through the whole paper on whether we have $\AgV \sim \AgentDist$ in the subscript or just $\AgV \sim \AgentDist$.
+I think we have only $\AgentDist$ in the problem description.}
 The minimum probability mass of users who prefer their best arm
@@
 \AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > \delta}$.
-Notice that while \AlmostTied{\delta} (being a measure of problematic
+Notice that \AlmostTied{\delta} (being a measure of problematic
 agents) is defined as a sum over all arms,
@@
 $s-1$ times at the start of phase $s$.
-Thus, phase $s$ ends when each $i \in S$ has been pulled at least once.
+Thus, phase $s$ \pfedit{has ended} when each $i \in S$ has been pulled at least once.
 Consider any time step $t$.

### 2018-02-13 Discussion.tex
added a new discussion tex file

--- 2018-02-12 algorithm.tex
@@
-\section{Main Algorithm and Analysis}
-\label{sec:ub}
-
-The algorithm achieving the claimed bounds of
-Theorem~\ref{thm:main-overview} is fairly simple.
-It mostly allows agents to exploits, but when an arm is estimated to
-be extremely unlikely to be pulled by any agents,
-the algorithm incentivizes such an arm with a payment that is so high
-that the next agent is guaranteed to pull the arm.
-This way, the algorithm ensures that each arm is pulled at least a
-certain minimum number of times.
-
-More precisely, the algorithm divides time into \emph{phases}
-$s = 1, 2, 3, \ldots$.
-Phase $s$ ends when each arm has been pulled at least $s$ times.
-An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
-if both of the following hold:
-
-\begin{itemize}
-\item $i$ has been pulled at most%
-\footnote{in fact: exactly, since the algorithm entered phase $s$}
-$s-1$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s-1$.
-\item Based on the current estimates \ArmEV{t}{i'} of all arms'
-attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s)$. \bccomment{Do we need to mention what if $\frac{1}{\log(s)}>1$? }
-Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
-  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
-be the probability that arm $i$ will be pulled
-by the next (random) agent based on the current estimates. 
-Then, the second criterion for payment-eligibility is that
-$\PullProb{t}{i} < 1/\log(s)$.
-\end{itemize}
-
-When multiple arms are payment-eligible, the algorithm picks one
-uniformly at random to incentivize.
-When the algorithm decides to incentivize an arm $i$,
-it offers ``whatever it takes,'' i.e., offers a payment of
-$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$.
-The maximum for \AgV is taken over the support of \AgentDist;
-recall that we assumed this support to be compact.
-The payment \Pay{t}{i} may appear unnecessarily high.
-Indeed, we show in Section~\ref{sec:pi} that it suffices to
-incentivize only a $1/\log(s)$ fraction of the agents.
-\dkcomment{Given that we don't prove anything there, is ``show'' the
-  right word?}
-Here, we focus on the higher payments for simplicity of analysis.
-
-Notice that \PullProb{t}{i} depends on the estimates for \emph{all}
-arms; thus, by pulling some other arm $i'$, an arm $i$ may become
-payment-eligible, or cease to be so.
-Algorithm~\ref{alg:basic-incentivizing} gives the full details.
-
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration \label{alg:basic-incentivizing}}
-\begin{algorithmic}
-\STATE Set the current phase number $s = 1$.
-\FOR{time steps $t = 1, 2, 3, \ldots$}
-\IF{$\NumPull{t}{i} \geq s$ for all arms $i$}
-\STATE Increment the phase $s = s + 1$.
-\ENDIF
-\IF{there is a payment-eligible arm $i$}
-\STATE Let $i$ be a uniformly random payment-eligible arm.
-\STATE Offer payment
-$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$
-for pulling arm $i$
-(and payment 0 for all other arms).
-\ELSE
-\STATE Let agent $t$ play myopically, i.e., offer payments 0 for all arms.
-\ENDIF
-\ENDFOR
-\end{algorithmic}
-\end{algorithm}
-
-The high-level idea of the proof of Theorem~\ref{thm:main-overview}
-is the following.
-Because the algorithm ensures that each arm is pulled
-``frequently enough,''
-the estimates \ArmEV{t}{i} become exponentially more accurate in the
-phase number $s$.
-Thus, the fraction of agents who misidentify their best arm decreases
-exponentially as well.
-Because for each arm, enough agents have a true preference for this
-arm, once the arms' attribute vectors are learned well enough,
-the algorithm will not need to incentivize any arm pulls any more,
-resulting in a payment bound independent of $T$.
-Similarly, the regret will decrease exponentially, and mostly accrue
-due to agents close to the border making mistakes in their arm choices.
-The detailed analysis following this outline is somewhat subtle, though,
-due to the dependencies between the agents' arm pulls and the
-estimates which in turn are based on past arm pulls.
-We begin with several technical lemmas that are used for both the
-payment and regret bounds.
-
-To capture the probability masses of problematic and non-problematic
-agents, we define the following:
-$\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
-\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
-is the total probability mass (across all arms) of agents
-whose (actual) preference for their best arm over their second-best
-arm is at most $\delta$.
-The minimum probability mass of users who prefer their best arm
-sufficiently strongly over their second-best arm is denoted by
-$\ClearPref{\delta} = \min_{i}
-\Prob[\AgV \sim \AgentDist]{\Best{\AgV}=i,%
-\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > \delta}$.
-Notice that while \AlmostTied{\delta} (being a measure of problematic
-agents) is defined as a sum over all arms,
-while  \ClearPref{\delta} (being a measure of non-problematic agents)
-is defined as a minimum over arms.
-Also notice that $\ClearPref{0} = \MinProb$.
-\dkcomment{We should stress somewhere that we assume that actual ties
-  have measure 0.}
-
-In this section, we prove Algorithm~\ref{alg:basic-incentivizing} achieves $O(\ARMNUM^2+\TieDensity(\log(T))^2)$ cumulative regret with $O(\ARMNUM^2)$ payment budget.
-This is stated in the following pair of theorems, which together constitute our main results.
-
-\begin{theorem}
-The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by $O(\ARMNUM^2)$. 
-\label{rst:budget}
-\end{theorem}
-
-\begin{theorem}
-The cumulative regret for Algorithm~\ref{alg:basic-incentivizing}
-is bounded above by $O(\ARMNUM^2 d + \TieDensity d^2(\log(T))^2)$.
-\label{rst:regret}
-\end{theorem}
-
-\subsection{General Lemmas}
-
-We begin by showing that under our assumptions, the measure of
-problematic arms cannot be too large.
-
-\begin{lemma} \label{lem:sdelta}
-$\AlmostTied{\delta} \leq \TieDensity \cdot \delta$ for all $\delta$.
-\end{lemma}
-
-\begin{emptyproof}
-Using the upper bound from Assumption~\ref{A1}, we can bound
-
-\begin{align*}
-\AlmostTied{\delta}
-& = \sum_{i,i'} \ProbC{\AgV \cdot (\ArmV{i} - \ArmV{i'}) \leq \delta}%
-    {\AgV \in \FirstTwo{i}{i'}}
-  \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}\\
-& \leq \sum_{i,i'} \TieDensity \cdot \delta
-    \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}
-\; = \; \TieDensity \cdot \delta. \QED
-\end{align*}
-\end{emptyproof}
-
-We next bound the length of any phase, which will be useful to bound
-the cumulative regret of the early rounds
-(before tail bounds have kicked in).
-
-\begin{lemma} \label{lem:phase-length}
-For any $s\geq 3$, the expected length of phase $s$ is at most
-$\ARMNUM \cdot \log(s)$ time steps.
-\end{lemma}
-
-\begin{proof}
-Let $S$ be the set of arms that have been pulled at most
-$s-1$ times at the start of phase $s$.
-Thus, phase $s$ ends when each $i \in S$ has been pulled at least once.
-Consider any time step $t$.
-If $S$ contains at least one payment-eligible arm $i$,
-then some payment-eligible arm will be pulled with probability 1,
-and every payment-eligible arm is in $S$.
-In particular, the size of $S$ decreases with probability 1.
-If $S$ contains no payment-eligible arm,
-then by definition of payment-eligibility,
-each arm $i \in S$ has probability at least $1/\log(s)$ of being pulled.
-In particular, the size of $S$ decreases with probability at least $1/\log(s)$.
-
-In either case, the expected number of time steps until
-$|S|$ decreases is at most $s$,
-so the expected number of steps until $S$ is empty is at most
-$\ARMNUM \cdot \log(s)$.
-\dkcomment{If we wanted, this bound could probably be improved using a
-  coupon collector argument. But it would look uglier.}
-\end{proof}
-
-The key technical lemma captures the intuition that
-the estimates of the arms' attribute vectors become
-exponentially more accurate with increasing phases $s$.
-That intuition is captured by the following lemma.
-
-\begin{lemma} \label{lem:round-prob}
-Let $x > 0$ be arbitrary.
-Recall that $\sigma$ is the standard deviation of the Gaussian noise.
-Let $\LatePhase \geq \max \SET{50, \frac{92.16 \sigma^4}{x^4}}$.
-
-\dkcomment{Is it problematic that we use $\sigma$ for two things here?}
-Let $\tau$ be any stopping time that is almost surely \dkcomment{What
-  exactly do we mean by this here?} in phase $s$,
-with respect to the filtration
-$\mathcal{F}_{t} = \sigma (\Pull{1}, \ldots, \Pull{t},
-                          \PayA{1}, \ldots, \PayA{t},
-                          \ObsV{1}, \ldots, \ObsV{t})$.
-Then, for all phases $s \geq \LatePhase$,
-with probability at least 
-$1- 24 \ARMNUM d \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$,
-the following holds for all arms $i$ and attributes $j$
-simultaneously:
-$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$.
-\dkcomment{We should clarify what the probability is over. It seems to
-  be over the entire past history, but not the current type.}
-\end{lemma}
-
-The proof of Lemma~\ref{lem:round-prob} is based on an adaptive
-concentration inequality due to \cite{zhao2016adaptive},
-given as Lemma~\ref{lem:ACI-inequality}.
-
-\begin{lemma}[Corollary 1 of \cite{zhao2016adaptive}]
-\label{lem:ACI-inequality}
-Let $X_i$ be zero-mean $1/2$-subgaussian random variables,
-and $\SET{S_n = \sum_{i=1}^n X_i, n \geq 1}$ the corresponding random walk.
-Let $J$ be any stopping time with respect to $\SET{X_1, X_2, \ldots}$.
-(We allow $J$ to take the value $\infty$,
-defining $\Prob{J = \infty} = 1 - \lim_{n \to \infty} \Prob{J \leq n}$.)
-Define \dkcomment{I'm making the dependence of $b$ on $n$ explicit,
-  since that's how we're using it.}
-\begin{align*}
-g(n) & = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b(n)}.
-\end{align*}
-Then, 
-\begin{align*}
-\Prob{J < \infty \mbox{ and } S_J \geq g(J)} \leq 12 \e^{-1.8 b(n)}.
-\end{align*}
-\end{lemma}
-
-\begin{extraproof}{Lemma~\ref{lem:round-prob}}
-Fix an arm $i$ and attribute $j$.
-For any $n \geq 1$, let $k_n$ be the time step right after arm $i$ has
-been pulled for the \Kth{n} time.
-\dkcomment{I'm writing $n$ instead of $s$ here because $S_s$ would
-  look ugly, and $n$ is consistent with the lemma.
-  Or we could rename $S$ to something else.}
-Define
-$S_n := \frac{n \cdot (\ArmE{k_n}{i}{j} - \Arm{i}{j})}{2 \sigma}$
-to be the sum of all attribute-$j$ noise components up to and
-including the \Kth{n} pull of arm $i$,
-\dkcomment{I'm not sure if we have defined the notation for components
-  of vectors in the \emph{superscript}. Let's make sure not to forget it.}
-renormalized to have standard deviation $1/2$.
-\dkcomment{Is this the correct scaling.}
-The $S_n$ define an unbiased half-subgaussian random walk,
-and we can therefore apply Lemma~\ref{lem:ACI-inequality} to them.
-Specifically, we set $b(n) = \frac{n x^2}{16 \sigma^2}$,
-and obtain that
-
-\begin{align*}
-\Prob{J < \infty \mbox{ and } S_J \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}}
-& \leq 12 \exp \left( \frac{-1.8 J x^2}{16 \sigma^2} \right).
-\end{align*}
-
-Applying Lemma~\ref{lem:ACI-inequality} to $-S_n$ with the same choice
-of $b(n)$, and taking a union bound over both cases, we obtain that
-
-\begin{align*}
-\Prob{J < \infty \mbox{ and } |S_J| \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}}
-& \leq 24 \exp \left( \frac{-1.8 J x^2}{16 \sigma^2} \right).
-\end{align*}
-
-In the high-probability case
-$|S_J| \leq
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}$,
-we first use that $\sqrt{\cdot}$ is sublinear to bound
-$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}
-\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$.
-
-\bccomment{If $b(n)$ is a constant, here we know $\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}
-\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{\sqrt{J} x}{4 \sigma}\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$.}
-
-Then, we use the following technical Lemma~\ref{lem:n0-inequality}
-(whose proof is given in the appendix, and whose precondition we verify
-momentarily) to bound the first term,
-giving us an overall upper bound of
-$|S_J| \leq \frac{J x}{2 \sigma}$.
-
-\begin{lemma} \label{lem:n0-inequality}
-For any $n \geq \LatePhase = \max (50, \frac{92.16 \sigma^4}{x^4})$, 
-\begin{align*}
-\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} & \leq \frac{n x}{4 \sigma}. 
-\end{align*}
-\end{lemma}
-
-Substituting the definition of $S_J$ and canceling common terms,
-the inequality implies that
-$|\ArmE{k_J}{i}{j} - \Arm{i}{j}| \leq x$.
-By the assumptions of the lemma,
-the stopping time $\tau$ is such that almost surely, each arm --- and
-in particular arm $i$ --- has been pulled at least
-$s \geq \LatePhase$ times at time $\tau$.
-Defining $J$ to be the number of times that $i$ has been pulled at
-time $\tau$, we obtain that $J$ satisfies the precondition of
-Lemma~\ref{lem:n0-inequality}.
-Furthermore, with probability 1, $J$ will be finite, meaning that
-\begin{align*}
-& \Prob{S_J \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16
-    \sigma^2}}}\\
-= & \Prob{J < \infty \mbox{ and } S_J \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16
-    \sigma^2}}}.
-\end{align*}
-
-Finally, this choice of $J$ ensures that
-$\ArmE{k_J}{i}{j} = \ArmE{\tau}{i}{j}$,
-and we have thus shown that
-$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$ for all $i,j$.
-The lemma now follows by a union bound over all \ARMNUM arms and $d$
-attributes.
-\end{extraproof}
-
-Lemma~\ref{lem:round-prob} implies that errors from myopic play
-decrease exponentially in the phase number $s$.
-
-\begin{corollary} \label{cor:right-choice}
-Let $x > 0$ be arbitrary.
-Let $\LatePhase \geq \max (50, \frac{92.16 \sigma^4}{x^4})$.
-
-Let $\tau$ be any stopping time that is almost surely \dkcomment{What
-  exactly do we mean by this here?} in phase $s$,
-with respect to the filtration
-$\mathcal{F}_{t} = \sigma (\Pull{1}, \ldots, \Pull{t},
-                          \PayA{1}, \ldots, \PayA{t},
-                          \ObsV{1}, \ldots, \ObsV{t})$.
-Then, for all $s \geq \LatePhase$,
-with probability (over the past history) at least 
-$1 - 24 \ARMNUM d \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$,
-\dkcomment{We should clarify what the probability is over. It seems to
-  be over the past history, but not the current agent.}
-an agent of type $\AgV = \AgentV{\tau}$ 
-will not pull a highly suboptimal arm, i.e., an arm $i$ with 
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
-\end{corollary}
-
-\begin{proof}
-Let $\tau$ be a (random) time.
-By Lemma~\ref{lem:round-prob},
-with probability at least
-$1 - 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16\sigma^2} \right)$,
-for all arms $i$ and attributes $j = 1, \ldots, d$ simultaneously,
-the estimated attribute $j$ for arm $i$ is close enough to the true attribute: 
-$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$.
-Condition on this high-probability event.
-
-Consider any agent type $\AgV = \AgentV{\tau}$ at the (random) time
-$\tau$.
-Let $i \neq \Best{\AgV}$ be any arm
-with much smaller true reward than the best arm:
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
-Because each coordinate of \ArmEV{\tau}{\Best{\AgV}} and of
-\ArmEV{\tau}{i} is estimated accurately to within $x$, 
-we get that 
-$\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
-\geq - \Diam d x$
-and
-$\AgV \cdot (\ArmEV{\tau}{i} - \ArmV{i}) \leq \Diam d x$.
-Hence,
-
-\begin{align}
-\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmEV{\tau}{i})
-& =
-\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
-+ \AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i})
-+ \AgV \cdot (\ArmV{i} - \ArmEV{\tau}{i}) \nonumber\\
-& > -\Diam d x + 2 \Diam d x - \Diam d x
-\; = \; 0, \label{equ:choice}
-\end{align}
-which means that the agent with type \AgV will not pull arm $i$
-under the high-probability event.
-\end{proof}
-
-\subsection{Bounding the Total Payment}
-
-Towards bounding the algorithm's total payment, we first bound the
-\emph{number} of rounds in which the algorithm makes a payment by a
-constant.
-This bound also turns out to be useful for bounding the total regret.
-
-\begin{lemma} \label{lem:numP}
-The expected number of time steps in which
-Algorithm~\ref{alg:basic-incentivizing}
-makes any payment is at most $O(\ARMNUM^2)$.
-\end{lemma}
-
-\begin{proof}
-We partition phases into early and late phases.
-For each of the early phases,
-we crudely bound the number of payments by \ARMNUM,
-using that each arm is incentivized at most once per phase.
-For later phases,
-we use that arms are payment-eligible only if their myopic pulling
-probability is less than $1/\log(s)$.
-Since at least a \MinProb fraction of agents would prefer arm $i$ if
-given accurate estimates, this would require misestimates that make a
-significant fraction of agents pull the wrong arm.
-But in later phases, such misestimates are unlikely by
-Corollary~\ref{cor:right-choice}.
-
-To make this intuition precise, we set
-$\delta = \frac{\MinProb}{2 \TieDensity}$,
-and $x = \frac{\delta}{2 \Diam d}$.
-The cutoff point between early and late phases is now set to
-$\EvenLaterPhase = \max(50, \frac{92.16 \sigma^4}{x^4}, \exp(\frac{2}{\MinProb}))$.
-Consider the \Kth{s} pull of an arm $i$, for $s \geq \EvenLaterPhase$.
-If this pull occurs before phase $s$, it was definitely not incentivized.
-So we condition on the pull occurring in phase $s$,
-and let $\tau$ be the time step when this pull occurred; notice that
-this means that this must be the first pull of arm $i$ in phase $s$.
-We can now apply Corollary~\ref{cor:right-choice}
-with this choice of $x$,
-and obtain that with probability at least 
-$1 - 24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$,
-all agent types \AgV with
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}})
-> 2\Diam d x = \delta$
-will pull their best arm \Best{\AgV}.
-\dkcomment{We are losing a factor \ARMNUM here.
-We already took a union bound over all arms in the lemma, and
-we now apply it only to one arm, then sum over all arms.}
-
-By Lemma~\ref{lem:sdelta}, the \emph{total} measure of agents (across
-all arms) whose best and second-best arm differ in utility by less
-than $\delta$ is at most $\TieDensity \delta = \frac{\MinProb}{2}$.
-In particular, this bound holds for agents whose best arm is $i$.
-By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
-as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
-has arm $i$ as their preferred arm by at least $\delta$ over any other
-arm $i'$.
-In the high-probability event, all such agents would myopically pull
-the arm $i$, and as a result, in the high-probability event,
-arm $i$ is not payment-eligible.
-
-Thus, for any phase $s \geq \EvenLaterPhase$
-Algorithm~\ref{alg:basic-incentivizing} incentivizes any given arm $i$
-with probability at most
-$24 \ARMNUM d \cdot \exp \left(
-  -\frac{1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-\right)$.
-Summing over all arms and phases $s$,
-and adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
-the first \EvenLaterPhase phases, 
-the expected total number of arm incentivizations is at most
-\begin{align*}
-\ARMNUM \EvenLaterPhase
-  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)}
-& = O\left( \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
-  + \frac{\ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right).
-\end{align*}
-\dkcomment{It seems like with our choice of $x$ (which may be
-  unavoidable), we get quite large factors, in particular with the
-  fourth power.
-  Also, it would be nice if we could simplify the $\frac{1}{1-\exp()}$
-  term. Unfortunately, I think that the inequality goes the wrong way
-  for applying the standard $\exp(-x) \geq 1-x$ bound.}
-
-\dkcomment{I'm leaving in all the dependencies on ``constant''
-  parameters for now. We can decide later which ones to absorb into
-  big-$O$.}
-\end{proof}
-
-It would be desirable to simply identify a constant upper bound on the
-payment made each time.
-Unfortunately, while the agent types are drawn from a bounded support,
-the noise in arm locations is not;
-hence, with small probability, arm locations may be grossly
-misestimated, resulting in high incentive payments.
-As a result, the actual analysis of the total payment is significantly more
-intricate, and hence,
-the proof of Theorem~\ref{rst:budget} is given in the appendix.
-
-\subsection{Bounding the Total Regret}
-In bounding the total regret, because agents' types are from a compact
-set by Assumption~\ref{A2}, the maximum regret in any one round is
-bounded by a constant.
-We use $\MAXR = \max_{\AgV, i,i'} \AgV \cdot (\ArmV{i} - \ArmV{i'})$
-to denote this constant upper bound on the maximum regret that can be
-incurred in any one time step.
-
-\dkcomment{The following paragraph is from Bangrui's version. It may
-  move to an earlier section, go away, or become a part somewhere.}
-As we can see later in our proof, we only need
-$\max_{i,j}\limsup_{y\rightarrow 0^{+}}\frac{F_{i,j}(y)}{y}$ to be
-finite.
-Intuitively, Assumption~\ref{A1} states that there are not many agents
-who are indifferent between their best arm and the second best arm.
-
-\begin{proof}
-Regret can arise in two ways:
-(1) an agent was incentivized to pull a suboptimal arm, or
-(2) an agent myopically pulled a suboptimal arm.
-By Lemma~\ref{lem:numP}, Algorithm~\ref{alg:basic-incentivizing}
-incentivizes agents at most 
-$O \left( \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
-  + \frac{\ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right)$
-times in expectation, each time causing regret at most \MAXR,
-for a total expected regret of at most
-$O \left(\MAXR\cdot\max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
-  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right)$.
-For the rest of the proof, we focus on the regret incurred when agents
-pull arms myopically and make mistakes.
-
-We distinguish between agents incurring large regret
-(which requires severe misestimates of arm locations;
-such misestimated are exponentially unlikely to occur), 
-and agents incurring small positive regret,
-which requires these agents to be almost tied in their preference for
-the best arm.
-To be more precise, we will define (with hindsight) a phase-dependent
-cutoff $g(s)$, and consider a regret exceeding $g(s)$ large.
-
-We first consider agents \AgV incurring positive regret less than $g(s)$.
-The second-best arm \Second{\AgV} of \AgV must satisfy
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(s)$.
-By Lemma~\ref{lem:sdelta}, the total measure of such agents
-is $\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$,
-and each incurs regret at most $g(s)$.
-Summing over all time steps, the expected total regret from such agents is at most
-\begin{align}
-&E[\sum_{s=1}^{T}\sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)] \leq \sum_{s=1}^{T}\TieDensity\cdot g^2(s)N\log(s). \nonumber 
-\end{align}
-
-To bound the regret incurred in time steps with large regret,
-let the random variable $t_s$ be the final time step in phase $s$,
-for each $s$.
-\dkcomment{Is $t_s$ better or $T_s$?}
-Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
-time step in the \Kth{s} phase,
-with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
-i.e., $k > t_{s}-t_{s-1}$.
-For $t = \tau_{s}^{k}$, we know
-\begin{align}
-&\Prob{\text{incur regret exceeding g(s)}} \nonumber \\
-\leq & \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}}.\nonumber 
-\end{align}
-
-Because the regret never exceeds \MAXR,
-the expected (large) regret for the \Kth{k} time step of phase $s$
-is bounded above by
-$\Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR$.
-Summing over all time steps $t$, we get that the total regret from
-large-regret steps is at most
-
-\begin{align*}
-\lefteqn{\sum_{s = 1}^T \sum_{t=t_s}^{t_{s+1}-1}
-  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR}
-\\ & =
-\sum_{s = 1}^T 
-  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
-  \cdot \Expect{\mbox{Length of phase } s}
-\\ & \leq
-\sum_{s = 1}^T 
- \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
-  \cdot \ARMNUM \log(s),
-\end{align*}
-where the inequality was an application of Lemma~\ref{lem:phase-length}.
-Adding all three terms,
-the cumulative regret up to time $T$ is at most
-
-\begin{align}
-&O \left( \MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
-  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right)
-\\
-+ & \sum_{s = 1}^T 
-  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
-  \cdot \ARMNUM \log(s),
-+ \sum_{s=1}^{T}\TieDensity \cdot g^2(s)\cdot N\log(s). \label{thm:equ}
-\end{align}
-
-The first line is independent of $T$, and we now choose
-$g^2(s) = \frac{288\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$
-with the goal of minimizing the second line.
-With this choice and same definition of $S_{s}$ as in the proof of Lemma~\ref{lem:round-prob}, 
-\begin{align*}
-&\Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \\
-\leq &\sum_{i,j}\Prob{|S_s|\geq 3\sqrt{\frac{2}{1.8}s\log(T)}} \\
-\leq &\sum_{i,j}\Prob{|S_s|\geq \sqrt{0.6s\log(\log_{1.1}(s)+1)+\frac{2}{1.8}\log(T)s}} \leq 24\ARMNUM d \cdot \exp(-2\log(T)),
-\end{align*}
-where the second to last inequality is because the following technical inequality, whose proof we include in the appendix.
-
-\begin{lemma} \label{lem:n1-inequality}
-For $2\leq s\leq T$, we have $3\sqrt{\frac{2}{1.8}s\log(T)} \geq \sqrt{0.6s\log(\log_{1.1}(s)+1)+\frac{2}{1.8}\log(T)s}$.
-\end{lemma}
-
-\bccomment{I believe the calculation up to this line should be correct now. The final equation we want to minimize is $\sum_{s=1}^{T}[\exp(-s*g^2(s))+g^2(s)*s]$, what should be our choice of $g(s)$?}
-
-Therefore, the second line becomes
-
-\begin{align*}
-\lefteqn{\sum_{s=1}^{T} 24\ARMNUM^2 d \log(s) \MAXR \exp\left(-2\log(T)\right)  +
-          \frac{288\ARMNUM\Diam^2 d^2\sigma^2
-          \TieDensity\log(T)}{1.8}\sum_{s=1}^{T}\frac{\log(s)}{s}}
-\\ & \leq
-24\ARMNUM^2 d R\frac{T(T-1)}{2T^2}  + 160 \ARMNUM \Diam^2 d^2\sigma^2
-          \TieDensity(\log(T))^2(\log(T)+1)
-  \\ & \leq
-12 \ARMNUM^2 d R  + 160 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^2(\log(T)+1). 
-\end{align*}
-
-Adding all terms gives an upper bound of
-
-\begin{multline*}
-O \left(\MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
-  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right) +
-O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3) 
-\end{multline*}
-
-on the cumulative expected regret.
-\dkcomment{I see a problem here: What's the value of $x$ in the
-  definition of \LatePhase? Presumably, we need to make $x$ small
-  enough that any $x$ we use in any application of Lemma 7 (or
-  Corollary 10) works. But notice that we use $x =
-  \Theta(g^2(\tau_s^k))$,
-  and in particular for the last step, I don't see how we can make
-  $\tau_s^k$ much smaller than $T$.
-  But then, we get that $x = O(\frac{\log T}{T})$, which would give
-  linear regret. How to handle this?}
-\end{proof}
-
-\dkcomment{Edited up to here.}
-
-\begin{corollary} \label{cor:constant-regret}
-If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O \left(\MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
-  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right) $.
-\end{corollary}
-
-\begin{proof}
-The proof of this corollary is similar to the proof of Theorem~\ref{rst:regret}.
-If we set $g^2(s) = \frac{288\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$, then there exists a $s^{0}$ such that for $s>s_{0}$, $q(g(s))=0$.
-Thus, similar to equation~\eqref{thm:equ}, we know the cumulative expected regret when we let the agents play myopically is bounded above by
-\begin{align}
-\sum_{s=1}^{T} 24\ARMNUM^2 d s \MAXR \exp\left(-2\log(T)\right)+ \sum_{s=1}^{s^{0}}\TieDensity g(s)^2\ARMNUM\log(s) \nonumber
-\end{align}
-Therefore, based on the same analysis of Theorem~\ref{rst:regret}, we know the cumulative regret is bounded by $O \left(\MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
-  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right) $.
-\end{proof}
-
 \subsection{Decreasing the Payment} \label{sec:pi}

### 2018-02-13 algorithm.tex
added a new discussion tex file

@@
 \end{proof}
-
-\subsection{Decreasing the Payment} \label{sec:pi}
-\dkcomment{Does this really need a whole subsection now?}
-
-In Algorithm~\ref{alg:basic-incentivizing},
-the payment \Pay{t}{i} offered for pulling payment-eligible arms $i$
-is high enough to ensure that arm $i$ will be pulled with probability 1.
-However, as can be seen in the proof of Lemma~\ref{lem:phase-length},
-we then lower-bound this probability by $1/\log(s)$.
-Thus, the bounds we prove do not deteriorate as long as the payment is
-high enough such that arm $i$ is pulled with probability at least $1/\log(s)$.
-A sufficient payment would be defined as
-$\Pay{t}{i} = \sup \Set{c \geq 0}{%
-  \Prob[\AgV \sim \AgentDist]{c + \AgV \cdot \ArmEV{t}{i} \leq \AgV \cdot \ArmEV{t}{i'}}}$.
-Except for offering different payments, the algorithm remains unchanged.
-Then, the exact same analysis shows that the modified algorithm
-provides the same guarantees.

### 2018-02-14 Discussion.tex
edited the discussion section

@@
+\subsection{Special Case}
+
+As we see in the proof of Theorem~\ref{rst:budget} and Theorem~\ref{rst:regret}, we occurred an exponential payment/regret at the initial phases simplily because we decrease the probability threshold too slowly, which is needed when bounding the regret after the concentration probability kicks in as in Equation~(\ref{equ:small_regret_bound}).
+In this section, we are going to discuss two special cases where we can get rid of the exponential dependency on the number of arms in the payment and regret bound.
+
+\textbf{Case 1: If $\exists \delta_0>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$.}
+
+In this case, we can simplily modify the payment-eligible criteria as follows: An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
+if both of the following hold:
+
+\begin{itemize}
+\item $i$ has been pulled at most%
+\footnote{in fact: exactly, since the algorithm entered phase $s$}
+$s-1$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s-1$.
+\item Based on the current estimates \ArmEV{t}{i'} of all arms'
+attribute vectors, the probability of pulling arm $i$ is less than $1/s$. Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
+  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
+be the probability that arm $i$ will be pulled
+by the next (random) agent based on the current estimates. 
+Then, the second criterion for payment-eligibility is that
+$\PullProb{t}{i} < 1/s$.
+\end{itemize}
+
+The algorithm remains the same as Algorithm~\ref{alg:basic-incentivizing}. Under this new payment-eligible criteria, we are able to prove the following results:
+
+\begin{theorem}
+The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by $O(\ARMNUM^2)$. 
+\end{theorem}
+
+\begin{proof}
+The proof is exact the same as the proof for Lemma~\ref{rst:budget} except we now define $s_2 =\frac{2}{p}$. The rest of the proof remains the same.
+\end{proof}
+
+\begin{lemma}  \label{lem:NumP1}
+The expected number of time steps in which
+Algorithm~\ref{alg:basic-incentivizing}
+makes any payment is at most 
+\begin{align}
+O\left(\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+  + \frac{\ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} \right). \nonumber 
+\end{align}
+\end{lemma}
+
+\begin{proof}
+The proof is exact the same as the proof for Lemma~\ref{lem:numP} except we now define $\EvenLaterPhase = \max(50, \frac{92.16 \sigma^4}{x^4}, \frac{2}{p})$.
+\end{proof}
+
+\begin{theorem}
+The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
+\begin{align}
+O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} \right).  \nonumber
+\end{align}
+\end{theorem}
+
+\begin{proof}
+The proof of this Theorem is similar as Theorem~\ref{rst:regret}, except
+\begin{itemize}
+\item We can use Lemma~\ref{lem:NumP1} to bound the regret when we decide to incentivize;
+\item The expected length of phase $s$ is bounded by $\ARMNUM s$;
+\item The regret in Equation~\ref{equ:small_regret_bound} can now be bounded by a constant based on our assumption.
+\end{itemize}
+The rest of the proof remains the same.
+\end{proof}
+
+\textbf{Case 2: If we know $\MinProb$ in advance.}
+
+If we know $\MinProb$ in advance, we can modify the payment-eligible criteria as follows: Denote $s_0=\min_{s=1,2,\cdots,}\{\frac{1}{\log(s_0)}\leq \frac{\MinProb}{2}\}$.
+An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
+if both of the following hold:
+
+\begin{itemize}
+\item $i$ has been pulled at most%
+\footnote{in fact: exactly, since the algorithm entered phase $s$}
+$s-1$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s-1$.
+\item Based on the current estimates \ArmEV{t}{i'} of all arms'
+attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s+s_0)$. Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
+  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
+be the probability that arm $i$ will be pulled
+by the next (random) agent based on the current estimates. 
+Then, the second criterion for payment-eligibility is that
+$\PullProb{t}{i} < 1/\log(s+s_0)$.
+\end{itemize}
+
+The algorithm remains the same as Algorithm~\ref{alg:basic-incentivizing}. Under this new algorithm, we can prove:
+
+\begin{theorem}
+The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by $O(\ARMNUM^2)$. 
+\end{theorem}
+
+\begin{proof}
+The proof is exact the same as the proof for Lemma~\ref{rst:budget} except we no longer needs $s_2$. The rest of the proof remains the same.
+\end{proof}
+
+\begin{lemma}  \label{lem:NumP2}
+The expected number of time steps in which
+Algorithm~\ref{alg:basic-incentivizing}
+makes any payment is at most 
+\begin{align}
+O\left(\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+  + \frac{\ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} \right). \nonumber 
+\end{align}
+\end{lemma}
+
+\begin{proof}
+The proof is exact the same as the proof for Lemma~\ref{lem:numP} except we now define $\EvenLaterPhase = \max(50, \frac{92.16 \sigma^4}{x^4})$ since $\frac{1}{\log(s+s_0)}\leq \frac{p}{2}$ is true for all $s$.
+\end{proof}
+
+\begin{theorem}
+The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
+\begin{align}
+O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} +\frac{\ARMNUM^2 d\MAXR}{p}+\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{p}\right).  \nonumber
+\end{align}
+\end{theorem}
+
+\begin{proof}
+The proof of this Theorem is similar as Theorem~\ref{rst:regret}, except
+\begin{itemize}
+\item We can use Lemma~\ref{lem:NumP2} to bound the regret when we decide to incentivize;
+\item The expected length of phase $s$ is bounded by $\ARMNUM \log(s+s_0)$;
+\item With the same choice of $g(s)$, the regret in Equation~\ref{equ:small_regret_bound} can now be bounded by $160 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1)\log(T+s_0)=O(\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{p})$.
+\end{itemize}
+The rest of the proof remains the same.
+\end{proof}
+
 \subsection{Decreasing the Payment} \label{sec:pi}

### 2018-02-14 algorithm.tex
edited the discussion section

@@
 \begin{theorem}
-The cumulative regret for Algorithm~\ref{alg:basic-incentivizing}
-is bounded above by $O(\ARMNUM^2 d + \TieDensity d^2(\log(T))^2)$.
+For any given $T$, the cumulative regret for Algorithm~\ref{alg:basic-incentivizing}
+is bounded above by 
+\begin{align}
+O \left(\MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
+  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} \right) +
+O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3).
+\end{align}
 \label{rst:regret}
@@
 \begin{align}
-&E[\sum_{s=1}^{T}\sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)] \leq \sum_{s=1}^{T}\TieDensity\cdot g^2(s)N\log(s). \nonumber 
+&E[\sum_{s=1}^{T}\sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)] \leq \sum_{s=1}^{T}\TieDensity\cdot g^2(s)N\log(s). \label{equ:small_regret_bound}
 \end{align}
@@
 \dkcomment{Edited up to here.}
-
-\begin{corollary} \label{cor:constant-regret}
-If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O \left(\MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
-  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right) $.
-\end{corollary}
-
-\begin{proof}
-The proof of this corollary is similar to the proof of Theorem~\ref{rst:regret}.
-If we set $g^2(s) = \frac{288\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$, then there exists a $s^{0}$ such that for $s>s_{0}$, $q(g(s))=0$.
-Thus, similar to equation~\eqref{thm:equ}, we know the cumulative expected regret when we let the agents play myopically is bounded above by
-\begin{align}
-\sum_{s=1}^{T} 24\ARMNUM^2 d s \MAXR \exp\left(-2\log(T)\right)+ \sum_{s=1}^{s^{0}}\TieDensity g(s)^2\ARMNUM\log(s) \nonumber
-\end{align}
-Therefore, based on the same analysis of Theorem~\ref{rst:regret}, we know the cumulative regret is bounded by $O \left(\MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
-  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right) $.
-\end{proof}

### 2018-02-14 lower_bound.tex
did some minor changes to the paper
lower bound changed to square

@@
 One may conjecture that this should hold more generally,
-in that that regret of the (fewer and fewer) agents on the boundary
+in that the regret of the (fewer and fewer) agents on the boundary
 between close arms should go to 0, while their fraction also goes to 0.
@@
 whose attribute vectors are $(0,0)$ and $(0,1)$, respectively.
-Agents types are distributed uniformly on the two-dimensional unit circle%
+Agents types are distributed uniformly on the (edge of the)
+two-dimensional unit square%
 \footnote{While our model technically assumed that all agent coordinates are
-non-negative, we could simply shift the unit circle.
+non-negative, we could simply shift the unit square.
 The present choice is solely for ease of notation.}  
-$\Set{\AgV}{|| \AgV ||_2 \leq 1}$.
+$\Set{\AgV}{\max(\Ag{1}, \Ag{2}) = 1}$,
+with density $\frac{1}{8}$.
 Because $\AgV \cdot (0,0) = 0$ and $\AgV \cdot (0,1) = \Ag{2}$,
 the best choice for agent \AgV is arm $(0,1)$ iff $\Ag{2} > 0$,
-i.e., the top half of the unit circle prefers the arm $(0,1)$,
+i.e., the top half of the unit circle square the arm $(0,1)$,
 and the bottom half prefers the arm $(0,0)$.
@@
 For simplicity of notation, we set the standard deviation of the arm
-$(0,1)$ to $\sigma = 1$; different values only lead to a scaling of
-the results.
+$(0,1)$ to $\sigma = 1$;
+different values only lead to a scaling of the results.
 
@@
 but will wrongly pull $(0,0)$ and incur regret \Ag{2}.
-The region
-$\Ag{2} > 0$ and $\Ag{1} < \frac{-(1+\Noise{2})}{\Noise{1}} \cdot \Ag{2}$
-defines a wedge.
-For any particular value of \Ag{2},
-the length of the interval of corresponding \Ag{1} is
-\begin{align*}
-  \sqrt{1-\Ag{2}^2} - \frac{1+\Noise{2}}{\Noise{1}} \cdot \Ag{2}
-  & \geq 1 - \Ag{2} - \frac{1+\Noise{2}}{\Noise{1}} \cdot \Ag{2}
-  \; = \; 1 - \frac{1+\Noise{1}+\Noise{2}}{\Noise{1}} \cdot \Ag{2}.
-\end{align*}
+The range of \AgV making the wrong choice is thus
+$0 < \Ag{2} < \frac{- \Noise{1}}{1+\Noise{2}} \cdot \Ag{1}$.
+Since we are proving a lower bound, we only focus on the
+case $\Ag{1} = -1$, and ignore the case $\Ag{2} = 1$
+(which is rare, since it requires \Noise{1} to be large).
+Thus, the set of agents incurring regret contains the set
+$\Set{\AgV = (-1, \Ag{2})}{0 < \Ag{2} < \frac{\Noise{1}}{1+\Noise{2}}}$.
+
+% For any particular value of \Ag{2},
+% the length of the interval of corresponding \Ag{1} is
+% \begin{align*}
+%   \sqrt{1-\Ag{2}^2} - \frac{1+\Noise{2}}{\Noise{1}} \cdot \Ag{2}
+%   & \geq 1 - \Ag{2} - \frac{1+\Noise{2}}{\Noise{1}} \cdot \Ag{2}
+%   \; = \; 1 - \frac{1+\Noise{1}+\Noise{2}}{\Noise{1}} \cdot \Ag{2}.
+% \end{align*}
 
 \item If $\Ag{2} < 0$ and $\Ag{1} \Noise{1} + \Ag{2} (1+\Noise{2}) > 0$,
-then \Ag should pull $(0,0)$,
+then \AgV should pull $(0,0)$,
 but will wrongly pull $(0,1)$ and incur regret $-\Ag{2}$.
@@
 Hence, the expected regret for given \Noise{1}, \Noise{2} is at least
+%\begin{align*}
+$2 \int_0^{\frac{\Noise{1}}{1+\Noise{2}}}
+  \Ag{2} \cdot \frac{1}{8} \dd \Ag{2}
+=
+\frac{1}{8} \cdot \left(\frac{\Noise{1}}{1+\Noise{2}}\right)^2$.
+%\end{align*}
+The expected regret, conditioned on
+$\Noise{1} > 0$ and $\Noise{2} > 0$, is therefore
+
+\dkcomment{Where did the 4 come from? Where did it go? Also, why did
+  you have $\pi^3$ (instead of $\pi^2$) before? (I changed it.)}
 \begin{align*}
-  2 \int_0^{\frac{\Noise{1}}{1+\Noise{1}+\Noise{2}}}
-  \left( 1 - \frac{1+\Noise{1}+\Noise{2}}{\Noise{1}} \cdot \Ag{2} \right)
-  \cdot \Ag{2} \cdot \frac{1}{\pi} \dd \Ag{2}
-& =
-\frac{1}{\pi} \cdot \left(\frac{\Noise{1}}{1+\Noise{1}+\Noise{2}}\right)^2
-- \frac{2}{3 \pi} \cdot \left(\frac{\Noise{1}}{1+\Noise{1}+\Noise{2}}\right)^2
-\\ & =
-\frac{1}{3 \pi} \cdot \left(\frac{\Noise{1}}{1+\Noise{1}+\Noise{2}}\right)^2.
+\ExpectC{\Regret{t}}{\Noise{1} > 0, \Noise{2} > 0}
+ & \geq \dkedit{4??} \cdot \frac{1}{8}
+    \int_{0}^{\infty} \int_{0}^{\infty}
+    \left( \frac{\Noise{1}}{1+\Noise{2}} \right)^2 \cdot
+    \frac{\e^{-\frac{t \Noise{1}^2}{2}} \sqrt{t}}{\sqrt{2\pi}} \dd\Noise{1}
+    \frac{\e^{-\frac{t \Noise{2}^2}{2}} \sqrt{t}}{\sqrt{2\pi}} \dd\Noise{2} \\
+ & = \frac{1}{16\pi} \int_{0}^{\infty} \int_{0}^{\infty}
+   \left( \frac{\Noise{1}}{\sqrt{t}+\Noise{2}} \right)^2
+   \e^{-\Noise{1}^2/2} \e^{-\Noise{2}^2/2} \dd \Noise{1} \dd \Noise{2}.
 \end{align*}
 
-\begin{align}
-&E[r(t)| \Noise{1}>0, \Noise{2}>0] \nonumber \\
-\geq & 4\times \frac{1}{3\pi} \int_{0}^{\infty} \int_{0}^{\infty} (\frac{\Noise{1}}{1+\Noise{1}+\Noise{2}})^2\frac{e^{-\frac{t \times \Noise{1}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(\Noise{1})\frac{e^{-\frac{t \times \Noise{2}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(\Noise{2}) \nonumber \\
-= & \frac{1}{3\pi^3} \int_{0}^{\infty} \int_{0}^{\infty} (\frac{\Noise{1}}{\sqrt{t}+\Noise{1}+\Noise{2}})^2e^{-\frac{\Noise{1}^2}{2}}d(\Noise{1})e^{-\frac{\Noise{2}^2}{2}}d(\Noise{2}) \nonumber 
-\end{align}
+We want to show that the expected regret per time step decreases only
+at a rate of $\Omega(1/t)$, and thereto consider the limit of the
+ratio of the two quantities:
 
-Below, we want to show 
-\begin{align}
-\lim_{t\rightarrow\infty}\frac{E[r(t)| \Noise{1}>0, \Noise{2}>0]}{\frac{1}{t}} = \Omega(1), \nonumber
-\end{align}
-and use the fact that $\sum_{n=1}^{T}\frac{1}{n}=O(\log(T))$ to show the regret is at least $\Omega(\log(T))$. Since
-\begin{align}
-&\lim_{t\rightarrow \infty}\frac{E[r(t)| \Noise{1}>0, \Noise{2}>0]}{\frac{1}{t}} \nonumber \\
-\geq & \lim_{t\rightarrow \infty}\frac{1}{3\pi^3}\int_{0}^{\infty} \int_{0}^{\infty}\left[ t(\frac{\Noise{1}}{\sqrt{t}+\Noise{1}+\Noise{2}})^2\right]e^{-\frac{\Noise{1}^2}{2}}e^{-\frac{\Noise{2}^2}{2}}d(\Noise{1})d(\Noise{2}) \nonumber  \\
-= & \frac{1}{3\pi^3}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ t(\frac{\Noise{1}}{\sqrt{t}+\Noise{1}+\Noise{2}})^2\right]e^{-\frac{\Noise{1}^2}{2}}e^{-\frac{\Noise{2}^2}{2}}d(\Noise{1})d(\Noise{2}) \nonumber  \\
-=&\frac{1}{3\pi^3}\int_{0}^{\infty} \int_{0}^{\infty}e^{-\frac{\Noise{1}^2}{2}}e^{-\frac{\Noise{2}^2}{2}}d(\Noise{1})d(\Noise{2}) = \frac{1}{3\pi^3}, \nonumber
-\end{align}
+\begin{align*}
+\lim_{t \to \infty} \frac{\ExpectC{\Regret{t}}{\Noise{1} > 0, \Noise{2} > 0}}{\frac{1}{t}}
+  & \geq
+    \lim_{t \to \infty} \left( \frac{1}{16\pi} \cdot
+    \int_{0}^{\infty} \int_{0}^{\infty}
+    t \cdot \left( \frac{\Noise{1}}{\sqrt{t}+\Noise{2}} \right)^2
+    \e^{-\Noise{1}^2/2} \e^{-\Noise{2}^2/2} \dd \Noise{1} \dd \Noise{2} \right) \\
+  & = \frac{1}{16\pi} \cdot \int_{0}^{\infty} \int_{0}^{\infty}
+    \lim_{t \to \infty}
+    \left( t \cdot \left( \frac{\Noise{1}}{\sqrt{t}+\Noise{2}} \right)^2 \right)
+    \e^{-\Noise{1}^2/2} \e^{-\Noise{2}^2/2} \dd \Noise{1} \dd \Noise{2} \\
+  & = \frac{1}{16\pi} \cdot \int_{0}^{\infty} \int_{0}^{\infty}
+    \e^{-\Noise{1}^2/2} \e^{-\Noise{2}^2/2} \dd \Noise{1} \dd \Noise{2}
+  \; = \; \frac{1}{16 \pi}; 
+\end{align*}
 
-where the third line is due to monotone convergence theorem since the derivative of $t(\frac{\Noise{1}}{\sqrt{t}+\Noise{1}+\Noise{2}})^2$ is greater than $0$.
-
-\dkcomment{I edited up to here. Waiting for some feedback about
-  whether my calculations are way off.
-  I did use one bound of $\sqrt{1-\Ag{2}^2} \geq 1-\Ag{2}$, but since
-  we are looking at small values of \Ag{2}, I cannot imagine that this
-  lost much. One can compute the integral without this simplification,
-  but it will be quite a bit uglier.}
+the second line is due to the monotone convergence theorem,
+which can be applied because
+$t \left(\frac{\Noise{1}}{\sqrt{t}+\Noise{2}}\right)^2$
+is strictly increasing in $t$.
+Because the expected regret in each time step is at least
+$\Omega(1/t)$, the total expected regret is at least
+$\Omega(\sum_{t=1}^{T}\frac{1}{t} = \Omega(\log(T))$.

### 2018-02-15 algorithm.tex
halfway through editing payment proof

@@
 Theorem~\ref{thm:main-overview} is fairly simple.
-It mostly allows agents to exploit, but when an arm is \pfdelete{estimated to
-be extremely} \pfedit{sufficiently} unlikely to be pulled\pfdelete{by any agents},
+It mostly allows agents to exploit, but when an arm is sufficiently
+unlikely to be pulled, 
 the algorithm incentivizes this arm with a payment high enough
-to guarantee the next agent pulls it.
+to guarantee that the next agent pulls it.
 This way the algorithm ensures each arm is pulled often enough.
@@
 \item Based on the current estimates \ArmEV{t}{i'} of all arms'
-attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s)$. \bccomment{Do we need to mention what if $\frac{1}{\log(s)}>1$? }
+attribute vectors, the probability of pulling arm $i$ is less than
+$1/\log(s)$.
+\bccomment{Do we need to mention what if $\frac{1}{\log(s)}>1$?}
+\dkcomment{I'm not sure why. It's not like the inequality is not
+  satisfied.}
 Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
@@
 \pfedit{$1/\log(1)$ is treated as $\infty$, and if $1/\log(s) \ge 1$ then this condition is automatically met.}
+\dkcomment{Do we need this?}
 \end{itemize}
@@
 
-In this section, we prove Algorithm~\ref{alg:basic-incentivizing} achieves $O(\ARMNUM^2+\TieDensity(\log(T))^2)$ cumulative regret with $O(\ARMNUM^2)$ payment budget.
+In this section, we prove that Algorithm~\ref{alg:basic-incentivizing} achieves $O(\ARMNUM^2+\TieDensity(\log(T))^2)$ cumulative regret with $O(\ARMNUM^2)$ payment budget.
 This is stated in the following pair of theorems, which together constitute our main results.
@@
 In either case, the expected number of time steps until
-$|S|$ decreases is at most $s$,
+$|S|$ decreases is at most $\log s$,
 so the expected number of steps until $S$ is empty is at most
 $\ARMNUM \cdot \log(s)$.
-\dkcomment{If we wanted, this bound could probably be improved using a
-  coupon collector argument. But it would look uglier.}
 \end{proof}
@@
 Define \dkcomment{I'm making the dependence of $b$ on $n$ explicit,
-  since that's how we're using it.}
+  since that's how we're using it. Is it true with $b$ depending on
+  $n$?
+If not, we need to revisit what we're doing.}
 \begin{align*}
@@
 Then, we use the following technical Lemma~\ref{lem:n0-inequality}
-(whose proof is given in the appendix, and whose precondition we verify
-momentarily) to bound the first term,
+(whose proof is given in Appendix~\ref{n0-inequality-proof}, and whose
+precondition we verify momentarily) to bound the first term,
 giving us an overall upper bound of
@@
 intricate, and hence,
-the proof of Theorem~\ref{rst:budget} is given in the appendix.
+the proof of Theorem~\ref{rst:budget} is given in
+Appendix~\ref{sec:payment-proof}.
 
@@
 \end{align*}
-where the second to last inequality is because the following technical inequality, whose proof we include in the appendix.
+where the second to last inequality is because the following technical inequality, whose proof we include in Appendix~\ref{sec:n1-inequality-proof}.
 

### 2018-02-15 payment-proof.tex
halfway through editing payment proof

\section{Proof of Theorem~\ref{rst:budget}}
\label{sec:payment-proof}

We restate the theorem here for convenience:

\begin{rtheorem}{Theorem}{\ref{rst:budget}}
\dkcomment{Copy here the final form of the theorem once it is finalized.}
\end{rtheorem}

The high-level idea of the proof is motivated by Lemma~\ref{lem:numP},
which shows that the expected \emph{number} of payments is constant.
Unfortunately, in contrast to the regret, there is no hard upper bound
on the payment in any one round.
If a draw of a particular arm comes out wildly inaccurate --- which is
an event of low but positive probability ---
then agents may require very large incentives to pull this arm again
in the future (and correct the inaccurate estimate).
The high payments are offset by the exceedingly low probability of
having to incur them, but a rigorous analysis requires some care:
if a high payment is required in one phase, this indicates a very
inaccurate estimate, which may require multiple phases to correct.
Hence, we need to handle dependency of payments across time steps and
phases.

To reason about such estimation errors formally, we define
\emph{envelopes} of sample paths.
A sample path \SP captures all the random events affecting the
algorithm, i.e., the random draws \AgentV{t} of agents and the
noise \Noise[t] in the draws the pulled arms,
with an infite \dkcomment{Is it infinite?} time horizon.
\dkcomment{We should be consistent about using filtration vs.~sample
  path.}

With foresight, we define $g(s, \ell) := \frac{12 \sigma \ell}{s^{2/5}}$.
Let $\ErrV{t}{i} = \ArmEV{t}{i} - \ArmV{i}$ be the estimation
error for the attribute vector \ArmV{i} at time $t$,
with components \Err{t}{i}{j}.
For any sample path \SP, let $s (t,\SP)$ be the phase number that the
algorithm is in at time $t$ with the sample path \SP.
Define the sets

\begin{align*}
\hat{L}_\ell(t)
  & = \Set{\SP}{|\Err{t}{i}{j}(\SP)| \leq g(s(t,\SP),\ell)
    \mbox{ for all } i,j},\\
\Env[t]{1} & = \hat{L}_1(t)\\ 
\Env[t]{\ell} & = \hat{L}_{\ell} (t) - \hat{L}_{\ell-1} (t)
  \qquad \mbox{ for } \ell \geq 2.
\end{align*}

% \begin{align*}
% L'[\ell](t)
%   & = \Set{\SP}{|\Err{t}{i}{j}(\SP)|\leq g(s(t,\SP),\ell), \forall i,j\}
% \end{align*}
We call \Env[t]{\ell} the \Kth{\ell} envelope at time $t$.
In words, \Env[t]{\ell} consists of all sample paths such that at time
$t$, all coordinates of all arm estimation errors are bounded by
$g(s, \ell)$, but at least one coordinate of one arm estimation error
is \emph{not} bounded by $g(s, \ell-1)$.
When $t$ is clear from the context, we omit it from the notation;
similarly, when \SP is clear, we omit it in the notation for
\Err{t}{i}{j}, payments, etc.
The importance of envelopes is that for small $\ell$, the payments are
tightly bounded, while for large $\ell$, the cumulative probability of
the sample paths in \Env[t]{\ell} is small.
This is captured by the following two lemmas.

\begin{lemma} \label{lem:sample-path-payment}
If $\SP \in \Env[t]{\ell}$ and $s(t,\SP) = s$, then
the payment in step $t$ is upper-bounded by
$\bar{c} (s,\ell) = \MAXR + 2 \Diam d \cdot g(s,\ell)$.
\dkcomment{Verify that the way I talk about $t$ vs.~$s$ is right.}
\end{lemma}

\begin{proof}
The maximum payment is upper-bounded by the maximum perceived
difference in value for any agent type and any two arms:
\begin{align*}
\bar{c} (s, \ell) & \leq 
\max_{\AgV} \left(  \max_{i} \AgV \cdot \ArmEV{t}{i}
                 - \min_{i'} \AgV \cdot \ArmEV{t}{i'} \right) \\
& = \max_{\AgV} \left( \max_{i}\AgV \cdot (\ErrV{t}{i}+\ArmV{i})
                    - \min_{i'}\AgV \cdot (\ErrV{t}{i'}+\ArmV{i'}) \right) \\
& \leq \max_{\AgV} \left(  \max_{i} \AgV \cdot \ArmV{i}
                        - \min_{i'} \AgV \cdot \ArmV{i'}
                        + \max_{i} \AgV \cdot \ErrV{t}{i}
                        - \min_{i'} \AgV \cdot \ErrV{t}{i'} \right) \\
& \leq \MAXR + 2 \Diam d \cdot g(s,\ell). 
\end{align*}
The final inequality used the definition of the envelope.
\end{proof}

\begin{lemma} \label{lem:envelope-probability}
For every $\ell \geq 2$ and $t$, we have that
$\Prob{\SP \in \Env[t]{\ell}} \leq 24 \ARMNUM d\exp(-1.8(\ell-1)^2)$. 
\end{lemma}

\begin{proof}
The proof idea is quite similar to the proof of
Lemma~\ref{lem:round-prob};
however, the specific form of the envelopes necessitates some subtle
changes in the specific forms of the bounds used.
For \SP to be in \Env[t]{\ell}, by definition, at least one coordinate
of at least one arm's estimation error must exceed $g(s(t,\SP),\ell-1)$.
For now, fix an arm $i$ and coordinate $j$.
Recall that $\NumPull{t}{i}(\SP) \geq s(t,\SP)$ is the number of times
that arm $i$ has been pulled by time $t$ under \SP.
We can express a bound on large deviations in terms of
the scaled estimation error
$\frac{\NumPull{t}{i} \cdot \Err{t}{i}{j}}{2\sigma}$:
\begin{align*}
\Prob{|\Err{t}{i}{j}| \geq g(s(t,\SP), \ell-1)}
& = \Prob{\frac{\NumPull{t}{i} \cdot \Err{t}{i}{j}}{2\sigma}
          \geq \frac{6\NumPull{t}{i}(\ell-1)}{s(t,\SP)^{2/5}}}\\
& \leq \; \Prob{\frac{\NumPull{t}{i} \cdot \Err{t}{i}{j}}{2\sigma}
          \geq 6\NumPull{t}{i}^{3/5}(\ell-1)}. 
\end{align*}

We will show below that
$5 n^{3/5} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}$
for all $n \geq 1$.
Applying this inequality and sublinearity of $\sqrt{\cdot}$,
we obtain that

\begin{align*}
6 \NumPull{t}{i}^{3/5}(\ell-1)
& \geq 5 \NumPull{t}{i}^{3/5} + \NumPull{t}{i}^{3/5}(\ell-1)  \\
& \geq \sqrt{0.6 \NumPull{t}{i} \log(\log_{1.1}(\NumPull{t}{i})+1)}
     + \sqrt{(\ell-1)^2 \NumPull{t}{i}}  \\
& \geq \sqrt{0.6\NumPull{t}{i}\log(\log_{1.1}(\NumPull{t}{i})+1)+(\ell-1)^2 \NumPull{t}{i}}. 
\end{align*}

Because the scaled estimation error
$\frac{\NumPull{t}{i} \cdot \Err{t}{i}{j}}{2\sigma}$
is a summation of $1/2$-Gaussian random variables, 
we can now apply Lemma~\ref{lem:ACI-inequality}
with $b(n) = (\ell-1)^2$ \dkcomment{omit dependence on $n$ here?},
to obtain that
\begin{align*}
\Prob{|\Err{t}{i}{j}| \geq g(s(t,\SP), \ell-1)}
& \leq 24 \e^{-1.8(\ell-1)^2}.
\end{align*}
Now, taking a union bound over all arms $i$ and
coordinates $j$ completes the proof.

It remains to show that
$5 n^{3/5} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}$
for all $n \geq 1$.
By squaring the inequality and canceling out a factor $n$,
the statement is equivalent to showing that
$25 n^{1/5} \geq \log(\log_{1.1}(n)+1)$.
We will show the stronger statement that
$25 n^{1/5} \geq \log_{1.1}(n)+1$.  
To see this, notice that the derivative of the left-hand side is
always strictly larger than the derivative of the right-hand side,
so the difference between the sides is minimized at $n=1$,
where it is positive. 
\end{proof}

\begin{extraproof}{Theorem~\ref{rst:budget}}

\noindent\textbf{Step 2: Introduce a new stochastic process which bounds the total payment in a phase}

Denote $\mathcal{F}_t$ as the filtration up to time $t$. Denote $V_t$ as the set of arms that have been pulled at least $s$ times at time $t$ in phase $s$. Based on our algorithm, we know

\begin{align}
\Prob{\text{play a new arm}|\mathcal{F}_t} & =
\begin{cases}
1       & \quad \text{if we incentivize}\\
\sum_{i\in \{1,\cdots,\ARMNUM\}\setminus V_t} P(\AgentV{t} \cdot \ArmEV{t}{i}>\AgentV{t}\cdot \ArmEV{t}{j} \forall j\neq i)  & \quad \text{otherwise}  
\end{cases} \label{dom_stoc}\\
 & \geq (\ARMNUM-|V_t|)\times \frac{1}{\log(s)}. \nonumber
\end{align}

\bccomment{probably we need to be more careful about $\frac{1}{\log(s)}$}.
Let $(Z_{s,v,m}:m\geq 0)$ be a sequence of independent Bernoulli random variable with success probability $\frac{\ARMNUM-v}{\log(s)}$. We will construct an alternative stochastic process for selecting which arm gets played that has the same distribution as the original process, but under which
\begin{align*}
t_{s}-t_{s-1}\leq \bar{T}_{s}:=\sum_{v=0}^{\ARMNUM-1}\bar{T}_{s,v}, 
\end{align*}
where $\bar{T}_{s,v}:=\inf\{m\geq 0: Z_{s,v,m}=1\}+1$.

The new stochastic process will have the property that whenever $Z_{s,v(s,t),m(s,t)}=1$, we will play a new arm at time t for $t\in [t_{s-1}, t_{s}]$, where $v(s,t)$ is the number of unique arms played in phase $s$ strictly before time $t$, and $m(s,t)$ is the number of times we have pulled a previously pulled arm for the current value of $v(s,t)$. At time $t$, to determine what arm to pull, calculate \eqref{dom_stoc} and let $q_t$ be the probability computed. Note $q_t\geq \frac{\ARMNUM-v(s,t)}{\log(s)}$.

If $Z_{s,v(s,t),m(s,t)}$ is 1, decide to play a new arm. Otherwise, draw a second Bernoulli random variable with probability $\frac{q_t-\frac{\ARMNUM-v(s,t)}{\log(s)}}{1-\frac{\ARMNUM-v(s,t)}{\log(s)}}$, and if it is 1, decide to play a new arm, and otherwise decide to play an old arm. Note that

\begin{align}
\Prob{\text{play a new arm}|\mathcal{F}_{t}}=\frac{\ARMNUM-v}{\log(s)}+\left[1-\frac{\ARMNUM-v}{\log(s)}\right]\times \frac{q_t-\frac{\ARMNUM-v}{\log(s)}}{1-\frac{\ARMNUM-v}{\log(s)}}=q_t.
\end{align}

Since we pull a new arm only when $Z_{s,v(s,t),m(s,t)}=1$, the number of times we pull an arm when $v(s,t)=v$ is bounded above by $\bar{T}_{s,v}$. Thus,

\begin{align}
t_{s}-t_{s-1}\leq \sum_{v=0}^{\ARMNUM-1}\bar{T}_{s,v}=\bar{T}_{s}.
\end{align}
Finally, we want to bound $\sum_{t}E[c(t)]$. Let $C(s)$ be the cost incurred in phase $s$. Thus $\sum_{t}E[c(t)]=\sum_{s}E[C(s)]$. We know
\begin{align*}
C(s)&=\sum_{t=t_{s-1}+1}^{t_{s}}c(t)=\sum_{t=t_{s-1}+1}^{t_{s}}\sum_{\ell}\mathbbm{1}\{\SP\in \Env{\ell}\}c(t)  \\
&\leq \sum_{t=t_{s-1}+1}^{t_{s}}\sum_{l}\mathbbm{1}\{\SP\in \Env{\ell}\}\bar{c}(s,\ell)  \\
&\leq (t_{s}-t_{s-1})\sum_{\ell} \mathbbm{1}\{\SP\in \Env{\ell}\}\bar{c}(s,\ell)  \\
&\leq \bar{T}_{s}\sum_{l}\mathbbm{1}\{\SP\in \Env{\ell}\}\bar{c}(s,\ell). 
\end{align*}

Since $\bar{T}_{s}$ is independent of \SP, we know
\begin{align*}
E[C(s)]\leq E[\bar{T}_{s}]\sum_{\ell}\Prob{\SP\in \Env{\ell}}\bar{c}(s,\SP). 
\end{align*}
\noindent\textbf{Step 3: Rewrite the total payment expression}.

Based on the above notations, we can rewrite the cumulative payment as follows:
\begin{align*}
\sum_{t=1}^{\infty}c(t) =\sum_{s=1}^{\infty}C(s)
\leq  \sum_{s=1}^{\infty}\sum_{\ell=1}^{\infty}\bar{T}_{s}\mathbbm{1}\{\SP\in \Env{\ell}\}\bar{c}(s,\ell). 
\end{align*}

Set $g(s,\ell)$ to be $\frac{12\sigma \ell}{s^{2/5}}$.
Since if $|\Arm{i}{j}-\ArmE{t}{i}{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\AgV\in \{\AgV:\AgV\cdot \ArmV{\Best{\AgV}}-\AgV \cdot \ArmV{\Second{\AgV}}> 2\Diam d\lambda\}$, they will correctly identify their best arm. Thus, if $|\Arm{i}{j}-\ArmE{t}{i}{j}|\leq \frac{12\sigma l}{s^{2/5}} \leq \frac{p^{-1}(\frac{\MinProb}{2})}{2\Diam d}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$. Further, if time $t$ is in a phase $s$ that satisfies $1/log(s)\leq \MinProb/2$, then our algorithm will not incentivize pulling any arms. Denote $a_0=\frac{24\Diam d\sigma}{p^{-1}(\frac{\MinProb}{2})}$. In order to have $\frac{12\sigma l}{s^{2/5}}\leq \frac{p^{-1}(\frac{\MinProb}{2})}{2\Diam d}$, it is sufficient to have $s\geq \lceil (a_{0} l)^\frac{5}{2} \rceil$. In order to have $1/\log(s)\leq \frac{\MinProb}{2}$, we need $s\geq \exp(\frac{2}{\MinProb})$. Denote $s_2=\exp(\frac{2}{\MinProb})$. Thus, we know we can only incur regret for sample paths \SP in the $\ell^{th}$ envelope in the first $\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}$ phases.

Thus,
\begin{align*}
\sum_{t=1}^{\infty}c(t)\leq\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(s,\ell)\mathbbm{1}\{\SP\in \Env{\ell}\}\bar{T}_{s}. 
\end{align*}

Therefore,

\begin{align*}
&E\left[\sum_{t=1}^{\infty}c(t)\right] \\
\leq &\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(s,\SP)\Prob{\SP \in \Env{\ell}}E[\bar{T}_{s}]  \\
=&\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[\MAXR+2\Diam d\frac{12\sigma \ell}{s^{2/5}}\right]\Prob(\SP\in \Env{\ell})E[\bar{T}_{s}]  \\
\leq &\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[\MAXR+24\Diam d\sigma l\right]\Prob(\SP\in \Env{\ell})E[\bar{T}_{s}]. 
\end{align*}

\noindent\textbf{Step 5: Final Step}

Thus,
\begin{align*}
&\sum_{t=1}^{\infty}c(t)  \\
\leq&\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]\Prob{\SP\in \Env{\ell})E[\bar{T}_{s}}  \\
\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\Prob{\SP\in L[1]}E[\bar{T}_{s}] +\sum_{l=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]\Prob{\SP\in \Env{\ell}}E[\bar{T}_{s}]  \\
\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24\Diam d\sigma \right]E[\bar{T}_{s}] +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24\ARMNUM d e^{-1.8(\ell-1)^2}E[\bar{T}_{s}] \\
\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\ARMNUM \log(s) +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24 \ARMNUM d e^{-1.8(\ell-1)^2}\ARMNUM \log(s)  \\
\leq & \left[\MAXR+24\Diam d\sigma \right]\ARMNUM (\max\{s_2,\lceil (a_0)^{5/2} \rceil\})^2+\sum_{\ell=2}^{\infty}24\ARMNUM^2 d[\MAXR+24\Diam d\ell\sigma](\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\})^2 e^{-1.8(\ell-1)^2}  \\
=& O(\max\{\frac{\ARMNUM^2}{\MinProb^5},\ARMNUM^2\exp(\frac{4}{\MinProb})\}). 
\end{align*}

\bccomment{in the second to last inequality, I use $s\leq \log(s)$, probably a very loose bound.}
\end{extraproof}

### 2018-02-15 algorithm.tex
addressed some comments

@@
 attribute vectors, the probability of pulling arm $i$ is less than
-$1/\log(s)$.
-\bccomment{Do we need to mention what if $\frac{1}{\log(s)}>1$?}
-\dkcomment{I'm not sure why. It's not like the inequality is not
-  satisfied.}
-Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
+$1/\log(s)$. Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
   \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
@@
 For any $n \geq 1$, let $k_n$ be the time step right after arm $i$ has
-been pulled for the \Kth{n} time.
-\dkcomment{I'm writing $n$ instead of $s$ here because $S_s$ would
-  look ugly, and $n$ is consistent with the lemma.
-  Or we could rename $S$ to something else.}
-Define
+been pulled for the \Kth{n} time. Define
 $S_n := \frac{n \cdot (\ArmE{k_n}{i}{j} - \Arm{i}{j})}{2 \sigma}$
@@
 
-\dkcomment{The following paragraph is from Bangrui's version. It may
-  move to an earlier section, go away, or become a part somewhere.}
-As we can see later in our proof, we only need
-$\max_{i,j}\limsup_{y\rightarrow 0^{+}}\frac{F_{i,j}(y)}{y}$ to be
-finite.
-Intuitively, Assumption~\ref{A1} states that there are not many agents
-who are indifferent between their best arm and the second best arm.
-
 \begin{proof}
@@
 
-\bccomment{I believe the calculation up to this line should be correct now. The final equation we want to minimize is $\sum_{s=1}^{T}[\exp(-s*g^2(s))+g^2(s)*s]$, what should be our choice of $g(s)$?}
-
 Therefore, the second line becomes
@@
 on the cumulative expected regret.
-\dkcomment{I see a problem here: What's the value of $x$ in the
-  definition of \LatePhase? Presumably, we need to make $x$ small
-  enough that any $x$ we use in any application of Lemma 7 (or
-  Corollary 10) works. But notice that we use $x =
-  \Theta(g^2(\tau_s^k))$,
-  and in particular for the last step, I don't see how we can make
-  $\tau_s^k$ much smaller than $T$.
-  But then, we get that $x = O(\frac{\log T}{T})$, which would give
-  linear regret. How to handle this?}
+
+\bccomment{David, could you go through the proof again if possible? Thanks}
+
 \end{proof}

### 2018-02-15 payment-proof.tex
simplification of payment proof

@@
   path.}
+\pfcomment{I removed discussion of filtrations and replaced them by discussion of history.}
 
@@
 We call \Env[t]{\ell} the \Kth{\ell} envelope at time $t$.
+\pfcomment{I believe we need the following definition for envelope $\ell$: 
+$\hat{L}_\ell
+  = \Set{\SP}{|\Err{t}{i}{j}(\SP)| \leq g(s(t,\SP),\ell)
+    \mbox{ for all } i,j,t}$
+This is what we use below in the proof of Theorem 3, plus a corresponding $L_\ell$.
+It's ok to have $\hat{L}(t)$ defined as well, but if we are going to define the version without $t$ then maybe we don't need the one wiht $t$.
+}
+
 In words, \Env[t]{\ell} consists of all sample paths such that at time
@@
 
-\noindent\textbf{Step 2: Introduce a new stochastic process which bounds the total payment in a phase}
-
-Denote $\mathcal{F}_t$ as the filtration up to time $t$. Denote $V_t$ as the set of arms that have been pulled at least $s$ times at time $t$ in phase $s$. Based on our algorithm, we know
-
-\begin{align}
-\Prob{\text{play a new arm}|\mathcal{F}_t} & =
-\begin{cases}
-1       & \quad \text{if we incentivize}\\
-\sum_{i\in \{1,\cdots,\ARMNUM\}\setminus V_t} P(\AgentV{t} \cdot \ArmEV{t}{i}>\AgentV{t}\cdot \ArmEV{t}{j} \forall j\neq i)  & \quad \text{otherwise}  
-\end{cases} \label{dom_stoc}\\
- & \geq (\ARMNUM-|V_t|)\times \frac{1}{\log(s)}. \nonumber
-\end{align}
-
-\bccomment{probably we need to be more careful about $\frac{1}{\log(s)}$}.
-Let $(Z_{s,v,m}:m\geq 0)$ be a sequence of independent Bernoulli random variable with success probability $\frac{\ARMNUM-v}{\log(s)}$.
-We will construct an alternative stochastic process for selecting which arm gets played that has the same distribution as the original process, but under which
-\begin{align*}
-t_{s}-t_{s-1}\leq \bar{T}_{s}:=\sum_{v=0}^{\ARMNUM-1}\bar{T}_{s,v}, 
-\end{align*}
-where $\bar{T}_{s,v}:=\inf\{m\geq 0: Z_{s,v,m}=1\}+1$.
-
-The new stochastic process will have the property that whenever $Z_{s,v(s,t),m(s,t)}=1$, we will play a new arm at time t for $t\in [t_{s-1}, t_{s}]$, where $v(s,t)$ is the number of unique arms played in phase $s$ strictly before time $t$, and $m(s,t)$ is the number of times we have pulled a previously pulled arm for the current value of $v(s,t)$.
-At time $t$, to determine what arm to pull, calculate \eqref{dom_stoc} and let $q_t$ be the probability computed.
-Note $q_t\geq \frac{\ARMNUM-v(s,t)}{\log(s)}$.
-
-If $Z_{s,v(s,t),m(s,t)}$ is 1, decide to play a new arm.
-Otherwise, draw a second Bernoulli random variable with probability $\frac{q_t-\frac{\ARMNUM-v(s,t)}{\log(s)}}{1-\frac{\ARMNUM-v(s,t)}{\log(s)}}$, and if it is 1, decide to play a new arm, and otherwise decide to play an old arm.
-Note that
-
-\begin{align}
-\Prob{\text{play a new arm}|\mathcal{F}_{t}}=\frac{\ARMNUM-v}{\log(s)}+\left[1-\frac{\ARMNUM-v}{\log(s)}\right]\times \frac{q_t-\frac{\ARMNUM-v}{\log(s)}}{1-\frac{\ARMNUM-v}{\log(s)}}=q_t.
-\end{align}
-
-Since we pull a new arm only when $Z_{s,v(s,t),m(s,t)}=1$, the number of times we pull an arm when $v(s,t)=v$ is bounded above by $\bar{T}_{s,v}$. Thus,
-
-\begin{align}
-t_{s}-t_{s-1}\leq \sum_{v=0}^{\ARMNUM-1}\bar{T}_{s,v}=\bar{T}_{s}.
-\end{align}
-Finally, we want to bound $\sum_{t}E[c(t)]$. Let $C(s)$ be the cost incurred in phase $s$. Thus $\sum_{t}E[c(t)]=\sum_{s}E[C(s)]$. We know
-\begin{align*}
-C(s)&=\sum_{t=t_{s-1}+1}^{t_{s}}c(t)=\sum_{t=t_{s-1}+1}^{t_{s}}\sum_{\ell}\mathbbm{1}\{\SP\in \Env{\ell}\}c(t)  \\
-&\leq \sum_{t=t_{s-1}+1}^{t_{s}}\sum_{l}\mathbbm{1}\{\SP\in \Env{\ell}\}\bar{c}(s,\ell)  \\
-&\leq (t_{s}-t_{s-1})\sum_{\ell} \mathbbm{1}\{\SP\in \Env{\ell}\}\bar{c}(s,\ell)  \\
-&\leq \bar{T}_{s}\sum_{l}\mathbbm{1}\{\SP\in \Env{\ell}\}\bar{c}(s,\ell). 
-\end{align*}
-
-Since $\bar{T}_{s}$ is independent of \SP, we know
-\begin{align*}
-E[C(s)]\leq E[\bar{T}_{s}]\sum_{\ell}\Prob{\SP\in \Env{\ell}}\bar{c}(s,\SP). 
-\end{align*}
 \noindent\textbf{Step 3: Rewrite the total payment expression}.
 
-Based on the above notations, we can rewrite the cumulative payment as follows:
+\pfcomment{I deleted Step 2 and replaced it by this simpler argument}
+Let $C(s)$ be the cost incurred in phase $s$.
+In each phase, we can make at most $N$ payments, because each arm is incentivized at most once.
+Noting that each sample path $\omega$ is in exactly one envelope and and using Lemma~\ref{lem:sample-path-payment}, we get
+this bound on the cumulative payment:
 \begin{align*}
 \sum_{t=1}^{\infty}c(t) =\sum_{s=1}^{\infty}C(s)
-\leq  \sum_{s=1}^{\infty}\sum_{\ell=1}^{\infty}\bar{T}_{s}\mathbbm{1}\{\SP\in \Env{\ell}\}\bar{c}(s,\ell). 
+\leq  \sum_{s=1}^{\infty}\sum_{\ell=1}^{\infty}\mathbbm{1}\{\SP\in \Env{\ell}\} N \bar{c}(s,\ell). 
 \end{align*}
@@
 Denote $s_2=\exp(\frac{2}{\MinProb})$.
-Thus, we know we can only incur regret for sample paths \SP in the $\ell^{th}$ envelope in the first $\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}$ phases.
+Thus, we know we can only incur regret \pfcomment{this should be payment cost, right?} for sample paths \SP in the $\ell^{th}$ envelope in the first $\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}$ phases.
 
@@
 \begin{align*}
-\sum_{t=1}^{\infty}c(t)\leq\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(s,\ell)\mathbbm{1}\{\SP\in \Env{\ell}\}\bar{T}_{s}. 
+\sum_{t=1}^{\infty}c(t)\leq\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(s,\ell)\mathbbm{1}\{\SP\in \Env{\ell}\}N. 
 \end{align*}
@@
 &E\left[\sum_{t=1}^{\infty}c(t)\right] \\
-\leq &\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(s,\SP)\Prob{\SP \in \Env{\ell}}E[\bar{T}_{s}]  \\
-=&\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[\MAXR+2\Diam d\frac{12\sigma \ell}{s^{2/5}}\right]\Prob(\SP\in \Env{\ell})E[\bar{T}_{s}]  \\
-\leq &\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[\MAXR+24\Diam d\sigma l\right]\Prob(\SP\in \Env{\ell})E[\bar{T}_{s}]. 
+\leq &\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(s,\SP)\Prob{\SP \in \Env{\ell}}N  \\
+=&\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[\MAXR+2\Diam d\frac{12\sigma \ell}{s^{2/5}}\right]\Prob{\SP\in \Env{\ell}}N  \\
+\leq &\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[\MAXR+24\Diam d\sigma l\right]\Prob{\SP\in \Env{\ell}}N. 
 \end{align*}
@@
 \begin{align*}
-&\sum_{t=1}^{\infty}c(t)  \\
-\leq&\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]\Prob{\SP\in \Env{\ell})E[\bar{T}_{s}}  \\
-\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\Prob{\SP\in L[1]}E[\bar{T}_{s}] +\sum_{l=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]\Prob{\SP\in \Env{\ell}}E[\bar{T}_{s}]  \\
-\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24\Diam d\sigma \right]E[\bar{T}_{s}] +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24\ARMNUM d e^{-1.8(\ell-1)^2}E[\bar{T}_{s}] \\
-\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\ARMNUM \log(s) +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24 \ARMNUM d e^{-1.8(\ell-1)^2}\ARMNUM \log(s)  \\
-\leq & \left[\MAXR+24\Diam d\sigma \right]\ARMNUM (\max\{s_2,\lceil (a_0)^{5/2} \rceil\})^2+\sum_{\ell=2}^{\infty}24\ARMNUM^2 d[\MAXR+24\Diam d\ell\sigma](\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\})^2 e^{-1.8(\ell-1)^2}  \\
-=& O(\max\{\frac{\ARMNUM^2}{\MinProb^5},\ARMNUM^2\exp(\frac{4}{\MinProb})\}). 
+&E\left[\sum_{t=1}^{\infty}c(t)\right]  \\
+\leq&\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]\Prob{\SP\in \Env{\ell}}N  \\
+\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\Prob{\SP\in L[1]}N +\sum_{l=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]\Prob{\SP\in \Env{\ell}}N  \\
+\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24\Diam d\sigma \right]N +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24\ARMNUM d e^{-1.8(\ell-1)^2}N \\
+\leq & \left[\MAXR+24\Diam d\sigma \right]\ARMNUM \max\{s_2,\lceil (a_0)^{5/2} \rceil\}+\sum_{\ell=2}^{\infty}24\ARMNUM^2 d[\MAXR+24\Diam d\ell\sigma]\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\} e^{-1.8(\ell-1)^2}  \\
+=& O\left(\max\left\{\frac{\ARMNUM^2}{\MinProb^{5/2}},\ARMNUM^2\exp\left(\frac{2}{\MinProb}\right)\right\}\right). 
 \end{align*}
+\pfcomment{the above bound got tighter.  I didn't carry this forward anywhere where we report on / use the bound.}
 
-\bccomment{in the second to last inequality, I use $s\leq \log(s)$, probably a very loose bound.}
 \end{extraproof}

### 2018-02-15 lower_bound.tex
addressed some comments
finished pass through payment proof

@@
 to bound the regret of the myopic algorithm which never incentivizes
-agents. \dkcomment{This feels ``clear'', but is it?}
+agents.
 
@@
 
-\dkcomment{Where did the 4 come from? Where did it go? Also, why did
-  you have $\pi^3$ (instead of $\pi^2$) before? (I changed it.)}
 \begin{align*}
 \ExpectC{\Regret{t}}{\Noise{1} > 0, \Noise{2} > 0}
- & \geq \dkedit{4??} \cdot \frac{1}{8}
+ & \geq \frac{1}{\Prob{\Noise{1}>0,\Noise{2}>0}} \cdot \frac{1}{8}
     \int_{0}^{\infty} \int_{0}^{\infty}
@@
     \frac{\e^{-\frac{t \Noise{2}^2}{2}} \sqrt{t}}{\sqrt{2\pi}} \dd\Noise{2} \\
- & = \frac{1}{16\pi} \int_{0}^{\infty} \int_{0}^{\infty}
+ & = \frac{1}{4\pi} \int_{0}^{\infty} \int_{0}^{\infty}
    \left( \frac{\Noise{1}}{\sqrt{t}+\Noise{2}} \right)^2
@@
   & \geq
-    \lim_{t \to \infty} \left( \frac{1}{16\pi} \cdot
+    \lim_{t \to \infty} \left( \frac{1}{4\pi} \cdot
     \int_{0}^{\infty} \int_{0}^{\infty}
@@
     \e^{-\Noise{1}^2/2} \e^{-\Noise{2}^2/2} \dd \Noise{1} \dd \Noise{2} \right) \\
-  & = \frac{1}{16\pi} \cdot \int_{0}^{\infty} \int_{0}^{\infty}
+  & = \frac{1}{4\pi} \cdot \int_{0}^{\infty} \int_{0}^{\infty}
     \lim_{t \to \infty}
@@
     \e^{-\Noise{1}^2/2} \e^{-\Noise{2}^2/2} \dd \Noise{1} \dd \Noise{2} \\
-  & = \frac{1}{16\pi} \cdot \int_{0}^{\infty} \int_{0}^{\infty}
+  & = \frac{1}{4\pi} \cdot \int_{0}^{\infty} \int_{0}^{\infty}
     \e^{-\Noise{1}^2/2} \e^{-\Noise{2}^2/2} \dd \Noise{1} \dd \Noise{2}
-  \; = \; \frac{1}{16 \pi}; 
+  \; = \; \frac{1}{4 \pi}; 
 \end{align*}
@@
 $\Omega(1/t)$, the total expected regret is at least
-$\Omega(\sum_{t=1}^{T}\frac{1}{t} = \Omega(\log(T))$.
+$\Omega(\sum_{t=1}^{T}\frac{1}{t}) = \Omega(\log(T))$.

### 2018-02-15 payment-proof.tex
finished pass through payment proof

@@
 algorithm, i.e., the random draws \AgentV{t} of agents and the
-noise \Noise[t] in the draws the pulled arms,
+noise \NoiseV[t] in the draws the pulled arms,
 with an infite \dkcomment{Is it infinite?} time horizon.
@@
 \begin{align*}
-\hat{L}_\ell(t)
+\hat{L}_\ell
   & = \Set{\SP}{|\Err{t}{i}{j}(\SP)| \leq g(s(t,\SP),\ell)
-    \mbox{ for all } i,j},\\
-\Env[t]{1} & = \hat{L}_1(t)\\ 
-\Env[t]{\ell} & = \hat{L}_{\ell} (t) - \hat{L}_{\ell-1} (t)
+    \mbox{ for all } i,j,t},\\
+\Env{1} & = \hat{L}_1\\ 
+\Env{\ell} & = \hat{L}_{\ell} - \hat{L}_{\ell-1}
   \qquad \mbox{ for } \ell \geq 2.
@@
 % \end{align*}
-We call \Env[t]{\ell} the \Kth{\ell} envelope at time $t$.
-\pfcomment{I believe we need the following definition for envelope $\ell$: 
-$\hat{L}_\ell
-  = \Set{\SP}{|\Err{t}{i}{j}(\SP)| \leq g(s(t,\SP),\ell)
-    \mbox{ for all } i,j,t}$
-This is what we use below in the proof of Theorem 3, plus a corresponding $L_\ell$.
-It's ok to have $\hat{L}(t)$ defined as well, but if we are going to define the version without $t$ then maybe we don't need the one wiht $t$.
-}
-
-In words, \Env[t]{\ell} consists of all sample paths such that at time
+We call \Env{\ell} the \Kth{\ell} envelope.
+In words, \Env{\ell} consists of all sample paths such that at all times
 $t$, all coordinates of all arm estimation errors are bounded by
-$g(s, \ell)$, but at least one coordinate of one arm estimation error
-is \emph{not} bounded by $g(s, \ell-1)$.
-When $t$ is clear from the context, we omit it from the notation;
-similarly, when \SP is clear, we omit it in the notation for
+$g(s, \ell)$,
+but for at least one time $t$, at least one coordinate of one arm
+estimation error is \emph{not} bounded by $g(s, \ell-1)$.
+When \SP is clear, we omit it in the notation for
 \Err{t}{i}{j}, payments, etc.
@@
 tightly bounded, while for large $\ell$, the cumulative probability of
-the sample paths in \Env[t]{\ell} is small.
+the sample paths in \Env{\ell} is small.
 This is captured by the following two lemmas.
@@
 \begin{lemma} \label{lem:sample-path-payment}
-If $\SP \in \Env[t]{\ell}$ and $s(t,\SP) = s$, then
+If $\SP \in \Env{\ell}$ and $s(t,\SP) = s$, then
 the payment in step $t$ is upper-bounded by
@@
 \begin{lemma} \label{lem:envelope-probability}
-For every $\ell \geq 2$ and $t$, we have that
-$\Prob{\SP \in \Env[t]{\ell}} \leq 24 \ARMNUM d\exp(-1.8(\ell-1)^2)$. 
+For every $\ell \geq 2$, we have that
+$\Prob{\SP \in \Env{\ell}} \leq 24 \ARMNUM d\exp(-1.8(\ell-1)^2)$. 
 \end{lemma}
@@
 changes in the specific forms of the bounds used.
-For \SP to be in \Env[t]{\ell}, by definition, at least one coordinate
-of at least one arm's estimation error must exceed $g(s(t,\SP),\ell-1)$.
+For \SP to be in \Env{\ell}, by definition,
+for at least one time $t$,
+at least one coordinate of at least one arm's estimation error must
+exceed $g(s(t,\SP),\ell-1)$.
 For now, fix an arm $i$ and coordinate $j$.
+
 Recall that $\NumPull{t}{i}(\SP) \geq s(t,\SP)$ is the number of times
 that arm $i$ has been pulled by time $t$ under \SP.
-We can express a bound on large deviations in terms of
-the scaled estimation error
-$\frac{\NumPull{t}{i} \cdot \Err{t}{i}{j}}{2\sigma}$:
+We define the scaled estimation error
+$S_{i,j}(t) := \frac{\NumPull{t}{i} \cdot \Err{t}{i}{j}}{2\sigma}$.
+The advantage of $S_{i,j}(t)$ is that it is 
+a summation of $1/2$-Gaussian random variables, 
+so we will be able to apply Lemma~\ref{lem:ACI-inequality}.
+First notice that we can express the desired probability as follows:
+
 \begin{align*}
 \Prob{|\Err{t}{i}{j}| \geq g(s(t,\SP), \ell-1)}
-& = \Prob{\frac{\NumPull{t}{i} \cdot \Err{t}{i}{j}}{2\sigma}
-          \geq \frac{6\NumPull{t}{i}(\ell-1)}{s(t,\SP)^{2/5}}}\\
-& \leq \; \Prob{\frac{\NumPull{t}{i} \cdot \Err{t}{i}{j}}{2\sigma}
-          \geq 6\NumPull{t}{i}^{3/5}(\ell-1)}. 
+& = \Prob{S_{i,j}(t) \geq \frac{6\NumPull{t}{i}(\ell-1)}{s(t,\SP)^{2/5}}}\\
+& \leq \; \Prob{S_{i,j}(t) \geq 6\NumPull{t}{i}^{3/5}(\ell-1)}. 
 \end{align*}
@@
      + \sqrt{(\ell-1)^2 \NumPull{t}{i}}  \\
-& \geq \sqrt{0.6\NumPull{t}{i}\log(\log_{1.1}(\NumPull{t}{i})+1)+(\ell-1)^2 \NumPull{t}{i}}. 
+& \geq \sqrt{0.6\NumPull{t}{i}\log(\log_{1.1}(\NumPull{t}{i})+1)+(\ell-1)^2 \NumPull{t}{i}}
+\; =: \; h(\NumPull{t}{i}).
 \end{align*}
 
-Because the scaled estimation error
-$\frac{\NumPull{t}{i} \cdot \Err{t}{i}{j}}{2\sigma}$
-is a summation of $1/2$-Gaussian random variables, 
-we can now apply Lemma~\ref{lem:ACI-inequality}
-with $b(n) = (\ell-1)^2$ \dkcomment{omit dependence on $n$ here?},
-to obtain that
+Let the random stopping time $\tau_{i,j}$ be the first value of
+\NumPull{t}{i} (i.e., the first pull of arm $i$) such that 
+$S_{i,j}(\tau_{i,j}) > h(\NumPull{t}{i})$.
+$\tau_{i,j} = \infty$ means that the estimation error never exceeds 
+$h(\NumPull{t}{i})$.
+We apply Lemma~\ref{lem:ACI-inequality}
+to $S_{i,j}(t)$, with a stopping time of $\tau_{i,j}$ and
+with $b(n) = (\ell-1)^2$ \dkcomment{omit dependence on $n$ here?}.
+We obtain that the probability that $\tau_{i,j} < \infty$ and 
+$S_{i,j}(\tau_{i,j}) > h(\tau_{i,j})$ is at most
+$12 \e^{-1.8 b(n)}$.
+By definition of $\tau_{i,j}$, the event is the same as simply
+$\tau_{i,j} < \infty$.
+Applying the lemma again to $-S_{i,j}(\tau_{i,j})$,
+and taking a union bound over both cases,
+gives us that the probability that there is \emph{any} time $t$ with
+$|S_{i,j}(\NumPull{t}{i})| > h (\NumPull{t}{i})$
+is at most $24 \e^{-1.8 b(n)}$.
+Hence, the probability that the error at \emph{any} time $t$ exceeds
+$g(s(t,\SP), \ell-1)$ is bounded by 
 \begin{align*}
@@
 
+Next, we show that for any sample path \SP in the envelope \Env{\ell},
+we can bound the total number of payments made in terms of $\ell$.
+Define $h(\ell) := \max \left( \exp(\frac{2}{\MinProb}),
+\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
+\right)$.
+
+\begin{lemma} \label{lem:envelope-payments}
+Let \SP be a sample path in \Env{\ell}.
+Then, under \SP, the algorithm makes payments at most for the first 
+$h(\ell)$ phases. 
+\end{lemma}
+
+\begin{proof}
+The proof is similar to that of Lemma~\ref{lem:numP}.
+Fix a sample path $\SP \in \Env{\ell}$.
+Consider a phase $s > h(\ell)$.
+
+By definition of \Env{\ell}, the coordinate-wise estimation errors at
+times $t$ in phase $s$ are
+$|\Arm{i}{j} - \ArmE{t}{i}{j}| \leq g(s,\ell)$.
+In particular, all agent typs \AgV whose preference for their best arm
+is sufficiently clear
+($\AgV \cdot \ArmV{\Best{\AgV}} - \AgV \cdot \ArmV{\Second{\AgV}}
+> 2\Diam d g(s,\ell)$) will pull their best arm.
+
+By Lemma~\ref{lem:sdelta}, the \emph{total} measure of agents (across
+all arms) whose best and second-best arm differ in utility by at most
+$2\Diam d \cdot g(s,\ell)$ is at most $2L \Diam d \cdot g(s,\ell)$.
+Substituting the definition of $g$, because 
+$s > h(\ell) \geq \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}$,
+the total measure of these agents is bounded by $\MinProb/2$.
+
+By Assumption~\ref{A3}, at least a \MinProb fraction of agents have
+$i$ as their best arm, so even with estimation errors, at least
+$\MinProb - \MinProb/2 = \MinProb/2$ fraction will still prefer to
+pull arm $i$.
+
+Because $s > h(\ell) \geq \exp(\frac{2}{\MinProb})$, 
+we get that $1/\log(s) \leq \MinProb/2$, so in phase $s$,
+the algorithm will not incentivize any arms whose pulling probability
+is more than $\MinProb/2$, which is all arms.
+So no payments will be made in phase $s$.
+\end{proof}
+
 \begin{extraproof}{Theorem~\ref{rst:budget}}
-
-\noindent\textbf{Step 3: Rewrite the total payment expression}.
-
-\pfcomment{I deleted Step 2 and replaced it by this simpler argument}
-Let $C(s)$ be the cost incurred in phase $s$.
-In each phase, we can make at most $N$ payments, because each arm is incentivized at most once.
-Noting that each sample path $\omega$ is in exactly one envelope and and using Lemma~\ref{lem:sample-path-payment}, we get
-this bound on the cumulative payment:
+We can write the total expected payment as
 \begin{align*}
-\sum_{t=1}^{\infty}c(t) =\sum_{s=1}^{\infty}C(s)
-\leq  \sum_{s=1}^{\infty}\sum_{\ell=1}^{\infty}\mathbbm{1}\{\SP\in \Env{\ell}\} N \bar{c}(s,\ell). 
+  \Expect{\sum_{t=1}^{\infty} \PayA{t}}
+& = \sum_{\ell = 1}^{\infty} \sum_{\SP \in \Env{\ell}}
+  \Prob{\SP} \cdot \sum_{t=1}^{\infty} \PayA{t}(\SP)
+\; = \; \sum_{\ell = 1}^{\infty} \sum_{\SP \in \Env{\ell}}
+  \Prob{\SP} \cdot \sum_{s=1}^{\infty} \sum_{t: s(t,\SP) = s} \PayA{t}(\SP).
 \end{align*}
 
-Set $g(s,\ell)$ to be $\frac{12\sigma \ell}{s^{2/5}}$.
-Since if $|\Arm{i}{j}-\ArmE{t}{i}{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\AgV\in \{\AgV:\AgV\cdot \ArmV{\Best{\AgV}}-\AgV \cdot \ArmV{\Second{\AgV}}> 2\Diam d\lambda\}$, they will correctly identify their best arm.
-Thus, if $|\Arm{i}{j}-\ArmE{t}{i}{j}|\leq \frac{12\sigma l}{s^{2/5}} \leq \frac{p^{-1}(\frac{\MinProb}{2})}{2\Diam d}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$.
-Further, if time $t$ is in a phase $s$ that satisfies $1/log(s)\leq \MinProb/2$, then our algorithm will not incentivize pulling any arms.
-Denote $a_0=\frac{24\Diam d\sigma}{p^{-1}(\frac{\MinProb}{2})}$.
-In order to have $\frac{12\sigma l}{s^{2/5}}\leq \frac{p^{-1}(\frac{\MinProb}{2})}{2\Diam d}$, it is sufficient to have $s\geq \lceil (a_{0} l)^\frac{5}{2} \rceil$.
-In order to have $1/\log(s)\leq \frac{\MinProb}{2}$, we need $s\geq \exp(\frac{2}{\MinProb})$.
-Denote $s_2=\exp(\frac{2}{\MinProb})$.
-Thus, we know we can only incur regret \pfcomment{this should be payment cost, right?} for sample paths \SP in the $\ell^{th}$ envelope in the first $\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}$ phases.
+By Lemma~\ref{lem:envelope-payments},
+the payments are 0 for $s > h(\ell)$,
+and by Lemma~\ref{lem:sample-path-payment},
+when $\SP \in \Env{\ell}$ and $s(t,\SP) = s$, we can bound
+$\PayA{t}(\SP) \leq \MAXR + 2 \Diam d \cdot g(s,\ell)$.
+Furthermore, in any one phase, because each arm is incentivized at
+most once, there are at most \ARMNUM payments total.
+Substituting these bounds, we obtain that
 
-Thus,
 \begin{align*}
-\sum_{t=1}^{\infty}c(t)\leq\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(s,\ell)\mathbbm{1}\{\SP\in \Env{\ell}\}N. 
+  \Expect{\sum_{t=1}^{\infty} \PayA{t}}
+& \leq \sum_{\ell = 1}^{\infty} \sum_{\SP \in \Env{\ell}} \Prob{\SP} \cdot
+  \sum_{s=1}^{h(\ell)} \ARMNUM \cdot (\MAXR + 2 \Diam d \cdot g(s,\ell))
+\\ & = \ARMNUM \cdot
+  \sum_{\ell = 1}^{\infty} \Prob{\SP \in \Env{\ell}} \cdot
+  \sum_{s=1}^{h(\ell)} \left( \MAXR + \frac{24 \Diam d \sigma \ell}{s^{2/5}} \right).
 \end{align*}
 
-Therefore,
+We now lower-bound $s^{2/5} \geq 1$, split off the term for $\ell=1$
+and bound $\Prob{\SP \in \Env{1}} \leq 1$, and apply
+Lemma~\ref{lem:envelope-probability} to the remaining
+$\Prob{\SP \in \Env{\ell}}$ terms, to bound
 
 \begin{align*}
-&E\left[\sum_{t=1}^{\infty}c(t)\right] \\
-\leq &\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\bar{c}(s,\SP)\Prob{\SP \in \Env{\ell}}N  \\
-=&\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[\MAXR+2\Diam d\frac{12\sigma \ell}{s^{2/5}}\right]\Prob{\SP\in \Env{\ell}}N  \\
-\leq &\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}}\left[\MAXR+24\Diam d\sigma l\right]\Prob{\SP\in \Env{\ell}}N. 
+\Expect{\sum_{t=1}^{\infty} \PayA{t}}
+& \leq
+\ARMNUM \cdot \sum_{s=1}^{h(1)} (\MAXR + 24 \Diam d \sigma)
++ \ARMNUM \cdot
+  \sum_{\ell = 2}^{\infty} 24 \ARMNUM d\exp(-1.8(\ell-1)^2) \cdot
+  \sum_{s=1}^{h(\ell)} (\MAXR + 24 \Diam d \sigma \ell)
+\\ & \leq
+\ARMNUM \cdot h(1) \cdot (\MAXR + 24 \Diam d \sigma)
++ 24 \ARMNUM^2 d \cdot \sum_{\ell = 2}^{\infty}
+     \exp(-1.8(\ell-1)^2) \cdot h(\ell) \cdot (\MAXR + 24 \Diam d \sigma \ell).
 \end{align*}
+Because $h(\ell)$ and $(\MAXR + 24 \Diam d \sigma \ell)$ grow
+polynomially in $\ell$, whereas $\exp(-1.8(\ell-1)^2)$ decreases
+exponentially in $\ell$, the sum is dominated by its first term, and
+the overall expected payment is bounded by
 
-\noindent\textbf{Step 5: Final Step}
-
-Thus,
 \begin{align*}
-&E\left[\sum_{t=1}^{\infty}c(t)\right]  \\
-\leq&\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]\Prob{\SP\in \Env{\ell}}N  \\
-\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\Prob{\SP\in L[1]}N +\sum_{l=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]\Prob{\SP\in \Env{\ell}}N  \\
-\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24\Diam d\sigma \right]N +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24\ARMNUM d e^{-1.8(\ell-1)^2}N \\
-\leq & \left[\MAXR+24\Diam d\sigma \right]\ARMNUM \max\{s_2,\lceil (a_0)^{5/2} \rceil\}+\sum_{\ell=2}^{\infty}24\ARMNUM^2 d[\MAXR+24\Diam d\ell\sigma]\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\} e^{-1.8(\ell-1)^2}  \\
-=& O\left(\max\left\{\frac{\ARMNUM^2}{\MinProb^{5/2}},\ARMNUM^2\exp\left(\frac{2}{\MinProb}\right)\right\}\right). 
+O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot h(1) \right)
+& = 
+O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma
+\cdot \exp(\frac{2}{\MinProb}) \right).
 \end{align*}
-\pfcomment{the above bound got tighter.  I didn't carry this forward anywhere where we report on / use the bound.}
-
+\dkcomment{$p^{-5/2}$ is dominated by $\exp(2/p)$.}
+\pfcomment{the bound got tighter.  I didn't carry this forward anywhere where we report on / use the bound.}
 \end{extraproof}

### 2018-02-16 technical-proofs.tex
cleaned up and tightened technical lemmas

\section{Proofs of Technical Lemmas}
\label{sec:n0-inequality-proof}
\label{sec:n1-inquality-proof}

In this section, we prove the two technical lemmas
\ref{lem:n0-inequality} and \ref{lem:n1-inequality}.
We restate both lemmas for convenience.

\dkcomment{I tightened these bounds a bit. Also, the proofs are quite
  a bit shorter now, so we might fold them into the main body?}

\begin{rtheorem}{Lemma}{\ref{lem:n0-inequality}}
For any $n \geq \LatePhase = \max (2, \frac{30 \sigma^3}{x^3})$, 
\begin{align*}
\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} & \leq \frac{n x}{4 \sigma}. 
\end{align*}
\end{rtheorem}

\begin{proof}
By squaring the statement and rearranging, it is equivalent to show that

\begin{align*}
\frac{n}{\log(\log_{1.1}(n)+1)}
  & \geq \frac{9.6\sigma^2}{x^2}.
\end{align*}

A numerical calculation and derivative test shows that
$\frac{n}{\log(\log_{1.1}(n)+1)} \geq n^{2/3}$ for all $n \geq 2$,
and for $n \geq \frac{30 \sigma^3}{x^3}$, we get that
$n^{2/3} \geq \frac{9.6 \sigma^2}{x^2}$.
\end{proof}

\begin{rtheorem}{Lemma}{\ref{lem:n1-inequality}}
For any $T \geq 2$ and $1 \leq n \leq T$, we have
\begin{align*}
2\sqrt{\frac{2}{1.8} n \log(T)}
& \geq \sqrt{0.6 n \log(\log_{1.1}(n)+1) + \frac{2}{1.8} n \log(T)}.
\end{align*}
\dkcomment{This also holds for $n=1$, and I improved the constant.}
\end{rtheorem}

\begin{proof}
By squaring the desired inequality and canceling out common terms, the
statement to prove is equivalent to
$\frac{50}{9} \log T \geq \log(\log_{1.1}(n) + 1)$.
It is sufficient to show that
$\frac{50}{9} \log T \geq \log(\log_{1.1}(T) + 1)$,
which can be verified by numerical calculation for $T=2$ and a
derivative test.
\end{proof}

### 2018-02-16 Discussion.tex
addressed some comments

@@
 \footnote{in fact: exactly, since the algorithm entered phase $s$}
-$s-1$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s-1$.
+$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
 \item Based on the current estimates \ArmEV{t}{i'} of all arms'
@@
 \begin{theorem}
-The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by $O(\ARMNUM^2)$. 
+The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
+\begin{align*}
+O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{p^{5/2}} \right). 
+\end{align*}
 \end{theorem}
@@
 \begin{proof}
-The proof is exact the same as the proof for Lemma~\ref{rst:budget} except we now define $s_2 =\frac{2}{p}$. The rest of the proof remains the same.
+The proof is exact the same as the proof for Theorem~\ref{rst:budget} except we now define $h(\ell) := \max \left( \frac{2}{\MinProb},
+\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
+\right)$. The rest of the proof remains the same.
 \end{proof}
@@
 \begin{align}
-O\left(\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+O\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
   + \frac{\ARMNUM^2 d}{1 - \exp \left(
@@
 \begin{proof}
-The proof is exact the same as the proof for Lemma~\ref{lem:numP} except we now define $\EvenLaterPhase = \max(50, \frac{92.16 \sigma^4}{x^4}, \frac{2}{p})$.
+The proof is exact the same as the proof for Lemma~\ref{lem:numP} except we now define $\EvenLaterPhase = \max (2, \frac{30 \sigma^3}{x^3}, \frac{2}{p})$.
 \end{proof}
@@
 \begin{proof}
-The proof is exact the same as the proof for Lemma~\ref{rst:budget} except we no longer needs $s_2$. The rest of the proof remains the same.
+The proof is exact the same as the proof for Lemma~\ref{rst:budget} except we define $h(\ell) := 
+\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}$. The rest of the proof remains the same.
 \end{proof}
@@
 \begin{proof}
-The proof is exact the same as the proof for Lemma~\ref{lem:numP} except we now define $\EvenLaterPhase = \max(50, \frac{92.16 \sigma^4}{x^4})$ since $\frac{1}{\log(s+s_0)}\leq \frac{p}{2}$ is true for all $s$.
+The proof is exact the same as the proof for Lemma~\ref{lem:numP} except we now define $\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3})$ since $\frac{1}{\log(s+s_0)}\leq \frac{p}{2}$ is true for all $s$.
 \end{proof}
@@
 \begin{align}
-O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
   + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
@@
 \item The expected length of phase $s$ is bounded by $\ARMNUM \log(s+s_0)$;
-\item With the same choice of $g(s)$, the regret in Equation~\ref{equ:small_regret_bound} can now be bounded by $160 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1)\log(T+s_0)=O(\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{p})$.
+\item With the same choice of $g(s)$, the regret in Equation~\ref{equ:small_regret_bound} can now be bounded by $71.11 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1)\log(T+s_0)=O(\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{p})$.
 \end{itemize}

### 2018-02-16 algorithm.tex
addressed some comments

@@
 $s = 1, 2, 3, \ldots$.
-Phase $s$ \pfcomment{starts?} ends when each arm has been pulled at least $s$ times.
-We indicate the start time of phase $s$ by $t_s$.
-\pfcomment{According to the notation we had before, in the .tex file below here,
-phase $s$ starts when I have $s$ pulls of each arm.  Also, we should make sure things are clear regarding the free pull at time $0$.}
-An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
+Phase $s$ starts when each arm has been pulled at least $s$ times.
+We indicate the start time of phase $s$ by $t_s$. An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
 if both of the following hold:
@@
 $\PullProb{t}{i} < 1/\log(s)$.
-\pfedit{$1/\log(1)$ is treated as $\infty$, and if $1/\log(s) \ge 1$ then this condition is automatically met.}
-\dkcomment{Do we need this?}
 \end{itemize}
@@
 
-In this section, we prove that Algorithm~\ref{alg:basic-incentivizing} achieves $O(\ARMNUM^2+\TieDensity(\log(T))^2)$ cumulative regret with $O(\ARMNUM^2)$ payment budget.
+In this section, we prove that Algorithm~\ref{alg:basic-incentivizing} achieves $O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
+O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3)$ cumulative regret with $O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right)$ payment budget.
 This is stated in the following pair of theorems, which together constitute our main results.
@@
 \begin{theorem}
-The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by $O(\ARMNUM^2)$. 
+The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
+\begin{align}
+O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right). \nonumber 
+\end{align} 
 \label{rst:budget}
@@
 \begin{align}
-O \left(\MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
-  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right) +
+O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
 O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3).
@@
 Let $S$ be the set of arms that have been pulled at most
-$s-1$ times at the start of phase $s$.
-Thus, phase $s$ \pfedit{has ended} when each $i \in S$ has been pulled at least once.
+$s$ times at the start of phase $s$.
+Thus, phase $s$ has ended when each $i \in S$ has been pulled at least once.
 Consider any time step $t$.
@@
 Recall that $\sigma$ is the standard deviation of the Gaussian noise.
-Let $\LatePhase \geq \max \SET{50, \frac{92.16 \sigma^4}{x^4}}$.
+Let $\LatePhase \geq \max (2, \frac{30 \sigma^3}{x^3})$.
 
@@
 defining $\Prob{J = \infty} = 1 - \lim_{n \to \infty} \Prob{J \leq n}$.)
-Define \dkcomment{I'm making the dependence of $b$ on $n$ explicit,
-  since that's how we're using it. Is it true with $b$ depending on
-  $n$?
-If not, we need to revisit what we're doing.}
+Define 
 \begin{align*}
-g(n) & = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b(n)}.
+g(n) & = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b}.
 \end{align*}
@@
 \begin{align*}
-\Prob{J < \infty \mbox{ and } S_J \geq g(J)} \leq 12 \e^{-1.8 b(n)}.
+\Prob{J < \infty \mbox{ and } S_J \geq g(J)} \leq 12 \e^{-1.8 b}.
 \end{align*}
@@
 to be the sum of all attribute-$j$ noise components up to and
-including the \Kth{n} pull of arm $i$,
-\dkcomment{I'm not sure if we have defined the notation for components
-  of vectors in the \emph{superscript}. Let's make sure not to forget it.}
-renormalized to have standard deviation $1/2$.
-\dkcomment{Is this the correct scaling.}
+including the \Kth{n} pull of arm $i$, renormalized to have standard deviation $1/2$.
 The $S_n$ define an unbiased half-subgaussian random walk,
 and we can therefore apply Lemma~\ref{lem:ACI-inequality} to them.
-Specifically, we set $b(n) = \frac{n x^2}{16 \sigma^2}$,
+Specifically, we set $b = \frac{x^2}{16 \sigma^2}$,
 and obtain that
@@
 \Prob{J < \infty \mbox{ and } S_J \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}}
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}}
 & \leq 12 \exp \left( \frac{-1.8 J x^2}{16 \sigma^2} \right).
@@
 Applying Lemma~\ref{lem:ACI-inequality} to $-S_n$ with the same choice
-of $b(n)$, and taking a union bound over both cases, we obtain that
+of $b$, and taking a union bound over both cases, we obtain that
 
@@
 \Prob{J < \infty \mbox{ and } |S_J| \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}}
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}}
 & \leq 24 \exp \left( \frac{-1.8 J x^2}{16 \sigma^2} \right).
@@
 $|S_J| \leq
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}$,
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}$,
 we first use that $\sqrt{\cdot}$ is sublinear to bound
-$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}
-\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$.
-
-\bccomment{If $b(n)$ is a constant, here we know $\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16 \sigma^2}}
-\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{\sqrt{J} x}{4 \sigma}\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$.}
+$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}
+\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$ (here we use the fact $\sqrt{J}\leq J$).
 
 Then, we use the following technical Lemma~\ref{lem:n0-inequality}
-(whose proof is given in Appendix~\ref{n0-inequality-proof}, and whose
+(whose proof is given in Appendix~\ref{lem:n0-inequality-proof}, and whose
 precondition we verify momentarily) to bound the first term,
@@
 \begin{lemma} \label{lem:n0-inequality}
-For any $n \geq \LatePhase = \max (50, \frac{92.16 \sigma^4}{x^4})$, 
+For any $n \geq \LatePhase = \max (2, \frac{30 \sigma^3}{x^3})$, 
 \begin{align*}
@@
 Let $x > 0$ be arbitrary.
-Let $\LatePhase \geq \max (50, \frac{92.16 \sigma^4}{x^4})$.
+Let $\LatePhase \geq \max (2, \frac{30 \sigma^3}{x^3})$.
 
@@
 Algorithm~\ref{alg:basic-incentivizing}
-makes any payment is at most $O(\ARMNUM^2)$.
+makes any payment is at most $O\left( N\exp\left(\frac{2}{p}\right) \right)$.
 \end{lemma}
@@
 The cutoff point between early and late phases is now set to
-$\EvenLaterPhase = \max(50, \frac{92.16 \sigma^4}{x^4}, \exp(\frac{2}{\MinProb}))$.
+$\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3}, \exp(\frac{2}{\MinProb}))$.
 Consider the \Kth{s} pull of an arm $i$, for $s \geq \EvenLaterPhase$.
@@
 will pull their best arm \Best{\AgV}.
-\dkcomment{We are losing a factor \ARMNUM here.
-We already took a union bound over all arms in the lemma, and
-we now apply it only to one arm, then sum over all arms.}
 
@@
 \begin{align*}
-\ARMNUM \EvenLaterPhase
+&\ARMNUM \EvenLaterPhase
   + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
     \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)}
-& = O\left( \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
+  \right)} \nonumber \\
+=& O\left( \max\{\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp(\frac{2}{p})\}
   + \frac{\ARMNUM^2 d}{1 - \exp \left(
     \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right).
+  \right)} \right) \nonumber  \\
+=& O\left( N\exp\left(\frac{2}{p}\right) \right).
 \end{align*}
-\dkcomment{It seems like with our choice of $x$ (which may be
-  unavoidable), we get quite large factors, in particular with the
-  fourth power.
-  Also, it would be nice if we could simplify the $\frac{1}{1-\exp()}$
-  term. Unfortunately, I think that the inequality goes the wrong way
-  for applying the standard $\exp(-x) \geq 1-x$ bound.}
 
@@
 incentivizes agents at most 
-$O \left( \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
-  + \frac{\ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right)$
+$O\left( N\exp\left(\frac{2}{p}\right) \right)$
 times in expectation, each time causing regret at most \MAXR,
 for a total expected regret of at most
-$O \left(\MAXR\cdot\max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
-  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right)$.
+$O\left(\MAXR\cdot N\exp\left(\frac{2}{p}\right) \right)$.
 For the rest of the proof, we focus on the regret incurred when agents
@@
 \begin{align}
-&E[\sum_{s=1}^{T}\sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)] \leq \sum_{s=1}^{T}\TieDensity\cdot g^2(s)N\log(s). \label{equ:small_regret_bound}
+&E\left[\sum_{s=1}^{T}\sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)\right] \leq \sum_{s=1}^{T}\TieDensity\cdot g^2(s)N\log(s). \label{equ:small_regret_bound}
 \end{align}
@@
 let the random variable $t_s$ be the final time step in phase $s$,
-for each $s$.
-\dkcomment{Is $t_s$ better or $T_s$?}
-Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
+for each $s$. Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
 time step in the \Kth{s} phase,
@@
 \begin{align}
-&O \left( \MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
-  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right)
+&O\left(\MAXR\cdot N\exp\left(\frac{2}{p}\right) \right)
 \\
@@
 The first line is independent of $T$, and we now choose
-$g^2(s) = \frac{288\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$
+$g^2(s) = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$
 with the goal of minimizing the second line.
@@
 &\Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \\
-\leq &\sum_{i,j}\Prob{|S_s|\geq 3\sqrt{\frac{2}{1.8}s\log(T)}} \\
+\leq &\sum_{i,j}\Prob{|S_s|\geq 2\sqrt{\frac{2}{1.8}s\log(T)}} \\
 \leq &\sum_{i,j}\Prob{|S_s|\geq \sqrt{0.6s\log(\log_{1.1}(s)+1)+\frac{2}{1.8}\log(T)s}} \leq 24\ARMNUM d \cdot \exp(-2\log(T)),
 \end{align*}
-where the second to last inequality is because the following technical inequality, whose proof we include in Appendix~\ref{sec:n1-inequality-proof}.
+where the second to last inequality is because the following technical inequality, whose proof we include in Appendix~\ref{lem:n1-inequality-proof}.
 
 \begin{lemma} \label{lem:n1-inequality}
-For $2\leq s\leq T$, we have $3\sqrt{\frac{2}{1.8}s\log(T)} \geq \sqrt{0.6s\log(\log_{1.1}(s)+1)+\frac{2}{1.8}\log(T)s}$.
+For any $T \geq 2$ and $1 \leq n \leq T$, we have
+\begin{align*}
+2\sqrt{\frac{2}{1.8} n \log(T)}
+& \geq \sqrt{0.6 n \log(\log_{1.1}(n)+1) + \frac{2}{1.8} n \log(T)}.
+\end{align*}
 \end{lemma}
@@
 \lefteqn{\sum_{s=1}^{T} 24\ARMNUM^2 d \log(s) \MAXR \exp\left(-2\log(T)\right)  +
-          \frac{288\ARMNUM\Diam^2 d^2\sigma^2
+          \frac{128\ARMNUM\Diam^2 d^2\sigma^2
           \TieDensity\log(T)}{1.8}\sum_{s=1}^{T}\frac{\log(s)}{s}}
 \\ & \leq
-24\ARMNUM^2 d R\frac{T(T-1)}{2T^2}  + 160 \ARMNUM \Diam^2 d^2\sigma^2
+24\ARMNUM^2 d R\frac{T(T-1)}{2T^2}  + 71.11 \ARMNUM \Diam^2 d^2\sigma^2
           \TieDensity(\log(T))^2(\log(T)+1)
   \\ & \leq
-12 \ARMNUM^2 d R  + 160 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^2(\log(T)+1). 
+12 \ARMNUM^2 d R  + 71.11 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^2(\log(T)+1). 
 \end{align*}
 
-Adding all terms gives an upper bound of
-
-\begin{multline*}
-O \left(\MAXR\cdot \max\{\frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}, N\exp(\frac{2}{p})\}
-  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right) +
-O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3) 
-\end{multline*}
-
-on the cumulative expected regret.
-
-\bccomment{David, could you go through the proof again if possible? Thanks}
+Adding all terms gives an upper bound of $O\left(\MAXR\cdot N\exp\left(\frac{2}{p}\right) \right) +O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3)$ on the cumulative expected regret.
 

### 2018-02-16 introduction.tex
small edits mostly to the problem setting section, but also to other sections
addressed some comments

@@
 
-\pfedit{Many websites and apps} are designed to facilitate joint discovery,
+Many websites and apps are designed to facilitate joint discovery,
 sharing, and recommendations of content\pfdelete{by large numbers of users}.
@@
 preferred by any agents.
-
-\dkcomment{I strongly dislike the ``Table of contents'' paragraph, and
-  much prefer weaving pointers into the main text.}

### 2018-02-16 lower_bound.tex
addressed some comments

@@
 
-We saw in Corollary~\ref{cor:constant-regret} that
+We saw in Corollary~\ref{cor:constant-regret} that \bccomment{David, could you put the right reference here?}
 when agent preferences for their best arm are sufficiently clear,
@@
 and $\Noise[t]{2} \sim \Normal{0}{\sqrt{1/t}})$.
-\dkcomment{I think we define this to be the estimates at the beginning
-  of round $t$, so we may be off by 1 here and in other places.}
 We lower-bound the regret in step $t$ by focusing on the event that

### 2018-02-16 payment-proof.tex
fixed some typos
addressed some comments

@@
 \begin{rtheorem}{Theorem}{\ref{rst:budget}}
-\dkcomment{Copy here the final form of the theorem once it is finalized.}
+The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
+\begin{align}
+O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right).  \nonumber 
+\end{align}
 \end{rtheorem}
@@
 noise \NoiseV[t] in the draws the pulled arms,
-with an infite \dkcomment{Is it infinite?} time horizon.
-\dkcomment{We should be consistent about using filtration vs.~sample
-  path.}
-\pfcomment{I removed discussion of filtrations and replaced them by discussion of history.}
+with an infinite time horizon.
 
@@
 \begin{align*}
-\hat{L}_\ell
+\hat{\mathcal{L}}_\ell
   & = \Set{\SP}{|\Err{t}{i}{j}(\SP)| \leq g(s(t,\SP),\ell)
     \mbox{ for all } i,j,t},\\
-\Env{1} & = \hat{L}_1\\ 
-\Env{\ell} & = \hat{L}_{\ell} - \hat{L}_{\ell-1}
-  \qquad \mbox{ for } \ell \geq 2.
+\Env{1} & = \hat{\mathcal{L}}_1,\\ 
+\Env{\ell} & = \hat{\mathcal{L}}_{\ell} \setminus \hat{\mathcal{L}}_{\ell-1}
+  \quad \mbox{ for } \ell \geq 2.
 \end{align*}
@@
 $\bar{c} (s,\ell) = \MAXR + 2 \Diam d \cdot g(s,\ell)$.
-\dkcomment{Verify that the way I talk about $t$ vs.~$s$ is right.}
 \end{lemma}
@@
 to $S_{i,j}(t)$, with a stopping time of $\tau_{i,j}$ and
-with $b(n) = (\ell-1)^2$ \dkcomment{omit dependence on $n$ here?}.
+with $b = (\ell-1)^2$.
 We obtain that the probability that $\tau_{i,j} < \infty$ and 
 $S_{i,j}(\tau_{i,j}) > h(\tau_{i,j})$ is at most
-$12 \e^{-1.8 b(n)}$.
+$12 \e^{-1.8 b}$.
 By definition of $\tau_{i,j}$, the event is the same as simply
@@
 \end{align*}
-\dkcomment{$p^{-5/2}$ is dominated by $\exp(2/p)$.}
-\pfcomment{the bound got tighter.  I didn't carry this forward anywhere where we report on / use the bound.}
 \end{extraproof}

### 2018-02-16 problem_setting.tex
minor edits
addressed some comments

@@
 Whenever arm $i$ is pulled, its current utility-relevant features are
-determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero \pfedit{independent} 
-Gaussian%
+determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero independent Gaussian%
 \footnote{For simplicity of notation, we assume that the variance
@@
 
-\dkcomment{Do we need this definition here?}\pfcomment{I agree that we can move the definition of phase to where we define our algorithm.}
-We call time $t_{n}=\min_{t}\{\forall i, \NumPull{t}{i} \geq n\}$ the
-\emph{starting point of the $n^{th}$ phase}.
-We call the set of times $[t_{n}, t_{n+1})$ the
-\emph{$n^{th}$ round}.
-
 \dkdelete{This behavior may be recovered if agents are Bayesian and

### 2018-02-16 algorithm.tex
pass through regret proof

@@
 \label{sec:ub}
+
+\dkcomment{Here and earlier, we are using a lot of displayed
+  equations. We could inline some/many of them to save space.}
 
@@
 to guarantee that the next agent pulls it.
-This way the algorithm ensures each arm is pulled often enough.
+This way the algorithm ensures that each arm is pulled often enough.
 
@@
 if both of the following hold:
-\pfdelete{
-We call time $t_{s}=\min_{t}\{\forall i, \NumPull{t}{i} \geq s\}$ the
-\emph{starting point of the $s^{th}$ phase}.
-We call the set of times $[t_{s}, t_{s+1})$ the
-\emph{$n^{th}$ phase}.
-}
 
@@
 uniformly at random to incentivize.
+\dkcomment{Is uniform randomness used anywhere? Does arbitrary work?}
 When the algorithm decides to incentivize an arm $i$,
@@
 \STATE Set the current phase number $s = 1$.
+\COMMENT{Each arm is pulled once initially ``for free''.}
 \FOR{time steps $t = 1, 2, 3, \ldots$}
-\IF{$\NumPull{t}{i} \geq s$ for all arms $i$}
+\IF{$\NumPull{t}{i} \geq \dkedit{s+1}$ for all arms $i$}
 \STATE Increment the phase $s = s + 1$.
@@
 \STATE Let $i$ be a uniformly random payment-eligible arm.
+\dkcomment{Is uniform randomness used anywhere?}
 \STATE Offer payment
@@
 
+\dkcomment{I had written ``exponentially'' in a few places here, but I
+  don't think that was correct. The error only decreases as
+  $\sqrt{s}$, while the probability of deviating beyond that error
+  decreases exponentially.}
 The high-level idea of the proof of Theorem~\ref{thm:main-overview}
@@
 ``frequently enough,''
-the estimates \ArmEV{t}{i} become exponentially more accurate in the
+the estimates \ArmEV{t}{i} become gradually more accurate in the
 phase number $s$.
-Thus, the fraction of agents who misidentify their best arm decreases
-exponentially as well.
+Thus, the fraction of agents who misidentify their best arm decreases.
 Because for each arm, enough agents have a true preference for this
@@
 resulting in a payment bound independent of $T$.
-Similarly, the regret will decrease exponentially, and mostly accrue
-due to agents close to the border \pfcomment{we could clarify what border} making mistakes in their arm choices.
+Similarly, the regret will decrease, and mostly accrue
+due to ``problematic'' agents who are nearly tied in their preferences
+between their top two arm choices.
 The detailed analysis following this outline is somewhat subtle, though,
@@
 
-To capture the probability masses of problematic and non-problematic
-agents \pfcomment{in another pass we could seek to clarify what we mean by being problematic in the context of the border statement above}, we define the following:
+To capture the probability masses of problematic agents,
+we define
 $\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
 \AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
-is the total probability mass (across all arms) of agents
+to be the total probability mass (across all arms) of agents
 whose (actual) preference for their best arm over their second-best
 arm is at most $\delta$.
-\pfcomment{We can check through the whole paper on whether we have $\AgV \sim \AgentDist$ in the subscript or just $\AgV \sim \AgentDist$.
-I think we have only $\AgentDist$ in the problem description.}
-The minimum probability mass of users who prefer their best arm
-sufficiently strongly over their second-best arm is denoted by
-$\ClearPref{\delta} = \min_{i}
-\Prob[\AgV \sim \AgentDist]{\Best{\AgV}=i,%
-\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > \delta}$.
-Notice that \AlmostTied{\delta} (being a measure of problematic
-agents) is defined as a sum over all arms,
-while  \ClearPref{\delta} (being a measure of non-problematic agents)
-is defined as a minimum over arms.
-Also notice that $\ClearPref{0} = \MinProb$.
+\pfcomment{We can check through the whole paper on whether we have
+  $\AgV \sim \AgentDist$ in the subscript or just $\AgV \sim
+  \AgentDist$.  I think we have only $\AgentDist$ in the problem
+  description.}
+\dkcomment{There must be a typo in Peter's comment.}
+%The minimum probability mass of users who prefer their best arm
+%sufficiently strongly over their second-best arm is denoted by
+%$\ClearPref{\delta} = \min_{i}
+%\Prob[\AgV \sim \AgentDist]{\Best{\AgV}=i,%
+%\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > \delta}$.
+%Notice that \AlmostTied{\delta} (being a measure of problematic
+%agents) is defined as a sum over all arms,
+%while  \ClearPref{\delta} (being a measure of non-problematic agents)
+%is defined as a minimum over arms.
+%Also notice that $\ClearPref{0} = \MinProb$.
 \dkcomment{We should stress somewhere that we assume that actual ties
   have measure 0.}
+\dkcomment{We weren't using $p(\delta)$ anywhere, so I got rid
+  of it.}
 
@@
 
+\dkcomment{Depending on how we structure Section 3, we might
+get rid of those theorems, and only consider them parts of Theorem 2
+that we prove here.}
+
 \begin{theorem}
-The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
+The expected payment budget for
+Algorithm~\ref{alg:basic-incentivizing} is bounded above by
 \begin{align}
@@
 \begin{theorem}
-For any given $T$, the cumulative regret for Algorithm~\ref{alg:basic-incentivizing}
-is bounded above by 
+For any given $T$, the expected cumulative regret for
+Algorithm~\ref{alg:basic-incentivizing} up to time $T$ is bounded
+above by 
 \begin{align}
@@
 the estimates of the arms' attribute vectors become
-exponentially more accurate with increasing phases $s$.
+more accurate with increasing phases $s$.
 That intuition is captured by the following lemma.
@@
 Fix an arm $i$ and attribute $j$.
+By the assumptions of the lemma,
+the stopping time $\tau$ is such that almost surely, each arm --- and
+in particular arm $i$ --- has been pulled at least
+$s \geq \LatePhase$ times at time $\tau$.
+Define $J$ to be the number of times that $i$ has been pulled at
+time $\tau$.
 For any $n \geq 1$, let $k_n$ be the time step right after arm $i$ has
@@
 The $S_n$ define an unbiased half-subgaussian random walk,
-and we can therefore apply Lemma~\ref{lem:ACI-inequality} to them.
+and we can therefore apply Lemma~\ref{lem:ACI-inequality} to them and
+the stopping time $J$.
 Specifically, we set $b = \frac{x^2}{16 \sigma^2}$,
@@
 
-In the high-probability case
-$|S_J| \leq
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}$,
-we first use that $\sqrt{\cdot}$ is sublinear to bound
-$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}
-\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$ (here we use the fact $\sqrt{J}\leq J$).
-
-Then, we use the following technical Lemma~\ref{lem:n0-inequality}
-(whose proof is given in Appendix~\ref{lem:n0-inequality-proof}, and whose
-precondition we verify momentarily) to bound the first term,
-giving us an overall upper bound of
-$|S_J| \leq \frac{J x}{2 \sigma}$.
-
-\begin{lemma} \label{lem:n0-inequality}
-For any $n \geq \LatePhase = \max (2, \frac{30 \sigma^3}{x^3})$, 
-\begin{align*}
-\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} & \leq \frac{n x}{4 \sigma}. 
-\end{align*}
-\end{lemma}
-
-Substituting the definition of $S_J$ and canceling common terms,
-the inequality implies that
-$|\ArmE{k_J}{i}{j} - \Arm{i}{j}| \leq x$.
-By the assumptions of the lemma,
-the stopping time $\tau$ is such that almost surely, each arm --- and
-in particular arm $i$ --- has been pulled at least
-$s \geq \LatePhase$ times at time $\tau$.
-Defining $J$ to be the number of times that $i$ has been pulled at
-time $\tau$, we obtain that $J$ satisfies the precondition of
-Lemma~\ref{lem:n0-inequality}.
-Furthermore, with probability 1, $J$ will be finite, meaning that
+Because $J$ will be finite with probability 1, we can drop the
+$J < \infty$ part of the event:
 \begin{align*}
@@
 
-Finally, this choice of $J$ ensures that
+In the high-probability case
+$|S_J| \leq
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}$,
+we first use that $\sqrt{\cdot}$ is sublinear to bound
+$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}
+\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$
+(here we use the fact $\sqrt{J} \leq J$).
+Then, we will show momentarily that
+$\sqrt{0.6 J \log (\log_{1.1}(J) + 1)} \leq \frac{J x}{4 \sigma}$,
+giving us an overall upper bound of
+$|S_J| \leq \frac{J x}{2 \sigma}$.
+
+Substituting the definition of $S_J$ and canceling common terms,
+the inequality implies that
+$|\ArmE{k_J}{i}{j} - \Arm{i}{j}| \leq x$.
+The choice of $J$ ensures that
 $\ArmE{k_J}{i}{j} = \ArmE{\tau}{i}{j}$,
@@
 attributes.
+
+It remains to show that
+$\sqrt{0.6 J \log (\log_{1.1}(J) + 1)} \leq \frac{J x}{4 \sigma}$.
+By squaring the statement and rearranging, it is equivalent to show that
+$\frac{J}{\log(\log_{1.1}(J)+1)} \geq \frac{9.6\sigma^2}{x^2}$.
+Because $J \geq \LatePhase \geq 2$,
+a numerical calculation and derivative test shows that
+$\frac{J}{\log(\log_{1.1}(J)+1)} \geq J^{2/3}$,
+and because $J \geq \LatePhase \geq \frac{30 \sigma^3}{x^3}$,
+we get that
+$J^{2/3} \geq \frac{9.6 \sigma^2}{x^2}$, completing the proof.
 \end{extraproof}
 
-Lemma~\ref{lem:round-prob} implies that errors from myopic play
-decrease exponentially in the phase number $s$.
+Lemma~\ref{lem:round-prob} implies that the probability of making
+large errors due to myopic play decreases exponentially in the phase
+number $s$.
 
@@
 
-Thus, for any phase $s \geq \EvenLaterPhase$
+Thus, for any phase $s \geq \EvenLaterPhase$,
 Algorithm~\ref{alg:basic-incentivizing} incentivizes any given arm $i$
@@
   \right)} \nonumber \\
-=& O\left( \max\{\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp(\frac{2}{p})\}
+=& O\left( \max\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp(\frac{2}{p})\right)
   + \frac{\ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
   \right)} \right) \nonumber  \\
@@
 
-\begin{proof}
+\begin{extraproof}{Theorem~\ref{rst:regret}}
 Regret can arise in two ways:
@@
 the best arm.
-To be more precise, we will define (with hindsight) a phase-dependent
-cutoff $g(s)$, and consider a regret exceeding $g(s)$ large.
+To be more precise, we will define (with foresight) a phase-dependent
+cutoff
+$g(s) = \sqrt{\frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}}$,
+and consider a regret exceeding $g(s)$ large.
 
 We first consider agents \AgV incurring positive regret less than $g(s)$.
-The second-best arm \Second{\AgV} of \AgV must satisfy
+The second-best arm \Second{\AgV} of such an agent \AgV must satisfy
 $\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(s)$.
@@
 and each incurs regret at most $g(s)$.
-Summing over all time steps, the expected total regret from such agents is at most
+Summing over all time steps,
+and using Lemma~\ref{lem:phase-length} to bound the number of time
+steps in phase $s$, 
+the expected total regret from such agents is at most
 \begin{align}
-&E\left[\sum_{s=1}^{T}\sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)\right] \leq \sum_{s=1}^{T}\TieDensity\cdot g^2(s)N\log(s). \label{equ:small_regret_bound}
+\Expect{\sum_{s=1}^{T} \sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)}
+& \leq \sum_{s=1}^{T} \TieDensity \cdot g^2(s) \ARMNUM \log(s).
+\label{equ:small_regret_bound}
 \end{align}
@@
 To bound the regret incurred in time steps with large regret,
-let the random variable $t_s$ be the final time step in phase $s$,
+we use a proof nearly identical to that of
+Lemma~\ref{lem:round-prob} and Corollary~\ref{cor:right-choice}.
+The only reason we cannot directly apply them is that in order
+to apply to arbitrary $x > 0$, we had to assume that
+$\LatePhase \geq \frac{30 \sigma^3}{x^3}$, a bound we cannot afford here.
+So here, we will choose a larger value of $x$, and in return
+will only need to assume that $T \geq 2$.
+
+Let the random variable $t_s$ be the final time step in phase $s$,
 for each $s$. Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
@@
 i.e., $k > t_{s}-t_{s-1}$.
-For $t = \tau_{s}^{k}$, we know
-\begin{align}
-&\Prob{\text{incur regret exceeding g(s)}} \nonumber \\
-\leq & \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}}.\nonumber 
-\end{align}
+Exactly as in the proof of Corollary~\ref{cor:right-choice},
+it is sufficient to show that with high probability,
+$|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq \frac{g(s)}{2\Diam d}$
+for all arms $i$ and attributes $j$.
 
-Because the regret never exceeds \MAXR,
-the expected (large) regret for the \Kth{k} time step of phase $s$
-is bounded above by
-$\Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR$.
-Summing over all time steps $t$, we get that the total regret from
-large-regret steps is at most
+The proof of this high-probability guarantee for the stopping time
+$t = \tau_s^k$ is identical to the proof of
+Lemma~\ref{lem:round-prob} with $x = \frac{g(s)}{2 \Diam d}$
+until the step where we start bounding
+$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}$.
+At that point in the proof, we had shown that 
+the probability of $|S_J|$ exceeding the preceding expression is at most
+\begin{align*}
+24 \exp \left( \frac{-1.8 s x^2}{16 \sigma^2} \right)
+  & = \frac{24}{T^2}.
+\end{align*}
+
+Substituting $J = s$ and $x = \frac{g(s)}{2 \Diam d}$, the upper bound is
+$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{2 \log T}{1.8 J}}$.
+We claim that for $J \leq T$ and $T \geq 2$, we have
+$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{2 \log T}{1.8 J}}
+\leq 2 \sqrt{\frac{2}{1.8} s \log(T)}$.
+Indeed, by squaring this inequality and canceling out common terms,
+the claimed inequality is equivalent to
+$\frac{50}{9} \log T \geq \log(\log_{1.1}(J) + 1)$.
+Because $J \leq T$, it is sufficient to show that
+$\frac{50}{9} \log T \geq \log(\log_{1.1}(T) + 1)$,
+which can be verified by numerical calculation for $T=2$ and a
+derivative test.
+
+With this upper bound of $|S_J| \leq 2 \sqrt{\frac{2}{1.8} s \log(T)}$,
+we can substitute the definition of $S_J$ to obtain that
+$|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq \frac{g(s)}{2\Diam d}$
+in the high-probability event.
+By a union bound over all arms $i$ and attributes $j$,
+the probability of incurring regret exceeding $g(s)$ is at most
+$\frac{24 \ARMNUM d}{T^2}$.
+
+Using that the regret never exceeds \MAXR,
+and applying Lemma~\ref{lem:phase-length},
+the total expected regret from large-regret steps is at most
 
 \begin{align*}
-\lefteqn{\sum_{s = 1}^T \sum_{t=t_s}^{t_{s+1}-1}
-  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR}
-\\ & =
-\sum_{s = 1}^T 
-  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
-  \cdot \Expect{\mbox{Length of phase } s}
-\\ & \leq
-\sum_{s = 1}^T 
- \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
-  \cdot \ARMNUM \log(s),
+\sum_{s = 1}^T \sum_{t=t_s}^{t_{s+1}-1}
+  \Prob{\mbox{incur regret exceeding } g(s) \mbox{ at step } t} \cdot \MAXR
+& \leq
+ \sum_{s = 1}^T \frac{24 \ARMNUM d}{T^2} \cdot \MAXR \cdot \ARMNUM \log(s)
+\\ & \leq 12 \ARMNUM^2 d \MAXR.
 \end{align*}
-where the inequality was an application of Lemma~\ref{lem:phase-length}.
-Adding all three terms,
+
+Adding all three types of regret terms,
+and substituting that 
+$g^2(s) = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
 the cumulative regret up to time $T$ is at most
 
-\begin{align}
-&O\left(\MAXR\cdot N\exp\left(\frac{2}{p}\right) \right)
-\\
-+ & \sum_{s = 1}^T 
-  \Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \cdot \MAXR
-  \cdot \ARMNUM \log(s),
-+ \sum_{s=1}^{T}\TieDensity \cdot g^2(s)\cdot N\log(s). \label{thm:equ}
-\end{align}
-
-The first line is independent of $T$, and we now choose
-$g^2(s) = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$
-with the goal of minimizing the second line.
-With this choice and same definition of $S_{s}$ as in the proof of Lemma~\ref{lem:round-prob}, 
 \begin{align*}
-&\Prob{\exists i,j, s.t. |\ArmE{t}{i}{j} - \Arm{i}{j}|\geq \frac{g(s)}{2\Diam d}} \\
-\leq &\sum_{i,j}\Prob{|S_s|\geq 2\sqrt{\frac{2}{1.8}s\log(T)}} \\
-\leq &\sum_{i,j}\Prob{|S_s|\geq \sqrt{0.6s\log(\log_{1.1}(s)+1)+\frac{2}{1.8}\log(T)s}} \leq 24\ARMNUM d \cdot \exp(-2\log(T)),
+\lefteqn{
+O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
++ \ARMNUM^2 \MAXR d
++ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} g^2(s) \log(s) \right)}
+\\ & = 
+O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
++ \ARMNUM^2 \MAXR d
++ \ARMNUM \TieDensity \Diam^2 d^2 \sigma^2 \cdot \log^3(T) \right).
 \end{align*}
-where the second to last inequality is because the following technical inequality, whose proof we include in Appendix~\ref{lem:n1-inequality-proof}.
-
-\begin{lemma} \label{lem:n1-inequality}
-For any $T \geq 2$ and $1 \leq n \leq T$, we have
-\begin{align*}
-2\sqrt{\frac{2}{1.8} n \log(T)}
-& \geq \sqrt{0.6 n \log(\log_{1.1}(n)+1) + \frac{2}{1.8} n \log(T)}.
-\end{align*}
-\end{lemma}
-
-Therefore, the second line becomes
-
-\begin{align*}
-\lefteqn{\sum_{s=1}^{T} 24\ARMNUM^2 d \log(s) \MAXR \exp\left(-2\log(T)\right)  +
-          \frac{128\ARMNUM\Diam^2 d^2\sigma^2
-          \TieDensity\log(T)}{1.8}\sum_{s=1}^{T}\frac{\log(s)}{s}}
-\\ & \leq
-24\ARMNUM^2 d R\frac{T(T-1)}{2T^2}  + 71.11 \ARMNUM \Diam^2 d^2\sigma^2
-          \TieDensity(\log(T))^2(\log(T)+1)
-  \\ & \leq
-12 \ARMNUM^2 d R  + 71.11 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^2(\log(T)+1). 
-\end{align*}
-
-Adding all terms gives an upper bound of $O\left(\MAXR\cdot N\exp\left(\frac{2}{p}\right) \right) +O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3)$ on the cumulative expected regret.
-
-\end{proof}
-
-\dkcomment{Edited up to here.}
+\end{extraproof}

### 2018-02-16 algorithm.tex
working on section 3

--- 2018-02-16 algorithm.tex
@@
 
-In this section, we prove that Algorithm~\ref{alg:basic-incentivizing} achieves $O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
-O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3)$ cumulative regret with $O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right)$ payment budget.
-This is stated in the following pair of theorems, which together constitute our main results.
-
-\begin{theorem}
-The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
-\begin{align}
-O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right). \nonumber 
-\end{align} 
-\label{rst:budget}
-\end{theorem}
-
-\begin{theorem}
-For any given $T$, the cumulative regret for Algorithm~\ref{alg:basic-incentivizing}
-is bounded above by 
-\begin{align}
-O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
-O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3).
-\end{align}
-\label{rst:regret}
-\end{theorem}
+We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.
 

### 2018-02-16 result_discussion.tex
working on section 3

@@
 \section{Overview of Results and Discussion}
-\dkcomment{I envision this section doing the following:
-\begin{enumerate}
-\item State the main theorem(s) formally.
-\item Discuss lower bounds or impossibility results.
-\item Discuss extensions.
-\item Discuss the justification or comparison to standard bandits.
-\item Discuss the comparison in the 2x2 square.
-\end{enumerate}
-}
-
-\dkcomment{For now, I am just copying over material from various other
-  parts that Bangrui/Peter wrote or I had written in earlier
-  iterations.}
 
@@
 
-\begin{theorem} \label{thm:main-overview}
-Under some technical assumptions, 
-there exists a policy which pays at most $O(\ARMNUM^2)$ in expectation,
-and achieves regret at most $O(\ARMNUM^2 + \log^2(T))$.
-\dkcomment{Omitting the density here.}
+%
+% State the main theorem(s) formally.
+%
+
+We will show below that our algorithm (described formally below as Algorithm~\ref{alg:basic-incentivizing}) achieves $O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) + O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3)$ cumulative regret with $O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right)$ payment budget.
+We state these results formally, which together constitute our main results.
+
+\begin{theorem}
+The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
+\begin{align}
+O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right). \nonumber 
+\end{align} 
+\label{rst:budget}
 \end{theorem}
+
+\begin{theorem}
+For any given $T$, the cumulative regret for Algorithm~\ref{alg:basic-incentivizing}
+is bounded above by 
+\begin{align}
+O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
+O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3).
+\end{align}
+\label{rst:regret}
+\end{theorem}
+
+% Discuss lower bounds or impossibility results.
+We also show a lower bound of $\Omega(\log(T))$ (section~\ref{sec:lb}) on the regret of any algorithm when agents have a density.
+
+In the specific case of discrete distributions over agent preferences, in which $L=0$ \pfcomment{check whether this is the right description}, we obtain tighter bounds:
+
+%Discuss extensions.
+
+% Discuss the justification or comparison to standard bandits.
+We compare these results to those possible for standard bandits. In standard bandits, the payment is obviously $0$, and the regret scales as $N \sqrt{T}$ \pfcomment{add cite}.
+
+% Discuss the comparison in the 2x2 square.
+
+\pfcomment{Below this is old text}
 

### 2018-02-16 lower_bound.tex

@@
 We saw in Corollary~\ref{cor:constant-regret} that \bccomment{David, could you put the right reference here?}
+\dkcomment{This was supposed to be a corollary (presumably in Section
+  3) we would write that would show that
+  in the special case $\TieDensity = 0$, the regret is constant.}
 when agent preferences for their best arm are sufficiently clear,

### 2018-02-16 Discussion.tex
Some progress cleaning up the special cases section

@@
-\subsection{Special Case}
+\subsection{Special Cases: Discrete Preferences and Known $p$}
 
-As we see in the proof of Theorem~\ref{rst:budget} and Theorem~\ref{rst:regret}, we occurred an exponential payment/regret at the initial phases simplily because we decrease the probability threshold too slowly, which is needed when bounding the regret after the concentration probability kicks in as in Equation~(\ref{equ:small_regret_bound}).
-In this section, we are going to discuss two special cases where we can get rid of the exponential dependency on the number of arms in the payment and regret bound.
+The proofs of Theorem~\ref{rst:budget} and Theorem~\ref{rst:regret} incur exponential payment and regret in the initial phases because the threshold required for incentivization $1/\log(s)$ decreases slowly.
+This slow decrease is needed to bound the regret in the later phases when the concentration inequality kicks in as in Equation~(\ref{equ:small_regret_bound}).
+In this section, we discuss two problem settings where we can modify our algorithm slightly and provide new bounds that remove this exponential dependence.
+Both problem settings are special cases of the more general problem setting previously considered.
 
-\textbf{Case 1: If $\exists \delta_0>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$.}
+We first discuss an assumption that holds when $\theta$ follows a finite discrete distribution.
+\begin{assumption}
+\label{a:discrete}
+(Discrete Preferences) 
+$\exists \delta_0>0$ such that $F_{i,j}(\delta_0)=0$ for all $i,j$.
+\end{assumption}
 
-In this case, we can simplily modify the payment-eligible criteria as follows: An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
-if both of the following hold:
-
+When Assumption~\ref{a:discrete} holds, we modify our algorithm to use a new payment-eligibility criterion: an arm $i$ is \emph{payment-eligible} at time $t$ in phase $s$ when both of the following are true:
 \begin{itemize}
@@
 
-The algorithm remains the same as Algorithm~\ref{alg:basic-incentivizing}. Under this new payment-eligible criteria, we are able to prove the following results:
+We refer to this modified version of Algorithm~\ref{alg:basic-incentivizing} as the {\it Discrete-Preference Algorithm.} We prove the following result for this algortithm under Assumption~\ref{a:discrete}.
+
+\pfcomment{I collapsed these results together into a single theorem, and consolidated the proofs.  I tweaked some wording in the proofs, but I didn't check them in detail.}
 
 \begin{theorem}
-The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
+Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has an expected payment budget bounded above by 
 \begin{align*}
@@
 \end{align*}
-\end{theorem}
-
-\begin{proof}
-The proof is exact the same as the proof for Theorem~\ref{rst:budget} except we now define $h(\ell) := \max \left( \frac{2}{\MinProb},
-\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
-\right)$. The rest of the proof remains the same.
-\end{proof}
-
-\begin{lemma}  \label{lem:NumP1}
-The expected number of time steps in which
-Algorithm~\ref{alg:basic-incentivizing}
-makes any payment is at most 
-\begin{align}
-O\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
-  + \frac{\ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right). \nonumber 
-\end{align}
-\end{lemma}
-
-\begin{proof}
-The proof is exact the same as the proof for Lemma~\ref{lem:numP} except we now define $\EvenLaterPhase = \max (2, \frac{30 \sigma^3}{x^3}, \frac{2}{p})$.
-\end{proof}
-
-\begin{theorem}
-The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
+and an expected regret bounded above by 
 \begin{align}
@@
 \begin{proof}
-The proof of this Theorem is similar as Theorem~\ref{rst:regret}, except
+The proof of the expected payment bound is the same as the proof of Theorem~\ref{rst:budget}, except that we now define $h(\ell) := \max \left( \frac{2}{\MinProb},
+\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
+\right)$.
+
+The proof of the expected regret bound first uses a lemma bounding the expectedt number of time steps in which a payment is made by 
+\begin{align}
+O\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
+  + \frac{\ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} \right). \nonumber 
+\end{align}
+The proof follows that of Lemma~\ref{lem:numP}, except that it defines $\EvenLaterPhase = \max (2, \frac{30 \sigma^3}{x^3}, \frac{2}{p})$.
+
+The proof of the expected regret bound then follows the proof of Theorem~\ref{rst:regret}, with these modifications:
 \begin{itemize}
-\item We can use Lemma~\ref{lem:NumP1} to bound the regret when we decide to incentivize;
+\item We use the lemma stated above to bound the regret on pulls that incentivize;
 \item The expected length of phase $s$ is bounded by $\ARMNUM s$;
-\item The regret in Equation~\ref{equ:small_regret_bound} can now be bounded by a constant based on our assumption.
+\item The regret in Equation~\ref{equ:small_regret_bound} can now be bounded by a constant.
 \end{itemize}
-The rest of the proof remains the same.
 \end{proof}

### 2018-02-16 Discussion.tex
finished edits to section 4.4

@@
-\subsection{Special Cases: Discrete Preferences and Known $p$}
+\subsection{Tighter Bounds Under Additional Assumptions: Discrete Preferences and Known $p$}
 
@@
 \begin{theorem}
+\label{rst:discrete}
 Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has an expected payment budget bounded above by 
@@
 
-\textbf{Case 2: If we know $\MinProb$ in advance.}
+We now consider an alternate assumption, that $\MinProb$ (or a strictly positive lower bound) is known.
+\begin{assumption}
+\label{a:known-p}
+(Known $\MinProb$) 
+A strictly positive lower bound on $\MinProb$ is known in advance.
+\end{assumption}
+\pfcomment{I wrote the assumption allowing a lower bound, but in the eligibility criterion we just use $\MinProb$.  We can modify the criterion.}
 
-If we know $\MinProb$ in advance, we can modify the payment-eligible criteria as follows: Denote $s_0=\min_{s=1,2,\cdots,}\{\frac{1}{\log(s_0)}\leq \frac{\MinProb}{2}\}$.
+When this assumption holds, we modify Algorithm~\ref{alg:basic-incentivizing} by modifying its payment eligibility criterion as follows.
+Let $s_0=\min_{s=1,2,\cdots,}\{\frac{1}{\log(s_0)}\leq \frac{\MinProb}{2}\}$.
 An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
 if both of the following hold:
-
 \begin{itemize}
@@
 
-The algorithm remains the same as Algorithm~\ref{alg:basic-incentivizing}. Under this new algorithm, we can prove:
+We refer to this modified version of Algorithm~\ref{alg:basic-incentivizing} as the {\it Known-$\MinProb$ Algorithm.} We prove the following result for this algortithm under Assumption~\ref{a:known-p}.
 
 \begin{theorem}
-The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
+\label{rst:known-p}
+Under Assumption~\ref{a:known-p}, the Known-$\MinProb$ Algorithm has an expected payment budget bounded above by 
 \begin{align*}
@@
 \end{align*}
-\end{theorem}
-
-\begin{proof}
-The proof is exact the same as the proof for Lemma~\ref{rst:budget} except we define $h(\ell) := 
-\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}$. The rest of the proof remains the same.
-\end{proof}
-
-\begin{lemma}  \label{lem:NumP2}
-The expected number of time steps in which
-Algorithm~\ref{alg:basic-incentivizing}
-makes any payment is at most 
-\begin{align}
-O\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
-  + \frac{\ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right). \nonumber 
-\end{align}
-\end{lemma}
-
-\begin{proof}
-The proof is exact the same as the proof for Lemma~\ref{lem:numP} except we now define $\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3})$ since $\frac{1}{\log(s+s_0)}\leq \frac{p}{2}$ is true for all $s$.
-\end{proof}
-
-\begin{theorem}
-The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
+and an expected regret bounded above by
 \begin{align}
@@
 \begin{proof}
-The proof of this Theorem is similar as Theorem~\ref{rst:regret}, except
+The proof of the expected payment bound follows Lemma~\ref{rst:budget} except we define $h(\ell) := 
+\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}$.
+
+The proof of the expected regret bound first establishes the following upper bound on the number of time steps in which a payment is made:
+\begin{align}
+O\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
+  + \frac{\ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} \right). \nonumber 
+\end{align}
+The proof of this result follows that of Lemma~\ref{lem:numP}, except it defines $\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3})$ since $\frac{1}{\log(s+s_0)}\leq \frac{p}{2}$ is true for all $s$.
+
+The proof of the expected regret bound then follows that of Theorem is similar as Theorem~\ref{rst:regret}, except:
 \begin{itemize}
-\item We can use Lemma~\ref{lem:NumP2} to bound the regret when we decide to incentivize;
+\item We use the result above to bound the regret when we incentivize;
 \item The expected length of phase $s$ is bounded by $\ARMNUM \log(s+s_0)$;
@@
 \end{itemize}
-The rest of the proof remains the same.
 \end{proof}

### 2018-02-16 algorithm.tex
addressing comments from david about stopping times and filtration notation

--- 2018-02-16 algorithm.tex
@@
 arm is at most $\delta$.
-\pfcomment{We can check through the whole paper on whether we have
-  $\AgV \sim \AgentDist$ in the subscript or just $\AgV \sim
-  \AgentDist$.  I think we have only $\AgentDist$ in the problem
-  description.}
-\dkcomment{There must be a typo in Peter's comment.}
+\pfcomment{We can check through the whole paper on whether we write
+$\AgV \sim \AgentDist$, $\AgentDist$ or $\AgV$ in the subscript, and make the use consistent.
+  Here we write $\AgV \sim \AgentDist$ while we have only $\AgentDist$ in the definition of $p$ in the problem description.}
 %The minimum probability mass of users who prefer their best arm
@@
   have measure 0.}
+
 \dkcomment{We weren't using $p(\delta)$ anywhere, so I got rid
@@
 that we prove here.}
+% We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.
 
@@
 Let $\LatePhase \geq \max (2, \frac{30 \sigma^3}{x^3})$.
-
-\dkcomment{Is it problematic that we use $\sigma$ for two things here?}
-Let $\tau$ be any stopping time that is almost surely \dkcomment{What
-  exactly do we mean by this here?} in phase $s$,
-with respect to the filtration
-$\mathcal{F}_{t} = \sigma (\Pull{1}, \ldots, \Pull{t},
-                          \PayA{1}, \ldots, \PayA{t},
-                          \ObsV{1}, \ldots, \ObsV{t})$.
+Let $\History{t}$ denote the random vector
+$(\Pull{1}, \ldots, \Pull{t}, \PayA{1}, \ldots, \PayA{t}, \ObsV{1}, \ldots, \ObsV{t})$
+and let $\tau$ be a stopping time 
+with respect to the filtration generated by $(\History{t} : t \ge 0)$.
+Assume that $\tau$ is almost surely in phase $s$,
+i.e., satisfying $\tau \in [t_s, t_{s+1})$ almost surely.
 Then, for all phases $s \geq \LatePhase$,
-with probability at least 
+with (unconditional) probability at least 
 $1- 24 \ARMNUM d \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$,
@@
   be over the entire past history, but not the current type.}
+\pfcomment{This is over the entire history, including the current type.  I tried to clarify, but maybe it needs more editing.}
 \end{lemma}
@@
 Let $\LatePhase \geq \max (2, \frac{30 \sigma^3}{x^3})$.
-
-Let $\tau$ be any stopping time that is almost surely \dkcomment{What
-  exactly do we mean by this here?} in phase $s$,
-with respect to the filtration
-$\mathcal{F}_{t} = \sigma (\Pull{1}, \ldots, \Pull{t},
-                          \PayA{1}, \ldots, \PayA{t},
-                          \ObsV{1}, \ldots, \ObsV{t})$.
+Let $\tau$ be a stopping time with respect to the filtration 
+generated by $(\History{t} : t \ge 0)$ that is almost surely in phase $s$.
 Then, for all $s \geq \LatePhase$,
-with probability (over the past history) at least 
+with (unconditional) probability (over the past history) at least 
 $1 - 24 \ARMNUM d \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$,
@@
   be over the past history, but not the current agent.}
+\pfcomment{I did the same kind of edits to this corollary as above in Lemma~\ref{lem:round-prob}.  David, can you take a look and resolve or edit?}
 an agent of type $\AgV = \AgentV{\tau}$ 

### 2018-02-16 algorithm.tex
finished draft of section 3

@@
 
-In this section, we prove that Algorithm~\ref{alg:basic-incentivizing} achieves $O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
-O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3)$ cumulative regret with $O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right)$ payment budget.
-This is stated in the following pair of theorems, which together constitute our main results.
-
-\dkcomment{Depending on how we structure Section 3, we might
-get rid of those theorems, and only consider them parts of Theorem 2
-that we prove here.}
-% We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.
-
-\begin{theorem}
-The expected payment budget for
-Algorithm~\ref{alg:basic-incentivizing} is bounded above by
-\begin{align}
-O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right). \nonumber 
-\end{align} 
-\label{rst:budget}
-\end{theorem}
-
-\begin{theorem}
-For any given $T$, the expected cumulative regret for
-Algorithm~\ref{alg:basic-incentivizing} up to time $T$ is bounded
-above by 
-\begin{align}
-O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
-O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3).
-\end{align}
-\label{rst:regret}
-\end{theorem}
+We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.
 

### 2018-02-16 introduction.tex
finished draft of section 3

@@
 quite simple: it mostly lets agents exploit arms, but incentivizes
-them to explore when arms that appear close enough to being tied are
-underexplored. It is presented in detail in Section~\ref{sec:ub}.
+them to explore when arms appear unlikely to be explored without incentives.
+It is presented in detail in Section~\ref{sec:ub}.
 The result can be smoothly extended when there some arms that are not

### 2018-02-16 result_discussion.tex
finished edits to section 4.4
finished draft of section 3

--- 2018-02-02 result_discussion.tex
@@
-\section{Problem Setup and Overview of Results}
-\dkcomment{I envision this section doing the following:
-\begin{enumerate}
-\item State the main theorem(s) formally.
-\item Discuss lower bounds or impossibility results.
-\item Discuss extensions.
-\item Discuss the justification or comparison to standard bandits.
-\item Discuss the comparison in the 2x2 square.
-\end{enumerate}
-}
+\section{Overview of Results and Discussion}
+%
+% State the main theorem(s) formally.
+%
 
-\dkcomment{For now, I am just copying over material from various other
-  parts that Bangrui/Peter wrote or I had written in earlier
-  iterations.}
+\pfcomment{I drafted this section but it feels a bit long, and may repeat itself.}  
+We will show below that our algorithm (Algorithm~\ref{alg:basic-incentivizing}, described formally below), achieves 
+$O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) + O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3)$ cumulative regret with 
+$O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right)$ payment budget.  We state this formally as two theorems, which together constitute our main results.
 
-\begin{theorem} \label{thm:main-intro}
-Under some technical assumptions, 
-there exists a policy which pays at most $O(\ARMNUM^2)$ in expectation,
-and achieves regret at most $O(\ARMNUM^2 + \log^2(T))$.
-\dkcomment{Omitting the density here.}
+\begin{theorem}
+The expected payment budget for
+Algorithm~\ref{alg:basic-incentivizing} is bounded above by
+\begin{align}
+O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp\left(2/\MinProb\right) \right). \nonumber 
+\end{align} 
+\label{rst:budget}
 \end{theorem}
 
-As we discuss in more detail in Section~\ref{sec:main-discussion},
-the reason we obtain stronger regret bounds than in the standard bandit
-setting is that the agents' heterogeneity in preferences will
-naturally lead to exploration.
+\begin{theorem}
+For any given $T$, the expected cumulative regret for
+Algorithm~\ref{alg:basic-incentivizing} up to time $T$ is bounded
+above by 
+\begin{align}
+O \left(\MAXR\cdot  N\exp\left(2/p\right)\right) +
+O\left(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3\right).
+\end{align}
+\label{rst:regret}
+\end{theorem}
 
-Here we pursue an alternate direction to our analysis of incentivizing exploration with heterogeneous preferences: we consider approximation-style results comparing achievable algorithm performance across four different problem settings, described in the table below.
+% Discuss lower bounds or impossibility results.
+We also show a lower bound on expected regret of $\Omega(\log(T))$ (Section~\ref{sec:lb}), found by studying a setting where agents choose between two arms, with one arm's attributes known and observations of the unknown arm provided for free.
+The $\log(T)$ growth in regret arises from agents with preferences that are nearly tied between the two arms, and their shrinking but strictly positive probability of incorrectly pulling the wrong arm.
 
-\begin{center}
-\begin{tabular}{ c|c|c| } 
- \hline
-     & Pulls arms directly & Needs to incentivize \\ 
-\hline
- Perfect Info on Preferences & $C11$: The ``God'' Policy & $C12$ \\ 
- Partial Info on Preferences & $C21$ & $C22$: actual algorithm \\ 
- \hline
-\end{tabular}
-\end{center}
+We remark that $p$ is bounded above by $1/N$, and thus the term $\exp(2/p)$ present in both the payment and regret bounds implies an exponential dependence on $N$.
+This exponential dependence arises from a need to continue to incentivize to ensure that nearly tied agents learn their best arms quickly, slowly decreasing the threshold on probability of myopic selection required for incentivization.
+When this threshold gets small relative to $p$, and when arms' estimates become sufficiently accurate, incentivization is no longer necessary because each agent can identify his best arm, each arm has a volume $p$ of agents for which it is best, and our threshold is small enough that this volume is enough to avoid incentivization.
+When $p$ is small, it takes a long time to decrease the threshold to this level, and we do a large amount of incentivization, causing both large payments and large regret (because the payment may prevent an agent from choosing his best arm).
 
-Columns indicate whether the principal pulls arms directly (left column) or incentivizes agents who in turn actually pull the arms.
-Rows indicate whether the principal knows the preferences of the agents (top row) or not (bottom row).
-Problem settings correspond to cells and are described by the names C11, C12, and so on.
-An optimal algorithm for problem setting C11 has the best performance possible.
+We can eliminate this $\exp(2/p)$ term with small modifications to our algorithm under either of a pair of additional assumptions that we present after our main analysis.
+In the first assumption, we suppose that $p$ is known.
+This allows us to modify our algorithm's threshold sequenceto eliminate a large amount of early incentivization, achieving
+expected regret of
+$O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
+  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} +\frac{\ARMNUM^2 d\MAXR}{p}+\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{p}\right)$
+with expected payments of 
+$O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot (\sigma L\Diam d / p)^{5/2} \right)$.
+This is stated formally below as Theorem~\ref{rst:known-p}.
 
-We wish to make two high-level points through this analysis:
+In the second assumption, we allow $p$ to be unknown, but assume that the distribution over preferences is discrete.
+This eliminates issues with nearly tied agents for large $T$, allowing us to achieve expected regret of
+$O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} \right)$ 
+  with expected payments of $O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot (\sigma L\Diam d / p)^{5/2} \right)$.
+This is stated formally below as Theorem~\ref{rst:discrete}.
 
-\begin{itemize}
-\item First, better performance is possible in setting C22 than in setting C21, in the sense we can find tight approximation guarantees relative to C11 that are better for C22 than for C21.
-This is achieved by setting up incentives in C22 that still allow agents to select arms aligned with their preferences, providing selections of arms that contain more information than in C21.
-\item Second, heterogeneity in preferences improves performance over what can be achieved in a setting with homogeneous preferences.
-This would be in the spirit of David K.'s results that heterogeneity in preference for money can be exploited to reduce the budget required.
-\end{itemize}
+% Discuss the justification or comparison to standard bandits.
+We focus on the dependence on $T$ and compare these bounds to those possible for standard bandits.  
+To recover the standard bandit setting from the one we consider, assume that preferences $\theta$ are concentrated on a single point, and that agents will pull an arm at the principal's direction without requiring payment.
+Then, the payment is $0$ and the expected regret scales as $\log(T)$ \cite[Theorem 2.1]{bubeck2012regret}.
+In contrast, our algorithm's payment is constant in $T$; 
+while regret is $O(\log(T)^3)$ in general with a lower bound of $\Omega(\log(T))$,  
+and constant in $T$ when preferences are discrete.
 
-Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
+From the viewpoint of dependence on $T$, the best performance achievable seems comparable to that in a standard multi-armed bandit problem, but when preferences our discrete  it is possible to achieve performance that surpasses a multi-armed bandit, achieving constant regret rather than $O(\log(T))$.
+(Note that our specialization of our problem to the standard bandit case used a discrete preference.)
+This may seem surprising, because our setting is one in which the principal has both less control and less information than in the standard bandit setting.
+It is possible because heterogeneity in preferences indeed provides free exploration, in which all of the arms can be pulled infinitely often without incurring regret.
+
+\pfcomment{Rather than actually placing a 2x2 square, this + the above text is my discussion of the ideas that seem worth sharing}
+While heterogeneity in preferences enables this free exploration, heterogeneity alone is not always beneficial sufficient for enabling performance improvements above what is possible in the standard bandit setting.
+Indeed, consider a version of our problem where agents are heterogeneous but modified to be more similar to the standard bandit setting by given the principal the power to pull arms directly.
+In this problem, the principal will be unable to correctly choose each agent's preferred arm even with infinite exploration of arm attributes, causing linear regret.
+
+Achieving the benefits of heterogeneous preferences also requires the prinicipal to give up direct control of the arms, providing agents the autonomy they need to express their private information about their own preferences.
+Our results show that simple arm-based incentives are sufficient overcome the apparent challenges created by this abdication of control.

### 2018-02-16 algorithm.tex
significant reorg of Section 4

--- 2018-02-16 algorithm.tex
@@
 
+Our main result is that Algorithm~\ref{alg:basic-incentivizing} achieves $O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
+O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3)$ cumulative regret with $O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right)$ payment budget.
+This is stated in the following pair of theorems.
+
+\dkcomment{Depending on how we structure Section 3, we might
+get rid of those theorems, and only consider them parts of Theorem 2
+that we prove here.}
+
+\begin{theorem}
+The expected payment budget for
+Algorithm~\ref{alg:basic-incentivizing} is bounded above by
+\begin{align}
+O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right). \nonumber 
+\end{align} 
+\label{rst:budget}
+\end{theorem}
+
+\begin{theorem}
+For any given $T$, the expected cumulative regret for
+Algorithm~\ref{alg:basic-incentivizing} up to time $T$ is bounded
+above by 
+\begin{align}
+O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
+O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3).
+\end{align}
+\label{rst:regret}
+\end{theorem}
+
 \dkcomment{I had written ``exponentially'' in a few places here, but I
@@
 To capture the probability masses of problematic agents,
-we define
+we define the quantity
 $\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
@@
 
-In this section, we prove that Algorithm~\ref{alg:basic-incentivizing} achieves $O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
-O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3)$ cumulative regret with $O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right)$ payment budget.
-This is stated in the following pair of theorems, which together constitute our main results.
-
-\dkcomment{Depending on how we structure Section 3, we might
-get rid of those theorems, and only consider them parts of Theorem 2
-that we prove here.}
-% We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.
-
-\begin{theorem}
-The expected payment budget for
-Algorithm~\ref{alg:basic-incentivizing} is bounded above by
-\begin{align}
-O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right). \nonumber 
-\end{align} 
-\label{rst:budget}
-\end{theorem}
-
-\begin{theorem}
-For any given $T$, the expected cumulative regret for
-Algorithm~\ref{alg:basic-incentivizing} up to time $T$ is bounded
-above by 
-\begin{align}
-O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
-O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3).
-\end{align}
-\label{rst:regret}
-\end{theorem}
+To formally reason about the event that the estimates of arms'
+attributes vectors are accurate enough --- or fail to be so ---
+we define the events
+$\AccE{t}{i}{j}{\epsilon} := [|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq \epsilon]$
+that attribute $j$ of arm $i$ at time $t$ is estimated to
+within accuracy $\epsilon$ or better.
+Then, 
+$\AccEU{t}{\epsilon} = \bigcap_{i,j} \AccE{t}{i}{j}{\epsilon}$
+is the event that at time $t$, all arm attribute
+estimates are accurate to within $\epsilon$ simultaneously.
+We will then show that for suitable choices of $t, x$,
+the events \AccE{t}{i}{j}{x}
+(and hence, by union bound, \AccEU{t}{\epsilon})
+have high probability,
+and that when they do, myopic agents do not make large mistakes.
 
@@
 more accurate with increasing phases $s$.
-That intuition is captured by the following lemma.
 
 \begin{lemma} \label{lem:round-prob}
-Let $x > 0$ be arbitrary.
 Recall that $\sigma$ is the standard deviation of the Gaussian noise.
-Let $\LatePhase \geq \max (2, \frac{30 \sigma^3}{x^3})$.
-Let $\History{t}$ denote the random vector
-$(\Pull{1}, \ldots, \Pull{t}, \PayA{1}, \ldots, \PayA{t}, \ObsV{1}, \ldots, \ObsV{t})$
-and let $\tau$ be a stopping time 
-with respect to the filtration generated by $(\History{t} : t \ge 0)$.
-Assume that $\tau$ is almost surely in phase $s$,
+Let \LatePhase be a phase cutoff, 
+and let $\epsilon_n, \epsilon'_n > 0$ be functions satisfying that
+$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon_n^2}{16 \sigma^2}}
+\leq \frac{n \epsilon'_n}{2 \sigma}$,
+for all $n \geq \LatePhase$.
+Let $\tau_s$ be a stopping time
+(which may depend on the entire past history)
+which is almost surely in phase $s$,
 i.e., satisfying $\tau \in [t_s, t_{s+1})$ almost surely.
-Then, for all phases $s \geq \LatePhase$,
-with (unconditional) probability at least 
-$1- 24 \ARMNUM d \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$,
-the following holds for all arms $i$ and attributes $j$
-simultaneously:
-$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$.
-\dkcomment{We should clarify what the probability is over. It seems to
-  be over the entire past history, but not the current type.}
-\pfcomment{This is over the entire history, including the current type.  I tried to clarify, but maybe it needs more editing.}
+
+Then, for any arm $i$, attribute $j$, and phase $s \geq \LatePhase$,
+we have that
+$\Prob{\AccE{\tau_s}{i}{j}{\epsilon'_s}}
+\geq 1 - 24 \exp\left(-\frac{1.8 s \epsilon_s^2}{16 \sigma^2} \right)$.
 \end{lemma}
@@
 By the assumptions of the lemma,
-the stopping time $\tau$ is such that almost surely, each arm --- and
-in particular arm $i$ --- has been pulled at least
-$s \geq \LatePhase$ times at time $\tau$.
+the stopping time $\tau_s$ is such that almost surely,
+each arm --- and in particular arm $i$ --- has been pulled at least
+$s \geq \LatePhase$ times at time $\tau_s$.
 Define $J$ to be the number of times that $i$ has been pulled at
-time $\tau$.
+time $\tau_s$.
 For any $n \geq 1$, let $k_n$ be the time step right after arm $i$ has
@@
 to be the sum of all attribute-$j$ noise components up to and
-including the \Kth{n} pull of arm $i$, renormalized to have standard deviation $1/2$.
+including the \Kth{n} pull of arm $i$,
+renormalized to have standard deviation $1/2$.
 The $S_n$ define an unbiased half-subgaussian random walk,
@@
 the stopping time $J$.
-Specifically, we set $b = \frac{x^2}{16 \sigma^2}$,
+Specifically, we set $b = \frac{\epsilon_J^2}{16 \sigma^2}$,
 and obtain that
@@
 \Prob{J < \infty \mbox{ and } S_J \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}}
-& \leq 12 \exp \left( \frac{-1.8 J x^2}{16 \sigma^2} \right).
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J \epsilon_J^2}{16 \sigma^2}}}
+& \leq 12 \exp \left( \frac{-1.8 J \epsilon_J^2}{16 \sigma^2} \right).
 \end{align*}
@@
 \Prob{J < \infty \mbox{ and } |S_J| \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}}
-& \leq 24 \exp \left( \frac{-1.8 J x^2}{16 \sigma^2} \right).
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J \epsilon_J^2}{16 \sigma^2}}}
+& \leq 24 \exp \left( \frac{-1.8 J \epsilon_J^2}{16 \sigma^2} \right).
 \end{align*}
@@
 & \Prob{S_J \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 \epsilon_J^2}{16
     \sigma^2}}}\\
 = & \Prob{J < \infty \mbox{ and } S_J \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x^2}{16
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 \epsilon_J^2}{16
     \sigma^2}}}.
@@
 
-In the high-probability case
-$|S_J| \leq
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}$,
-we first use that $\sqrt{\cdot}$ is sublinear to bound
-$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}
-\leq \sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1)} + \frac{J x}{4 \sigma}$
-(here we use the fact $\sqrt{J} \leq J$).
-Then, we will show momentarily that
-$\sqrt{0.6 J \log (\log_{1.1}(J) + 1)} \leq \frac{J x}{4 \sigma}$,
-giving us an overall upper bound of
-$|S_J| \leq \frac{J x}{2 \sigma}$.
+In the high-probability case, we now apply the assumed inequality
+between $\epsilon_J$ and $\epsilon'_J$, to obtain that
+\[
+|S_J| \; \leq \;
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J \epsilon_J^2}{16 \sigma^2}}
+\; \leq \; \frac{J \epsilon'_J}{2 \sigma}.
+\]
 
@@
 the inequality implies that
-$|\ArmE{k_J}{i}{j} - \Arm{i}{j}| \leq x$.
+$|\ArmE{k_J}{i}{j} - \Arm{i}{j}| \leq \epsilon'_J$.
 The choice of $J$ ensures that
-$\ArmE{k_J}{i}{j} = \ArmE{\tau}{i}{j}$,
+$\ArmE{k_J}{i}{j} = \ArmE{\tau_s}{i}{j}$,
 and we have thus shown that
-$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$ for all $i,j$.
-The lemma now follows by a union bound over all \ARMNUM arms and $d$
-attributes.
-
-It remains to show that
-$\sqrt{0.6 J \log (\log_{1.1}(J) + 1)} \leq \frac{J x}{4 \sigma}$.
-By squaring the statement and rearranging, it is equivalent to show that
-$\frac{J}{\log(\log_{1.1}(J)+1)} \geq \frac{9.6\sigma^2}{x^2}$.
-Because $J \geq \LatePhase \geq 2$,
-a numerical calculation and derivative test shows that
-$\frac{J}{\log(\log_{1.1}(J)+1)} \geq J^{2/3}$,
-and because $J \geq \LatePhase \geq \frac{30 \sigma^3}{x^3}$,
-we get that
-$J^{2/3} \geq \frac{9.6 \sigma^2}{x^2}$, completing the proof.
+$|\ArmE{\tau_s}{i}{j} - \Arm{i}{j}| \leq \epsilon'_s$.
 \end{extraproof}
 
-Lemma~\ref{lem:round-prob} implies that the probability of making
-large errors due to myopic play decreases exponentially in the phase
-number $s$.
+Next, we show the complementary part:
+when \AccE{t}{\epsilon} happens, no myopic agent incurs large regret.
 
-\begin{corollary} \label{cor:right-choice}
-Let $x > 0$ be arbitrary.
-Let $\LatePhase \geq \max (2, \frac{30 \sigma^3}{x^3})$.
-Let $\tau$ be a stopping time with respect to the filtration 
-generated by $(\History{t} : t \ge 0)$ that is almost surely in phase $s$.
-Then, for all $s \geq \LatePhase$,
-with (unconditional) probability (over the past history) at least 
-$1 - 24 \ARMNUM d \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$,
-\dkcomment{We should clarify what the probability is over. It seems to
-  be over the past history, but not the current agent.}
-\pfcomment{I did the same kind of edits to this corollary as above in Lemma~\ref{lem:round-prob}.  David, can you take a look and resolve or edit?}
-an agent of type $\AgV = \AgentV{\tau}$ 
-will not pull a highly suboptimal arm, i.e., an arm $i$ with 
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
-\end{corollary}
+\begin{lemma} \label{lem:right-choice}
+Let $\epsilon > 0$ be arbitrary.
+When \AccEU{t}{\epsilon} happens,
+no agent \AgV will pull a highly suboptimal arm, i.e., an arm $i$ with 
+$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d \epsilon$.
+\end{lemma}
 
 \begin{proof}
-Let $\tau$ be a (random) time.
-By Lemma~\ref{lem:round-prob},
-with probability at least
-$1 - 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16\sigma^2} \right)$,
-for all arms $i$ and attributes $j = 1, \ldots, d$ simultaneously,
-the estimated attribute $j$ for arm $i$ is close enough to the true attribute: 
-$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$.
-Condition on this high-probability event.
+By definition, when \AccEU{t}{\epsilon} happens,
+for all arms $i$ and attributes $j$,
+all arm attribute estimates are accurate to within $\epsilon$,
+in the sense that
+$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq \epsilon$.
 
-Consider any agent type $\AgV = \AgentV{\tau}$ at the (random) time
-$\tau$.
+Consider any agent type \AgV.
 Let $i \neq \Best{\AgV}$ be any arm
 with much smaller true reward than the best arm:
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
-Because each coordinate of \ArmEV{\tau}{\Best{\AgV}} and of
-\ArmEV{\tau}{i} is estimated accurately to within $x$, 
+$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d \epsilon$.
+Because each coordinate of \ArmEV{t}{\Best{\AgV}} and of
+\ArmEV{t}{i} is estimated accurately to within $\epsilon$, 
 we get that 
-$\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
-\geq - \Diam d x$
+$\AgV \cdot (\ArmEV{t}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
+\geq - \Diam d \epsilon$
 and
-$\AgV \cdot (\ArmEV{\tau}{i} - \ArmV{i}) \leq \Diam d x$.
+$\AgV \cdot (\ArmEV{t}{i} - \ArmV{i}) \leq \Diam d \epsilon$.
 Hence,
@@
 \begin{align}
-\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmEV{\tau}{i})
+\AgV \cdot (\ArmEV{t}{\Best{\AgV}} - \ArmEV{t}{i})
 & =
-\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
+\AgV \cdot (\ArmEV{t}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
 + \AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i})
-+ \AgV \cdot (\ArmV{i} - \ArmEV{\tau}{i}) \nonumber\\
-& > -\Diam d x + 2 \Diam d x - \Diam d x
++ \AgV \cdot (\ArmV{i} - \ArmEV{t}{i}) \nonumber\\
+& > -\Diam d \epsilon + 2 \Diam d \epsilon - \Diam d \epsilon
 \; = \; 0, \label{equ:choice}
 \end{align}
-which means that the agent with type \AgV will not pull arm $i$
-under the high-probability event.
+which means that the agent with type \AgV will not pull arm $i$.
 \end{proof}
@@
 
-Towards bounding the algorithm's total payment, we first bound the
+As a first step towards bound the total payment (and also regret),
+we show that for sufficiently late phases,
+under the event \AccEU{t}{\epsilon} for suitably small $\epsilon$,
+the algorithm does not offer any payments.
+
+\begin{lemma} \label{lem:no-incentives}
+Fix an arm $i$.
+Let $s \geq \exp(2/\MinProb)$, and let $\tau_s$ be the (random)
+time when arm $i$ is pulled for the \Kth{s} time.
+Under \AccEU{\tau_s}{\frac{p}{4\Diam d \TieDensity}},
+this pull of arm $i$ is not incentivized.
+\end{lemma}
+
+\begin{proof}
+By Lemma~\ref{lem:right-choice},
+under the event \AccEU{\tau_s}{\frac{\MinProb}{4\Diam d \TieDensity}},
+all agent types \AgV with
+$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}})
+> \frac{\MinProb}{2\TieDensity}$
+will pull their best arm \Best{\AgV}.
+
+By Lemma~\ref{lem:sdelta}, the measure of agents (across all arms)
+whose best and second-best arm differ in utility by less
+than $\frac{\MinProb}{2\TieDensity}$ is at most $\frac{\MinProb}{2}$.
+In particular, this bound holds for agents whose best arm is $i$.
+By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
+as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
+will myopically pull arm $i$.
+Because $1/\log(s) < \frac{\MinProb}{2}$ for
+$s \geq \exp(2/\MinProb)$, arm $i$ is not payment-eligible at time
+$\tau_s$.
+\end{proof}
+
+Towards bounding the algorithm's total payment, we now bound the
 \emph{number} of rounds in which the algorithm makes a payment by a
@@
 For later phases,
-we use that arms are payment-eligible only if their myopic pulling
-probability is less than $1/\log(s)$.
-Since at least a \MinProb fraction of agents would prefer arm $i$ if
-given accurate estimates, this would require misestimates that make a
-significant fraction of agents pull the wrong arm.
-But in later phases, such misestimates are unlikely by
-Corollary~\ref{cor:right-choice}.
+we use Lemma~\ref{lem:no-incentives},
+which rules out any incentives unless large misestimates of the arm
+locations occur, which is exponentially unlikely by 
+Lemma~\ref{lem:round-prob}.
 
@@
 $\delta = \frac{\MinProb}{2 \TieDensity}$,
-and $x = \frac{\delta}{2 \Diam d}$.
+and $\epsilon = \epsilon' = \frac{\delta}{2 \Diam d}$
+(which is independent of the phase number $s$).
 The cutoff point between early and late phases is now set to
-$\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3}, \exp(\frac{2}{\MinProb}))$.
-Consider the \Kth{s} pull of an arm $i$, for $s \geq \EvenLaterPhase$.
+$\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{\epsilon^3}, \exp(\frac{2}{\MinProb}))$.
+We will verify below that
+$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon^2}{16 \sigma^2}}
+\leq \frac{n \epsilon}{2 \sigma}$
+for all $n \geq \max(2, \frac{30 \sigma^3}{\epsilon^3})$.
+
+Fix an arm $i$, and consider the \Kth{s} pull of an arm $i$,
+for $s \geq \EvenLaterPhase$.
 If this pull occurs before phase $s$, it was definitely not incentivized.
 So we condition on the pull occurring in phase $s$,
-and let $\tau$ be the time step when this pull occurred; notice that
-this means that this must be the first pull of arm $i$ in phase $s$.
-We can now apply Corollary~\ref{cor:right-choice}
-with this choice of $x$,
-and obtain that with probability at least 
-$1 - 24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$,
-all agent types \AgV with
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}})
-> 2\Diam d x = \delta$
-will pull their best arm \Best{\AgV}.
+and let $\tau_s$ be the time step when this pull occurred;
+notice that this means that this must be the first pull of arm $i$ in
+phase $s$.
 
-By Lemma~\ref{lem:sdelta}, the \emph{total} measure of agents (across
-all arms) whose best and second-best arm differ in utility by less
-than $\delta$ is at most $\TieDensity \delta = \frac{\MinProb}{2}$.
-In particular, this bound holds for agents whose best arm is $i$.
-By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
-as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
-has arm $i$ as their preferred arm by at least $\delta$ over any other
-arm $i'$.
-In the high-probability event, all such agents would myopically pull
-the arm $i$, and as a result, in the high-probability event,
+By Lemma~\ref{lem:round-prob} (with our choice of $\epsilon = \epsilon'$),
+and a union bound over all $i,j$, we bound the probability
+$\Prob{\AccEU{\tau_s}{\epsilon}}
+\geq 1 - 24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s \epsilon^2}{16 \sigma^2} \right)$.
+And by Lemma~\ref{lem:no-incentives},
+under the event ${\mathcal E}_{\tau_s}(\epsilon)$,
 arm $i$ is not payment-eligible.
 
-Thus, for any phase $s \geq \EvenLaterPhase$,
-Algorithm~\ref{alg:basic-incentivizing} incentivizes any given arm $i$
+Thus, for any $s \geq \EvenLaterPhase$,
+the \Kth{s} pull of arm $i$ is incentivized  
 with probability at most
@@
 
+It remains to show that
+$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon^2}{16 \sigma^2}}
+\leq \frac{n \epsilon}{2 \sigma}$
+for all $n \geq \max(2, \frac{30 \sigma^3}{\epsilon^3}$.
+We first use that $\sqrt{\cdot}$ is sublinear to bound
+\[
+  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon^2}{16 \sigma^2}}
+\; \leq \; \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1)} + \frac{n \epsilon}{4 \sigma}
+\]
+(here we use the fact $\sqrt{n} \leq n$).
+Next, we show that
+$\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} \leq \frac{n \epsilon}{4 \sigma}$;
+then, adding the two terms gives the desired bound.
+
+By squaring the claimed statement and rearranging,
+it is equivalent to show that
+$\frac{n}{\log(\log_{1.1}(n)+1)} \geq \frac{9.6\sigma^2}{\epsilon^2}$.
+Because $n \geq 2$,
+a numerical calculation and derivative test shows that
+$\frac{n}{\log(\log_{1.1}(n)+1)} \geq n^{2/3}$,
+and because $n \geq \frac{30 \sigma^3}{\epsilon^3}$,
+we get that
+$n^{2/3} \geq \frac{9.6 \sigma^2}{\epsilon^2}$, completing the proof.
+
 \dkcomment{I'm leaving in all the dependencies on ``constant''
@@
 As a result, the actual analysis of the total payment is significantly more
-intricate, and hence,
+intricate;
 the proof of Theorem~\ref{rst:budget} is given in
@@
 
-To bound the regret incurred in time steps with large regret,
-we use a proof nearly identical to that of
-Lemma~\ref{lem:round-prob} and Corollary~\ref{cor:right-choice}.
-The only reason we cannot directly apply them is that in order
-to apply to arbitrary $x > 0$, we had to assume that
-$\LatePhase \geq \frac{30 \sigma^3}{x^3}$, a bound we cannot afford here.
-So here, we will choose a larger value of $x$, and in return
-will only need to assume that $T \geq 2$.
-
+We next bound the regret incurred in time steps with large regret.
 Let the random variable $t_s$ be the final time step in phase $s$,
@@
 i.e., $k > t_{s}-t_{s-1}$.
-Exactly as in the proof of Corollary~\ref{cor:right-choice},
-it is sufficient to show that with high probability,
-$|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq \frac{g(s)}{2\Diam d}$
-for all arms $i$ and attributes $j$.
+By Lemma~\ref{lem:right-choice},
+under \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}}, no agent at time $t$ will incur
+regret more than $g(s)$.
 
-The proof of this high-probability guarantee for the stopping time
-$t = \tau_s^k$ is identical to the proof of
-Lemma~\ref{lem:round-prob} with $x = \frac{g(s)}{2 \Diam d}$
-until the step where we start bounding
-$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x^2}{16 \sigma^2}}$.
-At that point in the proof, we had shown that 
-the probability of $|S_J|$ exceeding the preceding expression is at most
-\begin{align*}
-24 \exp \left( \frac{-1.8 s x^2}{16 \sigma^2} \right)
-  & = \frac{24}{T^2}.
-\end{align*}
+To bound the probability of \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}},
+we use Lemma~\ref{lem:round-prob}
+(with $\epsilon_s = \epsilon'_s = \frac{g(s)}{2 \Diam d}$
+and a stopping time of $\tau_s^k$).
+We first verify that this choice of $\epsilon_s, \epsilon'_s$
+satisfies the assumption of Lemma~\ref{lem:round-prob} for all
+$s \geq 2$,
+i.e., that
+$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon_n^2}{16 \sigma^2}}
+\leq \frac{n \epsilon_n}{2 \sigma}$
+for all $n \geq 2$.
+Substituting that
+$\epsilon_n = \frac{g(n)}{2 \Diam d} = \sqrt{\frac{32\log(T) \cdot \sigma^2}{1.8 n}}$,
+the left-hand side is
 
-Substituting $J = s$ and $x = \frac{g(s)}{2 \Diam d}$, the upper bound is
-$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{2 \log T}{1.8 J}}$.
-We claim that for $J \leq T$ and $T \geq 2$, we have
-$\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{2 \log T}{1.8 J}}
-\leq 2 \sqrt{\frac{2}{1.8} s \log(T)}$.
-Indeed, by squaring this inequality and canceling out common terms,
-the claimed inequality is equivalent to
-$\frac{50}{9} \log T \geq \log(\log_{1.1}(J) + 1)$.
-Because $J \leq T$, it is sufficient to show that
-$\frac{50}{9} \log T \geq \log(\log_{1.1}(T) + 1)$,
+\[
+  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 \log T}{1.8}}
+  \; \leq \;
+  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 n \log T}{1.8}},
+\]
+while the right-hand side is $\sqrt{\frac{8 n \log(T)}{1.8}}$.
+Squaring both sides and canceling out common terms,
+the desired inequality is equivalent to
+$\frac{50}{9} \log T \geq \log(\log_{1.1}(n) + 1)$.
+Because $n \leq T$, it is sufficient to show that
+$\frac{50}{9} \log T \geq \log(\log_{1.1}(n) + 1)$,
 which can be verified by numerical calculation for $T=2$ and a
@@
 
-With this upper bound of $|S_J| \leq 2 \sqrt{\frac{2}{1.8} s \log(T)}$,
-we can substitute the definition of $S_J$ to obtain that
-$|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq \frac{g(s)}{2\Diam d}$
-in the high-probability event.
-By a union bound over all arms $i$ and attributes $j$,
-the probability of incurring regret exceeding $g(s)$ is at most
-$\frac{24 \ARMNUM d}{T^2}$.
+Now, by Lemma~\ref{lem:round-prob} and a union bound over all arms $i$
+and attributes $j$, we get that 
+\begin{align*}
+\Prob{\AccEU{\tau_s^k}{\epsilon_s}}
+& \leq 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16 \sigma^2} \right)
+\; = \; \frac{24 \ARMNUM d}{T^2}.
+\end{align*}
 
-Using that the regret never exceeds \MAXR,
-and applying Lemma~\ref{lem:phase-length},
+In the low-probability event, we simply 
+bound the maximum regret by \MAXR.
+Now, applying Lemma~\ref{lem:phase-length},
 the total expected regret from large-regret steps is at most

### 2018-02-16 algorithm.tex

@@
 The algorithm achieving the claimed bounds of
-Theorem~\ref{thm:main-overview} is fairly simple.
+Theorems~\ref{rst:budget} and~\ref{rst:regret} is fairly simple.
 It mostly allows agents to exploit, but when an arm is sufficiently
@@
 
-Our main result is that Algorithm~\ref{alg:basic-incentivizing} achieves $O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
-O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3)$ cumulative regret with $O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right)$ payment budget.
-This is stated in the following pair of theorems.
-
-\dkcomment{Depending on how we structure Section 3, we might
-get rid of those theorems, and only consider them parts of Theorem 2
-that we prove here.}
-
-\begin{theorem}
-The expected payment budget for
-Algorithm~\ref{alg:basic-incentivizing} is bounded above by
-\begin{align}
-O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right). \nonumber 
-\end{align} 
-\label{rst:budget}
-\end{theorem}
-
-\begin{theorem}
-For any given $T$, the expected cumulative regret for
-Algorithm~\ref{alg:basic-incentivizing} up to time $T$ is bounded
-above by 
-\begin{align}
-O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
-O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3).
-\end{align}
-\label{rst:regret}
-\end{theorem}
-
-\dkcomment{I had written ``exponentially'' in a few places here, but I
-  don't think that was correct. The error only decreases as
-  $\sqrt{s}$, while the probability of deviating beyond that error
-  decreases exponentially.}
-The high-level idea of the proof of Theorem~\ref{thm:main-overview}
+The high-level idea in the proofs of our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret},
 is the following.
@@
 and that when they do, myopic agents do not make large mistakes.
+
+We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.
 

### 2018-02-16 algorithm.tex
folded 4.5 into the intro to section 4

@@
 The payment \Pay{t}{i} may appear unnecessarily high.
-Indeed, we show in Section~\ref{sec:pi} that it suffices to
-incentivize only a $1/\log(s)$ fraction of the agents.
-\dkcomment{Given that we don't prove anything there, is ``show'' the
-  right word?}
-Here, we focus on the higher payments for simplicity of analysis.
+Indeed, it suffices to
+incentivize only a $1/\log(s)$ fraction of the agents,
+and our bounds also hold for an alternate version of our algorithm that 
+offers payment
+$\Pay{t}{i} = \min \Set{c \geq 0}{%
+\Prob[\AgV \sim \AgentDist]{c + \AgV \cdot \ArmEV{t}{i} \geq \max_{i'\ne i} \AgV \cdot \ArmEV{t}{i'}} \ge 1/\log(s)}$.
+However, we focus on the higher payments for simplicity of presentation.
 

### 2018-02-16 algorithm.tex
edited payment proof to use new lemmas

@@
 we define the events
-$\AccE{t}{i}{j}{\epsilon} := [|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq \epsilon]$
+$\AccE{t}{i}{j}{x} := [|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq x]$
 that attribute $j$ of arm $i$ at time $t$ is estimated to
-within accuracy $\epsilon$ or better.
+within accuracy $x$ or better.
 Then, 
-$\AccEU{t}{\epsilon} = \bigcap_{i,j} \AccE{t}{i}{j}{\epsilon}$
+$\AccEU{t}{x} = \bigcap_{i,j} \AccE{t}{i}{j}{x}$
 is the event that at time $t$, all arm attribute
-estimates are accurate to within $\epsilon$ simultaneously.
+estimates are accurate to within $x$ simultaneously.
 We will then show that for suitable choices of $t, x$,
 the events \AccE{t}{i}{j}{x}
-(and hence, by union bound, \AccEU{t}{\epsilon})
+(and hence, by union bound, \AccEU{t}{x})
 have high probability,
@@
 Let \LatePhase be a phase cutoff, 
-and let $\epsilon_n, \epsilon'_n > 0$ be functions satisfying that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon_n^2}{16 \sigma^2}}
-\leq \frac{n \epsilon'_n}{2 \sigma}$,
+and let $x_n, x'_n > 0$ be functions satisfying that
+$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
+\leq \frac{n x'_n}{2 \sigma}$,
 for all $n \geq \LatePhase$.
@@
 we have that
-$\Prob{\AccE{\tau_s}{i}{j}{\epsilon'_s}}
-\geq 1 - 24 \exp\left(-\frac{1.8 s \epsilon_s^2}{16 \sigma^2} \right)$.
+$\Prob{\AccE{\tau_s}{i}{j}{x'_s}}
+\geq 1 - 24 \exp\left(-\frac{1.8 s x_s^2}{16 \sigma^2} \right)$.
 \end{lemma}
@@
 the stopping time $J$.
-Specifically, we set $b = \frac{\epsilon_J^2}{16 \sigma^2}$,
+Specifically, we set $b = \frac{x_J^2}{16 \sigma^2}$,
 and obtain that
@@
 \Prob{J < \infty \mbox{ and } S_J \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J \epsilon_J^2}{16 \sigma^2}}}
-& \leq 12 \exp \left( \frac{-1.8 J \epsilon_J^2}{16 \sigma^2} \right).
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x_J^2}{16 \sigma^2}}}
+& \leq 12 \exp \left( \frac{-1.8 J x_J^2}{16 \sigma^2} \right).
 \end{align*}
@@
 \Prob{J < \infty \mbox{ and } |S_J| \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J \epsilon_J^2}{16 \sigma^2}}}
-& \leq 24 \exp \left( \frac{-1.8 J \epsilon_J^2}{16 \sigma^2} \right).
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x_J^2}{16 \sigma^2}}}
+& \leq 24 \exp \left( \frac{-1.8 J x_J^2}{16 \sigma^2} \right).
 \end{align*}
@@
 & \Prob{S_J \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 \epsilon_J^2}{16
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x_J^2}{16
     \sigma^2}}}\\
 = & \Prob{J < \infty \mbox{ and } S_J \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 \epsilon_J^2}{16
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x_J^2}{16
     \sigma^2}}}.
@@
 In the high-probability case, we now apply the assumed inequality
-between $\epsilon_J$ and $\epsilon'_J$, to obtain that
+between $x_J$ and $x'_J$, to obtain that
 \[
 |S_J| \; \leq \;
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J \epsilon_J^2}{16 \sigma^2}}
-\; \leq \; \frac{J \epsilon'_J}{2 \sigma}.
+\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x_J^2}{16 \sigma^2}}
+\; \leq \; \frac{J x'_J}{2 \sigma}.
 \]
@@
 the inequality implies that
-$|\ArmE{k_J}{i}{j} - \Arm{i}{j}| \leq \epsilon'_J$.
+$|\ArmE{k_J}{i}{j} - \Arm{i}{j}| \leq x'_J$.
 The choice of $J$ ensures that
@@
 and we have thus shown that
-$|\ArmE{\tau_s}{i}{j} - \Arm{i}{j}| \leq \epsilon'_s$.
+$|\ArmE{\tau_s}{i}{j} - \Arm{i}{j}| \leq x'_s$.
 \end{extraproof}
@@
 Next, we show the complementary part:
-when \AccE{t}{\epsilon} happens, no myopic agent incurs large regret.
+when \AccE{t}{x} happens, no myopic agent incurs large regret.
 
 \begin{lemma} \label{lem:right-choice}
-Let $\epsilon > 0$ be arbitrary.
-When \AccEU{t}{\epsilon} happens,
+Let $x > 0$ be arbitrary.
+When \AccEU{t}{x} happens,
 no agent \AgV will pull a highly suboptimal arm, i.e., an arm $i$ with 
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d \epsilon$.
+$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
 \end{lemma}
@@
 \begin{proof}
-By definition, when \AccEU{t}{\epsilon} happens,
+By definition, when \AccEU{t}{x} happens,
 for all arms $i$ and attributes $j$,
-all arm attribute estimates are accurate to within $\epsilon$,
+all arm attribute estimates are accurate to within $x$,
 in the sense that
-$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq \epsilon$.
+$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$.
 
@@
 with much smaller true reward than the best arm:
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d \epsilon$.
+$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
 Because each coordinate of \ArmEV{t}{\Best{\AgV}} and of
-\ArmEV{t}{i} is estimated accurately to within $\epsilon$, 
+\ArmEV{t}{i} is estimated accurately to within $x$, 
 we get that 
 $\AgV \cdot (\ArmEV{t}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
-\geq - \Diam d \epsilon$
+\geq - \Diam d x$
 and
-$\AgV \cdot (\ArmEV{t}{i} - \ArmV{i}) \leq \Diam d \epsilon$.
+$\AgV \cdot (\ArmEV{t}{i} - \ArmV{i}) \leq \Diam d x$.
 Hence,
@@
 + \AgV \cdot (\ArmV{i} - \ArmEV{t}{i}) \nonumber\\
-& > -\Diam d \epsilon + 2 \Diam d \epsilon - \Diam d \epsilon
+& > -\Diam d x + 2 \Diam d x - \Diam d x
 \; = \; 0, \label{equ:choice}
@@
 we show that for sufficiently late phases,
-under the event \AccEU{t}{\epsilon} for suitably small $\epsilon$,
+under the event \AccEU{t}{x} for suitably small $x$,
 the algorithm does not offer any payments.
@@
 $\delta = \frac{\MinProb}{2 \TieDensity}$,
-and $\epsilon = \epsilon' = \frac{\delta}{2 \Diam d}$
+and $x = x' = \frac{\delta}{2 \Diam d}$
 (which is independent of the phase number $s$).
 The cutoff point between early and late phases is now set to
-$\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{\epsilon^3}, \exp(\frac{2}{\MinProb}))$.
+$\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3}, \exp(\frac{2}{\MinProb}))$.
 We will verify below that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon^2}{16 \sigma^2}}
-\leq \frac{n \epsilon}{2 \sigma}$
-for all $n \geq \max(2, \frac{30 \sigma^3}{\epsilon^3})$.
+$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
+\leq \frac{n x}{2 \sigma}$
+for all $n \geq \max(2, \frac{30 \sigma^3}{x^3})$.
 
@@
 
-By Lemma~\ref{lem:round-prob} (with our choice of $\epsilon = \epsilon'$),
+By Lemma~\ref{lem:round-prob} (with our choice of $x = x'$),
 and a union bound over all $i,j$, we bound the probability
-$\Prob{\AccEU{\tau_s}{\epsilon}}
-\geq 1 - 24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s \epsilon^2}{16 \sigma^2} \right)$.
+$\Prob{\AccEU{\tau_s}{x}}
+\geq 1 - 24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$.
 And by Lemma~\ref{lem:no-incentives},
-under the event ${\mathcal E}_{\tau_s}(\epsilon)$,
+under the event ${\mathcal E}_{\tau_s}(x)$,
 arm $i$ is not payment-eligible.
@@
 It remains to show that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon^2}{16 \sigma^2}}
-\leq \frac{n \epsilon}{2 \sigma}$
-for all $n \geq \max(2, \frac{30 \sigma^3}{\epsilon^3}$.
+$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
+\leq \frac{n x}{2 \sigma}$
+for all $n \geq \max(2, \frac{30 \sigma^3}{x^3}$.
 We first use that $\sqrt{\cdot}$ is sublinear to bound
 \[
-  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon^2}{16 \sigma^2}}
-\; \leq \; \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1)} + \frac{n \epsilon}{4 \sigma}
+  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
+\; \leq \; \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1)} + \frac{n x}{4 \sigma}
 \]
@@
 Next, we show that
-$\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} \leq \frac{n \epsilon}{4 \sigma}$;
+$\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} \leq \frac{n x}{4 \sigma}$;
 then, adding the two terms gives the desired bound.
@@
 it is equivalent to show that
-$\frac{n}{\log(\log_{1.1}(n)+1)} \geq \frac{9.6\sigma^2}{\epsilon^2}$.
+$\frac{n}{\log(\log_{1.1}(n)+1)} \geq \frac{9.6\sigma^2}{x^2}$.
 Because $n \geq 2$,
@@
 $\frac{n}{\log(\log_{1.1}(n)+1)} \geq n^{2/3}$,
-and because $n \geq \frac{30 \sigma^3}{\epsilon^3}$,
+and because $n \geq \frac{30 \sigma^3}{x^3}$,
 we get that
-$n^{2/3} \geq \frac{9.6 \sigma^2}{\epsilon^2}$, completing the proof.
+$n^{2/3} \geq \frac{9.6 \sigma^2}{x^2}$, completing the proof.
 
@@
 we use Lemma~\ref{lem:round-prob}
-(with $\epsilon_s = \epsilon'_s = \frac{g(s)}{2 \Diam d}$
+(with $x_s = x'_s = \frac{g(s)}{2 \Diam d}$
 and a stopping time of $\tau_s^k$).
-We first verify that this choice of $\epsilon_s, \epsilon'_s$
+We first verify that this choice of $x_s, x'_s$
 satisfies the assumption of Lemma~\ref{lem:round-prob} for all
@@
 i.e., that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n \epsilon_n^2}{16 \sigma^2}}
-\leq \frac{n \epsilon_n}{2 \sigma}$
+$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
+\leq \frac{n x_n}{2 \sigma}$
 for all $n \geq 2$.
 Substituting that
-$\epsilon_n = \frac{g(n)}{2 \Diam d} = \sqrt{\frac{32\log(T) \cdot \sigma^2}{1.8 n}}$,
+$x_n = \frac{g(n)}{2 \Diam d} = \sqrt{\frac{32\log(T) \cdot \sigma^2}{1.8 n}}$,
 the left-hand side is
@@
 \begin{align*}
-\Prob{\AccEU{\tau_s^k}{\epsilon_s}}
+\Prob{\AccEU{\tau_s^k}{x_s}}
 & \leq 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16 \sigma^2} \right)

### 2018-02-16 payment-proof.tex
edited payment proof to use new lemmas

@@
 \begin{proof}
-The proof idea is quite similar to the proof of
-Lemma~\ref{lem:round-prob};
-however, the specific form of the envelopes necessitates some subtle
-changes in the specific forms of the bounds used.
 For \SP to be in \Env{\ell}, by definition,
@@
 
+Define $x_s := \frac{4 \sigma (\ell-1)}{s^{1/2}}$ and
+$x'_s := g(s, \ell-1) = \frac{12 \sigma (\ell-1)}{s^{2/5}}$.
+
 Recall that $\NumPull{t}{i}(\SP) \geq s(t,\SP)$ is the number of times
 that arm $i$ has been pulled by time $t$ under \SP.
-We define the scaled estimation error
-$S_{i,j}(t) := \frac{\NumPull{t}{i} \cdot \Err{t}{i}{j}}{2\sigma}$.
-The advantage of $S_{i,j}(t)$ is that it is 
-a summation of $1/2$-Gaussian random variables, 
-so we will be able to apply Lemma~\ref{lem:ACI-inequality}.
-First notice that we can express the desired probability as follows:
-
-\begin{align*}
-\Prob{|\Err{t}{i}{j}| \geq g(s(t,\SP), \ell-1)}
-& = \Prob{S_{i,j}(t) \geq \frac{6\NumPull{t}{i}(\ell-1)}{s(t,\SP)^{2/5}}}\\
-& \leq \; \Prob{S_{i,j}(t) \geq 6\NumPull{t}{i}^{3/5}(\ell-1)}. 
-\end{align*}
-
-We will show below that
-$5 n^{3/5} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}$
-for all $n \geq 1$.
-Applying this inequality and sublinearity of $\sqrt{\cdot}$,
-we obtain that
-
-\begin{align*}
-6 \NumPull{t}{i}^{3/5}(\ell-1)
-& \geq 5 \NumPull{t}{i}^{3/5} + \NumPull{t}{i}^{3/5}(\ell-1)  \\
-& \geq \sqrt{0.6 \NumPull{t}{i} \log(\log_{1.1}(\NumPull{t}{i})+1)}
-     + \sqrt{(\ell-1)^2 \NumPull{t}{i}}  \\
-& \geq \sqrt{0.6\NumPull{t}{i}\log(\log_{1.1}(\NumPull{t}{i})+1)+(\ell-1)^2 \NumPull{t}{i}}
-\; =: \; h(\NumPull{t}{i}).
-\end{align*}
-
 Let the random stopping time $\tau_{i,j}$ be the first value of
 \NumPull{t}{i} (i.e., the first pull of arm $i$) such that 
-$S_{i,j}(\tau_{i,j}) > h(\NumPull{t}{i})$.
+the estimation error of attribute $j$ of arm $i$ exceeds
+$g(\NumPull{t}{i}, \ell-1)$.
 $\tau_{i,j} = \infty$ means that the estimation error never exceeds 
-$h(\NumPull{t}{i})$.
-We apply Lemma~\ref{lem:ACI-inequality}
-to $S_{i,j}(t)$, with a stopping time of $\tau_{i,j}$ and
-with $b = (\ell-1)^2$.
-We obtain that the probability that $\tau_{i,j} < \infty$ and 
-$S_{i,j}(\tau_{i,j}) > h(\tau_{i,j})$ is at most
-$12 \e^{-1.8 b}$.
-By definition of $\tau_{i,j}$, the event is the same as simply
-$\tau_{i,j} < \infty$.
-Applying the lemma again to $-S_{i,j}(\tau_{i,j})$,
-and taking a union bound over both cases,
-gives us that the probability that there is \emph{any} time $t$ with
-$|S_{i,j}(\NumPull{t}{i})| > h (\NumPull{t}{i})$
-is at most $24 \e^{-1.8 b(n)}$.
-Hence, the probability that the error at \emph{any} time $t$ exceeds
-$g(s(t,\SP), \ell-1)$ is bounded by 
-\begin{align*}
-\Prob{|\Err{t}{i}{j}| \geq g(s(t,\SP), \ell-1)}
-& \leq 24 \e^{-1.8(\ell-1)^2}.
-\end{align*}
-Now, taking a union bound over all arms $i$ and
-coordinates $j$ completes the proof.
-
-It remains to show that
-$5 n^{3/5} \geq \sqrt{0.6n \log(\log_{1.1}(n)+1)}$
+$g(\NumPull{t}{i}, \ell-1)$.
+We next verify that $x_s, x'_s$ as we defined them satisfy the 
+assumption 
+\[
+  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
+  \; \leq \; \frac{n x'_n}{2 \sigma}
+\]
+of Lemma~\ref{lem:round-prob}, for all $n \geq 1$.
+First, we show that
+$\sqrt{0.6n \log(\log_{1.1}(n)+1)} \leq 5 n^{3/5}$
 for all $n \geq 1$.
@@
 $25 n^{1/5} \geq \log(\log_{1.1}(n)+1)$.
-We will show the stronger statement that
+Indeed, a stronger statement holds, namely, that
 $25 n^{1/5} \geq \log_{1.1}(n)+1$.  
@@
 where it is positive. 
+Using this inequality and subadditivity of $\sqrt{\cdot}$, we can bound
+
+\[
+  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
+\; \leq \;
+  5 n^{3/5} + \frac{\sqrt{n} x_n}{4 \sigma}
+\; = \; 
+  5 n^{3/5} + (\ell-1)
+  \; \leq \; \frac{n x'_n}{2 \sigma}.
+\]
+
+\dkcomment{Unless I made a calculation mistake, we could replace a 12
+  with a 10.}
+
+Applying Lemma~\ref{lem:round-prob} to $\tau_{i,j}$,
+we conclude that the probability that the error in coordinate $j$ of
+arm $i$ exceeds $x'_s = g(s,\ell-1)$ at time $\tau_{i,j}$
+(and hence at any time, by definition of $\tau_{i,j}$)
+is at most
+$24 \exp\left(-\frac{1.8 s x_s^2}{16 \sigma^2} \right)
+\; = \; 24 \exp(-1.8 (\ell-1)^2)$.
+Now, taking a union bound over all arms $i$ and
+coordinates $j$ completes the proof.
 \end{proof}
@@
 Fix a sample path $\SP \in \Env{\ell}$.
-Consider a phase $s > h(\ell)$.
-
-By definition of \Env{\ell}, the coordinate-wise estimation errors at
-times $t$ in phase $s$ are
-$|\Arm{i}{j} - \ArmE{t}{i}{j}| \leq g(s,\ell)$.
-In particular, all agent typs \AgV whose preference for their best arm
-is sufficiently clear
-($\AgV \cdot \ArmV{\Best{\AgV}} - \AgV \cdot \ArmV{\Second{\AgV}}
-> 2\Diam d g(s,\ell)$) will pull their best arm.
-
-By Lemma~\ref{lem:sdelta}, the \emph{total} measure of agents (across
-all arms) whose best and second-best arm differ in utility by at most
-$2\Diam d \cdot g(s,\ell)$ is at most $2L \Diam d \cdot g(s,\ell)$.
-Substituting the definition of $g$, because 
-$s > h(\ell) \geq \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}$,
-the total measure of these agents is bounded by $\MinProb/2$.
-
-By Assumption~\ref{A3}, at least a \MinProb fraction of agents have
-$i$ as their best arm, so even with estimation errors, at least
-$\MinProb - \MinProb/2 = \MinProb/2$ fraction will still prefer to
-pull arm $i$.
-
-Because $s > h(\ell) \geq \exp(\frac{2}{\MinProb})$, 
-we get that $1/\log(s) \leq \MinProb/2$, so in phase $s$,
-the algorithm will not incentivize any arms whose pulling probability
-is more than $\MinProb/2$, which is all arms.
-So no payments will be made in phase $s$.
+Consider a phase $s > h(\ell)$ and a time $t$ in phase $s$.
+Because $\SP \in \Env{\ell}$, in particular, all estimation errors are
+bounded at time $t$, in the sense that the event \AccEU{t}{g(s,\ell)}
+happens.
+Because $s \geq h(\ell)$, we get that
+$g(s,\ell) \leq \frac{\MinProb}{4 \Diam d \TieDensity}$
+as well as $s \geq \exp(2/\MinProb)$.
+Therefore, we can apply Lemma~\ref{lem:no-incentives} and conclude
+that the pull at time $t$ was not incentivized.
 \end{proof}

### 2018-02-16 Discussion.tex
finished pass through stronger assumptions

@@
-\subsection{Tighter Bounds Under Additional Assumptions: Discrete Preferences and Known $p$}
+\subsection{Tighter Bounds Under Additional Assumptions}
+%: Discrete Preferences and Known \MinProb}
 
-The proofs of Theorem~\ref{rst:budget} and Theorem~\ref{rst:regret} incur exponential payment and regret in the initial phases because the threshold required for incentivization $1/\log(s)$ decreases slowly.
+The proofs of Theorem~\ref{rst:budget} and Theorem~\ref{rst:regret} incur exponential (in \ARMNUM) payment and regret in the initial phases because the threshold required for incentivization $1/\log(s)$ decreases slowly.
 This slow decrease is needed to bound the regret in the later phases when the concentration inequality kicks in as in Equation~(\ref{equ:small_regret_bound}).
-In this section, we discuss two problem settings where we can modify our algorithm slightly and provide new bounds that remove this exponential dependence.
+In this section, we discuss two restrictions on the problem setting under which  we can modify the algorithm slightly and provide stronger bounds, avoiding this exponential dependence.
 Both problem settings are special cases of the more general problem setting previously considered.
 
-We first discuss an assumption that holds when $\theta$ follows a finite discrete distribution.
-\begin{assumption}
+\subsubsection{Discrete Preferences}
+Discrete preferences by agents are captured by the following assumption (which states that the agents who are close to tied between two arms have measure 0):
+
+\begin{assumption}[Discrete Preferences]
 \label{a:discrete}
-(Discrete Preferences) 
-$\exists \delta_0>0$ such that $F_{i,j}(\delta_0)=0$ for all $i,j$.
+There is a positive $\delta_0$ such that
+$F_{i,j} (\delta_0) = 0$ for all $i,j$.
 \end{assumption}
 
-When Assumption~\ref{a:discrete} holds, we modify our algorithm to use a new payment-eligibility criterion: an arm $i$ is \emph{payment-eligible} at time $t$ in phase $s$ when both of the following are true:
+When Assumption~\ref{a:discrete} holds, we restrict the payment-eligibility criterion by only incentivizing arms with much smaller probability to be pulled: an arm $i$ is \emph{payment-eligible} at time $t$ in phase $s$ when both of the following are true:
 \begin{itemize}
-\item $i$ has been pulled at most%
-\footnote{in fact: exactly, since the algorithm entered phase $s$}
+\item $i$ has been pulled at most
 $s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
-\item Based on the current estimates \ArmEV{t}{i'} of all arms'
-attribute vectors, the probability of pulling arm $i$ is less than $1/s$. Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
-  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
-be the probability that arm $i$ will be pulled
-by the next (random) agent based on the current estimates. 
-Then, the second criterion for payment-eligibility is that
-$\PullProb{t}{i} < 1/s$.
+\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors, the probability of pulling arm $i$ is less than $1/s$ (compared to $1/\log(s)$ in the general algorithm).
 \end{itemize}
 
-We refer to this modified version of Algorithm~\ref{alg:basic-incentivizing} as the {\it Discrete-Preference Algorithm.} We prove the following result for this algortithm under Assumption~\ref{a:discrete}.
-
-\pfcomment{I collapsed these results together into a single theorem, and consolidated the proofs.  I tweaked some wording in the proofs, but I didn't check them in detail.}
+We refer to this modified version of Algorithm~\ref{alg:basic-incentivizing} as the \emph{Discrete-Preference Algorithm.}
+We outline a proof of the following result for this algortithm under Assumption~\ref{a:discrete}.
 
@@
 \label{rst:discrete}
-Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has an expected payment budget bounded above by 
+Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment budget bounded above by 
 \begin{align*}
-O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{p^{5/2}} \right). 
+O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
 \end{align*}
-and an expected regret bounded above by 
+and expected regret bounded above by 
 \begin{align}
@@
   + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
   \right)} \right).  \nonumber
@@
 
-The proof of the expected regret bound first uses a lemma bounding the expectedt number of time steps in which a payment is made by 
+To prove the bound on the expected regret, one can first prove tightened versions of Lemmas~\ref{lem:no-incentives} and \ref{lem:numP},
+which replace the $\exp(2/\MinProb)$ term with simply $2/\MinProb$.
+In return, the length of phase $s$ is now bounded only be $\ARMNUM s$ instead of $\ARMNUM \log(s)$.
+Substituting these changes into the proof of Theorem~\ref{rst:regret}, we obtain the claimed bounds.
+\end{proof}
+
+% bound first uses a lemma bounding the expected number of time steps in which a payment is made by 
+% \begin{align}
+% O\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
+%   + \frac{\ARMNUM^2 d}{1 - \exp \left(
+%     \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+%   \right)} \right). \nonumber 
+% \end{align}
+% The proof follows that of Lemma~\ref{lem:numP}, except that it defines $\EvenLaterPhase = \max (2, \frac{30 \sigma^3}{x^3}, \frac{2}{\MinProb})$.
+
+% The proof of the expected regret bound then follows the proof of Theorem~\ref{rst:regret}, with these modifications:
+% \begin{itemize}
+% \item We use the lemma stated above to bound the regret on pulls that incentivize;
+% \item The expected length of phase $s$ is bounded by $\ARMNUM s$;
+% \item The regret in Equation~\ref{equ:small_regret_bound} can now be bounded by a constant.
+% \end{itemize}
+
+\subsubsection{Known \MinProb}
+An alternative useful assumption is that \MinProb (or a strictly positive lower bound on \MinProb) is known.
+
+\begin{assumption}[Known $\MinProb$]
+\label{a:known-p}
+A strictly positive lower bound on \MinProb is known in advance.
+\end{assumption}
+
+When this assumption holds, we choose a different modification in the definition of payment eligibility.
+Let $s_0 = \exp(2/\MinProb)$.
+An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
+if both of the following hold:
+\begin{itemize}
+\item $i$ has been pulled at most
+$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
+\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s+s_0)$.
+\end{itemize}
+
+This, knowledge of \MinProb allows the algorithm to incentivize significantly fewer arm pulls.
+We refer to this modified version of Algorithm~\ref{alg:basic-incentivizing} as the \emph{Known-\MinProb Algorithm.}
+We outline a proof of the following result for this algortithm under Assumption~\ref{a:known-p}.
+
+\begin{theorem}
+\label{rst:known-p}
+Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has an expected payment budget bounded above by 
+\begin{align*}
+O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
+\end{align*}
+and an expected regret bounded above by
+\begin{align*}
+O \left(\frac{\MAXR \ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
+  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} +\frac{\ARMNUM^2 d\MAXR}{\MinProb}+\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
+\end{align*}
+\end{theorem}
+
+\begin{proof}
+  The proof of the expected payment bound follows Lemma~\ref{rst:budget} except for defining
+  $h(\ell) := \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}$
+(without including the $\exp(2/\MinProb)$ term).
+
+The proof of the expected regret bound first establishes tightened versions of Lemmas~\ref{lem:no-incentives} and \ref{lem:numP},
+proving the following upper bound on the number of time steps in which a payment is made:
 \begin{align}
@@
 \end{align}
-The proof follows that of Lemma~\ref{lem:numP}, except that it defines $\EvenLaterPhase = \max (2, \frac{30 \sigma^3}{x^3}, \frac{2}{p})$.
+The proof of this result follows that of Lemma~\ref{lem:numP}, but the less aggressive incentivization allows us to define $\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3})$ since $\frac{1}{\log(s+s_0)} \leq \frac{\MinProb}{2}$ is true for all $s$.
 
-The proof of the expected regret bound then follows the proof of Theorem~\ref{rst:regret}, with these modifications:
-\begin{itemize}
-\item We use the lemma stated above to bound the regret on pulls that incentivize;
-\item The expected length of phase $s$ is bounded by $\ARMNUM s$;
-\item The regret in Equation~\ref{equ:small_regret_bound} can now be bounded by a constant.
-\end{itemize}
+Using this tighter bound on the number of incentiziations, and the fact that phases now last at most $\ARMNUM \log(s+s_0)$ steps in expectation, we can bound the regret in Equation~\ref{equ:small_regret_bound} by
+%$71.11 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1)\log(T+s_0)$
+$O\left(\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right)$.
 \end{proof}
-
-We now consider an alternate assumption, that $\MinProb$ (or a strictly positive lower bound) is known.
-\begin{assumption}
-\label{a:known-p}
-(Known $\MinProb$) 
-A strictly positive lower bound on $\MinProb$ is known in advance.
-\end{assumption}
-\pfcomment{I wrote the assumption allowing a lower bound, but in the eligibility criterion we just use $\MinProb$.  We can modify the criterion.}
-
-When this assumption holds, we modify Algorithm~\ref{alg:basic-incentivizing} by modifying its payment eligibility criterion as follows.
-Let $s_0=\min_{s=1,2,\cdots,}\{\frac{1}{\log(s_0)}\leq \frac{\MinProb}{2}\}$.
-An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
-if both of the following hold:
-\begin{itemize}
-\item $i$ has been pulled at most%
-\footnote{in fact: exactly, since the algorithm entered phase $s$}
-$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
-\item Based on the current estimates \ArmEV{t}{i'} of all arms'
-attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s+s_0)$. Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
-  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
-be the probability that arm $i$ will be pulled
-by the next (random) agent based on the current estimates. 
-Then, the second criterion for payment-eligibility is that
-$\PullProb{t}{i} < 1/\log(s+s_0)$.
-\end{itemize}
-
-We refer to this modified version of Algorithm~\ref{alg:basic-incentivizing} as the {\it Known-$\MinProb$ Algorithm.} We prove the following result for this algortithm under Assumption~\ref{a:known-p}.
-
-\begin{theorem}
-\label{rst:known-p}
-Under Assumption~\ref{a:known-p}, the Known-$\MinProb$ Algorithm has an expected payment budget bounded above by 
-\begin{align*}
-O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{p^{5/2}} \right). 
-\end{align*}
-and an expected regret bounded above by
-\begin{align}
-O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
-  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} +\frac{\ARMNUM^2 d\MAXR}{p}+\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{p}\right).  \nonumber
-\end{align}
-\end{theorem}
-
-\begin{proof}
-The proof of the expected payment bound follows Lemma~\ref{rst:budget} except we define $h(\ell) := 
-\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}$.
-
-The proof of the expected regret bound first establishes the following upper bound on the number of time steps in which a payment is made:
-\begin{align}
-O\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
-  + \frac{\ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right). \nonumber 
-\end{align}
-The proof of this result follows that of Lemma~\ref{lem:numP}, except it defines $\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3})$ since $\frac{1}{\log(s+s_0)}\leq \frac{p}{2}$ is true for all $s$.
-
-The proof of the expected regret bound then follows that of Theorem is similar as Theorem~\ref{rst:regret}, except:
-\begin{itemize}
-\item We use the result above to bound the regret when we incentivize;
-\item The expected length of phase $s$ is bounded by $\ARMNUM \log(s+s_0)$;
-\item With the same choice of $g(s)$, the regret in Equation~\ref{equ:small_regret_bound} can now be bounded by $71.11 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1)\log(T+s_0)=O(\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{p})$.
-\end{itemize}
-\end{proof}

### 2018-02-16 introduction.tex
some edits in introduction

@@
 Many websites and apps are designed to facilitate joint discovery,
-sharing, and recommendations of content\pfdelete{by large numbers of users}.
-Such sites include news, photo, \pfedit{and} video sharing sites,
+sharing, and recommendations of content.
+Such sites include news, photo, and video sharing sites,
 sites to review restaurants, hotels, or travel experiences,
@@
 and citizen science projects
-(such as eBird \citep{sullivan2009ebird} or Galaxy Zoo).
-\dkcomment{Insert citations.}
-By learning from the experiences of other users, individuals can \pfdelete{make
-better choices to }improve their own experience.
+(such as eBird \citep{sullivan2009ebird,xue-ebird} or Galaxy Zoo \citep{lintott-galaxy-zoo}).
+By learning from the experiences of other users, individuals can
+improve their own experience \citep{schmit2017human}.
 
@@
 of times, and therefore have little incentive for exploration.
-A particular clean model is obtained when each user interacts with the
+A particularly clean model is obtained when each user interacts with the
 site only once, and hence has no intrinsic utility for exploration. 
@@
 
-\pfdelete{In order }To effect an outcome \pfdelete{which is }close to societally optimal,
+To effect an outcome close to societally optimal,
 it is necessary to provide exploration incentives to the individual users.
@@
 a reward for pulling particular arms.
-We follow the model of \citet{frazier2014incentivizing,han2015incentivizing}
+We follow the model of \citet{frazier2014incentivizing} and
+\citet{han2015incentivizing} 
 and consider a multi-armed bandit model in which the principal can
@@
 political, aesthetic, practical, etc.
-\pfedit{
 Indeed, the websites and mobile apps most widely used for joint discovery,
@@
 videos, travel experiences), and not items which have a universally
-agreed-on best order. \pfcomment{can we think of items with agreement?}
+agreed-on best order.
 This is perhaps because regimes with heterogeneous preferences are the
@@
 
+\dkcomment{Rearranging the next two paragraphs a bit.}
 Heterogeneity presents both a challenge and an opportunity.
-On the one hand, it hides critical information about an agent's preferences
-from the principal.  This presents the principal with a path to social
-optimality that requires giving up control, allowing the agent to reveal these
-preferences through action and not obscuring them with incentives.  However,
-the principal cannot give up control completely, and must use these incentives
-to force agents to explore against their preferences, for the greater good.
-Thus, heterogeneity presents a challenge.
+On the one hand, \dkedit{unobserved heterogeneity} hides critical
+information about an agent's preferences from the principal.
+On the other hand, heterogeneity also presents an opportunity, through the
+possibility of ``free exploration.''
+Even when left unincentivized, agents will
+play a variety of arms, revealing information about these arms' attributes.
+This stands in sharp contrast to the case of homogeneous preferences, where 
+unincentivized agents will herd onto a single apparently best arm, and providing
+essentially any exploration at all requires incentives.
 
-On the other hand, heterogeneity also presents an opportunity, through the
-possibilty of ``free exploration''.  Even when left unincentivized, agents will
-play a variety of arms, revealing information about these arms' attributes.
-This stands in sharp constrast to the case of homogeneous preferences, where 
-unincentized agents will hard onto a single apparently best arm, and providing
-essentially any exploration at all requires incentives.
-}
+In order to take advantage of unobserved heterogeneity, the principal
+has to give up some control, allowing the agent to reveal his
+preferences through action, rather than obscuring them with incentives.
+However, the principal cannot give up control completely,
+and must use incentives to force agents to explore against their
+preferences, for the greater good.
 
@@
 impact of user heterogeneity on our ability to achieve high social utility with
-low incentive payments, and on the best approaches for doing so.  We wish to
-understand whether incentivizing exploration with heterogeneous preferences  is
-``harder'' or ``easier'' than with homogenous ones, and to understand how 
-exploration strategies that do well in the heterogeneous preference setting
-differ from those in the homogenous one.
-
-\pfdelete{\emph{Our goal is to explore the impact of user heterogeneity
-on the tradeoff between societal utility and the principal's payments.}
-Heterogeneity in a bandit also offers a new perspective on bandit problems.
-}
+low incentive payments, and on the best approaches for doing so.
+We wish to understand whether incentivizing exploration with
+heterogeneous preferences  is ``harder'' or ``easier'' than with
+homogeneous ones,
+and to understand how exploration strategies that do well in the
+heterogeneous preference setting differ from those in the homogeneous one.
 
@@
 Arms and users (or \emph{agents}) are characterized by payoff-relevant
-\emph{attribute} (or \emph{feature}) vectors,
-both drawn from known distributions.
+\emph{attribute} (or \emph{feature}) vectors.
+\dkedit{Arms' attributes are a priori unknown, and
+  agents' attributes are drawn from a known distribution.}
 An agent's reward from pulling an arm is the inner product of their
@@
 agents small, while incurring only small total payments.
-Our main theorm can be stated informally as follows:
+Our main theorem can be stated informally as follows:
 
@@
 vanishes (in a sense made precise in Section~\ref{sec:ub}),
+\dkcomment{Make sure we cite the right section.}
 there is a policy that achieves constant
@@
 If near-ties have non-zero density,
-then the regret is bounded by $O(C + C'' \log^2(T))$,
+then the regret is bounded by $O(C + C'' \log^3(T))$,
 while the expected payment is still bounded by $C'$;
 here, $C''$ depends on the ``tie density.''
+\dkcomment{Make sure we get the right dependence on $T$.}
 \end{theorem}
@@
 quite simple: it mostly lets agents exploit arms, but incentivizes
-them to explore when arms appear unlikely to be explored without incentives.
+them to explore when arms appear unlikely to be pulled without incentives.
 It is presented in detail in Section~\ref{sec:ub}.
-The result can be smoothly extended when there some arms that are not
-preferred by any agents.
+
+\dkdelete{The result can be smoothly extended when there some arms that are not
+preferred by any agents.}
+\dkcomment{Deleted the sentence about smooth extension of the result
+  --- if we keep it, it goes in the conclusions section, I think.}

### 2018-02-17 abstract.tex
drafted an abstract

We consider the problem of incentivized exploration with heterogeneous agents.
In this problem, bandit arms provide vector-valued outcomes equal to an unknown
arm-specific attribute vector perturbed by independent normally distributed
noise.  Agents arrive sequentially and choose arms to pull based on their own
private and heterogeneous linear utility function over attributes and estimates
of the arms' attribute vectors derived from observations of other agents' past
pulls.  Agents are myopic and selfish and thus would choose the arm with
maximal estimated utility, except for an incentive payment that a principal may
offer to encourage agents to explore underplayed arms.  The principle seeks to
minimize the expected cumulative regret incurred by agents relative to their
best arms, while also making a small expected cumulative payment.  We propose
an algorithm that incentivizes arms played infrequently in the
past whose probability of being played in the next round would be small
without incentives.  Under the assumption that each arm is preferred by at
least a fraction $p>0$ of agents, we show this algorithm achieves expected
cumulative regret of $O(N\exp(2/p) + N \log(T)^3)$ using expected cumulative
payments of $O(N^2 \exp(2/p))$.  If $p$ is known or the distribution over agent
preferences is discrete, the term $\exp(2/p)$ can be eliminated.  In these
cases, the bound on payment improves to $O(N^2 / p^{5/2})$.  The bound on
regret improves to $O(N/p^4 + N^2/p^2 + N \log(T)^3 / p)$ for known $p$ and to
$O(N/p^4 + N^2/p^2)$ for discrete preference distributions.  Regret and
payments that are both constant in $T$ for discrete preferences stands
in contrast to the $\log(T)$ dependence on regret in standard multi-armed bandit
problems, and arises because heterogeneity in agent preferences allows
exploitation of arms to also explore fully.

### 2018-02-17 colt.tex
changes to COLT
finished edits up to payment
almost finished regret proof
added a new discussion tex file
halfway through editing payment proof
cleaned up and tightened technical lemmas
addressed some comments
pass through regret proof
Separating out a file for the abstract
drafted an abstract

@@
 \documentclass[twoside,11pt]{article}
-\usepackage{jmlr2e}
+\usepackage[anon]{jmlr2e}
 
@@
 \usepackage[]{algorithm}
-\usepackage[]{algorithmic}
+\usepackage[noend]{algorithmic}
 
-\usepackage[utf8]{inputenc} % allow utf-8 input
+%\usepackage[utf8]{inputenc} % allow utf-8 input
 %\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{xr} 
+%\usepackage{microtype}      % microtypography
+%\usepackage{xr}
+
 \usepackage{url}            % simple URL typesetting
 \usepackage{amsfonts}       % blackboard math symbols
+\usepackage{amsmath}
 \usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
 %\usepackage{amsthm}
-\usepackage{comment}
-\usepackage{subcaption}
-\usepackage{xcolor}
-\usepackage{amsmath}
-\usepackage{float}
+%\usepackage{mathtools}
+
+%\usepackage{comment}
+%\usepackage{subcaption}
+%\usepackage{xcolor}
+%\usepackage{float}
+\usepackage{bm}
 \usepackage{bbm}
+\usepackage{ifthen}
+\usepackage{xspace}
+
+\usepackage{color-edits}
+% home-made package by David that provides the following macros:
+% 1. \pfedit{}: prints argument in blue
+% 2. \pfcomment{}: prints argument in blue in [Peter: #1]
+% 3. \pfmargincomment{}: prints argument in blue in the margin as
+% [Peter: #1]
+% 4. \pfdelete{}: instead of text, marks a note in the margin in blue that says
+% "Peter deleted here"
+% Package has option [suppress], which gets rid of all color and all comments
+% and [showdeletions], which shows deleted text in color/strikeout.
+\addauthor[Peter]{pf}{blue}
+\addauthor[Bangrui]{bc}{green}
+\addauthor[David]{dk}{red}
+
+%\newcommand{\bccomment}[1]{{\color{blue}BC: #1}}
+%\newcommand{\pfcomment}[1]{{\color{blue}PF: #1}}
+
+\providecommand{\SET}[1]{\ensuremath{\{ #1 \}}\xspace}
+\providecommand{\Abs}[1]{\ensuremath{| #1 |}\xspace}
+\providecommand{\Set}[2]{\ensuremath{\SET{#1 \mid #2}}\xspace}
+
+\providecommand{\PROB}{\ensuremath{{\rm Prob}}\xspace}
+\providecommand{\Prob}[2][]{\ensuremath{%
+\ifthenelse{\equal{#1}{}}{\PROB\left[#2\right]}{\PROB_{#1}\left[#2\right]}}\xspace}
+\providecommand{\ProbC}[3][]{\Prob[#1]{#2\;|\;#3}}
+\providecommand{\Expect}[2][]{\ensuremath{%
+\ifthenelse{\equal{#1}{}}{\mathbb{E}}{\mathbb{E}_{#1}}%
+\left[#2\right]}\xspace}
+\providecommand{\ExpectC}[3][]{\Expect[#1]{#2\;|\;#3}}
+
+\newcommand{\e}{\mathrm{e}}
+\newcommand{\dd}{\mathrm{d}}
+\newcommand{\quarter}{\ensuremath{\frac{1}{4}}\xspace}
+
+\providecommand{\Kth}[1]{\ensuremath{{#1}^{\rm th}}}
+
+\def\QED{{\phantom{x}} \hfill \ensuremath{\rule{1.3ex}{1.3ex}}}
+
+\newcommand{\extraproof}[1]{\rm \trivlist \item[\hskip \labelsep{\bf Proof of #1. }]}
+\def\endextraproof{\QED \endtrivlist}
+
+\def\emptyproof{\rm \trivlist \item[\hskip \labelsep{\bf Proof. }]}
+\def\endemptyproof{\endtrivlist}
+
+\newenvironment{rtheorem}[3][]{
+
+\bigskip
+
+\noindent \ifthenelse{\equal{#1}{}}{\bf #2 #3}{\bf #2 #3 (#1)}
+\begin{it}
+}{\end{it}}
 
 \newcommand{\argmax}{\mathop{\mathrm{argmax}}}
-\usepackage{mathtools}
-
 \newcommand\floor[1]{\lfloor#1\rfloor}
 \newcommand\ceil[1]{\lceil#1\rceil}
-
-\newcommand{\bccomment}[1]{{\color{blue}BC: #1}}
-\newcommand{\pfcomment}[1]{{\color{blue}PF: #1}}
+\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
+\newcommand{\R}{\mathbb{R}} % real numbers
 
@@
 
-\newcommand{\dataset}{{\cal D}}
-\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}
+\input{localdefs}
 
@@
 
-\title{Incentivizing Exploration with Heterogeneous Utilities}
+\title{Incentivizing Exploration by Heterogeneous Users}
+% {Incentivizing Exploration with Heterogeneous Utilities}
 
-\author{\name Bangrui Chen \email bc496@cornell.edu \\
-\name Peter I.\ Frazier \email pf98@cornell.edu \\
-\addr Operations Research and Information Engineering\\
-Cornell University\\
-New York, NY 14850, USA
-\AND
-\name David Kempe \email david.m.kempe@gmail.com  \\
-\addr Department of Computer Science\\
-University of Southern California\\
-Los Angeles, CA 90089, USA}
+%\author{\name Bangrui Chen \email bc496@cornell.edu \\
+%\name Peter I.\ Frazier \email pf98@cornell.edu \\
+%\addr Operations Research and Information Engineering\\
+%Cornell University\\
+%New York, NY 14850, USA
+%\AND
+%\name David Kempe \email david.m.kempe@gmail.com  \\
+%\addr Department of Computer Science\\
+%University of Southern California\\
+%Los Angeles, CA 90089, USA}
 
@@
 \begin{abstract}
-sdafsd
+\input{abstract.tex}
 \end{abstract}
@@
 \begin{keywords}
-Incentivizing Exploration
+Incentivizing Exploration, Multi-Armed Bandits
 \end{keywords}
 
-\input{introduction.tex}
+\input{introduction}
 
-\input{problem_setting.tex}
+\input{problem_setting}
 
-\input{algorithm.tex}
+\input{result_discussion}
 
-\input{lower_bound.tex}
+\input{algorithm}
 
-\input{conclusion.tex}
+\input{Discussion}
+
+\input{lower_bound}
+
+\input{conclusion}
 
@@
 
-\input{appendix.tex}
+\input{payment-proof}
 
-\vskip 0.2in
+% \input{technical-proofs}
 

### 2018-02-17 introduction.tex

@@
 driving.)
-The principal can exploit this advantage and make recommendations to
-the individual agents which it is in their best interest to follow.
+The principal can exploit her%
+\footnote{We use male pronouns to refer to users and female pronouns
+  to refer to the principal.}
+advantage and make recommendations to the individual agents which it
+is in their best interest to follow.
 \citet{frazier2014incentivizing} and 
@@
 information about an agent's preferences from the principal.
-On the other hand, heterogeneity also presents an opportunity, through the
-possibility of ``free exploration.''
+On the other hand, heterogeneity also presents her an opportunity,
+through the possibility of ``free exploration.''
 Even when left unincentivized, agents will
 play a variety of arms, revealing information about these arms' attributes.
-This stands in sharp contrast to the case of homogeneous preferences, where 
-unincentivized agents will herd onto a single apparently best arm, and providing
-essentially any exploration at all requires incentives.
+This stands in sharp contrast to the case of homogeneous preferences,
+where unincentivized agents will herd onto a single apparently best arm;
+thus, effecting essentially any exploration at all requires incentives.
 
-In order to take advantage of unobserved heterogeneity, the principal
-has to give up some control, allowing the agent to reveal his
-preferences through action, rather than obscuring them with incentives.
-However, the principal cannot give up control completely,
+In order to take advantage of unobserved heterogeneity,
+the principal has to give up some control, allowing the agent to
+reveal his preferences through action, rather than obscuring them with
+incentives.
+However, she cannot give up control completely,
 and must use incentives to force agents to explore against their
@@
 With these challenges and opportunities in mind, our goal is to understand the
-impact of user heterogeneity on our ability to achieve high social utility with
-low incentive payments, and on the best approaches for doing so.
+impact of user heterogeneity on the principal's ability to achieve
+high social utility with low incentive payments,
+and on the best approaches for doing so.
 We wish to understand whether incentivizing exploration with
@@
   agents' attributes are drawn from a known distribution.}
-An agent's reward from pulling an arm is the inner product of their
-vectors (plus noise).
+An agent's reward from pulling an arm is the inner product of his
+vector with the arm's vector (plus noise).
 When an arm is pulled, a noisy version of its attribute vector is

### 2018-02-17 algorithm.tex
cleaned up the technical section

@@
 \label{sec:ub}
-
-\dkcomment{Here and earlier, we are using a lot of displayed
-  equations. We could inline some/many of them to save space.}
-
 The algorithm achieving the claimed bounds of
@@
 
-When multiple arms are payment-eligible, the algorithm picks one
-uniformly at random to incentivize.
-\dkcomment{Is uniform randomness used anywhere? Does arbitrary work?}
+When multiple arms are payment-eligible, the algorithm picks one arbitarily to incentivize.
 When the algorithm decides to incentivize an arm $i$,
@@
 \FOR{time steps $t = 1, 2, 3, \ldots$}
-\IF{$\NumPull{t}{i} \geq \dkedit{s+1}$ for all arms $i$}
+\IF{$\NumPull{t}{i} \geq s+1$ for all arms $i$}
 \STATE Increment the phase $s = s + 1$.
@@
 \IF{there is a payment-eligible arm $i$}
-\STATE Let $i$ be a uniformly random payment-eligible arm.
-\dkcomment{Is uniform randomness used anywhere?}
+\STATE Let $i$ be an arbitary payment-eligible arm.
 \STATE Offer payment
@@
 arm is at most $\delta$.
-\pfcomment{We can check through the whole paper on whether we write
-$\AgV \sim \AgentDist$, $\AgentDist$ or $\AgV$ in the subscript, and make the use consistent.
-  Here we write $\AgV \sim \AgentDist$ while we have only $\AgentDist$ in the definition of $p$ in the problem description.}
-%The minimum probability mass of users who prefer their best arm
-%sufficiently strongly over their second-best arm is denoted by
-%$\ClearPref{\delta} = \min_{i}
-%\Prob[\AgV \sim \AgentDist]{\Best{\AgV}=i,%
-%\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > \delta}$.
-%Notice that \AlmostTied{\delta} (being a measure of problematic
-%agents) is defined as a sum over all arms,
-%while  \ClearPref{\delta} (being a measure of non-problematic agents)
-%is defined as a minimum over arms.
-%Also notice that $\ClearPref{0} = \MinProb$.
 \dkcomment{We should stress somewhere that we assume that actual ties
   have measure 0.}
-
-\dkcomment{We weren't using $p(\delta)$ anywhere, so I got rid
-  of it.}
 
@@
 Next, we show the complementary part:
-when \AccE{t}{x} happens, no myopic agent incurs large regret.
+when \AccEU{t}{x} happens, no myopic agent incurs large regret.
 
@@
 in the sense that
-$|\ArmE{\tau}{i}{j} - \Arm{i}{j}| \leq x$.
+$|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq x$.
 
@@
 
-\dkcomment{I'm leaving in all the dependencies on ``constant''
-  parameters for now. We can decide later which ones to absorb into
-  big-$O$.}
 \end{proof}

### 2018-02-17 payment-proof.tex
cleaned up the technical section

@@
 \]
-
-\dkcomment{Unless I made a calculation mistake, we could replace a 12
-  with a 10.}
-
 Applying Lemma~\ref{lem:round-prob} to $\tau_{i,j}$,

### 2018-02-17 algorithm.tex
edits in problem definition, carried through to proofs

@@
 
-We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.
+%We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.
 
@@
 
-We begin by showing that under our assumptions, the measure of
-problematic arms cannot be too large.
+% We begin by showing that under our assumptions, the measure of
+% problematic arms cannot be too large.
 
-\begin{lemma} \label{lem:sdelta}
-$\AlmostTied{\delta} \leq \TieDensity \cdot \delta$ for all $\delta$.
-\end{lemma}
+% \begin{lemma} \label{lem:sdelta}
+% $\AlmostTied{\delta} \leq \TieDensity \cdot \delta$ for all $\delta$.
+% \end{lemma}
 
-\begin{emptyproof}
-Using the upper bound from Assumption~\ref{A1}, we can bound
+% \begin{emptyproof}
+% Using the upper bound from Assumption~\ref{A1}, we can bound
 
-\begin{align*}
-\AlmostTied{\delta}
-& = \sum_{i,i'} \ProbC{\AgV \cdot (\ArmV{i} - \ArmV{i'}) \leq \delta}%
-    {\AgV \in \FirstTwo{i}{i'}}
-  \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}\\
-& \leq \sum_{i,i'} \TieDensity \cdot \delta
-    \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}
-\; = \; \TieDensity \cdot \delta. \QED
-\end{align*}
-\end{emptyproof}
+% \begin{align*}
+% \AlmostTied{\delta}
+% & = \sum_{i,i'} \ProbC{\AgV \cdot (\ArmV{i} - \ArmV{i'}) \leq \delta}%
+%     {\AgV \in \FirstTwo{i}{i'}}
+%   \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}\\
+% & \leq \sum_{i,i'} \TieDensity \cdot \delta
+%     \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}
+% \; = \; \TieDensity \cdot \delta. \QED
+% \end{align*}
+% \end{emptyproof}
 
-We next bound the length of any phase, which will be useful to bound
+We begin by bounding the length of any phase, which will be useful to bound
 the cumulative regret of the early rounds
@@
 
-By Lemma~\ref{lem:sdelta}, the measure of agents (across all arms)
+By Assmption~\ref{A1},
+%Lemma~\ref{lem:sdelta},
+the measure of agents (across all arms)
 whose best and second-best arm differ in utility by less
@@
 $\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(s)$.
-By Lemma~\ref{lem:sdelta}, the total measure of such agents
+By Assumption~\ref{A1},
+%Lemma~\ref{lem:sdelta},
+the total measure of such agents
 is $\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$,

### 2018-02-17 abstract.tex
another abstract edit
abstract edit, added keyword
fixed a typo in abstract

@@
 maximal estimated utility, except for an incentive payment that a principal may
-offer to encourage agents to explore underplayed arms.  The principle seeks to
+offer to encourage agents to explore underplayed arms.  The principal seeks to
 minimize the expected cumulative regret incurred by agents relative to their
@@
 cases, the bound on payment improves to $O(N^2 / p^{5/2})$.  The bound on
-regret improves to $O(N/p^4 + N^2/p^2 + N \log(T)^3 / p)$ for known $p$ and to
-$O(N/p^4 + N^2/p^2)$ for discrete preference distributions.  Regret and
+regret improves to $O(N/p^4 + N \log(T)^3 / p)$ for known $p$ and to
+$O(N/p^4)$ for discrete preference distributions.  Regret and
 payments that are both constant in $T$ for discrete preferences stands
@@
 exploitation of arms to also explore fully.
+Succinctly, heterogeneity provides free exploration.

### 2018-02-17 abstract.tex
I thought I found a typo, but I was wrong

@@
 pulls.  Agents are myopic and selfish and thus would choose the arm with
-maximal estimated utility, except for an incentive payment that a principal may
+maximal estimated utility, except for an incentive payment that a principle may
 offer to encourage agents to explore underplayed arms.  The principal seeks to

### 2018-02-17 conclusion.tex
added a conclusion

@@
 \section{Conclusion}
-In this paper, we study the incentivizing exploration problem with heterogeneous user preferences, which generalize the problem setting studied by \cite{frazier2014incentivizing} and \cite{han2015incentivizing}.
-We propose a simple policy that mostly exploits and occasionally incentivizing exploration, which can achieve $O(N^2+M(\log(T))^2)$ cumulative expected regret with $O(N^2)$ payment budget.
+In this paper, we study the problem of incentivizing exploration with heterogeneous user preferences.
+We propose an algorithm for making incentive payments that achieves  expected cumulative regret of $O(N\exp(2/p) + N \log(T)^3)$ using expected cumulative payments of $O(N^2 \exp(2/p))$.
+It is possible to improve this bound on payments to $O(N^2 / p^{5/2})$ when $p$ is known or the preference distribution is discrete, with the bound on regret improving to $O(N/p^4 + N \log(T)^3 / p)$ in the former case and to $O(N/p^4)$ in the latter.
+
+Other questions are raised by this work.
+First, we conjecture that it is possible to eliminate the $\exp(2/p)$ term in our bounds by beginning our threshold at a level that becomes smaller with larger $N$, obtaining a bound with an exponential dependence on $pN$.
+Since $p \le 1/N$, the latter term would scale better with $N$.
+Second, we conjecture that our analysis can be extended to non-normal or correlated noise using alternate concentration inequalities. 
+Third, we wish to develop algorithms that do not require all arms to be preferred by a strictly positive fraction of agents.
+We imagine an alternate algorithm that only incentivizes an arm if its estimated attribute vector is close enough to a Pareto frontier.
+Regret will be $\Omega(\log(T)$ when at least one arm falls below the frontier, as we no longer have free exploration of all arms.  
+We plan to explore these and other questions in future research.

### 2018-02-17 lower_bound.tex

--- 2018-02-16 lower_bound.tex
@@
 
-We saw in Corollary~\ref{cor:constant-regret} that \bccomment{David, could you put the right reference here?}
+We saw in Theorem~\ref{rst:discrete} that 
 when agent preferences for their best arm are sufficiently clear,

### 2018-02-17 problem_setting.tex

--- 2018-02-06 problem_setting.tex
@@
 
-We consider a MAB setting with \ARMNUM arms.
+We consider a multi-armed bandit setting with \ARMNUM arms.
 Arm payoffs are determined by $d$ \emph{attributes} or \emph{features};
 hence, arms can be identified with vectors $\ArmV{i} \in \R^d$.
-The \ArmV{i} are (adversarially) fixed, but unknown to the agents
+The \ArmV{i} are (adversarially) fixed, and unknown to the agents
 or the principal.
 Whenever arm $i$ is pulled, its current utility-relevant features are
-determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero
-Gaussian%
+determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero independent Gaussian%
 \footnote{For simplicity of notation, we assume that the variance
-  $\sigma^2$ is uniform across time steps. This is not material for
-  the analysis.}
+  $\sigma^2$ is uniform across time steps.
+  This is not material for the analysis.
+\dkedit{In fact, the analysis extends straightforwardly to any
+  mean-zero sub-Gaussian noise.} \dkcomment{Is this true?}}
 noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.
-\dkcomment{Clarify if we can handle more general noise.}
 Here, $I_d$ denotes the $d \times d$ identity matrix.
@@
 At each time $t$, a new user (or \emph{agent}) arrives,
-whose feature vector (which we also call his%
-\footnote{We use male pronouns to refer to users and female pronouns
-  to refer to the principal. 
-  \dkcomment{Feel free to switch if you prefer it the other way.}}
-\emph{type}) $\AgentV{t} \in \R^d$ is drawn from a known distribution
-\AgentDist.
-Depending on context, we will identify a agents with their arrival time
+whose feature vector (which we also call his \emph{type})
+$\AgentV{t} \in \R^d$ is drawn from a known distribution \AgentDist.
+Depending on context, we will identify agents with their arrival time
 $t$ or their type \AgentV{t}.
@@
 and his reward is $\AgentV{t} \cdot \ObsV{t}$,
-i.e., agents have linear preferences.
+i.e., agents have linear preferences.%
+\footnote{\dkedit{Some of our results generalize to other forms of
+    agent rewards.}}
 
@@
 Then, user $t$ will pull an\footnote{We assume that ties are broken in
-  favor of an arm with largest payment \Pay{t}{i}; this assumption is
-  only for notational convenience, and can of course be avoided by
-  raising payments infinitesimally.} arm $i$ maximizing
-$\argmax_i (\Pay{t}{i} + \AgentV{t} \cdot \ArmEV{t}{i})$.
+  favor of an arm with largest payment \Pay{t}{i}.}
+% ; this assumption is
+%   only for notational convenience, and can of course be avoided by
+%   raising payments infinitesimally.
+%   \pfcomment{In the finite preference setting this is clear, but it's a little bit delicate when there are continuum preferences, since regardless of the payment we offer there may always be support within our preference distribution for a $\theta$ that causes a tie.
+In this continuum setting it should instead be possible to perturb infinitessimally so that we avoid ties with probability 1.}
+% }
+arm $i$ maximizing $\argmax_i (\Pay{t}{i} + \AgentV{t} \cdot \ArmEV{t}{i})$.
 The principal cannot observe \AgentV{t},
@@
 regret
-$\Expect[\POLICY]{\TotalRegret{T}}$ the cumulative expected payment
-$\Expect[\POLICY]{\TotalPay{T}}$ are small.
+$\Expect{\TotalRegret{T}}$ the cumulative expected payment
+$\Expect{\TotalPay{T}}$ are small.
+\dkcomment{Deleted the \POLICY subscript for the expectation, as the
+  expectation is also over the entire random history.}
 
@@
 denote the (indices of) the best and second-best arms for an agent
-with attribute vector \AgV;
-\dkdelete{breaking ties uniformly at random}.
-\dkcomment{What would it mean to break ties at random in a
-  definition?}
+with attribute vector \AgV,
+\dkedit{breaking ties arbitrarily (but consistently)}.
 
-\dkcomment{Do we need this definition here?}
-We call time $t_{n}=\min_{t}\{\forall i, \NumPull{t}{i} \geq n\}$ the
-\emph{starting point of the $n^{th}$ round}.
-We call the set of times $[t_{n}, t_{n+1})$ the
-\emph{$n^{th}$ round}.
-
-\dkdelete{This behavior may be recovered if agents are Bayesian and
-  share a common non-informative prior distribution that is constant
-  over $\mathbb{R}^m$ and know $\sigma^2$.  In this case, the
-  posterior distribution on $u_{i}$ at time $t$ is multivariate normal
-  with mean $u_{i,t}$, and the expected value of $\theta_t \cdot u_i$
-  under this posterior conditioned on $\theta_t$ is $\theta_t \cdot
-  u_{i,t}$ (see Equation 2.13 in Section 2.5, \cite{Ge04}).
-  Alternatively, one may simply take our assumption that agents use
-  the average as their estimate of an attribute value directly without
-  such a Bayesian justification.}
-\dkcomment{I wonder what's the best way to discuss this.}
+% \dkdelete{This behavior may be recovered if agents are Bayesian and
+%   share a common non-informative prior distribution that is constant
+%   over $\mathbb{R}^m$ and know $\sigma^2$.  In this case, the
+%   posterior distribution on $u_{i}$ at time $t$ is multivariate normal
+%   with mean $u_{i,t}$, and the expected value of $\theta_t \cdot u_i$
+%   under this posterior conditioned on $\theta_t$ is $\theta_t \cdot
+%   u_{i,t}$ (see Equation 2.13 in Section 2.5, \cite{Ge04}).
+%   Alternatively, one may simply take our assumption that agents use
+%   the average as their estimate of an attribute value directly without
+%   such a Bayesian justification.}
+% \dkcomment{I wonder what's the best way to discuss this.}
 
@@
 
-Let $\FirstTwo{i}{i'} = \Set{\AgV}{\Best{\AgV} = i, \Second{\AgV} = i'}$
-be the set of agent attribute vectors whose best arm is $i$ and
-second-best arm is $i'$.
-Let $F_{i,i'}$ be the marginal cumulative density function
+%Let $\FirstTwo{i}{i'} = \Set{\AgV}{\Best{\AgV} = i, \Second{\AgV} = i'}$
+%be the set of agent attribute vectors whose best arm is $i$ and
+%second-best arm is $i'$.
+% Let $F_{i,i'}$ be the cumulative density function
+% (or cumulative mass function if $\AgentDist(\cdot)$ is a discrete distribution)
+% $F_{i,i'}(z) = \Prob[\AgV \sim \AgentDist]{\AgV \in \FirstTwo{i}{i'}
+%   \mbox{ and } (\ArmV{i}-\ArmV{i'}) \cdot \AgV \leq z}$
+% of $(\ArmV{i}-\ArmV{i'}) \cdot \AgV$,
+% on $\AgV \in \Omega_{i,i^{'}}$.
+% In words, $F_{i,i'}$ is the distribution of the \emph{strength} of the
+% preference of a random agent for arm $i$ over arm $i'$
+
+% $\Best{\AgV} \in \argmax_i \AgV \cdot \ArmV{i}$
+% and
+% $ \Second{\AgV} \in \argmax_{i \neq \Best{\AgV}} \AgV \cdot \ArmV{i}$
+
+\dkedit{Let \AlmostTied{z} be the cumulative density function
 (or cumulative mass function if $\AgentDist(\cdot)$ is a discrete distribution)
-of $(\ArmV{i}-\ArmV{i'}) \cdot \AgV$,
-conditioned on $\AgV \in \Omega_{i,i^{'}}$.
-In words, $F_{i,i'}$ is the distribution of the \emph{strength} of the
-preference of a random agent for arm $i$ over arm $i'$, given that
-$i$ and $i'$ are the agent's first and second choices.
+$\AlmostTied{z} = \Prob[\AgV \sim \AgentDist]{%
+  (\ArmV{\Best{\AgV}}-\ArmV{\Second{\AgV}}) \cdot \AgV \leq z}$.
+In words, \AlmostTied{z} is the CDF of the \emph{strength} of the
+preference of a random agent for his best arm over his second-best arm.}
 
@@
 Near-ties have vanishing probability; 
-that is, there exists a constant \TieDensity such that
-for all pairs $i,i'$ of arms and all $z \in \R^+$,
-we have $F_{i,i'}(z) \leq \TieDensity \cdot z$.
+that is, there exists a constant \TieDensity such that for all $z \in \R^+$,
+%for all pairs $i,i'$ of arms and 
+$\AlmostTied{z} \leq \TieDensity \cdot z$.
 \end{assumption}
+
+\dkedit{\paragraph{Role of parameters:}
+Our problem setting is characterized by a fairly large number of
+parameters.
+Of these, we consider \ARMNUM, $\MinProb \leq 1/\ARMNUM$ and $T$ to be
+the key parameters, while $\sigma, \Diam, d, \TieDensity$ should be
+considered constant.
+We will keep track of these constants throughout most of our proofs,
+but report final results in terms of only the three key parameters
+(except where we illustrate a specific point).}
+
+\dkcomment{Stuff to discussion in conclusions:
+\begin{enumerate}
+\item Arms that are noone's best.
+\item Other utilities besides inner products.
+\item Other noise distributions.
+\item Better bounds.
+\end{enumerate}
+}

### 2018-02-17 Discussion-Proof.tex
moved some proofs to the appendix

--- 2018-02-16 Discussion.tex
@@
-\subsection{Tighter Bounds Under Additional Assumptions}
-%: Discrete Preferences and Known \MinProb}
-
-The proofs of Theorem~\ref{rst:budget} and Theorem~\ref{rst:regret} incur exponential (in \ARMNUM) payment and regret in the initial phases because the threshold required for incentivization $1/\log(s)$ decreases slowly.
-This slow decrease is needed to bound the regret in the later phases when the concentration inequality kicks in as in Equation~(\ref{equ:small_regret_bound}).
-In this section, we discuss two restrictions on the problem setting under which  we can modify the algorithm slightly and provide stronger bounds, avoiding this exponential dependence.
-Both problem settings are special cases of the more general problem setting previously considered.
-
-\subsubsection{Discrete Preferences}
-Discrete preferences by agents are captured by the following assumption (which states that the agents who are close to tied between two arms have measure 0):
-
-\begin{assumption}[Discrete Preferences]
-\label{a:discrete}
-There is a positive $\delta_0$ such that
-$F_{i,j} (\delta_0) = 0$ for all $i,j$.
-\end{assumption}
-
-When Assumption~\ref{a:discrete} holds, we restrict the payment-eligibility criterion by only incentivizing arms with much smaller probability to be pulled: an arm $i$ is \emph{payment-eligible} at time $t$ in phase $s$ when both of the following are true:
-\begin{itemize}
-\item $i$ has been pulled at most
-$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
-\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors, the probability of pulling arm $i$ is less than $1/s$ (compared to $1/\log(s)$ in the general algorithm).
-\end{itemize}
-
-We refer to this modified version of Algorithm~\ref{alg:basic-incentivizing} as the \emph{Discrete-Preference Algorithm.}
-We outline a proof of the following result for this algortithm under Assumption~\ref{a:discrete}.
-
-\begin{theorem}
-\label{rst:discrete}
-Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment budget bounded above by 
-\begin{align*}
-O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
-\end{align*}
-and expected regret bounded above by 
-\begin{align}
-O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
-  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right).  \nonumber
-\end{align}
-\end{theorem}
+\section{Proof of Theorem~\ref{rst:discrete}}
+\label{sec:discussion-proof1}
 
@@
 
-% bound first uses a lemma bounding the expected number of time steps in which a payment is made by 
-% \begin{align}
-% O\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
-%   + \frac{\ARMNUM^2 d}{1 - \exp \left(
-%     \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-%   \right)} \right). \nonumber 
-% \end{align}
-% The proof follows that of Lemma~\ref{lem:numP}, except that it defines $\EvenLaterPhase = \max (2, \frac{30 \sigma^3}{x^3}, \frac{2}{\MinProb})$.
-
-% The proof of the expected regret bound then follows the proof of Theorem~\ref{rst:regret}, with these modifications:
-% \begin{itemize}
-% \item We use the lemma stated above to bound the regret on pulls that incentivize;
-% \item The expected length of phase $s$ is bounded by $\ARMNUM s$;
-% \item The regret in Equation~\ref{equ:small_regret_bound} can now be bounded by a constant.
-% \end{itemize}
-
-\subsubsection{Known \MinProb}
-An alternative useful assumption is that \MinProb (or a strictly positive lower bound on \MinProb) is known.
-
-\begin{assumption}[Known $\MinProb$]
-\label{a:known-p}
-A strictly positive lower bound on \MinProb is known in advance.
-\end{assumption}
-
-When this assumption holds, we choose a different modification in the definition of payment eligibility.
-Let $s_0 = \exp(2/\MinProb)$.
-An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
-if both of the following hold:
-\begin{itemize}
-\item $i$ has been pulled at most
-$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
-\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s+s_0)$.
-\end{itemize}
-
-This, knowledge of \MinProb allows the algorithm to incentivize significantly fewer arm pulls.
-We refer to this modified version of Algorithm~\ref{alg:basic-incentivizing} as the \emph{Known-\MinProb Algorithm.}
-We outline a proof of the following result for this algortithm under Assumption~\ref{a:known-p}.
-
-\begin{theorem}
-\label{rst:known-p}
-Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has an expected payment budget bounded above by 
-\begin{align*}
-O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
-\end{align*}
-and an expected regret bounded above by
-\begin{align*}
-O \left(\frac{\MAXR \ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
-  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} +\frac{\ARMNUM^2 d\MAXR}{\MinProb}+\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
-\end{align*}
-\end{theorem}
+\section{Proof of Theorem~\ref{rst:known-p}}
+\label{sec:discussion-proof2}
 

### 2018-02-17 Discussion.tex
edits in problem definition, carried through to proofs
moved some proofs to the appendix

@@
 There is a positive $\delta_0$ such that
-$F_{i,j} (\delta_0) = 0$ for all $i,j$.
+$\AlmostTied{\delta_0} = 0$.
 \end{assumption}
@@
 We refer to this modified version of Algorithm~\ref{alg:basic-incentivizing} as the \emph{Discrete-Preference Algorithm.}
-We outline a proof of the following result for this algortithm under Assumption~\ref{a:discrete}.
+We outline a proof of the following result for this algortithm under Assumption~\ref{a:discrete} in Appendix~\ref{sec:discussion-proof1}.
 
@@
 \end{theorem}
-
-\begin{proof}
-The proof of the expected payment bound is the same as the proof of Theorem~\ref{rst:budget}, except that we now define $h(\ell) := \max \left( \frac{2}{\MinProb},
-\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
-\right)$.
-
-To prove the bound on the expected regret, one can first prove tightened versions of Lemmas~\ref{lem:no-incentives} and \ref{lem:numP},
-which replace the $\exp(2/\MinProb)$ term with simply $2/\MinProb$.
-In return, the length of phase $s$ is now bounded only be $\ARMNUM s$ instead of $\ARMNUM \log(s)$.
-Substituting these changes into the proof of Theorem~\ref{rst:regret}, we obtain the claimed bounds.
-\end{proof}
-
-% bound first uses a lemma bounding the expected number of time steps in which a payment is made by 
-% \begin{align}
-% O\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
-%   + \frac{\ARMNUM^2 d}{1 - \exp \left(
-%     \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-%   \right)} \right). \nonumber 
-% \end{align}
-% The proof follows that of Lemma~\ref{lem:numP}, except that it defines $\EvenLaterPhase = \max (2, \frac{30 \sigma^3}{x^3}, \frac{2}{\MinProb})$.
-
-% The proof of the expected regret bound then follows the proof of Theorem~\ref{rst:regret}, with these modifications:
-% \begin{itemize}
-% \item We use the lemma stated above to bound the regret on pulls that incentivize;
-% \item The expected length of phase $s$ is bounded by $\ARMNUM s$;
-% \item The regret in Equation~\ref{equ:small_regret_bound} can now be bounded by a constant.
-% \end{itemize}
 
@@
 We refer to this modified version of Algorithm~\ref{alg:basic-incentivizing} as the \emph{Known-\MinProb Algorithm.}
-We outline a proof of the following result for this algortithm under Assumption~\ref{a:known-p}.
+We outline a proof of the following result for this algortithm under Assumption~\ref{a:known-p} in the Appendix~\ref{sec:discussion-proof2}.
 
@@
 \end{theorem}
-
-\begin{proof}
-  The proof of the expected payment bound follows Lemma~\ref{rst:budget} except for defining
-  $h(\ell) := \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}$
-(without including the $\exp(2/\MinProb)$ term).
-
-The proof of the expected regret bound first establishes tightened versions of Lemmas~\ref{lem:no-incentives} and \ref{lem:numP},
-proving the following upper bound on the number of time steps in which a payment is made:
-\begin{align}
-O\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
-  + \frac{\ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right). \nonumber 
-\end{align}
-The proof of this result follows that of Lemma~\ref{lem:numP}, but the less aggressive incentivization allows us to define $\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3})$ since $\frac{1}{\log(s+s_0)} \leq \frac{\MinProb}{2}$ is true for all $s$.
-
-Using this tighter bound on the number of incentiziations, and the fact that phases now last at most $\ARMNUM \log(s+s_0)$ steps in expectation, we can bound the regret in Equation~\ref{equ:small_regret_bound} by
-%$71.11 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1)\log(T+s_0)$
-$O\left(\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right)$.
-\end{proof}

### 2018-02-17 Lemmas.tex
moved some proofs to the appendix

--- 2018-02-17 algorithm.tex
@@
-\section{Main Algorithm and Analysis}
-\label{sec:ub}
-The algorithm achieving the claimed bounds of
-Theorems~\ref{rst:budget} and~\ref{rst:regret} is fairly simple.
-It mostly allows agents to exploit, but when an arm is sufficiently
-unlikely to be pulled, 
-the algorithm incentivizes this arm with a payment high enough
-to guarantee that the next agent pulls it.
-This way the algorithm ensures that each arm is pulled often enough.
-
-More precisely, the algorithm divides time into \emph{phases}
-$s = 1, 2, 3, \ldots$.
-Phase $s$ starts when each arm has been pulled at least $s$ times.
-We indicate the start time of phase $s$ by $t_s$. An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
-if both of the following hold:
-
-\begin{itemize}
-\item $i$ has been pulled at most%
-\footnote{in fact: exactly, since the algorithm entered phase $s$}
-$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
-\item Based on the current estimates \ArmEV{t}{i'} of all arms'
-attribute vectors, the probability of pulling arm $i$ is less than
-$1/\log(s)$. Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
-  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
-be the probability that arm $i$ will be pulled
-by the next (random) agent based on the current estimates. 
-Then, the second criterion for payment-eligibility is that
-$\PullProb{t}{i} < 1/\log(s)$.
-\end{itemize}
-
-When multiple arms are payment-eligible, the algorithm picks one arbitarily to incentivize.
-When the algorithm decides to incentivize an arm $i$,
-it offers ``whatever it takes,'' i.e., offers a payment of
-$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$.
-The maximum for \AgV is taken over the support of \AgentDist;
-recall that we assumed this support to be compact.
-The payment \Pay{t}{i} may appear unnecessarily high.
-Indeed, it suffices to
-incentivize only a $1/\log(s)$ fraction of the agents,
-and our bounds also hold for an alternate version of our algorithm that 
-offers payment
-$\Pay{t}{i} = \min \Set{c \geq 0}{%
-\Prob[\AgV \sim \AgentDist]{c + \AgV \cdot \ArmEV{t}{i} \geq \max_{i'\ne i} \AgV \cdot \ArmEV{t}{i'}} \ge 1/\log(s)}$.
-However, we focus on the higher payments for simplicity of presentation.
-
-Notice that \PullProb{t}{i} depends on the estimates for \emph{all}
-arms; thus, by pulling some other arm $i'$, an arm $i$ may become
-payment-eligible, or cease to be so.
-Algorithm~\ref{alg:basic-incentivizing} gives the full details.
-
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration \label{alg:basic-incentivizing}}
-\begin{algorithmic}
-\STATE Set the current phase number $s = 1$.
-\COMMENT{Each arm is pulled once initially ``for free''.}
-\FOR{time steps $t = 1, 2, 3, \ldots$}
-\IF{$\NumPull{t}{i} \geq s+1$ for all arms $i$}
-\STATE Increment the phase $s = s + 1$.
-\ENDIF
-\IF{there is a payment-eligible arm $i$}
-\STATE Let $i$ be an arbitary payment-eligible arm.
-\STATE Offer payment
-$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$
-for pulling arm $i$
-(and payment 0 for all other arms).
-\ELSE
-\STATE Let agent $t$ play myopically, i.e., offer payments 0 for all arms.
-\ENDIF
-\ENDFOR
-\end{algorithmic}
-\end{algorithm}
-
-The high-level idea in the proofs of our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret},
-is the following.
-Because the algorithm ensures that each arm is pulled
-``frequently enough,''
-the estimates \ArmEV{t}{i} become gradually more accurate in the
-phase number $s$.
-Thus, the fraction of agents who misidentify their best arm decreases.
-Because for each arm, enough agents have a true preference for this
-arm, once the arms' attribute vectors are learned well enough,
-the algorithm will not need to incentivize any more,
-resulting in a payment bound independent of $T$.
-Similarly, the regret will decrease, and mostly accrue
-due to ``problematic'' agents who are nearly tied in their preferences
-between their top two arm choices.
-The detailed analysis following this outline is somewhat subtle, though,
-due to the dependencies between the agents' arm pulls and the
-estimates which in turn are based on past arm pulls.
-We begin with several technical lemmas that are used for both the
-payment and regret bounds.
-
-To capture the probability masses of problematic agents,
-we define the quantity
-$\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
-\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
-to be the total probability mass (across all arms) of agents
-whose (actual) preference for their best arm over their second-best
-arm is at most $\delta$.
-\dkcomment{We should stress somewhere that we assume that actual ties
-  have measure 0.}
-
-To formally reason about the event that the estimates of arms'
-attributes vectors are accurate enough --- or fail to be so ---
-we define the events
-$\AccE{t}{i}{j}{x} := [|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq x]$
-that attribute $j$ of arm $i$ at time $t$ is estimated to
-within accuracy $x$ or better.
-Then, 
-$\AccEU{t}{x} = \bigcap_{i,j} \AccE{t}{i}{j}{x}$
-is the event that at time $t$, all arm attribute
-estimates are accurate to within $x$ simultaneously.
-We will then show that for suitable choices of $t, x$,
-the events \AccE{t}{i}{j}{x}
-(and hence, by union bound, \AccEU{t}{x})
-have high probability,
-and that when they do, myopic agents do not make large mistakes.
-
-We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.
-
-\subsection{General Lemmas}
-
-We begin by showing that under our assumptions, the measure of
-problematic arms cannot be too large.
-
-\begin{lemma} \label{lem:sdelta}
-$\AlmostTied{\delta} \leq \TieDensity \cdot \delta$ for all $\delta$.
-\end{lemma}
-
-\begin{emptyproof}
-Using the upper bound from Assumption~\ref{A1}, we can bound
-
-\begin{align*}
-\AlmostTied{\delta}
-& = \sum_{i,i'} \ProbC{\AgV \cdot (\ArmV{i} - \ArmV{i'}) \leq \delta}%
-    {\AgV \in \FirstTwo{i}{i'}}
-  \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}\\
-& \leq \sum_{i,i'} \TieDensity \cdot \delta
-    \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}
-\; = \; \TieDensity \cdot \delta. \QED
-\end{align*}
-\end{emptyproof}
-
-We next bound the length of any phase, which will be useful to bound
-the cumulative regret of the early rounds
-(before tail bounds have kicked in).
-
-\begin{lemma} \label{lem:phase-length}
-For any $s\geq 3$, the expected length of phase $s$ is at most
-$\ARMNUM \cdot \log(s)$ time steps.
-\end{lemma}
+\section{Proof of Lemma~\ref{lem:phase-length}}
+\label{sec:lemma4-proof}
 
@@
 
-The key technical lemma captures the intuition that
-the estimates of the arms' attribute vectors become
-more accurate with increasing phases $s$.
-
-\begin{lemma} \label{lem:round-prob}
-Recall that $\sigma$ is the standard deviation of the Gaussian noise.
-Let \LatePhase be a phase cutoff, 
-and let $x_n, x'_n > 0$ be functions satisfying that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
-\leq \frac{n x'_n}{2 \sigma}$,
-for all $n \geq \LatePhase$.
-Let $\tau_s$ be a stopping time
-(which may depend on the entire past history)
-which is almost surely in phase $s$,
-i.e., satisfying $\tau \in [t_s, t_{s+1})$ almost surely.
-
-Then, for any arm $i$, attribute $j$, and phase $s \geq \LatePhase$,
-we have that
-$\Prob{\AccE{\tau_s}{i}{j}{x'_s}}
-\geq 1 - 24 \exp\left(-\frac{1.8 s x_s^2}{16 \sigma^2} \right)$.
-\end{lemma}
-
-The proof of Lemma~\ref{lem:round-prob} is based on an adaptive
-concentration inequality due to \cite{zhao2016adaptive},
-given as Lemma~\ref{lem:ACI-inequality}.
-
-\begin{lemma}[Corollary 1 of \cite{zhao2016adaptive}]
-\label{lem:ACI-inequality}
-Let $X_i$ be zero-mean $1/2$-subgaussian random variables,
-and $\SET{S_n = \sum_{i=1}^n X_i, n \geq 1}$ the corresponding random walk.
-Let $J$ be any stopping time with respect to $\SET{X_1, X_2, \ldots}$.
-(We allow $J$ to take the value $\infty$,
-defining $\Prob{J = \infty} = 1 - \lim_{n \to \infty} \Prob{J \leq n}$.)
-Define 
-\begin{align*}
-g(n) & = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b}.
-\end{align*}
-Then, 
-\begin{align*}
-\Prob{J < \infty \mbox{ and } S_J \geq g(J)} \leq 12 \e^{-1.8 b}.
-\end{align*}
-\end{lemma}
+\section{Proof of Lemma~\ref{lem:round-prob}}
+\label{sec:lemma5-proof}
 
@@
 
-Next, we show the complementary part:
-when \AccEU{t}{x} happens, no myopic agent incurs large regret.
-
-\begin{lemma} \label{lem:right-choice}
-Let $x > 0$ be arbitrary.
-When \AccEU{t}{x} happens,
-no agent \AgV will pull a highly suboptimal arm, i.e., an arm $i$ with 
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
-\end{lemma}
+\section{Proof of Lemma~\ref{lem:right-choice}}
+\label{sec:lemma7-proof}
 
@@
 \end{proof}
-
-\subsection{Bounding the Total Payment}
-
-As a first step towards bound the total payment (and also regret),
-we show that for sufficiently late phases,
-under the event \AccEU{t}{x} for suitably small $x$,
-the algorithm does not offer any payments.
-
-\begin{lemma} \label{lem:no-incentives}
-Fix an arm $i$.
-Let $s \geq \exp(2/\MinProb)$, and let $\tau_s$ be the (random)
-time when arm $i$ is pulled for the \Kth{s} time.
-Under \AccEU{\tau_s}{\frac{p}{4\Diam d \TieDensity}},
-this pull of arm $i$ is not incentivized.
-\end{lemma}
-
-\begin{proof}
-By Lemma~\ref{lem:right-choice},
-under the event \AccEU{\tau_s}{\frac{\MinProb}{4\Diam d \TieDensity}},
-all agent types \AgV with
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}})
-> \frac{\MinProb}{2\TieDensity}$
-will pull their best arm \Best{\AgV}.
-
-By Lemma~\ref{lem:sdelta}, the measure of agents (across all arms)
-whose best and second-best arm differ in utility by less
-than $\frac{\MinProb}{2\TieDensity}$ is at most $\frac{\MinProb}{2}$.
-In particular, this bound holds for agents whose best arm is $i$.
-By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
-as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
-will myopically pull arm $i$.
-Because $1/\log(s) < \frac{\MinProb}{2}$ for
-$s \geq \exp(2/\MinProb)$, arm $i$ is not payment-eligible at time
-$\tau_s$.
-\end{proof}
-
-Towards bounding the algorithm's total payment, we now bound the
-\emph{number} of rounds in which the algorithm makes a payment by a
-constant.
-This bound also turns out to be useful for bounding the total regret.
-
-\begin{lemma} \label{lem:numP}
-The expected number of time steps in which
-Algorithm~\ref{alg:basic-incentivizing}
-makes any payment is at most $O\left( N\exp\left(\frac{2}{p}\right) \right)$.
-\end{lemma}
-
-\begin{proof}
-We partition phases into early and late phases.
-For each of the early phases,
-we crudely bound the number of payments by \ARMNUM,
-using that each arm is incentivized at most once per phase.
-For later phases,
-we use Lemma~\ref{lem:no-incentives},
-which rules out any incentives unless large misestimates of the arm
-locations occur, which is exponentially unlikely by 
-Lemma~\ref{lem:round-prob}.
-
-To make this intuition precise, we set
-$\delta = \frac{\MinProb}{2 \TieDensity}$,
-and $x = x' = \frac{\delta}{2 \Diam d}$
-(which is independent of the phase number $s$).
-The cutoff point between early and late phases is now set to
-$\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3}, \exp(\frac{2}{\MinProb}))$.
-We will verify below that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
-\leq \frac{n x}{2 \sigma}$
-for all $n \geq \max(2, \frac{30 \sigma^3}{x^3})$.
-
-Fix an arm $i$, and consider the \Kth{s} pull of an arm $i$,
-for $s \geq \EvenLaterPhase$.
-If this pull occurs before phase $s$, it was definitely not incentivized.
-So we condition on the pull occurring in phase $s$,
-and let $\tau_s$ be the time step when this pull occurred;
-notice that this means that this must be the first pull of arm $i$ in
-phase $s$.
-
-By Lemma~\ref{lem:round-prob} (with our choice of $x = x'$),
-and a union bound over all $i,j$, we bound the probability
-$\Prob{\AccEU{\tau_s}{x}}
-\geq 1 - 24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$.
-And by Lemma~\ref{lem:no-incentives},
-under the event ${\mathcal E}_{\tau_s}(x)$,
-arm $i$ is not payment-eligible.
-
-Thus, for any $s \geq \EvenLaterPhase$,
-the \Kth{s} pull of arm $i$ is incentivized  
-with probability at most
-$24 \ARMNUM d \cdot \exp \left(
-  -\frac{1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-\right)$.
-Summing over all arms and phases $s$,
-and adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
-the first \EvenLaterPhase phases, 
-the expected total number of arm incentivizations is at most
-\begin{align*}
-&\ARMNUM \EvenLaterPhase
-  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \nonumber \\
-=& O\left( \max\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp(\frac{2}{p})\right)
-  + \frac{\ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right) \nonumber  \\
-=& O\left( N\exp\left(\frac{2}{p}\right) \right).
-\end{align*}
-
-It remains to show that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
-\leq \frac{n x}{2 \sigma}$
-for all $n \geq \max(2, \frac{30 \sigma^3}{x^3}$.
-We first use that $\sqrt{\cdot}$ is sublinear to bound
-\[
-  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
-\; \leq \; \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1)} + \frac{n x}{4 \sigma}
-\]
-(here we use the fact $\sqrt{n} \leq n$).
-Next, we show that
-$\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} \leq \frac{n x}{4 \sigma}$;
-then, adding the two terms gives the desired bound.
-
-By squaring the claimed statement and rearranging,
-it is equivalent to show that
-$\frac{n}{\log(\log_{1.1}(n)+1)} \geq \frac{9.6\sigma^2}{x^2}$.
-Because $n \geq 2$,
-a numerical calculation and derivative test shows that
-$\frac{n}{\log(\log_{1.1}(n)+1)} \geq n^{2/3}$,
-and because $n \geq \frac{30 \sigma^3}{x^3}$,
-we get that
-$n^{2/3} \geq \frac{9.6 \sigma^2}{x^2}$, completing the proof.
-
-\end{proof}
-
-It would be desirable to simply identify a constant upper bound on the
-payment made each time.
-Unfortunately, while the agent types are drawn from a bounded support,
-the noise in arm locations is not;
-hence, with small probability, arm locations may be grossly
-misestimated, resulting in high incentive payments.
-As a result, the actual analysis of the total payment is significantly more
-intricate;
-the proof of Theorem~\ref{rst:budget} is given in
-Appendix~\ref{sec:payment-proof}.
-
-\subsection{Bounding the Total Regret}
-In bounding the total regret, because agents' types are from a compact
-set by Assumption~\ref{A2}, the maximum regret in any one round is
-bounded by a constant.
-We use $\MAXR = \max_{\AgV, i,i'} \AgV \cdot (\ArmV{i} - \ArmV{i'})$
-to denote this constant upper bound on the maximum regret that can be
-incurred in any one time step.
-
-\begin{extraproof}{Theorem~\ref{rst:regret}}
-Regret can arise in two ways:
-(1) an agent was incentivized to pull a suboptimal arm, or
-(2) an agent myopically pulled a suboptimal arm.
-By Lemma~\ref{lem:numP}, Algorithm~\ref{alg:basic-incentivizing}
-incentivizes agents at most 
-$O\left( N\exp\left(\frac{2}{p}\right) \right)$
-times in expectation, each time causing regret at most \MAXR,
-for a total expected regret of at most
-$O\left(\MAXR\cdot N\exp\left(\frac{2}{p}\right) \right)$.
-For the rest of the proof, we focus on the regret incurred when agents
-pull arms myopically and make mistakes.
-
-We distinguish between agents incurring large regret
-(which requires severe misestimates of arm locations;
-such misestimated are exponentially unlikely to occur), 
-and agents incurring small positive regret,
-which requires these agents to be almost tied in their preference for
-the best arm.
-To be more precise, we will define (with foresight) a phase-dependent
-cutoff
-$g(s) = \sqrt{\frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}}$,
-and consider a regret exceeding $g(s)$ large.
-
-We first consider agents \AgV incurring positive regret less than $g(s)$.
-The second-best arm \Second{\AgV} of such an agent \AgV must satisfy
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(s)$.
-By Lemma~\ref{lem:sdelta}, the total measure of such agents
-is $\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$,
-and each incurs regret at most $g(s)$.
-Summing over all time steps,
-and using Lemma~\ref{lem:phase-length} to bound the number of time
-steps in phase $s$, 
-the expected total regret from such agents is at most
-\begin{align}
-\Expect{\sum_{s=1}^{T} \sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)}
-& \leq \sum_{s=1}^{T} \TieDensity \cdot g^2(s) \ARMNUM \log(s).
-\label{equ:small_regret_bound}
-\end{align}
-
-We next bound the regret incurred in time steps with large regret.
-Let the random variable $t_s$ be the final time step in phase $s$,
-for each $s$. Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
-time step in the \Kth{s} phase,
-with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
-i.e., $k > t_{s}-t_{s-1}$.
-By Lemma~\ref{lem:right-choice},
-under \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}}, no agent at time $t$ will incur
-regret more than $g(s)$.
-
-To bound the probability of \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}},
-we use Lemma~\ref{lem:round-prob}
-(with $x_s = x'_s = \frac{g(s)}{2 \Diam d}$
-and a stopping time of $\tau_s^k$).
-We first verify that this choice of $x_s, x'_s$
-satisfies the assumption of Lemma~\ref{lem:round-prob} for all
-$s \geq 2$,
-i.e., that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
-\leq \frac{n x_n}{2 \sigma}$
-for all $n \geq 2$.
-Substituting that
-$x_n = \frac{g(n)}{2 \Diam d} = \sqrt{\frac{32\log(T) \cdot \sigma^2}{1.8 n}}$,
-the left-hand side is
-
-\[
-  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 \log T}{1.8}}
-  \; \leq \;
-  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 n \log T}{1.8}},
-\]
-while the right-hand side is $\sqrt{\frac{8 n \log(T)}{1.8}}$.
-Squaring both sides and canceling out common terms,
-the desired inequality is equivalent to
-$\frac{50}{9} \log T \geq \log(\log_{1.1}(n) + 1)$.
-Because $n \leq T$, it is sufficient to show that
-$\frac{50}{9} \log T \geq \log(\log_{1.1}(n) + 1)$,
-which can be verified by numerical calculation for $T=2$ and a
-derivative test.
-
-Now, by Lemma~\ref{lem:round-prob} and a union bound over all arms $i$
-and attributes $j$, we get that 
-\begin{align*}
-\Prob{\AccEU{\tau_s^k}{x_s}}
-& \leq 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16 \sigma^2} \right)
-\; = \; \frac{24 \ARMNUM d}{T^2}.
-\end{align*}
-
-In the low-probability event, we simply 
-bound the maximum regret by \MAXR.
-Now, applying Lemma~\ref{lem:phase-length},
-the total expected regret from large-regret steps is at most
-
-\begin{align*}
-\sum_{s = 1}^T \sum_{t=t_s}^{t_{s+1}-1}
-  \Prob{\mbox{incur regret exceeding } g(s) \mbox{ at step } t} \cdot \MAXR
-& \leq
- \sum_{s = 1}^T \frac{24 \ARMNUM d}{T^2} \cdot \MAXR \cdot \ARMNUM \log(s)
-\\ & \leq 12 \ARMNUM^2 d \MAXR.
-\end{align*}
-
-Adding all three types of regret terms,
-and substituting that 
-$g^2(s) = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
-the cumulative regret up to time $T$ is at most
-
-\begin{align*}
-\lefteqn{
-O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
-+ \ARMNUM^2 \MAXR d
-+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} g^2(s) \log(s) \right)}
-\\ & = 
-O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
-+ \ARMNUM^2 \MAXR d
-+ \ARMNUM \TieDensity \Diam^2 d^2 \sigma^2 \cdot \log^3(T) \right).
-\end{align*}
-\end{extraproof}

### 2018-02-17 algorithm.tex
moved some proofs to the appendix

@@
 the cumulative regret of the early rounds
-(before tail bounds have kicked in).
+(before tail bounds have kicked in). We prove Lemma~\ref{lem:phase-length} in the Appendix~\ref{sec:lemma4-proof}.
 
@@
 
-\begin{proof}
-Let $S$ be the set of arms that have been pulled at most
-$s$ times at the start of phase $s$.
-Thus, phase $s$ has ended when each $i \in S$ has been pulled at least once.
-Consider any time step $t$.
-If $S$ contains at least one payment-eligible arm $i$,
-then some payment-eligible arm will be pulled with probability 1,
-and every payment-eligible arm is in $S$.
-In particular, the size of $S$ decreases with probability 1.
-If $S$ contains no payment-eligible arm,
-then by definition of payment-eligibility,
-each arm $i \in S$ has probability at least $1/\log(s)$ of being pulled.
-In particular, the size of $S$ decreases with probability at least $1/\log(s)$.
-
-In either case, the expected number of time steps until
-$|S|$ decreases is at most $\log s$,
-so the expected number of steps until $S$ is empty is at most
-$\ARMNUM \cdot \log(s)$.
-\end{proof}
-
-The key technical lemma captures the intuition that
+We now state the key technical lemma captures the intuition that
 the estimates of the arms' attribute vectors become
@@
 
-\begin{extraproof}{Lemma~\ref{lem:round-prob}}
-Fix an arm $i$ and attribute $j$.
-By the assumptions of the lemma,
-the stopping time $\tau_s$ is such that almost surely,
-each arm --- and in particular arm $i$ --- has been pulled at least
-$s \geq \LatePhase$ times at time $\tau_s$.
-Define $J$ to be the number of times that $i$ has been pulled at
-time $\tau_s$.
-For any $n \geq 1$, let $k_n$ be the time step right after arm $i$ has
-been pulled for the \Kth{n} time. Define
-$S_n := \frac{n \cdot (\ArmE{k_n}{i}{j} - \Arm{i}{j})}{2 \sigma}$
-to be the sum of all attribute-$j$ noise components up to and
-including the \Kth{n} pull of arm $i$,
-renormalized to have standard deviation $1/2$.
-The $S_n$ define an unbiased half-subgaussian random walk,
-and we can therefore apply Lemma~\ref{lem:ACI-inequality} to them and
-the stopping time $J$.
-Specifically, we set $b = \frac{x_J^2}{16 \sigma^2}$,
-and obtain that
-
-\begin{align*}
-\Prob{J < \infty \mbox{ and } S_J \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x_J^2}{16 \sigma^2}}}
-& \leq 12 \exp \left( \frac{-1.8 J x_J^2}{16 \sigma^2} \right).
-\end{align*}
-
-Applying Lemma~\ref{lem:ACI-inequality} to $-S_n$ with the same choice
-of $b$, and taking a union bound over both cases, we obtain that
-
-\begin{align*}
-\Prob{J < \infty \mbox{ and } |S_J| \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x_J^2}{16 \sigma^2}}}
-& \leq 24 \exp \left( \frac{-1.8 J x_J^2}{16 \sigma^2} \right).
-\end{align*}
-
-Because $J$ will be finite with probability 1, we can drop the
-$J < \infty$ part of the event:
-\begin{align*}
-& \Prob{S_J \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x_J^2}{16
-    \sigma^2}}}\\
-= & \Prob{J < \infty \mbox{ and } S_J \geq 
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J^2 x_J^2}{16
-    \sigma^2}}}.
-\end{align*}
-
-In the high-probability case, we now apply the assumed inequality
-between $x_J$ and $x'_J$, to obtain that
-\[
-|S_J| \; \leq \;
-\sqrt{0.6 J \cdot \log (\log_{1.1}(J) + 1) + \frac{J x_J^2}{16 \sigma^2}}
-\; \leq \; \frac{J x'_J}{2 \sigma}.
-\]
-
-Substituting the definition of $S_J$ and canceling common terms,
-the inequality implies that
-$|\ArmE{k_J}{i}{j} - \Arm{i}{j}| \leq x'_J$.
-The choice of $J$ ensures that
-$\ArmE{k_J}{i}{j} = \ArmE{\tau_s}{i}{j}$,
-and we have thus shown that
-$|\ArmE{\tau_s}{i}{j} - \Arm{i}{j}| \leq x'_s$.
-\end{extraproof}
-
-Next, we show the complementary part:
-when \AccEU{t}{x} happens, no myopic agent incurs large regret.
+We leave the proof of Lemma~\ref{lem:round-prob} in the Appendix~\ref{sec:lemma5-proof}. Next, we show the complementary part:
+when \AccEU{t}{x} happens, no myopic agent incurs large regret. We prove Lemma~\ref{lem:right-choice} in the Appendix~\ref{sec:lemma7-proof}.
 
@@
 \end{lemma}
-
-\begin{proof}
-By definition, when \AccEU{t}{x} happens,
-for all arms $i$ and attributes $j$,
-all arm attribute estimates are accurate to within $x$,
-in the sense that
-$|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq x$.
-
-Consider any agent type \AgV.
-Let $i \neq \Best{\AgV}$ be any arm
-with much smaller true reward than the best arm:
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
-Because each coordinate of \ArmEV{t}{\Best{\AgV}} and of
-\ArmEV{t}{i} is estimated accurately to within $x$, 
-we get that 
-$\AgV \cdot (\ArmEV{t}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
-\geq - \Diam d x$
-and
-$\AgV \cdot (\ArmEV{t}{i} - \ArmV{i}) \leq \Diam d x$.
-Hence,
-
-\begin{align}
-\AgV \cdot (\ArmEV{t}{\Best{\AgV}} - \ArmEV{t}{i})
-& =
-\AgV \cdot (\ArmEV{t}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
-+ \AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i})
-+ \AgV \cdot (\ArmV{i} - \ArmEV{t}{i}) \nonumber\\
-& > -\Diam d x + 2 \Diam d x - \Diam d x
-\; = \; 0, \label{equ:choice}
-\end{align}
-which means that the agent with type \AgV will not pull arm $i$.
-\end{proof}
 

### 2018-02-17 Discussion-Proof.tex
re-state lemmas/proofs in the appendix

@@
 \label{sec:discussion-proof1}
+
+\begin{rtheorem}{Theorem}{\ref{rst:discrete}}
+Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment budget bounded above by 
+\begin{align*}
+O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
+\end{align*}
+and expected regret bounded above by 
+\begin{align}
+O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
+  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} \right).  \nonumber
+\end{align}
+\end{rtheorem}
 
@@
 \label{sec:discussion-proof2}
+
+\begin{rtheorem}{Theorem}{\ref{rst:known-p}}
+Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has an expected payment budget bounded above by 
+\begin{align*}
+O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
+\end{align*}
+and an expected regret bounded above by
+\begin{align*}
+O \left(\frac{\MAXR \ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
+  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
+    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)} +\frac{\ARMNUM^2 d\MAXR}{\MinProb}+\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
+\end{align*}
+\end{rtheorem}
 

### 2018-02-17 Lemmas.tex
re-state lemmas/proofs in the appendix

@@
 \label{sec:lemma4-proof}
+
+\begin{rlemma}{Lemma}{\ref{lem:phase-length}}
+For any $s\geq 3$, the expected length of phase $s$ is at most
+$\ARMNUM \cdot \log(s)$ time steps.
+\end{rlemma}
 
@@
 \label{sec:lemma5-proof}
+
+\begin{rlemma}{Lemma}{\ref{lem:round-prob}}
+Recall that $\sigma$ is the standard deviation of the Gaussian noise.
+Let \LatePhase be a phase cutoff, 
+and let $x_n, x'_n > 0$ be functions satisfying that
+$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
+\leq \frac{n x'_n}{2 \sigma}$,
+for all $n \geq \LatePhase$.
+Let $\tau_s$ be a stopping time
+(which may depend on the entire past history)
+which is almost surely in phase $s$,
+i.e., satisfying $\tau \in [t_s, t_{s+1})$ almost surely.
+
+Then, for any arm $i$, attribute $j$, and phase $s \geq \LatePhase$,
+we have that
+$\Prob{\AccE{\tau_s}{i}{j}{x'_s}}
+\geq 1 - 24 \exp\left(-\frac{1.8 s x_s^2}{16 \sigma^2} \right)$.
+\end{rlemma}
 
@@
 
+\begin{rlemma}{Lemma}{\ref{lem:right-choice}}
+Let $x > 0$ be arbitrary.
+When \AccEU{t}{x} happens,
+no agent \AgV will pull a highly suboptimal arm, i.e., an arm $i$ with 
+$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
+\end{rlemma}
+
 \begin{proof}

### 2018-02-17 Lemmas.tex
re-state lemmas/proofs in the appendix

@@
 \end{proof}
+
+\section{Proof of Lemma~\ref{lem:no-incentives}}
+\label{sec:lemma8-proof}
+
+\begin{rlemma}{Lemma}{\ref{lem:no-incentives}}
+Fix an arm $i$.
+Let $s \geq \exp(2/\MinProb)$, and let $\tau_s$ be the (random)
+time when arm $i$ is pulled for the \Kth{s} time.
+Under \AccEU{\tau_s}{\frac{p}{4\Diam d \TieDensity}},
+this pull of arm $i$ is not incentivized.
+\end{rlemma}
+
+\begin{proof}
+By Lemma~\ref{lem:right-choice},
+under the event \AccEU{\tau_s}{\frac{\MinProb}{4\Diam d \TieDensity}},
+all agent types \AgV with
+$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}})
+> \frac{\MinProb}{2\TieDensity}$
+will pull their best arm \Best{\AgV}.
+
+By Assmption~\ref{A1},
+%Lemma~\ref{lem:sdelta},
+the measure of agents (across all arms)
+whose best and second-best arm differ in utility by less
+than $\frac{\MinProb}{2\TieDensity}$ is at most $\frac{\MinProb}{2}$.
+In particular, this bound holds for agents whose best arm is $i$.
+By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
+as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
+will myopically pull arm $i$.
+Because $1/\log(s) < \frac{\MinProb}{2}$ for
+$s \geq \exp(2/\MinProb)$, arm $i$ is not payment-eligible at time
+$\tau_s$.
+\end{proof}

### 2018-02-17 algorithm.tex
re-state lemmas/proofs in the appendix

@@
 under the event \AccEU{t}{x} for suitably small $x$,
-the algorithm does not offer any payments.
+the algorithm does not offer any payments. We prove Lemma~\ref{lem:no-incentives} in the Appendix~\ref{sec:lemma8-proof}.
 
@@
 \end{lemma}
-
-\begin{proof}
-By Lemma~\ref{lem:right-choice},
-under the event \AccEU{\tau_s}{\frac{\MinProb}{4\Diam d \TieDensity}},
-all agent types \AgV with
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}})
-> \frac{\MinProb}{2\TieDensity}$
-will pull their best arm \Best{\AgV}.
-
-By Assmption~\ref{A1},
-%Lemma~\ref{lem:sdelta},
-the measure of agents (across all arms)
-whose best and second-best arm differ in utility by less
-than $\frac{\MinProb}{2\TieDensity}$ is at most $\frac{\MinProb}{2}$.
-In particular, this bound holds for agents whose best arm is $i$.
-By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
-as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
-will myopically pull arm $i$.
-Because $1/\log(s) < \frac{\MinProb}{2}$ for
-$s \geq \exp(2/\MinProb)$, arm $i$ is not payment-eligible at time
-$\tau_s$.
-\end{proof}
 

### 2018-02-17 problem_setting.tex
edits to section 2 and conclusion

@@
 Arm payoffs are determined by $d$ \emph{attributes} or \emph{features};
-hence, arms can be identified with vectors $\ArmV{i} \in \R^d$.
+hence, arms are identified with vectors $\ArmV{i} \in \R^d$.
 The \ArmV{i} are (adversarially) fixed, and unknown to the agents
 or the principal.
-Whenever arm $i$ is pulled, its current utility-relevant features are
+When arm $i$ is pulled, its current utility-relevant features are
 determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero independent Gaussian%
@@
   $\sigma^2$ is uniform across time steps.
-  This is not material for the analysis.
-\dkedit{In fact, the analysis extends straightforwardly to any
-  mean-zero sub-Gaussian noise.} \dkcomment{Is this true?}}
+In fact, the analysis extends straightforwardly to any
+mean-zero \pfedit{sub-Gaussian($\sigma^2$)} noise \pfedit{that is independent but not necessarily identically distributed across time}.}
 noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.
@@
 i.e., agents have linear preferences.%
-\footnote{\dkedit{Some of our results generalize to other forms of
-    agent rewards.}}
 
@@
 An agent at time $t$ estimates arm $i$'s attribute vector as the
-average of vectors observed during past pulls of the arm:
+average of vectors observed during the arm's past pulls:
 $\ArmEV{t}{i} = \frac{1}{\NumPull{t}{i}+1} \cdot
@@
 here, \ArmEV{i}{0} is a single draw $\ArmV{i} + \NoiseV$ for arm $i$.
-(In other words, we assume that each arm is pulled once for free at time 0.)
+(In other words, we assume each arm is pulled once for free at time 0.)
 
@@
 and only knows the distribution \AgentDist from which it is drawn.
-Her goal is to achieve a good tradeoff between the cumulative
+Her goal is to reduce both the cumulative
 \emph{regret} experienced by all users up to time $T$,
@@
 $\Expect{\TotalPay{T}}$ are small.
-\dkcomment{Deleted the \POLICY subscript for the expectation, as the
-  expectation is also over the entire random history.}
 
@@
 with attribute vector \AgV,
-\dkedit{breaking ties arbitrarily (but consistently)}.
+breaking ties arbitrarily (but consistently).
 
@@
 
-\subsection{Properties of \AgentDist}
-Our algorithms rely on a few assumptions about the agent distribution
+% \paragraph{Properties of \AgentDist}
+Our algorithms rely on the following three assumptions on the agent distribution
 \AgentDist.
@@
 %second-best arm is $i'$.
-% Let $F_{i,i'}$ be the cumulative density function
-% (or cumulative mass function if $\AgentDist(\cdot)$ is a discrete distribution)
+% Let $F_{i,i'}$ be the cumulative distribution function,
 % $F_{i,i'}(z) = \Prob[\AgV \sim \AgentDist]{\AgV \in \FirstTwo{i}{i'}
@@
 
-\dkedit{Let \AlmostTied{z} be the cumulative density function
-(or cumulative mass function if $\AgentDist(\cdot)$ is a discrete distribution)
+Let \AlmostTied{z} be the cumulative distribution function (CDF)
 $\AlmostTied{z} = \Prob[\AgV \sim \AgentDist]{%
@@
 In words, \AlmostTied{z} is the CDF of the \emph{strength} of the
-preference of a random agent for his best arm over his second-best arm.}
+preference of a random agent for his best arm over his second-best arm.
 
@@
 
-\dkedit{\paragraph{Role of parameters:}
-Our problem setting is characterized by a fairly large number of
+\paragraph{Role of parameters:}
+Our problem setting is characterized by many 
 parameters.
 Of these, we consider \ARMNUM, $\MinProb \leq 1/\ARMNUM$ and $T$ to be
-the key parameters, while $\sigma, \Diam, d, \TieDensity$ should be
-considered constant.
-We will keep track of these constants throughout most of our proofs,
-but report final results in terms of only the three key parameters
-(except where we illustrate a specific point).}
-
-\dkcomment{Stuff to discussion in conclusions:
-\begin{enumerate}
-\item Arms that are noone's best.
-\item Other utilities besides inner products.
-\item Other noise distributions.
-\item Better bounds.
-\end{enumerate}
-}
+the key parameters, while we consider $\sigma, \Diam, d, \TieDensity$ to be
+constant.
+We track all parameters through most of our proofs,
+but report final results in terms of only the three key parameters,
+except where we illustrate a specific point.

### 2018-02-17 result_discussion.tex
finished pass through Section 3

--- 2018-02-05 result_discussion.tex
@@
 \section{Overview of Results and Discussion}
-\dkcomment{I envision this section doing the following:
-\begin{enumerate}
-\item State the main theorem(s) formally.
-\item Discuss lower bounds or impossibility results.
-\item Discuss extensions.
-\item Discuss the justification or comparison to standard bandits.
-\item Discuss the comparison in the 2x2 square.
-\end{enumerate}
-}
 
-\dkcomment{For now, I am just copying over material from various other
-  parts that Bangrui/Peter wrote or I had written in earlier
-  iterations.}
+Our main algorithm is presented as
+Algorithm~\ref{alg:basic-incentivizing}
+in Section~\ref{sec:ub}.
+Our main result is the following pair of theorems%
+\footnote{Recall that we omit the dependence on parameters other than
+  \ARMNUM, \MinProb, $T$ unless making a particular point.},
+analyzing the payments and regret of the algorithm.
 
-\dkcomment{In the results discussion clarify which results need to
-  know $T$ and which don't.}
-
-\begin{theorem} \label{thm:main-overview}
-Under some technical assumptions, 
-there exists a policy which pays at most $O(\ARMNUM^2)$ in expectation,
-and achieves regret at most $O(\ARMNUM^2 + \log^2(T))$.
-\dkcomment{Omitting the density here.}
+\begin{theorem} \label{rst:budget}
+The expected total payment of
+Algorithm~\ref{alg:basic-incentivizing} is at most
+$O \left(\ARMNUM^2 \cdot \e^{2/\MinProb} \right)$.
 \end{theorem}
 
-As we discuss in more detail in Section~\ref{sec:main-discussion},
-the reason we obtain stronger regret bounds than in the standard bandit
-setting is that the agents' heterogeneity in preferences will
-naturally lead to exploration.
+\begin{theorem} \label{rst:regret}
+For any time horizon $T$, the expected cumulative regret for
+Algorithm~\ref{alg:basic-incentivizing} up to time $T$ is bounded
+above by 
+$O \left(\ARMNUM \cdot \e^{2/\MinProb} + \TieDensity \ARMNUM \log^3(T) \right)$.
+\end{theorem}
 
-Here we pursue an alternate direction to our analysis of incentivizing exploration with heterogeneous preferences: we consider approximation-style results comparing achievable algorithm performance across four different problem settings, described in the table below.
+When $\TieDensity = 0$, the bound of Theorem~\ref{rst:regret} is
+constant in $T$;
+thus, the algorithm achieves constant regret for constant payment. 
+The case $\TieDensity = 0$ arises, for instance, in the case of a
+discrete distribution for agents.
+In fact, in the case of a discrete distribution of agents,
+it is possible to modify the algorithm to reduce the dependence on
+\MinProb from exponential to polynomial.
+Theorem~\ref{rst:discrete} (given later) states that the modified
+algorithm achieves expected regret
+$O \left(\frac{\ARMNUM}{\MinProb^4} \right)$
+with expected payments of
+$O \left(\frac{\ARMNUM^2}{\MinProb^{5/2}} \right)$.
 
-\begin{center}
-\begin{tabular}{ c|c|c| } 
- \hline
-     & Pulls arms directly & Needs to incentivize \\ 
-\hline
- Perfect Info on Preferences & $C11$: The ``God'' Policy & $C12$ \\ 
- Partial Info on Preferences & $C21$ & $C22$: actual algorithm \\ 
- \hline
-\end{tabular}
-\end{center}
+The fact that constant regret can be achieved with constant payment
+(independent of $T$) when $\TieDensity = 0$ suggests aiming for a
+constant bound more generally, i.e., for $\TieDensity > 0$.
+That such a bound is unachievable is shown in Section~\ref{sec:lb},
+where we show a lower bound of $\Omega(\log(T))$ on
+the expected regret of any algorithm.
+The instance is very simple: it has two arms, one of which has known
+attributes; in addition, one draw from the other arm is observed in
+each step $t$ even when it is not pulled.
+While the probability of pulling the wrong arm decreases over time, it
+does not do so fast enough, causing the stated regret.
 
-Columns indicate whether the principal pulls arms directly (left column) or incentivizes agents who in turn actually pull the arms.
-Rows indicate whether the principal knows the preferences of the agents (top row) or not (bottom row).
-Problem settings correspond to cells and are described by the names C11, C12, and so on.
-An optimal algorithm for problem setting C11 has the best performance possible.
+The exponential dependence on $1/\MinProb$ implies an exponential
+dependence on \ARMNUM (because $\MinProb \leq 1/\ARMNUM$).
+This exponential dependence arises from a need to continue to
+incentivize arm pulls to ensure that nearly tied agents learn their
+best arms quickly.
+Aside from the assumption that $\TieDensity = 0$, another assumption
+allows us to eliminate this exponential dependency.
+Namely, when \MinProb (or a lower bound on it) is known ahead of time,
+the algorithm can be modified to incentivize arms less aggressively.
+As shown in Theorem~\ref{rst:known-p},
+the modified algorithm will have expected regret at most
+$O \left(\frac{\ARMNUM}{\MinProb^3}
++\frac{\ARMNUM \TieDensity \log^3(T)}{\MinProb} \right)$,
+with expected payments of at most
+$O \left(\frac{\ARMNUM^2}{\MinProb^{5/2}} \right)$.
 
-We wish to make two high-level points through this analysis:
+We compare these bounds to those for standard bandits,
+focusing on the dependence on $T$.  
+The standard bandit setting is the case when the agent types \AgV
+are concentrated on a single point, and agents pull arms at the
+principal's direction without requiring payment.
+(Notice that this setting violates our Assumption~\ref{A3},
+so out bounds do not apply to it.)
+Then, the payment is $0$ and the expected regret scales as
+$\Theta(\log(T))$ \cite[Theorem 2.1]{bubeck2012regret}.
 
-\begin{itemize}
-\item First, better performance is possible in setting C22 than in setting C21, in the sense we can find tight approximation guarantees relative to C11 that are better for C22 than for C21.
-This is achieved by setting up incentives in C22 that still allow agents to select arms aligned with their preferences, providing selections of arms that contain more information than in C21.
-\item Second, heterogeneity in preferences improves performance over what can be achieved in a setting with homogeneous preferences.
-This would be in the spirit of David K.'s results that heterogeneity in preference for money can be exploited to reduce the budget required.
-\end{itemize}
+Our algorithm's payment is constant in $T$,
+while its regret is $O(\log^3(T))$ in general with a lower bound of
+$\Omega(\log(T))$;
+when preferences are discrete, our algorithm's regret is
+constant in $T$.
+Thus, viewed solely in terms of the dependence on $T$,
+the best performance achievable seems comparable to that in a standard
+multi-armed bandit problem;
+but when preferences our discrete, the constant regret (rather than
+$\Theta(\log T)$ surpasses a standard multi-armed bandit.
+This may seem surprising, because our setting is one in which the
+principal has both less control and less information than in the
+standard bandit setting.
+The result arises because heterogeneity in preferences indeed provides
+free exploration, in which all of the arms can be pulled infinitely
+often without incurring regret.
 
-Section~\ref{sec:lb} constructs an example showing regret is $\Omega(\log(T))$ in the worst case, regardless of incentive budget.
+While heterogeneity in preferences enables this free exploration,
+heterogeneity alone is not always sufficient for enabling performance
+improvements compare to the standard bandit setting.
+Indeed, consider a version in which agents are still heterogeneous,
+but the principal has the power to pull arms directly.
+Unless the heterogeneity can be observed (i.e., the principal knows
+the agents' types), the principal will be unable to correctly choose
+each agent's preferred arm,
+even with infinite exploration of arm attributes.
+Hence, in this setting, the regret will grow as $\Omega(T)$.
+
+Thus, reaping the benefits of (unobserved) heterogeneous preferences
+requires the principal to give up direct control of the arms,
+providing agents the autonomy they need to express their private
+information about their own preferences.
+Our results show that simple arm-based incentives are sufficient
+to overcome the apparent challenges created by this abdication of
+control.

### 2018-02-17 problem_setting.tex

@@
 In fact, the analysis extends straightforwardly to any
-mean-zero \pfedit{sub-Gaussian($\sigma^2$)} noise \pfedit{that is independent but not necessarily identically distributed across time}.}
+mean-zero sub-Gaussian($\sigma^2$) noise that is independent but not necessarily identically distributed across time.}
 noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.

### 2018-02-17 algorithm.tex
edits to shorten section 4, down to 14 pages

@@
 The algorithm achieving the claimed bounds of
-Theorems~\ref{rst:budget} and~\ref{rst:regret} is fairly simple.
+Theorems~\ref{rst:budget} and~\ref{rst:regret} is simple.
 It mostly allows agents to exploit, but when an arm is sufficiently
-unlikely to be pulled, 
-the algorithm incentivizes this arm with a payment high enough
-to guarantee that the next agent pulls it.
-This way the algorithm ensures that each arm is pulled often enough.
+unlikely to be pulled
+it incentivizes this arm with a payment high enough
+to guarantee the next agent pulls it.
+This way the algorithm ensures each arm is pulled often enough.
 
@@
 $s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
-\item Based on the current estimates \ArmEV{t}{i'} of all arms'
-attribute vectors, the probability of pulling arm $i$ is less than
-$1/\log(s)$. Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
-  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
-be the probability that arm $i$ will be pulled
+\item 
+The conditional probability of pulling arm $i$ is less than
+$1/\log(s)$ given current estimates \ArmEV{t}{i'} of arms'
+attribute vectors.  In other words, we require
+$\PullProb{t}{i} < 1/\log(s)$ where 
+$\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
+\cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i \pfedit{\mid \ArmEV{t}{i'}\ \forall i'}}$
+is the probability that arm $i$ will be pulled
 by the next (random) agent based on the current estimates. 
-Then, the second criterion for payment-eligibility is that
-$\PullProb{t}{i} < 1/\log(s)$.
 \end{itemize}
@@
 Notice that \PullProb{t}{i} depends on the estimates for \emph{all}
-arms; thus, by pulling some other arm $i'$, an arm $i$ may become
+arms; thus, by pulling another arm $i'$, an arm $i$ may become
 payment-eligible, or cease to be so.

### 2018-02-17 abstract.tex

--- 2018-02-17 abstract.tex
@@
-We consider the problem of incentivized exploration with heterogeneous agents.
+We consider the problem of incentivizing exploration with heterogeneous agents.
 In this problem, bandit arms provide vector-valued outcomes equal to an unknown
-arm-specific attribute vector perturbed by independent normally distributed
-noise.  Agents arrive sequentially and choose arms to pull based on their own
-private and heterogeneous linear utility function over attributes and estimates
-of the arms' attribute vectors derived from observations of other agents' past
-pulls.  Agents are myopic and selfish and thus would choose the arm with
-maximal estimated utility, except for an incentive payment that a principal may
-offer to encourage agents to explore underplayed arms.  The principle seeks to
-minimize the expected cumulative regret incurred by agents relative to their
-best arms, while also making a small expected cumulative payment.  We propose
-an algorithm that incentivizes arms played infrequently in the
+arm-specific attribute vector,
+perturbed by independent normally distributed noise.
+Agents arrive sequentially and choose arms to pull based on their own
+private and heterogeneous linear utility functions over attributes
+and the estimates of the arms' attribute vectors derived from
+observations of other agents' past pulls.
+Agents are myopic and selfish and thus would choose the arm with
+maximum estimated utility.
+A principal, knowing only the distribution from which agents'
+preferences are drawn, but not the specific draws,
+can offer incentive payments for pulling specific arms
+in order to encourage agents to explore underplayed arms.
+The principal seeks to minimize the total expected cumulative regret
+incurred by agents relative to their best arms,
+while also making a small expected cumulative payment.
+
+We propose an algorithm that incentivizes arms played infrequently in the
 past whose probability of being played in the next round would be small
-without incentives.  Under the assumption that each arm is preferred by at
-least a fraction $p>0$ of agents, we show this algorithm achieves expected
-cumulative regret of $O(N\exp(2/p) + N \log(T)^3)$ using expected cumulative
-payments of $O(N^2 \exp(2/p))$.  If $p$ is known or the distribution over agent
-preferences is discrete, the term $\exp(2/p)$ can be eliminated.  In these
-cases, the bound on payment improves to $O(N^2 / p^{5/2})$.  The bound on
-regret improves to $O(N/p^4 + N^2/p^2 + N \log(T)^3 / p)$ for known $p$ and to
-$O(N/p^4 + N^2/p^2)$ for discrete preference distributions.  Regret and
-payments that are both constant in $T$ for discrete preferences stands
-in contrast to the $\log(T)$ dependence on regret in standard multi-armed bandit
-problems, and arises because heterogeneity in agent preferences allows
-exploitation of arms to also explore fully.
+without incentives.
+Under the assumption that each arm is preferred by at
+least a fraction $\MinProb > 0$ of agents,
+we show that this algorithm achieves expected
+cumulative regret of $O (\ARMNUM \e^{2/\MinProb} + \ARMNUM \log^3(T))$,
+using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
+If \MinProb is known or the distribution over agent
+preferences is discrete,
+the exponential term $\e^{2/\MinProb}$ can be replaced with suitable
+polynomials in \ARMNUM and $1/\MinProb$.
+For discrete preferences, the regret dependence on $T$ can be
+eliminated entirely, giving constant (depending only polynomially on
+\ARMNUM and $1/\MinProb$) expected regret and payments.
+This constant regret stands in contrast to the $\Theta(\log(T))$ dependence of
+regret in standard multi-armed bandit problems.
+It arises because even unobserved heterogeneity in agent preferences
+allows exploitation of arms to also explore arms fully;
+succinctly, heterogeneity provides free exploration.

### 2018-02-17 algorithm.tex
more minor edits to section 4

@@
 
+\pfcomment{I deleted here we now define $q(z)$ in section 2}
+\pfdelete{
 To capture the probability masses of problematic agents,
@@
 arm is at most $\delta$.
+}
 \dkcomment{We should stress somewhere that we assume that actual ties
@@
 
-We begin by bounding the length of any phase, which will be useful to bound
-the cumulative regret of the early rounds
-(before tail bounds have kicked in). We prove Lemma~\ref{lem:phase-length} in the Appendix~\ref{sec:lemma4-proof}.
+We begin by bounding the length of any phase, which will support bounding
+the regret of early rounds
+(before tail bounds have kicked in). We prove Lemma~\ref{lem:phase-length} in Appendix~\ref{sec:lemma4-proof}.
 

### 2018-02-17 algorithm_general.tex
Broke algorithm.tex up into 4 files.

--- 2018-02-17 algorithm.tex
@@
-\section{Main Algorithm and Analysis}
-\label{sec:ub}
-The algorithm achieving the claimed bounds of
-Theorems~\ref{rst:budget} and~\ref{rst:regret} is simple.
-It mostly allows agents to exploit, but when an arm is sufficiently
-unlikely to be pulled
-it incentivizes this arm with a payment high enough
-to guarantee the next agent pulls it.
-This way the algorithm ensures each arm is pulled often enough.
-
-More precisely, the algorithm divides time into \emph{phases}
-$s = 1, 2, 3, \ldots$.
-Phase $s$ starts when each arm has been pulled at least $s$ times.
-We indicate the start time of phase $s$ by $t_s$. An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
-if both of the following hold:
-
-\begin{itemize}
-\item $i$ has been pulled at most%
-\footnote{in fact: exactly, since the algorithm entered phase $s$}
-$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
-\item 
-The conditional probability of pulling arm $i$ is less than
-$1/\log(s)$ given current estimates \ArmEV{t}{i'} of arms'
-attribute vectors.  In other words, we require
-$\PullProb{t}{i} < 1/\log(s)$ where 
-$\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
-\cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i \pfedit{\mid \ArmEV{t}{i'}\ \forall i'}}$
-is the probability that arm $i$ will be pulled
-by the next (random) agent based on the current estimates. 
-\end{itemize}
-
-When multiple arms are payment-eligible, the algorithm picks one arbitarily to incentivize.
-When the algorithm decides to incentivize an arm $i$,
-it offers ``whatever it takes,'' i.e., offers a payment of
-$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$.
-The maximum for \AgV is taken over the support of \AgentDist;
-recall that we assumed this support to be compact.
-The payment \Pay{t}{i} may appear unnecessarily high.
-Indeed, it suffices to
-incentivize only a $1/\log(s)$ fraction of the agents,
-and our bounds also hold for an alternate version of our algorithm that 
-offers payment
-$\Pay{t}{i} = \min \Set{c \geq 0}{%
-\Prob[\AgV \sim \AgentDist]{c + \AgV \cdot \ArmEV{t}{i} \geq \max_{i'\ne i} \AgV \cdot \ArmEV{t}{i'}} \ge 1/\log(s)}$.
-However, we focus on the higher payments for simplicity of presentation.
-
-Notice that \PullProb{t}{i} depends on the estimates for \emph{all}
-arms; thus, by pulling another arm $i'$, an arm $i$ may become
-payment-eligible, or cease to be so.
-Algorithm~\ref{alg:basic-incentivizing} gives the full details.
-
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration \label{alg:basic-incentivizing}}
-\begin{algorithmic}
-\STATE Set the current phase number $s = 1$.
-\COMMENT{Each arm is pulled once initially ``for free''.}
-\FOR{time steps $t = 1, 2, 3, \ldots$}
-\IF{$\NumPull{t}{i} \geq s+1$ for all arms $i$}
-\STATE Increment the phase $s = s + 1$.
-\ENDIF
-\IF{there is a payment-eligible arm $i$}
-\STATE Let $i$ be an arbitary payment-eligible arm.
-\STATE Offer payment
-$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$
-for pulling arm $i$
-(and payment 0 for all other arms).
-\ELSE
-\STATE Let agent $t$ play myopically, i.e., offer payments 0 for all arms.
-\ENDIF
-\ENDFOR
-\end{algorithmic}
-\end{algorithm}
-
-The high-level idea in the proofs of our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret},
-is the following.
-Because the algorithm ensures that each arm is pulled
-``frequently enough,''
-the estimates \ArmEV{t}{i} become gradually more accurate in the
-phase number $s$.
-Thus, the fraction of agents who misidentify their best arm decreases.
-Because for each arm, enough agents have a true preference for this
-arm, once the arms' attribute vectors are learned well enough,
-the algorithm will not need to incentivize any more,
-resulting in a payment bound independent of $T$.
-Similarly, the regret will decrease, and mostly accrue
-due to ``problematic'' agents who are nearly tied in their preferences
-between their top two arm choices.
-The detailed analysis following this outline is somewhat subtle, though,
-due to the dependencies between the agents' arm pulls and the
-estimates which in turn are based on past arm pulls.
-We begin with several technical lemmas that are used for both the
-payment and regret bounds.
-
-\pfcomment{I deleted here we now define $q(z)$ in section 2}
-\pfdelete{
-To capture the probability masses of problematic agents,
-we define the quantity
-$\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
-\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
-to be the total probability mass (across all arms) of agents
-whose (actual) preference for their best arm over their second-best
-arm is at most $\delta$.
-}
-\dkcomment{We should stress somewhere that we assume that actual ties
-  have measure 0.}
-
-To formally reason about the event that the estimates of arms'
-attributes vectors are accurate enough --- or fail to be so ---
-we define the events
-$\AccE{t}{i}{j}{x} := [|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq x]$
-that attribute $j$ of arm $i$ at time $t$ is estimated to
-within accuracy $x$ or better.
-Then, 
-$\AccEU{t}{x} = \bigcap_{i,j} \AccE{t}{i}{j}{x}$
-is the event that at time $t$, all arm attribute
-estimates are accurate to within $x$ simultaneously.
-We will then show that for suitable choices of $t, x$,
-the events \AccE{t}{i}{j}{x}
-(and hence, by union bound, \AccEU{t}{x})
-have high probability,
-and that when they do, myopic agents do not make large mistakes.
-
-%We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.
-
 \subsection{General Lemmas}
@@
 \end{lemma}
-
-\subsection{Bounding the Total Payment}
-
-As a first step towards bound the total payment (and also regret),
-we show that for sufficiently late phases,
-under the event \AccEU{t}{x} for suitably small $x$,
-the algorithm does not offer any payments. We prove Lemma~\ref{lem:no-incentives} in the Appendix~\ref{sec:lemma8-proof}.
-
-\begin{lemma} \label{lem:no-incentives}
-Fix an arm $i$.
-Let $s \geq \exp(2/\MinProb)$, and let $\tau_s$ be the (random)
-time when arm $i$ is pulled for the \Kth{s} time.
-Under \AccEU{\tau_s}{\frac{p}{4\Diam d \TieDensity}},
-this pull of arm $i$ is not incentivized.
-\end{lemma}
-
-Towards bounding the algorithm's total payment, we now bound the
-\emph{number} of rounds in which the algorithm makes a payment by a
-constant.
-This bound also turns out to be useful for bounding the total regret.
-
-\begin{lemma} \label{lem:numP}
-The expected number of time steps in which
-Algorithm~\ref{alg:basic-incentivizing}
-makes any payment is at most $O\left( N\exp\left(\frac{2}{p}\right) \right)$.
-\end{lemma}
-
-\begin{proof}
-We partition phases into early and late phases.
-For each of the early phases,
-we crudely bound the number of payments by \ARMNUM,
-using that each arm is incentivized at most once per phase.
-For later phases,
-we use Lemma~\ref{lem:no-incentives},
-which rules out any incentives unless large misestimates of the arm
-locations occur, which is exponentially unlikely by 
-Lemma~\ref{lem:round-prob}.
-
-To make this intuition precise, we set
-$\delta = \frac{\MinProb}{2 \TieDensity}$,
-and $x = x' = \frac{\delta}{2 \Diam d}$
-(which is independent of the phase number $s$).
-The cutoff point between early and late phases is now set to
-$\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3}, \exp(\frac{2}{\MinProb}))$.
-We will verify below that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
-\leq \frac{n x}{2 \sigma}$
-for all $n \geq \max(2, \frac{30 \sigma^3}{x^3})$.
-
-Fix an arm $i$, and consider the \Kth{s} pull of an arm $i$,
-for $s \geq \EvenLaterPhase$.
-If this pull occurs before phase $s$, it was definitely not incentivized.
-So we condition on the pull occurring in phase $s$,
-and let $\tau_s$ be the time step when this pull occurred;
-notice that this means that this must be the first pull of arm $i$ in
-phase $s$.
-
-By Lemma~\ref{lem:round-prob} (with our choice of $x = x'$),
-and a union bound over all $i,j$, we bound the probability
-$\Prob{\AccEU{\tau_s}{x}}
-\geq 1 - 24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$.
-And by Lemma~\ref{lem:no-incentives},
-under the event ${\mathcal E}_{\tau_s}(x)$,
-arm $i$ is not payment-eligible.
-
-Thus, for any $s \geq \EvenLaterPhase$,
-the \Kth{s} pull of arm $i$ is incentivized  
-with probability at most
-$24 \ARMNUM d \cdot \exp \left(
-  -\frac{1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-\right)$.
-Summing over all arms and phases $s$,
-and adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
-the first \EvenLaterPhase phases, 
-the expected total number of arm incentivizations is at most
-\begin{align*}
-&\ARMNUM \EvenLaterPhase
-  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \nonumber \\
-=& O\left( \max\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp(\frac{2}{p})\right)
-  + \frac{\ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right) \nonumber  \\
-=& O\left( N\exp\left(\frac{2}{p}\right) \right).
-\end{align*}
-
-It remains to show that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
-\leq \frac{n x}{2 \sigma}$
-for all $n \geq \max(2, \frac{30 \sigma^3}{x^3}$.
-We first use that $\sqrt{\cdot}$ is sublinear to bound
-\[
-  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
-\; \leq \; \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1)} + \frac{n x}{4 \sigma}
-\]
-(here we use the fact $\sqrt{n} \leq n$).
-Next, we show that
-$\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} \leq \frac{n x}{4 \sigma}$;
-then, adding the two terms gives the desired bound.
-
-By squaring the claimed statement and rearranging,
-it is equivalent to show that
-$\frac{n}{\log(\log_{1.1}(n)+1)} \geq \frac{9.6\sigma^2}{x^2}$.
-Because $n \geq 2$,
-a numerical calculation and derivative test shows that
-$\frac{n}{\log(\log_{1.1}(n)+1)} \geq n^{2/3}$,
-and because $n \geq \frac{30 \sigma^3}{x^3}$,
-we get that
-$n^{2/3} \geq \frac{9.6 \sigma^2}{x^2}$, completing the proof.
-
-\end{proof}
-
-It would be desirable to simply identify a constant upper bound on the
-payment made each time.
-Unfortunately, while the agent types are drawn from a bounded support,
-the noise in arm locations is not;
-hence, with small probability, arm locations may be grossly
-misestimated, resulting in high incentive payments.
-As a result, the actual analysis of the total payment is significantly more
-intricate;
-the proof of Theorem~\ref{rst:budget} is given in
-Appendix~\ref{sec:payment-proof}.
-
-\subsection{Bounding the Total Regret}
-In bounding the total regret, because agents' types are from a compact
-set by Assumption~\ref{A2}, the maximum regret in any one round is
-bounded by a constant.
-We use $\MAXR = \max_{\AgV, i,i'} \AgV \cdot (\ArmV{i} - \ArmV{i'})$
-to denote this constant upper bound on the maximum regret that can be
-incurred in any one time step.
-
-\begin{extraproof}{Theorem~\ref{rst:regret}}
-Regret can arise in two ways:
-(1) an agent was incentivized to pull a suboptimal arm, or
-(2) an agent myopically pulled a suboptimal arm.
-By Lemma~\ref{lem:numP}, Algorithm~\ref{alg:basic-incentivizing}
-incentivizes agents at most 
-$O\left( N\exp\left(\frac{2}{p}\right) \right)$
-times in expectation, each time causing regret at most \MAXR,
-for a total expected regret of at most
-$O\left(\MAXR\cdot N\exp\left(\frac{2}{p}\right) \right)$.
-For the rest of the proof, we focus on the regret incurred when agents
-pull arms myopically and make mistakes.
-
-We distinguish between agents incurring large regret
-(which requires severe misestimates of arm locations;
-such misestimated are exponentially unlikely to occur), 
-and agents incurring small positive regret,
-which requires these agents to be almost tied in their preference for
-the best arm.
-To be more precise, we will define (with foresight) a phase-dependent
-cutoff
-$g(s) = \sqrt{\frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}}$,
-and consider a regret exceeding $g(s)$ large.
-
-We first consider agents \AgV incurring positive regret less than $g(s)$.
-The second-best arm \Second{\AgV} of such an agent \AgV must satisfy
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(s)$.
-By Assumption~\ref{A1},
-%Lemma~\ref{lem:sdelta},
-the total measure of such agents
-is $\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$,
-and each incurs regret at most $g(s)$.
-Summing over all time steps,
-and using Lemma~\ref{lem:phase-length} to bound the number of time
-steps in phase $s$, 
-the expected total regret from such agents is at most
-\begin{align}
-\Expect{\sum_{s=1}^{T} \sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)}
-& \leq \sum_{s=1}^{T} \TieDensity \cdot g^2(s) \ARMNUM \log(s).
-\label{equ:small_regret_bound}
-\end{align}
-
-We next bound the regret incurred in time steps with large regret.
-Let the random variable $t_s$ be the final time step in phase $s$,
-for each $s$. Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
-time step in the \Kth{s} phase,
-with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
-i.e., $k > t_{s}-t_{s-1}$.
-By Lemma~\ref{lem:right-choice},
-under \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}}, no agent at time $t$ will incur
-regret more than $g(s)$.
-
-To bound the probability of \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}},
-we use Lemma~\ref{lem:round-prob}
-(with $x_s = x'_s = \frac{g(s)}{2 \Diam d}$
-and a stopping time of $\tau_s^k$).
-We first verify that this choice of $x_s, x'_s$
-satisfies the assumption of Lemma~\ref{lem:round-prob} for all
-$s \geq 2$,
-i.e., that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
-\leq \frac{n x_n}{2 \sigma}$
-for all $n \geq 2$.
-Substituting that
-$x_n = \frac{g(n)}{2 \Diam d} = \sqrt{\frac{32\log(T) \cdot \sigma^2}{1.8 n}}$,
-the left-hand side is
-
-\[
-  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 \log T}{1.8}}
-  \; \leq \;
-  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 n \log T}{1.8}},
-\]
-while the right-hand side is $\sqrt{\frac{8 n \log(T)}{1.8}}$.
-Squaring both sides and canceling out common terms,
-the desired inequality is equivalent to
-$\frac{50}{9} \log T \geq \log(\log_{1.1}(n) + 1)$.
-Because $n \leq T$, it is sufficient to show that
-$\frac{50}{9} \log T \geq \log(\log_{1.1}(n) + 1)$,
-which can be verified by numerical calculation for $T=2$ and a
-derivative test.
-
-Now, by Lemma~\ref{lem:round-prob} and a union bound over all arms $i$
-and attributes $j$, we get that 
-\begin{align*}
-\Prob{\AccEU{\tau_s^k}{x_s}}
-& \leq 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16 \sigma^2} \right)
-\; = \; \frac{24 \ARMNUM d}{T^2}.
-\end{align*}
-
-In the low-probability event, we simply 
-bound the maximum regret by \MAXR.
-Now, applying Lemma~\ref{lem:phase-length},
-the total expected regret from large-regret steps is at most
-
-\begin{align*}
-\sum_{s = 1}^T \sum_{t=t_s}^{t_{s+1}-1}
-  \Prob{\mbox{incur regret exceeding } g(s) \mbox{ at step } t} \cdot \MAXR
-& \leq
- \sum_{s = 1}^T \frac{24 \ARMNUM d}{T^2} \cdot \MAXR \cdot \ARMNUM \log(s)
-\\ & \leq 12 \ARMNUM^2 d \MAXR.
-\end{align*}
-
-Adding all three types of regret terms,
-and substituting that 
-$g^2(s) = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
-the cumulative regret up to time $T$ is at most
-
-\begin{align*}
-\lefteqn{
-O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
-+ \ARMNUM^2 \MAXR d
-+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} g^2(s) \log(s) \right)}
-\\ & = 
-O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
-+ \ARMNUM^2 \MAXR d
-+ \ARMNUM \TieDensity \Diam^2 d^2 \sigma^2 \cdot \log^3(T) \right).
-\end{align*}
-\end{extraproof}

### 2018-02-17 algorithm_intro.tex
Broke algorithm.tex up into 4 files.

--- 2018-02-17 algorithm.tex
@@
 %We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.
-
-\subsection{General Lemmas}
-
-% We begin by showing that under our assumptions, the measure of
-% problematic arms cannot be too large.
-
-% \begin{lemma} \label{lem:sdelta}
-% $\AlmostTied{\delta} \leq \TieDensity \cdot \delta$ for all $\delta$.
-% \end{lemma}
-
-% \begin{emptyproof}
-% Using the upper bound from Assumption~\ref{A1}, we can bound
-
-% \begin{align*}
-% \AlmostTied{\delta}
-% & = \sum_{i,i'} \ProbC{\AgV \cdot (\ArmV{i} - \ArmV{i'}) \leq \delta}%
-%     {\AgV \in \FirstTwo{i}{i'}}
-%   \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}\\
-% & \leq \sum_{i,i'} \TieDensity \cdot \delta
-%     \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}
-% \; = \; \TieDensity \cdot \delta. \QED
-% \end{align*}
-% \end{emptyproof}
-
-We begin by bounding the length of any phase, which will support bounding
-the regret of early rounds
-(before tail bounds have kicked in). We prove Lemma~\ref{lem:phase-length} in Appendix~\ref{sec:lemma4-proof}.
-
-\begin{lemma} \label{lem:phase-length}
-For any $s\geq 3$, the expected length of phase $s$ is at most
-$\ARMNUM \cdot \log(s)$ time steps.
-\end{lemma}
-
-We now state the key technical lemma captures the intuition that
-the estimates of the arms' attribute vectors become
-more accurate with increasing phases $s$.
-
-\begin{lemma} \label{lem:round-prob}
-Recall that $\sigma$ is the standard deviation of the Gaussian noise.
-Let \LatePhase be a phase cutoff, 
-and let $x_n, x'_n > 0$ be functions satisfying that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
-\leq \frac{n x'_n}{2 \sigma}$,
-for all $n \geq \LatePhase$.
-Let $\tau_s$ be a stopping time
-(which may depend on the entire past history)
-which is almost surely in phase $s$,
-i.e., satisfying $\tau \in [t_s, t_{s+1})$ almost surely.
-
-Then, for any arm $i$, attribute $j$, and phase $s \geq \LatePhase$,
-we have that
-$\Prob{\AccE{\tau_s}{i}{j}{x'_s}}
-\geq 1 - 24 \exp\left(-\frac{1.8 s x_s^2}{16 \sigma^2} \right)$.
-\end{lemma}
-
-The proof of Lemma~\ref{lem:round-prob} is based on an adaptive
-concentration inequality due to \cite{zhao2016adaptive},
-given as Lemma~\ref{lem:ACI-inequality}.
-
-\begin{lemma}[Corollary 1 of \cite{zhao2016adaptive}]
-\label{lem:ACI-inequality}
-Let $X_i$ be zero-mean $1/2$-subgaussian random variables,
-and $\SET{S_n = \sum_{i=1}^n X_i, n \geq 1}$ the corresponding random walk.
-Let $J$ be any stopping time with respect to $\SET{X_1, X_2, \ldots}$.
-(We allow $J$ to take the value $\infty$,
-defining $\Prob{J = \infty} = 1 - \lim_{n \to \infty} \Prob{J \leq n}$.)
-Define 
-\begin{align*}
-g(n) & = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b}.
-\end{align*}
-Then, 
-\begin{align*}
-\Prob{J < \infty \mbox{ and } S_J \geq g(J)} \leq 12 \e^{-1.8 b}.
-\end{align*}
-\end{lemma}
-
-We leave the proof of Lemma~\ref{lem:round-prob} in the Appendix~\ref{sec:lemma5-proof}. Next, we show the complementary part:
-when \AccEU{t}{x} happens, no myopic agent incurs large regret. We prove Lemma~\ref{lem:right-choice} in the Appendix~\ref{sec:lemma7-proof}.
-
-\begin{lemma} \label{lem:right-choice}
-Let $x > 0$ be arbitrary.
-When \AccEU{t}{x} happens,
-no agent \AgV will pull a highly suboptimal arm, i.e., an arm $i$ with 
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
-\end{lemma}
-
-\subsection{Bounding the Total Payment}
-
-As a first step towards bound the total payment (and also regret),
-we show that for sufficiently late phases,
-under the event \AccEU{t}{x} for suitably small $x$,
-the algorithm does not offer any payments. We prove Lemma~\ref{lem:no-incentives} in the Appendix~\ref{sec:lemma8-proof}.
-
-\begin{lemma} \label{lem:no-incentives}
-Fix an arm $i$.
-Let $s \geq \exp(2/\MinProb)$, and let $\tau_s$ be the (random)
-time when arm $i$ is pulled for the \Kth{s} time.
-Under \AccEU{\tau_s}{\frac{p}{4\Diam d \TieDensity}},
-this pull of arm $i$ is not incentivized.
-\end{lemma}
-
-Towards bounding the algorithm's total payment, we now bound the
-\emph{number} of rounds in which the algorithm makes a payment by a
-constant.
-This bound also turns out to be useful for bounding the total regret.
-
-\begin{lemma} \label{lem:numP}
-The expected number of time steps in which
-Algorithm~\ref{alg:basic-incentivizing}
-makes any payment is at most $O\left( N\exp\left(\frac{2}{p}\right) \right)$.
-\end{lemma}
-
-\begin{proof}
-We partition phases into early and late phases.
-For each of the early phases,
-we crudely bound the number of payments by \ARMNUM,
-using that each arm is incentivized at most once per phase.
-For later phases,
-we use Lemma~\ref{lem:no-incentives},
-which rules out any incentives unless large misestimates of the arm
-locations occur, which is exponentially unlikely by 
-Lemma~\ref{lem:round-prob}.
-
-To make this intuition precise, we set
-$\delta = \frac{\MinProb}{2 \TieDensity}$,
-and $x = x' = \frac{\delta}{2 \Diam d}$
-(which is independent of the phase number $s$).
-The cutoff point between early and late phases is now set to
-$\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3}, \exp(\frac{2}{\MinProb}))$.
-We will verify below that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
-\leq \frac{n x}{2 \sigma}$
-for all $n \geq \max(2, \frac{30 \sigma^3}{x^3})$.
-
-Fix an arm $i$, and consider the \Kth{s} pull of an arm $i$,
-for $s \geq \EvenLaterPhase$.
-If this pull occurs before phase $s$, it was definitely not incentivized.
-So we condition on the pull occurring in phase $s$,
-and let $\tau_s$ be the time step when this pull occurred;
-notice that this means that this must be the first pull of arm $i$ in
-phase $s$.
-
-By Lemma~\ref{lem:round-prob} (with our choice of $x = x'$),
-and a union bound over all $i,j$, we bound the probability
-$\Prob{\AccEU{\tau_s}{x}}
-\geq 1 - 24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$.
-And by Lemma~\ref{lem:no-incentives},
-under the event ${\mathcal E}_{\tau_s}(x)$,
-arm $i$ is not payment-eligible.
-
-Thus, for any $s \geq \EvenLaterPhase$,
-the \Kth{s} pull of arm $i$ is incentivized  
-with probability at most
-$24 \ARMNUM d \cdot \exp \left(
-  -\frac{1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-\right)$.
-Summing over all arms and phases $s$,
-and adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
-the first \EvenLaterPhase phases, 
-the expected total number of arm incentivizations is at most
-\begin{align*}
-&\ARMNUM \EvenLaterPhase
-  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \nonumber \\
-=& O\left( \max\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp(\frac{2}{p})\right)
-  + \frac{\ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right) \nonumber  \\
-=& O\left( N\exp\left(\frac{2}{p}\right) \right).
-\end{align*}
-
-It remains to show that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
-\leq \frac{n x}{2 \sigma}$
-for all $n \geq \max(2, \frac{30 \sigma^3}{x^3}$.
-We first use that $\sqrt{\cdot}$ is sublinear to bound
-\[
-  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
-\; \leq \; \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1)} + \frac{n x}{4 \sigma}
-\]
-(here we use the fact $\sqrt{n} \leq n$).
-Next, we show that
-$\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} \leq \frac{n x}{4 \sigma}$;
-then, adding the two terms gives the desired bound.
-
-By squaring the claimed statement and rearranging,
-it is equivalent to show that
-$\frac{n}{\log(\log_{1.1}(n)+1)} \geq \frac{9.6\sigma^2}{x^2}$.
-Because $n \geq 2$,
-a numerical calculation and derivative test shows that
-$\frac{n}{\log(\log_{1.1}(n)+1)} \geq n^{2/3}$,
-and because $n \geq \frac{30 \sigma^3}{x^3}$,
-we get that
-$n^{2/3} \geq \frac{9.6 \sigma^2}{x^2}$, completing the proof.
-
-\end{proof}
-
-It would be desirable to simply identify a constant upper bound on the
-payment made each time.
-Unfortunately, while the agent types are drawn from a bounded support,
-the noise in arm locations is not;
-hence, with small probability, arm locations may be grossly
-misestimated, resulting in high incentive payments.
-As a result, the actual analysis of the total payment is significantly more
-intricate;
-the proof of Theorem~\ref{rst:budget} is given in
-Appendix~\ref{sec:payment-proof}.
-
-\subsection{Bounding the Total Regret}
-In bounding the total regret, because agents' types are from a compact
-set by Assumption~\ref{A2}, the maximum regret in any one round is
-bounded by a constant.
-We use $\MAXR = \max_{\AgV, i,i'} \AgV \cdot (\ArmV{i} - \ArmV{i'})$
-to denote this constant upper bound on the maximum regret that can be
-incurred in any one time step.
-
-\begin{extraproof}{Theorem~\ref{rst:regret}}
-Regret can arise in two ways:
-(1) an agent was incentivized to pull a suboptimal arm, or
-(2) an agent myopically pulled a suboptimal arm.
-By Lemma~\ref{lem:numP}, Algorithm~\ref{alg:basic-incentivizing}
-incentivizes agents at most 
-$O\left( N\exp\left(\frac{2}{p}\right) \right)$
-times in expectation, each time causing regret at most \MAXR,
-for a total expected regret of at most
-$O\left(\MAXR\cdot N\exp\left(\frac{2}{p}\right) \right)$.
-For the rest of the proof, we focus on the regret incurred when agents
-pull arms myopically and make mistakes.
-
-We distinguish between agents incurring large regret
-(which requires severe misestimates of arm locations;
-such misestimated are exponentially unlikely to occur), 
-and agents incurring small positive regret,
-which requires these agents to be almost tied in their preference for
-the best arm.
-To be more precise, we will define (with foresight) a phase-dependent
-cutoff
-$g(s) = \sqrt{\frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}}$,
-and consider a regret exceeding $g(s)$ large.
-
-We first consider agents \AgV incurring positive regret less than $g(s)$.
-The second-best arm \Second{\AgV} of such an agent \AgV must satisfy
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(s)$.
-By Assumption~\ref{A1},
-%Lemma~\ref{lem:sdelta},
-the total measure of such agents
-is $\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$,
-and each incurs regret at most $g(s)$.
-Summing over all time steps,
-and using Lemma~\ref{lem:phase-length} to bound the number of time
-steps in phase $s$, 
-the expected total regret from such agents is at most
-\begin{align}
-\Expect{\sum_{s=1}^{T} \sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)}
-& \leq \sum_{s=1}^{T} \TieDensity \cdot g^2(s) \ARMNUM \log(s).
-\label{equ:small_regret_bound}
-\end{align}
-
-We next bound the regret incurred in time steps with large regret.
-Let the random variable $t_s$ be the final time step in phase $s$,
-for each $s$. Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
-time step in the \Kth{s} phase,
-with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
-i.e., $k > t_{s}-t_{s-1}$.
-By Lemma~\ref{lem:right-choice},
-under \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}}, no agent at time $t$ will incur
-regret more than $g(s)$.
-
-To bound the probability of \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}},
-we use Lemma~\ref{lem:round-prob}
-(with $x_s = x'_s = \frac{g(s)}{2 \Diam d}$
-and a stopping time of $\tau_s^k$).
-We first verify that this choice of $x_s, x'_s$
-satisfies the assumption of Lemma~\ref{lem:round-prob} for all
-$s \geq 2$,
-i.e., that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
-\leq \frac{n x_n}{2 \sigma}$
-for all $n \geq 2$.
-Substituting that
-$x_n = \frac{g(n)}{2 \Diam d} = \sqrt{\frac{32\log(T) \cdot \sigma^2}{1.8 n}}$,
-the left-hand side is
-
-\[
-  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 \log T}{1.8}}
-  \; \leq \;
-  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 n \log T}{1.8}},
-\]
-while the right-hand side is $\sqrt{\frac{8 n \log(T)}{1.8}}$.
-Squaring both sides and canceling out common terms,
-the desired inequality is equivalent to
-$\frac{50}{9} \log T \geq \log(\log_{1.1}(n) + 1)$.
-Because $n \leq T$, it is sufficient to show that
-$\frac{50}{9} \log T \geq \log(\log_{1.1}(n) + 1)$,
-which can be verified by numerical calculation for $T=2$ and a
-derivative test.
-
-Now, by Lemma~\ref{lem:round-prob} and a union bound over all arms $i$
-and attributes $j$, we get that 
-\begin{align*}
-\Prob{\AccEU{\tau_s^k}{x_s}}
-& \leq 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16 \sigma^2} \right)
-\; = \; \frac{24 \ARMNUM d}{T^2}.
-\end{align*}
-
-In the low-probability event, we simply 
-bound the maximum regret by \MAXR.
-Now, applying Lemma~\ref{lem:phase-length},
-the total expected regret from large-regret steps is at most
-
-\begin{align*}
-\sum_{s = 1}^T \sum_{t=t_s}^{t_{s+1}-1}
-  \Prob{\mbox{incur regret exceeding } g(s) \mbox{ at step } t} \cdot \MAXR
-& \leq
- \sum_{s = 1}^T \frac{24 \ARMNUM d}{T^2} \cdot \MAXR \cdot \ARMNUM \log(s)
-\\ & \leq 12 \ARMNUM^2 d \MAXR.
-\end{align*}
-
-Adding all three types of regret terms,
-and substituting that 
-$g^2(s) = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
-the cumulative regret up to time $T$ is at most
-
-\begin{align*}
-\lefteqn{
-O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
-+ \ARMNUM^2 \MAXR d
-+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} g^2(s) \log(s) \right)}
-\\ & = 
-O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
-+ \ARMNUM^2 \MAXR d
-+ \ARMNUM \TieDensity \Diam^2 d^2 \sigma^2 \cdot \log^3(T) \right).
-\end{align*}
-\end{extraproof}

### 2018-02-17 algorithm_payment.tex

--- 2018-02-17 algorithm.tex
@@
-\section{Main Algorithm and Analysis}
-\label{sec:ub}
-The algorithm achieving the claimed bounds of
-Theorems~\ref{rst:budget} and~\ref{rst:regret} is simple.
-It mostly allows agents to exploit, but when an arm is sufficiently
-unlikely to be pulled
-it incentivizes this arm with a payment high enough
-to guarantee the next agent pulls it.
-This way the algorithm ensures each arm is pulled often enough.
-
-More precisely, the algorithm divides time into \emph{phases}
-$s = 1, 2, 3, \ldots$.
-Phase $s$ starts when each arm has been pulled at least $s$ times.
-We indicate the start time of phase $s$ by $t_s$. An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
-if both of the following hold:
-
-\begin{itemize}
-\item $i$ has been pulled at most%
-\footnote{in fact: exactly, since the algorithm entered phase $s$}
-$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
-\item 
-The conditional probability of pulling arm $i$ is less than
-$1/\log(s)$ given current estimates \ArmEV{t}{i'} of arms'
-attribute vectors.  In other words, we require
-$\PullProb{t}{i} < 1/\log(s)$ where 
-$\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
-\cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i \pfedit{\mid \ArmEV{t}{i'}\ \forall i'}}$
-is the probability that arm $i$ will be pulled
-by the next (random) agent based on the current estimates. 
-\end{itemize}
-
-When multiple arms are payment-eligible, the algorithm picks one arbitarily to incentivize.
-When the algorithm decides to incentivize an arm $i$,
-it offers ``whatever it takes,'' i.e., offers a payment of
-$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$.
-The maximum for \AgV is taken over the support of \AgentDist;
-recall that we assumed this support to be compact.
-The payment \Pay{t}{i} may appear unnecessarily high.
-Indeed, it suffices to
-incentivize only a $1/\log(s)$ fraction of the agents,
-and our bounds also hold for an alternate version of our algorithm that 
-offers payment
-$\Pay{t}{i} = \min \Set{c \geq 0}{%
-\Prob[\AgV \sim \AgentDist]{c + \AgV \cdot \ArmEV{t}{i} \geq \max_{i'\ne i} \AgV \cdot \ArmEV{t}{i'}} \ge 1/\log(s)}$.
-However, we focus on the higher payments for simplicity of presentation.
-
-Notice that \PullProb{t}{i} depends on the estimates for \emph{all}
-arms; thus, by pulling another arm $i'$, an arm $i$ may become
-payment-eligible, or cease to be so.
-Algorithm~\ref{alg:basic-incentivizing} gives the full details.
-
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration \label{alg:basic-incentivizing}}
-\begin{algorithmic}
-\STATE Set the current phase number $s = 1$.
-\COMMENT{Each arm is pulled once initially ``for free''.}
-\FOR{time steps $t = 1, 2, 3, \ldots$}
-\IF{$\NumPull{t}{i} \geq s+1$ for all arms $i$}
-\STATE Increment the phase $s = s + 1$.
-\ENDIF
-\IF{there is a payment-eligible arm $i$}
-\STATE Let $i$ be an arbitary payment-eligible arm.
-\STATE Offer payment
-$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$
-for pulling arm $i$
-(and payment 0 for all other arms).
-\ELSE
-\STATE Let agent $t$ play myopically, i.e., offer payments 0 for all arms.
-\ENDIF
-\ENDFOR
-\end{algorithmic}
-\end{algorithm}
-
-The high-level idea in the proofs of our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret},
-is the following.
-Because the algorithm ensures that each arm is pulled
-``frequently enough,''
-the estimates \ArmEV{t}{i} become gradually more accurate in the
-phase number $s$.
-Thus, the fraction of agents who misidentify their best arm decreases.
-Because for each arm, enough agents have a true preference for this
-arm, once the arms' attribute vectors are learned well enough,
-the algorithm will not need to incentivize any more,
-resulting in a payment bound independent of $T$.
-Similarly, the regret will decrease, and mostly accrue
-due to ``problematic'' agents who are nearly tied in their preferences
-between their top two arm choices.
-The detailed analysis following this outline is somewhat subtle, though,
-due to the dependencies between the agents' arm pulls and the
-estimates which in turn are based on past arm pulls.
-We begin with several technical lemmas that are used for both the
-payment and regret bounds.
-
-To capture the probability masses of problematic agents,
-we define the quantity
-$\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
-\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
-to be the total probability mass (across all arms) of agents
-whose (actual) preference for their best arm over their second-best
-arm is at most $\delta$.
-\dkcomment{We should stress somewhere that we assume that actual ties
-  have measure 0.}
-
-To formally reason about the event that the estimates of arms'
-attributes vectors are accurate enough --- or fail to be so ---
-we define the events
-$\AccE{t}{i}{j}{x} := [|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq x]$
-that attribute $j$ of arm $i$ at time $t$ is estimated to
-within accuracy $x$ or better.
-Then, 
-$\AccEU{t}{x} = \bigcap_{i,j} \AccE{t}{i}{j}{x}$
-is the event that at time $t$, all arm attribute
-estimates are accurate to within $x$ simultaneously.
-We will then show that for suitable choices of $t, x$,
-the events \AccE{t}{i}{j}{x}
-(and hence, by union bound, \AccEU{t}{x})
-have high probability,
-and that when they do, myopic agents do not make large mistakes.
-
-%We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.
-
-\subsection{General Lemmas}
-
-% We begin by showing that under our assumptions, the measure of
-% problematic arms cannot be too large.
-
-% \begin{lemma} \label{lem:sdelta}
-% $\AlmostTied{\delta} \leq \TieDensity \cdot \delta$ for all $\delta$.
-% \end{lemma}
-
-% \begin{emptyproof}
-% Using the upper bound from Assumption~\ref{A1}, we can bound
-
-% \begin{align*}
-% \AlmostTied{\delta}
-% & = \sum_{i,i'} \ProbC{\AgV \cdot (\ArmV{i} - \ArmV{i'}) \leq \delta}%
-%     {\AgV \in \FirstTwo{i}{i'}}
-%   \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}\\
-% & \leq \sum_{i,i'} \TieDensity \cdot \delta
-%     \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}
-% \; = \; \TieDensity \cdot \delta. \QED
-% \end{align*}
-% \end{emptyproof}
-
-We begin by bounding the length of any phase, which will be useful to bound
-the cumulative regret of the early rounds
-(before tail bounds have kicked in). We prove Lemma~\ref{lem:phase-length} in the Appendix~\ref{sec:lemma4-proof}.
-
-\begin{lemma} \label{lem:phase-length}
-For any $s\geq 3$, the expected length of phase $s$ is at most
-$\ARMNUM \cdot \log(s)$ time steps.
-\end{lemma}
-
-We now state the key technical lemma captures the intuition that
-the estimates of the arms' attribute vectors become
-more accurate with increasing phases $s$.
-
-\begin{lemma} \label{lem:round-prob}
-Recall that $\sigma$ is the standard deviation of the Gaussian noise.
-Let \LatePhase be a phase cutoff, 
-and let $x_n, x'_n > 0$ be functions satisfying that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
-\leq \frac{n x'_n}{2 \sigma}$,
-for all $n \geq \LatePhase$.
-Let $\tau_s$ be a stopping time
-(which may depend on the entire past history)
-which is almost surely in phase $s$,
-i.e., satisfying $\tau \in [t_s, t_{s+1})$ almost surely.
-
-Then, for any arm $i$, attribute $j$, and phase $s \geq \LatePhase$,
-we have that
-$\Prob{\AccE{\tau_s}{i}{j}{x'_s}}
-\geq 1 - 24 \exp\left(-\frac{1.8 s x_s^2}{16 \sigma^2} \right)$.
-\end{lemma}
-
-The proof of Lemma~\ref{lem:round-prob} is based on an adaptive
-concentration inequality due to \cite{zhao2016adaptive},
-given as Lemma~\ref{lem:ACI-inequality}.
-
-\begin{lemma}[Corollary 1 of \cite{zhao2016adaptive}]
-\label{lem:ACI-inequality}
-Let $X_i$ be zero-mean $1/2$-subgaussian random variables,
-and $\SET{S_n = \sum_{i=1}^n X_i, n \geq 1}$ the corresponding random walk.
-Let $J$ be any stopping time with respect to $\SET{X_1, X_2, \ldots}$.
-(We allow $J$ to take the value $\infty$,
-defining $\Prob{J = \infty} = 1 - \lim_{n \to \infty} \Prob{J \leq n}$.)
-Define 
-\begin{align*}
-g(n) & = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b}.
-\end{align*}
-Then, 
-\begin{align*}
-\Prob{J < \infty \mbox{ and } S_J \geq g(J)} \leq 12 \e^{-1.8 b}.
-\end{align*}
-\end{lemma}
-
-We leave the proof of Lemma~\ref{lem:round-prob} in the Appendix~\ref{sec:lemma5-proof}. Next, we show the complementary part:
-when \AccEU{t}{x} happens, no myopic agent incurs large regret. We prove Lemma~\ref{lem:right-choice} in the Appendix~\ref{sec:lemma7-proof}.
-
-\begin{lemma} \label{lem:right-choice}
-Let $x > 0$ be arbitrary.
-When \AccEU{t}{x} happens,
-no agent \AgV will pull a highly suboptimal arm, i.e., an arm $i$ with 
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
-\end{lemma}
-
 \subsection{Bounding the Total Payment}
@@
 Appendix~\ref{sec:payment-proof}.
-
-\subsection{Bounding the Total Regret}
-In bounding the total regret, because agents' types are from a compact
-set by Assumption~\ref{A2}, the maximum regret in any one round is
-bounded by a constant.
-We use $\MAXR = \max_{\AgV, i,i'} \AgV \cdot (\ArmV{i} - \ArmV{i'})$
-to denote this constant upper bound on the maximum regret that can be
-incurred in any one time step.
-
-\begin{extraproof}{Theorem~\ref{rst:regret}}
-Regret can arise in two ways:
-(1) an agent was incentivized to pull a suboptimal arm, or
-(2) an agent myopically pulled a suboptimal arm.
-By Lemma~\ref{lem:numP}, Algorithm~\ref{alg:basic-incentivizing}
-incentivizes agents at most 
-$O\left( N\exp\left(\frac{2}{p}\right) \right)$
-times in expectation, each time causing regret at most \MAXR,
-for a total expected regret of at most
-$O\left(\MAXR\cdot N\exp\left(\frac{2}{p}\right) \right)$.
-For the rest of the proof, we focus on the regret incurred when agents
-pull arms myopically and make mistakes.
-
-We distinguish between agents incurring large regret
-(which requires severe misestimates of arm locations;
-such misestimated are exponentially unlikely to occur), 
-and agents incurring small positive regret,
-which requires these agents to be almost tied in their preference for
-the best arm.
-To be more precise, we will define (with foresight) a phase-dependent
-cutoff
-$g(s) = \sqrt{\frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}}$,
-and consider a regret exceeding $g(s)$ large.
-
-We first consider agents \AgV incurring positive regret less than $g(s)$.
-The second-best arm \Second{\AgV} of such an agent \AgV must satisfy
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(s)$.
-By Assumption~\ref{A1},
-%Lemma~\ref{lem:sdelta},
-the total measure of such agents
-is $\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$,
-and each incurs regret at most $g(s)$.
-Summing over all time steps,
-and using Lemma~\ref{lem:phase-length} to bound the number of time
-steps in phase $s$, 
-the expected total regret from such agents is at most
-\begin{align}
-\Expect{\sum_{s=1}^{T} \sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)}
-& \leq \sum_{s=1}^{T} \TieDensity \cdot g^2(s) \ARMNUM \log(s).
-\label{equ:small_regret_bound}
-\end{align}
-
-We next bound the regret incurred in time steps with large regret.
-Let the random variable $t_s$ be the final time step in phase $s$,
-for each $s$. Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
-time step in the \Kth{s} phase,
-with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
-i.e., $k > t_{s}-t_{s-1}$.
-By Lemma~\ref{lem:right-choice},
-under \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}}, no agent at time $t$ will incur
-regret more than $g(s)$.
-
-To bound the probability of \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}},
-we use Lemma~\ref{lem:round-prob}
-(with $x_s = x'_s = \frac{g(s)}{2 \Diam d}$
-and a stopping time of $\tau_s^k$).
-We first verify that this choice of $x_s, x'_s$
-satisfies the assumption of Lemma~\ref{lem:round-prob} for all
-$s \geq 2$,
-i.e., that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
-\leq \frac{n x_n}{2 \sigma}$
-for all $n \geq 2$.
-Substituting that
-$x_n = \frac{g(n)}{2 \Diam d} = \sqrt{\frac{32\log(T) \cdot \sigma^2}{1.8 n}}$,
-the left-hand side is
-
-\[
-  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 \log T}{1.8}}
-  \; \leq \;
-  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 n \log T}{1.8}},
-\]
-while the right-hand side is $\sqrt{\frac{8 n \log(T)}{1.8}}$.
-Squaring both sides and canceling out common terms,
-the desired inequality is equivalent to
-$\frac{50}{9} \log T \geq \log(\log_{1.1}(n) + 1)$.
-Because $n \leq T$, it is sufficient to show that
-$\frac{50}{9} \log T \geq \log(\log_{1.1}(n) + 1)$,
-which can be verified by numerical calculation for $T=2$ and a
-derivative test.
-
-Now, by Lemma~\ref{lem:round-prob} and a union bound over all arms $i$
-and attributes $j$, we get that 
-\begin{align*}
-\Prob{\AccEU{\tau_s^k}{x_s}}
-& \leq 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16 \sigma^2} \right)
-\; = \; \frac{24 \ARMNUM d}{T^2}.
-\end{align*}
-
-In the low-probability event, we simply 
-bound the maximum regret by \MAXR.
-Now, applying Lemma~\ref{lem:phase-length},
-the total expected regret from large-regret steps is at most
-
-\begin{align*}
-\sum_{s = 1}^T \sum_{t=t_s}^{t_{s+1}-1}
-  \Prob{\mbox{incur regret exceeding } g(s) \mbox{ at step } t} \cdot \MAXR
-& \leq
- \sum_{s = 1}^T \frac{24 \ARMNUM d}{T^2} \cdot \MAXR \cdot \ARMNUM \log(s)
-\\ & \leq 12 \ARMNUM^2 d \MAXR.
-\end{align*}
-
-Adding all three types of regret terms,
-and substituting that 
-$g^2(s) = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
-the cumulative regret up to time $T$ is at most
-
-\begin{align*}
-\lefteqn{
-O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
-+ \ARMNUM^2 \MAXR d
-+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} g^2(s) \log(s) \right)}
-\\ & = 
-O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
-+ \ARMNUM^2 \MAXR d
-+ \ARMNUM \TieDensity \Diam^2 d^2 \sigma^2 \cdot \log^3(T) \right).
-\end{align*}
-\end{extraproof}

### 2018-02-17 algorithm_regret.tex

--- 2018-02-17 algorithm.tex
@@
-\section{Main Algorithm and Analysis}
-\label{sec:ub}
-The algorithm achieving the claimed bounds of
-Theorems~\ref{rst:budget} and~\ref{rst:regret} is simple.
-It mostly allows agents to exploit, but when an arm is sufficiently
-unlikely to be pulled
-it incentivizes this arm with a payment high enough
-to guarantee the next agent pulls it.
-This way the algorithm ensures each arm is pulled often enough.
-
-More precisely, the algorithm divides time into \emph{phases}
-$s = 1, 2, 3, \ldots$.
-Phase $s$ starts when each arm has been pulled at least $s$ times.
-We indicate the start time of phase $s$ by $t_s$. An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
-if both of the following hold:
-
-\begin{itemize}
-\item $i$ has been pulled at most%
-\footnote{in fact: exactly, since the algorithm entered phase $s$}
-$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
-\item 
-The conditional probability of pulling arm $i$ is less than
-$1/\log(s)$ given current estimates \ArmEV{t}{i'} of arms'
-attribute vectors.  In other words, we require
-$\PullProb{t}{i} < 1/\log(s)$ where 
-$\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
-\cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i \pfedit{\mid \ArmEV{t}{i'}\ \forall i'}}$
-is the probability that arm $i$ will be pulled
-by the next (random) agent based on the current estimates. 
-\end{itemize}
-
-When multiple arms are payment-eligible, the algorithm picks one arbitarily to incentivize.
-When the algorithm decides to incentivize an arm $i$,
-it offers ``whatever it takes,'' i.e., offers a payment of
-$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$.
-The maximum for \AgV is taken over the support of \AgentDist;
-recall that we assumed this support to be compact.
-The payment \Pay{t}{i} may appear unnecessarily high.
-Indeed, it suffices to
-incentivize only a $1/\log(s)$ fraction of the agents,
-and our bounds also hold for an alternate version of our algorithm that 
-offers payment
-$\Pay{t}{i} = \min \Set{c \geq 0}{%
-\Prob[\AgV \sim \AgentDist]{c + \AgV \cdot \ArmEV{t}{i} \geq \max_{i'\ne i} \AgV \cdot \ArmEV{t}{i'}} \ge 1/\log(s)}$.
-However, we focus on the higher payments for simplicity of presentation.
-
-Notice that \PullProb{t}{i} depends on the estimates for \emph{all}
-arms; thus, by pulling another arm $i'$, an arm $i$ may become
-payment-eligible, or cease to be so.
-Algorithm~\ref{alg:basic-incentivizing} gives the full details.
-
-\begin{algorithm}
-\caption{Algorithm: Incentivizing Exploration \label{alg:basic-incentivizing}}
-\begin{algorithmic}
-\STATE Set the current phase number $s = 1$.
-\COMMENT{Each arm is pulled once initially ``for free''.}
-\FOR{time steps $t = 1, 2, 3, \ldots$}
-\IF{$\NumPull{t}{i} \geq s+1$ for all arms $i$}
-\STATE Increment the phase $s = s + 1$.
-\ENDIF
-\IF{there is a payment-eligible arm $i$}
-\STATE Let $i$ be an arbitary payment-eligible arm.
-\STATE Offer payment
-$\Pay{t}{i} = \max_{\AgV,i'} \AgV \cdot (\ArmEV{t}{i'} - \ArmEV{t}{i})$
-for pulling arm $i$
-(and payment 0 for all other arms).
-\ELSE
-\STATE Let agent $t$ play myopically, i.e., offer payments 0 for all arms.
-\ENDIF
-\ENDFOR
-\end{algorithmic}
-\end{algorithm}
-
-The high-level idea in the proofs of our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret},
-is the following.
-Because the algorithm ensures that each arm is pulled
-``frequently enough,''
-the estimates \ArmEV{t}{i} become gradually more accurate in the
-phase number $s$.
-Thus, the fraction of agents who misidentify their best arm decreases.
-Because for each arm, enough agents have a true preference for this
-arm, once the arms' attribute vectors are learned well enough,
-the algorithm will not need to incentivize any more,
-resulting in a payment bound independent of $T$.
-Similarly, the regret will decrease, and mostly accrue
-due to ``problematic'' agents who are nearly tied in their preferences
-between their top two arm choices.
-The detailed analysis following this outline is somewhat subtle, though,
-due to the dependencies between the agents' arm pulls and the
-estimates which in turn are based on past arm pulls.
-We begin with several technical lemmas that are used for both the
-payment and regret bounds.
-
-To capture the probability masses of problematic agents,
-we define the quantity
-$\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
-\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
-to be the total probability mass (across all arms) of agents
-whose (actual) preference for their best arm over their second-best
-arm is at most $\delta$.
-\dkcomment{We should stress somewhere that we assume that actual ties
-  have measure 0.}
-
-To formally reason about the event that the estimates of arms'
-attributes vectors are accurate enough --- or fail to be so ---
-we define the events
-$\AccE{t}{i}{j}{x} := [|\ArmE{t}{i}{j} - \Arm{i}{j}| \leq x]$
-that attribute $j$ of arm $i$ at time $t$ is estimated to
-within accuracy $x$ or better.
-Then, 
-$\AccEU{t}{x} = \bigcap_{i,j} \AccE{t}{i}{j}{x}$
-is the event that at time $t$, all arm attribute
-estimates are accurate to within $x$ simultaneously.
-We will then show that for suitable choices of $t, x$,
-the events \AccE{t}{i}{j}{x}
-(and hence, by union bound, \AccEU{t}{x})
-have high probability,
-and that when they do, myopic agents do not make large mistakes.
-
-%We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.
-
-\subsection{General Lemmas}
-
-% We begin by showing that under our assumptions, the measure of
-% problematic arms cannot be too large.
-
-% \begin{lemma} \label{lem:sdelta}
-% $\AlmostTied{\delta} \leq \TieDensity \cdot \delta$ for all $\delta$.
-% \end{lemma}
-
-% \begin{emptyproof}
-% Using the upper bound from Assumption~\ref{A1}, we can bound
-
-% \begin{align*}
-% \AlmostTied{\delta}
-% & = \sum_{i,i'} \ProbC{\AgV \cdot (\ArmV{i} - \ArmV{i'}) \leq \delta}%
-%     {\AgV \in \FirstTwo{i}{i'}}
-%   \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}\\
-% & \leq \sum_{i,i'} \TieDensity \cdot \delta
-%     \cdot \Prob{\AgV \in \FirstTwo{i}{i'}}
-% \; = \; \TieDensity \cdot \delta. \QED
-% \end{align*}
-% \end{emptyproof}
-
-We begin by bounding the length of any phase, which will be useful to bound
-the cumulative regret of the early rounds
-(before tail bounds have kicked in). We prove Lemma~\ref{lem:phase-length} in the Appendix~\ref{sec:lemma4-proof}.
-
-\begin{lemma} \label{lem:phase-length}
-For any $s\geq 3$, the expected length of phase $s$ is at most
-$\ARMNUM \cdot \log(s)$ time steps.
-\end{lemma}
-
-We now state the key technical lemma captures the intuition that
-the estimates of the arms' attribute vectors become
-more accurate with increasing phases $s$.
-
-\begin{lemma} \label{lem:round-prob}
-Recall that $\sigma$ is the standard deviation of the Gaussian noise.
-Let \LatePhase be a phase cutoff, 
-and let $x_n, x'_n > 0$ be functions satisfying that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
-\leq \frac{n x'_n}{2 \sigma}$,
-for all $n \geq \LatePhase$.
-Let $\tau_s$ be a stopping time
-(which may depend on the entire past history)
-which is almost surely in phase $s$,
-i.e., satisfying $\tau \in [t_s, t_{s+1})$ almost surely.
-
-Then, for any arm $i$, attribute $j$, and phase $s \geq \LatePhase$,
-we have that
-$\Prob{\AccE{\tau_s}{i}{j}{x'_s}}
-\geq 1 - 24 \exp\left(-\frac{1.8 s x_s^2}{16 \sigma^2} \right)$.
-\end{lemma}
-
-The proof of Lemma~\ref{lem:round-prob} is based on an adaptive
-concentration inequality due to \cite{zhao2016adaptive},
-given as Lemma~\ref{lem:ACI-inequality}.
-
-\begin{lemma}[Corollary 1 of \cite{zhao2016adaptive}]
-\label{lem:ACI-inequality}
-Let $X_i$ be zero-mean $1/2$-subgaussian random variables,
-and $\SET{S_n = \sum_{i=1}^n X_i, n \geq 1}$ the corresponding random walk.
-Let $J$ be any stopping time with respect to $\SET{X_1, X_2, \ldots}$.
-(We allow $J$ to take the value $\infty$,
-defining $\Prob{J = \infty} = 1 - \lim_{n \to \infty} \Prob{J \leq n}$.)
-Define 
-\begin{align*}
-g(n) & = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b}.
-\end{align*}
-Then, 
-\begin{align*}
-\Prob{J < \infty \mbox{ and } S_J \geq g(J)} \leq 12 \e^{-1.8 b}.
-\end{align*}
-\end{lemma}
-
-We leave the proof of Lemma~\ref{lem:round-prob} in the Appendix~\ref{sec:lemma5-proof}. Next, we show the complementary part:
-when \AccEU{t}{x} happens, no myopic agent incurs large regret. We prove Lemma~\ref{lem:right-choice} in the Appendix~\ref{sec:lemma7-proof}.
-
-\begin{lemma} \label{lem:right-choice}
-Let $x > 0$ be arbitrary.
-When \AccEU{t}{x} happens,
-no agent \AgV will pull a highly suboptimal arm, i.e., an arm $i$ with 
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
-\end{lemma}
-
-\subsection{Bounding the Total Payment}
-
-As a first step towards bound the total payment (and also regret),
-we show that for sufficiently late phases,
-under the event \AccEU{t}{x} for suitably small $x$,
-the algorithm does not offer any payments. We prove Lemma~\ref{lem:no-incentives} in the Appendix~\ref{sec:lemma8-proof}.
-
-\begin{lemma} \label{lem:no-incentives}
-Fix an arm $i$.
-Let $s \geq \exp(2/\MinProb)$, and let $\tau_s$ be the (random)
-time when arm $i$ is pulled for the \Kth{s} time.
-Under \AccEU{\tau_s}{\frac{p}{4\Diam d \TieDensity}},
-this pull of arm $i$ is not incentivized.
-\end{lemma}
-
-Towards bounding the algorithm's total payment, we now bound the
-\emph{number} of rounds in which the algorithm makes a payment by a
-constant.
-This bound also turns out to be useful for bounding the total regret.
-
-\begin{lemma} \label{lem:numP}
-The expected number of time steps in which
-Algorithm~\ref{alg:basic-incentivizing}
-makes any payment is at most $O\left( N\exp\left(\frac{2}{p}\right) \right)$.
-\end{lemma}
-
-\begin{proof}
-We partition phases into early and late phases.
-For each of the early phases,
-we crudely bound the number of payments by \ARMNUM,
-using that each arm is incentivized at most once per phase.
-For later phases,
-we use Lemma~\ref{lem:no-incentives},
-which rules out any incentives unless large misestimates of the arm
-locations occur, which is exponentially unlikely by 
-Lemma~\ref{lem:round-prob}.
-
-To make this intuition precise, we set
-$\delta = \frac{\MinProb}{2 \TieDensity}$,
-and $x = x' = \frac{\delta}{2 \Diam d}$
-(which is independent of the phase number $s$).
-The cutoff point between early and late phases is now set to
-$\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3}, \exp(\frac{2}{\MinProb}))$.
-We will verify below that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
-\leq \frac{n x}{2 \sigma}$
-for all $n \geq \max(2, \frac{30 \sigma^3}{x^3})$.
-
-Fix an arm $i$, and consider the \Kth{s} pull of an arm $i$,
-for $s \geq \EvenLaterPhase$.
-If this pull occurs before phase $s$, it was definitely not incentivized.
-So we condition on the pull occurring in phase $s$,
-and let $\tau_s$ be the time step when this pull occurred;
-notice that this means that this must be the first pull of arm $i$ in
-phase $s$.
-
-By Lemma~\ref{lem:round-prob} (with our choice of $x = x'$),
-and a union bound over all $i,j$, we bound the probability
-$\Prob{\AccEU{\tau_s}{x}}
-\geq 1 - 24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$.
-And by Lemma~\ref{lem:no-incentives},
-under the event ${\mathcal E}_{\tau_s}(x)$,
-arm $i$ is not payment-eligible.
-
-Thus, for any $s \geq \EvenLaterPhase$,
-the \Kth{s} pull of arm $i$ is incentivized  
-with probability at most
-$24 \ARMNUM d \cdot \exp \left(
-  -\frac{1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-\right)$.
-Summing over all arms and phases $s$,
-and adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
-the first \EvenLaterPhase phases, 
-the expected total number of arm incentivizations is at most
-\begin{align*}
-&\ARMNUM \EvenLaterPhase
-  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \nonumber \\
-=& O\left( \max\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp(\frac{2}{p})\right)
-  + \frac{\ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right) \nonumber  \\
-=& O\left( N\exp\left(\frac{2}{p}\right) \right).
-\end{align*}
-
-It remains to show that
-$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
-\leq \frac{n x}{2 \sigma}$
-for all $n \geq \max(2, \frac{30 \sigma^3}{x^3}$.
-We first use that $\sqrt{\cdot}$ is sublinear to bound
-\[
-  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
-\; \leq \; \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1)} + \frac{n x}{4 \sigma}
-\]
-(here we use the fact $\sqrt{n} \leq n$).
-Next, we show that
-$\sqrt{0.6 n \log (\log_{1.1}(n) + 1)} \leq \frac{n x}{4 \sigma}$;
-then, adding the two terms gives the desired bound.
-
-By squaring the claimed statement and rearranging,
-it is equivalent to show that
-$\frac{n}{\log(\log_{1.1}(n)+1)} \geq \frac{9.6\sigma^2}{x^2}$.
-Because $n \geq 2$,
-a numerical calculation and derivative test shows that
-$\frac{n}{\log(\log_{1.1}(n)+1)} \geq n^{2/3}$,
-and because $n \geq \frac{30 \sigma^3}{x^3}$,
-we get that
-$n^{2/3} \geq \frac{9.6 \sigma^2}{x^2}$, completing the proof.
-
-\end{proof}
-
-It would be desirable to simply identify a constant upper bound on the
-payment made each time.
-Unfortunately, while the agent types are drawn from a bounded support,
-the noise in arm locations is not;
-hence, with small probability, arm locations may be grossly
-misestimated, resulting in high incentive payments.
-As a result, the actual analysis of the total payment is significantly more
-intricate;
-the proof of Theorem~\ref{rst:budget} is given in
-Appendix~\ref{sec:payment-proof}.
-
 \subsection{Bounding the Total Regret}

### 2018-02-17 conclusion.tex
edits to section 2 and conclusion

--- 2018-01-26 conclusion.tex
@@
 \section{Conclusion}
-In this paper, we study the incentivizing exploration problem with heterogeneous user preferences, which generalize the problem setting studied by \cite{frazier2014incentivizing} and \cite{han2015incentivizing}.
-We propose a simple policy that mostly exploits and occasionally incentivizing exploration, which can achieve $O(N^2+M(\log(T))^2)$ cumulative expected regret with $O(N^2)$ payment budget.
+We study the problem of incentivizing exploration with heterogeneous
+user preferences.
+We propose an algorithm that achieves expected cumulative regret of
+$O(\ARMNUM \e^{2/\MinProb} + \ARMNUM \log^3(T))$,
+using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
+It is possible to improve these bounds to polynomial (in \ARMNUM and
+$1/\MinProb$) when \MinProb is known or the preference distribution is
+discrete.
+In fact, we conjecture that this should be possible even in the full
+generality of our model.
+As a first step towards such a polynomial bound, we believe that it
+should be possible to obtain an exponential dependence on
+$1/(\MinProb \ARMNUM)$, which gives polynomial dependence unless some
+arm has a much smaller fraction of the population preferring.
+
+Taking this goal one step further, we would like to 
+develop algorithms that do not require all arms to be preferred by a
+strictly positive fraction of agents.
+An alternate algorithm might only incentivize an arm if its estimated
+attribute vector is close enough to a Pareto frontier.
+The regret will then be $\Omega(\log(T)$ when at least one arm falls
+below the Pareto frontier, as we no longer have free exploration of
+all arms. 
+It is likely that a bound will deteriorate as the number of such
+unpreferred arms increases.
+
+Finally, it would be desirable to generalize the class of utility
+functions that can be handled beyond inner products.
+We believe that similar results hold for arbitrary
+Lipschitz-continuous utility functions of the arm's attribute vector,
+and that only minor modifications are necessary to the algorithm and
+proofs.

### 2018-02-17 algorithm_general.tex
stating once that proofs are in appendix

@@
 the regret of early rounds
-(before tail bounds have kicked in). We prove Lemma~\ref{lem:phase-length} in Appendix~\ref{sec:lemma4-proof}.
+(before tail bounds have kicked in). The proof of Lemma~\ref{lem:phase-length} and all other proofs missing in the main paper may be found in the Appendix.
 
@@
 
-We leave the proof of Lemma~\ref{lem:round-prob} in the Appendix~\ref{sec:lemma5-proof}. Next, we show the complementary part:
-when \AccEU{t}{x} happens, no myopic agent incurs large regret. We prove Lemma~\ref{lem:right-choice} in the Appendix~\ref{sec:lemma7-proof}.
+Next, we show the complementary part:
+when \AccEU{t}{x} happens, no myopic agent incurs large regret.
 

### 2018-02-17 introduction.tex
editted intro section

@@
 
-\dkcomment{Rearranging the next two paragraphs a bit.}
 Heterogeneity presents both a challenge and an opportunity.
-On the one hand, \dkedit{unobserved heterogeneity} hides critical
+On the one hand, unobserved heterogeneity hides critical
 information about an agent's preferences from the principal.
@@
 \emph{attribute} (or \emph{feature}) vectors.
-\dkedit{Arms' attributes are a priori unknown, and
-  agents' attributes are drawn from a known distribution.}
+Arms' attributes are a priori unknown, and
+  agents' attributes are drawn from a known distribution.
 An agent's reward from pulling an arm is the inner product of his
@@
 If furthermore, the density of ties in agent preferences between arms
-vanishes (in a sense made precise in Section~\ref{sec:ub}),
-\dkcomment{Make sure we cite the right section.}
+vanishes (in a sense made precise in Section~\ref{subsec:discrete}),
 there is a policy that achieves constant
@@
 here, $C''$ depends on the ``tie density.''
-\dkcomment{Make sure we get the right dependence on $T$.}
 \end{theorem}
@@
 It is presented in detail in Section~\ref{sec:ub}.
-
-\dkdelete{The result can be smoothly extended when there some arms that are not
-preferred by any agents.}
-\dkcomment{Deleted the sentence about smooth extension of the result
-  --- if we keep it, it goes in the conclusions section, I think.}

### 2018-02-17 algorithm_intro.tex
edits to algo intro, and problem statement

@@
 $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
-\cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i \pfedit{\mid \ArmEV{t}{i'}\ \forall i'}}$
+\cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i \mid \ArmEV{t}{i'}\ \forall i'}$
 is the probability that arm $i$ will be pulled
@@
 
-\pfcomment{I deleted here we now define $q(z)$ in section 2}
-\pfdelete{
-To capture the probability masses of problematic agents,
-we define the quantity
-$\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
-\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
-to be the total probability mass (across all arms) of agents
-whose (actual) preference for their best arm over their second-best
-arm is at most $\delta$.
-}
-\dkcomment{We should stress somewhere that we assume that actual ties
-  have measure 0.}
-
 To formally reason about the event that the estimates of arms'

### 2018-02-17 Discussion.tex

@@
 \subsubsection{Discrete Preferences}
+\label{subsec:discrete}
 Discrete preferences by agents are captured by the following assumption (which states that the agents who are close to tied between two arms have measure 0):

### 2018-02-17 algorithm_regret.tex
cleaned up formulas, proof

@@
 
-\begin{extraproof}{Theorem~\ref{rst:regret}}
+\begin{emptyextraproof}{Theorem~\ref{rst:regret}}
 Regret can arise in two ways:
@@
 \begin{align*}
-\lefteqn{
 O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
 + \ARMNUM^2 \MAXR d
-+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} g^2(s) \log(s) \right)}
-\\ & = 
-O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
-+ \ARMNUM^2 \MAXR d
-+ \ARMNUM \TieDensity \Diam^2 d^2 \sigma^2 \cdot \log^3(T) \right).
++ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} g^2(s) \log(s) \right)
+& = 
+O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
++ \ARMNUM \TieDensity \cdot \log^3(T) \right).\QED
 \end{align*}
-\end{extraproof}
+\end{emptyextraproof}

### 2018-02-17 algorithm_general.tex
shortening 4.1

@@
 i.e., satisfying $\tau \in [t_s, t_{s+1})$ almost surely.
-
 Then, for any arm $i$, attribute $j$, and phase $s \geq \LatePhase$,
-we have that
+we have 
 $\Prob{\AccE{\tau_s}{i}{j}{x'_s}}
@@
 Define 
-\begin{align*}
-g(n) & = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b}.
-\end{align*}
+$g(n)  = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b}$.
 Then, 
-\begin{align*}
-\Prob{J < \infty \mbox{ and } S_J \geq g(J)} \leq 12 \e^{-1.8 b}.
-\end{align*}
+$\Prob{J < \infty \mbox{ and } S_J \geq g(J)} \leq 12 \e^{-1.8 b}$.
 \end{lemma}
 
-Next, we show the complementary part:
-when \AccEU{t}{x} happens, no myopic agent incurs large regret.
+Next, we show the complementary result:
+when event \AccEU{t}{x} happens, no myopic agent incurs large regret.
 

### 2018-02-17 algorithm_payment.tex
stating once that proofs are in appendix

@@
 under the event \AccEU{t}{x} for suitably small $x$,
-the algorithm does not offer any payments. We prove Lemma~\ref{lem:no-incentives} in the Appendix~\ref{sec:lemma8-proof}.
+the algorithm does not offer any payments.
 
@@
 Summing over all arms and phases $s$,
-and adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
+adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
 the first \EvenLaterPhase phases, 
+and using that $\exp(-x) \leq 1-x/2$ for $x \leq 1$,
 the expected total number of arm incentivizations is at most
 \begin{align*}
-&\ARMNUM \EvenLaterPhase
+\lefteqn{\ARMNUM \EvenLaterPhase
   + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \nonumber \\
-=& O\left( \max\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp(\frac{2}{p})\right)
-  + \frac{\ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right) \nonumber  \\
-=& O\left( N\exp\left(\frac{2}{p}\right) \right).
+    \frac{-1.8 \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+  \right)}}  \\
+& = O\left( \max\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp(\frac{2}{p})\right)
+  + \frac{\ARMNUM^2 d^3 \TieDensity^2 \sigma^2 \Diam^2}{\MinProb^2} \right)
+\; = \; O\left( N\exp\left(\frac{2}{p}\right) \right).
 \end{align*}

### 2018-02-17 result_discussion.tex
copied changes from 4.4 to appendix, rearranged appendix order

@@
 constant bound more generally, i.e., for $\TieDensity > 0$.
-That such a bound is unachievable is shown in Section~\ref{sec:lb},
+That such a bound is unachievable is shown in Appendix~\ref{sec:lb},
 where we show a lower bound of $\Omega(\log(T))$ on

### 2018-02-17 result_discussion.tex
fix typos

@@
 but when preferences our discrete, the constant regret (rather than
-$\Theta(\log T)$ surpasses a standard multi-armed bandit.
+$\Theta(\log T)$) surpasses a standard multi-armed bandit.
 This may seem surprising, because our setting is one in which the
@@
 heterogeneity alone is not always sufficient for enabling performance
-improvements compare to the standard bandit setting.
+improvements compared to the standard bandit setting.
 Indeed, consider a version in which agents are still heterogeneous,

### 2018-02-17 introduction.tex
rephrased Theorem 1

@@
 with formal definitions given in Section~\ref{sec:prob}.)
-Arms and users (or \emph{agents}) are characterized by payoff-relevant
+The \ARMNUM arms and users (or \emph{agents})
+are characterized by payoff-relevant
 \emph{attribute} (or \emph{feature}) vectors.
-Arms' attributes are a priori unknown, and
-  agents' attributes are drawn from a known distribution.
+Arms' attributes are a priori unknown,
+and agents' attributes are drawn from a known distribution.
 An agent's reward from pulling an arm is the inner product of his
@@
 \begin{theorem} \label{thm:main-intro}
-Assume that for each arm, at least a constant fraction of the
-population likes this arm best.
-If furthermore, the density of ties in agent preferences between arms
-vanishes (in a sense made precise in Section~\ref{subsec:discrete}),
-there is a policy that achieves constant
-expected regret $C$ and constant%
-\footnote{The constants $C,C'$ depend on the number of arms and the
-  smallest fraction preferring any one arm.} expected payment $C'$.
-If near-ties have non-zero density,
-then the regret is bounded by $O(C + C'' \log^3(T))$,
-while the expected payment is still bounded by $C'$;
-here, $C''$ depends on the ``tie density.''
+Assume that for each arm, at least a constant fraction \MinProb
+of the population likes this arm best,
+and let \TieDensity be a measure of the ``density of near-ties''
+between agents' arms preferences
+(in a sense made precise in Section~\ref{subsec:discrete}).
+There is a policy that achieves expected 
+cumulative regret $O (\ARMNUM \e^{2/\MinProb} + \ARMNUM \log^3(T))$,
+using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
+In particular, when $\TieDensity = 0$
+(e.g., in the case of discrete agent preferences),
+both the expected regret and expected payment are bounded by constants
+(with respect to $T$). 
 \end{theorem}

### 2018-02-17 abstract.tex
removed normally distributed

@@
 arm-specific attribute vector,
-perturbed by independent normally distributed noise.
+perturbed by independent noise.
 Agents arrive sequentially and choose arms to pull based on their own

### 2018-02-17 introduction.tex
typo fixes

--- 2018-02-17 introduction.tex
@@
   to refer to the principal.}
-advantage and make recommendations to the individual agents which it
-is in their best interest to follow.
+advantage and make recommendations to the individual agents that 
+are in their best interest to follow.
 \citet{frazier2014incentivizing} and 
@@
 (such as reviews on an online retail site).
-They instead allow payments which the principal can offer to users as
+They instead suppose the principal can offer payments to users as
 a reward for pulling particular arms.
@@
 This is perhaps because regimes with heterogeneous preferences are the
-ones where discovery of the best items is the most difficult for people, and
-where the number of items to consider is largest, and thus where online
+ones where discovery of the best items is the most difficult for people, 
+and thus where online
 platforms tend to provide the greatest value.  Thus, we see an appropriate

### 2018-02-17 introduction.tex
typo

@@
 Even when left unincentivized, agents will
-play a variety of arms, revealing information about these arms' attributes.
+play a variety of arms, revealing information about their attributes.
 This stands in sharp contrast to the case of homogeneous preferences,
@@
 and let \TieDensity be a measure of the ``density of near-ties''
-between agents' arms preferences
+between agents' arm preferences
 (in a sense made precise in Section~\ref{subsec:discrete}).

### 2018-02-17 algorithm_intro.tex
fixed typos in 4, 4.4

@@
 It mostly allows agents to exploit, but when an arm is sufficiently
-unlikely to be pulled
+unlikely to be pulled,
 it incentivizes this arm with a payment high enough
-to guarantee the next agent pulls it.
-This way the algorithm ensures each arm is pulled often enough.
+to guarantee that the next agent pulls it.
+This way, the algorithm ensures that each arm is pulled often enough.
 
@@
 \footnote{in fact: exactly, since the algorithm entered phase $s$}
-$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
+$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
 \item 

### 2018-02-17 Lemmas.tex
moved Zhao to appendix, fixed typos

@@
 \end{rlemma}
+
+The proof of Lemma~\ref{lem:round-prob} is based on an adaptive
+concentration inequality due to \cite{zhao2016adaptive},
+given as Lemma~\ref{lem:ACI-inequality}.
+
+\begin{lemma}[Corollary 1 of \cite{zhao2016adaptive}]
+\label{lem:ACI-inequality}
+Let $X_i$ be zero-mean $1/2$-subgaussian random variables,
+and $\SET{S_n = \sum_{i=1}^n X_i, n \geq 1}$ the corresponding random walk.
+Let $J$ be any stopping time with respect to $\SET{X_1, X_2, \ldots}$.
+(We allow $J$ to take the value $\infty$,
+defining $\Prob{J = \infty} = 1 - \lim_{n \to \infty} \Prob{J \leq n}$.)
+Define 
+$g(n)  = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b}$.
+Then, 
+$\Prob{J < \infty \mbox{ and } S_J \geq g(J)} \leq 12 \e^{-1.8 b}$.
+\end{lemma}
 

### 2018-02-17 algorithm_general.tex
moved Zhao to appendix, fixed typos

@@
 the regret of early rounds
-(before tail bounds have kicked in). The proof of Lemma~\ref{lem:phase-length} and all other proofs missing in the main paper may be found in the Appendix.
+(before tail bounds have kicked in). The proof of Lemma~\ref{lem:phase-length} and all other proofs missing in the main paper may be found in the appendix.
 
@@
 
-We now state the key technical lemma captures the intuition that
+We now state the key technical lemma which captures the intuition that
 the estimates of the arms' attribute vectors become
@@
 
-The proof of Lemma~\ref{lem:round-prob} is based on an adaptive
-concentration inequality due to \cite{zhao2016adaptive},
-given as Lemma~\ref{lem:ACI-inequality}.
-
-\begin{lemma}[Corollary 1 of \cite{zhao2016adaptive}]
-\label{lem:ACI-inequality}
-Let $X_i$ be zero-mean $1/2$-subgaussian random variables,
-and $\SET{S_n = \sum_{i=1}^n X_i, n \geq 1}$ the corresponding random walk.
-Let $J$ be any stopping time with respect to $\SET{X_1, X_2, \ldots}$.
-(We allow $J$ to take the value $\infty$,
-defining $\Prob{J = \infty} = 1 - \lim_{n \to \infty} \Prob{J \leq n}$.)
-Define 
-$g(n)  = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b}$.
-Then, 
-$\Prob{J < \infty \mbox{ and } S_J \geq g(J)} \leq 12 \e^{-1.8 b}$.
-\end{lemma}
-
 Next, we show the complementary result:

### 2018-02-17 result_discussion.tex
typo
typo fix

@@
 Aside from the assumption that $\TieDensity = 0$, another assumption
-allows us to eliminate this exponential dependency.
+allows us to eliminate this exponential dependence.
 Namely, when \MinProb (or a lower bound on it) is known ahead of time,
@@
 multi-armed bandit problem;
-but when preferences our discrete, the constant regret (rather than
+but when preferences are discrete, the constant regret (rather than
 $\Theta(\log T)$) surpasses a standard multi-armed bandit.

### 2018-02-17 algorithm_intro.tex
changed min to sup

@@
 offers payment
-$\Pay{t}{i} = \min \Set{c \geq 0}{%
-\Prob[\AgV \sim \AgentDist]{c + \AgV \cdot \ArmEV{t}{i} \geq \max_{i'\ne i} \AgV \cdot \ArmEV{t}{i'}} \ge 1/\log(s)}$.
+$\Pay{t}{i} = \sup \Set{c \geq 0}{%
+\Prob[\AgV \sim \AgentDist]{c + \AgV \cdot \ArmEV{t}{i} \geq \max_{i'\ne i} \AgV \cdot \ArmEV{t}{i'}} \leq 1/\log(s)}$.
+(This definition ensures that \Pay{t}{i} is well-defined
+and incentivizes at least a $1/\log(s)$ measure of agents,
+even if $f$ has discrete points.)
 However, we focus on the higher payments for simplicity of presentation.

### 2018-02-17 algorithm_intro.tex
typo

@@
 The detailed analysis following this outline is somewhat subtle, though,
-due to the dependencies between the agents' arm pulls and the
+due to the dependence between the agents' arm pulls and the
 estimates which in turn are based on past arm pulls.

### 2018-02-17 algorithm_payment.tex
eidted payment section

@@
 
-As a first step towards bound the total payment (and also regret),
+As a first step towards bounding the total payment (and also regret),
 we show that for sufficiently late phases,
@@
 for $s \geq \EvenLaterPhase$.
-If this pull occurs before phase $s$, it was definitely not incentivized.
+If this pull occurred before phase $s$, it was definitely not incentivized.
 So we condition on the pull occurring in phase $s$,
@@
   \right)}}  \\
-& = O\left( \max\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp(\frac{2}{p})\right)
+& = O\left( \max\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp\left(\frac{2}{p}\right)\right)
   + \frac{\ARMNUM^2 d^3 \TieDensity^2 \sigma^2 \Diam^2}{\MinProb^2} \right)
@@
 \leq \frac{n x}{2 \sigma}$
-for all $n \geq \max(2, \frac{30 \sigma^3}{x^3}$.
+for all $n \geq \max(2, \frac{30 \sigma^3}{x^3})$.
 We first use that $\sqrt{\cdot}$ is sublinear to bound
@@
 $n^{2/3} \geq \frac{9.6 \sigma^2}{x^2}$, completing the proof.
-
 \end{proof}

### 2018-02-17 conclusion.tex
fixed a typo
typo in conclusions fixed

@@
 user preferences.
-We propose an algorithm that achieves expected cumulative regret of
+We proposed an algorithm that achieves expected cumulative regret of
 $O(\ARMNUM \e^{2/\MinProb} + \ARMNUM \log^3(T))$,
@@
 $1/(\MinProb \ARMNUM)$, which gives polynomial dependence unless some
-arm has a much smaller fraction of the population preferring.
+arm has a much smaller fraction of the population preferring it.
 
@@
 attribute vector is close enough to a Pareto frontier.
-The regret will then be $\Omega(\log(T)$ when at least one arm falls
+The regret will then be $\Omega(\log(T))$ when at least one arm falls
 below the Pareto frontier, as we no longer have free exploration of

### 2018-02-17 algorithm_regret.tex
fixed typo

@@
 Because $n \leq T$, it is sufficient to show that
-$\frac{50}{9} \log T \geq \log(\log_{1.1}(n) + 1)$,
+$\frac{50}{9} \log T \geq \log(\log_{1.1}(T) + 1)$,
 which can be verified by numerical calculation for $T=2$ and a

### 2018-05-14 abstract.tex
fixed a few typos

@@
 cumulative regret of $O (\ARMNUM \e^{2/\MinProb} + \ARMNUM \log^3(T))$,
-using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
+using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$, where $\ARMNUM$ is the total number of arms.
 If \MinProb is known or the distribution over agent

### 2018-05-14 colt.tex
moved some proofs to the appendix
re-state lemmas/proofs in the appendix
Broke algorithm.tex up into 4 files.
copied changes from 4.4 to appendix, rearranged appendix order
fixed a few typos

@@
 
+\newcommand{\emptyextraproof}[1]{\rm \trivlist \item[\hskip \labelsep{\bf Proof of #1. }]}
+\def\endemptyextraproof{\endtrivlist}
+
 \newenvironment{rtheorem}[3][]{
+
+\bigskip
+
+\noindent \ifthenelse{\equal{#1}{}}{\bf #2 #3}{\bf #2 #3 (#1)}
+\begin{it}
+}{\end{it}}
+
+\newenvironment{rlemma}[3][]{
 
@@
 \title{Incentivizing Exploration by Heterogeneous Users}
-% {Incentivizing Exploration with Heterogeneous Utilities}
 
-%\author{\name Bangrui Chen \email bc496@cornell.edu \\
-%\name Peter I.\ Frazier \email pf98@cornell.edu \\
-%\addr Operations Research and Information Engineering\\
-%Cornell University\\
-%New York, NY 14850, USA
-%\AND
-%\name David Kempe \email david.m.kempe@gmail.com  \\
-%\addr Department of Computer Science\\
-%University of Southern California\\
-%Los Angeles, CA 90089, USA}
+\author{\name Bangrui Chen \email bc496@cornell.edu \\
+\name Peter I.\ Frazier \email pf98@cornell.edu \\
+\addr Operations Research and Information Engineering\\
+Cornell University\\
+New York, NY 14850, USA
+\AND
+\name David Kempe \email david.m.kempe@gmail.com  \\
+\addr Department of Computer Science\\
+University of Southern California\\
+Los Angeles, CA 90089, USA}
 
@@
 \begin{keywords}
-Incentivizing Exploration, Multi-Armed Bandits
+Incentivizing Exploration, Multi-Armed Bandits, Social Learning
 \end{keywords}
@@
 
-\input{algorithm}
+\input{algorithm_intro}
+\input{algorithm_general}
+\input{algorithm_payment}
+\input{algorithm_regret}
 
 \input{Discussion}
-
-\input{lower_bound}
 
@@
 
+\input{lower_bound}
+
+\input{Lemmas}
+
 \input{payment-proof}
+
+\input{Discussion-Proof}
 

### 2018-05-14 introduction.tex
fixed a few typos

@@
 using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
-In particular, when $\TieDensity = 0$
-(e.g., in the case of discrete agent preferences),
+In particular, when agents who are close to tied between two arms have measure $0$,
 both the expected regret and expected payment are bounded by constants

### 2018-05-14 problem_setting.tex
edits to algo intro, and problem statement
fixed a few typos

@@
 % }
-arm $i$ maximizing $\argmax_i (\Pay{t}{i} + \AgentV{t} \cdot \ArmEV{t}{i})$.
+arm $i$ maximizing $(\Pay{t}{i} + \AgentV{t} \cdot \ArmEV{t}{i})$.
 The principal cannot observe \AgentV{t},
@@
 
-Let $\MinProb = \min_{i} \Prob[\AgentDist]{\Set{\AgV}{\Best{\AgV} = i}}$
+Let $\MinProb = \min_{i} \Prob[\AgentDist]{\Best{\AgV} = i}$
 denote the minimum (over all arms) fraction of users that prefer any
@@
 
+We emphasize that this assumption implies ties happen with probability $0$.
+
 \paragraph{Role of parameters:}

### 2018-05-14 result_discussion.tex
fixed a few typos

@@
 (Notice that this setting violates our Assumption~\ref{A3},
-so out bounds do not apply to it.)
+so our bounds do not apply to it.)
 Then, the payment is $0$ and the expected regret scales as

### 2018-06-02 introduction.tex
addressing modeling questions

@@
 observed by everyone.
+\pfedit{This models full-text product reviews on websites like Amazon, or ratings of ``service'', ``value'', and other restaurant attributes on websites like Tripadvisor.  }
 Agents are myopic and will pull the arm whose expected attribute
 vector (based on past noisy observations) maximizes their reward.
+\pfedit{Agents' ability to effectively base decisions on all past observations models platforms' abilities to aggregate and effectively display past feedback, through simple averages of ratings and automatic summarization of full-text reviews \citep{wang2010product,liu2012movie,abulaish2009feature}.
+While platforms can manipulate the display of user data, most have an incentive to be seen as truthful.}
 The principal can incentivize agents to pull particular arms by
@@
 Our main theorem can be stated informally as follows:
+
+%One example where agents give noisy observations of items’ feature vectors is restaurant reviews on TripAdvisor.
+Users provide not just an overall rating, but also separate ratings for Service, Value, Food and Atmosphere.
+We may treat these as our feature vector.
+Platforms collect similar explicit feature vector observations whenever their users rate not just satisfaction with an item but the more granular components that contribute to it.
+
+%As another example, consider websites like Amazon and Yelp whose users provide full-text reviews of items.
+Reviews on Yelp describe a restaurants’ attributes (service, value, etc.), and reviews on Amazon similarly describe products’ attributes.
+Thus, we can think of a user reading past reviews as aggregating past users’ observations of items’ feature vectors.
+In this way, platforms with full-text reviews implicitly provide feature vector observations.
+
+%As a third example, a platform with full-text reviews could run an NLP algorithm to extract features and sentiments from reviews, and then surface them to users as rated attributes.
 

### 2018-06-02 problem_setting.tex
addressing modeling questions

@@
 and his reward is $\AgentV{t} \cdot \ObsV{t}$,
-i.e., agents have linear preferences.%
+i.e., agents have linear preferences.
+\pfedit{(We are also free to create new attributes that are nonlinear transformations of existing attributes.)}
 
@@
 $\Expect{\TotalPay{T}}$ are small.
+
+\pfedit{
+We assume above that the distribution $\AgentDist$ over preference vectors is known.
+In practice, one would estimate this from agents' selections and the attribute estimates and offered payments on which they were based.
+While we do not show it, we hypothesize that our regret guarantees only change by constants as long as our estimate of the conditional probability of pulling an arm is correct within a constant factor (our algorithm depends on this quantity).
+}
+
+% \pfedit{
+% We assume above that the distribution $\AgentDist$ over preference vectors is known.
+% In practice, one would estimate this from agents' selections and attribute estimates $\ArmEV{t}{i}$
+% and offered payments $\Pay{t}{i}$ at the time of selection.  
+% In the process of doing such an estimation procedure, one could also select nonlinear transformations of existing attributes (increasing $d$) to improve the predictive accuracy of the assumed linear model.
+% Our analysis assumes such a procedure has already been conducted.
+% This assumption is most appropriate when the number of dimensions $d$ is small relative to the number of items $N$, so that the time required to estimate the distribution over preference vectors is small relative to the time required to learn about items.
+% }
+%\pfcomment{One modeling assumption I don't say anything about is that $\AgentDist$ is known.
+I thought about adding some text saying that it can actually be estimated from user selections as we go, which is true, but it isn't clear that we can learn it much quicker than the item attributes, in general.
+Another tact is to argue that our method is robust to mis-estimation of this, which seems true intuitively, but I'm not sure how to argue it here.
+Probably it is possible to desgin an algorithm that learns this distribution along with item attributes.}
 

### 2018-06-05 Discussion.tex
got rid of ugly expressions
fixed typos in 4, 4.4
significant edits throughout

@@
 \item $i$ has been pulled at most
-$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
+$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
 \item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors, the probability of pulling arm $i$ is less than $1/s$ (compared to $1/\log(s)$ in the general algorithm).
@@
 O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
-  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right).  \nonumber
+  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
+  \right).  \nonumber
 \end{align}
@@
 \item $i$ has been pulled at most
-$s$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s$.
+$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
 \item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s+s_0)$.
@@
 
-This, knowledge of \MinProb allows the algorithm to incentivize significantly fewer arm pulls.
+This knowledge of \MinProb allows the algorithm to incentivize
+significantly fewer arm pulls.
 We refer to this modified version of Algorithm~\ref{alg:basic-incentivizing} as the \emph{Known-\MinProb Algorithm.}
-We outline a proof of the following result for this algortithm under Assumption~\ref{a:known-p} in the Appendix~\ref{sec:discussion-proof2}.
+We outline a proof of the following result for this algortithm under Assumption~\ref{a:known-p} in Appendix~\ref{sec:discussion-proof2}.
 
@@
 \label{rst:known-p}
-Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has an expected payment budget bounded above by 
+Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has expected payment budget bounded above by 
 \begin{align*}
@@
 \end{align*}
-and an expected regret bounded above by
+and expected regret bounded above by
 \begin{align*}
 O \left(\frac{\MAXR \ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
-  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} +\frac{\ARMNUM^2 d\MAXR}{\MinProb}+\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
+  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
+  + \frac{\ARMNUM^2 d\MAXR}{\MinProb}
+  + \frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
 \end{align*}

### 2018-06-05 Lemmas.tex
significant edits throughout

@@
 $g(n)  = \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + n \cdot b}$.
+
 Then, 
@@
 
-By Assmption~\ref{A1},
-%Lemma~\ref{lem:sdelta},
+By Assmption~\ref{A1}
+\dkedit{(including that $\frac{\MinProb}{2\TieDensity} \leq \TieCutoff$)},
 the measure of agents (across all arms)

### 2018-06-05 abstract.tex
significant edits throughout

@@
 We consider the problem of incentivizing exploration with heterogeneous agents.
-In this problem, bandit arms provide vector-valued outcomes equal to an unknown
+In this problem, \dkedit{\ARMNUM} bandit arms provide vector-valued outcomes equal to an unknown
 arm-specific attribute vector,

### 2018-06-05 algorithm_general.tex
significant edits throughout

@@
 (before tail bounds have kicked in). The proof of Lemma~\ref{lem:phase-length} and all other proofs missing in the main paper may be found in the appendix.
+\dkcomment{If we only get 12 pages in the proceedings, make sure to
+  replace ``appendix'' by ``online appendix'' or ``supplemental
+  material'' or whatever we call it, here and everywhere else.}
 
@@
 which is almost surely in phase $s$,
-i.e., satisfying $\tau \in [t_s, t_{s+1})$ almost surely.
+i.e., satisfying $\dkedit{\tau_s} \in [t_s, t_{s+1})$ almost surely.
+\dkcomment{$\tau$ was missing the subscript $s$ here. I think that was
+  a mistake, but am marking it so someone can check.}
 Then, for any arm $i$, attribute $j$, and phase $s \geq \LatePhase$,
@@
 Next, we show the complementary result:
-when event \AccEU{t}{x} happens, no myopic agent incurs large regret.
+when the event \AccEU{t}{x} happens, no myopic agent incurs large regret.
 

### 2018-06-05 algorithm_intro.tex
significant edits throughout

@@
 The conditional probability of pulling arm $i$ is less than
-$1/\log(s)$ given current estimates \ArmEV{t}{i'} of arms'
+$1/\log(s)$ given the current estimates \ArmEV{t}{i'} of the arms'
 attribute vectors.  In other words, we require
@@
 \STATE Set the current phase number $s = 1$.
-\COMMENT{Each arm is pulled once initially ``for free''.}
+\COMMENT{Each arm is pulled once initially ``for free.''}
 \FOR{time steps $t = 1, 2, 3, \ldots$}
@@
 estimates are accurate to within $x$ simultaneously.
-We will then show that for suitable choices of $t, x$,
+We will show that for suitable choices of $t, x$,
 the events \AccE{t}{i}{j}{x}

### 2018-06-05 algorithm_payment.tex
significant edits throughout

@@
 
-Towards bounding the algorithm's total payment, we now bound the
-\emph{number} of rounds in which the algorithm makes a payment by a
-constant.
+Towards bounding the algorithm's total payment, we now bound by a
+constant the \emph{number} of rounds in which the algorithm makes a
+payment.
 This bound also turns out to be useful for bounding the total regret.
@@
 
-Fix an arm $i$, and consider the \Kth{s} pull of an arm $i$,
+Fix an arm $i$, and consider the \Kth{s} pull of arm $i$,
 for $s \geq \EvenLaterPhase$.

### 2018-06-05 algorithm_regret.tex
significant edits throughout

@@
 (which requires severe misestimates of arm locations;
-such misestimated are exponentially unlikely to occur), 
+such misestimates are exponentially unlikely to occur), 
 and agents incurring small positive regret,
@@
 the best arm.
-To be more precise, we will define (with foresight) a phase-dependent
+To be more precise, we define (with foresight) a phase-dependent
 cutoff
@@
 
+\dkedit{
+For most of the proof, we will focus on the case $g(s) \leq \TieCutoff$.
+The remaining phases are the ones with
+$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2 \TieCutoff^2$.
+Each such phase lasts for at most $\ARMNUM \cdot \log(s)$ steps
+in expectation by Lemma~\ref{lem:phase-length},
+and each step incurs regret at most \MAXR.
+The total expected regret incurred in these phases is at most
+$100 \ARMNUM \MAXR \log^2(T) \cdot \Diam^3 d^3 \sigma^3 \TieCutoff^3$.}
+
+\dkedit{For the remainder of the proof, we consider phases $s$
+with $g(s) \leq \TieCutoff$.}
 We first consider agents \AgV incurring positive regret less than $g(s)$.
@@
 $\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(s)$.
-By Assumption~\ref{A1},
+By Assumption~\ref{A1}, \dkedit{and because $g(s) \leq \TieCutoff$,}
 %Lemma~\ref{lem:sdelta},
@@
 is $\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$,
-and each incurs regret at most $g(s)$.
+and each such agent incurs regret at most $g(s)$.
 Summing over all time steps,
@@
 Let the random variable $t_s$ be the final time step in phase $s$,
-for each $s$. Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
+for each $s$.
+\dkcomment{We have already used $t_s$ before, e.g., in the preceding
+  formula. Do we need to redefine it here?}
+Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
 time step in the \Kth{s} phase,
@@
 regret more than $g(s)$.
+\dkcomment{Instead of the extra case distinction, I had thought of
+  defining $g(s)$ to be the minimum of the current definition and
+  \TieCutoff. Unfortunately, I think that we cannot necessarily apply
+  Lemma~\ref{lem:right-choice} with that definition. Just putting that
+  here in case you are thinking of simplifying the proof this way.}
 
@@
 
-Adding all three types of regret terms,
+Adding all \dkedit{four} types of regret terms,
 and substituting that 
@@
 \begin{align*}
-O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+\lefteqn{O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+\dkedit{+ \ARMNUM \MAXR \log^2(T)}
 + \ARMNUM^2 \MAXR d
-+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} g^2(s) \log(s) \right)
-& = 
++ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} g^2(s) \log(s) \right)}
+\\ & = 
 O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)

### 2018-06-05 colt.tex
fixed the format
addressing modeling questions
significant edits throughout

@@
-\documentclass[twoside,11pt]{article}
-\usepackage[anon]{jmlr2e}
+\documentclass[final,12pt]{colt2018}
+% \usepackage[anon]{jmlr2e}
 
@@
 
-% Heading arguments are {volume}{year}{pages}{date submitted}{date published}{paper id}{author-full-names}
+\title{Incentivizing Exploration by Heterogeneous Users}
+\usepackage{times}
 
-\jmlrheading{1}{2000}{1-48}{4/00}{10/00}{meila00a}{Marina Meil\u{a} and Michael I. Jordan}
-
-% Short headings should be running head and authors last names
-
-\ShortHeadings{Incentivizing Exploration with Heterogeneous Utilities}{Chen, Frazier and Kempe}
-\firstpageno{1}
-
-\begin{document}
-
-\title{Incentivizing Exploration by Heterogeneous Users}
-
-\author{\name Bangrui Chen \email bc496@cornell.edu \\
-\name Peter I.\ Frazier \email pf98@cornell.edu \\
+\coltauthor{\Name{Bangrui Chen} \Email{bc496@cornell.edu} \\
+\Name{Peter I.\ Frazier} \Email{pf98@cornell.edu} \\
 \addr Operations Research and Information Engineering\\
@@
 \AND
-\name David Kempe \email david.m.kempe@gmail.com  \\
+\Name{David Kempe} \Email{david.m.kempe@gmail.com}  \\
 \addr Department of Computer Science\\
@@
 
-\editor{}
+\begin{document}
 
@@
 \begin{abstract}
+\dkcomment{Should we be changing the ``Proveedings of ...'' part on
+  the top?}
+
 \input{abstract.tex}
@@
 
-\newpage
+\acks{PF and BC were partially supported by NSF CMMI-1254298 and AFOSR
+FA9550-15-1-0038.
+DK was supported in part by NSF grant 1423618.}
+
+\bibliography{reference}
 
@@
 
-\bibliography{reference}
 \end{document}

### 2018-06-05 conclusion.tex
significant edits throughout

@@
 user preferences.
-We proposed an algorithm that achieves expected cumulative regret of
+We proposed an algorithm that achieves expected cumulative regret
 $O(\ARMNUM \e^{2/\MinProb} + \ARMNUM \log^3(T))$,

### 2018-06-05 introduction.tex
significant edits throughout

@@
-\section{Introduction}
+\section{Introduction} \label{sec:introduction}
 
@@
 \citet{kremer2014implementing}
-and \citet{mansour2015bayesian,mansour2016bayesian}
+and
+\citet{mansour2015bayesian,mansour2016bayesian,mansour2018competition}
+(see \cite{slivkins:asymmetry} for a high-level overview)
 assume that the site (also called the \emph{principal}) has an
@@
 (such as reviews on an online retail site).
-They instead suppose the principal can offer payments to users as
+They instead suppose that the principal can offer payments to users as
 a reward for pulling particular arms.
@@
 Even when left unincentivized, agents will
-play a variety of arms, revealing information about their attributes.
+play a variety of arms, revealing information about the arms' attributes.
 This stands in sharp contrast to the case of homogeneous preferences,
@@
 observed by everyone.
-\pfedit{This models full-text product reviews on websites like Amazon, or ratings of ``service'', ``value'', and other restaurant attributes on websites like Tripadvisor.  }
+This models full-text product reviews on websites like Amazon,
+or ratings of ``service'', ``value'',
+and other restaurant attributes on websites like Tripadvisor.  
 Agents are myopic and will pull the arm whose expected attribute
 vector (based on past noisy observations) maximizes their reward.
-\pfedit{Agents' ability to effectively base decisions on all past observations models platforms' abilities to aggregate and effectively display past feedback, through simple averages of ratings and automatic summarization of full-text reviews \citep{wang2010product,liu2012movie,abulaish2009feature}.
+\dkedit{This assumption requires agents to have access to aggregate
+information about the feature vector estimates of all (relevant) arms. 
+Such access is facilitated by the platforms' ability to aggregate and
+effectively display past feedback, e.g., by displaying simple averages
+of ratings and using automatic summarization of full-text reviews 
+\citep{wang2010product,liu2012movie,abulaish2009feature}.
+While platforms could in principle manipulate the display of such
+data, most have an incentive to be seen as truthful.}
+%\pfedit{Agents' ability to effectively base decisions on all past observations models platforms' abilities to aggregate and effectively display past feedback, through simple averages of ratings and automatic summarization of full-text reviews \citep{wang2010product,liu2012movie,abulaish2009feature}.
 While platforms can manipulate the display of user data, most have an incentive to be seen as truthful.}
@@
 There is a policy that achieves expected 
-cumulative regret $O (\ARMNUM \e^{2/\MinProb} + \ARMNUM \log^3(T))$,
+cumulative regret $O (\ARMNUM \e^{2/\MinProb} + \dkedit{\TieDensity} \ARMNUM \log^3(T))$,
 using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
@@
 
+\dkcomment{Added the \TieDensity term in the statement.}
+
 The policy achieving the result of Theorem~\ref{thm:main-intro} is

### 2018-06-05 lower_bound.tex
significant edits throughout

@@
 showing that even in very simple settings, a (logarithmic) dependence
-on $T$ is typicaly unavoidable for \emph{any} incentivization strategy.
+on $T$ is typically unavoidable for \emph{any} incentivization strategy.
 
@@
 whose attribute vectors are $(0,0)$ and $(0,1)$, respectively.
-Agents types are distributed uniformly on the (edge of the)
+Agent types are distributed uniformly on the (edge of the)
 two-dimensional unit square%
@@
 The present choice is solely for ease of notation.}  
-$\Set{\AgV}{\max(\Ag{1}, \Ag{2}) = 1}$,
+$\Set{\AgV}{\max(|\Ag{1}|, |\Ag{2}|) = 1}$,
 with density $\frac{1}{8}$.
+\dkcomment{I added the absolute values. Seemed wrong without, but
+  please check!}
 Because $\AgV \cdot (0,0) = 0$ and $\AgV \cdot (0,1) = \Ag{2}$,
 the best choice for agent \AgV is arm $(0,1)$ iff $\Ag{2} > 0$,
-i.e., the top half of the unit circle square the arm $(0,1)$,
+i.e., the top half of the unit square prefers the arm $(0,1)$,
 and the bottom half prefers the arm $(0,0)$.

### 2018-06-05 payment-proof.tex
significant edits throughout

@@
 algorithm, i.e., the random draws \AgentV{t} of agents and the
-noise \NoiseV[t] in the draws the pulled arms,
+noise \NoiseV[t] in the draws of the pulled arms,
 with an infinite time horizon.
@@
 
+\dkcomment{Did we forget a sum over \SP here?}
+
 We now lower-bound $s^{2/5} \geq 1$, split off the term for $\ell=1$

### 2018-06-05 problem_setting.tex
significant edits throughout

@@
 \pfedit{(We are also free to create new attributes that are nonlinear transformations of existing attributes.)}
+\dkcomment{I have no idea what this sentence refers to.}
 
@@
 (\ArmEV{0}{i} + \sum_{t'<t: \Pull{t'} = i} \ObsV{t'})$;
-here, \ArmEV{i}{0} is a single draw $\ArmV{i} + \NoiseV$ for arm $i$.
+here, \ArmEV{0}{i} is a single draw $\ArmV{i} + \NoiseV$ for arm $i$.
 (In other words, we assume each arm is pulled once for free at time 0.)
+\dkedit{For a justification of the assumption that agents can observe
+the actual noisy vectors \ObsV{t'} of past pulls, see
+Section~\ref{sec:introduction}.}
 
@@
 
-\pfedit{
-We assume above that the distribution $\AgentDist$ over preference vectors is known.
-In practice, one would estimate this from agents' selections and the attribute estimates and offered payments on which they were based.
-While we do not show it, we hypothesize that our regret guarantees only change by constants as long as our estimate of the conditional probability of pulling an arm is correct within a constant factor (our algorithm depends on this quantity).
-}
+We assume above that the distribution $\AgentDist$ over preference
+vectors is known to the principal.
+In practice, a principal would estimate this distribution from agents'
+selections and the attribute estimates and offered payments on which
+they were based.
+While we do not show it, we hypothesize that our regret guarantees
+only change by constants as long as the principal's estimate of the
+conditional probability of pulling an arm is correct to within a
+constant factor.
+\dkdelete{(our algorithm depends on this quantity).}
 
@@
 breaking ties arbitrarily (but consistently).
+\dkedit{Notice that based on Assumption~\ref{A1} below,
+  \Best{\AgV} and \Second{\AgV} are unique with probability 1.}
 
@@
 
-Let $\MinProb = \min_{i} \Prob[\AgentDist]{\Best{\AgV} = i}$
+Let $\MinProb = \min_{i} \Prob[\AgV \sim \AgentDist]{\Best{\AgV} = i}$
 denote the minimum (over all arms) fraction of users that prefer any
@@
 Near-ties have vanishing probability; 
-that is, there exists a constant \TieDensity such that for all $z \in \R^+$,
-%for all pairs $i,i'$ of arms and 
-$\AlmostTied{z} \leq \TieDensity \cdot z$.
+that is, there exist constants
+\dkedit{$\TieDensity, \TieCutoff \geq \frac{\MinProb}{2 \TieDensity}$
+such that 
+$\AlmostTied{z} \leq \TieDensity \cdot z$ for all $z \leq \TieCutoff$.}
 \end{assumption}
 
-We emphasize that this assumption implies ties happen with probability $0$.
+\dkedit{
+The requirement that $\TieCutoff \geq \frac{\MinProb}{2 \TieDensity}$
+is not restrictive.
+Because \TieDensity and \TieCutoff are both constants,
+we could simply increase \TieDensity.
+Perhaps even more simply, $\MinProb \leq 1/\ARMNUM$,
+while \TieCutoff is a constant,
+so an alternative is to decrease \MinProb by a suitable constant factor.
 
-\paragraph{Role of parameters:}
-Our problem setting is characterized by many 
-parameters.
+Assumption~\ref{A1} implies that ties happen with probability $0$.
+One special case of interest we discuss below is
+$\TieDensity = 0$. This case arises when there is a cutoff
+\TieCutoff such that only a measure-zero set of agents has two best arms
+within utility \TieCutoff of each other.
+In particular, $\TieDensity = 0$ happens whenever \AgentDist is discrete,
+i.e., supported on a finite set of types.}
+
+\paragraph{Roles of parameters:}
+Our problem setting is characterized by many parameters.
 Of these, we consider \ARMNUM, $\MinProb \leq 1/\ARMNUM$ and $T$ to be
-the key parameters, while we consider $\sigma, \Diam, d, \TieDensity$ to be
-constant.
+the key parameters, while we consider
+$\sigma, \Diam, d, \TieDensity, \TieCutoff$ to be constant.
 We track all parameters through most of our proofs,
@@
 except where we illustrate a specific point.
+\dkedit{In particular, we consider $d$ a constant, because users
+typically evaluate products (or restaurants) by a small number of
+relevant features.}

### 2018-06-05 result_discussion.tex
significant edits throughout

@@
 constant in $T$;
-thus, the algorithm achieves constant regret for constant payment. 
-The case $\TieDensity = 0$ arises, for instance, in the case of a
-discrete distribution for agents.
-In fact, in the case of a discrete distribution of agents,
-it is possible to modify the algorithm to reduce the dependence on
-\MinProb from exponential to polynomial.
+thus, the algorithm achieves constant regret using constant payment. 
+\dkedit{As discussed in Section~\ref{sec:prob},
+the case $\TieDensity = 0$ arises, for instance, for
+discrete agent distributions.}
+In fact, in the case of a discrete agent distribution,
+it is possible to modify the algorithm to \dkedit{also}
+reduce the dependence on \MinProb from exponential to polynomial.
 Theorem~\ref{rst:discrete} (given later) states that the modified

### 2018-06-05 abstract.tex
edits to abstract

--- 2018-02-17 abstract.tex
@@
 We consider the problem of incentivizing exploration with heterogeneous agents.
-In this problem, bandit arms provide vector-valued outcomes equal to an unknown
+In this problem, \ARMNUM bandit arms provide vector-valued outcomes equal to an unknown
 arm-specific attribute vector,
@@
 can offer incentive payments for pulling specific arms
-in order to encourage agents to explore underplayed arms.
+to encourage agents to explore underplayed arms.
 The principal seeks to minimize the total expected cumulative regret
@@
 
-We propose an algorithm that incentivizes arms played infrequently in the
-past whose probability of being played in the next round would be small
+We propose an algorithm that incentivizes infrequently played arms 
+whose probability of being played in the next round would be small
 without incentives.
@@
 polynomials in \ARMNUM and $1/\MinProb$.
-For discrete preferences, the regret dependence on $T$ can be
+For discrete preferences, the regret's dependence on $T$ can be
 eliminated entirely, giving constant (depending only polynomially on
@@
 It arises because even unobserved heterogeneity in agent preferences
-allows exploitation of arms to also explore arms fully;
+causes exploitation of arms to also explore arms fully;
 succinctly, heterogeneity provides free exploration.

### 2018-06-05 introduction.tex
edits to the intro to tighten languange and save some space

@@
 
-Many websites and apps are designed to facilitate joint discovery,
-sharing, and recommendations of content.
-Such sites include news, photo, and video sharing sites,
-sites to review restaurants, hotels, or travel experiences,
-online stores at which users write reviews (such as Amazon),
+Many websites and apps facilitate joint discovery,
+sharing, and recommendation of content.
+This includes news-, photo-, and video-sharing sites;
+sites that host user-written reviews of products, restaurants, hotels, and travel experiences;
 and citizen science projects
-(such as eBird \citep{sullivan2009ebird,xue-ebird} or Galaxy Zoo \citep{lintott-galaxy-zoo}).
-By learning from the experiences of other users, individuals can
-improve their own experience \citep{schmit2017human}.
+such as eBird \citep{sullivan2009ebird,xue-ebird} and Galaxy Zoo \citep{lintott-galaxy-zoo}.
+Users of these sites improve their own experiences 
+by learning from the experiences of others 
+\citep{schmit2017human}.
 
 Viewed more abstractly, users jointly explore a space of
-many options (products, news stories, photos, birdwatching sites,
-patches of sky to train their telescopes on, $\ldots$),
+options (products, news stories, photos, birdwatching sites,
+%patches of sky to train their telescopes on, 
+$\ldots$),
 with the implicit goal of identifying the ``best'' ones.
-Therefore, such scenarios can be fruitfully modeled in a bandit
+Such scenarios are often modeled in a bandit
 learning framework.
-However, contrary to standard bandit settings, the utilities of the
-decision makers (the users) are not aligned with the overall utility.
-Societally (i.e., in a suitable aggregate over all users),
-it would be desirable to engage in considerable exploration of
-different options, so as to provide higher rewards for a large number
-of future users.
-However, individual users only interact with the site a limited number
-of times, and therefore have little incentive for exploration.
-A particularly clean model is obtained when each user interacts with the
-site only once, and hence has no intrinsic utility for exploration. 
-This model has been the subject of prior work, and forms the basis of
-the present submission.
+However, unlike standard bandit settings, the utilities of the
+decision makers (the users) are not aligned with overall utility.
+Societally (i.e., in a suitable aggregate over users),
+substantial exploration of options could provide higher future rewards.
+However, individual users interact with the site a limited number
+of times, and therefore have little incentive to explore.
+Recent work has focused on the setting where users interact only once, 
+and so have no intrinsic incentive to explore.
 
-To effect an outcome close to societally optimal,
-it is necessary to provide exploration incentives to the individual users.
-This was noted in two recent lines of work:
+Two recent lines of work have shown that
+effecting a societally near-optimal outcome in this setting requires
+explicitly incentivizing exploration:
 \citet{kremer2014implementing}
@@
 \citet{mansour2015bayesian,mansour2016bayesian,mansour2018competition}
-(see \cite{slivkins:asymmetry} for a high-level overview)
+(see \cite{slivkins:asymmetry} for an overview)
 assume that the site (also called the \emph{principal}) has an
 informational advantage in being the only one to observe the results
-of past arm pulls.
-(Such an assumption applies, for instance, to route recommendations in
-driving.)
-The principal can exploit her%
+of past arm pulls
+(as in driving route recommendations).
+The principal can use her%
 \footnote{We use male pronouns to refer to users and female pronouns
   to refer to the principal.}
-advantage and make recommendations to the individual agents that 
-are in their best interest to follow.
+advantage to induce exploration by recommending apparently sub-optimal arms,
+as long as agents cannot do better on their own.
 \citet{frazier2014incentivizing} and 
@@
 past arm pulls are publicly observable
-(such as reviews on an online retail site).
-They instead suppose that the principal can offer payments to users as
+(as on a review-sharing site).
+They suppose the principal can incentivize exploration by offering payments to users as
 a reward for pulling particular arms.
-We follow the model of \citet{frazier2014incentivizing} and
-\citet{han2015incentivizing} 
-and consider a multi-armed bandit model in which the principal can
-offer payments to the users for pulling particular arms.
+We follow this second model.
+% We follow the model of \citet{frazier2014incentivizing} and
+% \citet{han2015incentivizing} 
+% and consider a multi-armed bandit model in which the principal can
+% offer payments to the users for pulling particular arms.
 
 Past work has assumed that users are homogeneous, i.e., the expected
-reward a user derives from an arm is the same for all users.%
+reward derived from an arm is the same for all users.%
 \footnote{\citet{han2015incentivizing} assume that users are
@@
 In reality, users have different preferences, e.g., gastronomic,
-political, aesthetic, practical, etc.
+political, aesthetic, practical.
 Indeed, the websites and mobile apps most widely used for joint discovery,
 sharing, and recommendation of content tend to concern products and items 
-with large amounts of heterogeneity in preferences (movies, restaurants,
+with heterogeneity in preferences (movies, restaurants,
 videos, travel experiences), and not items which have a universally
@@
 and thus where online
-platforms tend to provide the greatest value.  Thus, we see an appropriate
+platforms provide the most value.  Thus, we see an appropriate
 accounting for heterogeneity as critical to an understanding of incentivizing

### 2018-06-05 abstract.tex
edits to abstract and intro

@@
 preferences are drawn, but not the specific draws,
-can offer incentive payments for pulling specific arms
+can offer \pfedit{arm-specific} incentive payments 
 to encourage agents to explore underplayed arms.
@@
 
-We propose an algorithm that incentivizes infrequently played arms 
+We propose an algorithm that incentivizes \pfedit{infrequently played arms}
 whose probability of being played in the next round would be small
@@
 polynomials in \ARMNUM and $1/\MinProb$.
-For discrete preferences, the regret's dependence on $T$ can be
+For discrete preferences, the \pfedit{regret's} dependence on $T$ can be
 eliminated entirely, giving constant (depending only polynomially on
-\ARMNUM and $1/\MinProb$) expected regret and payments.
+\ARMNUM and $1/\MinProb$) expected regret and payments\pfdelete{where \ARMNUM is the number of arms}.
 This constant regret stands in contrast to the $\Theta(\log(T))$ dependence of
@@
 It arises because even unobserved heterogeneity in agent preferences
-causes exploitation of arms to also explore arms fully;
+\pfedit{causes} exploitation of arms to also explore arms fully;
 succinctly, heterogeneity provides free exploration.

### 2018-06-05 introduction.tex
edits to abstract and intro

@@
 
+\pfedit{
 Many websites and apps facilitate joint discovery,
@@
 \citep{schmit2017human}.
+}
 
@@
 Societally (i.e., in a suitable aggregate over users),
-substantial exploration of options could provide higher future rewards.
+\pfedit{substantial exploration of options could provide higher future rewards.}
 However, individual users interact with the site a limited number
 of times, and therefore have little incentive to explore.
-Recent work has focused on the setting where users interact only once, 
-and so have no intrinsic incentive to explore.
+\pfedit{Recent work has focused on the setting where users interact only once, 
+and so have no intrinsic incentive to explore.}
 
 Two recent lines of work have shown that
-effecting a societally near-optimal outcome in this setting requires
-explicitly incentivizing exploration:
+effecting a societally \pfedit{near-optimal} outcome in this setting \pfedit{requires
+explicitly inducing exploration}:
 \citet{kremer2014implementing}
@@
   to refer to the principal.}
-advantage to induce exploration by recommending apparently sub-optimal arms,
-as long as agents cannot do better on their own.
+\pfedit{advantage to induce exploration by recommending apparently sub-optimal arms,
+as long as agents cannot do better on their own.}
 \citet{frazier2014incentivizing} and 
@@
 past arm pulls are publicly observable
-(as on a review-sharing site).
-They suppose the principal can incentivize exploration by offering payments to users as
-a reward for pulling particular arms.
-We follow this second model.
-% We follow the model of \citet{frazier2014incentivizing} and
-% \citet{han2015incentivizing} 
-% and consider a multi-armed bandit model in which the principal can
-% offer payments to the users for pulling particular arms.
+\pfedit{(as on a review-sharing site)}.
+They suppose the principal can \pfedit{incentivize exploration} by offering \pfedit{arm-specific reward payments}.
+\pfedit{We follow this second model.}
 
-Past work has assumed that users are homogeneous, i.e., the expected
-reward derived from an arm is the same for all users.%
-\footnote{\citet{han2015incentivizing} assume that users are
+Past work has assumed \pfedit{users have homogeneous preferences over arms, i.e., the expected
+reward derived from an arm is the same for all users}.
+(\citet{han2015incentivizing} \pfedit{models users that} are
 heterogeneous in their tradeoff between utility derived from arm pulls
-and utility derived from the principal's payment.}
+and utility derived from the principal's payment,
+\pfedit{but assumes preferences across arms are homogenous.})
 In reality, users have different preferences, e.g., gastronomic,
@@
 with heterogeneity in preferences (movies, restaurants,
-videos, travel experiences), and not items which have a universally
+videos, travel experiences), and not items \pfedit{with} a universally
 agreed-on best order.
 This is perhaps because regimes with heterogeneous preferences are the
-ones where discovery of the best items is the most difficult for people, 
+ones where \pfedit{people have the most difficulty discovering} the best items, 
 and thus where online
-platforms provide the most value.  Thus, we see an appropriate
-accounting for heterogeneity as critical to an understanding of incentivizing
+platforms provide the most value.  
+Thus, we see an appropriate
+accounting for heterogeneity as critical to incentivizing
 exploration in online communities.
 
+\pfedit{In this work, we present the first algorithm and analysis (of which we
+are aware) for incentivizing exploration when users have heterogeneous 
+preferences over arms.}
+\pfedit{Our analysis provides insight into the
+impact of user heterogeneity on the principal's ability to achieve
+high social utility with low incentive payments,
+and on the best approaches for doing so.}
 Heterogeneity presents both a challenge and an opportunity.
 On the one hand, unobserved heterogeneity hides critical
-information about an agent's preferences from the principal.
-On the other hand, heterogeneity also presents her an opportunity,
-through the possibility of ``free exploration.''
-Even when left unincentivized, agents will
-play a variety of arms, revealing information about the arms' attributes.
+information about an agent's preferences from the principal,
+\pfedit{making her unaware of agents' preferred arms.
+Thus, even with an unlimited incentive budget, incentivizing 
+pulls according to a standard multi-armed bandit algorithm does not provide
+low regret.  Instead, she must use incentives sparingly and 
+allow agents to reveal their preferences through action.}
+On the other hand, heterogeneity also \pfedit{offers}
+the possibility of ``free exploration.''
+Even \pfdelete{when left} unincentivized, agents will
+play a variety of arms, revealing information about their attributes.
 This stands in sharp contrast to the case of homogeneous preferences,
-where unincentivized agents will herd onto a single apparently best arm;
-thus, effecting essentially any exploration at all requires incentives.
+where unincentivized agents will herd onto a single apparently best arm,
+\pfedit{and where} effecting essentially any exploration at all requires incentives.
 
-In order to take advantage of unobserved heterogeneity,
-the principal has to give up some control, allowing the agent to
-reveal his preferences through action, rather than obscuring them with
-incentives.
-However, she cannot give up control completely,
-and must use incentives to force agents to explore against their
-preferences, for the greater good.
-
-With these challenges and opportunities in mind, our goal is to understand the
+\pfdelete{
+With these challenges and opportunities in mind, 
+our goal is to understand the
 impact of user heterogeneity on the principal's ability to achieve
@@
 heterogeneous preference setting differ from those in the homogeneous one.
-
-Toward that end, we model our setting as follows.
-(We describe our model at a high level here,
-with formal definitions given in Section~\ref{sec:prob}.)
+Toward that end, we model our setting as follows.}
+We describe our model at a high level here,
+with formal definitions given in Section~\ref{sec:prob}.
 The \ARMNUM arms and users (or \emph{agents})
@@
 vector (based on past noisy observations) maximizes their reward.
-\dkedit{This assumption requires agents to have access to aggregate
+This assumption requires agents to have access to aggregate
 information about the feature vector estimates of all (relevant) arms. 
@@
 While platforms could in principle manipulate the display of such
-data, most have an incentive to be seen as truthful.}
+data, most have an incentive to be seen as truthful.
 %\pfedit{Agents' ability to effectively base decisions on all past observations models platforms' abilities to aggregate and effectively display past feedback, through simple averages of ratings and automatic summarization of full-text reviews \citep{wang2010product,liu2012movie,abulaish2009feature}.
@@
 The principal can incentivize agents to pull particular arms by
-offering rewards for the specific arm.
+offering \pfedit{arm-specific payments}.
 The principal's goal is to keep the cumulative regret across all
 agents small, while incurring only small total payments.
+
 Our main theorem can be stated informally as follows:
@@
 There is a policy that achieves expected 
-cumulative regret $O (\ARMNUM \e^{2/\MinProb} + \dkedit{\TieDensity} \ARMNUM \log^3(T))$,
+cumulative regret $O (\ARMNUM \e^{2/\MinProb} + \TieDensity \ARMNUM \log^3(T))$,
 using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
@@
 
-\dkcomment{Added the \TieDensity term in the statement.}
-
 The policy achieving the result of Theorem~\ref{thm:main-intro} is
-quite simple: it mostly lets agents exploit arms, but incentivizes
+simple: it mostly lets agents exploit arms, but incentivizes
 them to explore when arms appear unlikely to be pulled without incentives.

### 2018-06-05 problem_setting.tex
edits to abstract
edits to abstract and intro

@@
 The \ArmV{i} are (adversarially) fixed, and unknown to the agents
-or the principal.
+and the principal.
 When arm $i$ is pulled, its current utility-relevant features are
@@
 i.e., agents have linear preferences.
-\pfedit{(We are also free to create new attributes that are nonlinear transformations of existing attributes.)}
-\dkcomment{I have no idea what this sentence refers to.}
+\pfedit{(Although linear, this model permits additional flexibility through the addition of derived attributes that are nonlinear transformation of some original attribute vector: define $\Agent{t}{i} = f_i(\AgentV{t})$ for some known nonlinear functions $f_i$ and $i=d+1,\ldots,d'$, and then increase $d$ to $d'$.)}
+\pfcomment{I added some detail.
+Is it clear now David?
+I'm just talking about a standard trick in linear models, where you add nonlinear transformations of your feature vector and have a linear model in higher dimensions.}
 

### 2018-06-05 problem_setting.tex
more edits to abstract, section 2

@@
 i.e., agents have linear preferences.
-\pfedit{(Although linear, this model permits additional flexibility through the addition of derived attributes that are nonlinear transformation of some original attribute vector: define $\Agent{t}{i} = f_i(\AgentV{t})$ for some known nonlinear functions $f_i$ and $i=d+1,\ldots,d'$, and then increase $d$ to $d'$.)}
+\pfedit{(Although linear, this model permits additional flexibility through the addition of derived attributes that are nonlinear transformation of some original attribute vector: define $\Agent{t}{i} = \Psi_i(\AgentV{t})$ for some known nonlinear functions $\Psi_i$ where $i=d+1,\ldots,d'$, and then increase $d$ to $d'$.)}
 \pfcomment{I added some detail.
@@
 (In other words, we assume each arm is pulled once for free at time 0.)
-\dkedit{For a justification of the assumption that agents can observe
+For a justification of the assumption that agents can observe
 the actual noisy vectors \ObsV{t'} of past pulls, see
-Section~\ref{sec:introduction}.}
+Section~\ref{sec:introduction}.
 
@@
 constant factor.
-\dkdelete{(our algorithm depends on this quantity).}
 
@@
 breaking ties arbitrarily (but consistently).
-\dkedit{Notice that based on Assumption~\ref{A1} below,
-  \Best{\AgV} and \Second{\AgV} are unique with probability 1.}
+Notice that based on Assumption~\ref{A1} below,
+  \Best{\AgV} and \Second{\AgV} are unique with probability 1.
 

### 2018-06-05 problem_setting.tex
going through edits from david

@@
   \Best{\AgV} and \Second{\AgV} are unique with probability 1.
+\pfcomment{Why is \Second{\AgV} unique with probability 1?  I don't think that is implied.  Can I remove that part of the statement?}
 
@@
 that is, there exist constants
-\dkedit{$\TieDensity, \TieCutoff \geq \frac{\MinProb}{2 \TieDensity}$
+$\TieDensity, \TieCutoff \geq \frac{\MinProb}{2 \TieDensity}$
 such that 
-$\AlmostTied{z} \leq \TieDensity \cdot z$ for all $z \leq \TieCutoff$.}
+$\AlmostTied{z} \leq \TieDensity \cdot z$ for all $z \leq \TieCutoff$.
 \end{assumption}
 
-\dkedit{
 The requirement that $\TieCutoff \geq \frac{\MinProb}{2 \TieDensity}$
@@
 In particular, $\TieDensity = 0$ happens whenever \AgentDist is discrete,
-i.e., supported on a finite set of types.}
+i.e., supported on a finite set of types,
+\pfedit{and each type has a unique best arm.}
 
@@
 except where we illustrate a specific point.
-\dkedit{In particular, we consider $d$ a constant, because users
+\pfcomment{We report Thm 1 with $L$ in it.  Maybe we can still leave this sentence like it is.  I'll revisit later, if someone else doesn't resolve this first.}
+In particular, we consider $d$ a constant, because users
 typically evaluate products (or restaurants) by a small number of
-relevant features.}
+relevant features.

### 2018-06-05 abstract.tex
went over abstract and Sections 1/2

--- 2018-06-05 abstract.tex
@@
 preferences are drawn, but not the specific draws,
-can offer incentive payments for pulling specific arms
+can offer arm-specific incentive payments 
 to encourage agents to explore underplayed arms.
@@
 
-We propose an algorithm that incentivizes infrequently played arms 
+We propose an algorithm that incentivizes \dkedit{arms played
+  infrequently in the past}
 whose probability of being played in the next round would be small

### 2018-06-05 introduction.tex
went over abstract and Sections 1/2

@@
 
-\pfedit{
 Many websites and apps facilitate joint discovery,
@@
 \citep{schmit2017human}.
-}
 
@@
 Societally (i.e., in a suitable aggregate over users),
-\pfedit{substantial exploration of options could provide higher future rewards.}
+substantial exploration of options could provide higher future rewards.
 However, individual users interact with the site a limited number
 of times, and therefore have little incentive to explore.
-\pfedit{Recent work has focused on the setting where users interact only once, 
-and so have no intrinsic incentive to explore.}
+Recent work has focused on the setting in which users interact only once, 
+and therefore have no intrinsic incentive to explore.
 
 Two recent lines of work have shown that
-effecting a societally \pfedit{near-optimal} outcome in this setting \pfedit{requires
-explicitly inducing exploration}:
+effecting a societally near-optimal outcome in this setting requires
+explicitly inducing exploration:
 \citet{kremer2014implementing}
@@
   to refer to the principal.}
-\pfedit{advantage to induce exploration by recommending apparently sub-optimal arms,
-as long as agents cannot do better on their own.}
+advantage to induce exploration by recommending apparently sub-optimal arms,
+as long as agents cannot do better on their own.
 \citet{frazier2014incentivizing} and 
@@
 past arm pulls are publicly observable
-\pfedit{(as on a review-sharing site)}.
-They suppose the principal can \pfedit{incentivize exploration} by offering \pfedit{arm-specific reward payments}.
-\pfedit{We follow this second model.}
+(as on a review-sharing site).
+They suppose that the principal can incentivize exploration by offering arm-specific reward payments.
+We follow this second model.
 
-Past work has assumed \pfedit{users have homogeneous preferences over arms, i.e., the expected
-reward derived from an arm is the same for all users}.
-(\citet{han2015incentivizing} \pfedit{models users that} are
+Past work has assumed that users have homogeneous preferences over
+arms, i.e., the expected reward derived from an arm is the same for all users.
+(\citet{han2015incentivizing} model users that are
 heterogeneous in their tradeoff between utility derived from arm pulls
 and utility derived from the principal's payment,
-\pfedit{but assumes preferences across arms are homogenous.})
+but assume that preferences across arms are homogenous.)
 In reality, users have different preferences, e.g., gastronomic,
@@
 with heterogeneity in preferences (movies, restaurants,
-videos, travel experiences), and not items \pfedit{with} a universally
+videos, travel experiences), and not items with a universally
 agreed-on best order.
 This is perhaps because regimes with heterogeneous preferences are the
-ones where \pfedit{people have the most difficulty discovering} the best items, 
-and thus where online
-platforms provide the most value.  
+ones where people have the most difficulty discovering the best items, 
+and thus where online platforms provide the most value.  
 Thus, we see an appropriate
@@
 
-\pfedit{In this work, we present the first algorithm and analysis (of which we
+In this work, we present the first algorithm and analysis (of which we
 are aware) for incentivizing exploration when users have heterogeneous 
-preferences over arms.}
-\pfedit{Our analysis provides insight into the
+preferences over arms.
+Our analysis provides insight into the
 impact of user heterogeneity on the principal's ability to achieve
 high social utility with low incentive payments,
-and on the best approaches for doing so.}
+and on the best approaches for doing so.
 Heterogeneity presents both a challenge and an opportunity.
@@
 information about an agent's preferences from the principal,
-\pfedit{making her unaware of agents' preferred arms.
+making her unaware of agents' preferred arms.
 Thus, even with an unlimited incentive budget, incentivizing 
@@
 low regret.  Instead, she must use incentives sparingly and 
-allow agents to reveal their preferences through action.}
-On the other hand, heterogeneity also \pfedit{offers}
+allow agents to reveal their preferences through action.
+On the other hand, heterogeneity also offers
 the possibility of ``free exploration.''
-Even \pfdelete{when left} unincentivized, agents will
+Even unincentivized, agents will
 play a variety of arms, revealing information about their attributes.
@@
 where unincentivized agents will herd onto a single apparently best arm,
-\pfedit{and where} effecting essentially any exploration at all requires incentives.
+and where effecting essentially any exploration at all requires incentives.
 
-\pfdelete{
-With these challenges and opportunities in mind, 
-our goal is to understand the
-impact of user heterogeneity on the principal's ability to achieve
-high social utility with low incentive payments,
-and on the best approaches for doing so.
-We wish to understand whether incentivizing exploration with
-heterogeneous preferences  is ``harder'' or ``easier'' than with
-homogeneous ones,
-and to understand how exploration strategies that do well in the
-heterogeneous preference setting differ from those in the homogeneous one.
-Toward that end, we model our setting as follows.}
+% With these challenges and opportunities in mind, 
+% our goal is to understand the
+% impact of user heterogeneity on the principal's ability to achieve
+% high social utility with low incentive payments,
+% and on the best approaches for doing so.
+% We wish to understand whether incentivizing exploration with
+% heterogeneous preferences  is ``harder'' or ``easier'' than with
+% homogeneous ones,
+% and to understand how exploration strategies that do well in the
+% heterogeneous preference setting differ from those in the homogeneous one.
+% Toward that end, we model our setting as follows.
 We describe our model at a high level here,
@@
 The principal can incentivize agents to pull particular arms by
-offering \pfedit{arm-specific payments}.
+offering arm-specific payments.
 The principal's goal is to keep the cumulative regret across all
@@
 between agents' arm preferences
-(in a sense made precise in Section~\ref{subsec:discrete}).
+(in a sense made precise in \dkedit{Section~\ref{sec:prob}}).
 There is a policy that achieves expected 

### 2018-06-05 problem_setting.tex
went over abstract and Sections 1/2

--- 2018-06-05 problem_setting.tex
@@
 i.e., agents have linear preferences.
-\pfedit{(Although linear, this model permits additional flexibility through the addition of derived attributes that are nonlinear transformation of some original attribute vector: define $\Agent{t}{i} = f_i(\AgentV{t})$ for some known nonlinear functions $f_i$ and $i=d+1,\ldots,d'$, and then increase $d$ to $d'$.)}
-\pfcomment{I added some detail.
-Is it clear now David?
-I'm just talking about a standard trick in linear models, where you add nonlinear transformations of your feature vector and have a linear model in higher dimensions.}
+Although the model is linear, it permits additional flexibility
+through the addition of derived attributes that are nonlinear
+transformation of some original attribute vector.
+\dkedit{One can simply define $\Ag{j} = g_j(\AgV{t})$ for some known
+nonlinear functions $g_j$ and $j=d+1,\ldots,d'$, and then increase the
+number of attributes to $d'$.}
 

### 2018-06-05 problem_setting.tex

--- 2018-06-05 problem_setting.tex
@@
 i.e., agents have linear preferences.
-\pfedit{(Although linear, this model permits additional flexibility through the addition of derived attributes that are nonlinear transformation of some original attribute vector: define $\Agent{t}{i} = \Psi_i(\AgentV{t})$ for some known nonlinear functions $\Psi_i$ where $i=d+1,\ldots,d'$, and then increase $d$ to $d'$.)}
-\pfcomment{I added some detail.
-Is it clear now David?
-I'm just talking about a standard trick in linear models, where you add nonlinear transformations of your feature vector and have a linear model in higher dimensions.}
+Although the model is linear, it permits additional flexibility
+through the addition of derived attributes that are nonlinear
+transformation of some original attribute vector.
+\dkedit{One can simply define $\Ag{j} = g_j(\AgV)$ for some known
+nonlinear functions $g_j$ and $j=d+1,\ldots,d'$, and then increase the
+number of attributes to $d'$.}
 

### 2018-06-05 result_discussion.tex

@@
 thus, the algorithm achieves constant regret using constant payment. 
-\dkedit{As discussed in Section~\ref{sec:prob},
+As discussed in Section~\ref{sec:prob},
 the case $\TieDensity = 0$ arises, for instance, for
-discrete agent distributions.}
+discrete agent distributions.
 In fact, in the case of a discrete agent distribution,
-it is possible to modify the algorithm to \dkedit{also}
+it is possible to modify the algorithm to also
 reduce the dependence on \MinProb from exponential to polynomial.
@@
 the expected regret of any algorithm.
-The instance is very simple: it has two arms, one of which has known
+The instance is \pfdelete{very} simple: it has two arms, one \pfedit{with}
 attributes; in addition, one draw from the other arm is observed in
@@
 As shown in Theorem~\ref{rst:known-p},
-the modified algorithm will have expected regret at most
+the modified algorithm \pfedit{has} expected regret at most
 $O \left(\frac{\ARMNUM}{\MinProb^3}
@@
 principal's direction without requiring payment.
-(Notice that this setting violates our Assumption~\ref{A3},
+(\pfedit{This} setting violates our Assumption~\ref{A3},
 so our bounds do not apply to it.)
@@
 multi-armed bandit problem;
-but when preferences are discrete, the constant regret (rather than
-$\Theta(\log T)$) surpasses a standard multi-armed bandit.
-This may seem surprising, because our setting is one in which the
-principal has both less control and less information than in the
+but when preferences are discrete, the constant regret
+surpasses \pfedit{the $\Theta(\log(T))$ achievable in the} standard multi-armed bandit.
+This may seem surprising, because the
+\pfedit{principal in our setting} has both less control and less information than in the
 standard bandit setting.
-The result arises because heterogeneity in preferences indeed provides
-free exploration, in which all of the arms can be pulled infinitely
-often without incurring regret.
+The result arises because heterogeneity in preferences \pfdelete{indeed} provides
+free exploration, \pfedit{and allows} all of the arms \pfedit{to} be pulled infinitely
+often without incurring regret \pfedit{once estimates are accurate enough}.
 
@@
 improvements compared to the standard bandit setting.
-Indeed, consider a version in which agents are still heterogeneous,
-but the principal has the power to pull arms directly.
-Unless the heterogeneity can be observed (i.e., the principal knows
-the agents' types), the principal will be unable to correctly choose
+Indeed, \pfedit{suppose} agents are still heterogeneous,
+but the principal \pfedit{pulls} arms directly.
+Unless \pfedit{the principal can also observe}
+the agents' types, \pfedit{she} will be unable to correctly choose
 each agent's preferred arm,
 even with infinite exploration of arm attributes.
-Hence, in this setting, the regret will grow as $\Omega(T)$.
+\pfedit{Regret will then} 
+grow as $\Omega(T)$.
 

### 2018-06-05 algorithm_intro.tex
edits through into of section 4

@@
 by the next (random) agent based on the current estimates. 
+\pfedit{(Our assumption of a continuous noise distribution and one free pull ensure that 
+ties in $\AgV \cdot \ArmEV{t}{i}$ between arms occur with probability $0$.)} 
 \end{itemize}
@@
 Thus, the fraction of agents who misidentify their best arm decreases.
-Because for each arm, enough agents have a true preference for this
-arm, once the arms' attribute vectors are learned well enough,
+Because \pfedit{each arm has enough agents that prefer its true attribute vector}, 
+once the arms' attribute vectors are learned well enough
 the algorithm will not need to incentivize any more,
 resulting in a payment bound independent of $T$.
-Similarly, the regret will decrease, and mostly accrue
+Similarly, \pfedit{instantaneous} regret will decrease, and mostly accrue
 due to ``problematic'' agents who are nearly tied in their preferences
-between their top two arm choices.
-The detailed analysis following this outline is somewhat subtle, though,
-due to the dependence between the agents' arm pulls and the
+between their top two \pfedit{arms}.
+The detailed analysis following this outline is \pfedit{complicated by}
+dependence between the agents' arm pulls and the
 estimates which in turn are based on past arm pulls.
@@
 the events \AccE{t}{i}{j}{x}
-(and hence, by union bound, \AccEU{t}{x})
+(and hence, by \pfedit{a} union bound, \AccEU{t}{x})
 have high probability,

### 2018-06-05 introduction.tex
resolving comments from david in section 1 to 3

@@
 between agents' arm preferences
-(in a sense made precise in \dkedit{Section~\ref{sec:prob}}).
+(in a sense made precise in Section~\ref{sec:prob}).
 There is a policy that achieves expected 

### 2018-06-05 problem_setting.tex
resolving comments from david in section 1 to 3

@@
 In fact, the analysis extends straightforwardly to any
-mean-zero sub-Gaussian($\sigma^2$) noise that is independent but not necessarily identically distributed across time.}
+\pfedit{continuous}
+mean-zero sub-Gaussian($\sigma^2$) noise that is independent but not necessarily identically distributed across time.
+\pfcomment{I used continuity below where the algorithm is defined to get rid of ties.}}
 noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.
@@
 transformation of some original attribute vector.
-\dkedit{One can simply define $\Ag{j} = g_j(\AgV)$ for some known
+One can simply define $\Ag{j} = g_j(\AgV)$ for some known
 nonlinear functions $g_j$ and $j=d+1,\ldots,d'$, and then increase the
-number of attributes to $d'$.}
+number of attributes to $d'$.
 

### 2018-06-05 algorithm_general.tex
edits to the end of section 4.1

@@
 Recall that $\sigma$ is the standard deviation of the Gaussian noise.
-Let \LatePhase be a phase cutoff, 
-and let $x_n, x'_n > 0$ be functions satisfying that
+Let \LatePhase be \pfedit{fixed}, 
+and let $x_n, x'_n > 0$ be \pfedit{sequences} satisfying 
 $\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}
@@
 which is almost surely in phase $s$,
-i.e., satisfying $\dkedit{\tau_s} \in [t_s, t_{s+1})$ almost surely.
-\dkcomment{$\tau$ was missing the subscript $s$ here. I think that was
-  a mistake, but am marking it so someone can check.}
+i.e., satisfying $\tau_s \in [t_s, t_{s+1})$ almost surely.
 Then, for any arm $i$, attribute $j$, and phase $s \geq \LatePhase$,

### 2018-06-05 Lemmas.tex
fixed (hopefully) L=0 issue

--- 2018-02-17 Lemmas.tex
@@
 time when arm $i$ is pulled for the \Kth{s} time.
-Under \AccEU{\tau_s}{\frac{p}{4\Diam d \TieDensity}},
+\dkedit{Let $\hat{x} = \frac{1}{2\Diam d}
+  \cdot \min(\TieCutoff, \frac{\MinProb}{2\TieDensity})$.
+Under \AccEU{\tau_s}{\hat{x}},}
 this pull of arm $i$ is not incentivized.
@@
 By Lemma~\ref{lem:right-choice},
-under the event \AccEU{\tau_s}{\frac{\MinProb}{4\Diam d \TieDensity}},
+under the event \dkedit{\AccEU{\tau_s}{\hat{x}}},
 all agent types \AgV with
 $\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}})
-> \frac{\MinProb}{2\TieDensity}$
+> \dkedit{2\Diam d \hat{x}}$
 will pull their best arm \Best{\AgV}.
+Notice that $\dkedit{2\Diam d \hat{x}
+= \min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})}$
 
 By Assmption~\ref{A1},
-%Lemma~\ref{lem:sdelta},
 the measure of agents (across all arms)
 whose best and second-best arm differ in utility by less
-than $\frac{\MinProb}{2\TieDensity}$ is at most $\frac{\MinProb}{2}$.
+than \dkedit{$\min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})$}
+is at most
+\dkedit{$\TieDensity \cdot \min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})
+\leq \frac{\MinProb}{2}$}.
 In particular, this bound holds for agents whose best arm is $i$.

### 2018-06-05 algorithm_payment.tex
fixed (hopefully) L=0 issue

@@
 To make this intuition precise, we set
-$\delta = \frac{\MinProb}{2 \TieDensity}$,
-and $x = x' = \frac{\delta}{2 \Diam d}$
+\dkedit{$x = x' = \frac{1}{2 \Diam d} \cdot \min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})$}
 (which is independent of the phase number $s$).
@@
 $24 \ARMNUM d \cdot \exp \left(
-  -\frac{1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+\dkedit{  - \frac{1.8 s}{256 \Diam^2 d^2 \sigma^2}
+  \cdot \min(\TieCutoff, \frac{\MinProb}{\TieDensity})^2}
 \right)$.
@@
   + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
-    \frac{-1.8 \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)}}  \\
-& = O\left( \max\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}, N\exp\left(\frac{2}{p}\right)\right)
-  + \frac{\ARMNUM^2 d^3 \TieDensity^2 \sigma^2 \Diam^2}{\MinProb^2} \right)
-\; = \; O\left( N\exp\left(\frac{2}{p}\right) \right).
+\dkedit{ - \frac{1.8}{256 \Diam^2 d^2 \sigma^2}
+  \cdot \min(\TieCutoff, \frac{\MinProb}{\TieDensity})^2}
+  \right)}}
+\\ & = O\left( \max \left(
+     \frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3},
+\dkedit{     \frac{\ARMNUM \Diam^3 d^3 \sigma^3}{\TieCutoff^3},}
+     \ARMNUM \exp \left(\frac{2}{\MinProb} \right) \right)
++ \max \left(
+     \frac{\ARMNUM^2 d^3 \TieDensity^2 \sigma^2 \Diam^2}{\MinProb^2},
+\dkedit{ \frac{\ARMNUM^2 d^3 \sigma^2 \Diam^2}{\TieCutoff^2}}
+\right) \right)
+\\ & = O\left( \ARMNUM \exp \left(\frac{2}{\MinProb}\right) \right).
 \end{align*}

### 2018-06-05 problem_setting.tex
fixed (hopefully) L=0 issue

@@
 In fact, the analysis extends straightforwardly to any
-\pfedit{continuous}
-mean-zero sub-Gaussian($\sigma^2$) noise that is independent but not necessarily identically distributed across time.
-\pfcomment{I used continuity below where the algorithm is defined to get rid of ties.}}
+continuous mean-zero sub-Gaussian($\sigma^2$) noise that is
+independent but not necessarily identically distributed across time.
+\dkcomment{Are we actually stating the result in this generality now?
+  If not, then why make the algorithm use continuity, as opposed to
+  that we have Gaussians? If we do make the algorithm that general,
+  then we should just define everything for Gaussians here.}}
 noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.
@@
 \pfcomment{Why is \Second{\AgV} unique with probability 1?  I don't think that is implied.  Can I remove that part of the statement?}
+\dkcomment{It is unique with probablity 1 over the draw of agent types
+  because for z=0, Assumption~\ref{A1} says that there is a measure 0
+  set of agents whose difference between the best and second-best
+  option is z=0. Or am I misunderstanding something?}
 
@@
 Near-ties have vanishing probability; 
-that is, there exist constants
-$\TieDensity, \TieCutoff \geq \frac{\MinProb}{2 \TieDensity}$
-such that 
+that is, there exist constants \dkedit{$\TieCutoff > 0, \TieDensity$} such that 
 $\AlmostTied{z} \leq \TieDensity \cdot z$ for all $z \leq \TieCutoff$.
@@
 
-The requirement that $\TieCutoff \geq \frac{\MinProb}{2 \TieDensity}$
-is not restrictive.
-Because \TieDensity and \TieCutoff are both constants,
-we could simply increase \TieDensity.
-Perhaps even more simply, $\MinProb \leq 1/\ARMNUM$,
-while \TieCutoff is a constant,
-so an alternative is to decrease \MinProb by a suitable constant factor.
+\dkdelete{
+% The requirement that $\TieCutoff \geq \frac{\MinProb}{2 \TieDensity}$
+%is not restrictive.
+%Because \TieDensity and \TieCutoff are both constants,
+%we could simply increase \TieDensity.
+%Perhaps even more simply, $\MinProb \leq 1/\ARMNUM$,
+%while \TieCutoff is a constant,
+%so an alternative is to decrease \MinProb by a suitable constant factor.
+}
 
@@
 i.e., supported on a finite set of types,
-\pfedit{and each type has a unique best arm.}
+and each type has a unique best arm.
 
@@
 Of these, we consider \ARMNUM, $\MinProb \leq 1/\ARMNUM$ and $T$ to be
-the key parameters, while we consider
-$\sigma, \Diam, d, \TieDensity, \TieCutoff$ to be constant.
+the key parameters, \dkedit{and also give some prominence to
+\TieDensity to illustrate an interesting phenomenon.}
+On the other hand, we consider
+$\sigma, \Diam, d$, and \TieCutoff to be constant.
 We track all parameters through most of our proofs,
-but report final results in terms of only the three key parameters,
+but report final results in terms of only the key parameters,
 except where we illustrate a specific point.
-\pfcomment{We report Thm 1 with $L$ in it.  Maybe we can still leave this sentence like it is.  I'll revisit later, if someone else doesn't resolve this first.}
 In particular, we consider $d$ a constant, because users
-typically evaluate products (or restaurants) by a small number of
+typically evaluate products (or restaurants, etc.) by a small number of
 relevant features.

### 2018-06-05 problem_setting.tex
mostly accepted Peter's edits

@@
   that we have Gaussians? If we do make the algorithm that general,
-  then we should just define everything for Gaussians here.}}
+  then we should just define everything generally here.}}
 noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.

### 2018-06-05 algorithm_regret.tex
adding some comments

@@
 The remaining phases are the ones with
-$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2 \TieCutoff^2$.
-Each such phase lasts for at most $\ARMNUM \cdot \log(s)$ steps
+$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2 \TieCutoff^2$.}
+\pfcomment{Is there a typo in the previous line?  Shouldn't it be 
+$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2 / \TieCutoff^2$?
+Or am I missing something?}
+\dkedit{Each such phase lasts for at most $\ARMNUM \cdot \log(s)$ steps
 in expectation by Lemma~\ref{lem:phase-length},

### 2018-06-05 problem_setting.tex
adding some comments

--- 2018-06-05 problem_setting.tex
@@
   option is z=0. Or am I misunderstanding something?}
+  \pfcomment{That argument says that $\Best{\AgV}$ is unique.
+But the second best, $\Second{\AgV}$, doesn't have to be.
+The measure of the set of agents with 0 gap between the second- and third-best  options might not vanish.}
 
@@
 Near-ties have vanishing probability; 
-that is, there exist constants \dkedit{$\TieCutoff > 0, \TieDensity$} such that 
+that is, there exist constants $\TieCutoff > 0, \TieDensity$ such that 
 $\AlmostTied{z} \leq \TieDensity \cdot z$ for all $z \leq \TieCutoff$.
 \end{assumption}
-
-\dkdelete{
-% The requirement that $\TieCutoff \geq \frac{\MinProb}{2 \TieDensity}$
-%is not restrictive.
-%Because \TieDensity and \TieCutoff are both constants,
-%we could simply increase \TieDensity.
-%Perhaps even more simply, $\MinProb \leq 1/\ARMNUM$,
-%while \TieCutoff is a constant,
-%so an alternative is to decrease \MinProb by a suitable constant factor.
-}
 
@@
 Of these, we consider \ARMNUM, $\MinProb \leq 1/\ARMNUM$ and $T$ to be
-the key parameters, \dkedit{and also give some prominence to
-\TieDensity to illustrate an interesting phenomenon.}
+the key parameters, and also give some prominence to
+\TieDensity to illustrate an interesting phenomenon.
 On the other hand, we consider

### 2018-06-05 algorithm_general.tex

@@
 Recall that $\sigma$ is the standard deviation of the Gaussian noise.
-Let \LatePhase be \pfedit{fixed}, 
-and let $x_n, x'_n > 0$ be \pfedit{sequences} satisfying 
+Let \LatePhase be fixed, 
+and let $x_n, x'_n > 0$ be sequences satisfying 
 $\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x_n^2}{16 \sigma^2}}

### 2018-06-05 algorithm_intro.tex

--- 2018-06-05 algorithm_intro.tex
@@
 \label{sec:ub}
-The algorithm achieving the claimed bounds of
+The algorithm achieving the \dkdelete{claimed} bounds of
 Theorems~\ref{rst:budget} and~\ref{rst:regret} is simple.
@@
 by the next (random) agent based on the current estimates. 
+Our assumption of a continuous noise distribution and one free pull
+ensure that ties in $\AgV \cdot \ArmEV{t}{i}$ between arms occur with
+probability $0$.
+\dkcomment{Should we say Gaussian here? Should we write everything in
+  the general model?}
 \end{itemize}
@@
 Thus, the fraction of agents who misidentify their best arm decreases.
-Because for each arm, enough agents have a true preference for this
-arm, once the arms' attribute vectors are learned well enough,
+Because each arm has enough agents that \dkedit{would prefer it based
+  on} its true attribute vector, 
+once the arms' attribute vectors are learned well enough,
 the algorithm will not need to incentivize any more,
 resulting in a payment bound independent of $T$.
-Similarly, the regret will decrease, and mostly accrue
+Similarly, instantaneous regret will decrease, and mostly accrue
 due to ``problematic'' agents who are nearly tied in their preferences
-between their top two arm choices.
-The detailed analysis following this outline is somewhat subtle, though,
-due to the dependence between the agents' arm pulls and the
+between their top two arms.
+The detailed analysis following this outline is complicated by
+dependence between the agents' arm pulls and the
 estimates which in turn are based on past arm pulls.
@@
 the events \AccE{t}{i}{j}{x}
-(and hence, by union bound, \AccEU{t}{x})
+(and hence, by a union bound, \AccEU{t}{x})
 have high probability,

### 2018-06-05 result_discussion.tex

@@
 constant in $T$;
-thus, the algorithm achieves constant regret using constant payment. 
+thus, the algorithm achieves constant regret using constant
+\dkedit{expected payments}. 
 As discussed in Section~\ref{sec:prob},
@@
 the expected regret of any algorithm.
-The instance is \pfdelete{very} simple: it has two arms, one \pfedit{with}
-attributes; in addition, one draw from the other arm is observed in
+The instance is simple: it has two arms, one \pfedit{with}
+attributes; \dkcomment{Should that be ``with \emph{known}
+  attributes''? I don't understand this edit.}
+in addition, one draw from the other arm is observed in
 each step $t$ even when it is not pulled.
@@
 As shown in Theorem~\ref{rst:known-p},
-the modified algorithm \pfedit{has} expected regret at most
+the modified algorithm has expected regret at most
 $O \left(\frac{\ARMNUM}{\MinProb^3}
@@
 principal's direction without requiring payment.
-(\pfedit{This} setting violates our Assumption~\ref{A3},
+(This setting violates our Assumption~\ref{A3},
 so our bounds do not apply to it.)
@@
 but when preferences are discrete, the constant regret
-surpasses \pfedit{the $\Theta(\log(T))$ achievable in the} standard multi-armed bandit.
-This may seem surprising, because the
-\pfedit{principal in our setting} has both less control and less information than in the
-standard bandit setting.
-The result arises because heterogeneity in preferences \pfdelete{indeed} provides
-free exploration, \pfedit{and allows} all of the arms \pfedit{to} be pulled infinitely
-often without incurring regret \pfedit{once estimates are accurate enough}.
+surpasses the $\Theta(\log(T))$ achievable in the standard multi-armed
+bandit \dkedit{setting}.
+This may seem surprising, because the principal in our setting has
+both less control and less information than in the standard bandit setting.
+The result arises because heterogeneity in preferences provides
+free exploration, and allows all of the arms to be pulled infinitely
+often without incurring regret once estimates are accurate enough.
 
@@
 improvements compared to the standard bandit setting.
-Indeed, \pfedit{suppose} agents are still heterogeneous,
-but the principal \pfedit{pulls} arms directly.
-Unless \pfedit{the principal can also observe}
-the agents' types, \pfedit{she} will be unable to correctly choose
-each agent's preferred arm,
+Indeed, suppose that agents are still heterogeneous,
+but the principal pulls arms directly.
+Unless the principal can also observe the agents' types,
+she will be unable to correctly choose each agent's preferred arm,
 even with infinite exploration of arm attributes.
-\pfedit{Regret will then} 
-grow as $\Omega(T)$.
+Regret will then grow as $\Omega(T)$.
 

### 2018-06-05 algorithm_regret.tex
addressed Peter's comments

@@
 The remaining phases are the ones with
-$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2 \TieCutoff^2$.}
-\pfcomment{Is there a typo in the previous line?  Shouldn't it be 
-$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2 / \TieCutoff^2$?
-Or am I missing something?}
+$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2/\TieCutoff^2$.}
 \dkedit{Each such phase lasts for at most $\ARMNUM \cdot \log(s)$ steps
@@
 The total expected regret incurred in these phases is at most
-$100 \ARMNUM \MAXR \log^2(T) \cdot \Diam^3 d^3 \sigma^3 \TieCutoff^3$.}
+$100 \ARMNUM \MAXR \log^2(T) \cdot \Diam^3 d^3 \sigma^3/\TieCutoff^3$.}
 

### 2018-06-05 algorithm_intro.tex
another comment

@@
 Thus, the fraction of agents who misidentify their best arm decreases.
-Because each arm has enough agents that \dkedit{would prefer it based
-  on} its true attribute vector, 
+Because each arm has enough agents that would prefer it based
+  on its true attribute vector, 
 once the arms' attribute vectors are learned well enough,

### 2018-06-05 algorithm_regret.tex
another comment

--- 2018-06-05 algorithm_regret.tex
@@
   formula. Do we need to redefine it here?}
+\pfcomment{Above we define $t_s$ to be the start time of phase $s$.}
 Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}

### 2018-06-05 result_discussion.tex
another comment

@@
 thus, the algorithm achieves constant regret using constant
-\dkedit{expected payments}. 
+expected payments. 
 As discussed in Section~\ref{sec:prob},
@@
 the expected regret of any algorithm.
-The instance is simple: it has two arms, one \pfedit{with}
-attributes; \dkcomment{Should that be ``with \emph{known}
-  attributes''? I don't understand this edit.}
+The instance is simple: it has two arms, one \pfedit{with known}
+attributes; 
 in addition, one draw from the other arm is observed in

### 2018-06-05 problem_setting.tex

@@
 Notice that based on Assumption~\ref{A1} below,
-  \Best{\AgV} and \Second{\AgV} are unique with probability 1.
-\pfcomment{Why is \Second{\AgV} unique with probability 1?  I don't think that is implied.  Can I remove that part of the statement?}
-\dkcomment{It is unique with probablity 1 over the draw of agent types
-  because for z=0, Assumption~\ref{A1} says that there is a measure 0
-  set of agents whose difference between the best and second-best
-  option is z=0. Or am I misunderstanding something?}
-  \pfcomment{That argument says that $\Best{\AgV}$ is unique.
-But the second best, $\Second{\AgV}$, doesn't have to be.
-The measure of the set of agents with 0 gap between the second- and third-best  options might not vanish.}
+\dkedit{\Best{\AgV} is unique with probability 1.}
 

### 2018-06-05 result_discussion.tex
resolving some easy edits

@@
 surpasses the $\Theta(\log(T))$ achievable in the standard multi-armed
-bandit \dkedit{setting}.
+bandit setting.
 This may seem surprising, because the principal in our setting has

### 2018-06-05 Lemmas.tex
checked and edited lemma 7

--- 2018-02-17 Lemmas.tex
@@
 time when arm $i$ is pulled for the \Kth{s} time.
-Under \AccEU{\tau_s}{\frac{p}{4\Diam d \TieDensity}},
+Let $\hat{x} = \frac{1}{2\Diam d}
+  \cdot \min(\TieCutoff, \frac{\MinProb}{2\TieDensity})$.
+Under \AccEU{\tau_s}{\hat{x}},
 this pull of arm $i$ is not incentivized.
@@
 By Lemma~\ref{lem:right-choice},
-under the event \AccEU{\tau_s}{\frac{\MinProb}{4\Diam d \TieDensity}},
+under the event \AccEU{\tau_s}{\hat{x}},
 all agent types \AgV with
 $\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}})
-> \frac{\MinProb}{2\TieDensity}$
+> 2\Diam d \hat{x}$
 will pull their best arm \Best{\AgV}.
+Notice that $2\Diam d \hat{x}
+= \min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})$
 
 By Assmption~\ref{A1},
-%Lemma~\ref{lem:sdelta},
 the measure of agents (across all arms)
 whose best and second-best arm differ in utility by less
-than $\frac{\MinProb}{2\TieDensity}$ is at most $\frac{\MinProb}{2}$.
+than $\min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})$
+is at most
+$\TieDensity \cdot \min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})
+\leq \frac{\MinProb}{2}$.
 In particular, this bound holds for agents whose best arm is $i$.
@@
 will myopically pull arm $i$.
-Because $1/\log(s) < \frac{\MinProb}{2}$ for
+Because $1/\log(s) \pfedit{\le} \frac{\MinProb}{2}$ for
 $s \geq \exp(2/\MinProb)$, arm $i$ is not payment-eligible at time

### 2018-06-05 algorithm_regret.tex
accepted Peter's changes

--- 2018-06-05 algorithm_regret.tex
@@
   formula. Do we need to redefine it here?}
+\pfcomment{Above we define $t_s$ to be the start time of phase $s$.}
+\dkcomment{So the new $t_s$ is the old $t_{s+1}-1$? That's a really
+  confusing subtle notation change. Is there a way we can avoid this
+  and just decide on one or the other, and use it consistently?}
 Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}

### 2018-06-05 algorithm_payment.tex
checked and edited lemma 7

@@
 time when arm $i$ is pulled for the \Kth{s} time.
-\dkedit{Let $\hat{x} = \frac{1}{2\Diam d}
+Let $\hat{x} = \frac{1}{2\Diam d}
   \cdot \min(\TieCutoff, \frac{\MinProb}{2\TieDensity})$.
-Under \AccEU{\tau_s}{\hat{x}},}
+Under \AccEU{\tau_s}{\hat{x}},
 this pull of arm $i$ is not incentivized.
@@
 To make this intuition precise, we set
-\dkedit{$x = x' = \frac{1}{2 \Diam d} \cdot \min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})$}
-(which is independent of the phase number $s$).
-The cutoff point between early and late phases is now set to
+$x = x' = \frac{1}{2 \Diam d} \cdot \min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})$
+(which is independent of the phase number $s$
+\pfedit{and is equal to $\hat{x}$ defined in Lemma~\ref{lem:no-incentives}}).
+\pfedit{We set} the cutoff point between early and late phases to
 $\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3}, \exp(\frac{2}{\MinProb}))$.
-We will verify below that
+We verify below that
 $\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
@@
 
+\pfdelete{
 Fix an arm $i$, and consider the \Kth{s} pull of arm $i$,
@@
 phase $s$.
+}
 
+\pfedit{Fix an arm $i$, let $s \geq \EvenLaterPhase$, and 
+define $\tau_s$ as in Lemma~\ref{lem:no-incentives}.}
 By Lemma~\ref{lem:round-prob} (with our choice of $x = x'$),
@@
 $24 \ARMNUM d \cdot \exp \left(
-\dkedit{  - \frac{1.8 s}{256 \Diam^2 d^2 \sigma^2}
-  \cdot \min(\TieCutoff, \frac{\MinProb}{\TieDensity})^2}
+- \frac{1.8 s}{\pfedit{64} \Diam^2 d^2 \sigma^2}
+  \cdot \min(\TieCutoff, \frac{\MinProb}{\TieDensity})^2
 \right)$.
@@
   + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
-\dkedit{ - \frac{1.8}{256 \Diam^2 d^2 \sigma^2}
-  \cdot \min(\TieCutoff, \frac{\MinProb}{\TieDensity})^2}
+- \frac{1.8}{\pfedit{64} \Diam^2 d^2 \sigma^2}
+  \cdot \min(\TieCutoff, \frac{\MinProb}{\TieDensity})^2
   \right)}}
@@
      \frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3},
-\dkedit{     \frac{\ARMNUM \Diam^3 d^3 \sigma^3}{\TieCutoff^3},}
+\frac{\ARMNUM \Diam^3 d^3 \sigma^3}{\TieCutoff^3},
      \ARMNUM \exp \left(\frac{2}{\MinProb} \right) \right)
@@
      \frac{\ARMNUM^2 d^3 \TieDensity^2 \sigma^2 \Diam^2}{\MinProb^2},
-\dkedit{ \frac{\ARMNUM^2 d^3 \sigma^2 \Diam^2}{\TieCutoff^2}}
+\frac{\ARMNUM^2 d^3 \sigma^2 \Diam^2}{\TieCutoff^2}
 \right) \right)

### 2018-06-05 algorithm_payment.tex
there was not a calculation error after all

@@
 $24 \ARMNUM d \cdot \exp \left(
-- \frac{1.8 s}{\pfedit{64} \Diam^2 d^2 \sigma^2}
+- \frac{1.8 s}{256 \Diam^2 d^2 \sigma^2}
   \cdot \min(\TieCutoff, \frac{\MinProb}{\TieDensity})^2
@@
   + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
-- \frac{1.8}{\pfedit{64} \Diam^2 d^2 \sigma^2}
+- \frac{1.8}{256 \Diam^2 d^2 \sigma^2}
   \cdot \min(\TieCutoff, \frac{\MinProb}{\TieDensity})^2

### 2018-06-05 algorithm_regret.tex
comments

@@
 and consider a regret exceeding $g(s)$ large.
+\pfcomment{We use $g$ in 3 places: here, when talking about adding new linear
+features in section 2, and in Lemma 11.  Maybe it's worth using different notation.}
 
-\dkedit{
 For most of the proof, we will focus on the case $g(s) \leq \TieCutoff$.
 The remaining phases are the ones with
-$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2/\TieCutoff^2$.}
-\dkedit{Each such phase lasts for at most $\ARMNUM \cdot \log(s)$ steps
+$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2/\TieCutoff^2$.
+Each such phase lasts for at most $\ARMNUM \cdot \log(s)$ steps
 in expectation by Lemma~\ref{lem:phase-length},
@@
 The total expected regret incurred in these phases is at most
-$100 \ARMNUM \MAXR \log^2(T) \cdot \Diam^3 d^3 \sigma^3/\TieCutoff^3$.}
+$100 \ARMNUM \MAXR \log^2(T) \cdot \Diam^3 d^3 \sigma^3/\TieCutoff^3$.
+\pfcomment{I get the $NR$, but where does $100 \log^2(T)  D^3 d^3 \sigma^3/\hat{z}^3$ come from?
+I assume this an identity for $\sum_{s=1}^m \log(s)$ I don't know --- could we add the identity we are using?}
 
-\dkedit{For the remainder of the proof, we consider phases $s$
-with $g(s) \leq \TieCutoff$.}
+For the remainder of the proof, we consider phases $s$
+with $g(s) \leq \TieCutoff$.
 We first consider agents \AgV incurring positive regret less than $g(s)$.
@@
 $\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(s)$.
-By Assumption~\ref{A1}, \dkedit{and because $g(s) \leq \TieCutoff$,}
+By Assumption~\ref{A1}, and because $g(s) \leq \TieCutoff$,
 %Lemma~\ref{lem:sdelta},
@@
 steps in phase $s$, 
+\pfcomment{We'll have to fix a probability bug here.}
 the expected total regret from such agents is at most

### 2018-06-05 algorithm_regret.tex
fixed upper bound

@@
 cutoff
-$g(s) = \sqrt{\frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}}$,
-and consider a regret exceeding $g(s)$ large.
-\pfcomment{We use $g$ in 3 places: here, when talking about adding new linear
-features in section 2, and in Lemma 11.  Maybe it's worth using different notation.}
+$\EarlyCut{s} = \sqrt{\frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}}$,
+and consider a regret exceeding \EarlyCut{s} large.
 
-For most of the proof, we will focus on the case $g(s) \leq \TieCutoff$.
+For most of the proof, we will focus on the case $\EarlyCut{s} \leq \TieCutoff$.
 The remaining phases are the ones with
@@
 and each step incurs regret at most \MAXR.
-The total expected regret incurred in these phases is at most
-$100 \ARMNUM \MAXR \log^2(T) \cdot \Diam^3 d^3 \sigma^3/\TieCutoff^3$.
-\pfcomment{I get the $NR$, but where does $100 \log^2(T)  D^3 d^3 \sigma^3/\hat{z}^3$ come from?
-I assume this an identity for $\sum_{s=1}^m \log(s)$ I don't know --- could we add the identity we are using?}
+\dkedit{The total expected regret incurred in these phases is at most
+$O(\ARMNUM \MAXR \cdot \log(T) \Diam^2 d^2 \sigma^2/\TieCutoff^2
+\cdot \log (\log(T) \cdot \Diam^2 d^2 \sigma^2/\TieCutoff^2)
+\leq O(\ARMNUM \MAXR \log^2(T) \cdot \Diam^3 d^3 \sigma^3/\TieCutoff^3)$,
+by crudely bounding $\log y \leq O(\sqrt{y})$.}
 
 For the remainder of the proof, we consider phases $s$
-with $g(s) \leq \TieCutoff$.
-We first consider agents \AgV incurring positive regret less than $g(s)$.
+with $\EarlyCut{s} \leq \TieCutoff$.
+We first consider agents \AgV incurring positive regret less than \EarlyCut{s}.
 The second-best arm \Second{\AgV} of such an agent \AgV must satisfy
-$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(s)$.
-By Assumption~\ref{A1}, and because $g(s) \leq \TieCutoff$,
+$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \EarlyCut{s}$.
+By Assumption~\ref{A1}, and because $\EarlyCut{s} \leq \TieCutoff$,
 %Lemma~\ref{lem:sdelta},
 the total measure of such agents
-is $\AlmostTied{g(s)} \leq \TieDensity \cdot g(s)$,
-and each such agent incurs regret at most $g(s)$.
+is $\AlmostTied{\EarlyCut{s}} \leq \TieDensity \cdot \EarlyCut{s}$,
+and each such agent incurs regret at most \EarlyCut{s}.
 Summing over all time steps,
@@
 \begin{align}
-\Expect{\sum_{s=1}^{T} \sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot g^2(s)}
+\Expect{\sum_{s=1}^{T} \sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot \EarlyCut[2]{s}}
 & \leq \sum_{s=1}^{T} \TieDensity \cdot g^2(s) \ARMNUM \log(s).
@@
 By Lemma~\ref{lem:right-choice},
-under \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}}, no agent at time $t$ will incur
-regret more than $g(s)$.
+under \AccEU{\tau_s^k}{\frac{\dkedit{\EarlyCut{s}}}{2\Diam d}}, no agent at time $t$ will incur
+regret more than \EarlyCut{s}.
 \dkcomment{Instead of the extra case distinction, I had thought of
-  defining $g(s)$ to be the minimum of the current definition and
+  defining \EarlyCut{s} to be the minimum of the current definition and
   \TieCutoff. Unfortunately, I think that we cannot necessarily apply
@@
 
-To bound the probability of \AccEU{\tau_s^k}{\frac{g(s)}{2\Diam d}},
+To bound the probability of \AccEU{\tau_s^k}{\frac{\EarlyCut{s}}{2\Diam d}},
 we use Lemma~\ref{lem:round-prob}
-(with $x_s = x'_s = \frac{g(s)}{2 \Diam d}$
+(with $x_s = x'_s = \frac{\EarlyCut{s}}{2 \Diam d}$
 and a stopping time of $\tau_s^k$).
@@
 Substituting that
-$x_n = \frac{g(n)}{2 \Diam d} = \sqrt{\frac{32\log(T) \cdot \sigma^2}{1.8 n}}$,
+$x_n = \frac{\EarlyCut{n}}{2 \Diam d} = \sqrt{\frac{32\log(T) \cdot \sigma^2}{1.8 n}}$,
 the left-hand side is
@@
 \sum_{s = 1}^T \sum_{t=t_s}^{t_{s+1}-1}
-  \Prob{\mbox{incur regret exceeding } g(s) \mbox{ at step } t} \cdot \MAXR
+  \Prob{\mbox{incur regret exceeding } \EarlyCut{s} \mbox{ at step } t} \cdot \MAXR
 & \leq
@@
 and substituting that 
-$g^2(s) = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
+$\EarlyCut[2]{s} = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
 the cumulative regret up to time $T$ is at most
@@
 + \ARMNUM^2 \MAXR d
-+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} g^2(s) \log(s) \right)}
++ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} \EarlyCut[2]{s} \log(s) \right)}
 \\ & = 

### 2018-06-05 problem_setting.tex
resolving some easy edits
fixed upper bound

@@
 transformation of some original attribute vector.
-One can simply define $\Ag{j} = g_j(\AgV)$ for some known
-nonlinear functions $g_j$ and $j=d+1,\ldots,d'$, and then increase the
+One can simply define \dkedit{$\Ag{j} = h_j(\AgV)$ for some known
+nonlinear functions $h_j$} and $j=d+1,\ldots,d'$, and then increase the
 number of attributes to $d'$.
@@
 Notice that based on Assumption~\ref{A1} below,
-\dkedit{\Best{\AgV} is unique with probability 1.}
+\Best{\AgV} is unique with probability 1.
 

### 2018-06-06 Lemmas.tex
accepted Peter's changes
changed gaussian noise to more general sub-gaussian noise

@@
 \begin{rlemma}{Lemma}{\ref{lem:round-prob}}
-Recall that $\sigma$ is the standard deviation of the Gaussian noise.
+Recall the noise is a mean-zero sub-Gaussian($\sigma^2$) random variable.
 Let \LatePhase be a phase cutoff, 
@@
 including the \Kth{n} pull of arm $i$,
-renormalized to have standard deviation $1/2$.
+renormalized to be a mean-zero sub-Gaussian($1/2$) random variable.
 The $S_n$ define an unbiased half-subgaussian random walk,
@@
 will myopically pull arm $i$.
-Because $1/\log(s) \pfedit{\le} \frac{\MinProb}{2}$ for
+Because $1/\log(s) \leq \frac{\MinProb}{2}$ for
 $s \geq \exp(2/\MinProb)$, arm $i$ is not payment-eligible at time

### 2018-06-06 problem_setting.tex
changed gaussian noise to more general sub-gaussian noise

@@
 When arm $i$ is pulled, its current utility-relevant features are
-determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero independent Gaussian%
+determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero independent sub-Gaussian%
 \footnote{For simplicity of notation, we assume that the variance
@@
 continuous mean-zero sub-Gaussian($\sigma^2$) noise that is
-independent but not necessarily identically distributed across time.
-\dkcomment{Are we actually stating the result in this generality now?
-  If not, then why make the algorithm use continuity, as opposed to
-  that we have Gaussians? If we do make the algorithm that general,
-  then we should just define everything generally here.}}
+independent but not necessarily identically distributed across time.}
 noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.

### 2018-06-06 algorithm_general.tex
changed gaussian noise to more general sub-gaussian noise
addressed some comments in the main paper

@@
 (before tail bounds have kicked in). The proof of Lemma~\ref{lem:phase-length} and all other proofs missing in the main paper may be found in the appendix.
-\dkcomment{If we only get 12 pages in the proceedings, make sure to
-  replace ``appendix'' by ``online appendix'' or ``supplemental
-  material'' or whatever we call it, here and everywhere else.}
 
@@
 \begin{lemma} \label{lem:round-prob}
-Recall that $\sigma$ is the standard deviation of the Gaussian noise.
+Recall the noise is a mean-zero sub-Gaussian($\sigma^2$) random variable.
 Let \LatePhase be fixed, 

### 2018-06-06 Lemmas.tex
fix to lemma 4, edits to thm 3

--- 2018-06-05 Lemmas.tex
@@
 $\ARMNUM \cdot \log(s)$ time steps.
+\pfedit{
+Moreover, for any set of types $A$, the expected number of times that 
+an agent with a type in $A$ appears in a phase $s$ is at most 
+$f(A) \cdot \ARMNUM \cdot \log(s)$,
+where $f(A) := \Prob[\AgV \sim \AgentDist]{\ArmV \in A}$.
+}
 \end{rlemma}
@@
 \begin{proof}
-Let $S$ be the set of arms that have been pulled at most
-$s$ times at the start of phase $s$.
-Thus, phase $s$ has ended when each $i \in S$ has been pulled at least once.
-Consider any time step $t$.
-If $S$ contains at least one payment-eligible arm $i$,
-then some payment-eligible arm will be pulled with probability 1,
-and every payment-eligible arm is in $S$.
-In particular, the size of $S$ decreases with probability 1.
-If $S$ contains no payment-eligible arm,
-then by definition of payment-eligibility,
-each arm $i \in S$ has probability at least $1/\log(s)$ of being pulled.
-In particular, the size of $S$ decreases with probability at least $1/\log(s)$.
+\pfedit{
+We show the second claim for general $A$, which implies the first claim by taking $A$ to be the support of $\AgentDist$.
 
-In either case, the expected number of time steps until
-$|S|$ decreases is at most $\log s$,
-so the expected number of steps until $S$ is empty is at most
-$\ARMNUM \cdot \log(s)$.
+Fix a phase $s$ and let $S_t$ be the set of arms that have been pulled at most $s$ times by time $t$.
+Let $\tau_m$ be the maximum of $t_s$ (the start of phase $s$) and the time $t$ when $S_t$ first contains $m$ elements.
+The phase ends when $S_t$ contains no elements, i.e., $\tau_0 = t_{s+1}$.
+We consider the expected number of pulls during times $[\tau_m, \tau_{m-1})$ made by agents whose types are in $A$.
+
+Consider a counter starting from $0$ at time $\tau_m$ that increments each time an agent arrives with a type in $A$, and that is stopped the first time an arm in $S_t$ is pulled.
+For any stopping time $t \in [\tau_m, \tau_{m-1})$, 
+the conditional probability that the counter increments
+given the history of pulls, payments, and observations at time $t$ 
+is $f(A)$.
+The conditional probability that the counter is stopped by that agent's pull is at least $1/\log(s)$.
+To see this, consider two cases.
+In the first case, there is at least one payment eligible arm, in which case the principal incentives an arm in $S_t$.
+In the second case, there are no payment eligible arms.
+Then, by definition of payment-eligibility,
+each arm $i \in S_t$ has conditional probability at least $1/\log(s)$ of being pulled.
+
+The expected value of this counter when it is stopped is bounded above by the expected stopped value of another counter whose conditional probability of being stopped is exactly $1/\log(s)$, and is otherwise identical.
+(This can be shown more formally via a coupling argument.)
+Let $V_\ell$ be the conditional expectation of this second counter's value when it is stopped,
+given that its current value is $\ell$ and it has not been stopped.  Observe that $V_\ell = \ell + V_0$.
+Enumerating outcomes (either the counter increments or not; either it stops or it continues) provides $V_0 = f(A)\frac1{\log(s)} + f(A) (1-\frac1{\log(s)}) V_1 + (1-f(A))(1-\frac1{\log(s)}) V_0$.
+Using $V_1 = 1 + V_0$ simplifies this to 
+$V_0 = f(A) + (1-\frac1{\log(s)}) V_0$.
+Noting $V_0$ is finite and solving for $V_0$ provides
+$V_0 = f(A) \log(s)$.
+Thus, the conditional expected number of pulls (given the history at time $\tau_m$) by an agent with a type in $A$ during times in $[\tau_m, \tau_{m-1})$ is no more than $f(A) \log(s)$.
+
+We may write the total number of pulls by agents with types in $A$ during phase $s$ as a sum of this quantity over $m$ ranging from $|S_{t_s}|$ down to 1.
+Noting that $|S_{t_s}| \le N$ and taking the expectation of this sum shows the claim.
+}
 \end{proof}

### 2018-06-06 problem_setting.tex

@@
 transformation of some original attribute vector.
-One can simply define \dkedit{$\Ag{j} = h_j(\AgV)$ for some known
-nonlinear functions $h_j$} and $j=d+1,\ldots,d'$, and then increase the
+One can simply define $\Ag{j} = h_j(\AgV)$ for some known
+nonlinear functions $h_j$ and $j=d+1,\ldots,d'$, and then increase the
 number of attributes to $d'$.

### 2018-06-06 algorithm_regret.tex
fixed upper bound

@@
 with $\EarlyCut{s} \leq \TieCutoff$.
+\pfedit{
 We first consider agents \AgV incurring positive regret less than \EarlyCut{s}.
-The second-best arm \Second{\AgV} of such an agent \AgV must satisfy
+Let $A$ be the set of types satisfying 
 $\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \EarlyCut{s}$.
 By Assumption~\ref{A1}, and because $\EarlyCut{s} \leq \TieCutoff$,
-%Lemma~\ref{lem:sdelta},
-the total measure of such agents
+the total measure of $A$
 is $\AlmostTied{\EarlyCut{s}} \leq \TieDensity \cdot \EarlyCut{s}$,
-and each such agent incurs regret at most \EarlyCut{s}.
-Summing over all time steps,
-and using Lemma~\ref{lem:phase-length} to bound the number of time
-steps in phase $s$, 
-\pfcomment{We'll have to fix a probability bug here.}
-the expected total regret from such agents is at most
-\begin{align}
-\Expect{\sum_{s=1}^{T} \sum_{t=t_{s-1}+1}^{t_{s}} \TieDensity \cdot \EarlyCut[2]{s}}
-& \leq \sum_{s=1}^{T} \TieDensity \cdot g^2(s) \ARMNUM \log(s).
+Then, by Lemma~\ref{lem:phase-length},
+the expected number of pulls in phase $s$ by agents in $A$  
+bounded above by $\TieDensity\ \EarlyCut{s} \ARMNUM \log(s)$, and the total expected number of pulls by these agents by $\sum_{s=1}^T \TieDensity \ \EarlyCut[2]{s} \ARMNUM \log(s)$.
+Consider any agent $\AgV$ incurring positive regret less than $\EarlyCut{s}$.
+This agent's type must be in $A$.
+Moreover, this agent's regret is bounded above by $\EarlyCut{s}$.
+Thus, the expected total regret from such agents is at most
+\begin{equation}
+\sum_{s=1}^{T} \TieDensity \cdot \EarlyCut[2]{s} \ARMNUM \log(s).
 \label{equ:small_regret_bound}
-\end{align}
+\end{equation}
+}
 
 We next bound the regret incurred in time steps with large regret.
-Let the random variable $t_s$ be the final time step in phase $s$,
-for each $s$.
-\dkcomment{We have already used $t_s$ before, e.g., in the preceding
-  formula. Do we need to redefine it here?}
-\pfcomment{Above we define $t_s$ to be the start time of phase $s$.}
-\dkcomment{So the new $t_s$ is the old $t_{s+1}-1$? That's a really
-  confusing subtle notation change. Is there a way we can avoid this
-  and just decide on one or the other, and use it consistently?}
 Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
@@
 with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
-i.e., $k > t_{s}-t_{s-1}$.
+i.e., $k > \pfedit{t_{s+1}-t_{s}}$.
 By Lemma~\ref{lem:right-choice},

### 2018-06-06 Lemmas.tex
getting closer

@@
 
-The expected value of this counter when it is stopped is bounded above by the expected stopped value of another counter whose conditional probability of being stopped is exactly $1/\log(s)$, and is otherwise identical.
+The expected value of this counter when it is stopped is bounded above by the expected stopped value of another counter whose conditional probability of being stopped is exactly $1/\log(s)$.
 (This can be shown more formally via a coupling argument.)

### 2018-06-06 algorithm_regret.tex
checking over changes from david
getting closer

@@
 and each step incurs regret at most \MAXR.
-\dkedit{The total expected regret incurred in these phases is at most
+The total expected regret incurred in these phases is at most
 $O(\ARMNUM \MAXR \cdot \log(T) \Diam^2 d^2 \sigma^2/\TieCutoff^2
@@
 \leq O(\ARMNUM \MAXR \log^2(T) \cdot \Diam^3 d^3 \sigma^3/\TieCutoff^3)$,
-by crudely bounding $\log y \leq O(\sqrt{y})$.}
+by crudely bounding $\log y \leq O(\sqrt{y})$.
 
@@
 By Lemma~\ref{lem:right-choice},
-under \AccEU{\tau_s^k}{\frac{\dkedit{\EarlyCut{s}}}{2\Diam d}}, no agent at time $t$ will incur
+under \AccEU{\tau_s^k}{\frac{\EarlyCut{s}}{2\Diam d}}, no agent at time $t$ will incur
 regret more than \EarlyCut{s}.
-\dkcomment{Instead of the extra case distinction, I had thought of
-  defining \EarlyCut{s} to be the minimum of the current definition and
-  \TieCutoff. Unfortunately, I think that we cannot necessarily apply
-  Lemma~\ref{lem:right-choice} with that definition. Just putting that
-  here in case you are thinking of simplifying the proof this way.}
 
@@
 
-\begin{align*}
-\sum_{s = 1}^T \sum_{t=t_s}^{t_{s+1}-1}
-  \Prob{\mbox{incur regret exceeding } \EarlyCut{s} \mbox{ at step } t} \cdot \MAXR
-& \leq
+\begin{equation*}
 \sum_{s = 1}^T \frac{24 \ARMNUM d}{T^2} \cdot \MAXR \cdot \ARMNUM \log(s)
-\\ & \leq 12 \ARMNUM^2 d \MAXR.
-\end{align*}
+\leq 12 \ARMNUM^2 d \MAXR.
+\end{equation*}
+%\pfcomment{I deleted the left-hand side of the above equation because it was using random terms in the summand, and actually wasn't true.
+What was intended was an expectation outside of the sum, but I thought it simpler just to delete that term.}
 
-Adding all \dkedit{four} types of regret terms,
+Adding all four types of regret terms,
 and substituting that 
@@
 \lefteqn{O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
-\dkedit{+ \ARMNUM \MAXR \log^2(T)}
++ \ARMNUM \MAXR \log^2(T)
 + \ARMNUM^2 \MAXR d

### 2018-06-06 problem_setting.tex
sub gaussian stuff

@@
 When arm $i$ is pulled, its current utility-relevant features are
-determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero independent sub-Gaussian%
-\footnote{For simplicity of notation, we assume that the variance
+determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero independent \pfedit{continuous} sub-Gaussian%
+\footnote{For simplicity of notation, we assume that the variance \pfedit{proxy}
   $\sigma^2$ is uniform across time steps.
-In fact, the analysis extends straightforwardly to any
-continuous mean-zero sub-Gaussian($\sigma^2$) noise that is
-independent but not necessarily identically distributed across time.}
+  \pfedit{The} analysis extends \pfedit{easily when the variance proxy changes over time}.}
 noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.

### 2018-06-06 Discussion.tex
onto 12 pages

@@
 This slow decrease is needed to bound the regret in the later phases when the concentration inequality kicks in as in Equation~(\ref{equ:small_regret_bound}).
-In this section, we discuss two restrictions on the problem setting under which  we can modify the algorithm slightly and provide stronger bounds, avoiding this exponential dependence.
-Both problem settings are special cases of the more general problem setting previously considered.
+In this section, we discuss two restrictions \pfdelete{on the problem setting} under which  we can modify the algorithm slightly and provide stronger bounds, avoiding this exponential dependence.
+Both problem settings are special cases of the more general \pfdelete{problem} setting previously considered.
 
@@
 \label{rst:discrete}
-Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment budget bounded above by 
+Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment \pfdelete{budget} bounded above by 
 \begin{align*}
@@
 An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
-if both of the following hold:
+if both: \pfdelete{of the following hold:}
 \begin{itemize}
@@
 \label{rst:known-p}
-Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has expected payment budget bounded above by 
+Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has expected payment \pfdelete{budget} bounded above by 
 \begin{align*}

### 2018-06-06 algorithm_regret.tex
onto 12 pages

@@
 the total expected regret from large-regret steps is at most
-
-\begin{equation*}
-\sum_{s = 1}^T \frac{24 \ARMNUM d}{T^2} \cdot \MAXR \cdot \ARMNUM \log(s)
-\leq 12 \ARMNUM^2 d \MAXR.
-\end{equation*}
+$\sum_{s = 1}^T \frac{24 \ARMNUM d}{T^2} \cdot \MAXR \cdot \ARMNUM \log(s)
+\leq 12 \ARMNUM^2 d \MAXR.$
 %\pfcomment{I deleted the left-hand side of the above equation because it was using random terms in the summand, and actually wasn't true.
@@
 Adding all four types of regret terms,
-and substituting that 
+and substituting 
 $\EarlyCut[2]{s} = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
 the cumulative regret up to time $T$ is at most
-
-\begin{align*}
-\lefteqn{O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+$
+O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
 + \ARMNUM \MAXR \log^2(T)
 + \ARMNUM^2 \MAXR d
-+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} \EarlyCut[2]{s} \log(s) \right)}
-\\ & = 
++ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} \EarlyCut[2]{s} \log(s) \right)\\
+= 
 O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
-+ \ARMNUM \TieDensity \cdot \log^3(T) \right).\QED
-\end{align*}
++ \ARMNUM \TieDensity \cdot \log^3(T) \right)$.\QED
 \end{emptyextraproof}

### 2018-06-06 algorithm_regret.tex
fixing issue in thm 3

@@
 bound the maximum regret by \MAXR.
-Now, applying Lemma~\ref{lem:phase-length},
+\pfedit{Summing over the $T$ time periods,}
+\pfdelete{Now, applying Lemma~\ref{lem:phase-length},}
 the total expected regret from large-regret steps is at most
-$\sum_{s = 1}^T \frac{24 \ARMNUM d}{T^2} \cdot \MAXR \cdot \ARMNUM \log(s)
-\leq 12 \ARMNUM^2 d \MAXR.$
+$\pfedit{24 \ARMNUM d \MAXR / T.}$
 %\pfcomment{I deleted the left-hand side of the above equation because it was using random terms in the summand, and actually wasn't true.
@@
 + \ARMNUM \MAXR \log^2(T)
-+ \ARMNUM^2 \MAXR d
++ \pfedit{\frac{\ARMNUM \MAXR d}{T}}
 + \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} \EarlyCut[2]{s} \log(s) \right)\\

### 2018-06-06 payment-proof.tex
find an error, but not sure how to fix it
proposed change to lemma 14

@@
 \begin{align}
-O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right).  \nonumber 
+O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp\left(\frac{2}{\MinProb}\right) \right).  \nonumber 
 \end{align}
@@
 Define $h(\ell) := \max \left( \exp(\frac{2}{\MinProb}),
+\pfedit{
+\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2},
+}
 \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
@@
 Because $s \geq h(\ell)$, we get that
-$g(s,\ell) \leq \frac{\MinProb}{4 \Diam d \TieDensity}$
+$g(s,\ell) \leq \pfedit{\min(\frac{\TieCutoff}{2\Diam d},} \frac{\MinProb}{4 \Diam d \TieDensity}\pfedit{)}$
 as well as $s \geq \exp(2/\MinProb)$.
@@
 
-\dkcomment{Did we forget a sum over \SP here?}
-
 We now lower-bound $s^{2/5} \geq 1$, split off the term for $\ell=1$

### 2018-06-06 Discussion-Proof.tex
copied changes from 4.4 to appendix, rearranged appendix order
changed the regret for Theorem 10
fix to thm 9

@@
-\section{Proof of Theorem~\ref{rst:discrete}}
+\section{Proof Sketch of Theorem~\ref{rst:discrete}}
 \label{sec:discussion-proof1}
@@
 \begin{align*}
-O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
+\pfedit{
+O \left(\ARMNUM^2  d^{7/2} D^{5/2} \sigma^{5/2} \cdot (\MAXR + \Diam d \sigma)\cdot
+    \max\bigg\{
+    \frac{1}{\TieCutoff},
+    \frac{\TieDensity}{\MinProb} \bigg\}^{5/2}
+\right)
+}
 \end{align*}
@@
 The proof of the expected payment bound is the same as the proof of Theorem~\ref{rst:budget}, except that we now define $h(\ell) := \max \left( \frac{2}{\MinProb},
+\pfedit{
+\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2},
+}
 \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
@@
 In return, the length of phase $s$ is now bounded only be $\ARMNUM s$ instead of $\ARMNUM \log(s)$.
-Substituting these changes into the proof of Theorem~\ref{rst:regret}, we obtain the claimed bounds.
+Substituting these changes into the proof\pfedit{s} of Theorem\pfedit{s}~\ref{rst:regret} \pfedit{and \ref{rst:budget}}, we obtain the claimed bounds.
+
+\pfcomment{
+The calculation I did for the bound on the expected payment is,
+\begin{align*}
+&O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot h(1) \right) \\ 
+&=O \left(\ARMNUM^2  d \cdot (\MAXR + \Diam d \sigma)\cdot
+    \max\bigg\{\frac{2}{p},
+    \left( \frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2},
+    \left( \frac{\sigma \TieDensity \Diam d}{\MinProb} \right)^{5/2}\bigg\}
+\right)\\
+&=O \left(\ARMNUM^2  d^{7/2} D^{5/2} \sigma^{5/2} \cdot (\MAXR + \Diam d \sigma)\cdot
+    \max\bigg\{
+    \frac{1}{\TieCutoff},
+    \frac{\TieDensity}{\MinProb} \bigg\}^{5/2}
+\right).
+\end{align*}
+}
+
 \end{proof}
 
-\section{Proof of Theorem~\ref{rst:known-p}}
+\section{Proof Sketch of Theorem~\ref{rst:known-p}}
 \label{sec:discussion-proof2}
@@
 and an expected regret bounded above by
+\bcedit{
 \begin{align*}
 O \left(\frac{\MAXR \ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
-  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} +\frac{\ARMNUM^2 d\MAXR}{\MinProb}+\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
+  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
+  + \frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
 \end{align*}
+}
 \end{rtheorem}
@@
   + \frac{\ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
+    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
   \right)} \right). \nonumber 
 \end{align}
-The proof of this result follows that of Lemma~\ref{lem:numP}, but the less aggressive incentivization allows us to define $\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3})$ since $\frac{1}{\log(s+s_0)} \leq \frac{\MinProb}{2}$ is true for all $s$.
+The proof of this result follows that of Lemma~\ref{lem:numP},
+but the less aggressive incentivization allows us to define $\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3})$ since $\frac{1}{\log(s+s_0)} \leq \frac{\MinProb}{2}$ is true for all $s$.
 

### 2018-06-06 Discussion-Proof.tex
fix to thm 9
addressed Theorem 10 when L=0

@@
 \begin{align*}
-\pfedit{
-O \left(\ARMNUM^2  d^{7/2} D^{5/2} \sigma^{5/2} \cdot (\MAXR + \Diam d \sigma)\cdot
-    \max\bigg\{
-    \frac{1}{\TieCutoff},
-    \frac{\TieDensity}{\MinProb} \bigg\}^{5/2}
-\right)
-}
+O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
 \end{align*}
@@
 The proof of the expected payment bound is the same as the proof of Theorem~\ref{rst:budget}, except that we now define $h(\ell) := \max \left( \frac{2}{\MinProb},
-\pfedit{
-\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2},
-}
 \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
@@
 In return, the length of phase $s$ is now bounded only be $\ARMNUM s$ instead of $\ARMNUM \log(s)$.
-Substituting these changes into the proof\pfedit{s} of Theorem\pfedit{s}~\ref{rst:regret} \pfedit{and \ref{rst:budget}}, we obtain the claimed bounds.
-
-\pfcomment{
-The calculation I did for the bound on the expected payment is,
-\begin{align*}
-&O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot h(1) \right) \\ 
-&=O \left(\ARMNUM^2  d \cdot (\MAXR + \Diam d \sigma)\cdot
-    \max\bigg\{\frac{2}{p},
-    \left( \frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2},
-    \left( \frac{\sigma \TieDensity \Diam d}{\MinProb} \right)^{5/2}\bigg\}
-\right)\\
-&=O \left(\ARMNUM^2  d^{7/2} D^{5/2} \sigma^{5/2} \cdot (\MAXR + \Diam d \sigma)\cdot
-    \max\bigg\{
-    \frac{1}{\TieCutoff},
-    \frac{\TieDensity}{\MinProb} \bigg\}^{5/2}
-\right).
-\end{align*}
-}
-
+Substituting these changes into the proof of Theorem~\ref{rst:regret}, we obtain the claimed bounds.
 \end{proof}
@@
 Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has an expected payment budget bounded above by 
+    \bcedit{
 \begin{align*}
-O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
+    O\left(\ARMNUM^2 d\cdot(R+Dd\sigma)\cdot \max\bigg\{ \left(\frac{24\sigma \ell \Diam d}{\TieCutoff} \right)^{5/2},
+        \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}\bigg\}\right)
 \end{align*}
+}
 and an expected regret bounded above by
@@
   The proof of the expected payment bound follows Lemma~\ref{rst:budget} except for defining
-  $h(\ell) := \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}$
+    \bcedit{
+    $h(\ell) := \max\big\{ \left(\frac{24\sigma \ell \Diam d}{\TieCutoff} \right)^{5/2},
+        \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}\big\}$
+    }
 (without including the $\exp(2/\MinProb)$ term).

### 2018-06-06 Discussion-Proof.tex
fixing theorem 9

@@
 \begin{align*}
-O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
+\pfedit{
+O \left(\ARMNUM^2  d \cdot (\MAXR + \Diam d \sigma)\cdot
+    \max\bigg\{\frac{2}{p},
+    \left( \frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2}
+    \bigg\}
+\right)
+}
 \end{align*}
@@
 The proof of the expected payment bound is the same as the proof of Theorem~\ref{rst:budget}, except that we now define $h(\ell) := \max \left( \frac{2}{\MinProb},
+\pfedit{
+\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2},
+}
 \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
-\right)$.
+\right)
+\pfedit{
+= 
+\max \left( \frac{2}{\MinProb},
+\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2}
+\right)
+}
+$.
 
@@
 In return, the length of phase $s$ is now bounded only be $\ARMNUM s$ instead of $\ARMNUM \log(s)$.
-Substituting these changes into the proof of Theorem~\ref{rst:regret}, we obtain the claimed bounds.
+Substituting these changes into the proof\pfedit{s} of Theorem\pfedit{s}~\ref{rst:regret} \pfedit{and \ref{rst:budget}}, we obtain the claimed bounds.
+
+\pfcomment{
+The calculation I did for the bound on the expected payment is,
+\begin{align*}
+&O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot h(1) \right) \\ 
+&=O \left(\ARMNUM^2  d \cdot (\MAXR + \Diam d \sigma)\cdot
+    \max\bigg\{\frac{2}{p},
+    \left( \frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2}
+    \bigg\}
+\right)
+\end{align*}
+}
+
 \end{proof}

### 2018-06-06 Discussion-Proof.tex
addressed the issue in Theorem 10
my late nite attempt to fix thm 9

@@
 and expected regret bounded above by 
-\begin{align}
-O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
-  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
-  \right).  \nonumber
-\end{align}
+\pfedit{
+\begin{align*}
+O \left(
+\ARMNUM \MAXR \left(
+	\frac2{\MinProb}
+       + \frac{\log^2(T) \Diam^4 d^4 \sigma^4}{\hat{z}^4}\right) \right)
+\end{align*}
+}
 \end{rtheorem}
@@
 \left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2}
-\right)
+\right).
 }
-$.
+$
+%\pfedit{and $s_1 = \max(2,\frac{30\sigma^3}{x^3}, \frac2{\MinProb})$}.
 
@@
 which replace the $\exp(2/\MinProb)$ term with simply $2/\MinProb$.
-In return, the length of phase $s$ is now bounded only be $\ARMNUM s$ instead of $\ARMNUM \log(s)$.
-Substituting these changes into the proof\pfedit{s} of Theorem\pfedit{s}~\ref{rst:regret} \pfedit{and \ref{rst:budget}}, we obtain the claimed bounds.
+In return, the length of phase $s$ is now bounded only by $\ARMNUM s$ instead of $\ARMNUM \log(s)$.
+Substituting these changes into the proof of Theorem~\ref{rst:regret}, we obtain the claimed bounds.
 
@@
 \end{align*}
+}
+
+\pfcomment{
+The calculation I did for the bound on the regret is:
+
+\begin{itemize}
+\item regret from times when we pay is $RN\frac2p$
+\item regret from times with $\gamma(s) >= \hat{z}$ is $NR \log^2(T) D^4 d^4 sigma^4 / \hat{z}^4$
+\item regret from small regret is 0
+\item regret from big regret is $NRd/T$
+\end{itemize}
+
+Total is NR ($\frac2p + \frac{d}{T} + \frac{\log^2(T) D^4 d^4 sigma^4}{zhat^4}$)
 }

### 2018-06-06 Lemmas.tex

@@
 $\ARMNUM \cdot \log(s)$ time steps.
-\pfedit{
-Moreover, for any set of types $A$, the expected number of times that 
+
+More generally, for any set of types $A$, the expected number of times that 
 an agent with a type in $A$ appears in a phase $s$ is at most 
 $f(A) \cdot \ARMNUM \cdot \log(s)$,
-where $f(A) := \Prob[\AgV \sim \AgentDist]{\ArmV \in A}$.
-}
+where $f(A) := \Prob[\AgV \sim \AgentDist]{\dkedit{\AgV} \in A}$.
 \end{rlemma}
@@
 \begin{proof}
-\pfedit{
-We show the second claim for general $A$, which implies the first claim by taking $A$ to be the support of $\AgentDist$.
+We show the second claim for general $A$,
+which implies the first claim by taking $A$ to be the support of $\AgentDist$.
 
-Fix a phase $s$ and let $S_t$ be the set of arms that have been pulled at most $s$ times by time $t$.
-Let $\tau_m$ be the maximum of $t_s$ (the start of phase $s$) and the time $t$ when $S_t$ first contains $m$ elements.
+Fix a phase $s$, and let $S_t$ be the set of arms that have been
+pulled at most $s$ times by time $t$.
+Let $\tau_m$ be the maximum of $t_s$ (the start of phase $s$)
+and the time $t$ when $S_t$ first contains \dkedit{(at most)} $m$ elements.
 The phase ends when $S_t$ contains no elements, i.e., $\tau_0 = t_{s+1}$.
-We consider the expected number of pulls during times $[\tau_m, \tau_{m-1})$ made by agents whose types are in $A$.
+We consider the expected number of pulls during times
+$\dkedit{t \in} [\tau_m, \tau_{m-1})$ made by agents whose types are in $A$.
 
-Consider a counter starting from $0$ at time $\tau_m$ that increments each time an agent arrives with a type in $A$, and that is stopped the first time an arm in $S_t$ is pulled.
+Consider a counter starting from $0$ at time $\tau_m$ that increments
+each time an agent arrives with a type in $A$,
+and that is stopped the first time an arm in $S_t$ is pulled.
 For any stopping time $t \in [\tau_m, \tau_{m-1})$, 
-the conditional probability that the counter increments
-given the history of pulls, payments, and observations at time $t$ 
+the conditional probability that the counter increments,
+given the history of pulls, payments, and observations at time $t$,
 is $f(A)$.
-The conditional probability that the counter is stopped by that agent's pull is at least $1/\log(s)$.
+The conditional probability that the counter is stopped by that
+agent's pull is at least $1/\log(s)$.
 To see this, consider two cases.
-In the first case, there is at least one payment eligible arm, in which case the principal incentives an arm in $S_t$.
-In the second case, there are no payment eligible arms.
+In the first case, there is at least one payment-eligible arm,
+in which case the principal incentivizes an arm in $S_t$.
+In the second case, there are no payment-eligible arms.
 Then, by definition of payment-eligibility,
@@
 
-The expected value of this counter when it is stopped is bounded above by the expected stopped value of another counter whose conditional probability of being stopped is exactly $1/\log(s)$.
+The expected value of this counter when it is stopped is bounded above
+by the expected stopped value of another counter whose conditional
+probability of being stopped is exactly $1/\log(s)$.
 (This can be shown more formally via a coupling argument.) 
 Let $V_\ell$ be the conditional expectation of this second counter's value when it is stopped,
-given that its current value is $\ell$ and it has not been stopped.  Observe that $V_\ell = \ell + V_0$.
-Enumerating outcomes (either the counter increments or not; either it stops or it continues) provides $V_0 = f(A)\frac1{\log(s)} + f(A) (1-\frac1{\log(s)}) V_1 + (1-f(A))(1-\frac1{\log(s)}) V_0$.
-Using $V_1 = 1 + V_0$ simplifies this to 
-$V_0 = f(A) + (1-\frac1{\log(s)}) V_0$.
-Noting $V_0$ is finite and solving for $V_0$ provides
+given that its current value is $\ell$ and it has not been stopped.
+Observe that $V_\ell = \ell + V_0$.
+Enumerating outcomes
+(either the counter increments or not; either it stops or it continues)
+gives us the recurrence relation
+$V_0 = f(A) \frac{1}{\log(s)} + f(A) (1-\frac{1}{\log(s)}) V_1
+   + (1-f(A))(1-\frac{1}{\log(s)}) V_0$.
+Using that $V_1 = 1 + V_0$, this equation simplifies to 
+$V_0 = f(A) + (1-\frac{1}{\log(s)}) V_0$.
+Noting that $V_0$ is finite and solving for $V_0$ gives us that
 $V_0 = f(A) \log(s)$.
-Thus, the conditional expected number of pulls (given the history at time $\tau_m$) by an agent with a type in $A$ during times in $[\tau_m, \tau_{m-1})$ is no more than $f(A) \log(s)$.
+Thus, the conditional expected number of pulls (given the history at time $\tau_m$)
+by an agent with a type in $A$ during times in $[\tau_m, \tau_{m-1})$
+is no more than $f(A) \log(s)$.
 
-We may write the total number of pulls by agents with types in $A$ during phase $s$ as a sum of this quantity over $m$ ranging from $|S_{t_s}|$ down to 1.
-Noting that $|S_{t_s}| \le N$ and taking the expectation of this sum shows the claim.
-}
+We may write the total number of pulls by agents with types in $A$
+during phase $s$ as a sum of this quantity over $m$ ranging from
+$|S_{t_s}|$ down to 1.
+Noting that $|S_{t_s}| \leq \ARMNUM$ and taking the expectation of
+this sum completes the proof. 
 \end{proof}

### 2018-06-06 algorithm_general.tex

@@
 
-We begin by bounding the length of any phase, which will support bounding
-the regret of early rounds
-(before tail bounds have kicked in). The proof of Lemma~\ref{lem:phase-length} and all other proofs missing in the main paper may be found in the appendix.
+We begin by bounding the length of any phase,
+\dkedit{and more generally, the number of arm pulls by any given set
+  of agents.
+The bound of Lemma~\ref{lem:phase-length}} will support bounding the
+regret of early rounds (before tail bounds have kicked in).
+The proof of Lemma~\ref{lem:phase-length} and all other proofs missing
+in the main paper may be found in the appendix.
 
@@
 $\ARMNUM \cdot \log(s)$ time steps.
+
+More generally, for any set of types $A$, the expected number of times that 
+an agent with a type in $A$ appears in a phase $s$ is at most 
+$f(A) \cdot \ARMNUM \cdot \log(s)$,
+where $f(A) := \Prob[\AgV \sim \AgentDist]{\dkedit{\AgV} \in A}$.
 \end{lemma}
+
+%For any $s\geq 3$, the expected length of phase $s$ is at most
+%$\ARMNUM \cdot \log(s)$ time steps.
 

### 2018-06-06 algorithm_regret.tex

--- 2018-06-06 algorithm_regret.tex
@@
 with $\EarlyCut{s} \leq \TieCutoff$.
-\pfedit{
 We first consider agents \AgV incurring positive regret less than \EarlyCut{s}.
-Let $A$ be the set of types satisfying 
+Let $A_s$ be the set of types satisfying 
 $\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \EarlyCut{s}$.
 By Assumption~\ref{A1}, and because $\EarlyCut{s} \leq \TieCutoff$,
-the total measure of $A$
-is $\AlmostTied{\EarlyCut{s}} \leq \TieDensity \cdot \EarlyCut{s}$,
+the total measure of $A_s$
+is $\AlmostTied{\EarlyCut{s}} \leq \TieDensity \cdot \EarlyCut{s}$.
 Then, by Lemma~\ref{lem:phase-length},
-the expected number of pulls in phase $s$ by agents in $A$  
-bounded above by $\TieDensity\ \EarlyCut{s} \ARMNUM \log(s)$, and the total expected number of pulls by these agents by $\sum_{s=1}^T \TieDensity \ \EarlyCut[2]{s} \ARMNUM \log(s)$.
-Consider any agent $\AgV$ incurring positive regret less than $\EarlyCut{s}$.
-This agent's type must be in $A$.
-Moreover, this agent's regret is bounded above by $\EarlyCut{s}$.
-Thus, the expected total regret from such agents is at most
+the expected number of pulls in phase $s$ by agents in $A_s$  
+is bounded above by $\TieDensity \EarlyCut{s} \cdot \ARMNUM \log(s)$.
+\dkdelete{and the total expected number of pulls by these agents by
+$\sum_{s=1}^T \TieDensity \EarlyCut[2]{s} \ARMNUM \log(s)$.
+Consider}
+Any agent \AgV incurring positive regret less than $\EarlyCut{s}$
+must have a type in $A_s$,
+\dkdelete{Moreover, this agent's regret is bounded above by $\EarlyCut{s}$.}
+so the expected total regret from such agents,
+\dkedit{summed over all phases,} is at most
 \begin{equation}
-\sum_{s=1}^{T} \TieDensity \cdot \EarlyCut[2]{s} \ARMNUM \log(s).
+\sum_{s=1}^{T} \TieDensity \EarlyCut[2]{s} \cdot \ARMNUM \log(s).
 \label{equ:small_regret_bound}
 \end{equation}
-}
 
@@
 with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
-i.e., $k > \pfedit{t_{s+1}-t_{s}}$.
+i.e., $k > t_{s+1}-t_{s}$.
 By Lemma~\ref{lem:right-choice},
@@
 bound the maximum regret by \MAXR.
-Now, applying Lemma~\ref{lem:phase-length},
+Summing over the $T$ time periods,
 the total expected regret from large-regret steps is at most
-$\sum_{s = 1}^T \frac{24 \ARMNUM d}{T^2} \cdot \MAXR \cdot \ARMNUM \log(s)
-\leq 12 \ARMNUM^2 d \MAXR.$
-%\pfcomment{I deleted the left-hand side of the above equation because it was using random terms in the summand, and actually wasn't true.
-What was intended was an expectation outside of the sum, but I thought it simpler just to delete that term.}
+$24 \ARMNUM d \MAXR / T$.
 
@@
 + \ARMNUM \MAXR \log^2(T)
-+ \ARMNUM^2 \MAXR d
++ \frac{\ARMNUM \MAXR d}{T}
 + \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} \EarlyCut[2]{s} \log(s) \right)\\

### 2018-06-06 problem_setting.tex

@@
 When arm $i$ is pulled, its current utility-relevant features are
-determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero independent \pfedit{continuous} sub-Gaussian%
-\footnote{For simplicity of notation, we assume that the variance \pfedit{proxy}
+determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero
+independent continuous sub-Gaussian%
+\footnote{For simplicity of notation, we assume that the variance proxy
   $\sigma^2$ is uniform across time steps.
-  \pfedit{The} analysis extends \pfedit{easily when the variance proxy changes over time}.}
+  The analysis extends easily when the variance proxy changes over time.}
 noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.

### 2018-06-06 algorithm_regret.tex
changes accepted

@@
 is bounded above by $\TieDensity \EarlyCut{s} \cdot \ARMNUM \log(s)$.
-\dkdelete{and the total expected number of pulls by these agents by
-$\sum_{s=1}^T \TieDensity \EarlyCut[2]{s} \ARMNUM \log(s)$.
-Consider}
 Any agent \AgV incurring positive regret less than $\EarlyCut{s}$
 must have a type in $A_s$,
-\dkdelete{Moreover, this agent's regret is bounded above by $\EarlyCut{s}$.}
 so the expected total regret from such agents,
-\dkedit{summed over all phases,} is at most
+summed over all phases, is at most
 \begin{equation}

### 2018-06-06 payment-proof.tex
fixes to thm 2
finished edits of proof of Theorem 2

--- 2018-06-05 payment-proof.tex
@@
 \begin{rtheorem}{Theorem}{\ref{rst:budget}}
-The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
-\begin{align}
-O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right).  \nonumber 
-\end{align}
+The expected total payment of
+Algorithm~\ref{alg:basic-incentivizing} is at most
+$O \left(\ARMNUM^2 \cdot \e^{2/\MinProb} \right)$.
+%The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
+%\begin{align}
+% O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp\left(\frac{2}{\MinProb}\right) \right).  
+%\pfedit{O \left(\ARMNUM^2  d \cdot (\MAXR + \Diam d \sigma)\cdot \max\bigg\{\exp\left(\frac{2}{p}\right),
+%\left( \frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2},
+%\left( \frac{\sigma \TieDensity \Diam d}{\MinProb} \right)^{5/2}\bigg\}
+%\right).}\nonumber 
+%\end{align}
+\pfcomment{Maybe we want to simplify the constants in the above? Not sure.}
+\dkcomment{I think that stating it the way we state it in Section 3
+  makes the most sense.}
 \end{rtheorem}
@@
 Define $h(\ell) := \max \left( \exp(\frac{2}{\MinProb}),
+\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2},
 \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
@@
 Because $s \geq h(\ell)$, we get that
-$g(s,\ell) \leq \frac{\MinProb}{4 \Diam d \TieDensity}$
+$g(s,\ell) \leq \min(\frac{\TieCutoff}{2\Diam d}, \frac{\MinProb}{4 \Diam d \TieDensity})$
 as well as $s \geq \exp(2/\MinProb)$.
@@
 \begin{align*}
-O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot h(1) \right)
-& = 
-O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma
-\cdot \exp(\frac{2}{\MinProb}) \right).
+& O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot h(1)
+  \right)
+\\ = 
+& O \left(\ARMNUM^2  d \cdot (\MAXR + \Diam d \sigma)\cdot
+  \max \left( \exp \left(\frac{2}{\MinProb}\right),
+		    \left( \frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2},
+    \left( \frac{\sigma \TieDensity \Diam d}{\MinProb} \right)^{5/2} \right)
+\right)
+\\ =
+& \dkedit{O \left( \ARMNUM^2 \cdot \exp \left(\frac{2}{\MinProb} \right) \right)}.
 \end{align*}

### 2018-06-06 algorithm_regret.tex
marked using bcedit

@@
 O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
-+ \ARMNUM \TieDensity \cdot \log^3(T) \right)$.\QED
++ \bcedit{\ARMNUM \log^2(T)} + \ARMNUM \TieDensity \cdot \log^3(T) \right)$.\QED
 \end{emptyextraproof}

### 2018-06-06 introduction.tex
marked using bcedit

@@
 There is a policy that achieves expected 
-cumulative regret $O (\ARMNUM \e^{2/\MinProb} + \TieDensity \ARMNUM \log^3(T))$,
+    cumulative regret $O (\ARMNUM \e^{2/\MinProb} + \bcedit{\ARMNUM \log^2(T)} + \TieDensity \ARMNUM \log^3(T))$,
 using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
-In particular, when agents who are close to tied between two arms have measure $0$,
-both the expected regret and expected payment are bounded by constants
-(with respect to $T$). 
 \end{theorem}

### 2018-06-06 result_discussion.tex
marked using bcedit

@@
 above by 
-$O \left(\ARMNUM \cdot \e^{2/\MinProb} + \TieDensity \ARMNUM \log^3(T) \right)$.
+    $O \left(\ARMNUM \cdot \e^{2/\MinProb} + \bcedit{\ARMNUM \log^2(T)}+ \TieDensity \ARMNUM \log^3(T) \right)$.
 \end{theorem}
@@
 the expected regret of any algorithm.
-The instance is simple: it has two arms, one \pfedit{with known}
-attributes; 
+The instance is simple: it has two arms, one with known attributes; 
 in addition, one draw from the other arm is observed in

### 2018-06-06 algorithm_regret.tex
Revert "marked using bcedit"
Reverting 3 of bangrui's commits that added in an extra term to the
regret guarantee that is polynomial in T.  Rather than making this
change, we are going to change the proof so that we get rid of this
term.

This reverts commit a6ab7f1767f177a8a9e980614ab0537c83b18402.

--- 2018-06-06 algorithm_regret.tex
@@
 O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
-+ \ARMNUM \TieDensity \cdot \log^3(T) \right)$.\QED
++ \ARMNUM \log^2(T) + \ARMNUM \TieDensity \cdot \log^3(T) \right)$.\QED
 \end{emptyextraproof}

### 2018-06-06 introduction.tex
Revert "marked using bcedit"
Reverting 3 of bangrui's commits that added in an extra term to the
regret guarantee that is polynomial in T.  Rather than making this
change, we are going to change the proof so that we get rid of this
term.

This reverts commit a6ab7f1767f177a8a9e980614ab0537c83b18402.

@@
 There is a policy that achieves expected 
-    cumulative regret $O (\ARMNUM \e^{2/\MinProb} + \bcedit{\ARMNUM \log^2(T)} + \TieDensity \ARMNUM \log^3(T))$,
+    cumulative regret $O (\ARMNUM \e^{2/\MinProb} + \ARMNUM \log^2(T) + \TieDensity \ARMNUM \log^3(T))$,
 using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.

### 2018-06-06 result_discussion.tex
Revert "marked using bcedit"
Reverting 3 of bangrui's commits that added in an extra term to the
regret guarantee that is polynomial in T.  Rather than making this
change, we are going to change the proof so that we get rid of this
term.

This reverts commit a6ab7f1767f177a8a9e980614ab0537c83b18402.

@@
 above by 
-    $O \left(\ARMNUM \cdot \e^{2/\MinProb} + \bcedit{\ARMNUM \log^2(T)}+ \TieDensity \ARMNUM \log^3(T) \right)$.
+    $O \left(\ARMNUM \cdot \e^{2/\MinProb} + \ARMNUM \log^2(T)+ \TieDensity \ARMNUM \log^3(T) \right)$.
 \end{theorem}

### 2018-06-06 algorithm_regret.tex
fixed proof of Theorem 3

--- 2018-06-06 algorithm_regret.tex
@@
 cutoff
-$\EarlyCut{s} = \sqrt{\frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}}$,
+$\EarlyCut{s} = \sqrt{\frac{128\log(\dkedit{s}) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}}$,
 and consider a regret exceeding \EarlyCut{s} large.
@@
 The remaining phases are the ones with
-$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2/\TieCutoff^2$.
-Each such phase lasts for at most $\ARMNUM \cdot \log(s)$ steps
+$\dkedit{\frac{s}{\log s}} \leq \frac{128}{1.8} \cdot \Diam^2 d^2 \sigma^2/\TieCutoff^2$.
+\dkedit{Because $\frac{s}{\log s} = \Omega(s^{2/3})$, there are at most
+$O(\Diam^3 d^3 \sigma^3/\TieCutoff^3)$ such phases,}
+each such phase lasts for at most $\ARMNUM \cdot \log(s)$ steps
 in expectation by Lemma~\ref{lem:phase-length},
 and each step incurs regret at most \MAXR.
-The total expected regret incurred in these phases is at most
-$O(\ARMNUM \MAXR \cdot \log(T) \Diam^2 d^2 \sigma^2/\TieCutoff^2
-\cdot \log (\log(T) \cdot \Diam^2 d^2 \sigma^2/\TieCutoff^2)
-\leq O(\ARMNUM \MAXR \log^2(T) \cdot \Diam^3 d^3 \sigma^3/\TieCutoff^3)$,
-by crudely bounding $\log y \leq O(\sqrt{y})$.
+Therefore, the total expected regret incurred in these phases is at most
+\dkedit{$O(\ARMNUM \MAXR \cdot \Diam^3 d^3 \sigma^3/\TieCutoff^3
+\cdot \log (\Diam^3 d^3 \sigma^3/\TieCutoff^3))
+\leq O(\ARMNUM \MAXR \Diam^4 d^4 \sigma^4/\TieCutoff^4)
+= O(\ARMNUM \MAXR)$,}
+by crudely bounding \dkedit{$\log y \leq O(y^{1/3})$}.
 
@@
 By Lemma~\ref{lem:right-choice},
-under \AccEU{\tau_s^k}{\frac{\EarlyCut{s}}{2\Diam d}}, no agent at time $t$ will incur
-regret more than \EarlyCut{s}.
+under \AccEU{\tau_s^k}{\frac{\EarlyCut{s}}{2\Diam d}},
+no agent at time $t$ will incur regret more than \EarlyCut{s}.
 
@@
 Substituting that
-$x_n = \frac{\EarlyCut{n}}{2 \Diam d} = \sqrt{\frac{32\log(T) \cdot \sigma^2}{1.8 n}}$,
+$x_n = \frac{\EarlyCut{n}}{2 \Diam d} = \sqrt{\frac{32\dkedit{\log(n)} \cdot \sigma^2}{1.8 n}}$,
 the left-hand side is
@@
 \[
-  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 \log T}{1.8}}
+  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 \dkedit{\log n}}{1.8}}
   \; \leq \;
-  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 n \log T}{1.8}},
+  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 n \dkedit{\log n}}{1.8}},
 \]
-while the right-hand side is $\sqrt{\frac{8 n \log(T)}{1.8}}$.
+while the right-hand side is $\sqrt{\frac{8 n \dkedit{\log(n)}}{1.8}}$.
 Squaring both sides and canceling out common terms,
 the desired inequality is equivalent to
-$\frac{50}{9} \log T \geq \log(\log_{1.1}(n) + 1)$.
-Because $n \leq T$, it is sufficient to show that
-$\frac{50}{9} \log T \geq \log(\log_{1.1}(T) + 1)$,
-which can be verified by numerical calculation for $T=2$ and a
+$\frac{50}{9} \dkedit{\log n} \geq \log(\log_{1.1}(n) + 1)$.
+\dkdelete{Because $n \leq T$, it is sufficient to show that
+$\frac{50}{9} \log T \geq \log(\log_{1.1}(T) + 1)$,}
+This can be verified by numerical calculation for \dkedit{$n=2$} and a
 derivative test.
@@
 \Prob{\AccEU{\tau_s^k}{x_s}}
-& \leq 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16 \sigma^2} \right)
-\; = \; \frac{24 \ARMNUM d}{T^2}.
+& \leq 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s \dkedit{x_s}^2}{16 \sigma^2} \right)
+\; = \; \frac{24 \ARMNUM d}{\dkedit{s^2}}.
 \end{align*}
 
-In the low-probability event, we simply 
-bound the maximum regret by \MAXR.
-Summing over the $T$ time periods,
+In the low-probability event, we simply bound the maximum regret by \MAXR.
+Summing over \dkedit{all} time periods,
 the total expected regret from large-regret steps is at most
-$24 \ARMNUM d \MAXR / T$.
+\dkedit{$24 \ARMNUM d \MAXR \cdot \frac{\pi^2}{6} = O(\ARMNUM \MAXR)$.}
 
@@
 and substituting 
-$\EarlyCut[2]{s} = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
+$\EarlyCut[2]{s} = \frac{128 \dkedit{\log(s)} \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
 the cumulative regret up to time $T$ is at most
@@
 O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
-+ \ARMNUM \MAXR \log^2(T)
-+ \frac{\ARMNUM \MAXR d}{T}
+\dkedit{+ \ARMNUM \MAXR}
+\dkedit{+ \ARMNUM \MAXR}
 + \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} \EarlyCut[2]{s} \log(s) \right)\\

### 2018-06-06 problem_setting.tex
clarified discrete nature

@@
 Assumption~\ref{A1} implies that ties happen with probability $0$.
-One special case of interest we discuss below is
-$\TieDensity = 0$. This case arises when there is a cutoff
+One special case of interest we discuss below is $\TieDensity = 0$.
+This case arises when there is a cutoff
 \TieCutoff such that only a measure-zero set of agents has two best arms
 within utility \TieCutoff of each other.
-In particular, $\TieDensity = 0$ happens whenever \AgentDist is discrete,
-i.e., supported on a finite set of types,
+In particular, $\TieDensity = 0$ happens whenever \AgentDist is \dkdelete{discrete,
+i.e.,} supported on a finite set of types,
 and each type has a unique best arm.

### 2018-06-06 Discussion-Proof.tex
making notes cleaner
fix theorem 9, check david edits

--- 2018-06-06 Discussion-Proof.tex
@@
 \begin{rtheorem}{Theorem}{\ref{rst:discrete}}
-Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment budget bounded above by 
-\begin{align*}
-\pfedit{
-O \left(\ARMNUM^2  d \cdot (\MAXR + \Diam d \sigma)\cdot
-    \max\bigg\{\frac{2}{p},
-    \left( \frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2}
-    \bigg\}
-\right)
-}
-\end{align*}
-and expected regret bounded above by 
-\begin{align}
-O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
-  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
-  \right).  \nonumber
-\end{align}
+Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment \pfdelete{budget} bounded above by 
+$\pfedit{O \left(\ARMNUM^2 /p \right)}$
+and expected regret bounded above by \pfedit{$O(\ARMNUM / p)$}.
 \end{rtheorem}
@@
 \pfedit{
-\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2},
+\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2}
 }
-\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
-\right)
-\pfedit{
-= 
-\max \left( \frac{2}{\MinProb},
-\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2}
-\right)
-}
-$.
+\right).
+$
+%\pfedit{and $s_1 = \max(2,\frac{30\sigma^3}{x^3}, \frac2{\MinProb})$}.
 
 To prove the bound on the expected regret, one can first prove tightened versions of Lemmas~\ref{lem:no-incentives} and \ref{lem:numP},
-which replace the $\exp(2/\MinProb)$ term with simply $2/\MinProb$.
-In return, the length of phase $s$ is now bounded only be $\ARMNUM s$ instead of $\ARMNUM \log(s)$.
-Substituting these changes into the proof\pfedit{s} of Theorem\pfedit{s}~\ref{rst:regret} \pfedit{and \ref{rst:budget}}, we obtain the claimed bounds.
+which replace the $\exp(2/\MinProb)$ term with \pfdelete{simply} $2/\MinProb$ \pfedit{and use $L=0$.}
+In return, the length of phase $s$ is now bounded only by $\ARMNUM s$ instead of $\ARMNUM \log(s)$, \pfedit{and the expectetd number of times steps in which a payment is made is bounded by $O(N/p + N^2)$.}
+Substituting these changes into the proof of Theorem~\ref{rst:regret}, we obtain the bound $O(R(N/p + N^2) + NR + NR) = O(N/p)$ since $p \le 1/N$.
 
@@
 
+\pfcomment{
+The calculation I did for the bound on the regret is:
+
+\begin{itemize}
+\item regret from times when we pay is $RN(N + 1/p)$
+\item regret from phases with $\gamma(s) >= \hat{z}$ is $O(NR D^6 d^6 \sigma^6 / \hat{z}^6)$
+\item regret from pulls with small regret is 0
+\item regret from pulls with big regret is $O(NR)$
+\end{itemize}
+}
+
 \end{proof}
@@
 \begin{align*}
-    O\left(\ARMNUM^2 d\cdot(R+Dd\sigma)\cdot \max\bigg\{ \left(\frac{24\sigma \ell \Diam d}{\TieCutoff} \right)^{5/2},
-        \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}\bigg\}\right)
+    O\left(\ARMNUM^2 d\cdot(R+Dd\sigma)\cdot \max\bigg\{ \left(\frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2},
+        \left( \frac{\sigma \TieDensity \Diam d}{\MinProb} \right)^{5/2}\bigg\}\right)
 \end{align*}
@@
     \bcedit{
-    $h(\ell) := \max\big\{ \left(\frac{24\sigma \ell \Diam d}{\TieCutoff} \right)^{5/2},
-        \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}\big\}$
+    $h(\ell) := \max\big\{ \left(\frac{24\sigma \ell\Diam d}{\TieCutoff} \right)^{5/2},
+        \left( \frac{48\sigma \ell\TieDensity \Diam d}{\MinProb} \right)^{5/2}\big\}$
     }

### 2018-06-06 Discussion.tex
changed the regret for Theorem 10
fixing theorem 9
addressed the issue in Theorem 10
my late nite attempt to fix thm 9
fix theorem 9, check david edits

@@
 \label{a:discrete}
-There is a positive $\delta_0$ such that
-$\AlmostTied{\delta_0} = 0$.
+There is a positive \pfedit{$\hat{z}$} such that
+$\AlmostTied{\pfedit{\hat{z}}} = 0$.
 \end{assumption}
@@
 Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment \pfdelete{budget} bounded above by 
-\begin{align*}
-O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
-\end{align*}
-and expected regret bounded above by 
-\begin{align}
-O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
-  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
-  \right).  \nonumber
-\end{align}
+$\pfedit{O \left(\ARMNUM^2 /p \right)}$
+and expected regret bounded above by \pfedit{$O(\ARMNUM / p)$}.
 \end{theorem}
@@
 Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has expected payment \pfdelete{budget} bounded above by 
+    \bcedit{
 \begin{align*}
-O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
+    O\left(\ARMNUM^2d\cdot(R+\Diam d\sigma)\cdot\max\bigg\{\left(\frac{\sigma \Diam d}{\TieCutoff}\right)^{5/2},
+    \left(\frac{\sigma \TieDensity\Diam d}{\MinProb}\right)^{5/2}\bigg\}\right)
 \end{align*}
+}
 and expected regret bounded above by
+\bcedit{
 \begin{align*}
@@
   + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
-  + \frac{\ARMNUM^2 d\MAXR}{\MinProb}
   + \frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
 \end{align*}
+}
 \end{theorem}

### 2018-06-06 algorithm_regret.tex
fix theorem 9, check david edits

--- 2018-06-06 algorithm_regret.tex
@@
 cutoff
-$\EarlyCut{s} = \sqrt{\frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}}$,
+$\EarlyCut{s} = \sqrt{\frac{128\log(s) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}}$,
 and consider a regret exceeding \EarlyCut{s} large.
@@
 The remaining phases are the ones with
-$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2/\TieCutoff^2$.
-Each such phase lasts for at most $\ARMNUM \cdot \log(s)$ steps
+$\frac{s}{\log s} \leq \frac{128}{1.8} \cdot \Diam^2 d^2 \sigma^2/\TieCutoff^2$.
+Because $\frac{s}{\log s} = \Omega(s^{2/3})$, there are at most
+$O(\Diam^3 d^3 \sigma^3/\TieCutoff^3)$ such phases,
+each such phase lasts for at most $\ARMNUM \cdot \log(s)$ steps
 in expectation by Lemma~\ref{lem:phase-length},
 and each step incurs regret at most \MAXR.
-The total expected regret incurred in these phases is at most
-$O(\ARMNUM \MAXR \cdot \log(T) \Diam^2 d^2 \sigma^2/\TieCutoff^2
-\cdot \log (\log(T) \cdot \Diam^2 d^2 \sigma^2/\TieCutoff^2)
-\leq O(\ARMNUM \MAXR \log^2(T) \cdot \Diam^3 d^3 \sigma^3/\TieCutoff^3)$,
-by crudely bounding $\log y \leq O(\sqrt{y})$.
+Therefore, the total expected regret incurred in these phases is at most
+$O(\ARMNUM \MAXR \cdot \Diam^3 d^3 \sigma^3/\TieCutoff^3
+\cdot \log (\Diam^3 d^3 \sigma^3/\TieCutoff^3))
+\leq O(\ARMNUM \MAXR \Diam^4 d^4 \sigma^4/\TieCutoff^4)
+= O(\ARMNUM \MAXR)$,
+by crudely bounding $\log y \leq O(y^{1/3})$.
 
@@
 Substituting that
-$x_n = \frac{\EarlyCut{n}}{2 \Diam d} = \sqrt{\frac{32\log(T) \cdot \sigma^2}{1.8 n}}$,
+$x_n = \frac{\EarlyCut{n}}{2 \Diam d} = \sqrt{\frac{32\log(n) \cdot \sigma^2}{1.8 n}}$,
 the left-hand side is
@@
 \[
-  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 \log T}{1.8}}
+  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 \log n}{1.8}}
   \; \leq \;
-  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 n \log T}{1.8}},
+  \sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{2 n \log n}{1.8}},
 \]
-while the right-hand side is $\sqrt{\frac{8 n \log(T)}{1.8}}$.
+while the right-hand side is $\sqrt{\frac{8 n \log(n)}{1.8}}$.
 Squaring both sides and canceling out common terms,
 the desired inequality is equivalent to
-$\frac{50}{9} \log T \geq \log(\log_{1.1}(n) + 1)$.
-Because $n \leq T$, it is sufficient to show that
-$\frac{50}{9} \log T \geq \log(\log_{1.1}(T) + 1)$,
-which can be verified by numerical calculation for $T=2$ and a
+$\frac{50}{9} \log n \geq \log(\log_{1.1}(n) + 1)$.
+This can be verified by numerical calculation for $n=2$ and a
 derivative test.
@@
 \Prob{\AccEU{\tau_s^k}{x_s}}
-& \leq 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x^2}{16 \sigma^2} \right)
-\; = \; \frac{24 \ARMNUM d}{T^2}.
+& \leq 24 \ARMNUM d \cdot \exp \left( \frac{-1.8 s x_s^2}{16 \sigma^2} \right)
+\; = \; \frac{24 \ARMNUM d}{s^2}.
 \end{align*}
 
-In the low-probability event, we simply 
-bound the maximum regret by \MAXR.
-Summing over the $T$ time periods,
+In the low-probability event, we simply bound the maximum regret by \MAXR.
+Summing over \dkedit{all} time periods,
 the total expected regret from large-regret steps is at most
-$24 \ARMNUM d \MAXR / T$.
+$24 \ARMNUM d \MAXR \cdot \frac{\pi^2}{6} = O(\ARMNUM \MAXR)$.
 
@@
 O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
-+ \ARMNUM \MAXR \log^2(T)
-+ \frac{\ARMNUM \MAXR d}{T}
++ \ARMNUM \MAXR
++ \ARMNUM \MAXR
 + \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} \EarlyCut[2]{s} \log(s) \right)\\
@@
 O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
-+ \ARMNUM \log^2(T) + \ARMNUM \TieDensity \cdot \log^3(T) \right)$.\QED
++ \ARMNUM \TieDensity \cdot \log^3(T) \right)$.\QED
 \end{emptyextraproof}

### 2018-06-06 result_discussion.tex

@@
 the case $\TieDensity = 0$ arises, for instance, for
-discrete agent distributions.
-In fact, in the case of a discrete agent distribution,
-it is possible to modify the algorithm to also
-reduce the dependence on \MinProb from exponential to polynomial.
+\dkdelete{discrete} agent distributions \dkedit{with finite support}.
+\dkdelete{In fact, in the case of a discrete agent distribution,}
+\dkedit{Alternatively, when $\TieDensity = 0$, 
+one can modify} the algorithm to
+reduce the dependence on \MinProb from exponential to polynomial,
+\dkedit{at the cost of reintroducing the poly-logarithmic dependence
+  on $T$}.
 Theorem~\ref{rst:discrete} (given later) states that the modified
@@
 $O \left(\frac{\ARMNUM^2}{\MinProb^{5/2}} \right)$.
+\dkcomment{Adjust these bounds.}
+\dkedit{Whether one can achieve regret that is simultaneously
+  independent of $T$ and polynomial in \ARMNUM and \MinProb is an
+  interesting open question.}
 
@@
 best arms quickly.
-Aside from the assumption that $\TieDensity = 0$, another assumption
-allows us to eliminate this exponential dependence.
+Aside from the assumption that $\TieDensity = 0$,
+another assumption allows us to eliminate this exponential dependence.
 Namely, when \MinProb (or a lower bound on it) is known ahead of time,

### 2018-06-06 Discussion-Proof.tex
edit to lemma 10

@@
 \begin{rtheorem}{Theorem}{\ref{rst:known-p}}
-Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has an expected payment budget bounded above by 
-    \bcedit{
-\begin{align*}
-    O\left(\ARMNUM^2 d\cdot(R+Dd\sigma)\cdot \max\bigg\{ \left(\frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2},
-        \left( \frac{\sigma \TieDensity \Diam d}{\MinProb} \right)^{5/2}\bigg\}\right)
-\end{align*}
-}
+Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has an expected payment bounded above by 
+$\pfedit{O\left(N^2 \max\{1, (L/p)^{5/2}\}\right)}$.
 and an expected regret bounded above by
@@
 \begin{proof}
-  The proof of the expected payment bound follows Lemma~\ref{rst:budget} except for defining
-    \bcedit{
-    $h(\ell) := \max\big\{ \left(\frac{24\sigma \ell\Diam d}{\TieCutoff} \right)^{5/2},
+	The proof of the expected payment bound follows Lemma~\ref{rst:budget} \pfedit{ except we define 
+	$h(\ell)$ without including the $\exp(2/\MinProb)$ term}
+    as $h(\ell) := \max\big\{ \left(\frac{24\sigma \ell\Diam d}{\TieCutoff} \right)^{5/2},
         \left( \frac{48\sigma \ell\TieDensity \Diam d}{\MinProb} \right)^{5/2}\big\}$
+\pfedit{
+The resulting bound on expected payment is
+$O\left(\ARMNUM^2 d\cdot(R+Dd\sigma)\cdot \max\bigg\{ \left(\frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2},
+ \left( \frac{\sigma \TieDensity \Diam d}{\MinProb} \right)^{5/2}\bigg\}\right)
+ = O\left(N^2 \max\{1, (L/p)^{5/2}\}\right)$.
 }
-(without including the $\exp(2/\MinProb)$ term).
 

### 2018-06-06 result_discussion.tex
putting back edits in section 3

--- 2018-06-06 result_discussion.tex
@@
 the case $\TieDensity = 0$ arises, for instance, for
-discrete agent distributions.
-In fact, in the case of a discrete agent distribution,
-it is possible to modify the algorithm to also
-reduce the dependence on \MinProb from exponential to polynomial.
+discrete agent distributions with finite support.
+\pfedit{In fact, when $\TieDensity = 0$,
+one can also modify} the algorithm to
+reduce the dependence on \MinProb from exponential to polynomial
+\pfdelete{at the cost of reintroducing the poly-logarithmic dependence
+  on $T$}.
 Theorem~\ref{rst:discrete} (given later) states that the modified
 algorithm achieves expected regret
-$O \left(\frac{\ARMNUM}{\MinProb^4} \right)$
+$O \left(\ARMNUM/\pfedit{\MinProb} \right)$
 with expected payments of
-$O \left(\frac{\ARMNUM^2}{\MinProb^{5/2}} \right)$.
+$O \left(\ARMNUM^2/\pfedit{\MinProb} \right)$.
+\pfdelete{Whether one can achieve regret that is simultaneously
+  independent of $T$ and polynomial in \ARMNUM and \MinProb is an
+  interesting open question.}
 

### 2018-06-06 Discussion-Proof.tex

@@
 \begin{rtheorem}{Theorem}{\ref{rst:discrete}}
-Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment \pfdelete{budget} bounded above by 
-$\pfedit{O \left(\ARMNUM^2 /p \right)}$
-and expected regret bounded above by \pfedit{$O(\ARMNUM / p)$}.
+Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm
+has expected payment bounded above by 
+$O \left(\ARMNUM^2/\MinProb \right)$
+and expected regret bounded above by $O(\ARMNUM / \MinProb)$.
 \end{rtheorem}
@@
 \begin{proof}
-The proof of the expected payment bound is the same as the proof of Theorem~\ref{rst:budget}, except that we now define $h(\ell) := \max \left( \frac{2}{\MinProb},
-\pfedit{
-\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2}
-}
-\right).
-$
+The proof of the expected payment bound is the same as the proof of
+Theorem~\ref{rst:budget},
+except that we now define
+$h(\ell) := \max \left( \frac{2}{\MinProb},
+\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2} \right)$.
 %\pfedit{and $s_1 = \max(2,\frac{30\sigma^3}{x^3}, \frac2{\MinProb})$}.
 
-To prove the bound on the expected regret, one can first prove tightened versions of Lemmas~\ref{lem:no-incentives} and \ref{lem:numP},
-which replace the $\exp(2/\MinProb)$ term with \pfdelete{simply} $2/\MinProb$ \pfedit{and use $L=0$.}
-In return, the length of phase $s$ is now bounded only by $\ARMNUM s$ instead of $\ARMNUM \log(s)$, \pfedit{and the expectetd number of times steps in which a payment is made is bounded by $O(N/p + N^2)$.}
-Substituting these changes into the proof of Theorem~\ref{rst:regret}, we obtain the bound $O(R(N/p + N^2) + NR + NR) = O(N/p)$ since $p \le 1/N$.
+To prove the bound on the expected regret,
+one can first prove tightened versions of Lemmas~\ref{lem:no-incentives} and \ref{lem:numP},
+which replace the $\exp(2/\MinProb)$ term with $2/\MinProb$ and use $L=0$.
+In return, the length of phase $s$ is now bounded only by $\ARMNUM s$
+instead of $\ARMNUM \log(s)$,
+and the expectetd number of times steps in which a payment is made is bounded by
+$O(\ARMNUM/\MinProb + \ARMNUM^2)$.
+Substituting these changes into the proof of Theorem~\ref{rst:regret},
+we obtain the bound $O(\MAXR(\ARMNUM/\MinProb + \ARMNUM^2) + \ARMNUM \MAXR +
+\ARMNUM \MAXR) = O(\ARMNUM/\MinProb)$ since $\MinProb \le 1/\ARMNUM$.
+\end{proof}
 
-\pfcomment{
-The calculation I did for the bound on the expected payment is,
-\begin{align*}
-&O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot h(1) \right) \\ 
-&=O \left(\ARMNUM^2  d \cdot (\MAXR + \Diam d \sigma)\cdot
-    \max\bigg\{\frac{2}{p},
-    \left( \frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2}
-    \bigg\}
-\right)
-\end{align*}
-}
+% \pfcomment{
+% The calculation I did for the bound on the expected payment is,
+% \begin{align*}
+% &O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot h(1) \right) \\ 
+% &=O \left(\ARMNUM^2  d \cdot (\MAXR + \Diam d \sigma)\cdot
+%     \max\bigg\{\frac{2}{p},
+%     \left( \frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2}
+%     \bigg\}
+% \right)
+% \end{align*}
+% }
+% \pfcomment{
+% The calculation I did for the bound on the regret is:
 
-\pfcomment{
-The calculation I did for the bound on the regret is:
-
-\begin{itemize}
-\item regret from times when we pay is $RN(N + 1/p)$
-\item regret from phases with $\gamma(s) >= \hat{z}$ is $O(NR D^6 d^6 \sigma^6 / \hat{z}^6)$
-\item regret from pulls with small regret is 0
-\item regret from pulls with big regret is $O(NR)$
-\end{itemize}
-}
-
-\end{proof}
+% \begin{itemize}
+% \item regret from times when we pay is $RN(N + 1/p)$
+% \item regret from phases with $\gamma(s) >= \hat{z}$ is $O(NR D^6 d^6 \sigma^6 / \hat{z}^6)$
+% \item regret from pulls with small regret is 0
+% \item regret from pulls with big regret is $O(NR)$
+% \end{itemize}
+% }
 

### 2018-06-06 Discussion-Proof.tex
edits in Theorem 10

--- 2018-06-06 Discussion-Proof.tex
@@
 \begin{align*}
-O \left(\frac{\MAXR \ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
-  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
-  + \frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
+O\left(\frac{\ARMNUM^2}{\MinProb^2}
+    + \frac{\ARMNUM^2}{\hat{z}^2} + \frac{\ARMNUM}{\hat{z}^3}
+    + \frac{NL\log^3(T)}{p}    
+    \right)
 \end{align*}
@@
 proving the following upper bound on the number of time steps in which a payment is made:
+    \bcedit{
 \begin{align}
-O\left(\frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
-  + \frac{\ARMNUM^2 d}{1 - \exp \left(
-    \frac{-1.8 \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
-  \right)} \right). \nonumber 
+O\left(\frac{\ARMNUM^2 \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^2}
+    + \frac{\ARMNUM^2 d^3 \sigma^2 \Diam^2}{\hat{z}^2} + \frac{\ARMNUM \Diam^3 d^3 \sigma^3}{\hat{z}^3}
+ \right). \nonumber 
 \end{align}
+}
 The proof of this result follows that of Lemma~\ref{lem:numP},

### 2018-06-06 Discussion-Proof.tex
fix a typo

--- 2018-06-06 Discussion-Proof.tex
@@
     as $h(\ell) := \max\big\{ \left(\frac{24\sigma \ell\Diam d}{\TieCutoff} \right)^{5/2},
-        \left( \frac{48\sigma \ell\TieDensity \Diam d}{\MinProb} \right)^{5/2}\big\}$
+        \left( \frac{48\sigma \ell\TieDensity \Diam d}{\MinProb} \right)^{5/2}\big\}$.
 \pfedit{

### 2018-06-06 Discussion-Proof.tex
typo

@@
 Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has an expected payment bounded above by 
-$\pfedit{O\left(N^2 \max\{1, (L/p)^{5/2}\}\right)}$.
+$\pfedit{O\left(N^2 \max\{1, (L/p)^{5/2}\}\right)}$
 and an expected regret bounded above by

### 2018-06-06 Lemmas.tex
resolving edits

@@
 $f(A) \cdot \ARMNUM \cdot \log(s)$,
-where $f(A) := \Prob[\AgV \sim \AgentDist]{\dkedit{\AgV} \in A}$.
+where $f(A) := \Prob[\AgV \sim \AgentDist]{\AgV \in A}$.
 \end{rlemma}
@@
 Let $\tau_m$ be the maximum of $t_s$ (the start of phase $s$)
-and the time $t$ when $S_t$ first contains \dkedit{(at most)} $m$ elements.
+and the time $t$ when $S_t$ first contains (at most) $m$ elements.
 The phase ends when $S_t$ contains no elements, i.e., $\tau_0 = t_{s+1}$.
 We consider the expected number of pulls during times
-$\dkedit{t \in} [\tau_m, \tau_{m-1})$ made by agents whose types are in $A$.
+$t \in [\tau_m, \tau_{m-1})$ made by agents whose types are in $A$.
 

### 2018-06-06 Discussion-Proof.tex
edited proof of Theorem 10

@@
 \begin{rtheorem}{Theorem}{\ref{rst:known-p}}
-Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has an expected payment bounded above by 
-$\pfedit{O\left(N^2 \max\{1, (L/p)^{5/2}\}\right)}$
-and an expected regret bounded above by
-\bcedit{
-\begin{align*}
-O\left(\frac{\ARMNUM^2}{\MinProb^2}
-    + \frac{\ARMNUM^2}{\hat{z}^2} + \frac{\ARMNUM}{\hat{z}^3}
-    + \frac{NL\log^3(T)}{p}    
-    \right)
-\end{align*}
-}
+% Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has an expected payment bounded above by 
+% $\pfedit{O\left(N^2 \max\{1, (L/p)^{5/2}\}\right)}$.
+% and an expected regret bounded above by
+% \bcedit{
+% \begin{align*}
+% O\left(\frac{\ARMNUM^2}{\MinProb^2}
+%     + \frac{\ARMNUM^2}{\hat{z}^2} + \frac{\ARMNUM}{\hat{z}^3}
+%     + \frac{NL\log^3(T)}{p}    
+%     \right)
+% \end{align*}
+% }
+Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has
+expected payment bounded above by  
+$O(\ARMNUM^2 \cdot \max(1,(\TieDensity/\MinProb)^{5/2}))$ 
+and expected regret bounded above by
+%\begin{align*}
+$O \left( \frac{\ARMNUM^2}{\MinProb^2}
+%  + \frac{\ARMNUM^2}{\hat{z}^2}+\frac{\ARMNUM}{\hat{z}^3}
+  +\frac{\ARMNUM \TieDensity \log^3(T)}{\MinProb}\right)$.
+%  \end{align*}
 \end{rtheorem}
@@
 \begin{proof}
-	The proof of the expected payment bound follows Lemma~\ref{rst:budget} \pfedit{ except we define 
-	$h(\ell)$ without including the $\exp(2/\MinProb)$ term}
-    as $h(\ell) := \max\big\{ \left(\frac{24\sigma \ell\Diam d}{\TieCutoff} \right)^{5/2},
-        \left( \frac{48\sigma \ell\TieDensity \Diam d}{\MinProb} \right)^{5/2}\big\}$.
-\pfedit{
-The resulting bound on expected payment is
-$O\left(\ARMNUM^2 d\cdot(R+Dd\sigma)\cdot \max\bigg\{ \left(\frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2},
- \left( \frac{\sigma \TieDensity \Diam d}{\MinProb} \right)^{5/2}\bigg\}\right)
- = O\left(N^2 \max\{1, (L/p)^{5/2}\}\right)$.
-}
+The proof of the expected payment bound follows Lemma~\ref{rst:budget},
+except we define $h(\ell)$ without including the $\exp(2/\MinProb)$ term,
+instead using
+$h(\ell) := \max \left(
+  \left(\frac{24\sigma \ell\Diam d}{\TieCutoff} \right)^{5/2},
+  \left( \frac{48\sigma \ell\TieDensity \Diam d}{\MinProb} \right)^{5/2}
+\right)$.
+The resulting bound on the expected payment is
+\begin{align*}
+O\left( \ARMNUM^2 d \cdot (\MAXR+\Diam d\sigma) \cdot
+  \max \left(
+    \left(\frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2},
+    \left( \frac{\sigma \TieDensity \Diam d}{\MinProb} \right)^{5/2}
+    \right) \right)
+& = O\left(\ARMNUM^2 \max (1, (\TieDensity/\MinProb)^{5/2}) \right).
+\end{align*}
 
@@
 proving the following upper bound on the number of time steps in which a payment is made:
-    \bcedit{
-\begin{align}
+
+\begin{align*}
 O\left(\frac{\ARMNUM^2 \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^2}
-    + \frac{\ARMNUM^2 d^3 \sigma^2 \Diam^2}{\hat{z}^2} + \frac{\ARMNUM \Diam^3 d^3 \sigma^3}{\hat{z}^3}
- \right). \nonumber 
-\end{align}
-}
+    + \frac{\ARMNUM^2 d^3 \sigma^2 \Diam^2}{\TieCutoff^2} + \frac{\ARMNUM \Diam^3 d^3 \sigma^3}{\TieCutoff^3}
+  \right)
+& \dkedit{= O \left( \frac{\ARMNUM^2}{\MinProb^2} \right)}.
+\end{align*}
+
 The proof of this result follows that of Lemma~\ref{lem:numP},
-but the less aggressive incentivization allows us to define $\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3})$ since $\frac{1}{\log(s+s_0)} \leq \frac{\MinProb}{2}$ is true for all $s$.
+but the less aggressive incentivization allows us to define
+$\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3})$
+since $\frac{1}{\log(s+s_0)} \leq \frac{\MinProb}{2}$ is true for all $s$.
 
-Using this tighter bound on the number of incentiziations, and the fact that phases now last at most $\ARMNUM \log(s+s_0)$ steps in expectation, we can bound the regret in Equation~\ref{equ:small_regret_bound} by
+Using this tighter bound on the number of incentivizations,
+and the fact that phases now last at most $\ARMNUM \log(s+s_0)$ steps in expectation,
+we can bound the regret in Equation~\eqref{equ:small_regret_bound} by
 %$71.11 \ARMNUM\Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1)\log(T+s_0)$
-$O\left(\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right)$.
+$O\left(\frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity \cdot (\log(T))^3}{\MinProb}\right)$.
 \end{proof}

### 2018-06-06 Discussion.tex
edits in Theorem 10
edits to Theorem 10

--- 2018-06-05 Discussion.tex
@@
 
-The proofs of Theorem~\ref{rst:budget} and Theorem~\ref{rst:regret} incur exponential (in \ARMNUM) payment and regret in the initial phases because the threshold required for incentivization $1/\log(s)$ decreases slowly.
-This slow decrease is needed to bound the regret in the later phases when the concentration inequality kicks in as in Equation~(\ref{equ:small_regret_bound}).
-In this section, we discuss two restrictions on the problem setting under which  we can modify the algorithm slightly and provide stronger bounds, avoiding this exponential dependence.
-Both problem settings are special cases of the more general problem setting previously considered.
+The proofs of Theorem~\ref{rst:budget} and Theorem~\ref{rst:regret}
+incur exponential (in \ARMNUM) payment and regret in the initial
+phases because the threshold $1/\log(s)$ required for incentivization
+decreases slowly. 
+This slow decrease is needed to bound the regret in the later phases
+when the concentration inequality kicks in as in
+Equation~(\ref{equ:small_regret_bound}).
+In this section, we discuss two restrictions under which we can
+modify the algorithm slightly and provide stronger bounds,
+avoiding this exponential dependence.
+Both problem settings are special cases of the more general
+setting previously considered.
 
@@
 \label{subsec:discrete}
-Discrete preferences by agents are captured by the following assumption (which states that the agents who are close to tied between two arms have measure 0):
+Discrete preferences by agents are captured by the following
+\dkedit{strengthening of Assumption~\ref{A1}},
+which states that the agents who are close to tied between
+two arms have measure 0:
 
@@
 \label{a:discrete}
-There is a positive $\delta_0$ such that
-$\AlmostTied{\delta_0} = 0$.
+There is a positive $\hat{z}$ such that
+$\AlmostTied{\hat{z}} = 0$.
 \end{assumption}
 
-When Assumption~\ref{a:discrete} holds, we restrict the payment-eligibility criterion by only incentivizing arms with much smaller probability to be pulled: an arm $i$ is \emph{payment-eligible} at time $t$ in phase $s$ when both of the following are true:
+When Assumption~\ref{a:discrete} holds,
+we restrict the payment-eligibility criterion by only incentivizing
+arms with much smaller probability to be pulled:
+an arm $i$ is payment-eligible at time $t$ in phase $s$ when both of
+the following are true:
+
 \begin{itemize}
-\item $i$ has been pulled at most
-$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
-\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors, the probability of pulling arm $i$ is less than $1/s$ (compared to $1/\log(s)$ in the general algorithm).
+\item $i$ has been pulled at most $s$ times up to time $t$,
+i.e., $\NumPull{t}{i} \leq s$.
+\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors,
+the probability of pulling arm $i$ is less than $1/s$
+(compared to $1/\log(s)$ in the general algorithm).
 \end{itemize}
 
-We refer to this modified version of Algorithm~\ref{alg:basic-incentivizing} as the \emph{Discrete-Preference Algorithm.}
-We outline a proof of the following result for this algortithm under Assumption~\ref{a:discrete} in Appendix~\ref{sec:discussion-proof1}.
+We refer to this modified version of
+Algorithm~\ref{alg:basic-incentivizing} as the
+\emph{Discrete-Preference Algorithm.}
+We outline a proof of the following result for this algortithm under
+Assumption~\ref{a:discrete} in Appendix~\ref{sec:discussion-proof1}.
 
@@
 \label{rst:discrete}
-Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment budget bounded above by 
-\begin{align*}
-O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
-\end{align*}
-and expected regret bounded above by 
-\begin{align}
-O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
-  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
-  \right).  \nonumber
-\end{align}
+Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm
+has expected payment bounded above by 
+$O \left(\ARMNUM^2/\MinProb \right)$
+and expected regret bounded above by $O(\ARMNUM / \MinProb)$.
 \end{theorem}
@@
 \subsubsection{Known \MinProb}
-An alternative useful assumption is that \MinProb (or a strictly positive lower bound on \MinProb) is known.
+An alternative useful assumption is that \MinProb
+(or a strictly positive lower bound on \MinProb) is known.
 
@@
 
-When this assumption holds, we choose a different modification in the definition of payment eligibility.
+When this assumption holds, we choose a different modification in the
+definition of payment eligibility.
 Let $s_0 = \exp(2/\MinProb)$.
 An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
-if both of the following hold:
+if both:
 \begin{itemize}
@@
 $s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
-\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors, the probability of pulling arm $i$ is less than $1/\log(s+s_0)$.
+\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors,
+the probability of pulling arm $i$ is less than $1/\log(s+s_0)$.
 \end{itemize}
@@
 significantly fewer arm pulls.
-We refer to this modified version of Algorithm~\ref{alg:basic-incentivizing} as the \emph{Known-\MinProb Algorithm.}
-We outline a proof of the following result for this algortithm under Assumption~\ref{a:known-p} in Appendix~\ref{sec:discussion-proof2}.
+We refer to this modified version of
+Algorithm~\ref{alg:basic-incentivizing} as the \emph{Known-\MinProb
+Algorithm.}
+We outline a proof of the following result for this algortithm under
+Assumption~\ref{a:known-p} in Appendix~\ref{sec:discussion-proof2}.
 
@@
 \label{rst:known-p}
-Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has expected payment budget bounded above by 
-\begin{align*}
-O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
-\end{align*}
+Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has
+expected payment  bounded above by  
+$O(\ARMNUM^2 \cdot \max(1,(\TieDensity/\MinProb)^{5/2}))$ 
 and expected regret bounded above by
-\begin{align*}
-O \left(\frac{\MAXR \ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
-  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
-  + \frac{\ARMNUM^2 d\MAXR}{\MinProb}
-  + \frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
-\end{align*}
+%\begin{align*}
+\dkedit{$O \left( \frac{\ARMNUM^2}{\MinProb^2}
+%  + \frac{\ARMNUM^2}{\hat{z}^2}+\frac{\ARMNUM}{\hat{z}^3}
+  +\frac{\ARMNUM \TieDensity \log^3(T)}{\MinProb}\right)$}.
+%  \end{align*}
 \end{theorem}

### 2018-06-06 Discussion.tex
spell check on body of paper

@@
 \emph{Discrete-Preference Algorithm.}
-We outline a proof of the following result for this algortithm under
+We outline a proof of the following result for this algorithm under
 Assumption~\ref{a:discrete} in Appendix~\ref{sec:discussion-proof1}.
@@
 Algorithm.}
-We outline a proof of the following result for this algortithm under
+We outline a proof of the following result for this algorithm under
 Assumption~\ref{a:known-p} in Appendix~\ref{sec:discussion-proof2}.

### 2018-06-06 Discussion.tex
resolving edits

--- 2018-06-06 Discussion.tex
@@
 Discrete preferences by agents are captured by the following
-\dkedit{strengthening of Assumption~\ref{A1}},
+strengthening of Assumption~\ref{A1},
 which states that the agents who are close to tied between
@@
 %\begin{align*}
-\dkedit{$O \left( \frac{\ARMNUM^2}{\MinProb^2}
+$O \left( \frac{\ARMNUM^2}{\MinProb^2}
 %  + \frac{\ARMNUM^2}{\hat{z}^2}+\frac{\ARMNUM}{\hat{z}^3}
-  +\frac{\ARMNUM \TieDensity \log^3(T)}{\MinProb}\right)$}.
+  +\frac{\ARMNUM \TieDensity \log^3(T)}{\MinProb}\right)$.
 %  \end{align*}

### 2018-07-04 Poster/poster.tex
added poster and slides to git

%==============================================================================
%== template for LATEX poster =================================================
%==============================================================================
%
%--A0 beamer slide-------------------------------------------------------------
\documentclass[final]{beamer} % use beamer
\usepackage[orientation=landscape,
            size=a0,          % poster size
            scale=1.2         % font scale factor
           ]{beamerposter}    % beamer in poster size

\usepackage{algorithmic}
\usepackage{enumitem}

%
%--some needed packages--------------------------------------------------------
\usepackage[american]{babel}  % language 
\usepackage{amsmath,amsthm, amssymb, latexsym}
\usepackage[utf8]{inputenc}   % std linux encoding
%\usepackage[authoryear]{natbib}
\usepackage[backend=bibtex, style=numeric, url=false, doi=false,isbn=false]{biblatex}
\bibliography{skipfree}
%\usepackage[doi=false,isbn=false]{biblatex}
%
%==The poster style============================================================
\usetheme{cpbgposter}            % our poster style
%--set colors for blocks (without frame)---------------------------------------
  \setbeamercolor{block title}{fg=nred,bg=white}
  \setbeamercolor{block body}{fg=black,bg=white}
%--set colors for alerted blocks (with frame)----------------------------------
%--textcolor = fg, backgroundcolor = bg, dblue is the jacobs blue
  \setbeamercolor{block alerted title}{fg=white,bg=nred!70}%frame color
  \setbeamercolor{block alerted body}{fg=black,bg=nred!10}%body color
%
%\theoremstyle{plain}
%\newtheorem{proposition}{Proposition}
%\newtheorem{claim}{Claim}
%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}
%\newtheorem{corollary}{Corollary}

%\theoremstyle{definition}
%\newtheorem{definition}{Definition}
%\newtheorem{example}{Example}[section]

%\theoremstyle{remark}
%\newtheorem{rk}{Remark}

%==Titel, date and authors of the poster=======================================
\title{Incentivizing Exploration By Heterogeneous Users}
\author{Bangrui Chen\footnotemark[1], Peter I. Frazier\footnotemark[1] \& David Kempe\footnotemark[2]}
\institute[ORIE]
          {\footnotemark[1] ORIE, Cornell University; \footnotemark[2] Department of Computer Science, USC}
\date{\today}
%
%==some usefull qm commands====================================================
%  |x>
\newcommand{\ket}[1]{\left\vert#1\right\rangle}
%  <x|
\newcommand{\bra}[1]{\left\langle#1\right\vert}
%  <x|y>
\newcommand{\braket}[2]{\left< #1 \vphantom{#2}\,
                        \right\vert\left.\!\vphantom{#1} #2 \right>}
%  <x|a|y>
\newcommand{\sandwich}[3]{\left< #1 \vphantom{#2 #3} \right|
                          #2 \left|\vphantom{#1 #2} #3 \right>}
%  d/dt
\newcommand{\ddt}{\frac{d}{dt}}
%  D/Dx
\newcommand{\pdd}[1]{\frac{\partial}{\partial#1}}
%  |x|
\newcommand{\abs}[1]{\left\vert#1\right\vert}
%  k_{x}
\newcommand{\kv}[1]{\mathbf{k}_{#1}}
%==============================================================================
%==the poster content==========================================================
%==============================================================================
\begin{document}
%--the poster is one beamer frame, so we have to start with:
\begin{frame}[t]
%--to seperate the poster in columns we can use the columns environment
\begin{columns}[t] % the [t] options aligns the columns content at the top
%--the left column-------------------------------------------------------------
\begin{column}{0.28\paperwidth}% the right size for a 3-column layout
%--abstract block--------------------------------------------------------------
\begin{alertblock}{Abstract}
\begin{itemize}[label=\textbullet]
\item We consider the problem of incentivizing exploration with heterogeneous agents. 
\item Under the assumption that each arm is preferred by at least a fraction $p > 0$ of agents, we propose an algorithm that achieves expected cumulative regret of $O(Ne^{2/p} + N \log^{3}(T))$, using expected cumulative payments of $O(N^{2}e^{2/p})$. 
\item If $p$ is known or the distribution over agent preferences is discrete, the exponential term $e^{2/p}$ can be replaced with suitable polynomials in $N$ and $1/p$. 
\item For discrete preferences, the regret’s dependence on T can be eliminated entirely, giving constant (depending only polynomially on N and 1/p) expected regret and payments.
%\item We give variance bounds of the Markov chain in terms of the proposed gap
\end{itemize}
\end{alertblock}
\vskip2ex
%--requirements block-----------------------------------------------------------

\begin{block}{Preliminaries}
\begin{itemize}[label=\textbullet]
\item In this problem, $N$ bandit arms provide vector-valued outcomes equal to an unknown arm-specific attribute vector $u_{i}\in \mathbb{R}^{d}$, perturbed by independent noise. 
\item Agents arrive sequentially with preference vector $\theta_t$ and choose arms to pull based on their own private and heterogeneous linear utility functions over attributes and the estimates of the arms’ attribute vectors $\hat{u}_{i,t}$, derived from observations of other agents’ past pulls. 
\item Agents are myopic and selfish and thus would choose the arm with maximum estimated utility, i.e. they will pull arm $i_t = \arg\max_{i}\{\theta_{t}\cdot \hat{u}_{i,t}\}$.
\item  A principal, knowing only the distribution from which agents’ preferences are drawn, but not the specific draws, can offer arm-specific incentive payments $c_{t,i}$ to encourage agents to explore underplayed arms. 
\item We define the regret at time $t$ as $r_t = (\max_{i} \theta_t \cdot u_i) - \theta_t \cdot u_{i_t}$ and payment $c_t = c_{t,i_t}$.
\item The principal seeks to minimize the total expected cumulative regret incurred by agents relative to their best arms, while also making a small expected cumulative payment.
\end{itemize}
\end{block}

\begin{block}{Literature Review}
Two recent lines of work have shown that effecting a societally near-optimal outcome in this setting requires explicitly inducing exploration:
\begin{itemize}[label=\textbullet]
\item Kremer et al. (2014) and Mansour et al. (2015, 2016, 2018) (see Slivkins (2017) for an overview) assume that the principal has an informational advantage in being the only one to observe the results of past arm pulls (as in driving route recommendations). The principal can use her advantage to induce exploration by recommending apparently sub-optimal arms, as long as agents cannot do better on their own.
\item Frazier et al. (2014) and Han et al. (2015) instead assume that the results of all past arm pulls are publicly observable (as on a review-sharing site). They suppose that the principal can incentivize exploration by offering arm-specific reward payments.
\end{itemize}
In this work, we present the first algorithm and analysis (of which we are aware) for incentivizing exploration when users have heterogeneous preferences over arms.\end{block}
\end{column}

\begin{column}{0.28\paperwidth}

\begin{block}{Key Assumptions}
\begin{itemize}[label=\textbullet]
\item (\textbf{Every arm is someone's best}) Each arm $i$ has a strictly positive proportion of users for whom $i$ is the best arm. We use $p$ to denote the minimum (over all arms) fraction of users that prefer any particular arm.
\item (\textbf{Not too many near-ties}) Let $q(z)$ be the cumulative distribution function of those agents whose utility difference between their best and second best arm is less than or equal to $z$, then there exists a $\hat{z}>0$, $L$ such that $q(z)\leq L\cdot z$ for all $z\leq \hat{z}$.
\item (\textbf{Compact Support}) $\theta$ has a compact support set contained in $[0,D]^{d}$.
\end{itemize}
\end{block}

\begin{block}{Main Results}
\begin{alertblock}{Theorem 1}
With the previously stated assumptions, there is a policy that achieves expected 
cumulative regret $O (N e^{2/p} + L N \log^3(T))$,
using expected cumulative payments of $O(N^2 e^{2/p})$.
\newline
\newline
In particular, when agents who are close to tied between two arms have measure $0$,
both the expected regret and expected payment are bounded by constants
(with respect to $T$). 
\end{alertblock}
\end{block}

\begin{block}{Algorithm}

\textbf{Notations:}
\vspace{0.5cm}
\begin{itemize}[label=\textbullet]
\item Phase: Our algorithm divides time into \emph{phases} $s = 1, 2, 3, \ldots$. Phase $s$ starts when each arm has been pulled at least $s$ times. We use $m_{t,i}$ to denote the number of pulls for arm $i$ up to time $t$ and indicate the start time of phase $s$ by $t_s$. 
\item Payment-eligible: An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$) if both of the following hold:
\begin{itemize}[label=\textbullet]
\item $i$ has been pulled at most $s$ times up to time $t$, i.e., $m_{t,i} \leq s$.
\item  The conditional probability of pulling arm $i$ is less than$1/\log(s)$ given the current estimates $\hat{u}_{t,i'}$ of the arms' attribute vectors.  
\end{itemize}
\end{itemize}

\vspace{0.5cm}
\textbf{Our Algorithm:}
\vspace{0.5cm}

\begin{algorithmic}
\STATE Set the current phase number $s = 1$.
\COMMENT{Each arm is pulled once initially ``for free.''}
\FOR{time steps $t = 1, 2, 3, \ldots$} {
\IF {$m_{t,i} \geq s+1$ for all arms $i$}
\STATE Increment the phase $s = s + 1$.
\ENDIF
\IF {there is a payment-eligible arm $i$} 
    \STATE Let $i$ be an arbitrary payment-eligible arm.
    \STATE Offer payment $c_{t,i} = \max_{\theta,i'} \theta \cdot (\hat{\mu}_{t,i'} - \hat{\mu}_{t,i})$ for pulling arm $i$ (and payment 0 for all other arms).
\ELSE
    \STATE Let agent $t$ play myopically, i.e., offer payments 0 for all arms.
\ENDIF 
}\ENDFOR
\end{algorithmic}

\end{block}

\end{column}

\begin{column}{0.28\paperwidth}

\begin{block}{Proof Sketch}
The key technical lemma in our proof is a Hoeffding-like concentration inequality that holds for a random, adaptively chosen number of samples.

\vspace{1cm}

\textbf{Payment Proof:}
\begin{itemize}[label=\textbullet]
\item For the early phases, we crudely bound the number of payment by $N$ for each phase;
\item For the later phases, we uses our technical lemma to rule out any incentives unless large misestimates of the arm locations occur, which is exponentially unlikely as the phase advances.
\end{itemize}

\vspace{1cm}

\textbf{Regret Proof:}
\begin{itemize}[label=\textbullet]
\item Regret occurred when an agent was incentivized to pull a sub-optimal arm: the analysis here is very similar to the payment proof;
\item Regret occurred when an agent myopically pulled a suboptimal arm: in this case, we define a phase-dependent cutoff to further distinguish agents based on their regret.
\begin{itemize}[label=\textbullet]
\item For those agents incurring large regret, which requires severe misestimates of arm locations and such misestimates are exponentially unlikely to occur, we use the following analysis to bound the regret:
\begin{itemize}[label=$\star$]
\item the technical lemma suggests this happens with exponentially decreasing probability;
\item based on our compact support assumption, the maximum regret is bounded above by a constant;
\end{itemize}
\item For those agents incurring small positive regret, which requires these agents to be almost tied in their preference for the best arm, we use the following analysis to bound the regret: 
\begin{itemize}[label=$\star$] 
\item there are not so many agents have near-ties preferences; 
\item the maximum regret is bounded above by the phase-dependent cutoff;
\end{itemize}
\end{itemize}
\end{itemize}
\vspace{1cm}

%\textbf{Lower Bound:}

%In our current setting, a logarithmic dependence on $T$ is typically unavoidable for any incentivization strategy when at least one arm falls below the Pareto frontier, as we no longer have free exploration of all arms.

\end{block}

\begin{block}{References}
[1] Ilan Kremer, Yishay Mansour, and Motty Perry. Implementing the “wisdom of the crowd”. Journal of Political Economy, 122(5):988–1012, 2014. \newline
[2] Yishay Mansour, Aleksandrs Slivkins, and Vasilis Syrgkanis. Bayesian incentive-compatible bandit exploration. In Proceedings of the 16th ACM Conference on Economics and Computation (EC), pages 565–582. ACM, 2015. \newline
[3] Yishay Mansour, Aleksandrs Slivkins, Vasilis Syrgkanis, and Zhiwei Steven Wu. Bayesian explo- ration: Incentivizing exploration in bayesian games. In Proceedings of the 17th ACM Conference on Economics and Computation (EC), 2016. \newline
[4] Yishay Mansour, Aleksandrs Slivkins, and Zhiwei Steven Wu. Bayesian exploration: Incentivizing exploration in bayesian games. In Proceedings of the 9th Innovations in Theoretical Computer Science (ITCS) conference, 2018. \newline
[5] Aleksandrs Slivkins. Incentivizing exploration via information asymmetry. ACM Crossroads, 24 (1):38–41, 2017. \newline
[6] Peter Frazier, David Kempe, Jon Kleinberg, and Robert Kleinberg. Incentivizing exploration. In Proceedings of the 15th ACM conference on Economics and Computation (EC), pages 5–22. ACM, 2014. \newline
[7] Li Han, David Kempe, and Ruixin Qiang. Incentivizing exploration with heterogeneous value of money. In Proceedings of the 11th International Conference on Web and Internet Economics (WINE), pages 370–383. Springer, 2015.
\end{block}
\end{column}
\end{columns}
\end{frame}
\end{document}

### 2018-07-04 Poster/poster.tex
edits to poster

@@
 \begin{itemize}[label=\textbullet]
-\item We consider the problem of incentivizing exploration with heterogeneous agents. 
-\item Under the assumption that each arm is preferred by at least a fraction $p > 0$ of agents, we propose an algorithm that achieves expected cumulative regret of $O(Ne^{2/p} + N \log^{3}(T))$, using expected cumulative payments of $O(N^{2}e^{2/p})$.
-\item If $p$ is known or the distribution over agent preferences is discrete, the exponential term $e^{2/p}$ can be replaced with suitable polynomials in $N$ and $1/p$. 
-\item For discrete preferences, the regret’s dependence on T can be eliminated entirely, giving constant (depending only polynomially on N and 1/p) expected regret and payments.
+\item We consider incentivizing exploration with heterogeneous agents. 
+\item When each arm is preferred by at least a fraction $p > 0$ of agents, our algorithm achieves expected cumulative regret of $O(Ne^{2/p} + N \log^{3}(T))$ using expected cumulative payments of $O(N^{2}e^{2/p})$.
+\item If $p$ is known or the distribution over agent preferences is discrete, the exponential term $e^{2/p}$ can be replaced with polynomials in $N$ and $1/p$. 
+\item For discrete preferences, the regret’s dependence on T can be eliminated, giving constant (depending only polynomially on N and 1/p) expected regret and payments.
 %\item We give variance bounds of the Markov chain in terms of the proposed gap
@@
 
-\begin{block}{Preliminaries}
+\begin{block}{Model}
 \begin{itemize}[label=\textbullet]
-\item In this problem, $N$ bandit arms provide vector-valued outcomes equal to an unknown arm-specific attribute vector $u_{i}\in \mathbb{R}^{d}$, perturbed by independent noise. 
-\item Agents arrive sequentially with preference vector $\theta_t$ and choose arms to pull based on their own private and heterogeneous linear utility functions over attributes and the estimates of the arms’ attribute vectors $\hat{u}_{i,t}$, derived from observations of other agents’ past pulls.
-\item Agents are myopic and selfish and thus would choose the arm with maximum estimated utility, i.e. they will pull arm $i_t = \arg\max_{i}\{\theta_{t}\cdot \hat{u}_{i,t}\}$.
-\item  A principal, knowing only the distribution from which agents’ preferences are drawn, but not the specific draws, can offer arm-specific incentive payments $c_{t,i}$ to encourage agents to explore underplayed arms.
-\item We define the regret at time $t$ as $r_t = (\max_{i} \theta_t \cdot u_i) - \theta_t \cdot u_{i_t}$ and payment $c_t = c_{t,i_t}$.
-\item The principal seeks to minimize the total expected cumulative regret incurred by agents relative to their best arms, while also making a small expected cumulative payment.
+\item $N$ bandit arms provide vector-valued outcomes equal to an unknown arm-specific attribute vector $u_{i}\in \mathbb{R}^{d}$, perturbed by independent noise. 
+\item Agents arrive sequentially.
+\item Agent $t$ sees estimates of the arms’ attribute vectors $\hat{u}_{i,t}$, which are averages of other agents’ past pulls. 
+\item Agents have heterogeneous linear preferences over arm attributes.
+\item Agent $t$ has preference vector $\theta_t$ drawn from a known distribution.
+\item A principal knows only the distribution from which agents’ preferences are drawn but not the specific draws.
+\item The principal can offer arm-specific incentive payments $c_{t,i}$ to encourage agents to explore underplayed arms. 
+\item Agents are myopic and selfish and choose the arm with maximum estimated utility, $i_t = \arg\max_{i}\{\theta_{t}\cdot \hat{u}_{i,t} + c_{t,i_t}\}$.
+\item The regret at time $t$ is $r_t = (\max_{i} \theta_t \cdot u_i) - \theta_t \cdot u_{i_t}$ and the payment is $c_t = c_{t,i_t}$.
+\item The principal seeks to minimize the total expected cumulative regret while also making a small expected cumulative payment.
 \end{itemize}
@@
 
-\textbf{Notations:}
+\textbf{Notation:}
 \vspace{0.5cm}
 \begin{itemize}[label=\textbullet]
-\item Phase: Our algorithm divides time into \emph{phases} $s = 1, 2, 3, \ldots$.
+\item Phase: We divide time into \emph{phases} $s = 1, 2, 3, \ldots$.
 Phase $s$ starts when each arm has been pulled at least $s$ times.
-We use $m_{t,i}$ to denote the number of pulls for arm $i$ up to time $t$ and indicate the start time of phase $s$ by $t_s$.
+$m_{t,i}$ denotes the number of pulls for arm $i$ up to time $t$.
+The start time of phase $s$ is $t_s$.
 \item Payment-eligible: An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$) if both of the following hold:

### 2018-07-04 Poster/poster.tex
changed the template

@@
-%==============================================================================
-%== template for LATEX poster =================================================
-%==============================================================================
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Jacobs Landscape Poster
+% LaTeX Template
+% Version 1.0 (29/03/13)
 %
-%--A0 beamer slide-------------------------------------------------------------
-\documentclass[final]{beamer} % use beamer
-\usepackage[orientation=landscape,
-            size=a0,          % poster size
-            scale=1.2         % font scale factor
-           ]{beamerposter}    % beamer in poster size
+% Created by:
+% Computational Physics and Biophysics Group, Jacobs University
+% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
+% 
+% Further modified by:
+% Nathaniel Johnston (nathaniel@njohnston.ca)
+%
+% This template has been downloaded from:
+% http://www.LaTeXTemplates.com
+%
+% License:
+% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
+%----------------------------------------------------------------------------------------
+%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
+%----------------------------------------------------------------------------------------
+
+\documentclass[final]{beamer}
+
+\usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster
 \usepackage{algorithmic}
-\usepackage{enumitem}
 
-%
-%--some needed packages--------------------------------------------------------
-\usepackage[american]{babel}  % language 
-\usepackage{amsmath,amsthm, amssymb, latexsym}
-\usepackage[utf8]{inputenc}   % std linux encoding
-%\usepackage[authoryear]{natbib}
-\usepackage[backend=bibtex, style=numeric, url=false, doi=false,isbn=false]{biblatex}
-\bibliography{skipfree}
-%\usepackage[doi=false,isbn=false]{biblatex}
-%
-%==The poster style============================================================
-\usetheme{cpbgposter}            % our poster style
-%--set colors for blocks (without frame)---------------------------------------
-  \setbeamercolor{block title}{fg=nred,bg=white}
-  \setbeamercolor{block body}{fg=black,bg=white}
-%--set colors for alerted blocks (with frame)----------------------------------
-%--textcolor = fg, backgroundcolor = bg, dblue is the jacobs blue
-  \setbeamercolor{block alerted title}{fg=white,bg=nred!70}%frame color
-  \setbeamercolor{block alerted body}{fg=black,bg=nred!10}%body color
-%
-%\theoremstyle{plain}
-%\newtheorem{proposition}{Proposition}
-%\newtheorem{claim}{Claim}
-%\newtheorem{theorem}{Theorem}
-%\newtheorem{lemma}{Lemma}
-%\newtheorem{corollary}{Corollary}
+\usetheme{confposter} % Use the confposter theme supplied with this template
 
-%\theoremstyle{definition}
-%\newtheorem{definition}{Definition}
-%\newtheorem{example}{Example}[section]
+\setbeamercolor{block title}{fg=ngreen,bg=white} % Colors of the block titles
+\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
+\setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
+\setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
+% Many more colors are available for use in beamerthemeconfposter.sty
 
-%\theoremstyle{remark}
-%\newtheorem{rk}{Remark}
+%-----------------------------------------------------------
+% Define the column widths and overall poster size
+% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
+% In this template, the separation width chosen is 0.024 of the paper width and a 4-column layout
+% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. (1-(4+1)*0.024)/4 = 0.22
+% Set twocolwid to be (2*onecolwid)+sepwid = 0.464
+% Set threecolwid to be (3*onecolwid)+2*sepwid = 0.708
 
-%==Titel, date and authors of the poster=======================================
-\title{Incentivizing Exploration By Heterogeneous Users}
-\author{Bangrui Chen\footnotemark[1], Peter I. Frazier\footnotemark[1] \& David Kempe\footnotemark[2]}
-\institute[ORIE]
-          {\footnotemark[1] ORIE, Cornell University; \footnotemark[2] Department of Computer Science, USC}
-\date{\today}
-%
-%==some usefull qm commands====================================================
-%  |x>
-\newcommand{\ket}[1]{\left\vert#1\right\rangle}
-%  <x|
-\newcommand{\bra}[1]{\left\langle#1\right\vert}
-%  <x|y>
-\newcommand{\braket}[2]{\left< #1 \vphantom{#2}\,
-                        \right\vert\left.\!\vphantom{#1} #2 \right>}
-%  <x|a|y>
-\newcommand{\sandwich}[3]{\left< #1 \vphantom{#2 #3} \right|
-                          #2 \left|\vphantom{#1 #2} #3 \right>}
-%  d/dt
-\newcommand{\ddt}{\frac{d}{dt}}
-%  D/Dx
-\newcommand{\pdd}[1]{\frac{\partial}{\partial#1}}
-%  |x|
-\newcommand{\abs}[1]{\left\vert#1\right\vert}
-%  k_{x}
-\newcommand{\kv}[1]{\mathbf{k}_{#1}}
-%==============================================================================
-%==the poster content==========================================================
-%==============================================================================
+\newlength{\sepwid}
+\newlength{\onecolwid}
+\newlength{\twocolwid}
+\newlength{\threecolwid}
+\setlength{\paperwidth}{48in} % A0 width: 46.8in
+\setlength{\paperheight}{36in} % A0 height: 33.1in
+\setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
+\setlength{\onecolwid}{0.30\paperwidth} % Width of one column
+\setlength{\twocolwid}{0.65\paperwidth} % Width of two columns
+\setlength{\topmargin}{-0.5in} % Reduce the top margin size
+%-----------------------------------------------------------
+
+\usepackage{graphicx}  % Required for including images
+
+\usepackage{booktabs} % Top and bottom rules for tables
+
+%----------------------------------------------------------------------------------------
+%	TITLE SECTION 
+%----------------------------------------------------------------------------------------
+
+\title{Incentivizing Exploration By Heterogeneous Users} % Poster title
+
+\author{Bangrui Chen\footnotemark[1], Peter I. Frazier\footnotemark[1] \& David Kempe\footnotemark[2]} % Author(s)
+
+\institute{\footnotemark[1] School of Operations Research and Information Engineering, Cornell University; \footnotemark[2] Department of Computer Science, USC} % Institution(s)
+
+%----------------------------------------------------------------------------------------
+
 \begin{document}
-%--the poster is one beamer frame, so we have to start with:
-\begin{frame}[t]
-%--to seperate the poster in columns we can use the columns environment
-\begin{columns}[t] % the [t] options aligns the columns content at the top
-%--the left column-------------------------------------------------------------
-\begin{column}{0.28\paperwidth}% the right size for a 3-column layout
-%--abstract block--------------------------------------------------------------
+
+\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks
+\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks
+
+\setlength{\belowcaptionskip}{2ex} % White space under figures
+\setlength\belowdisplayshortskip{2ex} % White space under equations
+
+\begin{frame}[t] % The whole poster is enclosed in one beamer frame
+
+\begin{columns}[t] % The whole poster consists of three major columns, the second of which is split into two columns twice - the [t] option aligns each column's content to the top
+
+\begin{column}{\sepwid}\end{column} % Empty spacer column
+
+\begin{column}{\onecolwid} % The first column
+
 \begin{alertblock}{Abstract}
-\begin{itemize}[label=\textbullet]
+
+\begin{itemize}
 \item We consider incentivizing exploration with heterogeneous agents. 
@@
 \item If $p$ is known or the distribution over agent preferences is discrete, the exponential term $e^{2/p}$ can be replaced with polynomials in $N$ and $1/p$. 
-\item For discrete preferences, the regret’s dependence on T can be eliminated, giving constant (depending only polynomially on N and 1/p) expected regret and payments.
-%\item We give variance bounds of the Markov chain in terms of the proposed gap
+\item For discrete preferences, the regret’s dependence on $T$ can be eliminated, giving constant (depending only polynomially on $N$ and $1/p$) expected regret and payments.
 \end{itemize}
+
 \end{alertblock}
-\vskip2ex
-%--requirements block-----------------------------------------------------------
 
 \begin{block}{Model}
-\begin{itemize}[label=\textbullet]
+\begin{itemize}
 \item $N$ bandit arms provide vector-valued outcomes equal to an unknown arm-specific attribute vector $u_{i}\in \mathbb{R}^{d}$, perturbed by independent noise. 
@@
 Two recent lines of work have shown that effecting a societally near-optimal outcome in this setting requires explicitly inducing exploration:
-\begin{itemize}[label=\textbullet]
+\begin{itemize}
 \item Kremer et al.
@@
 \end{itemize}
-In this work, we present the first algorithm and analysis (of which we are aware) for incentivizing exploration when users have heterogeneous preferences over arms.\end{block}
-\end{column}
+In this work, we present the first algorithm and analysis (of which we are aware) for incentivizing exploration when users have heterogeneous preferences over arms.
+\end{block}
 
-\begin{column}{0.28\paperwidth}
+\end{column} % End of the first column
+
+\begin{column}{\sepwid}\end{column} % Empty spacer column
+\begin{column}{\onecolwid} % The first column
 
 \begin{block}{Key Assumptions}
-\begin{itemize}[label=\textbullet]
+
+\begin{itemize}
 \item (\textbf{Every arm is someone's best}) Each arm $i$ has a strictly positive proportion of users for whom $i$ is the best arm.
@@
 \end{itemize}
+
 \end{block}
@@
 \vspace{0.5cm}
-\begin{itemize}[label=\textbullet]
+\begin{itemize}
 \item Phase: We divide time into \emph{phases} $s = 1, 2, 3, \ldots$.
@@
 \item Payment-eligible: An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$) if both of the following hold:
-\begin{itemize}[label=\textbullet]
+\begin{itemize}
 \item $i$ has been pulled at most $s$ times up to time $t$, i.e., $m_{t,i} \leq s$.
@@
 
+%----------------------------------------------------------------------------------------
 \end{column}
 
-\begin{column}{0.28\paperwidth}
+\begin{column}{\sepwid}\end{column} % Empty spacer column
+
+\begin{column}{\onecolwid} % The second column within column 2 (column 2.2)
 
@@
 \textbf{Payment Proof:}
-\begin{itemize}[label=\textbullet]
+\begin{itemize}
 \item For the early phases, we crudely bound the number of payment by $N$ for each phase;
@@
 \textbf{Regret Proof:}
-\begin{itemize}[label=\textbullet]
+\begin{itemize}
 \item Regret occurred when an agent was incentivized to pull a sub-optimal arm: the analysis here is very similar to the payment proof;
 \item Regret occurred when an agent myopically pulled a suboptimal arm: in this case, we define a phase-dependent cutoff to further distinguish agents based on their regret.
-\begin{itemize}[label=\textbullet]
+\begin{itemize}
 \item For those agents incurring large regret, which requires severe misestimates of arm locations and such misestimates are exponentially unlikely to occur, we use the following analysis to bound the regret:
-\begin{itemize}[label=$\star$]
+\begin{itemize}
 \item the technical lemma suggests this happens with exponentially decreasing probability;
@@
 \item For those agents incurring small positive regret, which requires these agents to be almost tied in their preference for the best arm, we use the following analysis to bound the regret: 
-\begin{itemize}[label=$\star$] 
+\begin{itemize}
 \item there are not so many agents have near-ties preferences; 
@@
 
-%\textbf{Lower Bound:}
-
-%In our current setting, a logarithmic dependence on $T$ is typically unavoidable for any incentivization strategy when at least one arm falls below the Pareto frontier, as we no longer have free exploration of all arms.
-
 \end{block}
-
 \begin{block}{References}
@@
 \end{block}
-\end{column}
-\end{columns}
-\end{frame}
+
+%----------------------------------------------------------------------------------------
+
+\end{column} % End of column 2.2
+
+\begin{column}{\sepwid}\end{column} % Empty spacer column
+
+\begin{column}{\onecolwid} % The third column
+
+%----------------------------------------------------------------------------------------
+
+\end{column} % End of the third column
+
+\end{columns} % End of all the columns in the poster
+
+\end{frame} % End of the enclosing frame
+
 \end{document}

### 2018-07-06 Poster/poster.tex
made some edits

@@
 
-\begin{alertblock}{Abstract}
+\begin{block}{Motivation}
+\begin{center}
+\includegraphics[scale=1]{example}
+\end{center}
 
-\begin{itemize}
-\item We consider incentivizing exploration with heterogeneous agents. 
-\item When each arm is preferred by at least a fraction $p > 0$ of agents, our algorithm achieves expected cumulative regret of $O(Ne^{2/p} + N \log^{3}(T))$ using expected cumulative payments of $O(N^{2}e^{2/p})$.
-\item If $p$ is known or the distribution over agent preferences is discrete, the exponential term $e^{2/p}$ can be replaced with polynomials in $N$ and $1/p$. 
-\item For discrete preferences, the regret’s dependence on $T$ can be eliminated, giving constant (depending only polynomially on $N$ and $1/p$) expected regret and payments.
-\end{itemize}
-
-\end{alertblock}
-
-\begin{block}{Model}
-\begin{itemize}
-\item $N$ bandit arms provide vector-valued outcomes equal to an unknown arm-specific attribute vector $u_{i}\in \mathbb{R}^{d}$, perturbed by independent noise. 
-\item Agents arrive sequentially.
-\item Agent $t$ sees estimates of the arms’ attribute vectors $\hat{u}_{i,t}$, which are averages of other agents’ past pulls. 
-\item Agents have heterogeneous linear preferences over arm attributes.
-\item Agent $t$ has preference vector $\theta_t$ drawn from a known distribution.
-\item A principal knows only the distribution from which agents’ preferences are drawn but not the specific draws.
-\item The principal can offer arm-specific incentive payments $c_{t,i}$ to encourage agents to explore underplayed arms. 
-\item Agents are myopic and selfish and choose the arm with maximum estimated utility, $i_t = \arg\max_{i}\{\theta_{t}\cdot \hat{u}_{i,t} + c_{t,i_t}\}$.
-\item The regret at time $t$ is $r_t = (\max_{i} \theta_t \cdot u_i) - \theta_t \cdot u_{i_t}$ and the payment is $c_t = c_{t,i_t}$.
-\item The principal seeks to minimize the total expected cumulative regret while also making a small expected cumulative payment.
-\end{itemize}
+An alternative that seems worse initially may remain unexplored because customers have no incentives to explore it!
 \end{block}
@@
 \begin{itemize}
-\item Kremer et al.
+\item \textbf{Without Money Transfer} Kremer et al.
 (2014) and Mansour et al.
-(2015, 2016, 2018) (see Slivkins (2017) for an overview) assume that the principal has an informational advantage in being the only one to observe the results of past arm pulls (as in driving route recommendations).
+(2015, 2016, 2018) assume that the principal has an informational advantage in being the only one to observe the results of past arm pulls (as in driving route recommendations).
 The principal can use her advantage to induce exploration by recommending apparently sub-optimal arms, as long as agents cannot do better on their own.
-\item Frazier et al.
+\item \textbf{With Money Transfer} Frazier et al.
 (2014) and Han et al.
@@
 \end{itemize}
-In this work, we present the first algorithm and analysis (of which we are aware) for incentivizing exploration when users have heterogeneous preferences over arms.
+In this work, we present the first algorithm/analysis for incentivizing exploration when users have heterogeneous preferences over arms and we prove \textbf{“heterogeneity provides free exploration"}.
+\end{block}
+
+\begin{block}{Model}
+\begin{itemize}
+\item $N$ bandit arms provide vector-valued outcomes equal to an unknown arm-specific attribute vector $u_{i}\in \mathbb{R}^{d}$, perturbed by independent noise. 
+\item Agents arrive sequentially and observe current estimates of the arms’ attribute vectors $\hat{u}_{i,t}$, which are averages of other agents’ past pulls. 
+\item Agents have heterogeneous linear preferences over arm attributes.
+\item Agent $t$ has preference vector $\theta_t$ drawn from a known distribution.
+\item A principal knows only the distribution from which agents’ preferences are drawn but not the specific draws.
+\item The principal can offer arm-specific incentive payments $c_{t,i}$ to encourage agents to explore underplayed arms. 
+\item Agents are myopic and choose the arm $i_t = \arg\max_{i}\{\theta_{t}\cdot \hat{u}_{i,t} + c_{t,i_t}\}$.
+\item The regret at time $t$ is $r_t = (\max_{i} \theta_t \cdot u_i) - \theta_t \cdot u_{i_t}$ and the payment is $c_t = c_{t,i_t}$.
+\item The principal seeks to minimize the total expected cumulative regret while also making a small expected cumulative payment.
+\end{itemize}
 \end{block}
@@
 \begin{itemize}
-\item (\textbf{Every arm is someone's best}) Each arm $i$ has a strictly positive proportion of users for whom $i$ is the best arm.
-We use $p$ to denote the minimum (over all arms) fraction of users that prefer any particular arm.
+\item (\textbf{Every arm is someone's best}) We use $p$ to denote the minimum (over all arms) fraction of users that prefer any particular arm.
 \item (\textbf{Not too many near-ties}) Let $q(z)$ be the cumulative distribution function of those agents whose utility difference between their best and second best arm is less than or equal to $z$, then there exists a $\hat{z}>0$, $L$ such that $q(z)\leq L\cdot z$ for all $z\leq \hat{z}$.
@@
 \begin{itemize}
-\item Phase: We divide time into \emph{phases} $s = 1, 2, 3, \ldots$.
-Phase $s$ starts when each arm has been pulled at least $s$ times.
-$m_{t,i}$ denotes the number of pulls for arm $i$ up to time $t$.
-The start time of phase $s$ is $t_s$.
+\item Phase: Phase $s$ starts when each arm has been pulled at least $s$ times. $m_{t,i}$ denotes the number of pulls for arm $i$ up to time $t$. 
 \item Payment-eligible: An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$) if both of the following hold:
@@
 \begin{block}{Proof Sketch}
-The key technical lemma in our proof is a Hoeffding-like concentration inequality that holds for a random, adaptively chosen number of samples.
+The key technical lemma in our proof is a Hoeffding-like concentration inequality that holds for a random, adaptively chosen number of samples (Zhao et al. 2016).
 
@@
 \item For the early phases, we crudely bound the number of payment by $N$ for each phase;
+\vspace{0.3cm}
 \item For the later phases, we uses our technical lemma to rule out any incentives unless large misestimates of the arm locations occur, which is exponentially unlikely as the phase advances.
@@
 \begin{itemize}
-\item Regret occurred when an agent was incentivized to pull a sub-optimal arm: the analysis here is very similar to the payment proof;
-\item Regret occurred when an agent myopically pulled a suboptimal arm: in this case, we define a phase-dependent cutoff to further distinguish agents based on their regret.
+\item Regret incurred when an agent was incentivized to pull a sub-optimal arm: the analysis here is very similar to the payment proof;
+\vspace{0.5cm}
+\item Regret incurred when an agent myopically pulled a suboptimal arm: in this case, we define a phase-dependent cutoff $\gamma(s(t))$ to distinguish agents based on their regret.
+\vspace{0.3cm}
 \begin{itemize}
-\item For those agents incurring large regret, which requires severe misestimates of arm locations and such misestimates are exponentially unlikely to occur, we use the following analysis to bound the regret:
+\item Agents with $r(t)\geq \gamma(s(t))$:
 \begin{itemize}
-\item the technical lemma suggests this happens with exponentially decreasing probability;
-\item based on our compact support assumption, the maximum regret is bounded above by a constant;
+\item this requires severe misestimates of arm locations and such misestimates are exponentially unlikely to occur;
+\vspace{0.1cm}
+\item since $\theta_t$ has a compact support, the maximum regret is bounded by a constant;
 \end{itemize}
-\item For those agents incurring small positive regret, which requires these agents to be almost tied in their preference for the best arm, we use the following analysis to bound the regret: 
+\vspace{0.3cm}
+\item Agents with $r(t)\leq \gamma(s(t))$: 
 \begin{itemize}
-\item there are not so many agents have near-ties preferences; 
-\item the maximum regret is bounded above by the phase-dependent cutoff;
+\item this requires agents to be almost tied in their preference for the best arm, but there are not so many agents have near-ties preferences;
+\vspace{0.1cm}
+\item the maximum regret is bounded above by $\gamma(s(t))$;
 \end{itemize}
@@
 \newline
-[5] Aleksandrs Slivkins. Incentivizing exploration via information asymmetry. ACM Crossroads, 24 (1):38–41, 2017. \newline
-[6] Peter Frazier, David Kempe, Jon Kleinberg, and Robert Kleinberg.
+[5] Peter Frazier, David Kempe, Jon Kleinberg, and Robert Kleinberg.
 Incentivizing exploration.
@@
 \newline
-[7] Li Han, David Kempe, and Ruixin Qiang.
+[6] Li Han, David Kempe, and Ruixin Qiang.
 Incentivizing exploration with heterogeneous value of money.
@@
 Springer, 2015.
+\newline
+[7] Shengjia Zhao, Enze Zhou, Ashish Sabharwal, and Stefano Ermon.
+Adaptive concentration inequal- ities for sequential decision problems.
+In Proceedings of the 30th Advances In Neural Information Processing Systems (NIPS), pages 1343–1351, 2016.
 \end{block}

### 2018-10-01 Discussion.tex
proposed general proof

@@
 Equation~(\ref{equ:small_regret_bound}).
-In this section, we discuss two restrictions under which we can
-modify the algorithm slightly and provide stronger bounds,
-avoiding this exponential dependence.
+\bccomment{In this secion, we first introduce a modified version of
+\textit{payment-eligible} definition with general probability threshold, and analyze
+its regret and payment bound. Then we discuss two restrictions under
+which we can provide stronger bounds, avoiding this exponential dependence.}
+%In this section, we discuss two restrictions under which we can
+%modify the algorithm slightly and provide stronger bounds,
+%avoiding this exponential dependence.
 Both problem settings are special cases of the more general
 setting previously considered.
+
+\bccomment{
+\subsubsection{General Algorithm}
+In this section, we introduce a more general definition of payment-eligible.
+More specifically, an arm $i$ is payment-eligible at time $t$ in phase $s$ when both of
+the following are true:
+
+\begin{itemize}
+\item $i$ has been pulled at most $s$ times up to time $t$,
+i.e., $\NumPull{t}{i} \leq s$.
+\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors,
+    the probability of pulling arm $i$ is less than $\phi(s)$
+\end{itemize}
+
+The general algorithm operates the same as Algorithm~\ref{alg:basic-incentivizing},
+except using the new definition of payment-eligible.
+
+With this definition of payment-eligible arms and probability threshold $\phi(s)$, we can
+prove
+
+\begin{theorem}
+\label{rst:general}
+With the probability threshold $\phi(s)$, the expected total payment for 
+Algorithm~\ref{alg:basic-incentivizing} is at most XXX, and the expected
+cumulative regret up to time T is bounded above by XXX.
+\end{theorem}
+}
 
@@
 arms with much smaller probability to be pulled:
-an arm $i$ is payment-eligible at time $t$ in phase $s$ when both of
-the following are true:
+\bccomment{we choose $\phi(s)=1/s$ (compared to $1/log(s)$ in Algorithm~\ref{alg:basic-incentivizing})}.
 
-\begin{itemize}
-\item $i$ has been pulled at most $s$ times up to time $t$,
-i.e., $\NumPull{t}{i} \leq s$.
-\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors,
-the probability of pulling arm $i$ is less than $1/s$
-(compared to $1/\log(s)$ in the general algorithm).
-\end{itemize}
+%an arm $i$ is payment-eligible at time $t$ in phase $s$ when both of
+%the following are true:
+
+%\begin{itemize}
+%\item $i$ has been pulled at most $s$ times up to time $t$,
+%i.e., $\NumPull{t}{i} \leq s$.
+%\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors,
+%the probability of pulling arm $i$ is less than $1/s$
+%(compared to $1/\log(s)$ in the general algorithm).
+%\end{itemize}
 
@@
 \emph{Discrete-Preference Algorithm.}
-We outline a proof of the following result for this algortithm under
-Assumption~\ref{a:discrete} in Appendix~\ref{sec:discussion-proof1}.
+\bccomment{
+    Plug $\phi(s)=1/s$ into Theorem~\ref{rst:general}, after some calculation (see details in XXX), we get:
+%We outline a proof of the following result for this algorithm under
+%Assumption~\ref{a:discrete} in Appendix~\ref{sec:discussion-proof1}.
 
-\begin{theorem}
+\begin{corollary}
 \label{rst:discrete}
@@
 and expected regret bounded above by $O(\ARMNUM / \MinProb)$.
-\end{theorem}
+\end{corollary}
+}
+
+%\begin{theorem}
+%\label{rst:discrete}
+%Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm
+%has expected payment bounded above by 
+%$O \left(\ARMNUM^2/\MinProb \right)$
+%and expected regret bounded above by $O(\ARMNUM / \MinProb)$.
+%\end{theorem}
 
@@
 definition of payment eligibility.
-Let $s_0 = \exp(2/\MinProb)$.
-An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
-if both:
-\begin{itemize}
-\item $i$ has been pulled at most
-$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
-\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors,
-the probability of pulling arm $i$ is less than $1/\log(s+s_0)$.
-\end{itemize}
+Let $s_0 = \exp(2/\MinProb)$ \bccomment{ and we set $\phi(s)=1/\log(s+s_0)$.}
+
+%An arm $i$ is \emph{payment-eligible} at time $t$ (in phase $s$)
+%if both:
+%\begin{itemize}
+%\item $i$ has been pulled at most
+%$s$ times up to time $t$, i.e., $\NumPull{t}{i} \leq s$.
+%\item Based on the current estimates \ArmEV{t}{i'} of all arms' attribute vectors,
+%the probability of pulling arm $i$ is less than $1/\log(s+s_0)$.
+%\end{itemize}
 
@@
 Algorithm.}
-We outline a proof of the following result for this algortithm under
-Assumption~\ref{a:known-p} in Appendix~\ref{sec:discussion-proof2}.
 
-\begin{theorem}
+\bccomment{
+Plug $\phi(s)=1/s$ into Theorem~\ref{rst:general}, after some calculation (see details in XXX), we get:
+\begin{corollary}
 \label{rst:known-p}
@@
 and expected regret bounded above by
+\begin{align*}
+O \left( \frac{\ARMNUM^2}{\MinProb^2}
+  +\frac{\ARMNUM \TieDensity \log^3(T)}{\MinProb}\right).
+\end{align*}
+\end{corollary}
+}
+
+%We outline a proof of the following result for this algorithm under
+%Assumption~\ref{a:known-p} in Appendix~\ref{sec:discussion-proof2}.
+
+%\begin{theorem}
+%\label{rst:known-p}
+%Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has
+%expected payment  bounded above by  
+%$O(\ARMNUM^2 \cdot \max(1,(\TieDensity/\MinProb)^{5/2}))$ 
+%and expected regret bounded above by
 %\begin{align*}
-$O \left( \frac{\ARMNUM^2}{\MinProb^2}
+%$O \left( \frac{\ARMNUM^2}{\MinProb^2}
 %  + \frac{\ARMNUM^2}{\hat{z}^2}+\frac{\ARMNUM}{\hat{z}^3}
-  +\frac{\ARMNUM \TieDensity \log^3(T)}{\MinProb}\right)$.
+%  +\frac{\ARMNUM \TieDensity \log^3(T)}{\MinProb}\right)$.
 %  \end{align*}
-\end{theorem}
+%\end{theorem}
